### 2014-07-28 TeXfiles/notes.tex
add note.tex file

\documentclass[12pt, a4paper]{article}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[francais,english]{babel}
\usepackage{refcheck}
\usepackage{xcolor}

\newcommand{\red}{\textcolor{red!95!black}}
\newcommand{\redm}{\textcolor{red!85!black}}
\newcommand{\blue}{\textcolor{blue!60!black}}
\newcommand{\green}{\textcolor{green!70!black}}
\newcommand{\black}{\textcolor{black}}
\newcommand{\orange}{\textcolor{red!50!yellow}}
\newcommand{\cyan}{\textcolor{green!50!blue}}
\newcommand{\yellow}{\textcolor{yellow}}

\setlength{\topmargin}{-0.5cm} \setlength{\textheight}{24cm}
\setlength{\textwidth}{15.5cm} \setlength{\oddsidemargin}{0.5cm}

\def\francais{\selectlanguage{francais}\hfuzz2pt }
\def\english{\selectlanguage{english}}

% general defs
\providecommand\mathbb{\bf}
\newcommand\R{{\mathbb R}}
\newcommand\N{{\mathbb N}}
\newcommand\Z{{\mathbb Z}}
\newcommand\T{{\mathbb T}}

\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{prop}{Property}[section]
\newtheorem{pro}{Proposition}[section]
\newtheorem{defi}{Definition}[section]
\newtheorem{coro}{Corollary}[section]
\newtheorem{remark}{Remark}[section]

\newcounter{Remark}
\newenvironment{Remark}
{\par\refstepcounter{Remark}
\medbreak\noindent\textbf{Remark~\theRemark.}} {\medbreak}
\renewcommand\theRemark{\arabic{Remark}}

\newcounter{steps}
\newenvironment{proof}[1][]{%
\par\medbreak\setcounter{steps}{0}
{\noindent\bfseries Proof#1. }} {\hfill\fbox{\ }\medbreak}
\newcommand\step{\par\smallbreak
\refstepcounter{steps} \noindent{\bf Step
\arabic{steps}.\unskip\quad}}
\newcounter{substeps}[steps]
\newcommand\substep{\par\smallbreak
\refstepcounter{substeps} \noindent{\bf Substep
\arabic{steps}.\alph{substeps}.\unskip\quad}}

%%%%%%%%%%%%%%%%%%%%

\newcommand{\xil}[0]{
\xi^\lambda}

\newcommand{\bl}[0]{
{\cal B}^\lambda}

\newcommand{\ble}[0]{
{\cal B}^{\lambda _\varepsilon}}

\newcommand{\cl}[0]{
{\cal C} ^\lambda}

\newcommand{\cle}[0]{
{\cal C}^{\lambda _\varepsilon}}

\newcommand{\ol}[0]{
{\cal O}_\lambda}

\newcommand{\radlo}[0]{
\sqrt{\lambda ^2 + \omega _c ^2}}

\newcommand{\intxv}[1]{
\int _{\R^2}\!\int _{\R^2} \!#1 \;\mathrm{d}v\mathrm{d}x}

\newcommand{\intx}[1]{
\int _{\R ^2} \!#1 \;\mathrm{d}x}

\newcommand{\intv}[1]{
\int _{\R ^2} \!#1 \;\mathrm{d}v}

\newcommand{\inttxv}[1]{
\int _{\R_+} \! \int _{\R^2}\!\int _{\R^2} \!#1 \;\mathrm{d}v\mathrm{d}x\mathrm{d}t}

\newcommand{\coctxv}[0]{
C^1 _c (\R_+ \times \R ^2 \times \R ^2)}

\newcommand{\coct}[0]{
C^1 _c (\R_+)}

\newcommand{\cocxv}[0]{
C^1 _c (\R ^2 \times \R ^2)}

\newcommand{\eps}[0]{
\varepsilon}

\newcommand{\epsk}[0]{
\varepsilon _k}

\newcommand{\fe}[0]{
f ^\varepsilon}

\newcommand{\ue}[0]{
u ^\varepsilon}

\newcommand{\uepsk}[0]{
u ^{\varepsilon _k}}

\newcommand{\re}[0]{
r ^\varepsilon}

\newcommand{\rez}[0]{
r ^{\varepsilon, 0}}

\newcommand{\reo}[0]{
r ^{\varepsilon, 1}}

\newcommand{\ren}[0]{
r ^{\varepsilon, n}}

\newcommand{\renpo}[0]{
r ^{\varepsilon, n + 1}}

\newcommand{\zez}[0]{
z ^{\varepsilon, 0}}

\newcommand{\zeo}[0]{
z ^{\varepsilon, 1}}

\newcommand{\zen}[0]{
z ^{\varepsilon, n}}

\newcommand{\zenpo}[0]{
z ^{\varepsilon, n + 1}}

\newcommand{\hen}[0]{
h ^{\varepsilon, n}}

\newcommand{\hez}[0]{
h ^{\varepsilon, 0}}

\newcommand{\heo}[0]{
h ^{\varepsilon, 1}}

\newcommand{\henpo}[0]{
h ^{\varepsilon, n + 1}}

\newcommand{\geps}[0]{
g ^\varepsilon}

\newcommand{\gez}[0]{
g ^{\varepsilon, 0}}

\newcommand{\geo}[0]{
g ^{\varepsilon, 1}}

\newcommand{\gen}[0]{
g ^{\varepsilon, n}}

\newcommand{\genpo}[0]{
g ^{\varepsilon, n + 1}}

\newcommand{\fek}[0]{
f ^{\varepsilon _k}}

\newcommand{\rek}[0]{
r ^{\varepsilon _k}}

\newcommand{\fo}[0]{
f ^1}

\newcommand{\fin}[0]{
f ^{\mathrm{in}}}

\newcommand{\fine}[0]{
f ^{\mathrm{in}}_{\varepsilon}}

\newcommand{\finek}[0]{
f ^{\mathrm{in}}_{\varepsilon _k}}

\newcommand{\Be}[0]{
B ^\varepsilon}

\newcommand{\Divx}[0]{
\mathrm{div}_x}

\newcommand{\Divv}[0]{
\mathrm{div}_v}

\newcommand{\Divxv}[0]{
\mathrm{div}_{x,v}}

\newcommand{\ran}[0]{
\mathrm{Range\;}}

\newcommand{\bB}[0]{
{\bold B}}

\newcommand{\ltxv}[0]{
L^2(\R ^2 \times \R ^2)}

\newcommand{\nxv}[0]{
\nabla_{x,v}}

\newcommand{\limn}[0]{
\lim _{n \to +\infty}}

\newcommand{\limk}[0]{
\lim _{k \to +\infty}}

\newcommand{\oc}[0]{
\omega _c (x)}

\newcommand{\tc}[0]{
T_c (x)}

\newcommand{\ave}[1]{
\left \langle #1 \right \rangle }

\newcommand{\D}[0]{
\mathrm{D}}

\newcommand{\lime}[0]{
\lim _{\varepsilon \searrow 0}}

% ----- SPACING -------
\baselinestretch\renewcommand{\baselinestretch}{1.5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\english

\title{Asymptotic preserving schemes for transport of charged particles under high magnetic fields}

\author{Miha\"{\i} Bostan
\thanks{Laboratoire d'Analyse, Topologie, Probabilit\'es LATP, Centre de Math\'ematiques et Informatique CMI, UMR CNRS 7353, 39 rue Fr\'ed\'eric Joliot Curie, 13453 Marseille  Cedex 13
France. E-mail : {\tt bostan@cmi.univ-mrs.fr}}
\!\!
C\'eline Caldini-Queiros
\thanks{Laboratoire de
Math\'ematiques de Besan{\c c}on, UMR CNRS 6623, Universit\'e de
Franche-Comt\'e, 16 route de Gray, 25030 Besan{\c c}on  Cedex
France. E-mail : {\tt celine.caldini@gmail.com}}
\!\!
Nicolas Crouseilles
\thanks{INRIA-Rennes Bretagne Atlantique,
ENS Cachan Bretagne, Projet IPSO France. Email : {\tt nicolas.crouseilles@inria.fr}}
\!\!
Mohammed Lemou
\thanks{IRMAR et Universit\'e de Rennes 1, Campus de Beaulieu 35042 Rennes France. Email : {\tt mohammed.lemou@univ-rennes1.fr}}
}

\date{ (\today)}

\maketitle

\begin{abstract}
One of the main topics in plasma physics concerns the energy production through thermonuclear fusion, which is achieved by magnetic confinement. From the mathematical point of view, the transport of charged particles under strong magnetic fields reduces to multiscale analysis. This paper deals with numerical schemes, based on micro-macro decomposition of the particle distribution function, which are uniformly consistent with the pde models for any order of the magnetic field. Numerical simulations, based on this approach, are presented for the resolution of the Vlasov equation.
\end{abstract}

\paragraph{Keywords:}
Vlasov equation, Gyrokinetic theory, Average operator, Asymptotic preserving scheme.

\paragraph{AMS classification:} 35Q75, 78A35, 82D10.

\section{Introduction}
\label{Intro}
\indent

Motivated by the confinement fusion, many research programs in plasma physics focus on strongly magnetized plasmas. Using the kinetic approach, we are led to the Vlasov equation
\begin{equation}
\label{Equ1} \partial _t \fe + v \cdot \nabla _x \fe + \frac{q}{m} ( E(x) + v \wedge \bB ^\eps (x) ) \cdot \nabla _v \fe = 0,\;\;(t,x,v) \in \R_+ \times \R ^3 \times \R ^3
\end{equation}
with the initial condition
\begin{equation}
\label{Equ2} \fe (0,x,v) = \fine (x,v),\;\;(x,v) \in \R ^3 \times \R ^3
\end{equation}
where $\fe = \fe (t,x,v) \geq 0$ is the distribution function of the particles in the phase space $(x,v) \in \R ^3 \times \R^3$, $m$ is the particle mass, $q$ is the particle charge and $(E, \bB ^\eps)$ stands for the electro-magnetic field. We consider here only the linear problem \eqref{Equ1}, \eqref{Equ2}, by assuming that $(E, \bB ^\eps)$ is a given smooth field. We are interested on the asymptotic behaviour of \eqref{Equ1} when the magnetic field becomes very large. Therefore we assume that
\[
\bB ^\eps (x) = \frac{\bB (x)}{\eps},\;\;\bB (x) = B(x) b(x),\;\;\Divx ( B b) = 0,\;\;0 < \eps <<1
\]
for some scalar positive function $B(x)$ and some field of unitary vectors $b(x)$.

It is well known that the particles turn around the magnetic lines at the cyclotronic frequency $q |\bB ^\eps|/m = q B/(m \eps)  \sim 1/\eps$, on Larmor circles of radius $\rho _L$ proportional to the reciprocal cyclotronic frequency {\it i.e.,} $\rho _L \sim \eps$. In the case of large magnetic fields ($\eps \searrow 0$) we deduce that the particles follow the magnetic lines ($\rho _L \searrow 0 $). Moreover, drift motions along the perpendicular directions (with respect to the magnetic lines) appear only at the next order, for example the electric cross field drift $E \wedge \bB ^\eps /|\bB ^\eps |^2 = \eps E\wedge b /B$. We take as observation unit a long time unit of order $1/\eps$ in such a way that the drift motions become significant at the dominant order
\[
\fe (t,x,v) = f^{\;\prime \eps} (t^{\;\prime}, x, v),\;\;t ^{\;\prime} = \eps t.
\]
%%
Denoting by $\oc = qB(x) /m$ the rescaled cyclotronic frequency, the Vlasov equation \eqref{Equ1} writes
\begin{equation}
\label{Equ3} \eps \partial _{t ^{\;\prime}} f^{\;\prime \eps} + v \cdot \nabla _x f^{\;\prime \eps} + \frac{q}{m} E(x) \cdot \nabla _v f^{\;\prime \eps} + \frac{\oc }{\eps} (v \wedge b(x) )\cdot \nabla _v f^{\;\prime \eps} = 0.
\end{equation}
From now on, we are dropping the prime, and we restrict our attention to the two dimensional problem, by neglecting the curvature of the magnetic field $\bB ^\eps = \frac{B(x)}{\eps} e_3$
\begin{equation}
\label{Equ4} \eps \partial _t \fe + \left (v \cdot \nabla _x + \frac{q}{m} E (x) \cdot \nabla _v     \right ) \fe + \frac{\oc }{\eps} \;^{\perp }v \cdot \nabla _v \fe = 0,\;\;(t,x,v) \in \R_+ \times \R ^2 \times \R ^2
\end{equation}
with the initial condition
\begin{equation}
\label{Equ5} \fe (0,x,v) = \fine (x,v),\;\;(x,v) \in \R ^2 \times \R ^2.
\end{equation}
%% 
A formal Hilbert expansion $\fe = f + \eps \fo + \eps ^2 f ^2 + ...$ leads to the system of transport equations
\begin{equation}
\label{Equ6} {\cal T} f = 0
\end{equation}
%%
\begin{equation}
\label{Equ7} a(x,v) \cdot \nabla _{x,v} f + {\cal T} f^1  = 0
\end{equation}
%%
\begin{equation}
\label{Equ8} \partial _t f + a(x,v) \cdot \nabla _{x,v} \fo + {\cal T} f^2 = 0
\end{equation}
%%
where $a(x,v) = (v, q E(x)/m)$ and ${\cal T} = \oc \;^{\perp}v\cdot \nabla _v$. The time evolution of the dominant distribution $f$ is given by \eqref{Equ8}, where the multipliers $f^1 (t), f^2(t)$ are such that at any moment $t$, the density $f(t)$ satisfies the constraints \eqref{Equ6}, \eqref{Equ7}. \red{The equation \eqref{Equ7} allows us to compute $\fo$ up to its projection on $\ker {\cal T}$, since ${\cal T}$ restricted to $(\ker {\cal T})^\perp$ is one to one, cf. Proposition \ref{TransportProp}. Denoting the orthogonal projection on $\ker {\cal T}$ by $\ave{\cdot}$ (since it coincides with the average along the flow of ${\cal T}$, cf. Proposition \ref{AverageProp}) we have
\begin{align}
\label{EquIntro1} 
\fo - \ave{\fo} = - {\cal T} ^{-1} ( a \cdot \nabla _{x,v} f).
\end{align}
As at any time $f(t,\cdot, \cdot)$ belongs to $\ker {\cal T}$, the closure for $f$ comes by averaging \eqref{Equ8}
\begin{equation}
\label{EquIntro2} \ave{\partial _t f } + \ave{a \cdot \nabla _{x,v} ( \fo - \ave{\fo})\;} + \ave{ a \cdot \nabla _{x,v} \ave{\fo}\;} + \ave{{\cal T} f^2} = 0.
\end{equation}
Since the flow of ${\cal T}$ is autonomous, the average and time derivative commute. Also notice that the average of any element in $\ran {\cal T}$ vanishes, since ${\cal T}$ is the derivative along its flow. By direct computation, in the case of the field $a = (v, qE(x)/m)$, we show that $\ave{a \cdot \nabla _{x,v} g } = 0$, for any $g \in \ker {\cal T}$. Substituting \eqref{EquIntro1} in \eqref{EquIntro2}, one gets
\begin{equation}
\label{EquContClosure} \partial _t f - \ave{ a \cdot \nabla _{x,v} ( {\cal T} ^{-1} ( a \cdot \nabla _{x,v} f ) ) \;} = 0.
\end{equation}
Moreover, it is shown that the term $- \ave{ a \cdot \nabla _{x,v} ( {\cal T} ^{-1} ( a \cdot \nabla _{x,v} f ) ) \;}$ reduces to a transport operator ${\cal C} \cdot \nabla _{x,v}f$ (see \eqref{Equ56} for the expression of the field ${\cal C}$), and the limit density $f = \lime \fe$ still satisfies a Vlasov like equation. 
}
%%
\begin{thm}
\label{WeakConv} Assume that the electro-magnetic field satisfies the hypotheses 
$$
E \in W^{1,\infty} (\R^2), \;\;\Divx \;^\perp E = 0,\;\;B \in W^{2,\infty}(\R^2),\;\;\inf _{x \in \R^2} B(x) >0.
$$
For any $\eps >0$ we denote by $\fe$ the unique weak solution of the Vlasov equation \eqref{Equ4} supplemented by the initial condition $\fine$. If the family $(\fine )_{\eps >0}$ converges weakly in $\ltxv$, when $\eps \searrow 0$, towards some function $\fin$ (not necessarily in $\ker {\cal T}$), then the family $(\fe)_{\eps>0}$  converges weakly $\star$ in $L^\infty( \R_+; \ltxv)$, when $\eps \searrow 0$, towards the unique weak solution $f$ of the problem
\begin{equation}
\label{Equ56} \partial _t f + \left ( \frac{^\perp E}{B} - \frac{|v|^2}{2 \omega _c} \;\frac{^\perp \nabla _x B}{B}     \right ) \cdot \nabla _x f + \frac{1}{2} \left ( \frac{^\perp E}{B} \cdot \frac{\nabla _x B}{B}  \right ) v \cdot \nabla _v f = 0,\;\;(t,x,v) \in \R_+ \times \R ^2\times \R ^2
\end{equation}
%%
\begin{equation}
\label{Equ57} f(0,\cdot, \cdot) = \mathrm{Proj} _{\ker {\cal T}} \fin.
\end{equation}
\end{thm}
%%
The proof of this convergence result follows by the arguments introduced in \cite{BosAsyAna}, \cite{BosGuidCent3D}, \cite{Bos12}. It relies on the notion of average along a characteristic flow (cf. \cite{BosTraSin}) and the commutation properties between the average operator and first order differential operators. Previous studies on strongly magnetized plasmas have been obtained in \cite{FreSon98}, \cite{FreSon01}.

Motivated by Theorem \ref{WeakConv}, when $\eps$ is very small, we can approximate the solution of \eqref{Equ4}, \eqref{Equ5} by the solution of \eqref{Equ56}, \eqref{Equ57}. The main advantage for doing this is that the limit model does not depend on $\eps$ and therefore we can appeal to standard explicit numerical schemes for solving it. On the contrary, at a given time step $\Delta t$, it is not possible to solve \eqref{Equ4}, \eqref{Equ5} by explicit methods when $\eps$ becomes small, since the CFL constraint imposes that $\Delta t \sim {\cal O} (\eps ^2)$.

Clearly, replacing $\fe$ by $f$ means that we neglect all the correction terms of orders $\eps, \eps ^2, ...$ in the Hilbert expansion $\fe = f + \eps \fo + \eps ^2 f ^2 + ...$, which is not reasonable when investigating intermediary regimes with $\eps \in \R_+ ^\star$. Therefore, we intend to design a numerical scheme which allows us to solve numerically \eqref{Equ4}, \eqref{Equ5} by using the same discretization parameters (basically the same time step, phase space grid size, ...) for any value of $\eps$ in the admissible range. Such numerical schemes, which are called Asymptotic Preserving (AP), have been introduced for the numerical simulation of the diffusion limits for kinetic equations \cite{Kla98}, \cite{Kla99}, \cite{JinParTos00}.

It will be shown that our scheme captures well the limit model \eqref{Equ56}, \eqref{Equ57}, since it degenerates to a discretization consistent to \eqref{Equ56}, \eqref{Equ57} when $\eps \searrow 0$. Surely, the main difficulties appear in the range of small $\eps$ and in that cases we know that the density function $\fe$ tends to some element of $\ker {\cal T}$. This motivates the splitting of the unknown $\fe$ into a dominant part, which coincides with the orthogonal projection on $\ker {\cal T}$, and a small reminder ({\it i.e.,} of order of $\eps$). Taking the projection of \eqref{Equ4} on $\ker {\cal T}$ and its orthogonal, leads to a system of two equations for the new independent unknowns $\geps :=\mathrm{Proj}_{\ker {\cal T}} \fe$, $\re :=\fe - \mathrm{Proj}_{\ker {\cal T}} \fe$. 
\red{More precisely we obtain, thanks to the identities $\ave{a \cdot \nxv \geps} = 0, \ave{{\cal T}\fe } = 0$
\begin{equation}
\label{EquIntro3} \partial _t \geps + \frac{1}{\eps} \ave{ a \cdot \nxv \re} = 0
\end{equation}
%%
\begin{equation}
\label{EquIntro4} \partial _t \re + \frac{1}{\eps} a \cdot \nxv \geps + \frac{1}{\eps} a \cdot \nxv \re - \frac{1}{\eps} \ave{a \cdot \nxv \re} + \frac{1}{\eps ^2} {\cal T} \re = 0.
\end{equation}
}
The high magnetic field affects only the time evolution of the reminder, requiring implicit methods, whereas the dominant part can be treated by explicit schemes. \red{For the moment we focus only on the time discretization
\begin{equation}
\label{EquIntro5} \frac{\genpo - \gen }{\Delta t} + \frac{1}{\eps} \ave{ a \cdot \nxv \renpo } = 0
\end{equation}
%%
\begin{equation}
\label{EquIntro6} \frac{\renpo - \ren}{\Delta t} + \frac{1}{\eps} a \cdot \nxv \gen + \frac{1}{\eps} a \cdot \nxv \ren - \frac{1}{\eps} \ave{ a \cdot \nxv \ren } + \frac{1}{\eps ^2} {\cal T} \renpo = 0,\;\;n \in \N.
\end{equation}
The point is that solving \eqref{EquIntro4} by implicit schemes allows us to compute the zero average part of $\fe$, uniformly with respect to $\eps >0$, since $\left ( \frac{\eps ^2}{\Delta t} I + {\cal T} \right ) ^{-1}$ remains uniformly bounded on the subspace of zero average functions (see Proposition \ref{UnifInv})
\begin{align}
\label{EquIntro7} \left ( \frac{\eps ^2}{\Delta t } I + {\cal T} \right )  & \frac{\renpo}{\eps}  = \\
& \frac{\eps ^2}{\Delta t} \left ( \frac{\ren}{\eps} \right ) -  a \cdot \nxv \gen - \eps a \cdot \nxv \left ( \frac{\ren}{\eps} \right ) + \eps \ave{a \cdot \nxv \left ( \frac{\ren}{\eps} \right ) }  .\nonumber 
\end{align}
As suggested by the continuous closure \eqref{EquContClosure}, we intend to substitute $\frac{\renpo}{\eps}$ in \eqref{EquIntro5}, which justifies our choice to evaluate $\re$ at time $t^{n+1}$ in \eqref{EquIntro5}. Clearly, the leading order term in \eqref{EquIntro7} is
\[
- \left ( \frac{\eps ^2}{\Delta t } I + {\cal T} \right )^{-1} ( a \cdot \nxv \gen ) = - {\cal T}^{-1} (a \cdot \nxv \gen ) + o(\eps)
\]
and therefore
\[
\frac{\genpo - \gen }{\Delta t} -  \ave{ a \cdot \nxv ( {\cal T}^{-1}(a \cdot \nxv \gen ) ) }  + o(\eps)= 0
\]
which proves the consistency with the continuous limit model (see Theorem \ref{Consistency}). Moreover, following the arguments developed when performing the continuous analysis, we show that the dominant term in $\ave{a \cdot \nxv \frac{\renpo}{\eps}}$ reduces to a transport operator ${\cal C}^\eps \cdot \nxv \gen$, whose advection field is determined explicitly, see Proposition \ref{Step3Bis}, and appears as a regular perturbation of the advection field ${\cal C}$ of the limit model \eqref{Equ56}
\[
{\cal C}^\eps = {\cal C} + O(\eps ^2).
\]
The complete scheme is detailed in \eqref{EquSch5}, \eqref{EquSch6}, \eqref{EquSch7}, \eqref{EquSch8}, \eqref{EquSch9}, \eqref{EquSch10} and by construction, can be solved with the same discretization parameters (time step, grid size) uniformly with respect to small values of $\eps$.}

Such kind of schemes, based on decomposition into dominant/fluctuation parts have been studied in \cite{BenLemMie08}, \cite{LemMie08}, \cite{CroLem11}. A new formulation, destinated to collisional models (Boltzmann equation for rarefied gases and the Landau-Fokker-Planck equation for plasmas) which avoids the inversion of the collisional operator at each time step, has been developped in \cite{Lem10}.

Our paper is organized as follows. In Section \ref{AveOpe} we introduce the notion of average operator and its main properties. The limit model is derived in Section \ref{LimMod}. After formal computations, a rigorous weak convergence result is presented. The numerical scheme is introduced in Section \ref{NumSch}. When $\eps \searrow 0$, we justify its consistency with respect to the limit model. The last Section \ref{NumSim} is devoted to numerical simulations.

\section{The average operator}
\label{AveOpe}
We recall briefly the construction of the average operator associated to the dominant advection field in \eqref{Equ4} {\it i.e.,} $(x,v) \to (0, \oc \;^\perp v )$. We consider the linear operator
\[
{\cal T} u = \Divv ( u \;\oc \;^\perp v)
\]
defined on the domain
\[
\D ({\cal T}) = \{ u(x,v) \in \ltxv\;:\; \Divv ( u \;\oc \;^\perp v) \in \ltxv \}.
\]
We denote by $\|\cdot \|$ the standard norm of $\ltxv$ and by $(X,V)(s;x,v)$ the characteristics of the field $ (x,v) \to (0, \oc \;^\perp v )$
\begin{equation}
\label{Equ21} \frac{\mathrm{d}X}{\mathrm{d}s} = 0,\;\;\frac{\mathrm{d}V}{\mathrm{d}s} = \omega _c (X(s;x,v)) \;^\perp V(s;x,v),\;\;(X,V)(0;x,v) = (x,v).
\end{equation}
It is easily seen that 
\begin{equation}
\label{Equ22}
X(s;x,v) = x,\;\;V(s;x,v) = {\cal R}(- \oc s) v
\end{equation}
where ${\cal R} (\theta) $ stands for the rotation of angle $\theta$
\begin{equation}\nonumber
{\cal R}(\theta) = \left (
\begin{array}{lll}
\cos \theta  &  -\sin \theta\\
\sin \theta  &\;\;\;   \cos \theta
\end{array}
\right ),\;\;\theta \in \R.
\end{equation}
Notice also that $\{\psi _ 1 = x_1, \psi _2 = x_2, \psi _3 = |v|\}$ is a family of independent prime integrals of this flow. The trajectories $(X,V)(s;x,v)$ are $\tc = 2\pi /\oc $ periodic, for any $(x,v) \in \R^2 \times \R^2$ and we introduce the average operator (cf. \cite{BosTraSin})
\begin{eqnarray}
\ave{u} (x,v) & = & \frac{1}{\tc} \int _0 ^{\tc} u (X(s;x,v), V(s;x,v))\;\mathrm{d}s \nonumber \\
& = & \frac{1}{2\pi} \int _0 ^{2\pi} u (x, {\cal R}(\alpha) v) \;\mathrm{d}\alpha \nonumber 
\end{eqnarray}
for any function $u \in \ltxv{}$. Clearly, the average operator depends only on the invariants $x_1, x_2, |v|$ and therefore $\ave{u} \in \ker {\cal T}$, for any 
$u \in \ltxv{}$. Moreover we prove (see \cite{BosGuidCent3D})
\begin{pro}
\label{AverageProp} The average operator is linear continuous. Moreover it coincides with the orthogonal projection on the kernel of ${\cal T}$ {\it i.e.,}
$$
\ave{u} \in \ker {\cal T}\;\mbox{ and }\;\intxv{(u - \ave{u}) \varphi } = 0,\;\;\forall \; \varphi \in \ker {\cal T}.
$$
\end{pro}
%%
Another key point relies on the solvability of the equation ${\cal T}u = w$. It is easily seen that if ${\cal T} u = w $ is solvable ({\it i.e.,} $w \in \ran {\cal T}$) then $\ave{w} = 0$. Indeed, for any function $\varphi \in \ker {\cal T}$ we have
\[
\intxv{(w - 0) \varphi } = \intxv{{\cal T} u \;\varphi } = - \intxv{u {\cal T}\varphi} = 0
\]
saying that $\ave{w} = 0$. On other words we have established the inclusion $\ran {\cal T} \subset \ker \ave{\cdot}$. Generally we can prove that $\overline{\ran {\cal T}} = \ker \ave{\cdot}$. This comes by using  that $\ave{\cdot} = \mathrm{Proj}_{\ker {\cal T}}$ and ${\cal T} ^\star = - {\cal T}$ as follows
\[
\ker \ave{\cdot} = \ker (\mathrm{Proj}_{\ker {\cal T}}) =
(\ker {\cal T} )^\perp = (\ker {\cal T}^\star ) ^\perp = \overline{\ran {\cal T}}.
\]
Under additional hypotheses the range of ${\cal T}$ is closed, leading to the characterization ~: ${\cal T }u  = w$ is solvable iff the right hand side $w$ has zero average. As in \cite{BosGuidCent3D} we establish the Poincar\'e inequality
\begin{pro}
\label{TransportProp}
We assume that $\inf _{x \in \R ^2} B (x)  >0$. \\
1. Then ${\cal T}$ restricted to $\ker \ave{\cdot}$ is one to one map onto $\ker \ave{\cdot}$. Its inverse, denoted ${\cal T}^{-1}$  belongs to ${\cal L }(\ker \ave{\cdot}, \ker \ave{\cdot} )$ and we have the Poincar\'e inequality
\begin{equation}
\label{EquPoincare} \|u \| \leq \frac{2 \pi }{|\omega _0 |} \|{\cal T} u \|,\;\;\omega _0 = \frac{q}{m} \inf _{x \in \R ^2} B(x) \neq 0
\end{equation}
for any $u \in \D({\cal T}) \cap \ker \ave{\cdot}$.\\
2. For any function $w \in \ker \ave{\cdot}$ with compact support
\[
\mathrm{supp} \;w \subset \{ (x,v) \in \R ^2 \times \R^2 \;:\; |x| \leq L_x,\;\;|v| \leq L_v\}
\]
the unique function $u \in \D({\cal T}) \cap \ker \ave{\cdot}$ such that ${\cal T } u  = w$ has the support contained in the same compact
\[
\mathrm{supp} \; u \subset \{ (x,v) \in \R ^2 \times \R^2 \;:\; |x| \leq L_x,\;\;|v| \leq L_v\}.
\]
\end{pro}
%%
Notice that the first order differential operators $b^1 \cdot \nxv = \partial _{x_1}$,  $b^2 \cdot \nxv = \partial _{x_2}$, $b^3 \cdot \nxv = \frac{v}{|v|} \cdot \nabla _v$ are commuting with the average operator $\ave{\cdot}$. Indeed, for any $u \in \ltxv{}$ such that $\partial _{x_i} u \in \ltxv{}$ we have
\[
\partial _{x_i} \ave{u} = \partial _{x_i}\left ( \frac{1}{2\pi} \int _0 ^{2\pi} u (x, {\cal R}(\alpha) v ) \;\mathrm{d}\alpha  \right ) =
\frac{1}{2\pi} \int _0 ^{2\pi} \partial _{x_i} u (x, {\cal R}(\alpha) v ) \;\mathrm{d}\alpha = \ave{\partial _{x_i} u }
\] 
and similarly, for any $u \in \ltxv{}$ such that $\frac{v}{|v|} \cdot \nabla _v u \in \ltxv{}$ we write
\begin{eqnarray}
\frac{v}{|v|} \cdot \nabla _v \ave{u} & = & \frac{v}{|v|} \cdot \nabla _v \left ( \frac{1}{2\pi} \int _0 ^{2\pi}  u (x, {\cal R}(\alpha) v ) \;\mathrm{d}\alpha   \right ) \nonumber \\
& = & \frac{v}{|v|} \cdot \frac{1}{2\pi} \int _0 ^{2\pi}  {^t {\cal R}} (\alpha) (\nabla _v u) (x, {\cal R}(\alpha) v ) \;\mathrm{d}\alpha \nonumber \\
& = & \frac{1}{2\pi} \int _0 ^{2\pi}  \frac{{\cal R} (\alpha) v}{|{\cal R} (\alpha)  v|} \cdot (\nabla _v u) (x, {\cal R}(\alpha) v ) \;\mathrm{d}\alpha \nonumber \\
& = & \ave{\frac{v}{|v|} \cdot \nabla _v u } \in \ltxv{}.\nonumber 
\end{eqnarray}
More generally, the following commutation formula between divergence and average holds

\begin{pro}
\label{DivAveCom} For any smooth vector field $\xi = \xi (x,v) \in \R^4$ we have
\[
\ave{\Divxv \xi} = \partial _{x_1} \ave{\xi _{x_1}} + \partial _{x_2} \ave{\xi _{x_2}} + \Divv \left \{\ave{\xi _v \cdot \frac{v}{|v|}} \frac{v}{|v|}   \right  \}.
\]
\end{pro}
%%
\begin{proof}
The previous computations allow us to write
\begin{eqnarray}
\label{EquC1} \ave{\Divxv \xi } & = & \ave{\partial _{x_1} \xi _{x_1}} + \ave{\partial _{x_2} \xi _{x_2}} + \ave{\Divv  \xi _v}  \\
& = & \partial _{x_1} \ave{\xi _{x_1}} + \partial _{x_2} \ave{\xi _{x_2}} + \ave{\Divv \left \{ \left (\xi _v \cdot \frac{v}{|v|}    \right ) \frac{v}{|v|}   \right \}} + \ave{\Divv \left \{ \left (\xi _v \cdot \frac{^\perp v}{|v|}    \right ) \frac{^\perp v}{|v|}   \right \}}.\nonumber
\end{eqnarray}
But 
\begin{eqnarray}
\Divv \left \{ \left (\xi _v \cdot \frac{v}{|v|}    \right ) \frac{v}{|v|}   \right \} & = & \left (\xi _v \cdot \frac{v}{|v|}    \right ) \Divv \left ( \frac{v}{|v|} \right ) + \frac{v}{|v|} \cdot \nabla _v \left ( \xi _v \cdot \frac{v}{|v|} \right ) \nonumber \\
& = &  \left (\xi _v \cdot \frac{v}{|v|}    \right )\frac{1}{|v|} +  \frac{v}{|v|}   \cdot \nabla _v \left (\xi _v \cdot \frac{v}{|v|}    \right ) \nonumber
\end{eqnarray}
implying that 
\begin{eqnarray}
\label{EquC2} \ave{\Divv \left \{ \left (\xi _v \cdot \frac{v}{|v|}    \right ) \frac{v}{|v|}   \right \}} & = & \Divv \left ( \frac{v}{|v|}  \right ) \ave{\xi _v \cdot \frac{v}{|v|} } + \frac{v}{|v|} \cdot \nabla _v \ave{\xi _v \cdot \frac{v}{|v|}} \nonumber \\
& = & \Divv \left \{ \ave{\xi _v \cdot \frac{v}{|v|} } \frac{v}{|v|}  \right \}.
\end{eqnarray}
The last term in \eqref{EquC1} vanishes since
\begin{equation}
\label{EquC3} \Divv \left \{ \left (\xi _v \cdot \frac{^\perp v}{|v|}    \right ) \frac{^\perp v}{|v|}   \right \} = {^\perp v} \cdot \nabla _v \left ( \xi _v \cdot \frac{^\perp v }{|v|^2} \right ) = {\cal T} \left (  \frac{\xi _v}{\omega _c} \cdot \frac{^\perp v}{|v|^2} \right ) \in \ker \ave{\cdot}.
\end{equation}
Our conclusion follows by combining \eqref{EquC1}, \eqref{EquC2}, \eqref{EquC3}.
\end{proof}
Notice also that the commutators of $b^1 \cdot \nxv$, $b^2 \cdot \nxv$, $b^3 \cdot \nxv$ with respect to ${\cal T}$ are given by
\[
[b^i\cdot \nxv , {\cal T}]= \frac{\nabla _x B}{B} {\cal T},\;\;i \in \{1,2\},\;\;
[b^3 \cdot \nxv, {\cal T}] = 0.
\]

\section{The limit model}
\label{LimMod}
We investigate now the model satisfied by the dominant density $f$. For that we have to eliminate $\fo, f^2$ from \eqref{Equ8}, by taking into account the constraints \eqref{Equ6}, \eqref{Equ7}. The constraint \eqref{Equ6} says that at any time $t$ the distribution $f(t)$ depends only on the invariants $x_1, x_2, |v|$
\[
\exists \;g = g(t,x,r)\;\mbox{ such that } f(t,x,v) = g(t,x,r = |v|).
\]
Notice that for such densities we have
\begin{equation}
\label{Equ34} \ave{a \cdot \nxv f} = \ave{v} \cdot \nabla _x g (t,x,|v|) + \frac{q}{m} E(x) \cdot \frac{\ave{v}}{|v|} \partial _r g (t,x,|v|) = 0
\end{equation}
since $\ave{v} = 0$. In that case the constraint \eqref{Equ7} writes
\[
{\cal T}(\fo - \ave{\fo} ) = - a(x,v) \cdot \nxv f
\]
and therefore 
\begin{equation}
\label{Equ35} \fo - \ave{\fo} = - {\cal T} ^{-1} (a(x,v) \cdot \nxv f).
\end{equation}
The idea is to construct a smooth divergence free vector field ${\cal B} \cdot \nxv $ satisfying $a \cdot \nxv = [{\cal T}, {\cal B} \cdot \nxv ]$ and mapping $\D({\cal B} \cdot \nxv ) \cap \ker {\cal T}$  to the subspace of zero average functions. Assume for the moment that such a vector field exists and let us see how we can use it.
%%
\begin{pro}
\label{Step2} For any function $f \in \D(a \cdot \nxv) \cap \D ( {\cal B} \cdot \nxv ) \cap \ker {\cal T}$ we have
\[
{\cal B} \cdot \nxv f \in \D ({\cal T})\;\mbox{ and } \; 
{\cal T} ^{-1} (a \cdot \nxv f ) = {\cal B} \cdot \nxv f.
\]
\end{pro}
%%
\begin{proof}
Consider a sequence of smooth functions $(f_n)_n$ such that the following convergences hold strongly in $\ltxv{}$
\[
\limn a\cdot \nxv f_n = a \cdot \nxv f,\;\;\limn {\cal B} \cdot \nxv f_n = {\cal B} \cdot \nxv f,\;\;\limn {\cal T} f_n = 0.
\]
By the definition of the vector field ${\cal B}$ we have
\[
a \cdot \nxv f_n = {\cal T} ( {\cal B} \cdot \nxv f_n) - {\cal B} \cdot \nxv ( {\cal T} f_n).
\]
Passing to the limit with respect to $n \to +\infty$ we deduce that ${\cal B} \cdot \nxv f \in \D({\cal T})$ and $a \cdot \nxv f = {\cal T} ({\cal B} \cdot \nxv f)$. Since we know that ${\cal B} \cdot \nxv $ maps the kernel of ${\cal T}$ to zero average functions, we deduce that
\[
{\cal T} ^{-1} (a \cdot \nxv f ) = {\cal B} \cdot \nxv f
\]
meaning that the unique zero average solution of ${\cal T} u = a \cdot \nxv f$ is given by $u = {\cal B} \cdot \nxv f$.

\end{proof}
%%
Combining \eqref{Equ35} and Proposition \ref{Step2}, we deduce that the constraint \eqref{Equ7} reduces to the following relation between the zero average part of the density $\fo$ and the dominant density $f$
\begin{equation}
\label{Equ36}
\fo - \ave{\fo} = - {\cal T} ^{-1} ( a \cdot \nxv f) = - {\cal B} \cdot \nxv f.
\end{equation}
Based on that, we eliminate $\fo$ and $f^2$ in \eqref{Equ8} and we will obtain the limit model for $f$. Recall that under the assumption in Proposition \ref{TransportProp} we have
\[
\ran {\cal T} = \overline{\ran {\cal T}} = \ker \ave{\cdot}.
\]
Then \eqref{Equ8} is equivalent to $\ave{\partial _t f + a \cdot \nxv \fo } = 0$. Taking into account that $\ave{\partial _t f} = \partial _t \ave{f} = \partial _t f $ and $\ave{ a \cdot \nxv \ave{\fo}} = 0$ (cf. \eqref{Equ34}) one gets
\[
\partial _t f + \ave{ a \cdot \nxv ( \fo - \ave{\fo}) } = 0.
\]
Using now \eqref{Equ36} yields the equation
\begin{equation}
\label{Equ37} \partial _t f - \ave{ a \cdot \nxv ( {\cal B} \cdot \nxv f ) } = 0
\end{equation}
which is, at least in this form, far from a Vlasov like equation, as expected from \eqref{Equ4}. We will see, performing some computations, that the second order term $a \cdot \nxv ( {\cal B} \cdot \nxv f )$ reduces after average to a first order term and finally the limit model remains a Vlasov like equation.
%%
\begin{pro}
\label{Step3}
There is a free divergence vector field ${\cal C}$ such that for any smooth function $f \in \ker {\cal T}$
\[
- \ave{a \cdot \nxv ( {\cal B} \cdot \nxv f)} = \Divxv ( f {\cal C}).
\]
The coordinates of ${\cal C} = ({\cal C}_x, {\cal C}_v) \in \R^4$ are given by
\[
{\cal C}_x = \ave{{\cal B}_v},\;\;{\cal C}_v = \ave{{\cal B} \cdot \nxv \frac{q}{m} \left ( E \cdot \frac{v}{|v|} \right ) } \frac{v}{|v|}.
\]
\end{pro}
%%
\begin{proof}
Using the formula $a \cdot \nxv = [{\cal T}, {\cal B} \cdot \nxv ]$ we have
\begin{eqnarray}
\label{Equ40} - \ave{a \cdot \nxv ( {\cal B} \cdot \nxv f )} & = & - \ave{{\cal T} {\cal B} \cdot \nxv ( {\cal B} \cdot \nxv f)} + \ave{{\cal B} \cdot \nxv ( {\cal T} ( {\cal B} \cdot \nxv f ))} \nonumber \\
& = & \ave{{\cal B} \cdot \nxv ( a \cdot  \nxv f) } 
\end{eqnarray}
since $\ran {\cal T} \subset \ker \ave{\cdot}$ and ${\cal T} ( {\cal B} \cdot \nxv f ) = a \cdot \nxv f$. Therefore there are no second order terms left in the expression of $\ave{a \cdot \nxv ( {\cal B} \cdot \nxv f)}$
\[
- \ave{a \cdot \nxv ( {\cal B} \cdot \nxv f)} = \frac{1}{2}\ave{[{\cal B} \cdot \nxv, a \cdot \nxv ]f} = \ave{\xi \cdot \nxv f}
\]
where $2\xi$ is the Poisson bracket between the vector fields $ {\cal B}$ and $a$. Since $\Divxv a = \Divxv {\cal B} = 0$, we have
\[
\Divxv \xi = \frac{1}{2}{\cal B} \cdot \nxv (\Divxv a) - \frac{1}{2} a \cdot \nxv ( \Divxv {\cal B}) = 0
\]
and therefore, by Proposition \ref{DivAveCom}, one gets
\begin{eqnarray}
\label{Equ41} - \ave{a \cdot \nxv ( {\cal B} \cdot \nxv f)} & = & \ave{\Divxv (f \xi)} \nonumber \\
& = & \Divx \ave{f \xi _x} + \Divv \left \{ \ave{f \xi _v \cdot \frac{v}{|v|}} \frac{v}{|v|}  \right \} \nonumber \\
& = & \Divx (f\ave{ \xi _x}) + \Divv \left \{ f \ave{ \xi _v \cdot \frac{v}{|v|}} \frac{v}{|v|}  \right \} \nonumber \\
& = & \Divxv (f {\cal C})
\end{eqnarray}
where ${\cal C} = \left ( \ave{\xi _x}, \ave{ \xi _v \cdot \frac{v}{|v|}} \frac{v}{|v|}\right )$. It remains to compute explicitely the coordinates of the vector field ${\cal C}$. Using \eqref{Equ40} with the function $\psi _i = x_i$, $i \in \{1,2\}$ we obtain
\[
\ave{\xi _{x_i}} = \ave{\xi \cdot \nxv \psi _i } = \frac{1}{2} \ave{[{\cal B} \cdot \nxv, a \cdot \nxv ] \psi _i }  = \ave{{\cal B} \cdot \nxv ( a \cdot \nxv \psi _i )} = \ave{{\cal B}_{v_i}}.
\]
Similarly, using the invariant $\psi _3 = |v|$ we deduce 
\begin{eqnarray}
\ave{\xi _v \cdot \frac{v}{|v|}} & = & \ave{\xi \cdot \nxv \psi _3 } = \frac{1}{2} \ave{[{\cal B} \cdot \nxv, a \cdot \nxv ] \psi _3 }  = \ave{{\cal B} \cdot \nxv ( a \cdot \nxv \psi _3 )} \nonumber \\
& = & \ave{{\cal B} \cdot \nxv \frac{q}{m} \left ( E \cdot \frac{v}{|v|} \right ) }\nonumber.
\end{eqnarray}
Clearly, taking $f = 1 \in \ker {\cal T}$ in \eqref{Equ41} yields $\Divxv {\cal C} = 0$.
\end{proof}
%%
By direct computation we obtain the following expression for the vector field ${\cal B}$ (see Proposition \ref{Step2Bis} for a more general result)
\begin{equation}
\label{Equ42} {\cal B} = \left ( - \frac{^\perp v}{\omega _c}, \frac{^\perp E}{B} - \left ( \frac{\nabla _x B}{B} \cdot \frac{v}{\omega _c} \right ) \;{^\perp v} \right)
\end{equation}
and the formula for the vector field ${\cal C}$ is given by
\begin{pro}
\label{CCoordinates} Assume that the electric field derives from a potential {\it i.e.,} $\Divx \;^\perp E = 0$. Then the vector field ${\cal C}$ writes
\begin{equation}
\label{Equ43} {\cal C} = \left (\frac{^\perp E}{B} - \frac{|v|^2}{2\omega _c} \;\frac{^\perp \nabla _x B}{B}, \frac{1}{2} \left (\frac{^\perp E}{B} \cdot \frac{\nabla _x B}{B}   \right ) v   \right ).
\end{equation}
\end{pro}
%%
\begin{proof}
We have 
$$
{\cal B}_x  = - \frac{^\perp v}{\omega _c},\;\;{\cal B}_v = \frac{^\perp E}{B} - \frac{^\perp v \otimes v}{B \omega _c} \nabla _x B.
$$
We use the formula
\[
\ave{v \otimes v} = \frac{|v|^2}{2} Id,\;\;\;\;\ave{^\perp v \otimes v } = \frac{|v|^2}{2} \left (
\begin{array}{rrr}
0  &  1\\
-1 &\;\;\;   0
\end{array}
\right )
\]
and therefore we obtain
\[
{\cal C}_x = \ave{{\cal B}_v} = \frac{^\perp E}{B} - \frac{|v|^2}{2B \omega _c } \;^\perp \nabla _x B = v_\wedge + v_{\mathrm{GD}}
\]
where $v _\wedge = {^\perp E}/B$ is the rescaled electric cross field drift and $v_{\mathrm{GD}} $ is the rescaled magnetic gradient drift (see \cite{HazMei03}). It remains to determine ${\cal C}_v$ and for that we need to compute $\ave{{\cal B} \cdot \nxv \left ( E \cdot \frac{v}{|v|}  \right ) }$. Notice that 
\begin{eqnarray}
{\cal B } \cdot \nxv  \left ( E \cdot \frac{v}{|v|}  \right ) & = & ({\cal B}_x \cdot \nabla _x ) E \cdot \frac{v}{|v|} + E \cdot ( {\cal B}_v \cdot \nabla _v ) \left ( \frac{v}{|v|} \right ) \nonumber \\
& = & \left ( \partial _x E\; {\cal B}_x , \frac{v}{|v|} \right ) + \left ( E, \partial _v \left ( \frac{v}{|v|} \right ) {\cal B}_v  \right ) \nonumber \\
& = & - ^t \partial _x E : \frac{^\perp v \otimes v}{\omega _c |v|} - \frac{E \otimes \nabla _x B}{B \omega _c } : \frac{^\perp v \otimes v}{|v|} - \frac{v \otimes v}{|v|^3} : \frac{^\perp E \otimes E}{B}. \nonumber
\end{eqnarray}
Taking the average leads to
\[
\ave{{\cal B } \cdot \nxv  \left ( E \cdot \frac{v}{|v|}  \right )} = \frac{1}{2\omega _c} \left ( ^\perp E \cdot \frac{\nabla _x B}{B} \right )
\]
and finally we obtain
\[
{\cal C}_v = \frac{1}{2}\left ( \frac{^\perp E}{B} \cdot \frac{\nabla _x B}{B} \right )v.
\]
\end{proof}
%%
\begin{pro}
\label{InvariantSubSpace} The operator ${\cal C} \cdot \nxv $ leaves invariant the subspaces $\ker {\cal T}$ and $\ker \ave{\cdot}$.
\end{pro}
%%
\begin{proof}
Notice that ${\cal C}$ is a linear combination of the vector fields $b^1, b^2, b^3$ with coefficients in $\ker {\cal T}$
\[
{\cal C} = \left ( \frac{E_2}{B} - \frac{|v|^2}{2\omega _c} \frac{\partial _{x_2}B}{B} \right ) b^1 - \left ( \frac{E_1}{B} - \frac{|v|^2}{2\omega _c} \frac{\partial _{x_1}B}{B} \right ) b^2 + \frac{|v|}{2}\;\frac{^\perp E \cdot \nabla _x B}{B^2} b^3.
\]
The fact that $\ker {\cal T}$ is left invariant by ${\cal C} \cdot \nxv$ follows by the same property of $b^i \cdot \nxv$, $i \in \{1,2,3\}$. Using the commutation properties between $b^i \cdot \nxv$ and the average operator, $i \in \{1,2,3\}$, we deduce that $\ker \ave{\cdot}$ is also left invariant by ${\cal C} \cdot \nxv$.
\end{proof}
%%
The previous arguments allow us to establish the weak convergence result stated in Theorem \ref{WeakConv}
\begin{proof} (of Theorem \ref{WeakConv})
It is well known that the $L^2$ norm is preserved in time
\[
\eps \frac{\mathrm{d}}{\mathrm{d}t} \intxv{ (\fe (t,x,v)) ^2} = 0 
\]
and therefore, since $(\fine)_\eps$ converges weakly in $\ltxv$, one gets 
\[
\sup _{\eps >0} \|\fe \|_{L^\infty(\R_+;\ltxv{})} = \sup _{\eps >0} \|\fine\| < +\infty.
\]
After extraction of a sequence $(\eps _k)_k$, $\limk \eps _k = 0$, we can assume that $(\fek)_k$ converges weakly $\star$ in $L^\infty(\R_+;\ltxv{})$ to some function $f \in L^\infty(\R_+;\ltxv{})$. Multiplying by $\epsk$ the weak formulation \eqref{Equ4} of $\fek$, it is easily seen that
\[
\inttxv{f(t,x,v) {\cal T} \varphi } = \limk \inttxv{\fek (t,x,v) {\cal T}\varphi } = 0
\]
for any $\varphi \in \coctxv{}$. We deduce that $f(t) \in \ker {\cal T}, t \in \R_+$. We consider now in the weak formulation of \eqref{Equ4} test functions of the form $\eta (t) \varphi (x,v)$ where $\eta \in \coct$ and $\varphi \in \cocxv \cap \ker {\cal T}$. 
\begin{equation}
\label{Equ45} - \inttxv{\!\!\eta ^{\;\prime}  \fek \varphi } - \eta (0) \!\!\intxv{\!\!\finek \varphi } - \frac{1}{\epsk} \inttxv{\!\!\eta  \fek \;a \cdot \nxv \varphi} = 0.
\end{equation}
Since ${\cal T } \varphi = 0$, we know by \eqref{Equ34} that $\ave{a \cdot \nxv \varphi } = 0$ and therefore
\[
\intxv{\ave{\fek (t)} a \cdot \nxv \varphi } = \intxv{\fek (t,x,v) \ave{a \cdot \nxv \varphi }} = 0.
\]
The equation \eqref{Equ45} can be written
\begin{eqnarray}
\label{Equ46} - \inttxv{\eta ^ {\;\prime} (t) \fek \varphi }  & - & \eta (0)\intxv{\finek \varphi }  \\
& = &  \inttxv{\eta (t) \frac{\fek - \ave{\fek}}{\epsk} a\cdot \nxv \varphi }.\nonumber
\end{eqnarray}
We intend to pass to the limit in \eqref{Equ46} when $k \to +\infty$. Clearly we have
\begin{equation}
\label{Equ48} \limk \inttxv{\eta ^{\;\prime} (t) \fek \varphi }= \inttxv{\eta ^{\;\prime} (t) f \varphi }
\end{equation}
and
\begin{equation}
\label{Equ49}
\limk \intxv{\finek \varphi } = \intxv{\fin \varphi } = \intxv{\ave{\fin} \varphi }.
\end{equation} 
For the treatment of the term in the right hand side of \eqref{Equ46} we introduce $\psi$ the unique smooth zero average function solving 
\[
{\cal T} \psi = - a \cdot \nxv \varphi.
\]
Indeed, the above equation has a unique zero average solution, by Proposition \ref{TransportProp}, since the right hand side has zero average. Moreover, this solution is given by $\psi = - {\cal B} \cdot \nxv \varphi$ cf. Proposition \ref{Step2}. We appeal one more time to the weak formulation \eqref{Equ4} with the test function $\eta (t) \psi (x,v)$
\begin{align*}
- \eps _k \inttxv{\!\!\eta ^{\;\prime}  \fek \psi }  & -  \epsk \eta (0) \!\!\intxv{\finek \psi } -  \!\!\inttxv{\!\!\eta  \fek a \cdot \nxv \psi }  \\
& = \inttxv{\eta  \frac{\fek - \ave{\fek}}{\epsk} {\cal T} \psi }
\end{align*}
leading to 
\begin{align*}
 -  \inttxv{\eta (t) & \frac{\fek - \ave{\fek}}{\epsk}  a \cdot \nxv \varphi }  =  
\inttxv{\eta (t) \frac{\fek - \ave{\fek}}{\epsk} {\cal T} \psi } \\
& =  - \epsk \inttxv{\eta ^{\;\prime}(t) \fek \psi } 
-  \epsk \eta (0) \intxv{\finek \psi } \\
& - \inttxv{\eta (t) \fek a \cdot \nxv \psi }.
\end{align*}
Passing to the limit when $k \to +\infty$ yields
\begin{align}
\label{Equ47}  - \!\!\limk \inttxv{\!\!\eta (t)  \frac{\fek - \ave{\fek}}{\epsk}  & a \cdot \nxv \varphi }  =  - \!\!\inttxv{\!\!\eta (t)  f a \cdot \nxv \psi }  \nonumber \\
& =  \inttxv{\eta (t)  f a \cdot \nxv ( {\cal B} \cdot \nxv \varphi ) }  \nonumber \\
& =  \inttxv{\eta (t) f \ave{a \cdot \nxv ( {\cal B} \cdot \nxv \varphi )}}  \nonumber \\
& - \inttxv{\eta (t) f \Divxv ( \varphi {\cal C}) }
\end{align}
where the last equality comes by Proposition \ref{Step3}. Combining \eqref{Equ46}, \eqref{Equ48}, \eqref{Equ49}, \eqref{Equ47} we deduce 
\begin{align}
\label{LimitModelForm}
 \inttxv{\!\!f \partial _t ( \eta \varphi )} & + \intxv{\!\!\ave{\fin} (\eta \varphi )(0,x,v)} \\
& +  \inttxv{\!\!f \Divxv (\eta \varphi {\cal C})} = 0 \nonumber
\end{align}
for any function $\eta \in \coct{}$ and $\varphi \in \cocxv{} \cap \ker {\cal T}$. Since we already know that $f(t) \in \ker {\cal T}, t \in \R_+$, the previous formula also holds true for any smooth zero average test function $\psi (x,v)$. Indeed, we have
\[
\inttxv{f \partial _t ( \eta \psi ) } = 0,\;\;\intxv{\ave{\fin} \eta (0) \psi (x,v)} = 0
\]
and
\[
\inttxv{f \eta (t)\; {\cal C}\cdot \nxv \psi } = 0
\]
since, by Proposition \ref{InvariantSubSpace}, we know that $\ave{{\cal C}\cdot \nxv \psi} = 0$. We deduce that \eqref{LimitModelForm} holds for any smooth test function, saying that $f$ solves weakly the Vlasov problem
\begin{equation}
\label{Equ50} \partial _t f + {\cal C} \cdot \nxv f = 0,\;\;(t,x,v) \in \R_+ \times \R ^2 \times \R ^2
\end{equation}
%%
\begin{equation}
\label{Equ51} f(0,x,v) = \ave{\fin}(x,v),\;\;(x,v) \in \R ^2 \times \R^2.
\end{equation}
By the uniqueness of the weak solution for \eqref{Equ50}, \eqref{Equ51} (which coincides with the solution by characteristics) we deduce that all the family $(\fe)_\eps$ converges weakly $\star$ in $L^\infty( \R_+;\ltxv{})$ towards $f$. 
\end{proof}
%%
\begin{remark}
\label{ConstraintPropag} The equation $\partial _t f + {\cal C} \cdot \nxv f = 0$ propagates the constraint ${\cal T} f = 0$. For checking that, notice that $[{\cal T}, {\cal C} \cdot \nxv ] = - (\;^\perp E \cdot \nabla _x B)/B^2 \;{\cal T}$. It is easily seen that ${\cal T}f$ solves the problem
\[
\partial _t ({\cal T}f) + {\cal C} \cdot \nxv ({\cal T}f) - \frac{^\perp E \cdot \nabla _x B}{B^2} \;{\cal T}f = 0,\;\;{\cal T}f |_{t = 0} = {\cal T}\ave{\fin} = 0
\]
and therefore, by the uniqueness of the weak solution we deduce that ${\cal T}f = 0$. Actually the point is that ${\cal C}\cdot \nxv $ leaves invariant $\ker {\cal T}$ (since the commutator $[{\cal T}, {\cal C}\cdot \nxv]$ is parallel to ${\cal T}$) and it is well known that, in that case, the translations along the flow of ${\cal C}$ also leave invariant $\ker {\cal T}$. Therefore at any time $t$, $f(t)$ belongs to $\ker {\cal T}$, as translation of the initial condition $\ave{\fin} \in \ker {\cal T}$ along the flow of ${\cal C}$. 
\end{remark}

\section{The numerical scheme}
\label{NumSch}

We focus now on the numerical resolution of \eqref{Equ4}, \eqref{Equ5}. As noticed before, when $\eps $ becomes small, the transport equation
\begin{equation}
\label{Equ55} \partial _t \fe + \frac{1}{\eps} a \cdot \nxv \fe + \frac{\omega _c}{\eps ^2} \;^\perp v \cdot \nabla _v \fe = 0
\end{equation}
is dominated by the advection $\frac{\omega _c}{\eps ^2} \;^\perp v \cdot \nabla _v = - \frac{\omega _c}{\eps ^2} \partial _\theta$, where $\theta$ is the polar angle of the velocity $v \in \R^2$. Notice that the standard CFL constraint leads to a time step $\Delta t \sim \eps ^2$. Therefore, when $\eps$ is small it is not reasonable to appeal to explicit numerical scheme. We will use implicit numerical schemes. Moreover, we are looking for numerical schemes which are consistent with the continuous model for all positive values of $\eps$ and that degenerate into a consistent discretization of \eqref{Equ56} when $\eps \searrow 0 $ and the time step is kept unchanged.

Recall that the limit when $\eps \searrow 0 $ of $(\fe)_\eps $ belongs to $\ker {\cal T}$ implying that for small $\eps >0$, the dominant part of $\fe$ is given by its average $\ave{\fe}$. Indeed, denoting by $\re = \fe - \ave{\fe}$ we have
\[
\ave{\re} = \ave{\fe - \ave{\fe}} = 0,\;\;{\cal T} \re = {\cal T} \fe = - \eps ^2 \partial _t \fe - \eps a \cdot \nxv \fe.
\]
Passing to the limit when $\eps \searrow 0$ we obtain, at least formally
\[
\ave{\lime \re} = 0,\;\;{\cal T} (\lime \re) = 0
\]
saying that 
\begin{equation}
\label{Equ58} \lime \re = 0.
\end{equation}
Based on the orthogonal decomposition $\fe = \ave{\fe} + \re $ in $\ltxv$, we intend to replace \eqref{Equ55} by a system for the unknowns $\ave{\fe}, \re$. This will be achieved by taking the orthogonal projection of \eqref{Equ55} on $\ker {\cal T}$ and its orthogonal. Since the orthogonal projection on $\ker {\cal T}$  coincides with the average operator and $a \cdot \nxv $ maps the functions of $\ker {\cal T}$ to zero average functions, we are led to
\begin{equation}
\label{Equ59} \partial _t \ave{\fe} + \frac{1}{\eps} \ave{a \cdot \nxv \re} = 0
\end{equation}
and
\begin{equation}
\label{Equ60} \partial _t \re + \frac{1}{\eps} a \cdot \nxv \ave{\fe} + \frac{1}{\eps} a \cdot \nxv \re - \frac{1}{\eps} \ave{a \cdot \nxv \re } + \frac{1}{\eps ^2} {\cal T} \re = 0.
\end{equation}
Therefore we can replace \eqref{Equ55} by the system
\begin{equation}
\label{Equ61} \partial _t \geps + \frac{1}{\eps} \ave{ a \cdot \nxv \re} = 0
\end{equation}
%%
\begin{equation}
\label{Equ62} \partial _t \re + \frac{1}{\eps} a \cdot \nxv \geps + \frac{1}{\eps} a \cdot \nxv \re - \frac{1}{\eps} \ave{a \cdot \nxv \re} + \frac{1}{\eps ^2} {\cal T} \re = 0.
\end{equation}
Naturally, we take as initial conditions
\begin{equation}
\label{Equ63} \geps | _{t = 0} = \ave{\fine},\;\;\re |_{t = 0} = \fine - \ave{\fine}.
\end{equation}
\begin{remark}
\label{Equivalence} It is easily seen that we have $\geps = \ave{\fe}$ and $\re = \fe - \ave{\fe}$. Indeed, applying the operator ${\cal T}$ to \eqref{Equ61} one gets
$
\partial _t {\cal T} \geps = 0
$
and thus ${\cal T} \geps (t) = {\cal T} \geps (0) = {\cal T} \ave{\fine} = 0$, saying that $\geps (t) \in \ker {\cal T}, t \in \R_+$. Applying now the average operator to \eqref{Equ62}, we deduce that $\partial _t \ave{\re} = 0$, since $\ave{a \cdot \nxv \geps (t)} = 0, t \in \R_+$ and thus $\ave{\re (t)} = \ave{\re (0)} = \ave{\fine - \ave{\fine}} = 0$. Taking the sum of \eqref{Equ61}, \eqref{Equ62} we obtain
\[
\partial _t ( \geps + \re) + \frac{1}{\eps} a \cdot \nxv ( \geps + \re) + \frac{1}{\eps ^2} {\cal T} ( \geps + \re) = 0
\]
%%
\[
( \geps + \re)|_{t = 0} = \fine.
\]
Therefore $\geps + \re$ and $\fe$ solve the same problem, and thanks to the uniqueness of the solution one gets $\geps + \re = \fe$. Since we already know that ${\cal T}\geps = 0, \ave{\re} = 0$ we deduce that 
\[
\geps = \ave{\geps + \re} = \ave{\fe},\;\;\re = \fe - \geps = \fe - \ave{\fe}.
\]
\end{remark}
%%

\subsection{Time discretization}

We propose now a numerical scheme for the system \eqref{Equ61}, \eqref{Equ62}, \eqref{Equ63}. For the moment we investigate only the time discretization. Pick a time step $\Delta t >0$ and let us denote by $t ^n = n \Delta t, n \in \N$, a uniform grid of $\R_+$. We consider the implicit time scheme
\begin{equation}
\label{Equ65} \frac{\renpo - \ren}{\Delta t} + \frac{1}{\eps} a \cdot \nxv \gen + \frac{1}{\eps} a \cdot \nxv \ren - \frac{1}{\eps} \ave{ a \cdot \nxv \ren } + \frac{1}{\eps ^2} {\cal T} \renpo = 0,\;\;n \in \N
\end{equation}
%%
\begin{equation}
\label{Equ66} \rez = \fine - \ave{\fine}.
\end{equation}
We recall here the following standard result
\begin{pro}
\label{UnifInv} For any $\lambda >0$ and $w \in \ltxv{}$, the equation $\lambda u + {\cal T} u = w$ has a unique solution $u$. The application $w \to (\lambda I + {\cal T})^{-1} w = u$ is linear continuous on $\ltxv{}$ and
\[
\| (\lambda I + {\cal T})^{-1}  \|_{{\cal L} (L^2, L^2)} \leq \frac{1}{\lambda},\;\;\lambda >0.
\] 
\red{Moreover, under the hypothesis $\inf _{x \in \R^2} B(x) >0$, if $w \in \ker \ave{\cdot}$, then $\|(\lambda I + {\cal T} ) ^{-1} w \| \leq \|{\cal T} ^{-1} w\|,\;\;\lambda >0$, saying that 
\[
\sup _{\lambda >0} \| (\lambda I + {\cal T} ) ^{-1}\|_{{\cal L} ( \ker \ave{\cdot}, \ave{\cdot})} \leq \|{\cal T}^{-1} \|_{{\cal L} ( \ker \ave{\cdot}, \ave{\cdot})} \leq \frac{2\pi}{|\omega _0|},\;\;\omega _0 = \frac{q}{m} \inf _{x \in \R^2} B(x) \neq 0.
\]
}
\end{pro}
%%
\begin{proof}
\red{Observe that the solution of $\lambda u_\lambda + {\cal T}u_\lambda = w$ is given by
\begin{equation}
\label{Equ67}
u_\lambda(x,v) = \int _{\R_-} e ^ {\lambda s} \;w (X(s;x,v), V(s;x,v))\;\mathrm{d}s
\end{equation}
where $(X,V)(s;x,v)$ is the flow associated to the first order operator ${\cal T}$. Therefore we obtain
\[
\|u_\lambda\| \leq \int _{\R_ -} e ^ {\lambda s}\;\|w((X,V)(s;\cdot,\cdot))\|\;\mathrm{d}s = \|w\| \int _{\R_ -} e ^ {\lambda s}\;\mathrm{d}s =\frac{\|w\|}{\lambda},\;\;\lambda >0
\]
saying that $\|(\lambda I + {\cal T})^{-1} \|_{{\cal L}(L^2, L^2)} \leq 1/\lambda,\; \lambda >0$. Consider now $w \in \ker \ave{\cdot}$. Clearly $u_\lambda \in \ker \ave{\cdot}$ since
\[
\lambda \ave{u_\lambda} = \ave{w - {\cal T}u_\lambda} = \ave{w} - \ave{{\cal T}u_\lambda } = 0.
\]
Let us denote by $u_0$ the unique zero average solution of ${\cal T} u_0 = w$, cf. Proposition \ref{TransportProp}, and thus we have
\[
\lambda u_\lambda + {\cal T} (u_\lambda - u_0) = 0.
\]
Multiplying by $u_\lambda-u_0$ we obtain $\lambda (u_\lambda, u_\lambda -u_0) = 0$, and by Cauchy-Schwarz inequality it comes that
\[
\|u_\lambda \| \leq \| u_0 \| = \|{\cal T} ^{-1} w \| \leq \|{\cal T}^{-1}\|_{{\cal L} ( \ker \ave{\cdot}, \ave{\cdot})} \|w\|.
\]
Finally, for any $\lambda >0$ we have
\[
\| (\lambda I + {\cal T} ) ^{-1}\|_{{\cal L} ( \ker \ave{\cdot}, \ave{\cdot})} \leq \|{\cal T}^{-1} \|_{{\cal L} ( \ker \ave{\cdot}, \ave{\cdot})} \leq \frac{2\pi}{|\omega _0|}.
\]
Notice that $(u_\lambda)_{\lambda >0}$ converges strongly in $\ltxv{}$, as $\lambda \searrow 0$, towards $u_0$. Indeed, it is easily seen that $(u_\lambda)_{\lambda >0}$ converges weakly in $\ltxv{}$, as $\lambda \searrow 0$, towards $u_0$, and that the convergence is strong, thanks to the inequality $\limsup _{\lambda \searrow 0} \|u _\lambda\| \leq \|u_0\|$.
}

\end{proof}
Thanks to Proposition \ref{UnifInv} we can solve for $\renpo$ in \eqref{Equ65}, uniformly with respect to $\eps, \Delta t$, since we need to invert $\frac{\eps ^2}{\Delta t} I + {\cal T}$ only on zero average functions. The time discretization \eqref{Equ65} uniquely determines $\renpo{}$ and we have
\begin{equation}
\label{Equ68} \renpo = \left ( \frac{\eps ^2}{\Delta t } I + {\cal T} \right ) ^{-1} \left (\frac{\eps ^2}{\Delta t} \ren - \eps a \cdot \nxv \gen - \eps a \cdot \nxv \ren + \eps \ave{a \cdot \nxv \ren }     \right ).
\end{equation}
We need to discretize \eqref{Equ61} as well. We complete our scheme by
\begin{equation}
\label{Equ69} \frac{\genpo - \gen }{\Delta t} + \frac{1}{\eps} \ave{ a \cdot \nxv \renpo } = 0
\end{equation}
%%
\begin{equation}
\label{Equ70}  \gez = \ave{\fine }.
\end{equation}
The choice of $t^{n+1}$ instead of $t^n$ as time evaluation for the term $\ave{a \cdot \nxv \re}$ will be clarified in the next proposition. The reason is that, with that choice, the numerical scheme degenerates into a consistent discretization of \eqref{Equ56} when $\eps \searrow 0$. In other words, our numerical scheme captures correctly the limit model of \eqref{Equ55} when $\eps \searrow 0$, for a time step range not depending on $\eps >0$. For the sake of simplicity we only state a formal result. Nevertheless, the properties of our numerical scheme will be emphasized by numerical simulations. 
%%
\begin{thm}
\label{Consistency} Assume that the electro-magnetic field satisfies the hypotheses
\[
E \in W^{1,\infty} (\R^2),\;\;\Divx \;^\perp E = 0,\;\;B \in W^{2,\infty} (\R^2),\;\; \inf _{x \in \R^2} B(x) >0
\]
and that \red{the initial conditions $(\fine)_\eps$ converge weakly in $\ltxv{}$, when $\eps \searrow 0$, towards some function $\fin$ (not necessarily in $ \ker {\cal T}$)}. The numerical scheme \eqref{Equ65}, \eqref{Equ66}, \eqref{Equ69}, \eqref{Equ70} remains consistent with the limit model \eqref{Equ56}, \eqref{Equ57} when $\eps \searrow 0$.  
\end{thm}
%%
\begin{proof}
It is easily seen that $\ave{\ren} = 0, {\cal T} \gen = 0, n \in \N$. Indeed, for $n = 0$ we have
\[
\ave{\rez} = \ave{\fine - \ave{\fine}} = 0,\;\;{\cal T} \gez = {\cal T} \ave{\fine} = 0.
\]
Assume now that $\ave{r ^{\eps, k}} = 0$ and ${\cal T}g ^{\eps, k} = 0$, for some $ k \in \N$. Taking the average in \eqref{Equ65} we obtain
\[
\frac{\ave{r ^{\eps, k+1}}}{\Delta t} + \frac{1}{\eps} \ave{a \cdot \nxv g ^{\eps, k}} = 0.
\]
Since ${\cal T} g ^{\eps, k} = 0$, we know that $\ave{a \cdot \nxv g ^{\eps, k}} = 0$ (cf. \eqref{Equ34}) and thus $\ave{r ^{\eps, k+1}} = 0$. Applying the operator ${\cal T} $ in \eqref{Equ69} implies ${\cal T} g ^{\eps, k+1} = {\cal T} g ^{\eps, k} = 0$.

We follow exactly the same steps as those in the continuous case, see Theorem \ref{WeakConv}. Multiplying \eqref{Equ65} by $\eps$ one gets
\[
{\cal T} \left ( \frac{\renpo}{\eps} \right ) = - a \cdot \nxv \gen - \eps \frac{\renpo - \ren}{\Delta t} - a\cdot \nxv \ren + \ave{a \cdot \nxv \ren}
\]
and since the right hand side is zero average
\[
\ave{ a \cdot \nxv \gen } = 0,\;\;\ave{ \renpo - \ren } = 0,\;\;\ave{a \cdot \nxv \ren - \ave{a \cdot \nxv \ren }} = 0
\]
we can solve for $\renpo / \eps$
\[
\frac{\renpo}{\eps} = - {\cal T} ^{-1} ( a \cdot \nxv \gen ) - \frac{\eps}{\Delta t } {\cal T} ^{-1} ( \renpo - \ren ) - {\cal T} ^ {-1} ( a \cdot \nxv \ren - \ave{a \cdot \nxv \ren } ).
\]
\red{The equality \eqref{Equ68}, which is a consequence of \eqref{Equ65}, says, at least formally, that $\ren = O(\eps), n \geq 1$, thanks to Proposition \ref{UnifInv}. By Proposition \ref{Step2} we obtain
\[
\frac{\renpo}{\eps} = - {\cal T} ^ {-1} ( a \cdot \nxv \gen ) + O (\eps) = - {\cal B} \cdot \nxv \gen + O(\eps),\;\;n \geq 1.
\]
}
Applying now Proposition \ref{Step3} yields
\begin{eqnarray}
\label{Equ73} \frac{1}{\eps} \ave{a \cdot \nxv \renpo} & = & - \ave{a \cdot \nxv ( {\cal B} \cdot \nxv \gen )} + O (\eps) \nonumber \\
& = & \Divxv(\gen {\cal C}) + O (\eps) \nonumber \\
& = & {\cal C} \cdot \nxv \gen + O (\eps).
\end{eqnarray}
Notice that the left hand side in \eqref{Equ73} coincides with the second term in the left hand side of \eqref{Equ69}. This is why we need to evaluate $\ave{a \cdot \nxv \re} /\eps $ at time $t^{n+1}$ instead of $t^n$, when looking for a time discretization of \eqref{Equ61}. Finally one gets
\[
\frac{\genpo - \gen}{\Delta t} + {\cal C} \cdot \nxv \gen + O(\eps) = 0,\;\;\gez = \ave{\fine} \rightharpoonup \ave{\fin}
\]
which is consistent with \eqref{Equ56}, \eqref{Equ57} when $\eps \searrow 0$. 
\end{proof}
\red{
Notice that \eqref{Equ68} writes 
\begin{align}
\label{EquExactExp}
\frac{\renpo}{\eps} & = - \left ( \frac{\eps ^2}{\Delta t}I + {\cal T}\right ) ^{-1} ( a \cdot \nxv \gen) - \left ( \frac{\eps ^2}{\Delta t}I + {\cal T}\right ) ^{-1} ( a \cdot \nxv \ren - \ave{a \cdot \nxv \ren } ) \nonumber \\
&  + \frac{\eps}{\Delta t } \left ( \frac{\eps ^2}{\Delta t}I + {\cal T}\right ) ^{-1} \ren
\end{align}
and thus, we expect that the leading order tem in the formula for $\frac{\renpo}{\eps}$ is 
\[
- \left ( \frac{\eps ^2}{\Delta t}I + {\cal T}\right ) ^{-1} (a\cdot \nxv \gen).
\]
In order to avoid the numerical errors coming from the discretization of this dominant term, we compute it analytically, following the result in Proposition \ref{Step2}.
%%
\begin{pro}
\label{Step2Bis}
$\;$\\
1. For any $\lambda >0$ there is a smooth divergence free vector field $\bl \cdot \nxv $ satisfying
\begin{equation}
\label{EquLambdaDecomp}
a\cdot \nxv = [{\cal T}, \bl \cdot \nxv] + \lambda \bl \cdot \nxv
\end{equation}
mapping $\D ( \bl \cdot \nxv ) \cap \ker {\cal T} $ to the subspace of zero average functions. This field is given by
\begin{equation}
\label{EquExpressionBLambda}
\bl \cdot \nxv =  \frac{\ol v}{\radlo}\cdot \nabla _x + \frac{q}{m \radlo} {^t \ol }E \cdot \nabla _v + \left ( \frac{{^\perp v} \otimes v }{\lambda ^2 + \omega _c ^2} \;{^t \ol} ^2 \;\;\nabla _x \omega _c \right ) \cdot \nabla _v
\end{equation}
with 
\[
\ol = \left(
\begin{array}{cc}
\frac{\lambda}{\radlo}   & - \frac{\omega _c}{\radlo}    \\
\frac{\omega _c}{\radlo}  &   \frac{\lambda}{\radlo}    
\end{array}
\right).
\]
2. For any function $f \in \D ( a \cdot \nxv ) \cap \D (\bl \cdot \nxv ) \cap \ker {\cal T}$ we have
\[
\bl \cdot \nxv f \in \D ({\cal T})\;\;\mbox{and} \;\; (\lambda I + {\cal T})^{-1} (a \cdot \nxv f) = \bl \cdot \nxv f.
\]
\end{pro}
%%
\begin{proof}
1. We consider the vector field basis
\[
b^0 \cdot \nxv = \;{^\perp v \cdot \nabla _v},\;\;b^1 \cdot \nxv = \partial _{x_1},\;\;b^2 \cdot \nxv = \partial _{x_2},\;\;b^3 \cdot \nxv = \frac{v}{|v|} \nabla _v
\]
and we search for $\bl \cdot \nxv = \sum _{i = 0} ^3 \beta _j b^j \cdot \nxv$, where $\beta _j$ are zero average coefficients to be determined. These coefficients come from the equalities
\[
a\cdot \nxv \psi _i = {\cal T} (\bl \cdot \nxv \psi _i ) - \bl \cdot \nxv ( {\cal T} \psi _i ) + \lambda \bl \cdot \nxv \psi _i 
\]
where $\psi _1 = x_1, \psi _2 = x_2, \psi _3 = |v|$ and $\psi _0 = - \theta (v)$, with $v = |v|(\cos \theta(v), \sin \theta (v))$ ($\psi _0 $ is multi-valued, but its gradient is well defined $\nxv \psi _0 = (0, {^\perp v}/|v|^2)$). Since $\psi_1, \psi _2, \psi _3$ are left invariant by ${\cal T}$, the coefficients $\beta _i = \bl \cdot \nxv \psi _i$ follow by solving 
\[
{\cal T} \beta _i + \lambda \beta _i = {\cal T} ( \bl \cdot \nxv \psi _i ) - \bl \cdot \nxv ( {\cal T} \psi _i ) + \lambda \bl \cdot \nxv \psi _i = a \cdot \nxv \psi _i,\;\;\ave{\beta _i} = 0,\;\;1\leq i \leq 3
\]
whose solution is given, cf. Proposition \ref{UnifInv}, by
\[
\beta _i = \int _{\R_ -} e ^{\lambda s} ( a \cdot \nxv \psi _i ) (x, {\cal R}(-\omega _c s) v)\;\mathrm{d}s.
\]
For the coefficient $\beta _0$, observe that ${\cal T} \psi _0 = \omega _c $, and use
\[
{\cal T} \beta _0 + \lambda \beta _0 = a \cdot \nxv \psi _0 + \bl \cdot \nxv \omega _c,\;\;\ave{\beta _0 } = 0.
\]
We obtain
\[
(\beta _1, \beta _2) = \frac{\ol v}{\radlo},\;\;\beta _3 = \frac{q}{m \radlo} E \cdot \ol \frac{v}{|v|}
\]
%%
\[
\beta _0 = \left ( {^t \ol}^2 \frac{\nabla _x \omega _c}{\lambda ^2 + \omega _c ^2} - \frac{q}{m \radlo} \;{^t \ol } \frac{^\perp E}{|v|^2}     \right ) \cdot v
\]
and \eqref{EquExpressionBLambda} follows. Taking the divergence in \eqref{EquLambdaDecomp} yields
\[
{\cal T} (\Divxv \bl) + \lambda \Divxv \bl = \Divxv a = 0
\]
and thus $\Divxv \bl = 0$. It remains to check that $\bl \cdot \nxv $ maps $\D (\bl \cdot \nxv ) \cap \ker {\cal T}$ to zero average functions. This is a consequence of the fact that $(b^i \cdot \nxv ) _{0 \leq i \leq 3}$ leave invariant $\ker {\cal T} $ and that $\ave{\beta _i}= 0, 0 \leq i \leq 3$. \\
2. For any $f \in \D ( a \cdot \nxv ) \cap \D ( \bl \cdot \nxv ) \cap \ker {\cal T}$ we have
\[
a\cdot \nxv f = {\cal T} ( \bl \cdot \nxv f ) + \lambda \bl \cdot \nxv f 
\]
and therefore
\[
\bl \cdot \nxv f \in \D ({\cal T})\;\;\mbox{ and } \;\;( \lambda I + {\cal T}) ^{-1} ( a \cdot \nxv f) = \bl \cdot \nxv f.
\]
\end{proof}
Thanks to Proposition \ref{Step2Bis}, the dominant term in the right hand side of \eqref{EquExactExp} writes
\[
- \left ( \frac{\eps ^2}{\Delta t} I + {\cal T} \right ) ^{-1} ( a \cdot \nxv \gen) = - \ble \cdot \nxv \gen
\]
with $\lambda _\eps = \frac{\eps ^2}{\Delta t}$, which will generate the following leading order term in $\frac{1}{\eps} \ave{a \cdot \nxv \renpo}$, appearing in \eqref{Equ69}
\[
- \ave{ a \cdot \nxv ( \ble \cdot \nxv \gen)}.
\]
The evaluation of the above term requires many approximations, since we need to discretize two transport operators and one average. Following Proposition \ref{Step3} we compute exactly such terms (see Appendix \ref{CLambda} for proof details).
%%
\begin{pro}
\label{Step3Bis} For any $\lambda >0$ there is a divergence free vector field $\cl$ such that  for any smooth function $f \in \ker {\cal T}$ 
\[
- \ave{( a - \lambda \bl ) \cdot \nxv ( \bl \cdot \nxv f )} = \Divxv ( f \cl ).
\]
The coordinates of $\cl = (\cl _x, \cl _v)$ are given by
\[
\cl _x = \ave{\xil _x},\;\;\cl _v = \ave{\xil _v \cdot \frac{v}{|v|}} \frac{v}{|v|},\;\;\xil = \frac{1}{2}[\bl, a].
\]
If the electric field derives from a potential, then the vector field $\cl$ writes
\begin{equation}
\label{EquExpressionCLambda}
\cl \cdot \nxv = \left [\frac{\omega _c ^2}{\lambda ^2 + \omega _c ^2} \frac{^\perp E}{B} + \frac{|v|^2}{2} \;{^\perp \nabla _x } \left ( \frac{\omega _c}{\lambda ^2 + \omega _c ^2 } \right ) \right ] \cdot \nabla _x - \frac{1}{2} \frac{^\perp E}{B} \cdot \nabla _x \left ( \frac{\omega _c}{\lambda ^2 + \omega _c ^2 } \right ) \omega _c v \cdot \nabla _v.
\end{equation}
\end{pro}
%%
\begin{remark}
\label{RemStep3Bis} It is easily seen that $\cl $ is a regular perturbation of ${\cal C}$
\[
\lim _{\lambda \searrow 0} \cl = \left ( \frac{^\perp E}{B} - \frac{|v|^2}{2\omega _c} \frac{^\perp \nabla _x B}{B}, \frac{1}{2} \left ( \frac{^\perp E}{B}\cdot \frac{\nabla _x B}{B} \right ) v \right ) = {\cal C}.
\]
\end{remark}
Combining Propositions \ref{Step2Bis}, \ref{Step3Bis}, the numerical scheme \eqref{Equ65}, \eqref{Equ66}, \eqref{Equ69}, \eqref{Equ70} becomes
\begin{equation}
\label{EquSch1} \frac{\renpo}{\eps} = - \ble \cdot \nxv \gen - \left (  \frac{\eps ^2}{\Delta t}I + {\cal T}\right )^{-1} \!\!\!\!( a \cdot \nxv \ren - \ave{a \cdot \nxv \ren } ) + \frac{\eps}{\Delta t} \left (  \frac{\eps ^2}{\Delta t}I + {\cal T}\right )^{-1} \!\!\!\!\!\!\ren
\end{equation}
%%
\begin{equation}
\label{EquSch2}
\left (  \frac{\eps ^2}{\Delta t}I + {\cal T}\right ) \hen = - \left ( a \cdot \nxv \left ( \frac{\ren }{\eps } \right )- \ave{a \cdot \nxv \left ( \frac{\ren }{\eps }\right ) } \right ) + \frac{\eps}{\Delta t} \left ( \frac{\ren}{\eps} \right )
\end{equation}
%%
\begin{equation}
\label{EquSch3} \frac{\genpo - \gen}{\Delta t} + \cle \cdot \nxv \gen - \lambda _\eps \ave{\ble \cdot \nxv ( \ble \cdot \nxv \gen )} + \eps \ave{a \cdot \nxv \hen} = 0
\end{equation}
with $\lambda _\eps = \eps ^2 /\Delta t$ and
\begin{equation}
\label{EquSch4}
\rez = \fine - \ave{\fine},\;\;\gez = \ave{\fine}.
\end{equation}
By \eqref{EquSch1} we have $\renpo = O(\eps), n \geq 0$, since $\left ( \frac{\eps ^2}{\Delta t} I + {\cal T} \right ) ^{-1}$ is uniformly bounded on the subspace of zero average functions. Therefore we introduce $\zen = \frac{\ren}{\eps}$, for any $n \geq 1$, and the previous scheme writes
\begin{enumerate}
\item Compute $\zeo, \heo, \geo$ using
\begin{align}
\label{EquSch5}
\zeo  = \frac{\reo}{\eps} = - \ble \cdot \nxv \gez - \left (  \frac{\eps ^2}{\Delta t}I + {\cal T}\right )^{-1} \!\!\!\!\left ( a \cdot \nxv \rez - \ave{a \cdot \nxv \rez } - \frac{\eps}{\Delta t}\rez \right )
\end{align}
%%
\begin{align}
\label{EquSch6}
\left (  \frac{\eps ^2}{\Delta t}I + {\cal T}\right )\heo = 
- \left ( 
a \cdot \nxv \zeo- \ave{a \cdot \nxv \zeo} 
\right ) + 
\frac{\eps}{\Delta t} 
\zeo
\end{align}
%%
\begin{align}
\label{EquSch7}
\frac{\geo - \gez}{\Delta t} + \cle \cdot \nxv \gez - \lambda _\eps \ave{\ble \cdot \nxv ( \ble \cdot \nxv \gez )} +  \ave{a \cdot \nxv \tilde{h}^{\eps, 0}} = 0
\end{align}
%%
with $\tilde{h}^{\eps, 0}$ given by
\[
\left (  \frac{\eps ^2}{\Delta t}I + {\cal T}\right )\tilde{h}^{\eps, 0} = - ( a \cdot \nxv \rez - \ave{a \cdot \nxv \rez}) + \frac{\eps}{\Delta t} \rez.
\]
%%
\item Given $(\zen, \hen, \gen)$ with $n \geq 1$, compute $(\zenpo, \henpo, \genpo)$ using
\begin{equation}
\label{EquSch8}
\zenpo = - \ble \cdot \nxv \gen + \eps \hen
\end{equation}
%%
\begin{align}
\label{EquSch9}
\left (  \frac{\eps ^2}{\Delta t}I + {\cal T}\right )\henpo = 
- \left ( 
a \cdot \nxv \zenpo- \ave{a \cdot \nxv \zenpo} 
\right ) + 
\frac{\eps}{\Delta t} 
\zenpo
\end{align}
%%
\begin{align}
\label{EquSch10}
\frac{\genpo - \gen}{\Delta t} + \cle \cdot \nxv \gen - \lambda _\eps \ave{\ble \cdot \nxv ( \ble \cdot \nxv \gen )} +  \eps\ave{a \cdot \nxv \hen} = 0.
\end{align}
%%
\end{enumerate}
%%
\begin{remark}
Clearly, when $\eps \searrow 0$, \eqref{EquSch10} remains consistent with \eqref{Equ56}, since
\[
\cle \cdot \nxv \to \cl \cdot \nxv\;\;\mbox{ and } \;\;\lambda _\eps \ave{\ble \cdot \nxv ( \ble \cdot \nxv )} \to 0.
\]
\end{remark}
}

\subsection{Phase space discretization}

mettre tout ce qu'il faut pour definir le schema de Lax-Ritchmyer (p130 de la these) : 
\begin{itemize}
\item definition de $\Phi$ 
\item definition de ${\cal B}\cdot \nabla_{x,v} g^n$
\item definition de ${\cal C}\cdot \nabla_{x,v} g^n$
\end{itemize}

\section{Numerical simulations}
\label{NumSim}

This section is devoted to numerical validation.

\subsection{Analytic test case}
correspond au 5.6.1 de la these p131

\subsection{Two stream instability}
correspond au test  de la these p 134 et 135 
\begin{itemize}
\item $\varepsilon_B  \rightarrow +\infty$ (p134)
\item $\varepsilon  \rightarrow 0$ (p135)
\end{itemize}

\subsection{Kelvin-Helmholtz}
correspond au test  de la these p 137
\begin{itemize}
\item tracer mode$(t)$ pour $t_{final}=50$ en  $N=64^4$ et $\Delta t$ 
$\varepsilon=1, 0.75, 0.5, 0.25, 0.01, 10^{-6}$ (cf p21 de munich13crous.pdf)
\item tracer $w/k$ en fonction de $(1-k)$ quand $\varepsilon$ petit 
\item plot 2d $(x,y)$
\end{itemize}

\subsection{Collision}
Expliquer rapidement le modele (scaling) et le modele asymptotique correspondant. 
Expliquer si besoin les modifications numeriques.

Meme condition initiale que Kelvin-Helmholtz
\begin{itemize}
\item tracer mode$(t)$ pour $t_{final}=50$ en  $64^4$ et $\Delta t$ 
$\varepsilon=1, 0.75, 0.5, 0.25, 0.01, 10^{-6}$ (cf p21 de munich13crous.pdf)
\item tracer $w/k$ en fonction de $(1-k)$ quand $\varepsilon$ petit 
\item plot 2d $(x,y)$
\end{itemize}
Objectif : exhiber l'influence des collisions.

\appendix

\section{Proof of Proposition \ref{Step3Bis}}
\label{CLambda}
%%
\begin{proof}
Using the formula $a \cdot \nxv - \lambda \bl \cdot \nxv = [{\cal T}, \bl \cdot \nxv ]$ we have
\begin{align*}
- \ave{(a - \lambda \bl) \cdot \nxv ( \bl \cdot \nxv f ) } & = - \ave{{\cal T} \bl \cdot \nxv ( \bl \cdot \nxv f ) } \\
& + \ave{\bl \cdot \nxv ( {\cal T} (\bl \cdot \nxv f ))} \\
& = \ave{\bl \cdot \nxv ( ( a - \lambda \bl ) \cdot \nxv f ) }
\end{align*}
since $\ran {\cal T} \subset \ker \ave{\cdot}$ and ${\cal T} ( \bl \cdot \nxv f ) = (a - \lambda \bl ) \cdot \nxv f$. Therefore
\begin{align*}
- \ave{(a - \lambda \bl) \cdot \nxv ( \bl \cdot \nxv f ) } & =\frac{1}{2} \ave{[\bl \cdot \nxv, (a - \lambda \bl ) \cdot \nxv ]f} \\
& = \frac{1}{2} \ave{[\bl \cdot \nxv, a \cdot \nxv ]f}\\
& = \ave{\xil \cdot \nxv f}
\end{align*}
where $2 \xil $ is the Poisson bracket between the vector fields $\bl$ and $a$. Since $\Divxv a = \Divxv \bl = 0$, we have $\Divxv \xil = 0$ and therefore, thanks to Proposition \ref{DivAveCom}, one gets
\begin{align*}
- \ave{(a - \lambda \bl) \cdot \nxv ( \bl \cdot \nxv f ) } & = \ave{\Divxv(f \xil)} \\
& = \Divx ( f \ave{\xil _x}) + \Divv \left \{ f  \ave{\xil _v \cdot \frac{v}{|v|}} \frac{v}{|v|} \right \}\\
& = \Divxv(f \cl)
\end{align*}
where $\cl = \left ( \ave{\xil _x},  \ave{\xil _v \cdot \frac{v}{|v|}} \frac{v}{|v|}\right )$. In particular, taking $f = 1 \in \ker {\cal T}$, one gets $\Divxv \cl = 0$. \\
\underline{Computation of $\cl _x$}\\
We use the invariant $\psi _1 = x_1$. Taking into account that 
\begin{align*}
\xil _{x_1} & = \xil \cdot \nxv \psi _1 = \frac{1}{2} [\bl \cdot \nxv, a \cdot \nxv ]\psi _1 \\
& = \frac{1}{2} \bl \cdot \nxv ( a \cdot \nxv \psi _1) - \frac{1}{2} a \cdot \nxv ( \bl \cdot \nxv \psi _1 ) \\
& = \frac{1}{2} \bl \cdot \nxv v_1 - \frac{1}{2} a \cdot \nxv \bl _{x_1}
\end{align*}
we deduce, thanks to Proposition \ref{DivAveCom}
\begin{align*}
\ave{\xil _{x_1}} & = \frac{1}{2}\ave{\Divxv( v_1 \bl)} - \frac{1}{2} \ave{\Divxv(\bl _{x_1} a)} \\
& = \frac{1}{2}\Divx \ave{v_1 \bl _x } + \frac{1}{2}\Divv \left [ \ave{v_1 \bl _v \cdot \frac{v}{|v|}}\frac{v}{|v|}  \right ]\\
& - \frac{1}{2}\Divx \ave{\bl _{x_1} v } - \frac{1}{2}\Divv \left [ \ave{\bl _{x_1} \frac{qE}{m}\cdot \frac{v}{|v|}}\frac{v}{|v|}  \right ]\\
& = - \frac{1}{2} \partial _{x_2} \ave{\frac{\ol}{\radlo}: {^\perp v} \otimes v}\\ 
& + \frac{1}{2} \Divv \left [\ave{\frac{q v \otimes v}{m \radlo |v|} : ( {^t \ol} E \otimes e_1 - E \otimes {^t \ol} e_1 ) } \frac{v}{|v|}    \right]\\
& = \frac{|v|^2}{2} \partial _{x_2} \left (   \frac{\omega _c}{\lambda ^2 + \omega _c ^2} \right ) + \frac{1}{2}\Divv \left (\frac{\omega _c ^2 }{\lambda ^2 + \omega _c ^2} \left ( \frac{^\perp E}{B} \right )_1 v   \right )\\
& = \frac{|v|^2}{2} \partial _{x_2} \left (   \frac{\omega _c}{\lambda ^2 + \omega _c ^2}\right ) 
+\frac{\omega _c ^2 }{\lambda ^2 + \omega _c ^2}\left ( \frac{^\perp E}{B} \right )_1.
\end{align*}
Similarly 
\[
\ave{\xil _{x_2}} = -\frac{|v|^2}{2} \partial _{x_1} \left (   \frac{\omega _c}{\lambda ^2 + \omega _c ^2}\right ) 
+\frac{\omega _c ^2 }{\lambda ^2 + \omega _c ^2}\left ( \frac{^\perp E}{B} \right )_2
\]
and therefore 
\[
\cl _x = \ave{\xil _x} = \frac{\omega _c ^2}{\lambda ^2 + \omega _c ^2}\frac{^\perp E}{B} + \frac{|v|^2}{2} \;{^\perp \nabla _x } \left ( \frac{\omega _c}{\lambda ^2 + \omega _c ^2}\right ).
\]
\underline{Computation of $\cl _v$}\\
We use the invariant $\psi _3 = |v|$. Taking into account that 
\begin{align*}
\xil _v \cdot \frac{v}{|v|} & = \xil \cdot \nxv \psi _3 = \frac{1}{2} [\bl \cdot \nxv, a \cdot \nxv ] \psi _3\\
& = \frac{1}{2} \bl \cdot \nxv ( a \cdot \nxv \psi _3) - \frac{1}{2} a \cdot \nxv ( \bl \cdot \nxv \psi _3) \\
& = \frac{1}{2} \bl \cdot \nxv \left ( \frac{qE}{m} \cdot \frac{v}{|v|} \right ) - \frac{1}{2} a \cdot \nxv \left ( \frac{q }{m \radlo} {^t \ol }E \cdot \frac{v}{|v|} \right )
\end{align*}
we deduce by Proposition \ref{DivAveCom}
\begin{align*}
\ave{\xil _v \cdot \frac{v}{|v|}} & = \frac{1}{2}\ave{\Divxv \left (\frac{qE}{m} \cdot \frac{v}{|v|} \bl \right )} - \frac{1}{2} \ave{\Divxv\left ( \frac{q}{m\radlo} \;{^t \ol} E \cdot \frac{v}{|v|} a   \right ) }\\
& = \frac{1}{2} \Divx \ave{\frac{qE}{m} \cdot \frac{v}{|v|} \frac{\ol v}{\radlo}} + 
\frac{1}{2}\Divv \left [ \ave{\frac{qE}{m} \cdot \frac{v}{|v|} \frac{q \;{^t \ol} E}{m \radlo}\cdot \frac{v}{|v|}   }\frac{v}{|v|}  \right ]\\
& - \frac{1}{2} \Divx \ave{\frac{q\;{^t \ol}E}{m\radlo} \cdot  \frac{v}{|v|} v} -
\frac{1}{2}\Divv \left [ \ave{ \frac{q \;{^t \ol} E}{m \radlo}\cdot \frac{v}{|v|} \frac{qE}{m} \cdot \frac{v}{|v|}  }\frac{v}{|v|}  \right ]\\
& = \frac{1}{2}\Divx \ave{\frac{q}{m \radlo |v|} [ \ol (v\otimes v) E - (v \otimes v) \;{^t \ol} E]}\\
& = - \frac{1}{2} \Divx \left ( \frac{q}{m} \frac{\omega _c}{\lambda ^2 + \omega _c ^2} |v| \;{^\perp E} \right ).
\end{align*}
Finally 
\[
\cl _v = \ave{\xil _v \cdot \frac{v}{|v|}} \frac{v}{|v|} = - \frac{1}{2} \frac{q}{m} \left ( {^\perp E} \cdot \nabla _x \left ( \frac{\omega _c}{\lambda ^2 + \omega _c ^2} \right ) \right )v
\]
and \eqref{EquExpressionCLambda} follows.
\end{proof}
%%

%%--------------------------------------
%%-------- Bibliographie ---------------
%%--------------------------------------

\begin{thebibliography}{999}

\bibitem{BenLemMie08} M. Bennoune, M. Lemou, L. Mieussens, Uniformly stable numerical scheme for the Boltzmann equation preserving compressible Navier-Stokes asymptotics, J. Comput. Phys. 227(2008) 3781-3803.

\bibitem{BosAsyAna} M. Bostan, {The Vlasov-Poisson system with strong external magnetic field. Finite Larmor radius regime}, Asymptot. Anal., 61(2009) 91-123.

\bibitem{BosTraSin} {M. Bostan}, {Transport equations with disparate advection fields. Application to the gyrokinetic models in plasma physics}, J. Differential Equations 249(2010) 1620-1663.

\bibitem{BosGuidCent3D} {M. Bostan}, {Gyrokinetic Vlasov equation in three dimensional setting. Second order approximation}, SIAM J. Multiscale Model. Simul. 8(2010) 1923-1957.

\bibitem{Bos12} {M. Bostan}, {Transport of charged particles under fast oscillating magnetic fields}, SIAM J. Math. Anal. 44(2012) 1415-1447.

\bibitem{CroLem11} N. Crouseilles, M. Lemou, {An asymptotic preserving scheme based on a micro-macro decomposition for collisional Vlasov equations: diffusion and high-field scaling limits}, Kinet. Relat. Models 4(2011) 441-477.

\bibitem{FreSon98} {E. Fr\'enod, E. Sonnendr\"ucker},
{Homogenization of the Vlasov equation and of the Vlasov-Poisson
system with strong external magnetic field}, Asymptotic Anal.
18(1998) 193-213.

\bibitem{FreSon01} {E. Fr\'enod, E. Sonnendr\"ucker}, The finite
Larmor radius approximation, SIAM J. Math. Anal. 32(2001) 1227-1247.

%\bibitem{GraBruBer06} V. Grandgirard, M. Brunetti, P. Bertrand, N.
%Besse, X. Garbet, P. Ghendrih, G. Manfredi, Y. Sarazin, O. Sauter,
%E. Sonnendr\"ucker, J. Vaclavik, L. Villard, A drift-kinetic
%semi-Lagrangian 4D code for ion turbulence simulation, J. Comput.
%Phys. 217(2006) 395-423.

\bibitem{HazMei03} R.D. Hazeltine, J.D. Meiss, Plasma confinement, Dover Publications, Inc. Mineola, New York, 2003.

\bibitem{JinParTos00} S. Jin, L. Pareschi, G. Toscani, Uniformly accurate diffusive relaxation schemes for multiscale transport equations, SIAM J. Num. Anal. 38(2000) 913-936.

\bibitem{Kla98} A. Klar, An asymptotic-induced scheme for nonstationary transport equations in the diffusion limit, SIAM J. Num. Anal. 35(1998) 1073-1094.

\bibitem{Kla99} A. Klar, An asymptotic preserving numerical scheme for kinetic equations in the low Mach number limit, SIAM J. Num. Anal. 36(1999) 1507-1527.

\bibitem{LemMie08} M. Lemou, L. Mieussens, A new asymptotic preserving scheme based on micro-macro formulation for linear kinetic equations in the diffusion limit, SIAM J. Sci. Comp. 31(2008) 334-368.

\bibitem{Lem10} M. Lemou, Relaxed micro-macro schemes for kinetic equations, C. R. Acad. Sci. Paris, S\'er. I Math. 348(2010) 455-460.

\end{thebibliography}

\end{document}

%%----------------------------------------------------------
%%------------ Exemples de solutions exactes ---------------
%%----------------------------------------------------------

For further comparison of the numerical solutions, it is useful to introduce exact solutions for the Vlasov equation \eqref{Equ55}, for any $\eps >0$. For example, when the electric field vanishes and the magnetic field is homogeneous, we consider two classes of exact solutions (see Appendix \ref{B} for the proof).

\begin{pro}
\label{ExactSol} Assume that $E = 0$ and $\nabla _x B = 0$.\\
1. (space homogeneous solution) If the initial condition is 
\[
f^{\mathrm{in}} (x,v) = \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right ) ( 1 + v_1 )
\]
then the solution of \eqref{Equ55} is 
\[
\fe(t,x,v) = \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right ) \left [ 1 + \cos \left ( \frac{\omega _c}{\eps ^2} t \right ) v_1 - \sin \left ( \frac{\omega _c}{\eps ^2} t \right ) v_2 \right ].
\]
The average and the fluctuation around the average are
\[
\geps (t)  = \ave{\fe (t)}=  \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right )
\]
%%
\[
\re (t) = \fe (t) - \ave{\fe (t)} = \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right ) \left [  \cos \left ( \frac{\omega _c}{\eps ^2} t \right ) v_1 - \sin \left ( \frac{\omega _c}{\eps ^2} t \right ) v_2  \right ].
\] 
%2. (stationary solution) If the initial condition is
%\[
%\fine (x,v) = \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right ) \left [ 1 + \alpha \cos \left ( x_1 + \frac{\eps}{\omega _c} v_2 \right ) \right ]
%\]
%then the solution of \eqref{Equ55} is $ \fe(t,x,v)  = \fine (x,v) $. The average and the fluctuation around the average are
%\[
%\geps = \ave{\fe } =  \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right ) \left [ 1 + \alpha J_0 \left ( \frac{\eps}{\omega _c} |v| \right ) \;\cos x_1 \right ]
%\]
%%
%\[
%\re = \fe - \ave{\fe} = \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right ) \alpha \left [ \cos \left ( x_1 + \frac{\eps}{\omega _c} v_2 \right )  -  J_0 \left ( \frac{\eps}{\omega _c} |v| \right ) \;\cos x_1  \right ]
%\]
%%
2. If the initial condition is
\[
\fine (x,v) = \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right ) \left ( 1 + \beta \cos x_1 \right )
\]
then the solution of \eqref{Equ55} is 
\[
\fe  = \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right ) \left [ 1 + \beta \cos \left ( x_1   + \frac{\eps}{\omega _c }v_2 - \frac{\eps}{\omega _c} \left (  \sin \left (\frac{\omega _c t }{ \eps ^2}   \right ) v_1 +  \cos  \left (\frac{\omega _c t }{ \eps ^2}   \right ) v_2 \right )   \right )  \right ].
\]
The average and the fluctuation around the average are
\[
\geps = \ave{\fe } =  \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right ) \left [ 1 + \beta J_0 \left ( \frac{2\eps}{|\omega _c|}\left | \sin \left ( \frac{\omega _c t }{2 \eps ^2 } \right )   \right | |v| \right ) \;\cos x_1 \right ]
\]
%%
\begin{eqnarray}
\re & = &  \fe - \ave{\fe} \nonumber \\
& = &  \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right ) \beta  \cos \left ( x_1 + \frac{\eps}{\omega _c} v_2  - \frac{\eps}{\omega _c} \left (  \sin \left (\frac{\omega _c t }{ \eps ^2}   \right ) v_1 +  \cos  \left (\frac{\omega _c t }{ \eps ^2}   \right ) v_2 \right ) \right  ) \nonumber \\
&  - &  \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right ) \beta  J_0 \left ( \frac{2\eps}{|\omega _c|}\left | \sin \left ( \frac{\omega _c t }{2 \eps ^2 } \right )   \right | |v| \right ) \;\cos x_1  \nonumber 
\end{eqnarray}
where $J_0$ is the Bessel function
\[
J_0 (r) : =  \frac{1}{2\pi} \int _0 ^{2\pi} e ^ { - i r \cos \theta } \;\mathrm{d}\theta = \frac{1}{2\pi} \int _0 ^{2\pi} \cos ( r \cos \theta) \;\mathrm{d}\theta.
\]
\end{pro}

\section{Exact solutions}
\label{B}
\begin{proof} (of Proposition \ref{ExactSol}) 
When the electric field vanishes and the magnetic field is space homogeneous, we determine easily the flow associated to the advection operator $\frac{v}{\eps} \cdot \nabla _x  + \frac{\omega _c}{\eps ^2} \;^\perp v \cdot \nabla _v $ appearing in \eqref{Equ55}. Actually it is easily seen that $ x + \frac{\eps}{\omega _c } \;^\perp v, |v|$ are left invariant by the flow
\[
\frac{d{\cal X}}{ds} = \frac{{\cal V}(s)}{\eps},\;\;\frac{d{\cal V}}{ds} = \frac{\omega _c}{\eps ^2} \;^\perp {\cal V}(s)
\]
%%
\[
{\cal X}(0;x,v) = x, {\cal V}(0;x,v) = v
\]
and we deduce that 
\begin{equation}\nonumber
{\cal X}(s;x,v) = x + \frac{\eps}{\omega _c} \left (
\begin{array}{lll}
\sin \left (\frac{\omega _c }{\eps ^2} s   \right )  &  1 - \cos \left (\frac{\omega _c }{\eps ^2} s   \right )\\
\cos \left (\frac{\omega _c }{\eps ^2} s   \right ) - 1  &\;\;\;   \sin \left (\frac{\omega _c }{\eps ^2} s   \right )
\end{array}
\right )\;v
\end{equation}
and
\[
{\cal V}(s;x,v)  = {\cal R} \left ( - \frac{\omega _c}{\eps ^2} s \right ) \;v.
\]
Therefore the exact solution of the Vlasov equation \eqref{Equ55} is given 
\[
\fe (t,x,v) = \fin ( {\cal X}(-t;x,v), {\cal V}(-t;x,v))
\]
and the assertions of 1. come immediately. 
Notice that the initial condition in 2 writes
\[
\fine (x,v) = \frac{1}{2\pi}  \exp \left (- \frac{|v|^2}{2}   \right )\left [ 1 + \beta \cos \left ( x_1 + \frac{\eps}{\omega _c} v_2 - \frac{\eps}{\omega _c }v_2 \right ) \right ].
\]
Since $|v|$ and $x_1 + \frac{\eps}{\omega _c} v_2$ are left invariant by the flow $({\cal X}, {\cal V})$, we have
\begin{eqnarray}
\fe  & = &  \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right ) \left [ 1 + \beta \cos \left ( x_1   + \frac{\eps}{\omega _c }v_2 - \frac{\eps}{\omega _c} {\cal V}_2 ( -t;x,v) \right ) \right ] \nonumber \\
& = & \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right ) \left [ 1 + \beta \cos \left ( \frac{\eps}{\omega _c} v_2 - \frac{\eps}{\omega _c} {\cal V}_2 ( -t;x,v) \right ) \cos x_1\right ]\nonumber \\
&  - &  \frac{1}{2\pi} \exp \left (- \frac{|v|^2}{2}   \right )\beta \sin \left ( \frac{\eps}{\omega _c} v_2 - \frac{\eps}{\omega _c} {\cal V}_2 ( -t;x,v) \right ) \sin x_1. \nonumber
\end{eqnarray}
We are done if we compute the average of the functions 
\[
(x,v) \to \cos \left ( \frac{\eps}{\omega _c} v_2 - \frac{\eps}{\omega _c} {\cal V}_2 ( -t;x,v) \right ),\;\;(x,v) \to \sin \left ( \frac{\eps}{\omega _c} v_2 - \frac{\eps}{\omega _c} {\cal V}_2 ( -t;x,v) \right )
\]
for any fixed $t \in \R_+$. Observe that we have
\[
{\cal R}(\alpha ) v - {\cal V}(-t;x, {\cal R}(\alpha ) v ) = 2 \sin \left ( \frac{\omega _c t }{2 \eps ^2}\right ) {\cal R} \left ( \frac{\omega _c t }{2 \eps ^2} - \frac{\pi}{2} + \alpha   \right ) v
\]
and therefore
\[
\ave{\cos \left ( \frac{\eps}{\omega _c} v_2 - \frac{\eps}{\omega _c} {\cal V}_2 ( -t;x,v) \right )} = \ave{\cos \left (  \frac{2\eps}{\omega _c} \sin \left (  \frac{\omega _c t}{2 \eps ^2}  \right )v_2   \right )}
\]
%%
\[
\ave{\sin \left ( \frac{\eps}{\omega _c} v_2 - \frac{\eps}{\omega _c} {\cal V}_2 ( -t;x,v) \right )} = \ave{\sin \left (  \frac{2\eps}{\omega _c} \sin \left (  \frac{\omega _c t}{2 \eps ^2}  \right )v_2   \right )}.
\]
Based on the formula
\[
\ave{\cos \left ( \gamma v_2 \right )} = J_0 \left ( |\gamma | \;|v| \right ),\;\;\ave{\sin \left ( \gamma v_2 \right ) } = 0,\;\;\gamma \in \R
\]
we obtain
\[
\ave{\cos \left ( \frac{\eps}{\omega _c} v_2 - \frac{\eps}{\omega _c} {\cal V}_2 ( -t;x,v) \right )} = J_0 \left ( \frac{2\eps}{|\omega _c|}\left | \sin \left ( \frac{\omega _c t }{2 \eps ^2 } \right )   \right | |v| \right )
\]
%%
\[
\ave{\sin \left ( \frac{\eps}{\omega _c} v_2 - \frac{\eps}{\omega _c} {\cal V}_2 ( -t;x,v) \right )} =0
\]
and the last assertions in 2. follow.
\end{proof}

### 2014-07-28 solve_mH1.m
solution of the eq with theta=0, H1 functions both for E1 and E2

@@ -1,0 +1,189 @@
+function [u,K,x]=solve_mH1(dx,lambda, nu)
+%mesh generation
+L=2;
+H=10;
+
+x=-L:dx:H;
+
+tic
+K=construct_block_matrix(x,nu,lambda);
+r=construct_rhs(x);
+toc
+disp( "formed the matrix and the RHS");
+tic
+u=K\r;
+toc
+end
+
+
+function a=alpha(x)
+
+    if x<=-1 a=1;
+    elseif x<=3 a=-x;
+    else a=-3;
+    end
+
+a=0.0;
+
+end
+
+function delta=delta(x)
+
+    if x<=-1 delta=0;
+    elseif x<=3 delta=0.5*(x+1);
+    else delta = 2;
+    end
+
+ delta=0.0;
+
+end
+
+
+
+%stiffness for P1
+function K=K_lpl(x)
+    L=length(x);
+    diagon=zeros(L,1);
+    diagon_und=zeros(L-1,1);
+    diagon(1)=1/(x(2)-x(1));
+
+    diagon(2:1:end-1)=1./(x(2:1:end-1)-x(1:1:end-2))+1./(x(3:1:end)-x(2:1:end-1));
+    diagon_und(1:1:end)=-1./(x(2:1:end)-x(1:1:end-1));
+
+    diagon(end-1)=1./(x(end)-x(end-1));
+
+    K=sparse(diag(diagon)+diag(diagon_und,-1)+diag(diagon_und,1));
+end
+
+%mass matrix for P1
+function K=mass_matrixP1(x)
+
+    L=length(x);
+    diagon=zeros(L,1);
+    diagon_und=zeros(L-1,1);
+    diagon(1)=(x(2)-x(1))/3;
+
+
+    diagon(2:1:end-1)=(x(2:1:end-1)-x(1:1:end-2))./3+(x(3:1:end)-x(2:1:end-1))./3;
+    diagon_und(1:1:end)=(x(2:1:end)-x(1:1:end-1))./6;
+
+    diagon(end)=(x(end)-x(end-1))./3;
+
+
+    K=sparse(diag(diagon)+diag(diagon_und, -1)+diag(diagon_und, 1));
+end
+
+%mass matrix for piecewise-constants
+function M=mass_matrixL2(x)
+    M=sparse(diagon(x(2:1:end)-x(1:1:end-1)));
+end
+
+
[…]

### 2014-07-28 solve_mH1.m
fixed a bug in the stiffness matrix

@@ -1,4 +1,4 @@
-function [u,K,x]=solve_mH1(dx,lambda, nu)
+function [u,K,x,r]=solve_mH1(dx,lambda, nu)
 %mesh generation
 L=2;
 H=10;
@@ -23,7 +23,7 @@ function a=alpha(x)
     else a=-3;
     end
 
-a=0.0;
+a=0;
 
 end
 
@@ -34,7 +34,8 @@ function delta=delta(x)
     else delta = 2;
     end
 
- delta=0.0;
+delta=0;
+
 
 end
 
@@ -50,7 +51,7 @@ function K=K_lpl(x)
     diagon(2:1:end-1)=1./(x(2:1:end-1)-x(1:1:end-2))+1./(x(3:1:end)-x(2:1:end-1));
     diagon_und(1:1:end)=-1./(x(2:1:end)-x(1:1:end-1));
 
-    diagon(end-1)=1./(x(end)-x(end-1));
+    diagon(end)=1./(x(end)-x(end-1));
 
     K=sparse(diag(diagon)+diag(diagon_und,-1)+diag(diagon_und,1));
 end

### 2014-07-28 solve_mH1.m
working for const alpha, delta

@@ -23,7 +23,7 @@ function a=alpha(x)
     else a=-3;
     end
 
-a=0;
+a=4;
 
 end
 
@@ -34,7 +34,7 @@ function delta=delta(x)
     else delta = 2;
     end
 
-delta=0;
+delta=sqrt(8);
 
 
 end
@@ -164,7 +164,8 @@ end
 
 function b=construct_rhs(x)
     b=zeros(2*length(x),1);
-    b(length(x)+1)=exp(1i*x(1));
+b(length(x)+1)=-2*1i*sqrt(2)*exp(1i*sqrt(2)*(-22));
+
 end
 
 

### 2014-07-29 solve_mH1.m
the solution of the system of equations is done with the Schur decomposition technique, the parameters of the iterative solvers are adjusted

@@ -1,17 +1,23 @@
-function [u,K,x,r]=solve_mH1(dx,lambda, nu)
+function [e1, e2, A,B,C,D,precond, x]=solve_mH1(dx,lambda, nu)
 %mesh generation
 L=2;
 H=10;
 
 x=-L:dx:H;
 
-tic
-K=construct_block_matrix(x,nu,lambda);
+
+[A,B,C,D]=construct_block_matrix(x,nu,lambda);
+
+
 r=construct_rhs(x);
-toc
-disp( "formed the matrix and the RHS");
+
+
+N=length(x);
+
 tic
-u=K\r;
+precond=schur_diagonal_precond(A,B,C,D);
+diagon_precond=@(x)precond.*x;
+[e1, e2]=solve_block_system(A,B,C,D,r(1:N), r((N+1):end),diagon_precond);
 toc
 end
 
@@ -92,7 +98,7 @@ function M=mass_matrixP1P1_scaled(x, func_kernel, nq)
 
 %nq is a number of quadrature points
     if(~nargin<3)
-        nq=5;
+        nq=2;
     end
     diagon=zeros(length(x),1);
     subdiagon=zeros(length(x)-1,1);
@@ -107,8 +113,13 @@ function M=mass_matrixP1P1_scaled(x, func_kernel, nq)
     quad_pts_current=@(a,b,quad_pts)(b-a)./2*quad_pts+(a+b)./2;
     w_current=@(a,b,w)(b-a)./2*w;
 
+
     if length(nq)==1
         [quad_pts,w]=lgwt(nq, -1, 1);
+
+
+
+
         for j=2:1:length(x)
             %integrate 1st part of diagonal ('left hat') and the subdiagonal
             %1) translate the quadrature points
@@ -146,20 +157,33 @@ function M=mass_matrixP1P1_scaled(x, func_kernel, nq)
 end
 
 
-function K=construct_block_matrix(x,nu,lambda)
+function [A,B,C,D]=construct_block_matrix(x,nu,lambda)
     L=length(x);
     K=zeros(2*L,2*L);
-    Mdelta=mass_matrixP1P1_scaled(x, @delta, 3);
-    Malpha=mass_matrixP1P1_scaled(x,@alpha,3);
-    M=mass_matrixP1(x);
[…]

### 2014-07-29 solve_mH1.m
fast implementation of the matrix assembly

@@ -1,13 +1,14 @@
-function [e1, e2, A,B,C,D,precond, x]=solve_mH1(dx,lambda, nu)
+function [e1, e2, A,B,C,D,precond, x,]=solve_mH1(dx,lambda, nu)
 %mesh generation
 L=2;
 H=10;
 
 x=-L:dx:H;
 
-
+tic
 [A,B,C,D]=construct_block_matrix(x,nu,lambda);
-
+toc
+display "for construction of the matrix"
 
 r=construct_rhs(x);
 
@@ -19,6 +20,7 @@ precond=schur_diagonal_precond(A,B,C,D);
 diagon_precond=@(x)precond.*x;
 [e1, e2]=solve_block_system(A,B,C,D,r(1:N), r((N+1):end),diagon_precond);
 toc
+display
 end
 
 
@@ -117,9 +119,6 @@ function M=mass_matrixP1P1_scaled(x, func_kernel, nq)
     if length(nq)==1
         [quad_pts,w]=lgwt(nq, -1, 1);
 
-
-
-
         for j=2:1:length(x)
             %integrate 1st part of diagonal ('left hat') and the subdiagonal
             %1) translate the quadrature points
@@ -156,14 +155,80 @@ function M=mass_matrixP1P1_scaled(x, func_kernel, nq)
     M=sparse(diag(diagon)+diag(subdiagon,-1)+diag(subdiagon,1));
 end
 
+% a (presumably) faster implementaiton of mass_matrixP1P1_scaled
+function M=mass_matrixP1P1_scaled_fast(x, func_kernel, nq)
+
+fleft_diagon=@(x_left,x_center,x)func_kernel(x).*(x-x_left).^2./(x_center-x_left).^2;
+fright_diagon=@(x_center,x_right,x)func_kernel(x).*(x-x_right).^2./(x_right-x_center).^2;
+
+
+fsubdiagon=@(x_left,x_right,x)-func_kernel(x).*bsxfun(@rdivide,bsxfun(@minus,x,x_left).*bsxfun(@minus,x,x_right),(x_right-x_left).^2);
+
+
+%nq is a number of quadrature points
+if(~nargin<3)
+nq=2;
+end
+
+diagon=zeros(1,length(x));
+subdiagon=zeros(1,length(x)-1);
+
+
+%translating quadpoints
[…]

### 2014-07-30 solve_mH1.m
fixed a major bug in generation of matrix elements with the new 'faster' function

@@ -1,4 +1,4 @@
-function [e1, e2, A,B,C,D,precond, x,]=solve_mH1(dx,lambda, nu)
+function [e1, e2, A,B,C,D,precond, x, M, G, Morig, Gorig]=solve_mH1(dx,lambda, nu)
 %mesh generation
 L=2;
 H=10;
@@ -8,9 +8,10 @@ x=-L:dx:H;
 tic
 [A,B,C,D]=construct_block_matrix(x,nu,lambda);
 toc
-display "for construction of the matrix"
+display ("for the construction of the matrix");
 
 r=construct_rhs(x);
+
 
 
 N=length(x);
@@ -20,29 +21,40 @@ precond=schur_diagonal_precond(A,B,C,D);
 diagon_precond=@(x)precond.*x;
 [e1, e2]=solve_block_system(A,B,C,D,r(1:N), r((N+1):end),diagon_precond);
 toc
-display
+display(" for the solution of the system of eqs");
 end
 
 
 function a=alpha(x)
-
+if length(x)==1
     if x<=-1 a=1;
     elseif x<=3 a=-x;
     else a=-3;
     end
-
-a=4;
+else
+a=zeros(size(x));
+a(x<=-1)=1;
+P=(x<=3)&(x>-1);
+a(P)=-x(P);
+a(x>3)=-3;
+end
 
 end
 
 function delta=delta(x)
-
+if length(x)==1
     if x<=-1 delta=0;
     elseif x<=3 delta=0.5*(x+1);
     else delta = 2;
     end
+else
+delta=zeros(size(x));
+delta(x<=-1)=0;
+P=(x<=3)&(x>-1);
+delta(P)=0.5*(x(P)+1);
+delta(x>3)=2;
+end
 
-delta=sqrt(8);
 
 
 end
@@ -158,8 +170,8 @@ end
 % a (presumably) faster implementaiton of mass_matrixP1P1_scaled
 function M=mass_matrixP1P1_scaled_fast(x, func_kernel, nq)
 
-fleft_diagon=@(x_left,x_center,x)func_kernel(x).*(x-x_left).^2./(x_center-x_left).^2;
-fright_diagon=@(x_center,x_right,x)func_kernel(x).*(x-x_right).^2./(x_right-x_center).^2;
[…]

### 2014-07-31 solve_mH1.m
local changes, need to check the correctness

@@ -1,4 +1,4 @@
-function [e1, e2, A,B,C,D,precond, x, M, G, Morig, Gorig]=solve_mH1(dx,lambda, nu)
+function [e1, e2, A,B,D,x]=solve_mH1(dx,lambda, nu)
 %mesh generation
 L=2;
 H=10;
@@ -6,10 +6,10 @@ H=10;
 x=-L:dx:H;
 
 tic
-[A,B,C,D]=construct_block_matrix(x,nu,lambda);
-toc
-display ("for the construction of the matrix");
-
+[A,B,D]=construct_block_matrix(x,nu,lambda);
+time_passed=toc();
+display (strcat(num2str(time_passed)," for the construction of the matrix"));
+p=schur_diagonal_precond(A,B,-1i*B,D);
 r=construct_rhs(x);
 
 
@@ -17,81 +17,75 @@ r=construct_rhs(x);
 N=length(x);
 
 tic
-precond=schur_diagonal_precond(A,B,C,D);
-diagon_precond=@(x)precond.*x;
-[e1, e2]=solve_block_system(A,B,C,D,r(1:N), r((N+1):end),diagon_precond);
-toc
-display(" for the solution of the system of eqs");
+[e1, e2]=solve_block_system(A,B,D,r(1:N), r((N+1):end),p);
+time_passed=toc()
+display(strcat(num2str(time_passed)," for the solution of the system of eqs"));
 end
 
 
 function a=alpha(x)
-if length(x)==1
-    if x<=-1 a=1;
-    elseif x<=3 a=-x;
-    else a=-3;
-    end
-else
+
 a=zeros(size(x));
 a(x<=-1)=1;
 P=(x<=3)&(x>-1);
 a(P)=-x(P);
 a(x>3)=-3;
-end
 
+a=4;
 end
 
 function delta=delta(x)
-if length(x)==1
-    if x<=-1 delta=0;
-    elseif x<=3 delta=0.5*(x+1);
-    else delta = 2;
-    end
-else
+
 delta=zeros(size(x));
-delta(x<=-1)=0;
-P=(x<=3)&(x>-1);
-delta(P)=0.5*(x(P)+1);
+delta(x<=-15)=0;
+P=(x>-15)&(x<=0);
+delta(P)=1+x(P)./15;
+P=(x>0)&(x<=3);
+delta(P)=1+x(P)./3;
 delta(x>3)=2;
+
+
+delta=8;
 end
 
[…]

### 2014-08-01 solve_mH1.m
efficiency improved

@@ -20,32 +20,37 @@ tic
 [e1, e2]=solve_block_system(A,B,D,r(1:N), r((N+1):end),p);
 time_passed=toc()
 display(strcat(num2str(time_passed)," for the solution of the system of eqs"));
+
 end
+
+
 
 
 function a=alpha(x)
 
 a=zeros(size(x));
-a(x<=-1)=1;
-P=(x<=3)&(x>-1);
-a(P)=-x(P);
-a(x>3)=-3;
+%a(x<=-1)=1;
+%P=(x<=3)&(x>-1);
+%a(P)=-x(P);
+%a(x>3)=-3;
+a=x;
 
-a=4;
+%a=4;
+
 end
 
 function delta=delta(x)
 
 delta=zeros(size(x));
-delta(x<=-15)=0;
-P=(x>-15)&(x<=0);
-delta(P)=1+x(P)./15;
-P=(x>0)&(x<=3);
-delta(P)=1+x(P)./3;
-delta(x>3)=2;
+%delta(x<=-15)=0;
+%P=(x>-15)&(x<=0);
+%delta(P)=1+x(P)./15;
+%P=(x>0)&(x<=3);
+%delta(P)=1+x(P)./3;
+%delta(x>3)=2;
 
+delta=0;
 
-delta=8;
 end
 
 %since the matrices are symmetric tridiagonal, each matrix constructor returns 
@@ -240,9 +245,9 @@ end
 function [A,B,D]=construct_block_matrix(x,nu,lambda)
               L=length(x);
     
-    Mdelta=mass_matrixP1P1_scaled_fast(x, @delta,3);
+    Mdelta=mass_matrixP1P1_scaled_fast(x, @delta,4);
 
-    Malpha=mass_matrixP1P1_scaled_fast(x,@alpha,3);
+    Malpha=mass_matrixP1P1_scaled_fast(x,@alpha,4);
     
     M=mass_matrixP1(x);
 
@@ -259,8 +264,7 @@ end
 
 function b=construct_rhs(x)
     b=zeros(2*length(x),1);
-b(length(x)+1)=-2*1i*sqrt(2)*exp(1i*sqrt(2)*(-22));
-
+    b(length(x)+1)=-2*1i*sqrt(2)*exp(1i*sqrt(2)*(-22));
 end
 
 
@@ -311,28 +315,24 @@ end
   
   
 %solves the block system
-%Ax+By=alpha
-  %B'x+Dy=beta
[…]

### 2014-08-01 solve_mH1.m
intermediate version. Fixed an improper sign, the new version seems to work with variable coefficients

@@ -1,15 +1,21 @@
-function [e1, e2, A,B,D,x]=solve_mH1(dx,lambda, nu)
+function [e1, e2, A,B,D,x, e11, e21]=solve_mH1(dx,lambda, nu, uniform)
 %mesh generation
-L=2;
+L=20;
 H=10;
-
+if uniform
 x=-L:dx:H;
+else
+phi=-pi/2:dx:pi/2;
+ x=(H+L)*sin(phi)/2.0+(H-L)./2.0;
+ %x=-L:dx/2.0:H/2;
+ %x=[x (H./2+dx):dx:H];
 
+end
 tic
 [A,B,D]=construct_block_matrix(x,nu,lambda);
 time_passed=toc();
 display (strcat(num2str(time_passed)," for the construction of the matrix"));
-p=schur_diagonal_precond(A,B,-1i*B,D);
+p=schur_diagonal_precond(A,B,B,D);
 r=construct_rhs(x);
 
 
@@ -17,8 +23,9 @@ r=construct_rhs(x);
 N=length(x);
 
 tic
-[e1, e2]=solve_block_system(A,B,D,r(1:N), r((N+1):end),p);
-time_passed=toc()
+[e1, e2]=solve_block_system_gmres(A,B,D,r);%(A,B,B,D,r(1:N), r((N+1):end),p);
+[e11,e21]=solve_block_system_naively(A,B,D,r(1:N), r((N+1):end),p);
+time_passed=toc();
 display(strcat(num2str(time_passed)," for the solution of the system of eqs"));
 
 end
@@ -33,9 +40,9 @@ a=zeros(size(x));
 %P=(x<=3)&(x>-1);
 %a(P)=-x(P);
 %a(x>3)=-3;
-a=x;
+%a=x;
 
-%a=4;
+a=x;
 
 end
 
@@ -180,19 +187,17 @@ fright_diagon=@(x_center,x_right,x)bsxfun(@rdivide, func_kernel(x).*(bsxfun(@min
 
 fsubdiagon=@(x_left,x_right,x)-func_kernel(x).*bsxfun(@rdivide,bsxfun(@minus,x,x_left).*bsxfun(@minus,x,x_right),(x_right-x_left).^2);
 
-
 %nq is a number of quadrature points
-if(~nargin<3)
+if(nargin<3)
 nq=2;
 end
-
-diagon=zeros(1,length(x));
-subdiagon=zeros(1,length(x)-1);
[…]

### 2014-08-04 solve_mH1.m
works with non-constant coefficient alpha, as well as non-uniform mesh

@@ -1,4 +1,4 @@
-function [e1, e2, A,B,D,x, e11, e21]=solve_mH1(dx,lambda, nu, uniform)
+function [e1, e2, Amat,Bmat,Dmat,x, e11, e21]=solve_mH1(dx,lambda, nu, uniform)
 %mesh generation
 L=20;
 H=10;
@@ -23,10 +23,15 @@ r=construct_rhs(x);
 N=length(x);
 
 tic
-[e1, e2]=solve_block_system_gmres(A,B,D,r);%(A,B,B,D,r(1:N), r((N+1):end),p);
-[e11,e21]=solve_block_system_naively(A,B,D,r(1:N), r((N+1):end),p);
+%[e1, e2]=solve_block_system_gmres(A,B,D,r);%(A,B,B,D,r(1:N), r((N+1):end),p);
+[e1,e2]=solve_block_system(A,B,B,D,r(1:N), r((N+1):end),p);
 time_passed=toc();
 display(strcat(num2str(time_passed)," for the solution of the system of eqs"));
+
+Dmat=spdiags([D(:,2) D(:,1) circshift(D(:,2),1)], -1:1, length(D), length(D));
+Amat=spdiags([A(:,2) A(:,1) circshift(A(:,2),1)], -1:1, length(A), length(A));
+Bmat=spdiags([B(:,2) B(:,1) circshift(B(:,2),1)], -1:1, length(B), length(B));
+
 
 end
 
@@ -42,7 +47,7 @@ a=zeros(size(x));
 %a(x>3)=-3;
 %a=x;
 
-a=x;
+a=-x;
 
 end
 
@@ -269,7 +274,8 @@ end
 
 function b=construct_rhs(x)
     b=zeros(2*length(x),1);
-    b(length(x)+1)=-2*1i*sqrt(2)*exp(1i*sqrt(2)*(-22));
+ %   b(length(x)+1)=-2*1i*sqrt(2)*exp(1i*sqrt(2)*(-22));
+     b(length(x)+1)=(0.17641*i*2-0.89286);
 end
 
 
@@ -321,7 +327,11 @@ end
 %Ax+By=a
   %B'x+Dy=br
 %by Schur complement and GMRES
+
+
 function [x,y]=solve_block_system_naively(A,B,D,a,br)
+  
+  
   K=zeros(length(A)+length(B));
   L=length(A);
[…]

### 2014-08-04 solve_mH1.m
forms the 7-diagonal matrix instead of the matrix consisting of 4 3-diagonal blocks and solves the system of equations with the help of the internal octave solver for banded matrices. Works in the case alpha(x)=-x, and delta(x)=0

@@ -7,36 +7,64 @@ x=-L:dx:H;
 else
 phi=-pi/2:dx:pi/2;
  x=(H+L)*sin(phi)/2.0+(H-L)./2.0;
- %x=-L:dx/2.0:H/2;
- %x=[x (H./2+dx):dx:H];
+
 
 end
 tic
 [A,B,D]=construct_block_matrix(x,nu,lambda);
 time_passed=toc();
 display (strcat(num2str(time_passed)," for the construction of the matrix"));
-p=schur_diagonal_precond(A,B,B,D);
 r=construct_rhs(x);
 
-
-
-N=length(x);
-
 tic
-%[e1, e2]=solve_block_system_gmres(A,B,D,r);%(A,B,B,D,r(1:N), r((N+1):end),p);
-[e1,e2]=solve_block_system(A,B,B,D,r(1:N), r((N+1):end),p);
+[M,rhs]=permute(A,B,D,r);
+sol=M\rhs;
+size(sol)
+size(M)
+size(rhs)
+
+[e1, e2]=permute_solution_back(sol);
+
 time_passed=toc();
 display(strcat(num2str(time_passed)," for the solution of the system of eqs"));
 
-Dmat=spdiags([D(:,2) D(:,1) circshift(D(:,2),1)], -1:1, length(D), length(D));
-Amat=spdiags([A(:,2) A(:,1) circshift(A(:,2),1)], -1:1, length(A), length(A));
-Bmat=spdiags([B(:,2) B(:,1) circshift(B(:,2),1)], -1:1, length(B), length(B));
 
 
 end
 
 
+function [M,rhs]=permute(A,B,D,rhs_old)
+n1=size(A);
+n2=size(B);
+band=zeros(n1(1)+n2(1), 4);%7-diagonal symmetric system
+%column permutation
+%e_new_{j}=e_{1,(j+1)/2} if j is odd
+%e_new_{j}=e_{2,j/2} if j is even
+rhs=zeros(length(rhs_old),1);
+rhs(2)=rhs_old(n1(1)+1);
+%forming the new symmetric matrix, with the row permutation being the same as the column permutation
+%main diagonal
+band(1:2:(end-1),1)=A(:,1);
+band(2:2:end, 1)=D(:,1);
+%subdiagonal
+band(1:2:(end-1),2)=B(:,1);
+band(2:2:(end),2)=B(:,2);
[…]

### 2014-08-04 solve_mH1.m
deleted unnessessary functions

@@ -1,4 +1,4 @@
-function [e1, e2, Amat,Bmat,Dmat,x, e11, e21]=solve_mH1(dx,lambda, nu, uniform)
+function [e1, e2,A,B,D,x]=solve_mH1(dx,lambda, nu, uniform)
 %mesh generation
 L=20;
 H=10;
@@ -18,6 +18,7 @@ r=construct_rhs(x);
 
 tic
 [M,rhs]=permute(A,B,D,r);
+save('M.mat', 'M');
 sol=M\rhs;
 size(sol)
 size(M)
@@ -36,7 +37,7 @@ end
 function [M,rhs]=permute(A,B,D,rhs_old)
 n1=size(A);
 n2=size(B);
-band=zeros(n1(1)+n2(1), 4);%7-diagonal symmetric system
+band=zeros(n1(1)+n2(1), 4);%7-diagonal symmetric system; the 'band' contains the diagonals and subdiagonals
 %column permutation
 %e_new_{j}=e_{1,(j+1)/2} if j is odd
 %e_new_{j}=e_{2,j/2} if j is even
@@ -69,10 +70,10 @@ end
 function a=alpha(x)
 
 a=zeros(size(x));
-%a(x<=-1)=1;
-%P=(x<=3)&(x>-1);
-%a(P)=-x(P);
-%a(x>3)=-3;
+a(x<=-1)=1;
+P=(x<=3)&(x>-1);
+a(P)=-x(P);
+a(x>3)=-3;
 a=-x;
 
 %a=x.^2+1;
@@ -82,15 +83,14 @@ end
 function delta=delta(x)
 
 delta=zeros(size(x));
-%delta(x<=-15)=0;
-%P=(x>-15)&(x<=0);
-%delta(P)=1+x(P)./15;
-%P=(x>0)&(x<=3);
-%delta(P)=1+x(P)./3;
-%delta(x>3)=2;
-delta=0;
+delta(x<=-15)=0;
+P=(x>-15)&(x<=0);
+delta(P)=1+x(P)./15;
+P=(x>0)&(x<=3);
+delta(P)=1+x(P)./3;
+delta(x>3)=2;
 %delta=sqrt((x.^2+1)).*sqrt(x.^2+1+x);
-
+delta=0;
 end
 
 %since the matrices are symmetric tridiagonal, each matrix constructor returns 
@@ -256,6 +256,7 @@ diagon_left=sum(result.');
 
                 
 %similarly for fright_diagon
+
[…]

### 2014-08-05 code_validity.tex
added a new file with very brief description of what we're doing

\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\newtheorem{theor}{Theorem}
\newtheorem{Lemma}{Lemma}
\newtheorem{remark}{Remark}
\newtheorem{assumption}{Assumption}\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
                                        % Activate to display a given date or no date
\newcommand{\bs}{\left\{}
\newcommand{\es}{\right.}
\newcommand{\ba}{\begin{array}}
\newcommand{\ea}{\end{array}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\ora}{\overrightarrow}
\newcommand{\x}{{\bf x}}
\newcommand{\E}{{\bf E}}
\newcommand{\n}{{\bf n}}
\newcommand{\f}{{\bf f}}
\begin{document}
\begin{subsection}{Discretization}
Idea:

Clearly, $u$ solves the well-posed problem 
\begin{align*}
a(u, v)=(f,v)\text{ for all } v=(v_{1},v_{2})^{T}\in V^2, 
\end{align*}
if and only if (this can be easily checked)
\begin{align*}
a(u,(v_{1},0)^{T})=(f,(v_{1},0)^{T}),\\
a(u,(0,v_{2})^{T})=(f,(0,v_{2})^{T}).
\end{align*}
For us it may be sufficient to check that the first equation is uniquely solvable in the sense of distributions (and if $\delta, \alpha$ are positive, we can probably even bound the norm of the solution), and thus the second equation is uniquely solvable as well (because it will be the bilinear form for the Helmholtz equation, see the thesis of Lise-Marie).

\begin{remark}
The application of the above to the variational formulation (\ref{}) allows to obtain the following system of two equations:
\[\begin{array}{l}
i\theta \displaystyle \int_{-L}^H (E_2' -\imath\theta E_1)\overline{\tilde E_1} - \int_{-L}^H \left((\epsilon_0 +\imath\nu \operatorname{Id}) \E\right)_{1} \overline{\tilde E}_{1}
=0
\end{array}
\]
and 
\begin{align}
\label{eq:E2}
\begin{array}{l}
\displaystyle \int_{-L}^H (E_2' -\imath\theta E_1)\tilde {E_2'} - \int_{-L}^H\left( (\epsilon_0 +\imath\nu\operatorname{Id}) \E\right)_{2}\overline{\tilde{E}}_{2}
\\ \displaystyle  - \imath \sqrt{\alpha(-L)} E_2 (-L) \tilde E_2 (-L) = -g_{inc} (-L) \overline{( \tilde E_2(-L) )} 
\end{array}
\end{align}
Let us consider the case $\theta=0$; in particular, from the first equation we obtain:
\begin{align*}
\int_{-L}^{H}\left((\alpha+i\nu)E_{1}+i\delta E_{2}\right)\overline{\tilde E}_{1}=0
\end{align*}
for all ${\tilde E}_{1}\in L_{2}(\Omega)$.

If the following operator
\begin{align*}
M\psi = \frac{i\delta}{(\alpha+i\nu)}\psi
\end{align*}
defines an isomorphism from $L_{2}(\Omega)$ to $L_{2}(\Omega)$, it can be shown that 
$ \frac{i\delta}{(\alpha+i\nu)}\left((\alpha+i\nu)E_{1}+i\delta E_{2}\right)$ also belongs to $L_{2}(\Omega)$ and equals zero.

Hence, we can add the second expression (\ref{eq:E2}) to
\begin{align*}
\int_{-L}^{H}\left(i\delta E_{1}-\delta^2(\alpha+i\nu)^{-1} E_{2}\right)\overline{\tilde E}_{2}=0
\end{align*}
to obtain the variational formulation for $E_{2}$, that will coincide with the variational formulation for the Helmholtz equation, and thus will be well-posed (see the thesis of L.M.I.G.).
\end{remark}

Introducing two basis spaces, $V_{E_{1}}=\{\psi_{j}\}_{j=1}^{N_{1}}$ and $V_{E_{2}}=\{\phi_{i}\}_{i=1}^{N_{2}}$, we look for the solution of the problem (\ref{}) in the form:
\begin{align*}
E_{1}=\sum\limits_{k=1}^{N_{1}}e_{1k}\psi_{k},\; E_{2}=\sum\limits_{k=1}^{N_{2}}e_{2k}\phi_{k}.
\end{align*}
Substituting $\tilde{E}_{1}=\psi_{m}, \; m=1,\ldots,N_{1}$ and $\tilde{E}_{2}=0$ into the variational formulation (\ref{}), we obtain:
\begin{align*}
i\theta\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}\bar{\psi}_{m}dx+\theta^2\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx\\
-\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{k}\bar{\psi}_{m}dx-i\sum\limits_{1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\delta(x)\phi_{k}(x)\bar{\psi}_{m}dx=0.
\end{align*}
Similarly, for $\tilde{E}_{1}=0$ and $\tilde{E}_{2}=\phi_{\ell},\; \ell=1,\ldots, N_{2}$:
\begin{align*}
\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx-i\theta\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}(x)\bar{\phi}'_{\ell}(x)dx\\
+i
\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\delta(x)\psi_{k}\bar{\phi}_{m}dx-\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\phi_{k}\bar{\phi}_{m}dx\\
-
i\lambda\sum\limits_{k=1}^{N_{2}}e_{2k}\phi_{k}(-L)\bar{\phi}_{m}(-L)=-g_{inc}(x)\bar{\phi}_{m}(-L).
\end{align*}
After introduction 
\begin{align*}
\left(K^{\psi,\phi'}\right)_{mk}=\int\limits_{-L}^{H}\bar{\psi}_{m}\phi'_{k}dx,\qquad \left(M^{\psi}\right)_{mk}=\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx,\\
\left(M^{\alpha,\psi}\right)_{mk}=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{m}\bar{\psi}_{k}dx, \qquad \left(M^{\delta,\psi,\phi}\right)_{mk}=\int\limits_{-L}^{H}\delta(x)\bar{\psi}_{m}\phi_{k}dx,\\
K_{\ell k}=\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx,\qquad \left(M^{\alpha,\phi}\right)_{\ell k}=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\bar{\phi}_{\ell}\phi_{k}dx,\\
I_{km}^{\Gamma}=\bar{\phi}_{m}(-L)\phi_{k}(-L),\\
\boldsymbol{e}_{1}=\left(e_{11},\ldots,e_{1 N_{1}}\right)^{T},\; \boldsymbol{e}_{2}=\left(e_{21},\ldots,e_{2 N_{1}}\right)^{T},\\
\boldsymbol{0}_{n} \text{ is an $n$-dimensional column vector with all zeros}.
\end{align*}
the above system of equations can be rewritten in an antisymmetric block form:
\begin{align*}
\left(\begin{matrix}
\theta^2 M_{\psi}-M^{\alpha,\psi} & i\theta K^{\psi,\phi'}-i M^{\delta,\psi,\phi} \\
-i\theta (K^{\psi,\phi'})^{*}+i (M^{\delta,\psi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
\end{matrix}\right)
\left(
\begin{matrix}
\boldsymbol{e}_1\\
\boldsymbol{e}_2
\end{matrix}
\right)=-g_{inc}(-L)
\left(
\begin{matrix}
\boldsymbol{0}_{N_{1}}\\
\bar{\phi}_{1}(-L)\\
\bar{\phi}_{2}(-L)\\
\vdots\\
\bar{\phi}_{N_{2}}(-L)
\end{matrix}
\right).
\end{align*}
This expression greatly simplifies when choosing $V_{E_{1}}=V_{E_{2}}=\left(\phi_{m}\right)_{m=1}^{N_{2}}$ and in the case $\theta=0$:
\begin{align*}
\left(\begin{matrix}
M^{\alpha,\phi} & i M^{\delta,\phi,\phi} \\
i (M^{\delta,\phi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
\end{matrix}\right)
\left(
\begin{matrix}
\boldsymbol{e}_1\\ 
\boldsymbol{e}_2
\end{matrix}
\right)=-g_{inc}(-L)
\left(
\begin{matrix}
\boldsymbol{0}_{N_{1}}\\
\bar{\phi}_{1}(-L)\\
\bar{\phi}_{2}(-L)\\
\vdots\\
\bar{\phi}_{N_{2}}(-L)
\end{matrix}
\right).
\end{align*}
\end{subsection}
\begin{subsection}{Numerical Experiments}
We implemented the above scheme for a simple case

To check the validity of the code, we perform a numerical experiment with parameters:
\begin{align*}
\alpha(x)=x^2+1,\qquad \delta(x)=\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}.
\end{align*}
Additionally, the boundary conditions read as 
\begin{align}
\label{eq:bcs}
\partial_{1}E_{2}(-L)+2iE_{2}(-L)=2iAi(-L)+Ai'(-L),\\
\partial_{1}E_{2}(H)=0,
\end{align}
where $Ai(x)$ is the Airy function.

It can be shown that 
\begin{align*}
E_{2}=Ai(x),\\
E_{1}=-i\frac{\delta(x)}{\alpha(x)}Ai(x)
\end{align*}
is the solution to the problem (\ref{}) with the boundary condition (\ref{eq:bcd}).

In Figure \ref{} we show the convergence rate for the problem.

The next experiment we perform for the case of the resonance.

We consider the dependence of the condition number of the obtained matrix on $\nu$, for various values $h$.

$L=-20$, $H=10$, the parameters are like in the thesis of LMIG, and $\lambda=2$.

\begin{figure}
\end{figure}

\end{subsection}

\end{document}

### 2014-08-05 solve_mH1.m
cleaned up the code a bit

@@ -1,6 +1,6 @@
-function [e1, e2,A,B,D,x]=solve_mH1(dx,lambda, nu, uniform)
+function [e1, e2,M,x]=solve_mH1(dx,lambda, nu, uniform)
 %mesh generation
-L=20;
+L=2;
 H=10;
 if uniform
 x=-L:dx:H;
@@ -21,8 +21,7 @@ tic
 save('M.mat', 'M');
 sol=M\rhs;
 size(sol)
-size(M)
-size(rhs)
+
 
 [e1, e2]=permute_solution_back(sol);
 
@@ -67,6 +66,11 @@ e2=sol(2:2:end);
 
 end
 
+
+
+
+
+
 function a=alpha(x)
 
 a=zeros(size(x));
@@ -74,7 +78,7 @@ a(x<=-1)=1;
 P=(x<=3)&(x>-1);
 a(P)=-x(P);
 a(x>3)=-3;
-a=-x;
+%a=-x;
 
 %a=x.^2+1;
 
@@ -82,15 +86,13 @@ end
 
 function delta=delta(x)
 
+
 delta=zeros(size(x));
-delta(x<=-15)=0;
-P=(x>-15)&(x<=0);
-delta(P)=1+x(P)./15;
-P=(x>0)&(x<=3);
-delta(P)=1+x(P)./3;
+delta(x<=-1)=0;
+P=(x<=3)&(x>-1);
+delta(P)=0.5*(x(P)+1);
 delta(x>3)=2;
-%delta=sqrt((x.^2+1)).*sqrt(x.^2+1+x);
-delta=0;
+
 end
 
 %since the matrices are symmetric tridiagonal, each matrix constructor returns 

### 2014-08-06 time_dependant_pb.py
bugged time dependant pb file

@@ -1,0 +1,180 @@
+#!/usr/bin/python
+# -*- coding: utf-8 -*-
+from __future__ import division
+import os
+from time import time
+import numpy as np
+from pylab import *
+from scipy.special import airy
+#mesh size
+N = 256
+#domain ]-L ; H[, (mL=-L)
+mL = -20
+H =  10
+#space step 
+dx = (H-mL)/N
+#time step
+dt = 0.5*dx
+#final time 
+tfinal = 10
+#constants 
+me = 9.11e-31#electron mass (kg)
+Ne = 1e19 #density of e- f(x)
+e =  1.6e-19 #electron charge (coulombs)
+eps0 = 8.85e-12 #permeability  (F/m)
+nu = 1000#friction
+B0 = 1 #given
+c = 3e8 
+
+gamma = e*dt / (me*c*c*eps0)
+beta = e*B0*dt/(c*me)
+nud = nu*dt/c
+
+alphamL = 2
+alphaey = complex(0,alphamL)/2 - 1/dx
+#airy function return
+def airy_one(x):
+    [A,B,C,D] = airy(x)
+    return A
+def airy_two(x):
+    [A,B,C,D] = airy(x)
+    return B
+
+#initialisation
+def g(t) : 
+    return (airy_two(mL) + complex(0,alphamL)*airy_one(mL))*np.exp(complex(0,t))
+X    = map(lambda i: mL + i*dx, range(N+2))
+X12  = map(lambda i: mL+0.5*dx + i*dx, range(N+1))
+#Ex   = map(lambda x: np.exp(complex(0,k*x)),X)
+Ex   = map(lambda x: 0, X)
+#ux   = map(lambda x: np.exp(complex(0,k*x)),X)
+ux   = map(lambda x: 0, X)
+#H    = map(lambda x: np.exp(complex(0,k*x)),X)
+H    = map(lambda x: 0, X)
+#Ey   = map(lambda x: np.exp(complex(0,k*x)),X12)
+Ey   = map(lambda x: airy_one(x),X12)
+AiryVec = map(lambda x: airy_one(x),X12)
+#uy   = map(lambda x: np.exp(complex(0,k*x)),X12)
+uy    = map(lambda x: 0, X)
+def Ne(x) : 
+    a = (gamma*gamma- beta*beta)*e*e*e*e/(me*me*eps0*eps0)
[…]

### 2014-08-06 time_dependant_pb.py
still some bugs

@@ -20,14 +20,14 @@ tfinal = 10
 #constants 
 me = 9.11e-31#electron mass (kg)
 Ne = 1e19 #density of e- f(x)
-e =  1.6e-19 #electron charge (coulombs)
+e =  -1.6e-19 #electron charge (coulombs)
 eps0 = 8.85e-12 #permeability  (F/m)
-nu = 1000#friction
+nu = 0#friction
 B0 = 1 #given
 c = 3e8 
 
 gamma = e*dt / (me*c*c*eps0)
-beta = e*B0*dt/(c*me)
+beta = abs(e)*B0*dt/(c*me)
 nud = nu*dt/c
 
 alphamL = 2
@@ -42,7 +42,7 @@ def airy_two(x):
 
 #initialisation
 def g(t) : 
-    return (airy_two(mL) + complex(0,alphamL)*airy_one(mL))*np.exp(complex(0,t))
+    return (airy_two(mL)+complex(0,alphamL)*airy_one(mL))*np.exp(complex(0,t))*eps0*c
 X    = map(lambda i: mL + i*dx, range(N+2))
 X12  = map(lambda i: mL+0.5*dx + i*dx, range(N+1))
 #Ex   = map(lambda x: np.exp(complex(0,k*x)),X)
@@ -56,17 +56,26 @@ Ey   = map(lambda x: airy_one(x),X12)
 AiryVec = map(lambda x: airy_one(x),X12)
 #uy   = map(lambda x: np.exp(complex(0,k*x)),X12)
 uy    = map(lambda x: 0, X)
+wc= abs(e*B0)/me
+kappa = wc/(c*(c*c-wc*wc))
+psi = 1/(c*c-wc*wc)
 def Ne(x) : 
-    a = (gamma*gamma- beta*beta)*e*e*e*e/(me*me*eps0*eps0)
-    b =  (x*beta+2*beta)*(e/(me*eps0))
+    a = (kappa*kappa- psi*psi)*e*e*e*e/(me*me*eps0*eps0)
+    b =  (x*psi+2*psi)*(e/(me*eps0))
     c = x-1
-    delta = (x*beta+2*beta-beta*beta)**2 - 4*(x-1)*(gamma*gamma*e*e*e*e/(me*me*eps0*eps0))
+    delta = (x*psi+2*psi-psi*psi)**2 - 4*(x-1)*(kappa*kappa*e*e*e*e/(me*me*eps0*eps0))
+    print delta 
[…]

### 2014-08-07 time_dependant_pb.py
corr time dependant problem (still bugs)

@@ -1,48 +1,68 @@
 #!/usr/bin/python
 # -*- coding: utf-8 -*-
+
 from __future__ import division
 import os
 from time import time
 import numpy as np
 from pylab import *
 from scipy.special import airy
-#mesh size
-N = 256
-#domain ]-L ; H[, (mL=-L)
-mL = -20
-H =  10
-#space step 
-dx = (H-mL)/N
-#time step
-dt = 0.5*dx
-#final time 
-tfinal = 10
-#constants 
-me = 9.11e-31#electron mass (kg)
-Ne = 1e19 #density of e- f(x)
-e =  -1.6e-19 #electron charge (coulombs)
-eps0 = 8.85e-12 #permeability  (F/m)
-nu = 0#friction
-B0 = 1 #given
-c = 3e8 
 
-gamma = e*dt / (me*c*c*eps0)
-beta = abs(e)*B0*dt/(c*me)
-nud = nu*dt/c
 
+#---------------CONSTANTS--------------------#
+# mesh size
+N      = 124
+# domain ]-L ; H[, (mL=-L)
+mL     = -20
+H      =  10
+# space step 
+dx     = (H-mL)/N
+print "dx", dx
+# time step
+dt     = 0.5*dx
+print "dt",dt
+# Number of time steps
+Ntime = 1
+# constants 
+me     = 1#9.11e-31               #electron mass (kg)
+e      = 1#1.6e-19               #electron charge (coulombs)
+eps0   = 1#8.85e-12               #permeability  (F/m)
+nu     = 1                     #friction
+B0     = 1                      #given
+c      = 1#3e8 
+
+
+#gamma/beta/nudelta
+gamma  = -e*dt / (me*c*c*eps0)
+beta   = -abs(e)*B0*dt/(c*me)
+nud    = nu*dt/c
+print 'gamma',gamma
+print 'beta',beta
+print 'nudelta', nud
+#alpha(-L)
 alphamL = 2
+
+#coeff alpha (1/alpha_Ey)Ey in left BC
 alphaey = complex(0,alphamL)/2 - 1/dx
-#airy function return
+print 'alphaey', alphaey
+#-------------airy functions------------------#
+#return A
 def airy_one(x):
     [A,B,C,D] = airy(x)
     return A
+#return A'
[…]

### 2014-08-07 time_dependant_pb.py
last version

@@ -7,13 +7,13 @@ from time import time
 import numpy as np
 from pylab import *
 from scipy.special import airy
-
+import copy
 
 #---------------CONSTANTS--------------------#
 # mesh size
-N      = 124
+N      = 500
 # domain ]-L ; H[, (mL=-L)
-mL     = -20
+mL     = -1
 H      =  10
 # space step 
 dx     = (H-mL)/N
@@ -22,13 +22,13 @@ print "dx", dx
 dt     = 0.5*dx
 print "dt",dt
 # Number of time steps
-Ntime = 1
+Ntime = 50
 # constants 
 me     = 1#9.11e-31               #electron mass (kg)
 e      = 1#1.6e-19               #electron charge (coulombs)
 eps0   = 1#8.85e-12               #permeability  (F/m)
 nu     = 1                     #friction
-B0     = 1                      #given
+B0     = 0                      #given
 c      = 1#3e8 
 
 
@@ -57,8 +57,10 @@ def airy_two(x):
 #-----------------------------------------------#
 
 #--------------G for left BC -------------------#
+alpha = 2
+omega = 0
 def g(t) : 
-    return (airy_two(mL)+complex(0,alphamL)*airy_one(mL))*np.exp(complex(0,t))*eps0*c
+    return np.exp(-alpha*t)*(-alpha*np.exp(-alpha*mL)+ complex(0,alphamL)*np.exp(-alpha*mL)) #(airy_two(mL)+complex(0,alphamL)*airy_one(mL))*np.exp(complex(0,t))*eps0*c
 
 #-----------------------------------------------#
 #------table and functions initialisation-------#
@@ -70,18 +72,18 @@ Ex   = map(lambda x: 0, X)
 #ux   = map(lambda x: np.exp(complex(0,k*x)),X)
 ux   = map(lambda x: 0, X)
 #H    = map(lambda x: np.exp(complex(0,k*x)),X)
-H    = map(lambda x: 0, X)
-#Ey   = map(lambda x: np.exp(complex(0,k*x)),X12)
-Ey   = map(lambda x: airy_one(x),X12)
[…]

### 2014-08-07 time_dependant_pb.py
fixed a couple of bugs

@@ -6,6 +6,7 @@ import os
 from time import time
 import numpy as np
 from pylab import *
+import scipy.io
 from scipy.special import airy
 import copy
 
@@ -65,8 +66,8 @@ def g(t) :
 #-----------------------------------------------#
 #------table and functions initialisation-------#
 #-----------------------------------------------#
-X    = map(lambda i: mL + i*dx, range(N+2))
-X12  = map(lambda i: mL+0.5*dx + i*dx, range(N+1))
+X    = map(lambda i: mL + i*dx, range(N+1))
+X12  = map(lambda i: mL+0.5*dx + i*dx, range(N))
 #Ex   = map(lambda x: np.exp(complex(0,k*x)),X)
 Ex   = map(lambda x: 0, X)
 #ux   = map(lambda x: np.exp(complex(0,k*x)),X)
@@ -80,6 +81,7 @@ Ey   = map(lambda x: np.exp(-alpha*x),X12)
 uy    = map(lambda x: 0, X12)
 
 H12 = map(lambda x: -np.exp(-alpha*dt/2)*np.exp(-alpha*x),X)
+
 tux = copy.deepcopy(ux)
 tuy = copy.deepcopy(uy)
 tEx = copy.deepcopy(Ex)
@@ -175,56 +177,64 @@ def Kcoeff(x):
 #------------------------time loop--------------------------#
 #-----------------------------------------------------------#
 t = 1
-while (t<Ntime):
+
+while (t<=Ntime):
     
 
     #------------------- ux -> tux
-    for i in range(N+1):
+    for i in range(N-1):
         
-        [K1,K2,K1x,K2x] = Kcoeff(NE[i])
+       # [K1,K2,K1x,K2x] = Kcoeff(NE[i])
         tux[i] =  0 #(1/K1x) * (K2x*ux[i] + gamma*Ex[i] + ((beta*gamma)/(2*K1))*Ey[i]\
                     #           - beta*gamma*dt/(4*K1)*((H12[i] - H12[i-1])/dx)   \
                     #           + (beta/2)*(K2/K1 + 1)*uy[i])
         
[…]

### 2014-08-08 time_dependant_pb.py
add uy

@@ -168,10 +168,14 @@ def plot_imag2(X,T,U,s,s5,s2,s3,s4):
 
 #--------------------K1&K2 s def function-------------------#
 def Kcoeff(x): 
-    K1     =  1 + nud/2. - (gamma*dt)*e*x/4
-    K2     =  1 - nud/2. + (gamma*dt)*e*x/4
-    K1x    =  K1 + beta*beta/(4*K1)
-    K2x    =  K2 - beta*beta/(4*K1)
+    #K1     =  1 + nud/2. - (gamma*dt)*e*x/4
+    K1     =  1 + nu * dt/2 + dt*dt*Ne*e*e/(4*me)
+    #K2     =  1 - nud/2. + (gamma*dt)*e*x/4
+    K2     =  1 - nu * dt/2 - dt*dt*Ne*e*e/(4*me)
+    #K1x    =  K1 + beta*beta/(4*K1)
+    #K2x    =  K2 - beta*beta/(4*K1)
+    K1x = 0
+    K2x = 0
     return [K1,K2,K1x,K2x]
 #-----------------------------------------------------------#
 #------------------------time loop--------------------------#
@@ -194,21 +198,23 @@ while (t<=Ntime):
     tux[N] =  0#(1/K1x)*(K2x*ux[N+1] + gamma*Ex[N+1] + ((beta*gamma)/(2*K1))*Ey[N]\
                  #             - beta*gamma*dt/(4*K1)*(H12[N+1] - H12[N])/dx   \
                  #             + (beta/2)*(K2/K1 + 1)*uy[N])
+    scipy.io.savemat('uy.mat',  {'uy': uy}); 
 
     #-------------------- u y->tuy
     for i in range(N-2):
-      #  [K1,K2,K1x,K2x] = Kcoeff(NE[i])
-        tuy[i] = 0# (1/K1)*(K2*uy[i] + gamma*Ey[i] - gamma*dt/2 *(H12[i+1] - H12[i])/dx\
+        [K1,K2,K1x,K2x] = Kcoeff(NE[i])
+        #tuy[i] = 0# (1/K1)*(K2*uy[i] + gamma*Ey[i] - gamma*dt/2 *(H12[i+1] - H12[i])/dx\
                   #            - beta*(tux[i] + ux[i])/2)
[…]

### 2014-08-08 time_dependant_pb.py
correc

@@ -169,9 +169,9 @@ def plot_imag2(X,T,U,s,s5,s2,s3,s4):
 #--------------------K1&K2 s def function-------------------#
 def Kcoeff(x): 
     #K1     =  1 + nud/2. - (gamma*dt)*e*x/4
-    K1     =  1 + nu * dt/2 + dt*dt*Ne*e*e/(4*me)
+    K1     =  1 + nu * dt/2 + dt*dt*x*e*e/(4*me)
     #K2     =  1 - nud/2. + (gamma*dt)*e*x/4
-    K2     =  1 - nu * dt/2 - dt*dt*Ne*e*e/(4*me)
+    K2     =  1 - nu * dt/2 - dt*dt*x*e*e/(4*me)
     #K1x    =  K1 + beta*beta/(4*K1)
     #K2x    =  K2 - beta*beta/(4*K1)
     K1x = 0
@@ -210,7 +210,7 @@ while (t<=Ntime):
   #  [K1,K2,K1x,K2x] = Kcoeff(NE[N+1])
     #tuy[N-1] =  0#(1/K1)*(K2*uy[N] + gamma*Ey[N] - gamma*dt/2 *(H12[N+1] - H12[N])/dx\
                #           - beta*(tux[N] + ux[N])/2)
-    tuy[N-1] = (1/K1) * (K2 * uy[N-1] - dt * e / me * Ey[N-1] + dt*dt*e/(2*me) * (H12[N+1] - H12[N])/dx)
+    tuy[N-1] = (1/K1) * (K2 * uy[N-1] - dt * e / me * Ey[N-1] + dt*dt*e/(2*me) * (H12[N] - H12[N-1])/dx)
     #------------------- E -> tE
     scipy.io.savemat('H12.mat',  {'H12': H12});
     scipy.io.savemat('Eyo.mat',  {'Eyo': Ey});

### 2014-08-08 make_convergence_test.m
added additional files to check the validity of the code, compute errors as well as run convergence tests

@@ -1,0 +1,37 @@
+h0=1.0;
+k=0:1:15
+nu=2.^(-k);
+href=1e-6;
+l=1:1:20;
+h=href*2.^l;
+result_l2e1=zeros(length(nu), length(h));
+result_l2e2=zeros(length(nu), length(h));
+result_h1e2=zeros(length(nu), length(h));
+result_pwe1=zeros(length(nu), length(h));
+result_pwe2=zeros(length(nu), length(h));
+
+for k=1:1:16
+	%compute the reference solution for nu(k)
+	[e1ref,e2ref]=solve_mH1(href,2.0,nu(k),1);
+	for l=1:1:20
+		%compute the solution for the current h(l)
+		[e1,e2,M,x,Kstiff, Mmass]=solve_mH1(h(l),2.0,nu(k),1);
+		%compute the reference solutions on the coarser mesh
+		e1rc=e1ref(1:(2^l):end);
+		e2rc=e2ref(1:(2^l):end);
+		
+		[result_l2e1(k,l), result_h1e2(k,l), result_l2e2(k,l), result_pwe1(k,l), result_pwe2(k,l)]=compute_error(Kstiff, Mmass, e1, e2, e1rc, e2rc);
+	end
+end
+
+save('result_l2e1.mat', 'result_l2e1');
+save('result_h1e2.mat', 'result_h1e2');
+save('result_l2e2.mat', 'result_l2e2');
+save('result_pwe1.mat', 'result_pwe1');
+save('result_pwe2.mat', 'result_pwe2');
+
+
+
+
+
+

### 2014-08-08 make_convergence_test_exact.m
added convergence tests

@@ -1,0 +1,18 @@
+function [e1l2, e2l2, e2h1]=make_convergence_test_exact
+p=0:1:7;
+h=10.^(-7+p);
+e1l2=zeros(length(h),1 );
+e2l2=zeros(length(h),1 );
+e2h1=zeros(length(h),1 );
+
+f=@(x)airy(x);
+g=@(x)airy(1,x);
+ex=@(x)airy(x).*(-1i).*sqrt(x.^2+1).*sqrt(x.^2+1+x)./(x.^2+1);
+for k=1:1:8
+ [e1, e2,M,x, Kstiff, Mmass]=solve_mH1_airy(h(k),2, 0,1);
+ [e1l2(k), e2l2(k), e2h1(k)]=compute_error_exact(e1,e2,x,ex,f,g);
+end
+save('e1l2.mat', 'e1l2');
+save('e2l2.mat', 'e2l2');
+save('e2h1.mat', 'e2h1');
+end

### 2014-08-08 compute_error_exact.m
changed ()^2 to ||^2 for the computation of the l2 norm

@@ -25,7 +25,7 @@ Q=quad_pts_current(x(1:1:end-1)',x(2:1:end)',quad_pts);
 F=bsxfun(@times, weight_matrix, (f(Q)+q(Q)-exact(Q)).^2);
 
 
-e1=sqrt(sum(sum(F)))
+e1=sqrt(sum(sum(abs(F))))
 
 
 end
@@ -51,7 +51,7 @@ F=bsxfun(@times, weight_matrix, A);
 P=F;
 
 
-e2=sqrt(sum(sum(F)))
+e2=sqrt(sum(sum(abs(F))))
 
 
 %B=zeros(size(A));

### 2014-08-08 time_dependant_pb.py
fixings....

@@ -28,18 +28,19 @@ Ntime = 50
 me     = 1#9.11e-31               #electron mass (kg)
 e      = 1#1.6e-19               #electron charge (coulombs)
 eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 1                     #friction
+nu     = 0                     #friction
 B0     = 0                      #given
 c      = 1#3e8 
 
 
 #gamma/beta/nudelta
-gamma  = -e*dt / (me*c*c*eps0)
-beta   = -abs(e)*B0*dt/(c*me)
-nud    = nu*dt/c
-print 'gamma',gamma
-print 'beta',beta
-print 'nudelta', nud
+#gamma  = -e*dt / (me*c*c*eps0)
+
+#beta   = -abs(e)*B0*dt/(c*me)
+#nud    = nu*dt/c
+#print 'gamma',gamma
+#print 'beta',beta
+#print 'nudelta', nud
 #alpha(-L)
 alphamL = 2
 
@@ -48,44 +49,15 @@ alphaey = complex(0,alphamL)/2 - 1/dx
 print 'alphaey', alphaey
 #-------------airy functions------------------#
 #return A
-def airy_one(x):
-    [A,B,C,D] = airy(x)
-    return A
+#def airy_one(x):
+#    [A,B,C,D] = airy(x)
+#    return A
 #return A'
-def airy_two(x):
-    [A,B,C,D] = airy(x)
-    return B
+#def airy_two(x):
+#    [A,B,C,D] = airy(x)
+#    return B
 #-----------------------------------------------#
 
-#--------------G for left BC -------------------#
-alpha = 2
-omega = 0
-def g(t) : 
-    return np.exp(-alpha*t)*(-alpha*np.exp(-alpha*mL)+ complex(0,alphamL)*np.exp(-alpha*mL)) #(airy_two(mL)+complex(0,alphamL)*airy_one(mL))*np.exp(complex(0,t))*eps0*c
-
-#-----------------------------------------------#
-#------table and functions initialisation-------#
-#-----------------------------------------------#
-X    = map(lambda i: mL + i*dx, range(N+1))
-X12  = map(lambda i: mL+0.5*dx + i*dx, range(N))
-#Ex   = map(lambda x: np.exp(complex(0,k*x)),X)
[…]

### 2014-08-08 time_dependant_pb.py
fixed a boundary condition related bug

@@ -86,7 +86,8 @@ gamma = np.sqrt(omega*omega-wp*wp)
 alpha = 2
 
 def g(t) : 
-    return (1/dt)*np.exp(complex(0,omega*t)-gamma*mL)*(1-np.exp(-gamma*dx))+complex(0,alphamL)*np.exp(-gamma*mL+complex(0,omega*t)) 
+    return np.exp(complex(0,omega*t))*np.exp(-gamma*mL)*(-gamma+complex(0,alphamL));
+#(1/dt)*np.exp(complex(0,omega*t)-gamma*mL)*(1-np.exp(-gamma*dx))+complex(0,alphamL)*np.exp(-gamma*mL+complex(0,omega*t)) 
 #(airy_two(mL)+complex(0,alphamL)*airy_one(mL))*np.exp(complex(0,t))*eps0*c
 #-----------------------------------------------#
 #------table and functions initialisation-------#

### 2014-08-08 time_dependant_pb.py
bugs

@@ -192,7 +192,7 @@ t = 1
 while (t<=Ntime):
     #---------------- H -> H12
     H12[0] = H12[0] -  dt/dx * (tEy[0] \
-                                  - (1/alphaey) * (g(t*dt) -  complex(0,alphamL)/2 * tEy[0] \
+                                  - (1/alphaey) * (g(t*dt-dt) -  complex(0,alphamL)/2 * tEy[0] \
                                                        - (1/dx)* tEy[0]))
 
     #H12[0] = H12[0] - dt/dx *(tEy[0] - np.exp(-alpha*(mL-dx/2))*np.exp(-alpha*t*dt))
@@ -258,7 +258,7 @@ while (t<=Ntime):
     H  = copy.deepcopy(H12)
     time = t*dt
     Eyex   = map(lambda x: np.exp(complex(0,omega*time))*np.exp(-gamma*x),X12)
-    Hex    = map(lambda x: (gamma/complex(0,omega))*np.exp(-gamma*x)*np.exp(complex(0,omega*time)),X)
+    Hex    = map(lambda x: (gamma/complex(0,omega))*np.exp(-gamma*x)*np.exp(complex(0,omega*(time+dt/2))),X)
     Uyex   = map(lambda x: -(e/me)*np.exp(complex(0,omega*time)-gamma*x),X12)
     temp = 0
     for i in range(N):

### 2014-08-08 time_dependant_pb_v2.py
extra code with some bugs fixed

@@ -1,0 +1,297 @@
+#!/usr/bin/python
+# -*- coding: utf-8 -*-
+
+from __future__ import division
+import os
+from time import time
+import numpy as np
+from pylab import *
+import scipy.io
+from scipy.special import airy
+import copy
+
+#---------------CONSTANTS--------------------#
+# mesh size
+N      = 500
+# domain ]-L ; H[, (mL=-L)
+mL     = -1
+H      =  10
+# space step 
+dx     = (H-mL)/N
+print "dx", dx
+# time step
+dt     = 0.5*dx
+print "dt",dt
+# Number of time steps
+Ntime = 50
+# constants 
+me     = 1#9.11e-31               #electron mass (kg)
+e      = 1#1.6e-19               #electron charge (coulombs)
+eps0   = 1#8.85e-12               #permeability  (F/m)
+nu     = 0                     #friction
+B0     = 0                      #given
+c      = 1#3e8 
+
+
+#gamma/beta/nudelta
+#gamma  = -e*dt / (me*c*c*eps0)
+
+#beta   = -abs(e)*B0*dt/(c*me)
+#nud    = nu*dt/c
+#print 'gamma',gamma
+#print 'beta',beta
+#print 'nudelta', nud
+#alpha(-L)
+alphamL = 2
+
+#coeff alpha (1/alpha_Ey)Ey in left BC
+alphaey = complex(0,alphamL)/2 - 1/dx
+print 'alphaey', alphaey
+#-------------airy functions------------------#
+#return A
+#def airy_one(x):
+#    [A,B,C,D] = airy(x)
+#    return A
+#return A'
+#def airy_two(x):
+#    [A,B,C,D] = airy(x)
+#    return B
+#-----------------------------------------------#
+
+#-------------------------- NE --------------------------#
+# Ne constants definition
+wc    = e*abs(B0)/me
+print "omega_c" ,wc
+# Ne function
+def Ne(x) :  
+    a     = wc/(c*(wc*wc-c*c))
+    b     = 1/(wc*wc-c*c)
+    kappa = e*e/(eps0*me)
+
+    a2    = (a*a-b*b)*kappa*kappa
[…]

### 2014-08-11 code_validity.tex
the file that describes what we're doing
the file that describes the discretization and some of the numerics
fixed a mistake

@@
 \usepackage{epstopdf}
+\usepackage{tikz}
+\usepackage{pgfplots}
+\usepackage{slashbox}
 \newtheorem{theor}{Theorem}
@@
 \newtheorem{remark}{Remark}
+\usepackage[font=small,skip=0pt]{caption}
+\setlength{\abovecaptionskip}{20pt plus 3pt minus 2pt}
 \newtheorem{assumption}{Assumption}\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
@@
 to obtain the variational formulation for $E_{2}$, that will coincide with the variational formulation for the Helmholtz equation, and thus will be well-posed (see the thesis of L.M.I.G.).
+
+Thus we can repeat the estimates from the above-mentioned thesis, and estimate $\|E_{1}\|_{L_{2}}$ in terms of $\|E_{2}\|_{L_{2}}$.
 \end{remark}
@@
 This expression greatly simplifies when choosing $V_{E_{1}}=V_{E_{2}}=\left(\phi_{m}\right)_{m=1}^{N_{2}}$ and in the case $\theta=0$:
-\begin{align*}
+\begin{align}
+\label{eq:simple_system}
 \left(\begin{matrix}
@@
 \right).
-\end{align*}
+\end{align}
 \end{subsection}
 \begin{subsection}{Numerical Experiments}
-We implemented the above scheme for a simple case
+We implemented the above scheme for a simple case of $P_{1}$-space used for the approximation of $E_{1}$ and $E_{2}$, $\theta=0$.
 
-To check the validity of the code, we perform a numerical experiment with parameters:
-\begin{align*}
+To check the validity of the code, we perform a numerical experiment with (formally chosen) parameters:
+\begin{align}
+\label{eq:parameters}
 \alpha(x)=x^2+1,\qquad \delta(x)=\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}.
-\end{align*}
+\end{align}
 Additionally, the boundary conditions read as 
@@
 \end{align*}
-is the solution to the problem (\ref{}) with the boundary condition (\ref{eq:bcd}).
+is the solution to the problem with parameters (\ref{eq:parameters}) with the boundary condition (\ref{eq:bcs}).
 
-In Figure \ref{} we show the convergence rate for the problem.
-
-The next experiment we perform for the case of the resonance.
-
-We consider the dependence of the condition number of the obtained matrix on $\nu$, for various values $h$.
-
-$L=-20$, $H=10$, the parameters are like in the thesis of LMIG, and $\lambda=2$.
+In Figure \ref{fig:conv_rate} we demonstrate the convergence rates for this problem, with 
+\begin{align*}
+\|E_{1}-E_{1}^{c}\|_{L_{2}(\Omega)}=\left(\int\limits_{\Omega}\left|E_{1}-\sum\limits_{k=0}^{N}E_{1i}\phi_{i}\right|^2dx\right),
+\end{align*}
+where $\left(\phi_{i}\right)$ are $P_{1}$-finite elements. Similarly $\|E_{2}-E_{2}^{c}\|_{L_{2}(\Omega)}$ and $\|E_{2}-E_{2}^{c}\|_{H_{1}(\Omega)}$ are defined.
 
 \begin{figure}
+\begin{tikzpicture}
+    \begin{loglogaxis}[
+        xlabel=$h$,
+        ylabel=$Error$,
+        legend style={
+at={(0.2,1.5)},
+legend pos= south east,
+anchor=south east, 
+draw=none
+}
+]
+    \addplot[mark=*,blue] table {E1L2.dat}; 
+    \addlegendentry{$\|E_{1}-E_{1}^{c}\|_{L_{2}}$};
+    \addplot[mark=*,red] table {E2H1.dat};
+        \addlegendentry{$\|E_{2}-E_{2}^{c}\|_{H_{1}}$};
+
+          \addplot[mark=*,cyan] table {E2L2.dat};
+        \addlegendentry{$\|E_{2}-E_{2}^{c}\|_{L_{2}}$};  
+        \addplot[dotted] table{E_h2.dat};
+         \addlegendentry{$O(h^2)$};
+         \addplot[dashed] table{H.dat};
+         \addlegendentry{$O(h)$};
+    \end{loglogaxis}
+    \end{tikzpicture}
+    \caption{Convergence rates for the problem with parameters (\ref{eq:parameters}) with the boundary condition (\ref{eq:bcs}).}
+    \label{fig:conv_rate}
+\end{figure}
+
+Note that in the last 3 experiments the accuracy of the solution of the system of equations, namely $\|Ae-r\|$ (where $e$ is the solution vector, $r$ is the right hand side and $A$ us the matrix) exceeded 1.6e-9 (namely, it was 1.6e-9 ($h=3.2e-5$), 1.3e-08 ($h=8e-6$), 1.04e-07 ($h=2e-6$))
+
+The next experiment we perform for the case of the resonance. $L=-2$, $H=10$, the parameters are like in the thesis of LMIG, and the boundary condition (\ref{eq:bcs}) with $g^{inc}=2, \lambda=2.0$.
+
+We consider the dependence of the condition number of the block matrix on $\nu$, for several values of $h$ (see Table \ref{tab:cond_number}).
+\begin{table}[ht!]
+\begin{tabular}{c|ccccccccc}
+\backslashbox{$h$}{$\nu$}
+ & 100 & 10 & 1 & 0.1 & 1e-2 & 1e-3 & 1e-4 & 1e-8 & 0\\
+ \hline
+1 & 3.9634&4.3787 &4.987&36.949&42.394& 42.757 &42.79&42.793&42.793\\
+\hline
+0.5&      3.9931& 6.87&48.473 & 168.41  &207.34  & 209.63 & 209.83 & 209.85&  209.85\\
+\hline
+ 0.1&      16.09  &     159.56  &     1146.1   &    8304.1   &     19169  &      20270   &     20344   &     20352   &     20352\\
+ \hline
+0.05&      64.046  &     637.18  &     4686.2   &     38876 &  1.4e5 &  1.58e5 &   1.58e5 &  1.58e5 &  1.58e5\\
+\hline
+ 0.01&       1600    &   15921 & 1.2e5  & 1.1e6 & 8.3e6  & 1.8e7   & 1.93e7  & 1.93e7  & 1.93e7\\
+\end{tabular}
+\caption{The condition number of the matrix of the system (\ref{eq:simple_system}) for different values of $\nu$ and $h$. }
+\label{tab:cond_number}
+\end{table}
+
+For $\nu=0$ the computed matrices are not singular; perhaps the bilinear form $a(u,v)$ is coercive on the chosen discrete subspace of $(L_{2}(\Omega); H^{1}(\Omega)$ (?
+$\alpha(x)$ enters the discretized problem only through a computation of $\int\limits_{\tau}\alpha(x)\phi_{i}(x)\phi_{j}(x)dx$, and for coarse enough meshes the discretization probably won't 'see' $\alpha(0)=0$).
+
+At the next step we are numerically determining an optimal relation of $h$ to $\nu$. We fix $\nu$ and compute the error of the solution comparing it to the finest mesh.
+\begin{figure}
+
 \end{figure}

### 2014-08-11 make_convergence_test.m
fixed the function call in accordance with new 'compute_error.m'

@@ -12,15 +12,14 @@ result_pwe2=zeros(length(nu), length(h));
 
 for k=1:1:16
 	%compute the reference solution for nu(k)
-	[e1ref,e2ref]=solve_mH1(href,2.0,nu(k),1);
+	[e1ref,e2ref,M,xref]=solve_mH1(href,2.0,nu(k),1);
 	for l=1:1:20
 		%compute the solution for the current h(l)
 		[e1,e2,M,x,Kstiff, Mmass]=solve_mH1(h(l),2.0,nu(k),1);
 		%compute the reference solutions on the coarser mesh
-		e1rc=e1ref(1:(2^l):end);
-		e2rc=e2ref(1:(2^l):end);
+	
 		
-		[result_l2e1(k,l), result_h1e2(k,l), result_l2e2(k,l), result_pwe1(k,l), result_pwe2(k,l)]=compute_error(Kstiff, Mmass, e1, e2, e1rc, e2rc);
+		[result_l2e1(k,l), result_l2e2(k,l)]=compute_error( e1, e2, e1ef, e2ref, x, xref);
 	end
 end
 

### 2014-08-11 compute_error.m
correct computation of the L2-error provided the data on a coarser and a finer mesh

@@ -1,11 +1,49 @@
-function [err1, err2, err2l2, epw1, epw2]=compute_error(Kstiff, Mmass, e1, e2, e1c, e2c)
-err1p=e1-e1c;
-err1=sqrt(err1p'*Mmass*err1p);
-err2p=e2-e2c;
-err2=sqrt(err2p'*Mmass*err2p+err2p'*Kstiff*err2p);
+function [err1, err2]=compute_error(e1,e2,e1c,e2c,x,xc)
 
-err2l2=sqrt(err2p'*Mmass*err2p);
+err1=compute_L2_error(e1,e1c,x,xc);
+err2=compute_L2_error(e2,e2c,x,xc);
 
-epw1=norm(err1p);
-epw2=norm(err2p);
+end
+
+function [e1]=compute_L2_error(e, exact, x, xexact)
+
+
+
+fexact=@(t)bsxfun(@times, exact(1:1:end-1), ...
+	bsxfun(@times, bsxfun(@minus, xexact'(2:1:end), t), 1./(xexact'(2:1:end)-xexact'(1:1:end-1))));
+qexact=@(t)bsxfun(@times, exact(2:1:end), ...
+	bsxfun(@times, bsxfun(@minus, t, xexact'(1:1:end-1)), 1./(xexact'(2:1:end)-xexact'(1:1:end-1))));
+
+
+
+quad_pts_current=@(a,b,quad_pts)bsxfun(@plus,bsxfun(@minus,b,a)./2*quad_pts,bsxfun(@plus,b,a)./2);
+w_current=@(a,b,w)(b-a)./2*w;
+[quad_pts, w]=lgwt(5,-1,1);
+quad_pts=quad_pts';
+w=w';
+W=@(weights)w_current(xexact(1:1:end-1)',xexact(2:1:end)',weights);
+weight_matrix=W(w);
+
+Q=quad_pts_current(xexact(1:1:end-1)',xexact(2:1:end)',quad_pts);
+
+FQ=zeros(size(Q));
+c=1;
+%hold on
+
+for c=1:1:length(x)-1
+	P=(xexact>=x(c))&(xexact<x(c+1));
+	FQ(P,:)=e(c+1)*(Q(P,:)-x(c))./(x(c+1)-x(c))+e(c)*(x(c+1)-Q(P,:))./(x(c+1)-x(c));
+end
+
+
+
+
[…]

### 2014-08-12 time_dependant_pb.py
time dep pb

@@ -12,7 +12,7 @@ import copy
 
 #---------------CONSTANTS--------------------#
 # mesh size
-N      = 500
+N      = 1024
 # domain ]-L ; H[, (mL=-L)
 mL     = -1
 H      =  10
@@ -33,20 +33,10 @@ B0     = 0                      #given
 c      = 1#3e8 
 
 
-#gamma/beta/nudelta
-#gamma  = -e*dt / (me*c*c*eps0)
 
-#beta   = -abs(e)*B0*dt/(c*me)
-#nud    = nu*dt/c
-#print 'gamma',gamma
-#print 'beta',beta
-#print 'nudelta', nud
 #alpha(-L)
 alphamL = 2
 
-#coeff alpha (1/alpha_Ey)Ey in left BC
-alphaey = complex(0,alphamL)/2 - 1/dx
-print 'alphaey', alphaey
 #-------------airy functions------------------#
 #return A
 #def airy_one(x):
@@ -86,26 +76,19 @@ gamma = np.sqrt(omega*omega-wp*wp)
 alpha = 2
 
 def g(t) : 
-    return np.exp(complex(0,omega*t))*np.exp(-gamma*mL)*(-gamma+complex(0,alphamL));
-#(1/dt)*np.exp(complex(0,omega*t)-gamma*mL)*(1-np.exp(-gamma*dx))+complex(0,alphamL)*np.exp(-gamma*mL+complex(0,omega*t)) 
-#(airy_two(mL)+complex(0,alphamL)*airy_one(mL))*np.exp(complex(0,t))*eps0*c
+    return np.exp(complex(0,omega*t))*np.exp(-gamma*mL)*(-gamma+complex(0,alphamL))
 #-----------------------------------------------#
 #------table and functions initialisation-------#
 #-----------------------------------------------#
 X    = map(lambda i: mL + i*dx, range(N+1))
-NE    = map(lambda x: 3*me/(e*e),  X)
+NE   = map(lambda x: 3*me/(e*e),  X)
 X12  = map(lambda i: mL+0.5*dx + i*dx, range(N))
-#Ex   = map(lambda x: np.exp(complex(0,k*x)),X)
+NEy  = map(lambda x: 3*me/(e*e),  X12)
 Ex   = map(lambda x: 0, X)
-#ux   = map(lambda x: np.exp(complex(0,k*x)),X)
[…]

### 2014-08-12 time_dependant_pb_v2.py
uncommented a line where $Ey$ depends on $uy$

@@ -12,7 +12,7 @@ import copy
 
 #---------------CONSTANTS--------------------#
 # mesh size
-N      = 500
+N      = 1024
 # domain ]-L ; H[, (mL=-L)
 mL     = -1
 H      =  10
@@ -33,20 +33,10 @@ B0     = 0                      #given
 c      = 1#3e8 
 
 
-#gamma/beta/nudelta
-#gamma  = -e*dt / (me*c*c*eps0)
 
-#beta   = -abs(e)*B0*dt/(c*me)
-#nud    = nu*dt/c
-#print 'gamma',gamma
-#print 'beta',beta
-#print 'nudelta', nud
 #alpha(-L)
 alphamL = 2
 
-#coeff alpha (1/alpha_Ey)Ey in left BC
-alphaey = complex(0,alphamL)/2 - 1/dx
-print 'alphaey', alphaey
 #-------------airy functions------------------#
 #return A
 #def airy_one(x):
@@ -87,25 +77,18 @@ alpha = 2
 
 def g(t) : 
     return np.exp(complex(0,omega*t))*np.exp(-gamma*mL)*(-gamma+complex(0,alphamL))
-#(1/dt)*np.exp(complex(0,omega*t)-gamma*mL)*(1-np.exp(-gamma*dx))+complex(0,alphamL)*np.exp(-gamma*mL+complex(0,omega*t)) 
-#(airy_two(mL)+complex(0,alphamL)*airy_one(mL))*np.exp(complex(0,t))*eps0*c
 #-----------------------------------------------#
 #------table and functions initialisation-------#
 #-----------------------------------------------#
 X    = map(lambda i: mL + i*dx, range(N+1))
-NE    = map(lambda x: 3*me/(e*e),  X)
+NE   = map(lambda x: 3*me/(e*e),  X)
 X12  = map(lambda i: mL+0.5*dx + i*dx, range(N))
-#Ex   = map(lambda x: np.exp(complex(0,k*x)),X)
+NEy  = map(lambda x: 3*me/(e*e),  X12)
 Ex   = map(lambda x: 0, X)
-#ux   = map(lambda x: np.exp(complex(0,k*x)),X)
 ux   = map(lambda x: 0, X)
-#H    = map(lambda x: np.exp(complex(0,k*x)),X)
[…]

### 2014-08-13 time_dependant_pb_v2.py
fixed some mistakes

@@ -67,9 +67,9 @@ def Ne(x) :
     return  - a1 /(2*a2)
 
 #NE    = map(lambda x: 3*me/(e*e),  X)
-omega = np.sqrt(7)
-wp = np.sqrt(3)
-gamma = np.sqrt(omega*omega-wp*wp)
+omega = np.sqrt(3)
+wp = np.sqrt(7)
+gamma = np.sqrt(-omega*omega+wp*wp)
 #---------------------------------------------------------#
 
 #--------------G for left BC -------------------#
@@ -81,7 +81,8 @@ def g(t) :
 #------table and functions initialisation-------#
 #-----------------------------------------------#
 X    = map(lambda i: mL + i*dx, range(N+1))
-NE   = map(lambda x: 3*me/(e*e),  X)
+NE   = map(lambda x: (wp**2)*me/(e*e),  X)
+scipy.io.savemat('NE.mat', {'NE':NE});
 X12  = map(lambda i: mL+0.5*dx + i*dx, range(N))
 NEy  = map(lambda x: 3*me/(e*e),  X12)
 Ex   = map(lambda x: 0, X)
@@ -122,7 +123,7 @@ t = 1
 #coeff alpha (1/alpha_Ey)Ey in left BC
 alphaey = complex(0,alphamL)/2 - 1/dx
 print 'alphaey', alphaey
-Ntime=10;
+Ntime=1;
 while (t<=Ntime):
     print "iter : ",t,"time : ", t*dt
 
@@ -153,9 +154,10 @@ while (t<=Ntime):
 
 
     #-------------------- u y->tuy
-
     for i in range(N):
         [K1,K2,K1x,K2x] = Kcoeff(NE[i])
+        print K1
+        print K2
         tuy[i] = (1/K1) * (K2 * uy[i] -dt * e / me * Ey[i] +dt*dt*e/(2*me) * (H12[i+1] - H12[i])/dx)
 
     #------------------- E -> tE
@@ -163,8 +165,8 @@ while (t<=Ntime):
 
     for i in range(N):
        # tEx[i] = Ex[i] + e*NE[i]*dt* (tux[i] + ux[i])/2
-
-        tEy[i] = Ey[i] - (dt) * (H12[i+1] - H12[i])/dx +(dt*e*NEy[i]/(2*me))*(tuy[i] + uy[i])
[…]

### 2014-08-13 time_dependant_pb.py
BC

@@ -12,7 +12,7 @@ import copy
 
 #---------------CONSTANTS--------------------#
 # mesh size
-N      = 1024
+N      = 124
 # domain ]-L ; H[, (mL=-L)
 mL     = -1
 H      =  10
@@ -23,7 +23,7 @@ print "dx", dx
 dt     = 0.5*dx
 print "dt",dt
 # Number of time steps
-Ntime = 50
+Ntime = 1
 # constants 
 me     = 1#9.11e-31               #electron mass (kg)
 e      = 1#1.6e-19               #electron charge (coulombs)
@@ -69,7 +69,7 @@ def Ne(x) :
 #NE    = map(lambda x: 3*me/(e*e),  X)
 omega = np.sqrt(7)
 wp = np.sqrt(3)
-gamma = np.sqrt(omega*omega-wp*wp)
+gamma = 2
 #---------------------------------------------------------#
 
 #--------------G for left BC -------------------#
@@ -112,6 +112,8 @@ def Kcoeff(x):
     K1x = 0
     K2x = 0
     return [K1,K2,K1x,K2x]
+[K1,K2,K1x,K2x] = Kcoeff(3*me/(e*e))
+
 #-----------------------------------------------------------#
 #------------------------time loop--------------------------#
 #-----------------------------------------------------------#
@@ -127,10 +129,12 @@ while (t<=Ntime):
     print "iter : ",t,"time : ", t*dt
 
     #---------------- H -> H12
-    H12[0] = H[0] -  dt/dx * (Ey[0] \
-                                    - (1/alphaey) * (g((t-1)*dt) -  complex(0,alphamL)/2 * Ey[0] \
-                                                         - (1/dx)* Ey[0]))
+    H12[0] = H[0] -  dt/dx* (Ey[0] - 1/alphaey * (Ey[0] *(- 1/dx - complex(0,alphamL)/2)+g((t-1)*dt)))
+    time = t*dt
+    Hex    = map(lambda x: (gamma/complex(0,omega))*np.exp(-gamma*x)*np.exp(complex(0,omega*(time+dt/2))) ,X)
+    print H12[0] - Hex[0]
 
+    
     i = 1
     while (i<N):
         H12[i] = H[i] - dt/dx*(Ey[i] - Ey[i-1])
[…]

### 2014-08-13 time_dependant_pb.py
Ey, H, uy coupling working. TODO: add Ex, ux

@@ -12,7 +12,7 @@ import copy
 
 #---------------CONSTANTS--------------------#
 # mesh size
-N      = 124
+N      = 500
 # domain ]-L ; H[, (mL=-L)
 mL     = -1
 H      =  10
@@ -23,12 +23,12 @@ print "dx", dx
 dt     = 0.5*dx
 print "dt",dt
 # Number of time steps
-Ntime = 1
+Ntime = 100
 # constants 
 me     = 1#9.11e-31               #electron mass (kg)
 e      = 1#1.6e-19               #electron charge (coulombs)
 eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 0                     #friction
+nu     = 0                   #friction
 B0     = 0                      #given
 c      = 1#3e8 
 
@@ -67,13 +67,13 @@ def Ne(x) :
     return  - a1 /(2*a2)
 
 #NE    = map(lambda x: 3*me/(e*e),  X)
-omega = np.sqrt(7)
-wp = np.sqrt(3)
+omega = np.sqrt(3)
+wp = np.sqrt(7)
 gamma = 2
 #---------------------------------------------------------#
 
 #--------------G for left BC -------------------#
-alpha = 2
+alpha = 1
 
 def g(t) : 
     return np.exp(complex(0,omega*t))*np.exp(-gamma*mL)*(-gamma+complex(0,alphamL))
@@ -81,9 +81,9 @@ def g(t) :
 #------table and functions initialisation-------#
 #-----------------------------------------------#
 X    = map(lambda i: mL + i*dx, range(N+1))
-NE   = map(lambda x: 3*me/(e*e),  X)
+NE   = map(lambda x: wp**2*me/(e*e),  X)
 X12  = map(lambda i: mL+0.5*dx + i*dx, range(N))
-NEy  = map(lambda x: 3*me/(e*e),  X12)
+NEy  = map(lambda x: wp**2*me/(e*e),  X12)
 Ex   = map(lambda x: 0, X)
 ux   = map(lambda x: 0, X)
 H    = map(lambda x: (gamma/complex(0,omega))*np.exp(-gamma*x)*np.exp(complex(0,-omega*dt/2)), X)
@@ -112,7 +112,7 @@ def Kcoeff(x):
     K1x = 0
     K2x = 0
[…]

### 2014-08-13 compute_error.m
correct, but slow computation of the error

@@ -1,7 +1,9 @@
 function [err1, err2]=compute_error(e1,e2,e1c,e2c,x,xc)
-
+tic;
 err1=compute_L2_error(e1,e1c,x,xc);
 err2=compute_L2_error(e2,e2c,x,xc);
+t=toc();
+display (strcat(num2str(t)," for the computation of the total error"));
 
 end
 

### 2014-08-13 time_dependant_pb_v2.py
Ey/H/uy coupling is ok, TODO: Ex, ux

@@ -12,7 +12,7 @@ import copy
 
 #---------------CONSTANTS--------------------#
 # mesh size
-N      = 1024
+N      = 500
 # domain ]-L ; H[, (mL=-L)
 mL     = -1
 H      =  10
@@ -23,12 +23,12 @@ print "dx", dx
 dt     = 0.5*dx
 print "dt",dt
 # Number of time steps
-Ntime = 50
+Ntime = 100
 # constants 
 me     = 1#9.11e-31               #electron mass (kg)
 e      = 1#1.6e-19               #electron charge (coulombs)
 eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 0                     #friction
+nu     = 0                   #friction
 B0     = 0                      #given
 c      = 1#3e8 
 
@@ -69,11 +69,11 @@ def Ne(x) :
 #NE    = map(lambda x: 3*me/(e*e),  X)
 omega = np.sqrt(3)
 wp = np.sqrt(7)
-gamma = np.sqrt(-omega*omega+wp*wp)
+gamma = 2
 #---------------------------------------------------------#
 
 #--------------G for left BC -------------------#
-alpha = 2
+alpha = 1
 
 def g(t) : 
     return np.exp(complex(0,omega*t))*np.exp(-gamma*mL)*(-gamma+complex(0,alphamL))
@@ -81,10 +81,9 @@ def g(t) :
 #------table and functions initialisation-------#
 #-----------------------------------------------#
 X    = map(lambda i: mL + i*dx, range(N+1))
-NE   = map(lambda x: (wp**2)*me/(e*e),  X)
-scipy.io.savemat('NE.mat', {'NE':NE});
+NE   = map(lambda x: wp**2*me/(e*e),  X)
 X12  = map(lambda i: mL+0.5*dx + i*dx, range(N))
-NEy  = map(lambda x: 3*me/(e*e),  X12)
+NEy  = map(lambda x: wp**2*me/(e*e),  X12)
 Ex   = map(lambda x: 0, X)
 ux   = map(lambda x: 0, X)
 H    = map(lambda x: (gamma/complex(0,omega))*np.exp(-gamma*x)*np.exp(complex(0,-omega*dt/2)), X)
@@ -113,25 +112,28 @@ def Kcoeff(x):
     K1x = 0
     K2x = 0
     return [K1,K2,K1x,K2x]
+
+
[…]

### 2014-08-14 time_dependant_pb.py
the last version: commit just to make sure it's the last one we have

@@ -159,7 +159,7 @@ while (t<=Ntime):
     #-------------------- u y->tuy
 
     for i in range(N):
-        [K1,K2,K1x,K2x] = Kcoeff(NEy[i])
+        [K1,K2,K1x,K2x] = Kcoeff(NEy[i]);
         tuy[i] = (1/K1) * (K2 * uy[i] -dt * e / me * Ey[i] +dt*dt*e/(2*me) * (H12[i+1] - H12[i])/dx)
        # tuy[i] = -e/(me*complex(0,omega))*np.exp(complex(0,omega*time)-gamma*X12[i])
     #------------------- E -> tE

### 2014-08-14 test.py
test.py ex/ux

@@ -1,0 +1,116 @@
+#!/usr/bin/python
+# -*- coding: utf-8 -*-
+
+from __future__ import division
+import os
+from time import time
+import numpy as np
+from pylab import *
+import scipy.io
+from scipy.special import airy
+import copy
+
+#---------------CONSTANTS--------------------#
+# mesh size
+N      = 1000
+# domain ]-L ; H[, (mL=-L)
+mL     = -1
+H      =  10
+# space step 
+dx     = (H-mL)/N
+print "dx", dx
+# time step
+dt     = 0.5*dx
+print "dt",dt
+# Number of time steps
+Ntime = 1
+# constants 
+me     = 1#9.11e-31               #electron mass (kg)
+e      = 1#1.6e-19               #electron charge (coulombs)
+eps0   = 1#8.85e-12               #permeability  (F/m)
+nu     = 0                     #friction
+B0     = 0                      #given
+c      = 1#3e8 
+
+
+
+#alpha(-L)
+alphamL = 2
+
+# Ne constants definition
+wc    = e*abs(B0)/me
+print "omega_c" ,wc
+
+omega = np.sqrt(7)
+wp = np.sqrt(3)
+gamma = 2
+#--------------G for left BC -------------------#
+def g(t) :
+    return (-gamma + complex(0,alphamL))*np.exp(complex(-gamma*mL,omega*t))
+
+#-----------------------------------------------#
+#------table and functions initialisation-------#
+#-----------------------------------------------#
+X    = map(lambda i: mL + i*dx, range(N+1))
+NE   = map(lambda x: omega*omega*me,  X)
+X12  = map(lambda i: mL+0.5*dx + i*dx, range(N))
+NEy  = map(lambda x: omega*omega*me,  X12)
+Ex   = map(lambda x: np.exp(-gamma*x), X)
+ux   = map(lambda x: -(e/me)*(1/(complex(0,alphamL)))*x, Ex)
+H    = map(lambda x: 0,X)#(gamma/complex(0,omega))*np.exp(-gamma*x), X)
+Ey   = map(lambda x: 0,X12)#np.exp(-gamma*x),X12)
+uy   = map(lambda x: 0,X12)#-(e/me)*(1/complex(0,omega))*np.exp(-gamma*x), X12)
+
[…]

### 2014-08-17 code_validity.tex
added the plots of the convergence of the L2-error for the case of resonance

@@
 \begin{subsection}{Discretization}
-Idea:
-
 Clearly, $u$ solves the well-posed problem 
@@
 \end{align*}
-For us it may be sufficient to check that the first equation is uniquely solvable in the sense of distributions (and if $\delta, \alpha$ are positive, we can probably even bound the norm of the solution), and thus the second equation is uniquely solvable as well (because it will be the bilinear form for the Helmholtz equation, see the thesis of Lise-Marie).
 
@@
 \boldsymbol{e}_{1}=\left(e_{11},\ldots,e_{1 N_{1}}\right)^{T},\; \boldsymbol{e}_{2}=\left(e_{21},\ldots,e_{2 N_{1}}\right)^{T},\\
-\boldsymbol{0}_{n} \text{ is an $n$-dimensional column vector with all zeros}.
+\boldsymbol{0}_{n} \text{ is an $n$-dimensional zero column vector}.
 \end{align*}
@@
 \begin{align*}
-\|E_{1}-E_{1}^{c}\|_{L_{2}(\Omega)}=\left(\int\limits_{\Omega}\left|E_{1}-\sum\limits_{k=0}^{N}E_{1i}\phi_{i}\right|^2dx\right),
+\|E_{1}-E_{1}^{c}\|_{L_{2}(\Omega)}=\left(\int\limits_{\Omega}\left|E_{1}(x)-\sum\limits_{k=0}^{N}E_{1i}\phi_{i}\right|^2dx\right),
 \end{align*}
-where $\left(\phi_{i}\right)$ are $P_{1}$-finite elements. Similarly $\|E_{2}-E_{2}^{c}\|_{L_{2}(\Omega)}$ and $\|E_{2}-E_{2}^{c}\|_{H_{1}(\Omega)}$ are defined.
+where $\left(\phi_{i}\right)_{i=1}^{N}$ are $P_{1}$-finite elements and $E_{1}(x)$ is a known analytic solution.
+Similarly $\|E_{2}-E_{2}^{c}\|_{L_{2}(\Omega)}$ and $\|E_{2}-E_{2}^{c}\|_{H_{1}(\Omega)}$ are defined.
 
@@
 ]
-    \addplot[mark=*,blue] table {E1L2.dat}; 
+    \addplot[mark=*,blue] table {pics/E1L2.dat}; 
     \addlegendentry{$\|E_{1}-E_{1}^{c}\|_{L_{2}}$};
-    \addplot[mark=*,red] table {E2H1.dat};
+    \addplot[mark=*,red] table {pics/E2H1.dat};
         \addlegendentry{$\|E_{2}-E_{2}^{c}\|_{H_{1}}$};
 
-          \addplot[mark=*,cyan] table {E2L2.dat};
+          \addplot[mark=*,cyan] table {pics/E2L2.dat};
         \addlegendentry{$\|E_{2}-E_{2}^{c}\|_{L_{2}}$};  
-        \addplot[dotted] table{E_h2.dat};
+        \addplot[dotted] table{pics/E_h2.dat};
          \addlegendentry{$O(h^2)$};
-         \addplot[dashed] table{H.dat};
+         \addplot[dashed] table{pics/H.dat};
          \addlegendentry{$O(h)$};
@@
 
-Note that in the last 3 experiments the accuracy of the solution of the system of equations, namely $\|Ae-r\|$ (where $e$ is the solution vector, $r$ is the right hand side and $A$ us the matrix) exceeded 1.6e-9 (namely, it was 1.6e-9 ($h=3.2e-5$), 1.3e-08 ($h=8e-6$), 1.04e-07 ($h=2e-6$))
+Note that in the last 3 experiments the error of the solution of the system of equations, namely $\|Ae-r\|$ (where $e$ is the solution vector, $r$ is the right hand side and $A$ is the block matrix (\ref{eq:simple_system}) ) exceeded 1.6e-9 (namely, it was 1.6e-9 ($h=3.2e-5$), 1.3e-08 ($h=8e-6$), 1.04e-07 ($h=2e-6$))
 
-The next experiment we perform for the case of the resonance. $L=-2$, $H=10$, the parameters are like in the thesis of LMIG, and the boundary condition (\ref{eq:bcs}) with $g^{inc}=2, \lambda=2.0$.
+The next experiment we perform for the case of the resonance. The parameters for the problem are given in Table \ref{tab:parameters}.
+\begin{table}
+\begin{tabular}{lr}
+$\alpha(x)$ & $\left\{\begin{array}{cc}
+10, & x\leq -10,\\
+-x, & -10<x\leq 5,\\
+-5, & x>5.
+\end{array}\right.$ \\
+$\delta(x)$ & 
+$\left\{\begin{array}{cc}
+0, & x\leq -10,\\
+4/30x+4/3,& -10<x\leq 5,\\
+2, & x>5.
+\end{array}\right.$ \\
+$g^{inc}(-L)$ & $-2 \sqrt{2}i\exp(-22\sqrt{2}i)$\\
+$\lambda$ & 
+$\sqrt{10}$\\
+$L$& 15\\
+$H$ & 10 \\
+\end{tabular}
+\caption{The parameters for the problem with the resonance}
+\label{tab:parameters}
+\end{table}
 
@@
 
-At the next step we are numerically determining an optimal relation of $h$ to $\nu$. We fix $\nu$ and compute the error of the solution comparing it to the finest mesh.
+At the next step we are numerically determining an optimal relation of $h$ to $\nu$.
+We fix $\nu$ and compute the error of the solution compared to the solution computed on the finest mesh  (with $h=2e-6$).
+The results are depicted in Figures \ref{fig:l2_err_e1} and \ref{fig:l2_err_e2}.
+
 \begin{figure}
+\begin{tikzpicture}
+    \begin{loglogaxis}[
+    	width=0.7\textwidth,
+        xlabel=$h$,
+        ylabel=$Error$,
+        legend style={
+at={(0.2,1.5)},
+legend pos= south east,
+anchor=south east, 
+draw=none
+}
+]
+\addplot[mark=*,blue] table {pics/result_l2e1.1.dat}; 
+\addlegendentry{$\nu=1$};
+\addplot[mark=*,green] table {pics/result_l2e1.0.25.dat}; 
+\addlegendentry{$\nu=2^{-2}$};
+\addplot[mark=*,red] table {pics/result_l2e1.0.0625.dat}; 
+\addlegendentry{$\nu=2^{-4}$};
+\addplot[mark=square,blue] table {pics/result_l2e1.0.015625.dat}; 
+\addlegendentry{$\nu=2^{-6}$};
+\addplot[mark=square,green] table {pics/result_l2e1.0.0039062.dat}; 
+\addlegendentry{$\nu=2^{-8}$};
+\addplot[mark=square,red] table {pics/result_l2e1.0.0039062.dat}; 
+\addlegendentry{$\nu=2^{-10}$};
+\addplot[mark=triangle,blue] table {pics/result_l2e1.0.00097656.dat}; 
+\addlegendentry{$\nu=2^{-12}$};
+\addplot[mark=triangle,green] table {pics/result_l2e1.0.00024414.dat}; 
+\addlegendentry{$\nu=2^{-12}$};
+\addplot[mark=triangle, red] table {pics/result_l2e1.6.1035e-05.dat};
+\addlegendentry{$\nu=2^{-14}$};
+\addplot[mark=*, violet] table{pics/result_l2e1.1.5259e-05.dat};
+\addlegendentry{$\nu=2^{-16}$};
+\end{loglogaxis}
+\end{tikzpicture} 
+\caption{The $L_{2}$-error of $E_{1}(x)$}
+\label{fig:l2_err_e1}
+\end{figure}
 
+\begin{figure}
+\begin{tikzpicture}
+    \begin{loglogaxis}[
+    	width=0.7\textwidth,
+        xlabel=$h$,
+        ylabel=$Error$,
+        legend style={
+at={(0.2,1.5)},
+legend pos= south east,
+anchor=south east, 
+draw=none
+}
+]
+\addplot[mark=*,blue] table {pics/result_l2e2.1.dat}; 
+\addlegendentry{$\nu=1$};
+\addplot[mark=*,green] table {pics/result_l2e2.0.25.dat}; 
+\addlegendentry{$\nu=2^{-2}$};
+\addplot[mark=*,red] table {pics/result_l2e2.0.0625.dat}; 
+\addlegendentry{$\nu=2^{-4}$};
+\addplot[mark=square,blue] table {pics/result_l2e2.0.015625.dat}; 
+\addlegendentry{$\nu=2^{-6}$};
+\addplot[mark=square,green] table {pics/result_l2e2.0.0039062.dat}; 
+\addlegendentry{$\nu=2^{-8}$};
+\addplot[mark=square,red] table {pics/result_l2e2.0.0039062.dat}; 
+\addlegendentry{$\nu=2^{-10}$};
+\addplot[mark=triangle,blue] table {pics/result_l2e2.0.00097656.dat}; 
+\addlegendentry{$\nu=2^{-12}$};
+\addplot[mark=triangle,green] table {pics/result_l2e2.0.00024414.dat}; 
+\addlegendentry{$\nu=2^{-12}$};
+\addplot[mark=triangle, red] table{pics/result_l2e2.6.1035e-05.dat};
+\addlegendentry{$\nu=2^{-14}$};
+\addplot[mark=*, violet] table{pics/result_l2e2.1.5259e-05.dat};
+\addlegendentry{$\nu=2^{-16}$};
+\end{loglogaxis}
+\end{tikzpicture} 
+\caption{The $L_{2}$-error of $E_{2}(x)$}
+\label{fig:l2_err_e2}
+\end{figure}
+
+Let us denote by $E_{1}^{h}$ the solution $E_{1}(x)$ computed on the mesh with a width $h$, and by $E_{1}^{c}$ the solution computed on the finest mesh. We introduce 
+\begin{align}
+\label{eq:def_epsilon}
+h_{\epsilon}=\sup\{h: \|E_{1}^{h'}-E_{1}^{c}\|<\epsilon \text{ for all } h'<h\}.
+\end{align}
+The computed dependence of $h_{\epsilon}$ on $\nu$ is shown in Figure \ref{}.
+\begin{figure}
+\begin{tikzpicture}
+    \begin{loglogaxis}[
+    	width=0.7\textwidth,
+        xlabel=$\nu$,
+        ylabel=$h_{\epsilon}$,
+        legend style={
+at={(0.2,1.5)},
+legend pos= south east,
+anchor=south east, 
+draw=none
+}
+]
+\addplot[mark=*,blue] table {pics/h1e-1.dat}; 
+\addlegendentry{$\epsilon=1e-1$};
+\addplot[mark=o,red] table {pics/h1e-2.dat}; 
+\addlegendentry{$\epsilon=1e-2$};
+\addplot[mark=triangle,green] table {pics/h1e-3.dat}; 
+\addlegendentry{$\epsilon=1e-3$};
+\addplot[mark=square,cyan] table {pics/h1e-4.dat}; 
+\addlegendentry{$\epsilon=1e-4$};
+\addplot[dashed, red] table {pics/nu1.dat}; 
+\addlegendentry{$O(\nu)$};
+\addplot[dashed, blue] table {pics/nu32.dat}; 
+\addlegendentry{$O(\nu^{\frac{3}{2}})$};
+\end{loglogaxis}
+\end{tikzpicture} 
+\caption{The dependence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$.}
 \end{figure}

### 2014-08-17 compute_error.m

@@ -37,7 +37,7 @@ for c=1:1:length(x)-1
 	FQ(P,:)=e(c+1)*(Q(P,:)-x(c))./(x(c+1)-x(c))+e(c)*(x(c+1)-Q(P,:))./(x(c+1)-x(c));
 end
 
-
+save('FQ2.mat', 'FQ');
 
 
 F=bsxfun(@times, weight_matrix, (abs(FQ-fexact(Q)-qexact(Q))).^2);

### 2014-08-17 functions_test/Ksubdiag_x_upper.m

@@ -4,8 +4,6 @@ hi=xi_r-xi_l;
 
 if abs(alpha-xi_l)<=1e-13
  val=0;
-else if abs(alpha-xi_r)<=1e-13
- val=hi^2/12+xi_l*hi/6;
 else
  p=(alpha-xi_l)/hi;
  val=hi^2*(p^3/3-p^4/4)+hi*xi_l*(p^2/2-p^3/3);

### 2014-08-17 make_convergence_test.m

@@ -1,8 +1,8 @@
 h0=1.0;
-k=0:1:15
+k=0:2:16
 nu=2.^(-k);
-href=1e-6;
-l=1:1:20;
+href=2e-6;
+l=1:2:21;
 h=href*2.^l;
 result_l2e1=zeros(length(nu), length(h));
 result_l2e2=zeros(length(nu), length(h));
@@ -10,17 +10,25 @@ result_h1e2=zeros(length(nu), length(h));
 result_pwe1=zeros(length(nu), length(h));
 result_pwe2=zeros(length(nu), length(h));
 
-for k=1:1:16
+for k=1:1:length(nu)
 	%compute the reference solution for nu(k)
-	[e1ref,e2ref,M,xref]=solve_mH1(href,2.0,nu(k),1);
-	for l=1:1:20
+	[e1ref,e2ref,M,xref]=solve_mH1(href,sqrt(10.0),nu(k),1);
+	fname=strcat('e1.', num2str(2e-6), '.', num2str(nu(k)), '.mat');
+                save(fname, 'e1ref');
+  	fname=strcat('e2.', num2str(2e-6), '.', num2str(nu(k)), '.mat');
+                save(fname, 'e2ref');
+	for l=1:1:length(h)
 		%compute the solution for the current h(l)
-		[e1,e2,M,x,Kstiff, Mmass]=solve_mH1(h(l),2.0,nu(k),1);
+		[e1,e2,M,x,Kstiff, Mmass]=solve_mH1(h(l),sqrt(10.0),nu(k),1);
 		%compute the reference solutions on the coarser mesh
-	
+                fname=strcat('e1.', num2str(h(l)), '.', num2str(nu(k)), '.mat');
+		save(fname, 'e1');
+	        fname=strcat('e2.', num2str(h(l)), '.', num2str(nu(k)), '.mat');                save(fname, 'e2');
 		
-		[result_l2e1(k,l), result_l2e2(k,l)]=compute_error( e1, e2, e1ef, e2ref, x, xref);
+	%	[result_l2e1(k,l), result_l2e2(k,l)]=compute_error( e1, e2, e1ref, e2ref, x, xref);
 	end
+	save('result_l2e1.mat', 'result_l2e1');
+	save('result_l2e2.mat', 'result_l2e2');
 end
 
 save('result_l2e1.mat', 'result_l2e1');

### 2014-08-17 make_convergence_test_exact.m

@@ -1,6 +1,5 @@
 function [e1l2, e2l2, e2h1]=make_convergence_test_exact
-p=0:1:7;
-h=10.^(-7+p);
+h=2e-6*2.^[0:2:20];
 e1l2=zeros(length(h),1 );
 e2l2=zeros(length(h),1 );
 e2h1=zeros(length(h),1 );
@@ -8,9 +7,9 @@ e2h1=zeros(length(h),1 );
 f=@(x)airy(x);
 g=@(x)airy(1,x);
 ex=@(x)airy(x).*(-1i).*sqrt(x.^2+1).*sqrt(x.^2+1+x)./(x.^2+1);
-for k=1:1:8
- [e1, e2,M,x, Kstiff, Mmass]=solve_mH1_airy(h(k),2, 0,1);
- [e1l2(k), e2l2(k), e2h1(k)]=compute_error_exact(e1,e2,x,ex,f,g);
+for k=1:1:length(h)
+ [e1, e2,M,x, Kstiff, Mmass]=solve_mH1_airy(h(end-k+1),2, 0,1);
+ [e1l2(end-k+1), e2l2(end-k+1), e2h1(end-k+1)]=compute_error_exact(e1,e2,x,ex,f,g);
 end
 save('e1l2.mat', 'e1l2');
 save('e2l2.mat', 'e2l2');

### 2014-08-17 solve_mH1.m

@@ -1,6 +1,6 @@
-function [e1, e2,M,x]=solve_mH1(dx,lambda, nu, uniform)
+function [e1, e2,M,x, Kstiff, Mmass]=solve_mH1(dx,lambda, nu, uniform)
 %mesh generation
-L=2;
+L=15;
 H=10;
 if uniform
 x=-L:dx:H;
@@ -18,18 +18,21 @@ r=construct_rhs(x);
 
 tic
 [M,rhs]=permute(A,B,D,r);
-save('M.mat', 'M');
+%save('M.mat', 'M');
 sol=M\rhs;
-size(sol)
 
+norm(M*sol-rhs)
 
 [e1, e2]=permute_solution_back(sol);
 
 time_passed=toc();
 display(strcat(num2str(time_passed)," for the solution of the system of eqs"));
 
-
-
+%auxiliary matrices, namely the mass matrix and the stiffness matrix
+Kst=K_lpl(x);
+Mm=mass_matrixP1(x);
+Kstiff=spdiags([Kst(:,2) Kst(:,1) circshift(Kst(:,2),1)], -1:1, length(Kst), length(Kst));
+Mmass=spdiags([Mm(:,2) Mm(:,1) circshift(Mm(:,2),1)], -1:1, length(Mm), length(Mm));
 end
 
 
@@ -74,24 +77,21 @@ end
 function a=alpha(x)
 
 a=zeros(size(x));
-a(x<=-1)=1;
-P=(x<=3)&(x>-1);
+a(x<=-10)=10;
+P=(x<=5)&(x>-10);
 a(P)=-x(P);
-a(x>3)=-3;
-%a=-x;
-
-%a=x.^2+1;
-
+a(x>5)=-5;
 end
 
 function delta=delta(x)
 
 
 delta=zeros(size(x));
-delta(x<=-1)=0;
-P=(x<=3)&(x>-1);
-delta(P)=0.5*(x(P)+1);
-delta(x>3)=2;
+delta(x<=-10)=0;
+P=(x<=5)&(x>-10);
+delta(P)=4/30*x(P)+4/3;
+delta(x>5)=2;
+%delta=sqrt(x.^2+1).*sqrt(x.^2+1+x);
 
 end
 
@@ -155,7 +155,7 @@ function M=mass_matrixP1P1_scaled(x, func_kernel, nq)
 
 
 %nq is a number of quadrature points
-    if(~nargin<3)
+    if(nargin<3)
         nq=2;
     end
 
[…]

### 2014-08-17 test.py
(Ex/Ux working)

@@ -28,7 +28,7 @@ Ntime = 1
 me     = 1#9.11e-31               #electron mass (kg)
 e      = 1#1.6e-19               #electron charge (coulombs)
 eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 0                     #friction
+nu     = 0                    #friction
 B0     = 0                      #given
 c      = 1#3e8 
 
@@ -41,8 +41,8 @@ alphamL = 2
 wc    = e*abs(B0)/me
 print "omega_c" ,wc
 
-omega = np.sqrt(7)
-wp = np.sqrt(3)
+wp = np.sqrt(3);
+omega=wp;
 gamma = 2
 #--------------G for left BC -------------------#
 def g(t) :
@@ -52,11 +52,11 @@ def g(t) :
 #------table and functions initialisation-------#
 #-----------------------------------------------#
 X    = map(lambda i: mL + i*dx, range(N+1))
-NE   = map(lambda x: omega*omega*me,  X)
+NE   = map(lambda x: wp**2*me/(e**2),  X)
 X12  = map(lambda i: mL+0.5*dx + i*dx, range(N))
-NEy  = map(lambda x: omega*omega*me,  X12)
+NEy  = map(lambda x: wp**2*me/(e**2),  X12)
 Ex   = map(lambda x: np.exp(-gamma*x), X)
-ux   = map(lambda x: -(e/me)*(1/(complex(0,alphamL)))*x, Ex)
+ux   = map(lambda x: -(e/me)*(1/(complex(0,omega)))*x, Ex)
 H    = map(lambda x: 0,X)#(gamma/complex(0,omega))*np.exp(-gamma*x), X)
 Ey   = map(lambda x: 0,X12)#np.exp(-gamma*x),X12)
 uy   = map(lambda x: 0,X12)#-(e/me)*(1/complex(0,omega))*np.exp(-gamma*x), X12)
@@ -74,19 +74,19 @@ scipy.io.savemat('H120.mat', {'H120':H12})
 def Kcoeff(x): 
     #K1     =  1 + nu * dt/2 + dt*dt*x*e*e/(4*me)
     #K2     =  1 - nu * dt/2 - dt*dt*x*e*e/(4*me)
-    K1x =  1 + dt*dt*x*e*e/(4*me)
[…]

### 2014-08-19 time_dependant_pb.py
coupling x/y

@@ -23,13 +23,13 @@ print "dx", dx
 dt     = 0.5*dx
 print "dt",dt
 # Number of time steps
-Ntime = 100
+Ntime = 10
 # constants 
 me     = 1#9.11e-31               #electron mass (kg)
-e      = 1#1.6e-19               #electron charge (coulombs)
+e      = -1#1.6e-19               #electron charge (coulombs)
 eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 0                   #friction
-B0     = 0                      #given
+nu     = 1                        #friction
+B0     = 1                        #given
 c      = 1#3e8 
 
 
@@ -52,21 +52,9 @@ alphamL = 2
 # Ne constants definition
 wc    = e*abs(B0)/me
 print "omega_c" ,wc
-# Ne function
-def Ne(x) :  
-    a     = wc/(c*(wc*wc-c*c))
-    b     = 1/(wc*wc-c*c)
-    kappa = e*e/(eps0*me)
 
-    a2    = (a*a-b*b)*kappa*kappa
-    a1    = (2*kappa*b + b*x*kappa) 
-    a0    = 1 + x
     
-    #D     = a1*a1 + 4 * a2 * a0
-    
-    return  - a1 /(2*a2)
 
-#NE    = map(lambda x: 3*me/(e*e),  X)
 omega = np.sqrt(3)
 wp = np.sqrt(7)
 gamma = 2
@@ -84,8 +72,8 @@ X    = map(lambda i: mL + i*dx, range(N+1))
 NE   = map(lambda x: wp**2*me/(e*e),  X)
 X12  = map(lambda i: mL+0.5*dx + i*dx, range(N))
 NEy  = map(lambda x: wp**2*me/(e*e),  X12)
-Ex   = map(lambda x: 0, X)
-ux   = map(lambda x: 0, X)
+Ex   = map(lambda x: np.exp(-gamma*x), X)
+ux   = map(lambda x: -e/(me*complex(0,omega))*np.exp(-gamma*x), X)
 H    = map(lambda x: (gamma/complex(0,omega))*np.exp(-gamma*x)*np.exp(complex(0,-omega*dt/2)), X)
 Ey   = map(lambda x: np.exp(-gamma*x),X12)
 uy   = map(lambda x: -e/(me*complex(0,omega))*np.exp(-gamma*x), X12)
[…]

### 2014-08-20 time_dependant_pb.py
initialization pb?

@@ -14,8 +14,8 @@ import copy
 # mesh size
 N      = 500
 # domain ]-L ; H[, (mL=-L)
-mL     = -1
-H      =  10
+mL     = -2
+H      =  50
 # space step 
 dx     = (H-mL)/N
 print "dx", dx
@@ -72,11 +72,15 @@ X    = map(lambda i: mL + i*dx, range(N+1))
 NE   = map(lambda x: wp**2*me/(e*e),  X)
 X12  = map(lambda i: mL+0.5*dx + i*dx, range(N))
 NEy  = map(lambda x: wp**2*me/(e*e),  X12)
-Ex   = map(lambda x: np.exp(-gamma*x), X)
-ux   = map(lambda x: -e/(me*complex(0,omega))*np.exp(-gamma*x), X)
-H    = map(lambda x: (gamma/complex(0,omega))*np.exp(-gamma*x)*np.exp(complex(0,-omega*dt/2)), X)
 Ey   = map(lambda x: np.exp(-gamma*x),X12)
-uy   = map(lambda x: -e/(me*complex(0,omega))*np.exp(-gamma*x), X12)
+H    = map(lambda x: -(gamma/complex(0,omega))*np.exp(-gamma*x)*np.exp(complex(0,-omega*dt/2)), X)
+uy   = map(lambda x:-(1/(e*NE[1]))*(eps0*complex(0,omega)-complex(0,gamma*gamma/omega))*np.exp(-gamma*x), X12)
+ux   = map(lambda x: (1/(B0*e)*(-me/(e*NE[1])*(eps0*omega*omega+gamma*gamma)-e+nu*me/(e*NE[1])*(complex(0,-omega-gamma*gamma/omega))))*np.exp(-gamma*x), X)
+Ex   = map(lambda x: ((e*NE[1])/(eps0*complex(0,omega)))*x, ux)
+
+
+
+
 
 #H12 = map(lambda x: -np.exp(-alpha*dt/2)*np.exp(-alpha*x),X)
 

### 2014-08-20 time_dependant_pb.py
fix Ne constant with appropriate value

@@ -69,7 +69,7 @@ def g(t) :
 #------table and functions initialisation-------#
 #-----------------------------------------------#
 X    = map(lambda i: mL + i*dx, range(N+1))
-NE   = map(lambda x: wp**2*me/(e*e),  X)
+NE   = map(lambda x:3.13895515115395 + 3.66439242009228*complex(0,1) ,  X)
 X12  = map(lambda i: mL+0.5*dx + i*dx, range(N))
 NEy  = map(lambda x: wp**2*me/(e*e),  X12)
 Ey   = map(lambda x: np.exp(-gamma*x),X12)
@@ -77,10 +77,6 @@ H    = map(lambda x: -(gamma/complex(0,omega))*np.exp(-gamma*x)*np.exp(complex(0
 uy   = map(lambda x:-(1/(e*NE[1]))*(eps0*complex(0,omega)-complex(0,gamma*gamma/omega))*np.exp(-gamma*x), X12)
 ux   = map(lambda x: (1/(B0*e)*(-me/(e*NE[1])*(eps0*omega*omega+gamma*gamma)-e+nu*me/(e*NE[1])*(complex(0,-omega-gamma*gamma/omega))))*np.exp(-gamma*x), X)
 Ex   = map(lambda x: ((e*NE[1])/(eps0*complex(0,omega)))*x, ux)
-
-
-
-
 
 #H12 = map(lambda x: -np.exp(-alpha*dt/2)*np.exp(-alpha*x),X)
 

### 2014-08-20 time_dependant_pb_Nefunc.py
imp Ne function

@@ -1,0 +1,187 @@
+#!/usr/bin/python
+# -*- coding: utf-8 -*-
+
+from __future__ import division
+import os
+from time import time
+import numpy as np
+from pylab import *
+import scipy.io
+from scipy.special import airy
+import copy
+
+#---------------CONSTANTS--------------------#
+# mesh size
+N      = 500
+# domain ]-L ; H[, (mL=-L)
+mL     = -2
+H      =  50
+# space step 
+dx     = (H-mL)/N
+print "dx", dx
+# time step
+dt     = 0.5*dx
+print "dt",dt
+# Number of time steps
+Ntime = 10
+# constants 
+me     = 9.11e-31               #electron mass (kg)
+e      = -1.6e-19               #electron charge (coulombs)
+eps0   = 8.85e-12               #permeability  (F/m)
+nu     = 0                        #friction
+B0     = 0.95                        #given
+c      = 3e8 
+
+
+
+#alpha(-L)
+alphamL = 2
+
+#-------------airy functions------------------#
+#return A
+#def airy_one(x):
+#    [A,B,C,D] = airy(x)
+#    return A
+#return A'
+#def airy_two(x):
+#    [A,B,C,D] = airy(x)
+#    return B
+#-----------------------------------------------#
+
+#-------------------------- NE --------------------------#
+# Ne constants definition
+wc    = e*abs(B0)/me
+print "omega_c" ,wc
+def Ne(x) : 
+    return (2*B0)/(1+exp(-x)) ;
+    
+
+omega = np.sqrt(3)
+wp = np.sqrt(7)
+gamma = 2
+#---------------------------------------------------------#
+
+#--------------G for left BC -------------------#
+alpha = 1
+
+def g(t) : 
+    return np.exp(complex(0,omega*t))*np.exp(-gamma*mL)*(-gamma+complex(0,alphamL))
+#-----------------------------------------------#
+#------table and functions initialisation-------#
+#-----------------------------------------------#
[…]

### 2014-08-24 time_dependant_pb_omega.py
dirichlet BC on the right

@@ -12,10 +12,10 @@ import copy
 
 #---------------CONSTANTS--------------------#
 # mesh size
-N      = 1000
+N      = 500
 # domain ]-L ; H[, (mL=-L)
 mL     = -1
-H      =  50
+H      =  10
 # space step 
 dx     = (H-mL)/N
 print "dx", dx
@@ -29,7 +29,7 @@ me     = 1#9.11e-31               #electron mass (kg)
 e      = -1#1.6e-19              #electron charge (coulombs)
 eps0   = 1#8.85e-12               #permeability  (F/m)
 nu     = 0                       #friction
-B0     = 0.95                        #given
+B0     = 1#0.95                        #given
 c      = 1
 
 
@@ -123,7 +123,7 @@ def plot2(X,T,s,s2,s3):
     #leg = axarr.legend(shadow = True, loc = 3)
     plt.draw()
     
-    time.sleep(0.001)
+    #time.sleep(0.001)
 
 
 #---------------------------------------------------------#
@@ -133,8 +133,8 @@ def plot2(X,T,s,s2,s3):
 def Kcoeff(x): 
     K1     =  1 + nu * dt/2 + dt*dt*x*x/(4)
     K2     =  1 - nu * dt/2 - dt*dt*x*x/(4)
-    K1x    =  K1 - wc*dt*wc*dt/(4*K1)
-    K2x    =  K2 + wc*dt*wc*dt/(4*K1)
+    K1x    =  K1 + wc*dt*wc*dt/(4*K1)
+    K2x    =  K2 - wc*dt*wc*dt/(4*K1)
     
     return [K1,K2,K1x,K2x]
 
@@ -155,30 +155,31 @@ while (t<=Ntime):
     print "iter : ",t,"time : ", t*dt
 
     #---------------- H -> H12
-    H12[0] = H[0] -  dt/dx* (Ey[0] - 1/alphaey * (Ey[0] *(- 1/dx - complex(0,alphamL)/2)+g((t-1)*dt)))
+    H12[0] = H[0] -  dt/dx* (Ey[0] - 1/alphaey * (g((t-1)*dt)-Ey[0]*(1/dx+complex(0,alphamL)/2)))
 
     i = 1
     while (i<N):
[…]

### 2014-08-24 time_dependant_pb_omega.py
few bug fix

@@ -12,10 +12,10 @@ import copy
 
 #---------------CONSTANTS--------------------#
 # mesh size
-N      = 500
+N      = 1000
 # domain ]-L ; H[, (mL=-L)
 mL     = -1
-H      =  10
+H      =  100
 # space step 
 dx     = (H-mL)/N
 print "dx", dx
@@ -28,8 +28,8 @@ Ntime = 4000
 me     = 1#9.11e-31               #electron mass (kg)
 e      = -1#1.6e-19              #electron charge (coulombs)
 eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 0                       #friction
-B0     = 1#0.95                        #given
+nu     = 0.5                      #friction
+B0     = 0.95                        #given
 c      = 1
 
 
@@ -49,10 +49,10 @@ c      = 1
 #wc    = abs(e)*B0/me
 #print "omega_c" ,wc
 def Ne(x) : 
-    return  7# (2*B0)/(1+exp(-x)) ;
+    return (2*B0)/(1+exp(-x)) ;
     
 
-omega = 0.5#np.sqrt(3)
+omega = 3
 
 
 gamma = 2
@@ -63,8 +63,9 @@ alpha = 1
 
 def g(t) : 
     #return np.exp(complex(0,omega*t))*np.exp(-gamma*mL)*(-gamma+complex(0,alphamL))
-    return 1/2*(1+tanh((t-2)/0.1))*np.exp(-omega*t*complex(0,1))
-
+    #return 1/2*(1+tanh((t-2)/0.1))*np.exp(-omega*t*complex(0,1))
+    return B0*sin(omega*t)
+    
 print g(0)
 #-----------------------------------------------#
 #------table and functions initialisation-------#
@@ -82,7 +83,7 @@ WP   = map(lambda x   : sqrt(e*e*x/(me*eps0)), NE)
 wc   = abs(e)*B0/me
 WPy  = map(lambda x   : sqrt(e*e*x/(me*eps0)), NEy)
 Wy   = map(lambda x   : x*x + wc*wc, WPy)
-
+print 'wp = ', WP[1]
[…]

### 2014-08-26 presentation/solve_mH1.m
parameters for the picture2.pdf and main_pic.pdf, used for the presentation

@@ -1,0 +1,346 @@
+function [e1, e2,M,x, Kstiff, Mmass]=solve_mH1(dx,lambda, nu, uniform)
+%mesh generation
+L=7;
+H=10;
+if uniform
+x=-L:dx:H;
+else
+phi=-pi/2:dx:pi/2;
+ x=(H+L)*sin(phi)/2.0+(H-L)./2.0;
+
+
+end
+tic
+[A,B,D]=construct_block_matrix(x,nu,lambda);
+save('A.mat', 'A');
+time_passed=toc();
+display (strcat(num2str(time_passed)," for the construction of the matrix"));
+r=construct_rhs(x);
+
+tic
+[M,rhs]=permute(A,B,D,r);
+save('M.mat', 'M');
+sol=M\rhs;
+
+norm(M*sol-rhs)
+
+[e1, e2]=permute_solution_back(sol);
+
+time_passed=toc();
+display(strcat(num2str(time_passed)," for the solution of the system of eqs"));
+
+%auxiliary matrices, namely the mass matrix and the stiffness matrix
+Kst=K_lpl(x);
+Mm=mass_matrixP1(x);
+Kstiff=spdiags([Kst(:,2) Kst(:,1) circshift(Kst(:,2),1)], -1:1, length(Kst), length(Kst));
+Mmass=spdiags([Mm(:,2) Mm(:,1) circshift(Mm(:,2),1)], -1:1, length(Mm), length(Mm));
+end
+
+
+function [M,rhs]=permute(A,B,D,rhs_old)
+n1=size(A);
+n2=size(B);
+band=zeros(n1(1)+n2(1), 4);%7-diagonal symmetric system; the 'band' contains the diagonals and subdiagonals
+%column permutation
+%e_new_{j}=e_{1,(j+1)/2} if j is odd
+%e_new_{j}=e_{2,j/2} if j is even
+rhs=zeros(length(rhs_old),1);
+rhs(2)=rhs_old(n1(1)+1);
+%forming the new symmetric matrix, with the row permutation being the same as the column permutation
+%main diagonal
+band(1:2:(end-1),1)=A(:,1);
+band(2:2:end, 1)=D(:,1);
+%subdiagonal
+band(1:2:(end-1),2)=B(:,1);
+band(2:2:(end),2)=B(:,2);
+%subsubiagonal
+band(1:2:(end-1),3)=A(:,2);
[…]

### 2014-08-26 time_dependant_pb_omega.py
last version

@@ -12,24 +12,24 @@ import copy
 
 #---------------CONSTANTS--------------------#
 # mesh size
-N      = 1000
-# domain ]-L ; H[, (mL=-L)
-mL     = -1
-H      =  100
+N      = 400
+# domain ]-L ; L[, (mL=-L)
+mL     = -20
+pL      =  20
 # space step 
-dx     = (H-mL)/N
+dx     = (pL-mL)/N
 print "dx", dx
 # time step
 dt     = 0.5*dx
 print "dt",dt
 # Number of time steps
-Ntime = 4000
+Ntime = 100
 # constants 
 me     = 1#9.11e-31               #electron mass (kg)
 e      = -1#1.6e-19              #electron charge (coulombs)
 eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 0.5                      #friction
-B0     = 0.95                        #given
+nu     = 0                    #friction
+B0     = 1#0.95                        #given
 c      = 1
 
 
@@ -49,7 +49,12 @@ c      = 1
 #wc    = abs(e)*B0/me
 #print "omega_c" ,wc
 def Ne(x) : 
-    return (2*B0)/(1+exp(-x)) ;
+    if (x < -10) :
+        return 0
+    elif (x >= -10) and (x <= 10 ):
+        return 36*(x+10)/20
+    else :
+        return 36
     
 
 omega = 3
@@ -64,7 +69,7 @@ alpha = 1
 def g(t) : 
     #return np.exp(complex(0,omega*t))*np.exp(-gamma*mL)*(-gamma+complex(0,alphamL))
     #return 1/2*(1+tanh((t-2)/0.1))*np.exp(-omega*t*complex(0,1))
-    return B0*sin(omega*t)
+    return cos(omega*t)
     
 print g(0)
 #-----------------------------------------------#
@@ -77,13 +82,16 @@ NEy  = map(lambda x : Ne(x),X12)
 Ey   = map(lambda x : 0, X12)
 H    = map(lambda x : 0, X)
[…]

### 2014-08-26 code_validity.tex
added a plot
fixed a bug in a figure

@@
     \begin{loglogaxis}[
-    	width=0.7\textwidth,
+    	width=0.9\textwidth,
         xlabel=$h$,
@@
 \addlegendentry{$\nu=2^{-8}$};
-\addplot[mark=square,red] table {pics/result_l2e1.0.0039062.dat}; 
+\addplot[mark=triangle,red] table {pics/result_l2e1.0.00097656.dat}; 
 \addlegendentry{$\nu=2^{-10}$};
-\addplot[mark=triangle,blue] table {pics/result_l2e1.0.00097656.dat}; 
+\addplot[mark=triangle,blue] table {pics/result_l2e1.0.00024414.dat}; 
 \addlegendentry{$\nu=2^{-12}$};
-\addplot[mark=triangle,green] table {pics/result_l2e1.0.00024414.dat}; 
-\addlegendentry{$\nu=2^{-12}$};
-\addplot[mark=triangle, red] table {pics/result_l2e1.6.1035e-05.dat};
+\addplot[mark=triangle, green] table {pics/result_l2e1.6.1035e-05.dat};
 \addlegendentry{$\nu=2^{-14}$};
-\addplot[mark=*, violet] table{pics/result_l2e1.1.5259e-05.dat};
+\addplot[mark=triangle, red] table{pics/result_l2e1.1.5259e-05.dat};
 \addlegendentry{$\nu=2^{-16}$};
@@
 \addlegendentry{$\nu=2^{-8}$};
-\addplot[mark=square,red] table {pics/result_l2e2.0.0039062.dat}; 
+\addplot[mark=square, red] table {pics/result_l2e2.0.00097656.dat}; 
 \addlegendentry{$\nu=2^{-10}$};
-\addplot[mark=triangle,blue] table {pics/result_l2e2.0.00097656.dat}; 
+\addplot[mark=triangle,blue] table {pics/result_l2e2.0.00024414.dat}; 
 \addlegendentry{$\nu=2^{-12}$};
-\addplot[mark=triangle,green] table {pics/result_l2e2.0.00024414.dat}; 
-\addlegendentry{$\nu=2^{-12}$};
-\addplot[mark=triangle, red] table{pics/result_l2e2.6.1035e-05.dat};
+\addplot[mark=triangle, green] table{pics/result_l2e2.6.1035e-05.dat};
 \addlegendentry{$\nu=2^{-14}$};
-\addplot[mark=*, violet] table{pics/result_l2e2.1.5259e-05.dat};
+\addplot[mark=triangle, red] table{pics/result_l2e2.1.5259e-05.dat};
 \addlegendentry{$\nu=2^{-16}$};
@@
 \addlegendentry{$\epsilon=1e-1$};
-\addplot[mark=o,red] table {pics/h1e-2.dat}; 
-\addlegendentry{$\epsilon=1e-2$};
+%\addplot[mark=o,red] table {pics/h1e-2.dat}; 
+%\addlegendentry{$\epsilon=1e-2$};
 \addplot[mark=triangle,green] table {pics/h1e-3.dat}; 
 \addlegendentry{$\epsilon=1e-3$};
-\addplot[mark=square,cyan] table {pics/h1e-4.dat}; 
-\addlegendentry{$\epsilon=1e-4$};
+%\addplot[mark=square,cyan] table {pics/h1e-4.dat}; 
+%\addlegendentry{$\epsilon=1e-4$};
 \addplot[dashed, red] table {pics/nu1.dat}; 

### 2014-08-26 presentation/content.tex
test commit

% DO NOT COMPILE THIS FILE DIRECTLY!
% This is included by the the driver file (FlipBeamerTemplate.tex).

%{ %% This is a total kludge for a fancy title page background
%\setbeamertemplate{sidebar right}
 {\setbeamertemplate{sidebar right}{\llap{\includegraphics[width=\paperwidth,height=\paperheight]{BG_upper}}}
\begin{frame}[c]%{\phantom{title page}} 
% The \phantom{title page} is a kludge to get the red bar on top
% \titlepage
\begin{center}
	% \includegraphics[width=7cm]{WarpedPenguinsReturn}
%\vspace*{-2cm}
	\begin{tikzpicture}%[show background grid] %% Use grid for positioning, then turn off
		\node[inner sep=10pt,anchor =north west] (title) 
			{ \includegraphics[width=7cm]{\titleimage} };
			 \node (title) at (0.5,-2.5) {};
	\end{tikzpicture}
	\quad

	% \includegraphics[width=7cm]{\titleimage} 
	%\vspace*{1cm}
	\tiny{Céline Caldini-Queiros, Bruno Després, Lise-Marie Imbert-Gérard, Maryna Kachanovska\\ (with Olivier Lafitte and Remi Sart)}
	\vspace{.5em}

	\footnotesize\textcolor{brunfonce}{08.04.2014}
%	\texttt{[arXiv:1234.5678]}
	\vspace{1cm}
%

\end{center}
\end{frame}}
\begin{frame}{Modelisation}
 \begin{minipage}{0.45\linewidth}
 \begin{figure}
       		\includegraphics[scale = 0.7]{./images/ITER_cut}
       	\caption{ITER}
     	 \end{figure} 
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
 \begin{figure}
       		\includegraphics[scale = 1.2]{./images/antenne}
       		\caption{waves}
     	 \end{figure} 
\end{minipage}
\begin{block}{Equations : Maxwell-Newton}
\[
\begin{cases}
&-\frac{1}{c^2}\partial_t E + \nabla \wedge B = \mu_0 J \hspace{3cm} J = e N_e u_e\\
&\partial_t B + \nabla \wedge E  = 0	\\
&m_e \partial_t u_e  =  -e(E + u_e \wedge B_0 ) - m_e \nu u_e
\end{cases}
\]
\end{block}

\end{frame}
\begin{frame}{References}
\begin{itemize}
\item Décomposition de domaines pour la simulation "full wave" dans un plasma froid T. Hattori (thesis) \\ \ \\
\item Analyse mathématique et numérique de problèmes d’ondes apparaissant dans les plasmas
magnétiques, L.-M. Imbert-Gérard (thesis)\\ \ \\
\item Hybrid resonance of Maxwell's equations in slab geometry, B.Després, L.M. Imbert-Gérard and R. Weder, in JMPA\\ \ \\
\item  Stable coupling of the Yee scheme with a linear current model, F. Da Silva, M. Campos-Pinto, B. Després, S. Heuraux, HAL preprint 2014 . \\ 
\end{itemize}
\end{frame}
\begin{frame}{Frequency domain study}
In 1D : $\partial_t = \imath \theta$

\alert{Variational formulation :}
\[
\begin{array}{l}
\displaystyle \int_{-L}^H (E_2' -\imath\theta E_1)\overline{(\tilde E_2' -\imath \theta \tilde E_1)} - \int_{-L}^H (\eps_0 +\imath\nu Id) \E \cdot \overline{\tilde \E}
\\ \displaystyle  - \imath \sqrt{\alpha(-L)} E_2 (-L) \tilde E_2 (-L) = -g_{inc} (-L) \overline{( \tilde E_2(-L) )} 
\end{array}
\]
\[
a(\ubf,\vbf) = a_1 (\ubf,\vbf) +\imath a_2(\ubf,\vbf)\  \text{ and } \  l(\vbf) = -g_{inc} (-L) \overline{(v_2(-L) )} 
\]
\[
\left\{\begin{array}{l}
a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -\imath\theta u_1)\overline{(v_2' -\imath \theta v_1)} - \int_{-L}^H \eps_0 \ubf\cdot \overline{\vbf}, 
\\ a_2(\ubf,\vbf) = -\nu \int_{-L}^H  \ubf\cdot \overline{\vbf} -  \sqrt{\alpha(-L)} u_2 (-L) \overline{v_2 (-L)} , 
\end{array}\right.
\]
where $a_1= a_1^*$ and $a_2=a_2^*$ are hermitian.
\begin{block}{}
\[
|a(u,u)| \geq \min\left(\frac{1}{4} \frac{\sqrt{\alpha(-L)}}{|\Omega|} , \frac{1}{16}\frac{\sqrt{\frac{\nu}{\heps + \theta^2}}}{|\Omega|^2}\right) \|u\|^2_{L^2}
\]
\end{block}
\end{frame}

\begin{frame}{Simulation in frequency domain}
\ALERT{Matlab code, $P^1$ FEM}

 \begin{minipage}{0.7\linewidth}
 \begin{figure}
       		\includegraphics[scale = 0.6]{./images/picture2}
       	\caption{ITER}
     	 \end{figure} 
\end{minipage}
\hfill
\begin{minipage}{0.25\linewidth}
\[
E_\nu \approx \frac{c}{x + \imath \nu}
\]
\end{minipage}
\end{frame}
 {\setbeamertemplate{sidebar right}{\llap{\includegraphics[width=\paperwidth,height=\paperheight]{BG_upper}}}
\begin{frame}
\begin{center}
\textcolor{lightred}{\scalebox{2}{Thank you for your attention !}}
\end{center}
\end{frame}}

### 2014-08-26 presentation/content.tex
need to add space in coercivity study

@@
 \end{frame}}
-\begin{frame}{Modelisation}
+\begin{frame}{Model}
  \begin{minipage}{0.45\linewidth}
@@
 \end{frame}
-\begin{frame}{References}
+\begin{frame}{Some references}
 \begin{itemize}
-\item Décomposition de domaines pour la simulation "full wave" dans un plasma froid T. Hattori (thesis) \\ \ \\
+\item Décomposition de domaines pour la simulation "full wave" dans un plasma froid, T. Hattori (thesis) \\ 
 \item Analyse mathématique et numérique de problèmes d’ondes apparaissant dans les plasmas
-magnétiques, L.-M. Imbert-Gérard (thesis)\\ \ \\
-\item Hybrid resonance of Maxwell's equations in slab geometry, B.Després, L.M. Imbert-Gérard and R. Weder, in JMPA\\ \ \\
-\item  Stable coupling of the Yee scheme with a linear current model, F. Da Silva, M. Campos-Pinto, B. Després, S. Heuraux, HAL preprint 2014 . \\ 
+magnétiques, L.-M. Imbert-Gérard (thesis)\\ 
+\item Hybrid resonance of Maxwell's equations in slab geometry, B.Després, L.M. Imbert-Gérard and R. Weder, in JMPA\\ 
+\item  Stable coupling of the Yee scheme with a linear current model, F. Da Silva, M. Campos-Pinto, B. Després, S. Heuraux, HAL preprint 2014. \\ 
+\item Full-wave modeling of the O-X mode conversion in the Pegasus Toroidal Experiment, A.
+Kohn, J.
+Jacquot, M.W.
+Bongard, S.
+Gallian, E.T.
+Hinson and F.A.
+Volpe, arXiv:1104.0743 [physics.plasm-ph](2011).
 \end{itemize}
@@
 \begin{frame}{Frequency domain study}
-In 1D : $\partial_t = \imath \theta$
+In 1D : $\partial_t = \imath \theta$. Unknowns : $\ubf =(E_1,E_2) = (E_x,E_y)$
 
@@
 where $a_1= a_1^*$ and $a_2=a_2^*$ are hermitian.
+\end{frame}
+\begin{frame}{Frequency domain study}
+\[
+|a(\ubf,\ubf)| \geq \frac{1}{4} \sqrt{\frac{\nu}{\heps + \theta^2}}\|u_2'\|^2_{L^2} +  \frac{\nu}{4} \|\ubf\|_{L^2}^2,
+\]
 \begin{block}{}
@@
 
- \begin{minipage}{0.7\linewidth}
+\ \\
+
+ \begin{minipage}{0.45\linewidth}
 \begin{figure}
-       		\includegraphics[scale = 0.6]{./images/picture2}
-       	\caption{ITER}
+	\begin{center}
+       	\includegraphics[width = 0.9\textwidth]{./images/picture2}
+       	\caption{Convergence $E_x^\nu(x)$}
+    \end{center}
 \end{figure} 
@@
 \hfill
-\begin{minipage}{0.25\linewidth}
+\begin{minipage}{0.45\linewidth}
+	\begin{figure}
+\begin{center}
+       	\includegraphics[width = 0.9\textwidth]{./images/pics3}
+       	\caption{Convergence $E^\nu_y(x)$}
+    \end{center}
+\end{figure} 
+\end{minipage}
 \[
-E_\nu \approx \frac{c}{x + \imath \nu}
+E_x^\nu \approx \frac{c}{x + \imath \nu}
 \]
-\end{minipage}
+
+\end{frame}
+\begin{frame}
+\begin{figure}[ht]
+\subfigure[Convergence rates]{
+    \includegraphics[width=0.4\textwidth]{./images/fig1}
+  }
+  \subfigure[The $L_2$ error of $E_x(x)$]{
+    \includegraphics[width=0.4\textwidth]{./images/fig2}
+  }
+
+  \subfigure[The $L_2$ error of $E_y(x)$]{
+    \includegraphics[width=0.4\textwidth]{./images/fig3}
+  }
+  \subfigure[The dependance of $h_\veps$ in $\nu$]{
+    \includegraphics[width=0.4\textwidth]{./images/fig4}
+  }
+
+\end{figure}
+\end{frame}
+
+\begin{frame}{Time dependant problem}
+\[
+\begin{cases}
+- \veps_0 \partial_t E_x = e N_e u_x \\
+- \veps_0 \partial_t E_y - \partial_x E_y = 0 e N_e u_y \\
+\partial_t H_z + \partial_x E_y = 0 \\
+m_e \partial_t u_x = e (E_x + u_y B_0) - \nu m_e u_x
+m_e \partial_t u_y = e (E_x - u_x B_0) - \nu m_e u_y
+\end{cases}
+\]
+
+\alert{Finite difference, 1D energy conservative scheme\footnote{ Stable coupling of the Yee scheme with a linear current model, F.
+Da Silva, M.
+Campos-Pinto, B.
+Després, S.
+Heuraux, HAL preprint 2014}}
+
 \end{frame}

### 2014-08-26 presentation/content.tex
first draft

@@
 \end{frame}}
-\begin{frame}{Model}
+\begin{frame}{Physical context and model}
  \begin{minipage}{0.45\linewidth}
@@
 \end{frame}
-\begin{frame}{Some references}
+\begin{frame}{Some references on numerical simulation}
 \begin{itemize}
@@
 \begin{frame}{Frequency domain study}
-In 1D : $\partial_t = \imath \theta$. Unknowns : $\ubf =(E_1,E_2) = (E_x,E_y)$
+In 1D : $\partial_t = i \theta$. Unknowns : $\ubf =(E_1,E_2) = (E_x,E_y)$
 
@@
 \begin{array}{l}
-\displaystyle \int_{-L}^H (E_2' -\imath\theta E_1)\overline{(\tilde E_2' -\imath \theta \tilde E_1)} - \int_{-L}^H (\eps_0 +\imath\nu Id) \E \cdot \overline{\tilde \E}
-\\ \displaystyle  - \imath \sqrt{\alpha(-L)} E_2 (-L) \tilde E_2 (-L) = -g_{inc} (-L) \overline{( \tilde E_2(-L) )} 
+\displaystyle \int_{-L}^H (E_2' -i\theta E_1)\overline{(\tilde E_2' -i \theta \tilde E_1)} - \int_{-L}^H (\eps_0 +i\nu Id) \E \cdot \overline{\tilde \E}
+\\ \displaystyle  - i \sqrt{\alpha(-L)} E_2 (-L) \tilde E_2 (-L) = -g_{inc} (-L) \overline{( \tilde E_2(-L) )} 
 \end{array}
@@
 \[
-a(\ubf,\vbf) = a_1 (\ubf,\vbf) +\imath a_2(\ubf,\vbf)\  \text{ and } \  l(\vbf) = -g_{inc} (-L) \overline{(v_2(-L) )} 
+a(\ubf,\vbf) = a_1 (\ubf,\vbf) +i a_2(\ubf,\vbf)\  \text{ and } \  l(\vbf) = -g_{inc} (-L) \overline{(v_2(-L) )} 
 \]
@@
 \left\{\begin{array}{l}
-a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -\imath\theta u_1)\overline{(v_2' -\imath \theta v_1)} - \int_{-L}^H \eps_0 \ubf\cdot \overline{\vbf}, 
+a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -i\theta u_1)\overline{(v_2' -i \theta v_1)} - \int_{-L}^H \eps_0 \ubf\cdot \overline{\vbf}, 
 \\ a_2(\ubf,\vbf) = -\nu \int_{-L}^H  \ubf\cdot \overline{\vbf} -  \sqrt{\alpha(-L)} u_2 (-L) \overline{v_2 (-L)} , 
@@
 where $a_1= a_1^*$ and $a_2=a_2^*$ are hermitian.
+\[
+\ubf,\vbf \in V =  \{ (E_1,E_2) |\; E_1,E_2,E_2'  \in L^2\}
+\]
+\[
+\|u\|_{V}^2 = \|E_1\|^2_{L^2} + \|E_2\|^2_{L^2} + \|E_2'\|_{L^2}
+\]
 \end{frame}
@@
 \]
-\begin{block}{}
+
 \[
@@
 \]
+\begin{block}{}
+\begin{itemize}
+\item The problem is well-posed (existence/uniqueness)
+\item Passing to the limit $\nu \rightarrow 0^+$ is the limit absorption principle
+\end{itemize}
 \end{block}
@@
 \ALERT{Matlab code, $P^1$ FEM}
+
+For physically adapted coefficients $N_e$, $B_0$ it yields the hybrid resonnance
 
@@
 \[
-E_x^\nu \approx \frac{c}{x + \imath \nu}
+E_x^\nu \approx \frac{c}{x + i \nu}
 \]
@@
 \begin{figure}[ht]
-\subfigure[Convergence rates]{
-    \includegraphics[width=0.4\textwidth]{./images/fig1}
+\subfigure[\footnotesize{Convergence non sigular case}]{
+    \includegraphics[width=0.38\textwidth]{./images/fig1}
   }
-  \subfigure[The $L_2$ error of $E_x(x)$]{
-    \includegraphics[width=0.4\textwidth]{./images/fig2}
+  \subfigure[\footnotesize{$E_x(x)$ error (singular case)}]{
+    \includegraphics[width=0.38\textwidth]{./images/fig2}
   }
 
-  \subfigure[The $L_2$ error of $E_y(x)$]{
-    \includegraphics[width=0.4\textwidth]{./images/fig3}
+  \subfigure[$E_y(x)$ error (singular case)]{
+    \includegraphics[width=0.38\textwidth]{./images/fig3}
   }
-  \subfigure[The dependance of $h_\veps$ in $\nu$]{
-    \includegraphics[width=0.4\textwidth]{./images/fig4}
+  \subfigure[$h_\veps$  vs $\nu$ (sing.)]{
+    \includegraphics[width=0.38\textwidth]{./images/fig4}
   }
@@
 
-\begin{frame}{Time dependant problem}
+\begin{frame}{Time dependent problem}
+Harmonic forcing on the boundary : recover the limiting amplitude principle\footnote{C. Morawetz, CPAM, 1962} at the limit $t\rightarrow \infty$ 
 \[
@@
 - \veps_0 \partial_t E_x = e N_e u_x \\
-- \veps_0 \partial_t E_y - \partial_x E_y = 0 e N_e u_y \\
+- \veps_0 \partial_t E_y - \partial_x E_y =  e N_e u_y \\
 \partial_t H_z + \partial_x E_y = 0 \\
@@
 
-\alert{Finite difference, 1D energy conservative scheme\footnote{ Stable coupling of the Yee scheme with a linear current model, F.
+\alert{Finite difference, 1D energy conservative leap-frog scheme\footnote{ Stable coupling of the Yee scheme with a linear current model, F.
 Da Silva, M.

### 2014-08-27 time_dependant_pb_Bruno.py
new version of the code

@@ -1,5 +1,4 @@
-#!/usr/bin/python
-# -*- coding: utf-8 -*-
+#!/usr/bin/python# -*- coding: utf-8 -*-
 
 from __future__ import division
 import os
@@ -14,22 +13,23 @@ import copy
 # mesh size
 N      = 400
 # domain ]-L ; L[, (mL=-L)
-mL     = -20
-pL      =  20
+mL     =  -15
+pL      = 10
 # space step 
 dx     = (pL-mL)/N
 print "dx", dx
 # time step
-dt     = 0.5*dx
+dt     = 0.3*dx
 print "dt",dt
 # Number of time steps
-Ntime = 100
+Ntime = 20000
+tempsmax= 200
 # constants 
 me     = 1#9.11e-31               #electron mass (kg)
 e      = -1#1.6e-19              #electron charge (coulombs)
 eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 0                    #friction
-B0     = 1#0.95                        #given
+nu     = .0               #friction
+B0     = 4./3./sqrt(10) #0.95                        #given
 c      = 1
 
 
@@ -50,17 +50,17 @@ c      = 1
 #print "omega_c" ,wc
 def Ne(x) : 
     if (x < -10) :
-        return 0
-    elif (x >= -10) and (x <= 10 ):
-        return 36*(x+10)/20
+            return 0
+    elif (x <= 5 ):
+            return 1.5*(10-16/90)*(x+10)/15
     else :
-        return 36
+            return 1.5*(10-16/90)
     
 
-omega = 3
+omega = sqrt(10)
 
 
-gamma = 2
+#gamma = 2
 #---------------------------------------------------------#
 
 #--------------G for left BC -------------------#
@@ -69,7 +69,7 @@ alpha = 1
 def g(t) : 
     #return np.exp(complex(0,omega*t))*np.exp(-gamma*mL)*(-gamma+complex(0,alphamL))
[…]

### 2014-10-23 lanceur.py
added visual/audio data

@@ -21,7 +21,7 @@ print "dx", dx
 dt     = 0.5*dx
 print "dt",dt
 # Number of time steps
-Ntime = 1000
+Ntime = 10000
 # constants 
 me     = 1#9.11e-31               #electron mass (kg)
 e      = -1#1.6e-19              #electron charge (coulombs)
@@ -42,7 +42,7 @@ def Ne(x) :
         return 36
     
 
-omega = 3
+omega = 1
 
 
 gamma = 2
@@ -52,7 +52,7 @@ gamma = 2
 alpha = 1
 
 def g(t) : 
-    return cos(omega*t)
+    return sin(omega*t)
     
 print g(0)
 #-----------------------------------------------#

### 2014-10-23 lanceur2.py

@@ -26,7 +26,7 @@ Ntime = 2e6
 me     = 1#9.11e-31               #electron mass (kg)
 e      = -1#1.6e-19              #electron charge (coulombs)
 eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 1e4                  #friction
+nu     = 1e-3                  #friction
 B0     = 0#0.95                        #given
 c      = 1
 
@@ -34,7 +34,7 @@ c      = 1
 #-------------------------- NE --------------------------#
 
 def Ne(x) : 
-	return 0.2;
+	return 0.1;
 #    if (x < -10) :
 #        return 0
 #    elif (x >= -10) and (x <= 10 ):
@@ -53,7 +53,7 @@ gamma = 2
 alpha = 1
 
 def g(t) : 
-    return cos(omega*t)
+    return sin(omega*t)
     
 print g(0)
 #-----------------------------------------------#

### 2014-10-23 scriptvideo.py

@@ -11,7 +11,7 @@ import matplotlib.pyplot as plt
 from pylab import *
 import copy
 import sub
-Niter = 5000
+Niter = 10000
 
 f, axarr = plt.subplots(3,2)
 f.subplots_adjust(hspace=.5)
@@ -54,39 +54,39 @@ def plot2(X,ux,Ex,H,X12,uy,Ey,T,Et):
 iter = 0
 while (iter <Niter):
     print 'iter',iter
-    mat = np.loadtxt('files/ux%4.4d.data'%iter)
+    mat = np.loadtxt('/UMA/tmp/maryna/password//ux%4.4d.data'%iter)
     X = mat[:,0]
     ux = mat[:,1]
     print 'X', np.isnan(np.sum(X))
     print 'ux', np.isnan(np.sum(ux))
     
-    mat = np.loadtxt('files/Ex%4.4d.data'%iter)
+    mat = np.loadtxt('/UMA/tmp/maryna/password//Ex%4.4d.data'%iter)
     Ex = mat[:,1]
     print 'Ex', np.isnan(np.sum(Ex))
     
-    mat = np.loadtxt('files/H%4.4d.data'%iter)
+    mat = np.loadtxt('/UMA/tmp/maryna/password//H%4.4d.data'%iter)
     H = mat[:,1]
     print 'H', np.isnan(np.sum(H))
 
     
-    mat = np.loadtxt('files/uy%4.4d.data'%iter)
+    mat = np.loadtxt('/UMA/tmp/maryna/password//uy%4.4d.data'%iter)
     X12 = mat[:,0]
     uy = mat[:,1]
     print 'X12', np.isnan(np.sum(X12))
     print 'uy', np.isnan(np.sum(uy))
-    mat = np.loadtxt('files/Ey%4.4d.data'%iter)
+    mat = np.loadtxt('/UMA/tmp/maryna/password//Ey%4.4d.data'%iter)
     Ey = mat[:,1]
     print 'Ey',np.isnan(np.sum(Ey))
 
-    mat = np.loadtxt('files/ET.data')
+    mat = np.loadtxt('/UMA/tmp/maryna/password//ET.data')
     T = mat[:,0]
     Et = mat[:,1]
     print "T", np.isnan(np.sum(T))
     print 'Et', np.isnan(np.sum(Ey))
     plot(X,ux)
-    #plot2(X,ux,Ex,H,X12,uy,Ey,T,Et)
[…]

### 2014-10-23 solve_mH1.m

@@ -1,7 +1,7 @@
 function [e1, e2,M,x, Kstiff, Mmass]=solve_mH1(dx,lambda, nu, uniform)
 %mesh generation
-L=15;
-H=10;
+L= 19.99267220322423120; %20!!!
+H=10.007327796775769;%10!!!
 if uniform
 x=-L:dx:H;
 else
@@ -13,7 +13,7 @@ end
 tic
 [A,B,D]=construct_block_matrix(x,nu,lambda);
 time_passed=toc();
-display (strcat(num2str(time_passed)," for the construction of the matrix"));
+display (strcat(num2str(time_passed),' for the construction of the matrix'));
 r=construct_rhs(x);
 
 tic
@@ -26,7 +26,7 @@ norm(M*sol-rhs)
 [e1, e2]=permute_solution_back(sol);
 
 time_passed=toc();
-display(strcat(num2str(time_passed)," for the solution of the system of eqs"));
+display(strcat(num2str(time_passed),' for the solution of the system of eqs'));
 
 %auxiliary matrices, namely the mass matrix and the stiffness matrix
 Kst=K_lpl(x);
@@ -76,23 +76,24 @@ end
 
 function a=alpha(x)
 
-a=zeros(size(x));
-a(x<=-10)=10;
-P=(x<=5)&(x>-10);
-a(P)=-x(P);
-a(x>5)=-5;
+%a=zeros(size(x));
+%a(x<=-10)=1;
+%P=(x<=5)&(x>-10);
+%a(P)=-x(P)/10;
+%a(x>5)=-1/2;
+a=0.9;%0.8*ones(size(x));
 end
 
 function delta=delta(x)
 
 
 delta=zeros(size(x));
-delta(x<=-10)=0;
-P=(x<=5)&(x>-10);
-delta(P)=4/30*x(P)+4/3;
-delta(x>5)=2;
+%delta(x<=-10)=0;
+%P=(x<=5)&(x>-10);
+%delta(P)=(1+x(P)/10)*1e-2;
+%delta(x>5)=3/2*1e-2;
 %delta=sqrt(x.^2+1).*sqrt(x.^2+1+x);
-
+delta=0;
 end
 
 %since the matrices are symmetric tridiagonal, each matrix constructor returns 
@@ -306,7 +307,8 @@ end
 
 function b=construct_rhs(x)
     b=zeros(2*length(x),1);
[…]

### 2014-10-23 tdp.f90

@@ -86,7 +86,7 @@ contains
     do iter = 0, Ntime
        t = (iter+1.0)*dt
        
-       H12(0) = sin(omega*t)
+       H12(0) = sin(omega*(t-dt/2.0))
        do i = 1, N-1
           H12(i) = H(i) - (dt/dx)*(Ey(i)-Ey(i-1))
        end do
@@ -136,7 +136,7 @@ contains
        do i = 0, N-1
           En = En+ Ey(i)*Ey(i)+Ex(i)*Ex(i) + H12(i)*H12(i)
        end do
-       if (mod(iter,10).eq.0 .and. iter>=1900000) then
+       if (iter>=1990000) then
          call writeall(iter,N,Ntime,X,X12,ux,uy,Ex,Ey,H)            
        end if
        write(15,*) iter*dt, En

### 2014-10-23 time_dependant_pb.f90

@@ -21,15 +21,15 @@ contains
     real(8), dimension(0:N-1), intent(in) :: X12, uy, Ey
     character (len=90) :: filename
     integer :: i
-    write (filename, '( "ux", i4.4, ".data" )' ) t
+    write (filename, '( "/UMA/tmp/maryna/password/ux", i7.7, ".data" )' ) t
     open(10, file = filename)
-    write (filename, '( "Ex", i4.4, ".data" )' ) t
+    write (filename, '( "/UMA/tmp/maryna/password/Ex", i7.7, ".data" )' ) t
     open(11, file= filename)
-    write (filename, '( "H", i4.4, ".data" )' ) t
+    write (filename, '( "/UMA/tmp/maryna/password/H", i7.7, ".data" )' ) t
     open(12, file=filename)
-    write (filename, '( "uy", i4.4, ".data" )' ) t
+    write (filename, '( "/UMA/tmp/maryna/password/uy", i7.7, ".data" )' ) t
     open(13, file = filename)
-    write (filename, '( "Ey", i4.4, ".data" )' ) t
+    write (filename, '( "/UMA/tmp/maryna/password/Ey", i7.7, ".data" )' ) t
     open(14, file = filename)
     do i = 0, N-1
        write(10,*) X(i), ux(i)
@@ -80,13 +80,13 @@ contains
     H(0:N)    = Hi(0:N)
     uy(0:N-1) = uyi(0:N-1)
     Ey(0:N-1) = Eyi(0:N-1)
-    open(15, file = "ET.data")
+    open(15, file = "/UMA/tmp/maryna/password/ET.data")
     !time loop
 
     do iter = 0, Ntime
-       t = iter*dt
+       t = (iter+1.0)*dt
        
-       H12(0) = cos(omega*t)
+       H12(0) = sin(omega*t)
        do i = 1, N-1
           H12(i) = H(i) - (dt/dx)*(Ey(i)-Ey(i-1))
        end do
@@ -136,7 +136,9 @@ contains
        do i = 0, N-1
           En = En+ Ey(i)*Ey(i)+Ex(i)*Ex(i) + H12(i)*H12(i)
        end do
+       !if (mod(iter,10).eq.0 .and. iter>=1900000) then
        call writeall(iter,N,Ntime,X,X12,ux,uy,Ex,Ey,H)            
+       !end if
        write(15,*) iter*dt, En
        if (maxval(H)<1E-10) then
           print *, iter,'H nul ?!'

### 2014-10-23 time_dependant_pb.py

@@ -1,182 +1,0 @@
-#!/usr/bin/python
-# -*- coding: utf-8 -*-
-
-from __future__ import division
-import os
-from time import time
-import numpy as np
-from pylab import *
-import scipy.io
-from scipy.special import airy
-import copy
-
-#---------------CONSTANTS--------------------#
-# mesh size
-N      = 500
-# domain ]-L ; H[, (mL=-L)
-mL     = -2
-H      =  50
-# space step 
-dx     = (H-mL)/N
-print "dx", dx
-# time step
-dt     = 0.5*dx
-print "dt",dt
-# Number of time steps
-Ntime = 10
-# constants 
-me     = 1#9.11e-31               #electron mass (kg)
-e      = -1#1.6e-19               #electron charge (coulombs)
-eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 1                        #friction
-B0     = 1                        #given
-c      = 1#3e8 
-
-
-
-#alpha(-L)
-alphamL = 2
-
-#-------------airy functions------------------#
-#return A
-#def airy_one(x):
-#    [A,B,C,D] = airy(x)
-#    return A
-#return A'
-#def airy_two(x):
-#    [A,B,C,D] = airy(x)
-#    return B
-#-----------------------------------------------#
-
-#-------------------------- NE --------------------------#
-# Ne constants definition
-wc    = e*abs(B0)/me
-print "omega_c" ,wc
-
-    
-
-omega = np.sqrt(3)
-wp = np.sqrt(7)
-gamma = 2
-#---------------------------------------------------------#
-
-#--------------G for left BC -------------------#
-alpha = 1
-
-def g(t) : 
-    return np.exp(complex(0,omega*t))*np.exp(-gamma*mL)*(-gamma+complex(0,alphamL))
-#-----------------------------------------------#
-#------table and functions initialisation-------#
-#-----------------------------------------------#
-X    = map(lambda i: mL + i*dx, range(N+1))
[…]

### 2014-10-23 time_dependant_pb_Bruno.py

@@ -1,318 +1,0 @@
-#!/usr/bin/python# -*- coding: utf-8 -*-
-
-from __future__ import division
-import os
-import time
-import numpy as np
-from pylab import *
-import scipy.io
-from scipy.special import airy
-import copy
-
-#---------------CONSTANTS--------------------#
-# mesh size
-N      = 400
-# domain ]-L ; L[, (mL=-L)
-mL     =  -15
-pL      = 10
-# space step 
-dx     = (pL-mL)/N
-print "dx", dx
-# time step
-dt     = 0.3*dx
-print "dt",dt
-# Number of time steps
-Ntime = 20000
-tempsmax= 200
-# constants 
-me     = 1#9.11e-31               #electron mass (kg)
-e      = -1#1.6e-19              #electron charge (coulombs)
-eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = .0               #friction
-B0     = 4./3./sqrt(10) #0.95                        #given
-c      = 1
-
-
-#-------------airy functions------------------#
-#return A
-#def airy_one(x):
-#    [A,B,C,D] = airy(x)
-#    return A
-#return A'
-#def airy_two(x):
-#    [A,B,C,D] = airy(x)
-#    return B
-#-----------------------------------------------#
-
-#-------------------------- NE --------------------------#
-# Ne constants definition
-#wc    = abs(e)*B0/me
-#print "omega_c" ,wc
-def Ne(x) : 
-    if (x < -10) :
-            return 0
-    elif (x <= 5 ):
-            return 1.5*(10-16/90)*(x+10)/15
-    else :
-            return 1.5*(10-16/90)
-    
-
-omega = sqrt(10)
-
-
-#gamma = 2
-#---------------------------------------------------------#
-
-#--------------G for left BC -------------------#
-alpha = 1
-
-def g(t) : 
[…]

### 2014-10-23 time_dependant_pb_Nefunc.py

@@ -1,221 +1,0 @@
-#!/usr/bin/python
-# -*- coding: utf-8 -*-
-
-from __future__ import division
-import os
-import time
-import numpy as np
-from pylab import *
-import scipy.io
-from scipy.special import airy
-import copy
-
-#---------------CONSTANTS--------------------#
-# mesh size
-N      = 500
-# domain ]-L ; H[, (mL=-L)
-mL     = -1
-H      =  10
-# space step 
-dx     = (H-mL)/N
-print "dx", dx
-# time step
-dt     = 0.5*dx
-print "dt",dt
-# Number of time steps
-Ntime = 4000
-# constants 
-me     = 1#9.11e-31               #electron mass (kg)
-e      = -1#1.6e-19              #electron charge (coulombs)
-eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 0                       #friction
-B0     = 0#0.95                        #given
-c      = 1#3e8 
-
-
-
-#alpha(-L)
-alphamL = 2
-
-#-------------airy functions------------------#
-#return A
-#def airy_one(x):
-#    [A,B,C,D] = airy(x)
-#    return A
-#return A'
-#def airy_two(x):
-#    [A,B,C,D] = airy(x)
-#    return B
-#-----------------------------------------------#
-
-#-------------------------- NE --------------------------#
-# Ne constants definition
-wc    = abs(e)*B0/me
-print "omega_c" ,wc
-def Ne(x) : 
-    return 7#(2*B0)/(1+exp(-x)) ;
-    
-
-omega = np.sqrt(3)
-wp = np.sqrt(7)
-
-gamma = 2
-#---------------------------------------------------------#
-
-#--------------G for left BC -------------------#
-alpha = 1
-
-def g(t) : 
-    #return np.exp(complex(0,omega*t))*np.exp(-gamma*mL)*(-gamma+complex(0,alphamL))
-    return 1/2*(1+tanh((t-2)/0.1))*np.exp(omega*t*complex(0,1))
-
-print g(0)
-#-----------------------------------------------#
[…]

### 2014-10-23 time_dependant_pb_Nefunc_v2.py

@@ -1,221 +1,0 @@
-#!/usr/bin/python
-# -*- coding: utf-8 -*-
-
-from __future__ import division
-import os
-import time
-import numpy as np
-from pylab import *
-import scipy.io
-from scipy.special import airy
-import copy
-
-#---------------CONSTANTS--------------------#
-# mesh size
-N      = 500
-# domain ]-L ; H[, (mL=-L)
-mL     = -1
-H      =  200
-# space step 
-dx     = (H-mL)/N
-print "dx", dx
-# time step
-dt     = 0.5*dx
-print "dt",dt
-# Number of time steps
-Ntime = 5000
-# constants 
-me     = 1#9.11e-31               #electron mass (kg)
-e      = -1#1.6e-19              #electron charge (coulombs)
-eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 0                       #friction
-B0     = 1 #0.95                        #given
-c      = 1#3e8 
-
-
-
-#alpha(-L)
-alphamL = 2
-
-#-------------airy functions------------------#
-#return A
-#def airy_one(x):
-#    [A,B,C,D] = airy(x)
-#    return A
-#return A'
-#def airy_two(x):
-#    [A,B,C,D] = airy(x)
-#    return B
-#-----------------------------------------------#
-
-#-------------------------- NE --------------------------#
-# Ne constants definition
-wc    = abs(e)*B0/me
-print "omega_c" ,wc
-def Ne(x) : 
-    return 1#(2*B0)/(1+exp(-x)) ;
-    
-
-omega = 0
-wp = 1
-
-gamma = 2
-#---------------------------------------------------------#
-
-#--------------G for left BC -------------------#
-alpha = 1
-
-def g(t) : 
-    #return np.exp(complex(0,omega*t))*np.exp(-gamma*mL)*(-gamma+complex(0,alphamL))
-    return -1/2*(1+tanh((t-2)/0.1))*np.exp(omega*t*complex(0,1)) 
-
-print g(0)
-#-----------------------------------------------#
[…]

### 2014-10-23 time_dependant_pb_omega.py

@@ -1,289 +1,0 @@
-#!/usr/bin/python
-# -*- coding: utf-8 -*-
-
-from __future__ import division
-import os
-import time
-import numpy as np
-from pylab import *
-import scipy.io
-from scipy.special import airy
-import copy
-
-#---------------CONSTANTS--------------------#
-# mesh size
-N      = 400
-# domain ]-L ; L[, (mL=-L)
-mL     = -20
-pL      =  20
-# space step 
-dx     = (pL-mL)/N
-print "dx", dx
-# time step
-dt     = 0.5*dx
-print "dt",dt
-# Number of time steps
-Ntime = 100
-# constants 
-me     = 1#9.11e-31               #electron mass (kg)
-e      = -1#1.6e-19              #electron charge (coulombs)
-eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 0                    #friction
-B0     = 1#0.95                        #given
-c      = 1
-
-
-#-------------airy functions------------------#
-#return A
-#def airy_one(x):
-#    [A,B,C,D] = airy(x)
-#    return A
-#return A'
-#def airy_two(x):
-#    [A,B,C,D] = airy(x)
-#    return B
-#-----------------------------------------------#
-
-#-------------------------- NE --------------------------#
-# Ne constants definition
-#wc    = abs(e)*B0/me
-#print "omega_c" ,wc
-def Ne(x) : 
-    if (x < -10) :
-        return 0
-    elif (x >= -10) and (x <= 10 ):
-        return 36*(x+10)/20
-    else :
-        return 36
-    
-
-omega = 3
-
-
-gamma = 2
-#---------------------------------------------------------#
-
-#--------------G for left BC -------------------#
-alpha = 1
-
-def g(t) : 
-    #return np.exp(complex(0,omega*t))*np.exp(-gamma*mL)*(-gamma+complex(0,alphamL))
[…]

### 2014-10-23 time_dependant_pb_v2.py

@@ -1,243 +1,0 @@
-#!/usr/bin/python
-# -*- coding: utf-8 -*-
-
-from __future__ import division
-import os
-import time
-import numpy as np
-from pylab import *
-import scipy.io
-from scipy.special import airy
-import copy
-
-#---------------CONSTANTS--------------------#
-# mesh size
-N      = 500
-# domain ]-L ; H[, (mL=-L)
-mL     = -1
-H      =  10
-# space step 
-dx     = (H-mL)/N
-print "dx", dx
-# time step
-dt     = 0.5*dx
-print "dt",dt
-# Number of time steps
-Ntime = 1000
-# constants 
-me     = 1#9.11e-31               #electron mass (kg)
-e      = -1#1.6e-19               #electron charge (coulombs)
-eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 0                   #friction
-B0     = 0                      #given
-c      = 1#3e8 
-
-
-
-#alpha(-L)
-alphamL = 2
-
-#-------------airy functions------------------#
-#return A
-#def airy_one(x):
-#    [A,B,C,D] = airy(x)
-#    return A
-#return A'
-#def airy_two(x):
-#    [A,B,C,D] = airy(x)
-#    return B
-#-----------------------------------------------#
-
-#-------------------------- NE --------------------------#
-# Ne constants definition
-wc    = e*abs(B0)/me
-print "omega_c" ,wc
-# Ne function
-def Ne(x) :  
-    a     = wc/(c*(wc*wc-c*c))
-    b     = 1/(wc*wc-c*c)
-    kappa = e*e/(eps0*me)
-
-    a2    = (a*a-b*b)*kappa*kappa
-    a1    = (2*kappa*b + b*x*kappa) 
-    a0    = 1 + x
-    
-    #D     = a1*a1 + 4 * a2 * a0
-    
-    return  - a1 /(2*a2)
-
-#NE    = map(lambda x: 3*me/(e*e),  X)
-omega = np.sqrt(3)
-wp = np.sqrt(7)
-gamma = 2
-#---------------------------------------------------------#
-
-#--------------G for left BC -------------------#
[…]

### 2014-10-27 solve_mH1_td_compliant.m
taking into account the non-diagonal terms (closer to the time domain implementation)

@@ -1,4 +1,4 @@
-function [e1, e2,M,x, Kstiff, Mmass]=solve_mH1(dx,lambda, nu, uniform)
+function [e1, e2,M,x, Kstiff, Mmass]=solve_mH1_td_compliant(dx,lambda, nu, nu_delta, uniform)
 
 %mesh generation
 L= 19.99267220322423120; %20!!!
@@ -12,7 +12,7 @@ phi=-pi/2:dx:pi/2;
 
 end
 tic
-[A,B,D]=construct_block_matrix(x,nu,lambda);
+[A,B,D]=construct_block_matrix(x,nu,nu_delta,lambda);
 time_passed=toc();
 display (strcat(num2str(time_passed),' for the construction of the matrix'));
 r=construct_rhs(x);
@@ -71,30 +71,38 @@ e2=sol(2:2:end);
 end
 
 
+function n=n_e(x)
+n=0.2;
+end
 
-
+function [omega, omega_c]=main_parameters()
+omega=1;
+omega_c=0;
+end
 
 
 function a=alpha(x)
+[omega, omega_c]=main_parameters();
+n=n_e(x);
+a=omega^2*(1-n_e/(omega^2-omega_c^2));
 
-%a=zeros(size(x));
-%a(x<=-10)=1;
-%P=(x<=5)&(x>-10);
-%a(P)=-x(P)/10;
-%a(x>5)=-1/2;
-a=0.9;%0.8*ones(size(x));
 end
 
 function delta=delta(x)
+[omega, omega_c]=main_parameters();
+n=n_e(x);
+delta=omega*omega_c*n_e/(omega^2-omega_c^2);
+end
 
+function nu_a=nu_alpha(x)
+[omega, omega_c]=main_parameters();
+n=n_e(x);
+nu_a=omega^2*n_e*(omega^2+omega_c^2)./(omega^2-omega_c^2);
+end
 
-delta=zeros(size(x));
-%delta(x<=-10)=0;
-%P=(x<=5)&(x>-10);
-%delta(P)=(1+x(P)/10)*1e-2;
-%delta(x>5)=3/2*1e-2;
-%delta=sqrt(x.^2+1).*sqrt(x.^2+1+x);
-delta=0;
+function nu_delta=nu_delta
+[omega, omega_c]=main_parameters();
+nu_delta=omega^2*2*omega/(omega^2-omega_c^2);
 end
 
[…]

### 2014-12-12 report/proc.tex
report folder

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}

\begin{document}
\input{intro}
%\input{}

\begin{thebibliography}{99}
\bibitem{stable_yee_plasma_current} F. da Silva, M. Campos Pinto, B. Despres, S. Heuraux, Stable Coupling of the Yee Scheme with a Linear Current Model,
2014
\end{thebibliography}

\end{document}

### 2014-12-16 lanceur_airy.py
experiments_absorptions: might be an error

@@ -10,40 +10,52 @@ import copy
 import sub
 #---------------CONSTANTS--------------------#
 # mesh size
-N      = 2048
+N      = 420;
 # domain ]-L ; L[, (mL=-L)
-mL     = -20
+mL     = -0.5
 pL      = 10
 # space step 
-dx     = (pL-mL)/(N-1)
+dx     = (pL-mL)/(N)
 print "dx", dx
 # time step
 dt     = 0.5*dx
 print "dt",dt
 # Number of time steps
-Ntime = 1e6
+Ntime = 2e7
 # constants 
 me     = 1#9.11e-31               #electron mass (kg)
 e      = -1#1.6e-19              #electron charge (coulombs)
 eps0   = 1#8.85e-12               #permeability  (F/m)
-nu     = 0                  #friction
-B0     = 0#0.95                        #given
+nu     = 0.001;#1e-2                  #friction
+B0     = 0;#0.5#0.95                        #given
 c      = 1
 
+omega = 1
+omega_c = e*B0;
 
 #-------------------------- NE --------------------------#
 
 def Ne(x) : 
-	return 0.1;
-#    if (x < -10) :
-#        return 0
+	return 1+x;
+#	return 1+x;
+#	d=sqrt((2*omega*omega+x)**2-4*(x+omega**2)*(omega**2-omega_c**2));
+#	return 0.5*(2*omega**2+x+d);
+#	return (1+x);
+#    if (x < -1) :
+#        return 0.5*0.75;
+#    elif (x>=-1) and (x<5):
+#	return 0.75*(1+x/2);
+#    else:
+#	return 7/2*0.75;
+
 #    elif (x >= -10) and (x <= 10 ):
 #        return 36*(x+10)/20
 #    else :
 #        return 36
     
 
-omega = 1
+
+
 
 
 gamma = 2
@@ -117,7 +129,7 @@ alphamL = 1
 
 
 
-sub.tdp.tdp_sub(dx,dt,Ntime,me,e,eps0,nu,B0,omega,NE,NEy,ux,H,Ex,Ey,uy,X,X12)
+sub.tdpn.tdp_sub(dx,dt,Ntime,me,e,eps0,nu,B0,omega,NE,NEy,ux,H,Ex,Ey,uy,X,X12)
 
 
 #plot2(X12,Ey,X,Ex,X,H,X,ux,T,Et,T,nEx,'b','$E$','E')

### 2014-12-16 solve_mH1.m

@@ -1,8 +1,8 @@
 function [e1, e2,M,x, Kstiff, Mmass]=solve_mH1(dx,lambda, nu, uniform)
 
 %mesh generation
-L= 19.99267220322423120; %20!!!
-H=10.007327796775769;%10!!!
+L=5; %20!!!
+H=19;%10!!!
 if uniform
 x=-L:dx:H;
 else
@@ -71,31 +71,51 @@ e2=sol(2:2:end);
 end
 
 
+function n=n_e(x)
+n=zeros(size(x));
+[omega, omega_c]=main_parameters();
 
+n(x<-0.5)=0.25;
+P=(x>=-0.5 & x<=9);
+n(P)=(1+x(P))/2;
+n(x>9)=5;
+%if omega_c==0
+%    d=x;
+%else
+%    d=sqrt((2*omega^2+x).^2-4*(x+omega^2)*(omega^2-omega_c^2));
+%end
+%n=0.5*(2*omega^2+x+d);%for omega=1
 
+%n(x<-1)=0.5*0.75;
+%P=(x>=-1)&(x<5);
+%n(P)=0.75*(1+x(P)/2);
+%P=(x>=5);
+%n(P)=7/2*0.75;
+end
+
+function [omega, omega_c]=main_parameters()
+omega=1;
+omega_c=sqrt(0.5);
+end
 
 
 function a=alpha(x)
+[omega, omega_c]=main_parameters();
+n=n_e(x);
+a=omega^2*(1-n/(omega^2-omega_c^2));
 
-%a=zeros(size(x));
-%a(x<=-10)=1;
-%P=(x<=5)&(x>-10);
-%a(P)=-x(P)/10;
-%a(x>5)=-1/2;
-a=0.9;%0.8*ones(size(x));
 end
 
 function delta=delta(x)
-
-
-delta=zeros(size(x));
-%delta(x<=-10)=0;
-%P=(x<=5)&(x>-10);
-%delta(P)=(1+x(P)/10)*1e-2;
-%delta(x>5)=3/2*1e-2;
-%delta=sqrt(x.^2+1).*sqrt(x.^2+1+x);
-delta=0;
+[omega, omega_c]=main_parameters();
+n=n_e(x);
+delta=omega*omega_c*n/(omega^2-omega_c^2);
 end
+
+
+
+
+
 
 %since the matrices are symmetric tridiagonal, each matrix constructor returns 
 %a vector K of size $L\times 2$, where L is the size of the matrix
[…]

### 2014-12-16 solve_mH1_td_compliant.m

@@ -1,8 +1,8 @@
 function [e1, e2,M,x, Kstiff, Mmass]=solve_mH1_td_compliant(dx,lambda, nu, nu_delta, uniform)
 
 %mesh generation
-L= 19.99267220322423120; %20!!!
-H=10.007327796775769;%10!!!
+L=3; %20!!!
+H=22;%10!!!
 if uniform
 x=-L:dx:H;
 else
@@ -71,33 +71,40 @@ e2=sol(2:2:end);
 end
 
 
+
 function n=n_e(x)
-n=0.2;
+n=zeros(size(x));
+n(x<-1)=0.5*0.75;
+P=(x>=-1)&(x<5);
+n(P)=0.75*(1+x(P)/2);
+P=(x>=5);
+n(P)=7/2*0.75;
 end
+
 
 function [omega, omega_c]=main_parameters()
 omega=1;
-omega_c=0;
+omega_c=-0.5;
 end
 
 
 function a=alpha(x)
 [omega, omega_c]=main_parameters();
 n=n_e(x);
-a=omega^2*(1-n_e/(omega^2-omega_c^2));
+a=omega^2*(1-n/(omega^2-omega_c^2));
 
 end
 
 function delta=delta(x)
 [omega, omega_c]=main_parameters();
 n=n_e(x);
-delta=omega*omega_c*n_e/(omega^2-omega_c^2);
+delta=omega*omega_c*n/(omega^2-omega_c^2);
 end
 
 function nu_a=nu_alpha(x)
 [omega, omega_c]=main_parameters();
 n=n_e(x);
-nu_a=omega^2*n_e*(omega^2+omega_c^2)./(omega^2-omega_c^2);
+nu_a=omega^2*(omega^2+omega_c^2)./(omega^2-omega_c^2)*n
 end
 
 function nu_delta=nu_delta

### 2014-12-16 tdpn.f90

@@ -1,7 +1,7 @@
 !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 ! this file contains the program to compute the time dependant pb for Xmode eq
 !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-module tdp
+module tdpn
 implicit none 
 contains
   subroutine Kcoeff(x,K1,K2,K1x,K2x,nu,dt,e,me,eps0,B0)
@@ -21,15 +21,15 @@ contains
     real(8), dimension(0:N-1), intent(in) :: X12, uy, Ey
     character (len=90) :: filename
     integer :: i
-    write (filename, '( "/UMA/tmp/maryna/password/ux", i7.7, ".data" )' ) t
+    write (filename, '( "/UMA/tmp/maryna/password0_airy_old/ux", i8.8, ".data" )' ) t
     open(10, file = filename)
-    write (filename, '( "/UMA/tmp/maryna/password/Ex", i7.7, ".data" )' ) t
+    write (filename, '( "/UMA/tmp/maryna/password0_airy_old/Ex", i8.8, ".data" )' ) t
     open(11, file= filename)
-    write (filename, '( "/UMA/tmp/maryna/password/H", i7.7, ".data" )' ) t
+    write (filename, '( "/UMA/tmp/maryna/password0_airy_old/H", i8.8, ".data" )' ) t
     open(12, file=filename)
-    write (filename, '( "/UMA/tmp/maryna/password/uy", i7.7, ".data" )' ) t
+    write (filename, '( "/UMA/tmp/maryna/password0_airy_old/uy", i8.8, ".data" )' ) t
     open(13, file = filename)
-    write (filename, '( "/UMA/tmp/maryna/password/Ey", i7.7, ".data" )' ) t
+    write (filename, '( "/UMA/tmp/maryna/password0_airy_old/Ey", i8.8, ".data" )' ) t
     open(14, file = filename)
     do i = 0, N-1
[…]

### 2014-12-16 lanceur2.py
some changes

@@ -10,31 +10,31 @@ import copy
 import sub
 #---------------CONSTANTS--------------------#
 # mesh size
-N      = 512
+N      = 2500
 # domain ]-L ; L[, (mL=-L)
-mL     = -20
-pL      = 10
+mL     = -5
+pL      = 5
 # space step 
-dx     = (pL-mL)/(N-1)
+dx     = (pL-mL)/(N)
 print "dx", dx
 # time step
 dt     = 0.5*dx
 print "dt",dt
 # Number of time steps
-Ntime = 3e6
+Ntime = 5e4
 # constants 
 me     = 1#9.11e-31               #electron mass (kg)
 e      = -1#1.6e-19              #electron charge (coulombs)
 eps0   = 1#8.85e-12               #permeability  (F/m)
 nu     = 0                  #friction
-B0     = 0#0.95                        #given
+B0     = 0.1#0.95                        #given
 c      = 1
 
 
 #-------------------------- NE --------------------------#
 
 def Ne(x) : 
-	return 0.1;
+	return 0.8;
 #    if (x < -10) :
 #        return 0
 #    elif (x >= -10) and (x <= 10 ):

### 2014-12-16 solve_mH1.m

@@ -1,8 +1,8 @@
 function [e1, e2,M,x, Kstiff, Mmass]=solve_mH1(dx,lambda, nu, uniform)
 
 %mesh generation
-L= 19.99267220322423120; %20!!!
-H=10.007327796775769;%10!!!
+L=7;%19.99267220322423120; %20!!!
+H=10;%10.007327796775769;%10!!!
 if uniform
 x=-L:dx:H;
 else
@@ -71,31 +71,66 @@ e2=sol(2:2:end);
 end
 
 
-
-
-
-
 function a=alpha(x)
+
+a=zeros(size(x));
+a(x<=-5)=5;
+P=(x<=2)&(x>-5);
+a(P)=-x(P);
+a(x>2)=-2;
+end
+
+function delta=delta(x)
+delta=zeros(size(x));
+delta(x<=-5)=0;
+P=(x<=2)&(x>-5);
+delta(P)=1/7*x(P)+5/7;
+delta(x>2)=1;
+%delta=sqrt(x.^2+1).*sqrt(x.^2+1+x);
+
+end
+
+
+
+%function a=alpha(x)
 
 %a=zeros(size(x));
 %a(x<=-10)=1;
 %P=(x<=5)&(x>-10);
 %a(P)=-x(P)/10;
 %a(x>5)=-1/2;
-a=0.9;%0.8*ones(size(x));
-end
-
-function delta=delta(x)
 
 
-delta=zeros(size(x));
+
+%a=zeros(size(x));
+%a(x<=-10)=10;
+%P=(x<=5)&(x>-10);
+%a(P)=-x(P);
+%a(x>5)=-5;
+
+%end
+
+%function delta=delta(x)
+
+
+%delta=zeros(size(x));
 %delta(x<=-10)=0;
 %P=(x<=5)&(x>-10);
 %delta(P)=(1+x(P)/10)*1e-2;
 %delta(x>5)=3/2*1e-2;
 %delta=sqrt(x.^2+1).*sqrt(x.^2+1+x);
-delta=0;
-end
+%delta=0;
+
+%delta(x<=-10)=0;
+%P=(x<=5)&(x>-10);
+%delta(P)=(10+x(P))*0.1;
+%delta(x>5)=1.5;
+
+%delta(x<=-10)=0;
+%P=(x<=5)&(x>-10);
+%delta(P)=4/30*x(P)+4/3;
+%delta(x>5)=2;
+%end
 
 %since the matrices are symmetric tridiagonal, each matrix constructor returns 
[…]

### 2014-12-16 tdp.f90

@@ -96,7 +96,7 @@ contains
     do iter = 0, Ntime
        t = (iter+1.0)*dt
        
-       H12(0) = sin(omega*(t-dt/2.0))*(exp(-12*(t-dt/2)*(t-dt/2)))
+       H12(0) = sin(omega*(t-dt/2.0))*(exp(-100*(t-dt/2-1)*(t-dt/2-1)))
        do i = 1, N-1
           H12(i) = H(i) - (dt/dx)*(Ey(i)-Ey(i-1))
        end do
@@ -147,7 +147,7 @@ contains
           En = En+ Ey(i)*Ey(i)+Ex(i)*Ex(i) + H12(i)*H12(i)
        end do
        !if (iter>=2e5) then
-       ! call writeall(iter,N,Ntime,X,X12,ux,uy,Ex,Ey,H)            
+       call writeall(iter,N,Ntime,X,X12,ux,uy,Ex,Ey,H)            
        !end if
        write(15,*) iter*dt, En
        if (maxval(H)<1E-10) then

### 2014-12-17 report/intro.tex
add macros files (usefull for eq typing, can script it out later if needed), copied password_00.tex into equation files, corrections to come

\section{Introduction}

We consider the set of Maxwell equations with a linear current in two dimensions \cite{stable_yee_plasma_current}
 with absorption terms
 \begin{align*}
\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\\
\mu_0\partial_t H+\partial_x E_y-\partial_y E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
\end{align*}
posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. The boundary conditions 
\begin{align*}
 H|_{-L}=g(t).
\end{align*}
\subsection{Boundary condition}
Robin Boundary condition at the left boundary of the domain
\be
-curl \E -\imath \sqrt{\alpha(-{ L})}\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath \sqrt{\alpha(-{ L})}\E_{inc} \wedge \n,
\ee
where  $\E_{inc} = \exp \left(\imath \sqrt{\alpha(-L)}x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$

$curl \E = 0$ at the right boundary

### 2014-12-17 report/numerics.tex

\section{Discretization}
\subsection{Discretization of the Frequency Domain Problem}

We look for a ratio $h(\nu)$ that would ensure that 
\begin{align*}
 \|E^{\nu}_{1}-E^{\nu,h}_{1}\|_{L_{2}(\Omega)}<\epsilon,
\end{align*}
for a fixed $\epsilon>0$.

To conjecture the dependence of $h(\nu)$, we suggest the following (not rigorous argument). 
Recall that for the problem (\ref{}) the C\'ea's lemma gives
\begin{align*}
 \|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V},
\end{align*}
where $C_c$ is the continuity and $C_i$ is the coercivity constants.
\begin{lemma}{}
Let $\alpha(x), \; \delta(x)$ satisfy
\begin{align*}
\end{align*}
Then, for all $\nu_*>0$ and for all $\nu>\nu_*$, the error between the numerical solution $\mathbf{E}^{h,\nu}$ and the 
solution $\mathbf{E}^{\nu}$
\begin{align*}
\|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|_{V}\leq 
\end{align*}
\end{lemma}
\begin{proof}
The C\'ea's lemma states 
\begin{align*}
 \|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V},
\end{align*}
where $C_c$ is the continuity and $C_i$ is the coercivity constants.
Indeed,
\begin{align*}
 \min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}\leq \min_{\mathbf{v}\in V_h}\|\mathbf{E}-I^{h}\mathbf{v}\|,
\end{align*}
where $I^{h}\mathbf{v}$ is an interpolation operator. The estimates from \cite[Chapter 0]{Brenner_Scott} give us
\begin{align*}
 \|E_1-I^{h}E_1\|_{L_{2}(\Omega)}\leq Ch^2|E_1''|_{L_{2}(\Omega)},\\
 \|E_2-I^{h}E_2\|_{H_{1}(\Omega)}\leq Ch|E_2''|_{H_{1}(\Omega)}.
\end{align*}
To obtain these bounds, we require an explicit bound on $E_1, \; E_2$. In \cite{Despers et al Hybrid} 
it was shown that 
%\begin{align*}

%\end{align*}

\end{proof}

\subsection{Discretization of the Time Domain Problem}
\section{Numerical Experiments}
\subsection{Frequency Domain}
\subsection{Time Domain}

### 2015-01-14 report/attic/numerics.tex
added numerics.tex file which contains a more detailed description of one of the experiments

\documentclass{article}
\usepackage{amsfonts,graphicx,amssymb}%amsfonts pour les \mathbb
\usepackage{amsmath,amsthm,amssymb}
\begin{document}
\section{Discretization}

\section{Numerical Experiments}
This section is organized as follows. The first part is dedicated to the numerical implementation
of the frequency domain formulation (\ref{}). We study the convergence of this formulation and the behaviour 
of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
performed on a laptop with ... CPU, with the help of the code written in Octave 
The second part of the section deals with the question of the equivalence of the limiting absorption and limited amplitude 
principle.
\subsection{Frequency Domain Problem}
This section is

\subsection{Discretization of the Frequency Domain Problem}

Let us consider the case of the resonance, more precisely, we consider sufficiently smooth
$\alpha,\delta$, s.t. $\alpha(0)=0$ and $\delta(0)\neq 0$, and the solvability conditions 
of Theorem \ref{}  are satisfied. 
For simplicity, let us consider 
\begin{align}
\label{eq:cond}
 \alpha(x)=-x \text{  in some neighbourhood of $0$ }.
\end{align}

Given the space $\mathbf{V}_{h}=S_{h}^{1}\times S_{h}^{1}$, with $S_{h}^{1}$ consisting of piecewise-linear (hat) functions, we look for a ratio $h(\nu)$ that would ensure that the absolute error 
\begin{align}
\label{eq:problem1}
\|E^{\nu}_{1}-E^{\nu,h}_{1}\|_{L_{2}(\Omega)}<\epsilon,
\end{align}
given a fixed value of $\epsilon>0$.

We use the following well-known facts:
\begin{itemize}
 \item The C\'ea's lemma applied to the problem (\ref{}); here $C_c$ is the continuity and $C_i$ is the coercivity constants:
\begin{align}
\label{eq:cea}
\begin{split}
 \|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|_{V}\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}\\
 \leq \nu^{-1}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}.
 \end{split}
\end{align}
The last inequality follows from Theorem \ref{}.  
\item The form of the exact solution to the problem (\ref{}):
\begin{align}
\label{eq:exact}
 E_{1}^{\nu}=E_{2}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f(x)}{\alpha(x)+i\nu},
\end{align}
for some $f(x)\in L_{2}(\Omega)$.
\item The estimate from \cite[Chapter 0]{Brenner_Scott} on the rate of convergence of the interpolation 
\begin{align}
\label{eq:bsc}
 \|v-I^{h}v\|_{L_{2}(\Omega)}\leq Ch^2|v''|_{L_{2}(\Omega)},\; C>0,\\
 %\|v-I^{h}v\|_{H_{1}(\Omega)}\leq Ch|v''|_{L_{2}(\Omega)},\; C>0, 
\end{align}
where $I^{h}v$ is an interpolation operator onto $S_{h}^{1}$.
\end{itemize}
For $E_{1}^{\nu},\;f(x)$ in (\ref{eq:exact}) being sufficiently smooth, 
\begin{align*}
 \frac{d^2}{dx^2}E_{1}^{\nu}=\frac{f''}{\alpha+i\nu}-2\frac{f'\alpha'}{(\alpha+i\nu)^2}+\frac{f\alpha''}{(\alpha+i\nu)^3},
\end{align*}
from which, together with (\ref{eq:cond}), it follows that there exists $c>0$ s.t. for all sufficiently small $\nu$ 
\begin{align*}
 \left|  \frac{d^2}{dx^2}E_{1}^{\nu}\right|_{L_2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx\\
 &=c\left.
 \left(\frac{x}{4(x^2+\nu^2)^2}\nu^{-2}+\frac{3x}{8(x^2+\nu^2)}\nu^{-4}+\frac{3}{8}\nu^{-5}\operatorname{atan}\frac{x}{\nu}\right)\right|_{-L}^{H}\\
 &\leq C\nu^{-5},\; 
\end{align*}
where $C>0$ does not depend on $\nu$. This, together with the estimates (\ref{eq:cea}) and (\ref{eq:bsc}), results in 
\begin{align*}
 \|E^{\nu}_{1}-E^{\nu,h}_{1}\|_{L_{2}(\Omega)}\leq C\nu^{-\frac{7}{2}}h^2,
\end{align*}
from which it follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as $\alpha_{\epsilon}\nu^{\frac{7}{4}}$, 
where $\alpha_{\epsilon}>0$ depends on $\epsilon$ but does not depend on $\nu$.

Let us check whether this holds true. 
To do so, we conduct the following numerical experiment.

We can show that 
\begin{align*}
 \|E^{\nu}_{1}\|_{L_{2}(\Omega)}\leq \frac{C}{\sqrt{\nu}},\; C>0, 
\end{align*}
and thus the relative error control
\begin{align*}
 \frac{\|E^{\nu}_{1}-E^{\nu,h}_{1}\|_{L_{2}(\Omega)}}{\|E^{\nu}_{1}\|_{L_{2}(\Omega)}}\leq \epsilon
\end{align*}
can be ensured by choosing $h$ as $\beta_{\epsilon}\nu^{\frac{3}{4}}$.

\subsection{Discretization of the Time Domain Problem}
\section{Numerical Experiments}
\subsection{Frequency Domain}
\subsection{Time Domain}
\end{document}

### 2015-01-14 report/attic/numerics.tex
1) added TODO to clarify the question of regularity of the tensor of dielectric permittivity; 2) in numerics.tex: added/modified sections on variational formulation and implementation

@@
-\documentclass{article}
+\documentclass[proc]{edpsmath}
 \usepackage{amsfonts,graphicx,amssymb}%amsfonts pour les \mathbb
 \usepackage{amsmath,amsthm,amssymb}
+\newcommand{\bs}{\left\{}
+\newcommand{\es}{\right.}
+\newcommand{\ba}{\begin{array}}
+\newcommand{\ea}{\end{array}}
+\newcommand{\be}{\begin{equation}}
+\newcommand{\ee}{\end{equation}}
+\newcommand{\ora}{\overrightarrow}
+\newcommand{\x}{{\bf x}}
+\newcommand{\E}{{\bf E}}
+\newcommand{\n}{{\bf n}}
+\newcommand{\f}{{\bf f}}
 \begin{document}
 \section{Discretization}
+Clearly, the solution of the problem 
+\begin{align*}
+a(u, v)=(f,v)\text{ for all } v=(v_{1},v_{2})^{T}\in \mathbf{V}=V_1\times V_2, 
+\end{align*}
+is equivalent to the solution of
+\begin{align*}
+a(u,(v_{1},0)^{T})=(f,(v_{1},0)^{T}),\text{ for all } v_1\in V_1,\\
+a(u,(0,v_{2})^{T})=(f,(0,v_{2})^{T}),\text{ for all } v_2\in V_2.
+\end{align*}
+Thus, the variational formulation (\ref{}) can be rewritten as a system of two equations:
+\begin{align*}
+\begin{split}
+i\theta \displaystyle \int_{-L}^H (E_2' -\imath\theta E_1)\overline{\tilde E_1} - \int_{-L}^H \left((\epsilon_0 +\imath\nu \operatorname{Id}) \E\right)_{1} \overline{\tilde E}_{1}
+&=0,\\
+\displaystyle \int_{-L}^H (E_2' -\imath\theta E_1)\tilde {E_2'} - \int_{-L}^H\left( (\epsilon_0 +\imath\nu\operatorname{Id}) \E\right)_{2}\overline{\tilde{E}}_{2}
+  - \imath \sqrt{\alpha(-L)} E_2 (-L) \tilde E_2 (-L) &= -g_{inc} (-L) \overline{( \tilde E_2(-L) )},\\
+  \text{ for all } \tilde E_{1}\in L_{2}(\Omega), \; \tilde{E}_{2}\in H_{1}(\Omega).
+  \end{split}
+\end{align*}
+Inserting an explisit expression for the dielectric permittivity tensor 
+\be \label{eq:epsilonmu}
+ \epsilon_0(x) =
+\left(
+\begin{array}{cc}
+\alpha(\x) & \imath \delta (\x)\\
+-\imath \delta (\x) & \alpha(\x)
+\end{array}
+\right)
+\ee
+into the above, we obtain
+\begin{align}
+\label{eq:var_form2}
+\begin{split}
+ i\theta \displaystyle \int_{-L}^H (E_2' -\imath\theta E_1)\overline{\tilde E_1} - 
+ \int_{-L}^H \left((\alpha+i\nu)E_1+\imath\delta E_2\right)_{1} \overline{\tilde E}_{1}
+&=0,\\
+\int_{-L}^H (E_2' -\imath\theta E_1)\tilde {E_2'} -
+\int_{-L}^H\left( -\imath \delta E_1+(\alpha+i\nu) E_2\right)_{2}\overline{\tilde{E}}_{2}
+  - \imath \sqrt{\alpha(-L)} E_2 (-L) \tilde E_2 (-L) &= -g_{inc} (-L) \overline{( \tilde E_2(-L) )},\\
+  \text{ for all } \tilde E_{1}\in L_{2}(\Omega), \; \tilde{E}_{2}\in H_{1}(\Omega).
+  \end{split}
+\end{align}
+
+\begin{remark}
+Let us assume that the operator
+\begin{align*}
+M\psi = \frac{i\delta}{(\alpha+i\nu)}\psi
+\end{align*}
+defines an isomorphism from $L_{2}(\Omega)$ to $L_{2}(\Omega)$. 
+Given $E_1,\; E_2\in L_{2}(\Omega)$, the function $\mathcal{F}=\frac{i\delta}{(\alpha+\imath\nu)}\left((\alpha+\imath\nu)E_{1}+i\delta E_{2}\right)$ also belongs to $L_{2}(\Omega)$. 
+If $E_1,\; E_2$ satisfy the problem (\ref{eq:var_form2}) for $\theta=0$, the function $\mathcal{F}=0$, 
+i.e.
+\begin{align*}
+ (\mathcal{F},\tilde{E}_{2})_{L_{2}}=\int_{-L}^{H}\left(\imath\delta E_{1}-\delta^2(\alpha+i\nu)^{-1} E_{2}\right)\overline{\tilde E}_{2}=0,
+\end{align*}
+for all $\overline{\tilde E}_2\in H_{1}(\Omega)$. Adding this to the second expression of (\ref{eq:var_form2}), we obtain 
+the variational formulation for $E_2$, which coincides with the variational formulation for the Helmholtz equation. The well-posedness 
+of this problem had been studied in \cite{}. 
+Hence, we can add the second expression (\ref{eq:E2}) to
+\begin{align*}
+\int_{-L}^{H}\left(i\delta E_{1}-\delta^2(\alpha+i\nu)^{-1} E_{2}\right)\overline{\tilde E}_{2}=0
+\end{align*}
+to obtain the variational formulation for $E_{2}$, which will coincide with the variational formulation for the Helmholtz equation, and thus will be well-posed 
+(see the thesis \cite{thesis_lmig}).
+The estimates from \cite{thesis_lmig} can be employed to bound $\|E_{1}\|_{L_{2}}$.
+\end{remark}
+
+Introducing two basis spaces, $V_{E_{1}}=\{\psi_{j}\}_{j=1}^{N_{1}}$ and $V_{E_{2}}=\{\phi_{i}\}_{i=1}^{N_{2}}$, we look for the solution of the problem (\ref{}) in the form:
+\begin{align*}
+E_{1}=\sum\limits_{k=1}^{N_{1}}e_{1k}\psi_{k},\; E_{2}=\sum\limits_{k=1}^{N_{2}}e_{2k}\phi_{k}.
+\end{align*}
+Substituting $\tilde{E}_{1}=\psi_{m}, \; m=1,\ldots,N_{1}$ and $\tilde{E}_{2}=0$ into the variational formulation (\ref{}), we obtain:
+\begin{align*}
+i\theta\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}\bar{\psi}_{m}dx+\theta^2\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx\\
+-\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{k}\bar{\psi}_{m}dx-i\sum\limits_{1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\delta(x)\phi_{k}(x)\bar{\psi}_{m}dx=0.
+\end{align*}
+Similarly, for $\tilde{E}_{1}=0$ and $\tilde{E}_{2}=\phi_{\ell},\; \ell=1,\ldots, N_{2}$:
+\begin{align*}
+\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx-i\theta\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}(x)\bar{\phi}'_{\ell}(x)dx\\
++i
+\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\delta(x)\psi_{k}\bar{\phi}_{m}dx-\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\phi_{k}\bar{\phi}_{m}dx\\
+-
+i\lambda\sum\limits_{k=1}^{N_{2}}e_{2k}\phi_{k}(-L)\bar{\phi}_{m}(-L)=-g_{inc}(x)\bar{\phi}_{m}(-L).
+\end{align*}
+After introduction 
+\begin{align*}
+\left(K^{\psi,\phi'}\right)_{mk}=\int\limits_{-L}^{H}\bar{\psi}_{m}\phi'_{k}dx,\qquad \left(M^{\psi}\right)_{mk}=\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx,\\
+\left(M^{\alpha,\psi}\right)_{mk}=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{m}\bar{\psi}_{k}dx, \qquad \left(M^{\delta,\psi,\phi}\right)_{mk}=\int\limits_{-L}^{H}\delta(x)\bar{\psi}_{m}\phi_{k}dx,\\
+K_{\ell k}=\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx,\qquad \left(M^{\alpha,\phi}\right)_{\ell k}=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\bar{\phi}_{\ell}\phi_{k}dx,\\
+I_{km}^{\Gamma}=\bar{\phi}_{m}(-L)\phi_{k}(-L),\\
+\boldsymbol{e}_{1}=\left(e_{11},\ldots,e_{1 N_{1}}\right)^{T},\; \boldsymbol{e}_{2}=\left(e_{21},\ldots,e_{2 N_{1}}\right)^{T},\\
+\boldsymbol{0}_{n} \text{ is an $n$-dimensional zero column vector}.
+\end{align*}
+the above system of equations can be rewritten in an antisymmetric block form:
+\begin{align*}
+\left(\begin{matrix}
+\theta^2 M_{\psi}-M^{\alpha,\psi} & i\theta K^{\psi,\phi'}-i M^{\delta,\psi,\phi} \\
+-i\theta (K^{\psi,\phi'})^{*}+i (M^{\delta,\psi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
+\end{matrix}\right)
+\left(
+\begin{matrix}
+\boldsymbol{e}_1\\
+\boldsymbol{e}_2
+\end{matrix}
+\right)=-g_{inc}(-L)
+\left(
+\begin{matrix}
+\boldsymbol{0}_{N_{1}}\\
+\bar{\phi}_{1}(-L)\\
+\bar{\phi}_{2}(-L)\\
+\vdots\\
+\bar{\phi}_{N_{2}}(-L)
+\end{matrix}
+\right).
+\end{align*}
+This expression greatly simplifies when choosing $V_{E_{1}}=V_{E_{2}}=\left(\phi_{m}\right)_{m=1}^{N_{2}}$ and in the case $\theta=0$:
+\begin{align}
+\label{eq:simple_system}
+\left(\begin{matrix}
+M^{\alpha,\phi} & i M^{\delta,\phi,\phi} \\
+i (M^{\delta,\phi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
+\end{matrix}\right)
+\left(
+\begin{matrix}
+\boldsymbol{e}_1\\ 
+\boldsymbol{e}_2
+\end{matrix}
+\right)=-g_{inc}(-L)
+\left(
+\begin{matrix}
+\boldsymbol{0}_{N_{1}}\\
+\bar{\phi}_{1}(-L)\\
+\bar{\phi}_{2}(-L)\\
+\vdots\\
+\bar{\phi}_{N_{2}}(-L)
+\end{matrix}
+\right).
+\end{align}
+In all numerical experiments, we make use of the formulation, where the Lagrange piecewise-linear ('hat') finite elements are used as a 
+basis and trial space (see \cite{brenner}). We apply permutation to the above system 
+to obtain a 7-diagonal Hermitian matrix and solve the system with the Gauss back substitution algorithm.
 
@@
 of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
-performed on a laptop with ... CPU, with the help of the code written in Octave 
+performed on a laptop with 2.6GHz Intel Core i5 CPU, with the help of the code written in Octave (compatible with Matlab).
+
 The second part of the section deals with the question of the equivalence of the limiting absorption and limited amplitude 
-principle.
+principle. We compare the solutions obtained as $\nu\rightarrow 0$ with the help of our frequency domain code 
+and of the time domain code (computed for large values of time). 
+The time-domain code implements the scheme described in Section \ref{} and 
+is written in Fortran. 
 \subsection{Frequency Domain Problem}
-This section is
-
-\subsection{Discretization of the Frequency Domain Problem}
+\subsubsection{Validity of Implementation}
+\subsubsection{Solution of $X$-Mode Prolbem}
 
@@
 \begin{split}
- \|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|_{V}\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}\\
+ \|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|_{V}\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}
  \leq \nu^{-1}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}.
@@
 \begin{align*}
- \left|  \frac{d^2}{dx^2}E_{1}^{\nu}\right|_{L_2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx\\
- &=c\left.
- \left(\frac{x}{4(x^2+\nu^2)^2}\nu^{-2}+\frac{3x}{8(x^2+\nu^2)}\nu^{-4}+\frac{3}{8}\nu^{-5}\operatorname{atan}\frac{x}{\nu}\right)\right|_{-L}^{H}\\
- &\leq C\nu^{-5},\; 
+ \left|  \frac{d^2}{dx^2}E_{1}^{\nu}\right|_{L_2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
+ %\\
+ %&=c\left.
+ %\left(\frac{x}{4(x^2+\nu^2)^2}\nu^{-2}+\frac{3x}{8(x^2+\nu^2)}\nu^{-4}+\frac{3}{8}\nu^{-5}\operatorname{atan}\frac{x}{\nu}\right)\right|_{-L}^{H}
+ \leq C\nu^{-5},\; 
 \end{align*}

### 2015-01-14 solve_mH1.m

@@ -1,4 +1,4 @@
-function [e1, e2,M,x, Kstiff, Mmass]=solve_mH1(dx,lambda, nu, uniform)
+function [e1, e2,M,x, A,B,D]=solve_mH1(dx,lambda, nu, uniform)
 
 %mesh generation
 L=5; %20!!!
@@ -29,11 +29,7 @@ norm(M*sol-rhs)
 time_passed=toc();
 display(strcat(num2str(time_passed),' for the solution of the system of eqs'));
 
-%auxiliary matrices, namely the mass matrix and the stiffness matrix
-Kst=K_lpl(x);
-Mm=mass_matrixP1(x);
-Kstiff=spdiags([Kst(:,2) Kst(:,1) circshift(Kst(:,2),1)], -1:1, length(Kst), length(Kst));
-Mmass=spdiags([Mm(:,2) Mm(:,1) circshift(Mm(:,2),1)], -1:1, length(Mm), length(Mm));
+
 end
 
 

### 2015-01-19 report/numerics.tex
update in the numerics section according to Maryna's updates on the file in the attic

@@
 \section{Discretization}
-\subsection{Discretization of the Frequency Domain Problem}
+Clearly, the solution of the problem 
+\begin{align*}
+a(u, v)=(f,v)\text{ for all } v=(v_{1},v_{2})^{T}\in \mathbf{V}=V_1\times V_2, 
+\end{align*}
+is equivalent to the solution of
+\begin{align*}
+a(u,(v_{1},0)^{T})=(f,(v_{1},0)^{T}),\text{ for all } v_1\in V_1,\\
+a(u,(0,v_{2})^{T})=(f,(0,v_{2})^{T}),\text{ for all } v_2\in V_2.
+\end{align*}
+Thus, the variational formulation (\ref{}) can be rewritten as a system of two equations:
+\begin{align*}
+\begin{split}
+i\theta \displaystyle \int_{-L}^H (E_2' -\imath\theta E_1)\overline{\tilde E_1} - \int_{-L}^H \left((\epsilon_0 +\imath\nu \operatorname{Id}) \E\right)_{1} \overline{\tilde E}_{1}
+&=0,\\
+\displaystyle \int_{-L}^H (E_2' -\imath\theta E_1)\tilde {E_2'} - \int_{-L}^H\left( (\epsilon_0 +\imath\nu\operatorname{Id}) \E\right)_{2}\overline{\tilde{E}}_{2}
+  - \imath \sqrt{\alpha(-L)} E_2 (-L) \tilde E_2 (-L) &= -g_{inc} (-L) \overline{( \tilde E_2(-L) )},\\
+  \text{ for all } \tilde E_{1}\in L_{2}(\Omega), \; \tilde{E}_{2}\in H_{1}(\Omega).
+  \end{split}
+\end{align*}
+Inserting an explisit expression for the dielectric permittivity tensor 
+\be \label{eq:epsilonmu}
+ \epsilon_0(x) =
+\left(
+\begin{array}{cc}
+\alpha(\x) & \imath \delta (\x)\\
+-\imath \delta (\x) & \alpha(\x)
+\end{array}
+\right)
+\ee
+into the above, we obtain
+\begin{align}
+\label{eq:var_form2}
+\begin{split}
+ i\theta \displaystyle \int_{-L}^H (E_2' -\imath\theta E_1)\overline{\tilde E_1} - 
+ \int_{-L}^H \left((\alpha+i\nu)E_1+\imath\delta E_2\right)_{1} \overline{\tilde E}_{1}
+&=0,\\
+\int_{-L}^H (E_2' -\imath\theta E_1)\tilde {E_2'} -
+\int_{-L}^H\left( -\imath \delta E_1+(\alpha+i\nu) E_2\right)_{2}\overline{\tilde{E}}_{2}
+  - \imath \sqrt{\alpha(-L)} E_2 (-L) \tilde E_2 (-L) &= -g_{inc} (-L) \overline{( \tilde E_2(-L) )},\\
+  \text{ for all } \tilde E_{1}\in L_{2}(\Omega), \; \tilde{E}_{2}\in H_{1}(\Omega).
+  \end{split}
+\end{align}
 
-We look for a ratio $h(\nu)$ that would ensure that 
+\begin{remark}
+Let us assume that the operator
 \begin{align*}
+M\psi = \frac{i\delta}{(\alpha+i\nu)}\psi
+\end{align*}
+defines an isomorphism from $L_{2}(\Omega)$ to $L_{2}(\Omega)$. 
+Given $E_1,\; E_2\in L_{2}(\Omega)$, the function $\mathcal{F}=\frac{i\delta}{(\alpha+\imath\nu)}\left((\alpha+\imath\nu)E_{1}+i\delta E_{2}\right)$ also belongs to $L_{2}(\Omega)$. 
+If $E_1,\; E_2$ satisfy the problem (\ref{eq:var_form2}) for $\theta=0$, the function $\mathcal{F}=0$, 
+i.e.
+\begin{align*}
+ (\mathcal{F},\tilde{E}_{2})_{L_{2}}=\int_{-L}^{H}\left(\imath\delta E_{1}-\delta^2(\alpha+i\nu)^{-1} E_{2}\right)\overline{\tilde E}_{2}=0,
+\end{align*}
+for all $\overline{\tilde E}_2\in H_{1}(\Omega)$. Adding this to the second expression of (\ref{eq:var_form2}), we obtain 
+the variational formulation for $E_2$, which coincides with the variational formulation for the Helmholtz equation. The well-posedness 
+of this problem had been studied in \cite{}. 
+Hence, we can add the second expression (\ref{eq:E2}) to
+\begin{align*}
+\int_{-L}^{H}\left(i\delta E_{1}-\delta^2(\alpha+i\nu)^{-1} E_{2}\right)\overline{\tilde E}_{2}=0
+\end{align*}
+to obtain the variational formulation for $E_{2}$, which will coincide with the variational formulation for the Helmholtz equation, and thus will be well-posed 
+(see the thesis \cite{thesis_lmig}).
+The estimates from \cite{thesis_lmig} can be employed to bound $\|E_{1}\|_{L_{2}}$.
+\end{remark}
+
+Introducing two basis spaces, $V_{E_{1}}=\{\psi_{j}\}_{j=1}^{N_{1}}$ and $V_{E_{2}}=\{\phi_{i}\}_{i=1}^{N_{2}}$, we look for the solution of the problem (\ref{}) in the form:
+\begin{align*}
+E_{1}=\sum\limits_{k=1}^{N_{1}}e_{1k}\psi_{k},\; E_{2}=\sum\limits_{k=1}^{N_{2}}e_{2k}\phi_{k}.
+\end{align*}
+Substituting $\tilde{E}_{1}=\psi_{m}, \; m=1,\ldots,N_{1}$ and $\tilde{E}_{2}=0$ into the variational formulation (\ref{}), we obtain:
+\begin{align*}
+i\theta\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}\bar{\psi}_{m}dx+\theta^2\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx\\
+-\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{k}\bar{\psi}_{m}dx-i\sum\limits_{1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\delta(x)\phi_{k}(x)\bar{\psi}_{m}dx=0.
+\end{align*}
+Similarly, for $\tilde{E}_{1}=0$ and $\tilde{E}_{2}=\phi_{\ell},\; \ell=1,\ldots, N_{2}$:
+\begin{align*}
+\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx-i\theta\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}(x)\bar{\phi}'_{\ell}(x)dx\\
++i
+\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\delta(x)\psi_{k}\bar{\phi}_{m}dx-\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\phi_{k}\bar{\phi}_{m}dx\\
+-
+i\lambda\sum\limits_{k=1}^{N_{2}}e_{2k}\phi_{k}(-L)\bar{\phi}_{m}(-L)=-g_{inc}(x)\bar{\phi}_{m}(-L).
+\end{align*}
+After introduction 
+\begin{align*}
+\left(K^{\psi,\phi'}\right)_{mk}=\int\limits_{-L}^{H}\bar{\psi}_{m}\phi'_{k}dx,\qquad \left(M^{\psi}\right)_{mk}=\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx,\\
+\left(M^{\alpha,\psi}\right)_{mk}=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{m}\bar{\psi}_{k}dx, \qquad \left(M^{\delta,\psi,\phi}\right)_{mk}=\int\limits_{-L}^{H}\delta(x)\bar{\psi}_{m}\phi_{k}dx,\\
+K_{\ell k}=\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx,\qquad \left(M^{\alpha,\phi}\right)_{\ell k}=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\bar{\phi}_{\ell}\phi_{k}dx,\\
+I_{km}^{\Gamma}=\bar{\phi}_{m}(-L)\phi_{k}(-L),\\
+\boldsymbol{e}_{1}=\left(e_{11},\ldots,e_{1 N_{1}}\right)^{T},\; \boldsymbol{e}_{2}=\left(e_{21},\ldots,e_{2 N_{1}}\right)^{T},\\
+\boldsymbol{0}_{n} \text{ is an $n$-dimensional zero column vector}.
+\end{align*}
+the above system of equations can be rewritten in an antisymmetric block form:
+\begin{align*}
+\left(\begin{matrix}
+\theta^2 M_{\psi}-M^{\alpha,\psi} & i\theta K^{\psi,\phi'}-i M^{\delta,\psi,\phi} \\
+-i\theta (K^{\psi,\phi'})^{*}+i (M^{\delta,\psi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
+\end{matrix}\right)
+\left(
+\begin{matrix}
+\boldsymbol{e}_1\\
+\boldsymbol{e}_2
+\end{matrix}
+\right)=-g_{inc}(-L)
+\left(
+\begin{matrix}
+\boldsymbol{0}_{N_{1}}\\
+\bar{\phi}_{1}(-L)\\
+\bar{\phi}_{2}(-L)\\
+\vdots\\
+\bar{\phi}_{N_{2}}(-L)
+\end{matrix}
+\right).
+\end{align*}
+This expression greatly simplifies when choosing $V_{E_{1}}=V_{E_{2}}=\left(\phi_{m}\right)_{m=1}^{N_{2}}$ and in the case $\theta=0$:
+\begin{align}
+\label{eq:simple_system}
+\left(\begin{matrix}
+M^{\alpha,\phi} & i M^{\delta,\phi,\phi} \\
+i (M^{\delta,\phi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
+\end{matrix}\right)
+\left(
+\begin{matrix}
+\boldsymbol{e}_1\\ 
+\boldsymbol{e}_2
+\end{matrix}
+\right)=-g_{inc}(-L)
+\left(
+\begin{matrix}
+\boldsymbol{0}_{N_{1}}\\
+\bar{\phi}_{1}(-L)\\
+\bar{\phi}_{2}(-L)\\
+\vdots\\
+\bar{\phi}_{N_{2}}(-L)
+\end{matrix}
+\right).
+\end{align}
+In all numerical experiments, we make use of the formulation, where the Lagrange piecewise-linear ('hat') finite elements are used as a 
+basis and trial space (see \cite{brenner}). We apply permutation to the above system 
+to obtain a 7-diagonal Hermitian matrix and solve the system with the Gauss back substitution algorithm.
+
+\section{Numerical Experiments}
+This section is organized as follows. The first part is dedicated to the numerical implementation
+of the frequency domain formulation (\ref{}). We study the convergence of this formulation and the behaviour 
+of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
+performed on a laptop with 2.6GHz Intel Core i5 CPU, with the help of the code written in Octave (compatible with Matlab).
+
+The second part of the section deals with the question of the equivalence of the limiting absorption and limited amplitude 
+principle. We compare the solutions obtained as $\nu\rightarrow 0$ with the help of our frequency domain code 
+and of the time domain code (computed for large values of time). 
+The time-domain code implements the scheme described in Section \ref{} and 
+is written in Fortran. 
+\subsection{Frequency Domain Problem}
+\subsubsection{Validity of Implementation}
+\subsubsection{Solution of $X$-Mode Prolbem}
+
+Let us consider the case of the resonance, more precisely, we consider sufficiently smooth
+$\alpha,\delta$, s.t. $\alpha(0)=0$ and $\delta(0)\neq 0$, and the solvability conditions 
+of Theorem \ref{}  are satisfied. 
+For simplicity, let us consider 
+\begin{align}
+\label{eq:cond}
+ \alpha(x)=-x \text{  in some neighbourhood of $0$ }.
+\end{align}
+
+Given the space $\mathbf{V}_{h}=S_{h}^{1}\times S_{h}^{1}$, with $S_{h}^{1}$ consisting of piecewise-linear (hat) functions, we look for a ratio $h(\nu)$ that would ensure that the absolute error 
+\begin{align}
+\label{eq:problem1}
 \|E^{\nu}_{1}-E^{\nu,h}_{1}\|_{L_{2}(\Omega)}<\epsilon,
+\end{align}
+given a fixed value of $\epsilon>0$.
+
+We use the following well-known facts:
+\begin{itemize}
+ \item The C\'ea's lemma applied to the problem (\ref{}); here $C_c$ is the continuity and $C_i$ is the coercivity constants:
+\begin{align}
+\label{eq:cea}
+\begin{split}
+ \|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|_{V}\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}
+ \leq \nu^{-1}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}.
+ \end{split}
+\end{align}
+The last inequality follows from Theorem \ref{}.  
+\item The form of the exact solution to the problem (\ref{}):
+\begin{align}
+\label{eq:exact}
+ E_{1}^{\nu}=E_{2}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f(x)}{\alpha(x)+i\nu},
+\end{align}
+for some $f(x)\in L_{2}(\Omega)$.
+\item The estimate from \cite[Chapter 0]{Brenner_Scott} on the rate of convergence of the interpolation 
+\begin{align}
+\label{eq:bsc}
+ \|v-I^{h}v\|_{L_{2}(\Omega)}\leq Ch^2|v''|_{L_{2}(\Omega)},\; C>0,\\
+ %\|v-I^{h}v\|_{H_{1}(\Omega)}\leq Ch|v''|_{L_{2}(\Omega)},\; C>0, 
+\end{align}
+where $I^{h}v$ is an interpolation operator onto $S_{h}^{1}$.
+\end{itemize}
+For $E_{1}^{\nu},\;f(x)$ in (\ref{eq:exact}) being sufficiently smooth, 
+\begin{align*}
+ \frac{d^2}{dx^2}E_{1}^{\nu}=\frac{f''}{\alpha+i\nu}-2\frac{f'\alpha'}{(\alpha+i\nu)^2}+\frac{f\alpha''}{(\alpha+i\nu)^3},
 \end{align*}
-for a fixed $\epsilon>0$.
+from which, together with (\ref{eq:cond}), it follows that there exists $c>0$ s.t. for all sufficiently small $\nu$ 
+\begin{align*}
+ \left|  \frac{d^2}{dx^2}E_{1}^{\nu}\right|_{L_2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
+ %\\
+ %&=c\left.
+ %\left(\frac{x}{4(x^2+\nu^2)^2}\nu^{-2}+\frac{3x}{8(x^2+\nu^2)}\nu^{-4}+\frac{3}{8}\nu^{-5}\operatorname{atan}\frac{x}{\nu}\right)\right|_{-L}^{H}
+ \leq C\nu^{-5},\; 
+\end{align*}
+where $C>0$ does not depend on $\nu$. This, together with the estimates (\ref{eq:cea}) and (\ref{eq:bsc}), results in 
+\begin{align*}
+ \|E^{\nu}_{1}-E^{\nu,h}_{1}\|_{L_{2}(\Omega)}\leq C\nu^{-\frac{7}{2}}h^2,
+\end{align*}
+from which it follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as $\alpha_{\epsilon}\nu^{\frac{7}{4}}$, 
+where $\alpha_{\epsilon}>0$ depends on $\epsilon$ but does not depend on $\nu$.
 
-To conjecture the dependence of $h(\nu)$, we suggest the following (not rigorous argument). 
-Recall that for the problem (\ref{}) the C\'ea's lemma gives
+Let us check whether this holds true. 
+To do so, we conduct the following numerical experiment.
+
+We can show that 
 \begin{align*}
- \|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V},
+ \|E^{\nu}_{1}\|_{L_{2}(\Omega)}\leq \frac{C}{\sqrt{\nu}},\; C>0, 
 \end{align*}
-where $C_c$ is the continuity and $C_i$ is the coercivity constants.
-\begin{lemma}{}
-Let $\alpha(x), \; \delta(x)$ satisfy
+and thus the relative error control
 \begin{align*}
+ \frac{\|E^{\nu}_{1}-E^{\nu,h}_{1}\|_{L_{2}(\Omega)}}{\|E^{\nu}_{1}\|_{L_{2}(\Omega)}}\leq \epsilon
 \end{align*}
-Then, for all $\nu_*>0$ and for all $\nu>\nu_*$, the error between the numerical solution $\mathbf{E}^{h,\nu}$ and the 
-solution $\mathbf{E}^{\nu}$
-\begin{align*}
-\|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|_{V}\leq 
-\end{align*}
-\end{lemma}
-\begin{proof}
-The C\'ea's lemma states 
-\begin{align*}
- \|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V},
-\end{align*}
-where $C_c$ is the continuity and $C_i$ is the coercivity constants.
-Indeed,
-\begin{align*}
- \min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}\leq \min_{\mathbf{v}\in V_h}\|\mathbf{E}-I^{h}\mathbf{v}\|,
-\end{align*}
-where $I^{h}\mathbf{v}$ is an interpolation operator. The estimates from \cite[Chapter 0]{Brenner_Scott} give us
-\begin{align*}
- \|E_1-I^{h}E_1\|_{L_{2}(\Omega)}\leq Ch^2|E_1''|_{L_{2}(\Omega)},\\
- \|E_2-I^{h}E_2\|_{H_{1}(\Omega)}\leq Ch|E_2''|_{H_{1}(\Omega)}.
-\end{align*}
-To obtain these bounds, we require an explicit bound on $E_1, \; E_2$. In \cite{Despers et al Hybrid} 
-it was shown that 
-%\begin{align*}
-
-%\end{align*}
-
-\end{proof}
+can be ensured by choosing $h$ as $\beta_{\epsilon}\nu^{\frac{3}{4}}$.
 

### 2015-01-19 report/timedomain.tex
reorganisation of some sort

\section{Time dependant problem}
\subsection{Problem}
$[$ insert continuous equations here $]$

\subsection{Numerical scheme}
\be 
\eps_0 \frac{E_x\inp- E_x\midin}{\Delta t} = -e N_e \frac{u_x\inp + u_x \midin}{2}
\label{eq:ns1}
\ee 
\be
\eps_0 \frac{E_y\ihnp-E_y\ihn}{\Delta t}+ \frac{H_z\ipnh-H_z\inh}{\Delta x} = -eN_x \frac{u_y\ihnp + u_y\ihn}{2} 
\label{eq:ns2}
\ee
\be
 \frac{H_z\inh-H_z\inmh}{\Delta t}+ \frac{E_y\ihn-E_y\imhn}{\Delta x}=0
 \label{eq:ns3}
\ee
\be 
m_e \frac{u_x\inp-u_x\midin }{\Delta x} = e N_e \frac{E_x\inp+E_x\midin}{2}-\nu m_e\frac{u_x\inp+u_x \midin}{2}+ eB_0\frac{u_y\ihn+u_y\ihnp}{2}
\label{eq:ns4}
\ee
\be
m_e \frac{u_y\ihnp-u_y\ihn}{\Delta t} = eN_e \frac{E_y\ihnp + E_y\ihn}{2}- \nu m_e \frac{u_y\ihnp +u_y\ihn}{2}-eB_0 \frac{u_x\midin+u_x\inp}{2}
\ee
We first compute $H_z$ at time $n+1/2$ with \eqref{eq:ns3}. Then, \eqref{eq:ns2} gives the expression $E_y\ihnp$ as a function of known variables, and $u_y^{n+1}$, as follow
\be
E_y\ihnp = E_y\ihn - \frac{\Delta t }{\eps_0}\frac{H_z\ipnh-H_z\inh}{\Delta x} - \frac{\Delta t e N_e}{\eps_0}\frac{u_y\ihnp + u_y\ihn}{2}.
\label{eq:ns5}
\ee
By incorporating this expression into \eqref{eq:ns5} we then obtain $u_y$ at time $n+1$ as a function of known variables and $u_x^{n+1}$, 
\be 
\begin{array}{l}
u_y\ihnp m_e = m_e u_y\ihn + \Delta t eN_e \frac{E_y\ihn}{2}\\
+ \Delta teN_e\left(E_y\ihn - \frac{\Delta t }{\eps_0}\frac{H_z\ipnh-H_z\inh}{\Delta x} - \frac{\Delta t e N_e}{\eps_0}\frac{u_y\ihnp + u_y\ihn}{2}\right) \\
-\nu \Delta t m_e \frac{u_y\ihnp +u_y\ihn}{2}-\Delta teB_0 \frac{u_x\midin-u_x\inp}{2},
\end{array}
\label{eq:ns6}
\ee
which gives the following expression for $u_y\ihnp$
\be
\begin{array}{l}
u_y\ihnp \left(m_e(1+\frac{\Delta t \nu}{2}) +\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right)\\
\\
= \left(m_e(1-\frac{\Delta t \nu}{2}) -\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right)u_y\ihn\\
\\
\qquad +\Delta t eN_e E_y\ihn\\
\\
\qquad -  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}\\
\\
\qquad - \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right),
\end{array}
\label{eq:ns7} 
\ee
which we write 
\be
\begin{array}{l}
u_y\ihnp K_1 \\
\\
= K_2 u_y\ihn\\
\\
\qquad +\Delta t eN_e E_y\ihn\\
\\
\qquad -  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}\\
\\
\qquad - \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right).
\end{array}
\label{eq:ns7bis} 
\ee
with $K_1 =  m_e(1+\frac{\Delta t \nu}{2}) +\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}$ and $K_2 =m_e(1- \frac{\Delta t \nu}{2}) -\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}$.

Now we just need an expression of $E_x\inp$ as a function of time $n$ variables and $u_x^{n+1}$ and putting \eqref{eq:ns7} in \eqref{eq:ns4}, the scheme will be explicit. 
We can find such and expression in \eqref{eq:ns1}
\be 
E_x\inp = E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2}.
\label{eq:ns8}
\ee

We then have the scheme 
\be
\begin{array}{l}
m_e u_x\inp=  m_e u_x\midin \\
\qquad + \Delta t e N_e \frac{1}{2}\left( E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2}\right)\\
\qquad + \Delta t  e N_e \frac{1}{2}E_x\midin\\
\qquad -\Delta t\nu m_e\frac{u_x\inp+u_x \midin}{2}\\
\qquad +  \frac{e B_O \Delta t}{2K_1}\Big(K_2 u_y\ihn\\
\qquad +\Delta t eN_e E_y\ihn\\
\qquad -  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}\\

- \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right).\Big)\\
+  \frac{1}{2}\Delta teB_0u_y\ihn,
\end{array}
\label{eq:ns9}
\ee
which one can simplify into
\be
\begin{array}{l}
u_x \left(me(1+\frac{\Delta t \nu}{2})+ \frac{(eB_0\Delta t)^2}{4K_1} + \frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\inp \\
= \left(me(1-\frac{\Delta t \nu}{2})- \frac{(eB_0\Delta t)^2}{4K_1} -\frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\midin\\
\qquad + e \Delta t N_e E_x \midin \\
\qquad + \left( \frac{eB_0 \Delta t K_2}{2 K_1}+ \frac{e B_0 \Delta t}{2}\right) u_y\ihn\\
\qquad - \frac{(e\Delta t)^2 N_e B_0}{2K_1}E_y\ihn \\
\qquad - \frac{e^2(\Delta t)^3 B_0}{4K_1}\frac{H_z \ipnh- H_z \inh}{\Delta x}
\end{array}
\label{eq:ns10} 
\ee

### 2015-01-19 report/timedomain.tex
tikz grid of discretized domain position
some sentences added (push before break)

@@
-\section{Time dependant problem}
-\subsection{Problem}
-$[$ insert continuous equations here $]$
+\subsubsection{Problem}
+\textcolor{red}{$[$ insert continuous equations here $]$}
 
-\subsection{Numerical scheme}
+\subsubsection{Numerical scheme}
+We compute a numerical approximation of \textcolor{red}{insert ref of continuous equations} on a Cartesian grid using the Yee scheme.
+Let $n$ denote the time step, as usual $t_n = n \Delta t$.
+$H_z$ will then be taken on a half time step, and our equation, discretized in them write :
+ \textcolor{red}{$[$ insert discretized equations here $]$}
+ We discretize our equation on staggered grid, meaning $E_x$, $u_x$, $E_y$, $u_y$ and $H_z$ are not and the same grid. Evidently we already stated it for $H_z$ in the time discretization. 
+\input{grid}
 \be 

### 2015-01-19 report/timedomain.tex
added some sentences in timedomain discretization (yee scheme)

@@
 $H_z$ will then be taken on a half time step, and our equation, discretized in them write :
- \textcolor{red}{$[$ insert discretized equations here $]$}
- We discretize our equation on staggered grid, meaning $E_x$, $u_x$, $E_y$, $u_y$ and $H_z$ are not and the same grid. Evidently we already stated it for $H_z$ in the time discretization. 
-\input{grid}
+ \textcolor{red}{$[$ insert time-discretized equations here $]$}
+ We discretize our equation on staggered grid, meaning $E_x$, $u_x$, $E_y$, $u_y$ and $H_z$ are not and the same grid.
+Evidently we already stated it for $H_z$ in the time discretization.
+Fig.~\ref{schemepos} shows the positions of $Ex$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) on the discretized grid in space and time.
+We obtain the following discretized equations,
+
 \be 
-\eps_0 \frac{E_x\inp- E_x\midin}{\Delta t} = -e N_e \frac{u_x\inp + u_x \midin}{2}
+\eps_0 \frac{E_x\inp- E_x\midin}{\Delta t} = -e N_e \frac{u_x\inp + u_x \midin}{2},
 \label{eq:ns1}
@@
 \be
-\eps_0 \frac{E_y\ihnp-E_y\ihn}{\Delta t}+ \frac{H_z\ipnh-H_z\inh}{\Delta x} = -eN_x \frac{u_y\ihnp + u_y\ihn}{2} 
+\eps_0 \frac{E_y\ihnp-E_y\ihn}{\Delta t}+ \frac{H_z\ipnh-H_z\inh}{\Delta x} = -eN_x \frac{u_y\ihnp + u_y\ihn}{2} ,
 \label{eq:ns2}
@@
 \be
- \frac{H_z\inh-H_z\inmh}{\Delta t}+ \frac{E_y\ihn-E_y\imhn}{\Delta x}=0
+ \frac{H_z\inh-H_z\inmh}{\Delta t}+ \frac{E_y\ihn-E_y\imhn}{\Delta x}=0,
  \label{eq:ns3}
@@
 \be 
-m_e \frac{u_x\inp-u_x\midin }{\Delta x} = e N_e \frac{E_x\inp+E_x\midin}{2}-\nu m_e\frac{u_x\inp+u_x \midin}{2}+ eB_0\frac{u_y\ihn+u_y\ihnp}{2}
+m_e \frac{u_x\inp-u_x\midin }{\Delta x} = e N_e \frac{E_x\inp+E_x\midin}{2}-\nu m_e\frac{u_x\inp+u_x \midin}{2}+ eB_0\frac{u_y\ihn+u_y\ihnp}{2},
 \label{eq:ns4}
@@
 \be
-m_e \frac{u_y\ihnp-u_y\ihn}{\Delta t} = eN_e \frac{E_y\ihnp + E_y\ihn}{2}- \nu m_e \frac{u_y\ihnp +u_y\ihn}{2}-eB_0 \frac{u_x\midin+u_x\inp}{2}
+m_e \frac{u_y\ihnp-u_y\ihn}{\Delta t} = eN_e \frac{E_y\ihnp + E_y\ihn}{2}- \nu m_e \frac{u_y\ihnp +u_y\ihn}{2}-eB_0 \frac{u_x\midin+u_x\inp}{2},
 \ee
+\input{grid}
+
 We first compute $H_z$ at time $n+1/2$ with \eqref{eq:ns3}. Then, \eqref{eq:ns2} gives the expression $E_y\ihnp$ as a function of known variables, and $u_y^{n+1}$, as follow
@@
 \ee
+
 By incorporating this expression into \eqref{eq:ns5} we then obtain $u_y$ at time $n+1$ as a function of known variables and $u_x^{n+1}$, 
@@
 \qquad - \frac{(e\Delta t)^2 N_e B_0}{2K_1}E_y\ihn \\
-\qquad - \frac{e^2(\Delta t)^3 B_0}{4K_1}\frac{H_z \ipnh- H_z \inh}{\Delta x}
+\qquad - \frac{e^2(\Delta t)^3 B_0}{4K_1}\frac{H_z \ipnh- H_z \inh}{\Delta x},
 \end{array}
@@
 \ee
+and out scheme is then fully explicit.

### 2015-01-19 report/proc.tex
add comment : toc
proposition : including all file in a "meta" squeletton file
minor change
minor changes
reorganisation of some sort
minor changes #3
template proc essaim
tikz grid of discretized domain position
adding temporary title and randomly ordered list of name

@@
-\documentclass[a4paper,10pt]{article}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
+%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% This is a template file for Proccedings 
+%
+% Copy it to a new file with a new name and use it as the basis
+% for your article
+%
+%%%%%%%%%%%%%%%%%%%%%%%%   EDP Sciences  %%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+\documentclass[proc]{edpsmath}
+%
+%\usepackage{amsfonts,graphicx,amssymb}%amsfonts pour les \mathbb
+%\usepackage{amsmath,amsthm,amssymb}
+%%%%%%%%%%%%%--PREAMBLE--%%%%%%%%%%%%%%%%%%
+%%-----------------------------
+%%         ...........
+%%         your macros
+\usepackage[frenchb,english]{babel}
+\usepackage{macros}
+\usepackage{tikz}
+\usepackage{xcolor}
+\newenvironment{remark}[1][Remark]{\begin{trivlist}
+\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\definecolor{blue}{rgb}{0.30,0.8,1}
+\definecolor{red}{rgb}{1,0.3,0.3}
+\usetikzlibrary{positioning,shapes,shadows,arrows}
+
+%%         ...........
+%%-------------------------%%----
+%%%%%%%%%%%%%%%--BODY--%%%%%%%%%%%%%%%%%%
 
 \begin{document}
+
+%%-----------------------------
+%%      the top matter
+%%-----------------------------
+\title{Study of the
+	numerical solution of X-Modes equations around the hybrid resonnance} %\thanks{...}\thanks{...}% At most 5 thanks
+%
+\author{Maryna Kachanovska}\address{UMA, ENSTA, Paris}
+\author{Bruno Depsr\'es}\address{Laboratoire Jacques-Louis Lions, University PARIS 6}
+\author{Imbert Lise-Marie}{Courant Institute of Mathematical Sciences, New York University}
+\author{C\'eline Caldini-Queiros}{Max Planck Institute für PlasmaPhysik, Garching bei Muenchen}
+
+%
+%\dedicated{\it Dedicated to Maurice Dupont} %if necessary
+%
+\begin{abstract} ... \end{abstract}
+%
+\begin{resume} ... \end{resume}
+%
+%
+\maketitle
+%!!!!!!!!!!!todo !!!!!!!!!!!
+
+%\item !!!!to do : correct proof of coercivity (celine)
+%\item !!!!to do : write Yee scheme 			(celine)
+%
+%%with explicit in \nu coercivity and continuity constants
+
 \input{intro}
-%\input{}
-
+\input{equations}
+\input{numerics}
+\input{timedomain}
 \begin{thebibliography}{99}

### 2015-01-19 report/absorption.tex
added extra numerics. TODO: resonance numerics

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
\usepackage{tikz}
\usepackage{caption}
\usepackage{pgfplots}
\usepackage{ulem}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{hyperref}
\begin{document}
\subsection{Limiting Amplitude and Limiting Absorption Principle}
In this section we perform several numerical experiments,
with the normalization chosen as $\epsilon_0=\mu_0=1$, $\omega=c=1$. 
Also, we set $m_e=1$ and $e=-1$. From this it follows that $w_c=-B_0$ and $w_p^2=N_e$. 
We consider the following two cases:
\begin{itemize}
 \item case $N_e\neq \operatorname{const}$, no resonance
 \item case $N_e\neq \operatorname{const}$, resonance
\end{itemize}
For every fixed absorption rate $\nu$, in the time domain we choose the boundary conditions of the form
\begin{align}
\label{eq:bcs}
\left.\partial_t H\right|_{x=-L}&=-\left.\partial_x E_y\right|_{x=-L}=G\sin(t),\; G\in \mathbb{R}, \\
 \nonumber
 \left.\partial_t H\right|_{x=H}&=0,
\end{align}
and zero initial conditions, and in the frequency domain
\begin{align*}
 \left.\partial_x \hat{E}_y\right|_{x=-L}&=G,\\
 \left.\partial_x \hat{E}_y\right|_{x=H}&=0.
\end{align*}
We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain (the solution computed numerically at the time step $n$ is denoted by $\mathbf{E}^{\nu}_{n}$), and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain. 
Our goal is to check whether
\begin{align*}
\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t)=\Im\left(\hat{\mathbf{E}}^{\nu}\exp(it)\right).
\end{align*}

\subsubsection{No-Resonance Case}
We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{2}$ satisfies 
the Airy equation (\ref{}).

We set $\omega_c=0$ (thus $\delta(x)=0$), $\omega=1$ (hence $\alpha(x)=1-N_e(x)$), 
choose the domain as $[-0.5, 10]$ and set the electron density $N_e(x)=1+x$. Importantly, $N_e(x)>0$ on the whole interval.
The boundary conditions in (\ref{eq:bcs}) are chosen as $G=Ai'(0.5)$. 
In all the experiments in this section the CFL number was chosen to be equal to 0.5.

First let us fix $\nu=1e-2$. 
To demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
inside the domain $(-L,\; H)$ and plot the dependence of the solution $E_{2}^{\nu}(x_c,t), \; \hat{E}_2^{\nu}(x_c)\mathrm{e}^{it}$ 
on time $t$ for a range of $t\gg 1$ in Figure \ref{fig:nu1e2_harmon}.

\begin{figure}[htb]
\includegraphics[width=0.9\textwidth]{figure_nu1e2-crop.pdf}
 \label{fig:nu1e2_harmon}
\end{figure}

In Figure \ref{fig:nu1e2_harmon2} (left figure) we compare this solution to the computed $\hat{E}_2^{\nu}\mathrm{e}^{it}$, for
fixed values of $t$. Both solutions appear to be in close agreement. 
\begin{figure}[htb]
 \begin{tabular}{ll}
\includegraphics[width=0.5\textwidth]{figure_nu1e2_2-crop.pdf}
&
\includegraphics[width=0.5\textwidth]{figure_error_nu1e4-crop.pdf}\\
\end{tabular}
\caption{In the left figure we show the solution to (\ref{}) for $\nu=10^{-2}$, for two fixed moment of times. In the right figure 
the dependence of the error (\ref{eq:error}) on time for $\nu=10^{-4}$ is demonstrated. 
We can see that the error is decreasing.}
 \label{fig:nu1e2_harmon2}
\end{figure}
The computed $L_2$ error
\begin{align}
\label{eq:error}
\mathcal{E}(t)=\|\Im\left(\hat{E}_y^{\nu}\exp(it)\right)-E_y^{\nu}(t)\|_{L_{2}(-L;H)}.
\end{align}
for $\nu=1e-2$ did not exceed $1.1e-3$ for values of $t\in \left(28501,  30000\right)$.

Figure show the solutions at fixed time steps for $\nu=1e-4$. As before, 
to demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
inside the domain $(-L,\; H)$ and plot 
the dependence of the solution $E_{2}^{\nu}(x_c,t)$ on time $t$ for a range of $t\gg 1$. 
The error (\ref{eq:error}) for $\nu=1e-4$ at the time interval $[228000.05,\; 240000.05]$ does not exceed 2.8e-4. 
One of our observations was that for smaller $\nu$ one requires more time steps to achieve the limiting amplitude solution, 
c.f. e.g. Figure \ref{fig:nu1e2_harmon2}. 
We were not able to obtain the limiting amplitude solution for $t<3\cdot 10^{4}$, unlike in the case of $\nu=10^{-2}$. 
For example, for $\nu=1e-6$ we were not able to reach the limiting amplitude solution even on the time interval $t\leq 1.92e6$, 
see Figure \ref{fig:nu1e4_harmon}. 
\begin{figure}
\begin{tabular}{c}
 \includegraphics[width=\textwidth]{figure_nu1e4-crop.pdf}\\
 \includegraphics[width=\textwidth]{figure_nu1e6-crop.pdf}\\
\end{tabular}
\caption{In the upper figure we plot the dependence of the solution $E_{2}^{\nu}(x_c,t)$ on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$. 
In the lower figure we show the solution for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
$\nu=10^{-4}$ the limiting amplitude solution was reached for large $t$. For $\nu=10^{-6}$ we were not able 
to obtain the limiting amplitude solution even for $t\approx 1.9e6$. }
  \label{fig:nu1e4_harmon}
\end{figure}

\subsubsection{Resonance Case}
For the resonance case, we choose the parameters as given in Table \ref{}.
\begin{tabular}{cc}
$L$ & 5\\
$H$ & 19\\
$\omega_c$ &  $\sqrt{0.5}$\\
$N_e(x)$ &  $\left\{
 \begin{array}{cc}
  0.25, & x<-0.5,\\
  \frac{1+x}{2}, & x\geq -0.5, x\leq 9\\
  5, & x>9.
 \end{array}\right.$
 $G$ as in (\ref{eq:bcs}) & 0.11 \\
\end{tabular}
Since $\alpha(x)=(1-2N_e(x))$, $\alpha(0)=0$. Clearly, $\delta(0)\neq 0$ (resonance case).

The electron density 
\begin{align*}
 N_e(x)=
 \left\{
 \begin{array}{cc}
  0.25, & x<-0.5,\\
  \frac{1+x}{2}, & x\geq -0.5, x\leq 9\\
  5, & x>9.
 \end{array}\right.
\end{align*}

Since $\alpha(x)=(1-2N_e(x))$, $\alpha(0)=0$. Clearly, $\delta(0)\neq 0$ (resonance case).

We solve this problem on the interval $[-5,\; 19]$.
The boundary condition is
\begin{align*}
 \partial_y E(-5)=-\partial_t H(-5)=-0.11\cos(t).
\end{align*}

We choose $\omega_c:=\sqrt{0.5}$ and $\omega=1$.

In all the experiments we choose in the time domain $\Delta x=0.0125$ and CFL=0.9.

The electron density 
\begin{align*}
 N_e(x)=
 \left\{
 \begin{array}{cc}
  0.25, & x<-0.5,\\
  \frac{1+x}{2}, & x\geq -0.5, x\leq 9\\
  5, & x>9.
 \end{array}\right.
\end{align*}

We solve this problem on the interval $[-5,\; 19]$.
The boundary condition is
\begin{align*}
 \partial_y E(-5)=-\partial_t H(-5)=-0.11\cos(t).
\end{align*}

The results for $\nu=1e-2$ (chosen as a parameter both in frequency and time domain) 
are shown in Figure \ref{resonance_nu1e2}.

\end{document}

### 2015-01-19 report/proc.tex
comment on O.L. & R.S.

@@
 \author{Bruno Depsr\'es}\address{Laboratoire Jacques-Louis Lions, University PARIS 6}
-\author{Imbert Lise-Marie}{Courant Institute of Mathematical Sciences, New York University}
-\author{C\'eline Caldini-Queiros}{Max Planck Institute für PlasmaPhysik, Garching bei Muenchen}
+\author{Imbert Lise-Marie}\address{Courant Institute of Mathematical Sciences, New York University}
+\author{C\'eline Caldini-Queiros}\address{Max Planck Institute für PlasmaPhysik, Garching bei Muenchen}
 
@@
 \maketitle
+\textcolor{red}{should we add Olivier Lafitte and Remi Sart anywhere in the proceeding ?}\\
 %!!!!!!!!!!!todo !!!!!!!!!!!

### 2015-01-19 report/timedomain.tex

@@
-\subsubsection{Problem}
-\textcolor{red}{$[$ insert continuous equations here $]$}
+The equations of consideration write as
+ \begin{align}
+ \epsilon_0\partial_t E_{x}-\partial_y H_z=-eN_e u_x, \nonumber\\
+ \epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\nonumber\\
+ \mu_0\partial_t H_z+\partial_x E_y-\partial_y E_x=0, \label{eq:tdpb}\\
+ m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
+ m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y.\nonumber
+ \end{align}
 
-\subsubsection{Numerical scheme}
-We compute a numerical approximation of \textcolor{red}{insert ref of continuous equations} on a Cartesian grid using the Yee scheme.
+We compute a numerical approximation of~\eqref{eq:tdpb} on a Cartesian grid using the Yee scheme.
 Let $n$ denote the time step, as usual $t_n = n \Delta t$.
 $H_z$ will then be taken on a half time step, and our equation, discretized in them write :
- \textcolor{red}{$[$ insert time-discretized equations here $]$}
+ \begin{align}
+ \epsilon_0\frac{ E_{x}^{n+1}-E_x^{n}}{\Delta t}-\partial_y H_z=-eN_e u_x, \nonumber\\
+ \epsilon_0\frac{ E_{y}^{n+1}-E_y^{n}}{\Delta t}+\partial_x H_z=-eN_e u_y,\nonumber\\
+ \mu_0\frac{ H_z^{n+1/2}-H_z^{n-1/2}}{\Delta t}+\partial_x E_y-\partial_y E_x=0, \label{eq:tdiscretizedpb}\\
+ m_e\frac{ u_{x}^{n+1}-u_x^{n}}{\Delta t}=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
+ m_e\frac{u_{y}^{n+1}-u_y^{n}}{\Delta t}=eE_y-eu_xB_0-\nu m_e u_y.\nonumber
+ \end{align}
  We discretize our equation on staggered grid, meaning $E_x$, $u_x$, $E_y$, $u_y$ and $H_z$ are not and the same grid.
@@
 which gives the following expression for $u_y\ihnp$
-\be
-\begin{array}{l}
-u_y\ihnp \left(m_e(1+\frac{\Delta t \nu}{2}) +\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right)\\
-\\
-= \left(m_e(1-\frac{\Delta t \nu}{2}) -\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right)u_y\ihn\\
-\\
-\qquad +\Delta t eN_e E_y\ihn\\
-\\
-\qquad -  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}\\
-\\
-\qquad - \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right),
-\end{array}
+
+\begin{align}
+u_y\ihnp \left(m_e(1+\frac{\Delta t \nu}{2}) +\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right) =&\left(m_e(1-\frac{\Delta t \nu}{2}) -\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right)u_y\ihn +\Delta t eN_e E_y\ihn \nonumber\\
+&- \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x} - \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right),
 \label{eq:ns7} 
-\ee
+\end{align}
 which we write 
-\be
-\begin{array}{l}
-u_y\ihnp K_1 \\
-\\
-= K_2 u_y\ihn\\
-\\
-\qquad +\Delta t eN_e E_y\ihn\\
-\\
-\qquad -  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}\\
-\\
-\qquad - \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right).
-\end{array}
+\begin{align}
+u_y\ihnp K_1&= K_2 u_y\ihn +\Delta t eN_e E_y\ihn-  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}- \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right).
 \label{eq:ns7bis} 
-\ee
+\end{align}
 with $K_1 =  m_e(1+\frac{\Delta t \nu}{2}) +\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}$ and $K_2 =m_e(1- \frac{\Delta t \nu}{2}) -\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}$.
@@
 We then have the scheme
-\be
-\begin{array}{l}
-m_e u_x\inp=  m_e u_x\midin \\
-\qquad + \Delta t e N_e \frac{1}{2}\left( E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2}\right)\\
-\qquad + \Delta t  e N_e \frac{1}{2}E_x\midin\\
-\qquad -\Delta t\nu m_e\frac{u_x\inp+u_x \midin}{2}\\
-\qquad +  \frac{e B_O \Delta t}{2K_1}\Big(K_2 u_y\ihn\\
-\qquad +\Delta t eN_e E_y\ihn\\
-\qquad -  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}\\
 
-- \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right).\Big)\\
-+  \frac{1}{2}\Delta teB_0u_y\ihn,
-\end{array}
+\begin{align}
+m_e u_x\inp= & m_e u_x\midin  + \Delta t e N_e \frac{1}{2}\left( E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2}\right) + \Delta t  e N_e \frac{1}{2}E_x\midin -\Delta t\nu m_e\frac{u_x\inp+u_x \midin}{2}\nonumber\\
+&+  \frac{e B_O \Delta t}{2K_1}\Big(K_2 u_y\ihn +\Delta t eN_e E_y\ihn -  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}\nonumber\\
+&- \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right)\Big)+  \frac{1}{2}\Delta teB_0u_y\ihn,
 \label{eq:ns9}
-\ee
+\end{align}
+
 which one can simplify into
-\be
-\begin{array}{l}
-u_x \left(me(1+\frac{\Delta t \nu}{2})+ \frac{(eB_0\Delta t)^2}{4K_1} + \frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\inp \\
-= \left(me(1-\frac{\Delta t \nu}{2})- \frac{(eB_0\Delta t)^2}{4K_1} -\frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\midin\\
-\qquad + e \Delta t N_e E_x \midin \\
-\qquad + \left( \frac{eB_0 \Delta t K_2}{2 K_1}+ \frac{e B_0 \Delta t}{2}\right) u_y\ihn\\
-\qquad - \frac{(e\Delta t)^2 N_e B_0}{2K_1}E_y\ihn \\
-\qquad - \frac{e^2(\Delta t)^3 B_0}{4K_1}\frac{H_z \ipnh- H_z \inh}{\Delta x},
-\end{array}
-\label{eq:ns10} 
-\ee
-and out scheme is then fully explicit.
+\begin{align}
+u_x & \left(me(1+\frac{\Delta t \nu}{2})+ \frac{(eB_0\Delta t)^2}{4K_1} + \frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\inp 
+= \left(me(1-\frac{\Delta t \nu}{2})- \frac{(eB_0\Delta t)^2}{4K_1} -\frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\midin \nonumber\\
+& + e \Delta t N_e E_x \midin  + \left( \frac{eB_0 \Delta t K_2}{2 K_1}+ \frac{e B_0 \Delta t}{2}\right) u_y\ihn - \frac{(e\Delta t)^2 N_e B_0}{2K_1}E_y\ihn  - \frac{e^2(\Delta t)^3 B_0}{4K_1}\frac{H_z \ipnh- H_z \inh}{\Delta x},
+&\label{eq:ns10} 
+\end{align}
+and the scheme is then fully implicit.

### 2015-01-20 report/absorption.tex
report modified

@@
-\documentclass[a4paper,10pt]{article}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
-\usepackage{tikz}
-\usepackage{caption}
-\usepackage{pgfplots}
-\usepackage{ulem}
-\usepackage{pifont}% http://ctan.org/pkg/pifont
-\usepackage{hyperref}
-\begin{document}
 \subsection{Limiting Amplitude and Limiting Absorption Principle}
@@
 \subsubsection{Resonance Case}
-For the resonance case, we choose the parameters as given in Table \ref{}.
-\begin{tabular}{cc}
+\label{sec:resn}
+For the resonance case, we choose the parameters as given in Table \ref{tab:parameters_resonance}.
+\begin{table}[htb!]
+\begin{tabular}{c|c}
+Parameter & Value \\
+\hline
 $L$ & 5\\
@@
   5, & x>9.
- \end{array}\right.$
+ \end{array}\right.$\\
  $G$ as in (\ref{eq:bcs}) & 0.11 \\
 \end{tabular}
+\label{tab:parameters_resonance}
+\caption{Parameters for numerical simulations in Section \ref{sec:resn}}
+\end{table}
 Since $\alpha(x)=(1-2N_e(x))$, $\alpha(0)=0$. Clearly, $\delta(0)\neq 0$ (resonance case).
-
-The electron density 
-\begin{align*}
- N_e(x)=
- \left\{
- \begin{array}{cc}
-  0.25, & x<-0.5,\\
-  \frac{1+x}{2}, & x\geq -0.5, x\leq 9\\
-  5, & x>9.
- \end{array}\right.
-\end{align*}
-
-Since $\alpha(x)=(1-2N_e(x))$, $\alpha(0)=0$. Clearly, $\delta(0)\neq 0$ (resonance case).
-
-We solve this problem on the interval $[-5,\; 19]$.
-The boundary condition is
-\begin{align*}
- \partial_y E(-5)=-\partial_t H(-5)=-0.11\cos(t).
-\end{align*}
-
-We choose $\omega_c:=\sqrt{0.5}$ and $\omega=1$.
-
-In all the experiments we choose in the time domain $\Delta x=0.0125$ and CFL=0.9.
-
-The electron density 
-\begin{align*}
- N_e(x)=
- \left\{
- \begin{array}{cc}
-  0.25, & x<-0.5,\\
-  \frac{1+x}{2}, & x\geq -0.5, x\leq 9\\
-  5, & x>9.
- \end{array}\right.
-\end{align*}
-
-We solve this problem on the interval $[-5,\; 19]$.
-The boundary condition is
-\begin{align*}
- \partial_y E(-5)=-\partial_t H(-5)=-0.11\cos(t).
-\end{align*}
 
@@
 are shown in Figure \ref{resonance_nu1e2}.
-
-\end{document}

### 2015-01-20 report/proc.tex
report modified

@@
 \usepackage{xcolor}
+\usepackage[utf8]{inputenc}
+\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
+\usepackage{tikz}
+\usepackage{caption}
+\usepackage{pgfplots}
+\usepackage{ulem}
+\usepackage{pifont}% http://ctan.org/pkg/pifont
+\usepackage{hyperref}
 \newenvironment{remark}[1][Remark]{\begin{trivlist}
@@
 %
+\author{C\'eline Caldini-Queiros}\address{Max Planck Institute für PlasmaPhysik, Garching bei Muenchen}
+\author{Bruno Depsr\'es}\address{Laboratoire Jacques-Louis Lions, University PARIS 6}
+\author{Lise-Marie Imbert}\address{Courant Institute of Mathematical Sciences, New York University}
 \author{Maryna Kachanovska}\address{UMA, ENSTA, Paris}
-\author{Bruno Depsr\'es}\address{Laboratoire Jacques-Louis Lions, University PARIS 6}
-\author{Imbert Lise-Marie}\address{Courant Institute of Mathematical Sciences, New York University}
-\author{C\'eline Caldini-Queiros}\address{Max Planck Institute für PlasmaPhysik, Garching bei Muenchen}
 
@@
 \input{timedomain}
+\input{absorption}
 \begin{thebibliography}{99}

### 2015-01-20 report/timedomain.tex
1D-ed the model in timedomain.tex

@@
-The equations of consideration write as
+The equations of consideration for the one dimensionnal model write as
  \begin{align}
- \epsilon_0\partial_t E_{x}-\partial_y H_z=-eN_e u_x, \nonumber\\
+ \epsilon_0\partial_t E_{x}=-eN_e u_x, \nonumber\\
  \epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\nonumber\\
@@
  \end{align}
-
 We compute a numerical approximation of~\eqref{eq:tdpb} on a Cartesian grid using the Yee scheme.
@@
  \begin{align}
- \epsilon_0\frac{ E_{x}^{n+1}-E_x^{n}}{\Delta t}-\partial_y H_z=-eN_e u_x, \nonumber\\
+ \epsilon_0\frac{ E_{x}^{n+1}-E_x^{n}}{\Delta t}=-eN_e u_x, \nonumber\\
  \epsilon_0\frac{ E_{y}^{n+1}-E_y^{n}}{\Delta t}+\partial_x H_z=-eN_e u_y,\nonumber\\
@@
 \end{align}
-and the scheme is then fully implicit.
+and the scheme is then fully explicit.

### 2015-01-20 report/absorption.tex
experiments adding+ formatting has changed a bit

@@
 
-The results for $\nu=1e-2$ (chosen as a parameter both in frequency and time domain) 
-are shown in Figure \ref{resonance_nu1e2}.
+The results for $\nu=10^{-2}$ (chosen as a parameter both in frequency and time domain) 
+are shown in Figure \ref{fig:resonance_nu1e2} and for $\nu=10^{-3}$ in Figure \ref{resonance_nu1e3}. 
+\begin{figure}
+
+ \caption{In the }
+ \label{fig:resonance_nu1e2}
+\end{figure}
+
+For $\nu=10^{-6}$, like in the previous case, we were not able to obtain the limiting amplitude solution in the time domain.

### 2015-01-20 report/numerics.tex
experiments adding+ formatting has changed a bit

--- 2014-12-17 report/numerics.tex
@@
-\section{Discretization}
-\subsection{Discretization of the Frequency Domain Problem}
+\section{Discretization of the Frequency Domain Problem}
+\label{sec:discr}
+Testing the variational formulation (\ref{eq:varformulation}) with $(\tilde E_x,0)$ and $(0,\; \tilde{E}_y)\in\mathbf{V}(\Omega)$, we can rewrite it as a system of two equations:
+\begin{align*}
+\begin{split}
+i\theta \displaystyle \int_{-L}^H (E_y' -\imath\theta E_x)\overline{\tilde E_x} - \int_{-L}^H \left((\epsilon_0 +\imath\nu \operatorname{Id}) \E\right)_{1} \overline{\tilde E}_{x}
+&=0,\\
+\displaystyle \int_{-L}^H (E_y' -\imath\theta E_x)\tilde {E_y'} - \int_{-L}^H\left( (\epsilon_0 +\imath\nu\operatorname{Id}) \E\right)_{2}\overline{\tilde{E}}_{y}
+  - \imath \sqrt{\alpha(-L)} E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
+  \text{ for all } \tilde E_x\in L_{2}(\Omega), \; \tilde{E}_{y}\in H_{1}(\Omega).
+  \end{split}
+\end{align*}
+Inserting an explicit expression for the dielectric permittivity tensor 
+\be \label{eq:epsilonmu}
+ \epsilon_0(x) =
+\left(
+\begin{array}{cc}
+\alpha(\x) & \imath \delta (\x)\\
+-\imath \delta (\x) & \alpha(\x)
+\end{array}
+\right)
+\ee
+into the above, we obtain
+\begin{align}
+\label{eq:var_form2}
+\begin{split}
+ i\theta \displaystyle \int_{-L}^H (E_y' -\imath\theta E_x)\overline{\tilde E_x} - 
+ \int_{-L}^H \left((\alpha+i\nu)E_x+\imath\delta E_y\right)_{1} \overline{\tilde E}_{x}
+&=0,\\
+\int_{-L}^H (E_y' -\imath\theta E_x)\tilde {E_y'} -
+\int_{-L}^H\left( -\imath \delta E_x+(\alpha+i\nu) E_y\right)_{2}\overline{\tilde{E}}_{y}
+  - \imath \sqrt{\alpha(-L)} E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
+  \text{ for all } \tilde E_x\in L_{2}(\Omega), \; \tilde{E}_{y}\in H_{1}(\Omega).
+  \end{split}
+\end{align}
+Let us introduce the basis spaces $V_{E_x}=\{\psi_{j}\}_{j=1}^{N_{1}}$ and $V_{E_{2}}=\{\phi_{i}\}_{i=1}^{N_{2}}$, we look for the solution of the problem (\ref{}) in the form:
+\begin{align*}
+E_x=\sum\limits_{k=1}^{N_{1}}e_{1k}\psi_{k},\; E_{2}=\sum\limits_{k=1}^{N_{2}}e_{2k}\phi_{k}.
+\end{align*}
 
-We look for a ratio $h(\nu)$ that would ensure that 
+% Substituting $\tilde{E}_{x}=\psi_{m}, \; m=1,\ldots,N_{1}$ and $\tilde{E}_{y}=0$ into the variational formulation (\ref{}), we obtain:
+% \begin{align*}
+% i\theta\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}\bar{\psi}_{m}dx+\theta^2\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx\\
+% -\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{k}\bar{\psi}_{m}dx-i\sum\limits_{1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\delta(x)\phi_{k}(x)\bar{\psi}_{m}dx=0.
+% \end{align*}
+% Similarly, for $\tilde{E}_{x}=0$ and $\tilde{E}_{y}=\phi_{\ell},\; \ell=1,\ldots, N_{2}$:
+% \begin{align*}
+% \sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx-i\theta\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}(x)\bar{\phi}'_{\ell}(x)dx\\
+% +i
+% \sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\delta(x)\psi_{k}\bar{\phi}_{m}dx-\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\phi_{k}\bar{\phi}_{m}dx\\
+% -
+% i\lambda\sum\limits_{k=1}^{N_{2}}e_{2k}\phi_{k}(-L)\bar{\phi}_{m}(-L)=-g_{inc}(x)\bar{\phi}_{m}(-L).
+% \end{align*}
+After introduction 
 \begin{align*}
- \|E^{\nu}_{1}-E^{\nu,h}_{1}\|_{L_{2}(\Omega)}<\epsilon,
+\left(K^{\psi,\phi'}\right)_{mk}=\int\limits_{-L}^{H}\bar{\psi}_{m}\phi'_{k}dx,\qquad \left(M^{\psi}\right)_{mk}=\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx,\\
+\left(M^{\alpha,\psi}\right)_{mk}=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{m}\bar{\psi}_{k}dx, \qquad \left(M^{\delta,\psi,\phi}\right)_{mk}=\int\limits_{-L}^{H}\delta(x)\bar{\psi}_{m}\phi_{k}dx,\\
+K_{\ell k}=\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx,\qquad \left(M^{\alpha,\phi}\right)_{\ell k}=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\bar{\phi}_{\ell}\phi_{k}dx,\\
+I_{km}^{\Gamma}=\bar{\phi}_{m}(-L)\phi_{k}(-L),\\
+\boldsymbol{e}_{x}=\left(e_{11},\ldots,e_{1 N_{1}}\right)^{T},\; \boldsymbol{e}_{y}=\left(e_{21},\ldots,e_{2 N_{1}}\right)^{T},\\
+\boldsymbol{0}_{n} \text{ is an $n$-dimensional zero column vector}.
 \end{align*}
-for a fixed $\epsilon>0$.
+the system (\ref{eq:var_form2}) can be rewritten in an antisymmetric block form:
+\begin{align*}
+\left(\begin{matrix}
+\theta^2 M_{\psi}-M^{\alpha,\psi} & i\theta K^{\psi,\phi'}-i M^{\delta,\psi,\phi} \\
+-i\theta (K^{\psi,\phi'})^{*}+i (M^{\delta,\psi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
+\end{matrix}\right)
+\left(
+\begin{matrix}
+\boldsymbol{e}_x\\
+\boldsymbol{e}_y
+\end{matrix}
+\right)=-g_{inc}(-L)
+\left(
+\begin{matrix}
+\boldsymbol{0}_{N_{1}}\\
+\bar{\phi}_{x}(-L)\\
+\bar{\phi}_{y}(-L)\\
+\vdots\\
+\bar{\phi}_{N_{2}}(-L)
+\end{matrix}
+\right).
+\end{align*}
+This expression greatly simplifies when choosing $V_{E_x}=V_{E_{2}}=\left(\phi_{m}\right)_{m=1}^{N_{2}}$ and in the case $\theta=0$:
+\begin{align}
+\label{eq:simple_system}
+\left(\begin{matrix}
+M^{\alpha,\phi} & i M^{\delta,\phi,\phi} \\
+i (M^{\delta,\phi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
+\end{matrix}\right)
+\left(
+\begin{matrix}
+\boldsymbol{e}_x\\ 
+\boldsymbol{e}_y
+\end{matrix}
+\right)=-g_{inc}(-L)
+\left(
+\begin{matrix}
+\boldsymbol{0}_{N_{1}}\\
+\bar{\phi}_{x}(-L)\\
+\bar{\phi}_{y}(-L)\\
+\vdots\\
+\bar{\phi}_{N_{2}}(-L)
+\end{matrix}
+\right).
+\end{align}
 
-To conjecture the dependence of $h(\nu)$, we suggest the following (not rigorous argument). 
-Recall that for the problem (\ref{}) the C\'ea's lemma gives
+\section{Numerical Experiments}
+This section is organized as follows. The first part is dedicated to the numerical implementation
+of the frequency domain formulation (\ref{}). We study the convergence of this formulation and the behaviour 
+of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
+performed on a laptop with 2.6GHz Intel Core i5 CPU, with the help of the code written in Octave (compatible with Matlab). 
+We implemented the scheme described in Section \ref{sec:discr} for a simple case of $P_{1}$-space used 
+for the approximation of $E_{1}$ and $E_{2}$ and $\theta=0$, thus working with the system (\ref{eq:simple_system}). 
+We apply permutation to the above system 
+to obtain a 7-diagonal Hermitian matrix and solve the system with the Gauss back substitution algorithm.
+
+The second part of the section deals with the question of the equivalence of the limiting absorption and limited amplitude 
+principle. We compare the solutions obtained as $\nu\rightarrow 0$ with the help of our frequency domain code 
+and of the time domain code (computed for large values of time). 
+The time-domain code implements the scheme described in Section \ref{} and 
+is written in Fortran. 
+\subsection{Frequency Domain Problem}
+\subsubsection{Validity of Implementation}
+To check the validity of the code, we perform a numerical experiment with (formally chosen) parameters:
+\begin{align}
+\label{eq:parameters}
+\alpha(x)=x^2+1,\qquad \delta(x)=\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}.
+\end{align}
+Additionally, the boundary conditions read as 
+\begin{align}
+\label{eq:bcs}
+\partial_{1}E_{2}(-L)+2iE_{2}(-L)=2iAi(-L)+Ai'(-L),\\
+\partial_{1}E_{2}(H)=0,
+\end{align}
+where $Ai(x)$ is the Airy function \cite{}.
+
+It can be shown that $E_{y}$ thus satisfies the Airy equation \cite{}, and hence, with the choice of the boundary conditions as above, we obtain  
 \begin{align*}
- \|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V},
+E_{y}=Ai(x),\qquad 
+E_{x}=-i\frac{\delta(x)}{\alpha(x)}Ai(x)
 \end{align*}
-where $C_c$ is the continuity and $C_i$ is the coercivity constants.
-\begin{lemma}{}
-Let $\alpha(x), \; \delta(x)$ satisfy
+is the solution to the problem with parameters (\ref{eq:parameters}) with the boundary condition (\ref{eq:bcs}).
+
+In Figure \ref{fig:conv_rate} we demonstrate the convergence rates for this problem, with 
 \begin{align*}
+\|E_{1}-E_{1}^{c}\|_{L_{2}(\Omega)}=\left(\int\limits_{\Omega}\left|E_{1}(x)-\sum\limits_{k=0}^{N}E_{1i}\phi_{i}\right|^2dx\right),
 \end{align*}
-Then, for all $\nu_*>0$ and for all $\nu>\nu_*$, the error between the numerical solution $\mathbf{E}^{h,\nu}$ and the 
-solution $\mathbf{E}^{\nu}$
+where $\left(\phi_{i}\right)_{i=1}^{N}$ are $P_{1}$-finite elements and $E_{1}(x)$ is a known analytic solution.
+Similarly $\|E_{2}-E_{2}^{c}\|_{L_{2}(\Omega)}$ and $\|E_{2}-E_{2}^{c}\|_{H_{1}(\Omega)}$ are defined.
+
+\begin{figure}
+\begin{tikzpicture}
+    \begin{loglogaxis}[
+        xlabel=$h$,
+        ylabel=$Error$,
+        legend style={
+at={(0.2,1.5)},
+legend pos= south east,
+anchor=south east, 
+draw=none
+}
+]
+    \addplot[mark=*,blue] table {pics/E1L2.dat}; 
+    \addlegendentry{$\|E_{1}-E_{1}^{c}\|_{L_{2}}$};
+    \addplot[mark=*,red] table {pics/E2H1.dat};
+        \addlegendentry{$\|E_{2}-E_{2}^{c}\|_{H_{1}}$};
+
+          \addplot[mark=*,cyan] table {pics/E2L2.dat};
+        \addlegendentry{$\|E_{2}-E_{2}^{c}\|_{L_{2}}$};  
+        \addplot[dotted] table{pics/E_h2.dat};
+         \addlegendentry{$O(h^2)$};
+         \addplot[dashed] table{pics/H.dat};
+         \addlegendentry{$O(h)$};
+    \end{loglogaxis}
+    \end{tikzpicture}
+    \caption{Convergence rates for the problem with parameters (\ref{eq:parameters}) with the boundary condition (\ref{eq:bcs}).}
+    \label{fig:conv_rate}
+\end{figure}
+
+Note that in the last 3 experiments the error of the solution of the system of equations, namely $\|Ae-r\|$ (where $e$ is the solution vector, $r$ is the right hand side and $A$ is the block matrix (\ref{eq:simple_system}) ) exceeded 1.6e-9
+(namely, it was 1.6e-9 ($h=3.2e-5$), 1.3e-08 ($h=8e-6$), 1.04e-07 ($h=2e-6$)).
+
+Importantly, the obtained convergence rates are in agreement with standard estimates of \cite{brenner}.
+
+\subsubsection{Solution of $X$-Mode Prolbem}
+\paragraph{Convergence}
+Let us consider the case of the resonance, more precisely, we consider sufficiently smooth
+$\alpha,\delta$, s.t. $\alpha(0)=0$ and $\delta(0)\neq 0$, and the solvability conditions 
+of Theorem \ref{}  are satisfied. 
+For simplicity, let us consider 
+\begin{align}
+\label{eq:cond}
+ \alpha(x)=-x \text{  in some neighbourhood of $0$ }.
+\end{align}
+
+Given the space $\mathbf{V}_{h}=S_{h}^{1}\times S_{h}^{1}$, with $S_{h}^{1}$ consisting of piecewise-linear (hat) functions, we look for a ratio $h(\nu)$ that would ensure that the absolute error 
+\begin{align}
+\label{eq:problem1}
+\|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}<\epsilon,
+\end{align}
+given a fixed value of $\epsilon>0$.
+
+We use the following well-known facts:
+\begin{itemize}
+ \item The C\'ea's lemma applied to the problem (\ref{}); here $C_c$ is the continuity and $C_i$ is the coercivity constants:
+\begin{align}
+\label{eq:cea}
+\begin{split}
+ \|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|_{V}\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}
+ \leq \nu^{-1}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}.
+ \end{split}
+\end{align}
+The last inequality follows from Theorem \ref{}.  
+\item The form of the exact solution to the problem (\ref{}):
+\begin{align}
+\label{eq:exact}
+ E_x^{\nu}=E_{2}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f(x)}{\alpha(x)+i\nu},
+\end{align}
+for some $f(x)\in L_{2}(\Omega)$.
+\item The estimate from \cite[Chapter 0]{Brenner_Scott} on the rate of convergence of the interpolation 
+\begin{align}
+\label{eq:bsc}
+ \|v-I^{h}v\|_{L_{2}(\Omega)}\leq Ch^2|v''|_{L_{2}(\Omega)},\; C>0,\\
+ %\|v-I^{h}v\|_{H_{1}(\Omega)}\leq Ch|v''|_{L_{2}(\Omega)},\; C>0, 
+\end{align}
+where $I^{h}v$ is an interpolation operator onto $S_{h}^{1}$.
+\end{itemize}
+For $E_x^{\nu},\;f(x)$ in (\ref{eq:exact}) being sufficiently smooth, 
 \begin{align*}
-\|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|_{V}\leq 
+ \frac{d^2}{dx^2}E_x^{\nu}=\frac{f''}{\alpha+i\nu}-2\frac{f'\alpha'}{(\alpha+i\nu)^2}+\frac{f\alpha''}{(\alpha+i\nu)^3},
 \end{align*}
-\end{lemma}
-\begin{proof}
-The C\'ea's lemma states 
+from which, together with (\ref{eq:cond}), it follows that there exists $c>0$ s.t. for all sufficiently small $\nu$ 
 \begin{align*}
- \|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V},
+ \left|  \frac{d^2}{dx^2}E_x^{\nu}\right|_{L_2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
+ %\\
+ %&=c\left.
+ %\left(\frac{x}{4(x^2+\nu^2)^2}\nu^{-2}+\frac{3x}{8(x^2+\nu^2)}\nu^{-4}+\frac{3}{8}\nu^{-5}\operatorname{atan}\frac{x}{\nu}\right)\right|_{-L}^{H}
+ \leq C\nu^{-5},\; 
 \end{align*}
-where $C_c$ is the continuity and $C_i$ is the coercivity constants.
-Indeed,
+where $C>0$ does not depend on $\nu$. This, together with the estimates (\ref{eq:cea}) and (\ref{eq:bsc}), results in 
 \begin{align*}
- \min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}\leq \min_{\mathbf{v}\in V_h}\|\mathbf{E}-I^{h}\mathbf{v}\|,
+ \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}\leq C\nu^{-\frac{7}{2}}h^2,
 \end{align*}
-where $I^{h}\mathbf{v}$ is an interpolation operator. The estimates from \cite[Chapter 0]{Brenner_Scott} give us
+from which it follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
+\begin{align}
+\label{eq:estimate_h}
+ h=\alpha_{\epsilon}\nu^{\frac{7}{4}},
+\end{align}
+where $\alpha_{\epsilon}>0$ depends on $\epsilon$ but does not depend on $\nu$.
+
+Let us check whether this holds true. 
+To do so, we conduct the  numerical experiment with parameters for the problem as given in Table \ref{tab:parameters}.
+\begin{table}
+\begin{tabular}{l|r}
+Parameter & Value \\
+\hline
+$\alpha(x)$ & $\left\{\begin{array}{cc}
+10, & x\leq -10,\\
+-x, & -10<x\leq 5,\\
+-5, & x>5.
+\end{array}\right.$ \\
+$\delta(x)$ & 
+$\left\{\begin{array}{cc}
+0, & x\leq -10,\\
+4/30x+4/3,& -10<x\leq 5,\\
+2, & x>5.
+\end{array}\right.$ \\
+$g^{inc}(-L)$ & $-2 \sqrt{2}i\exp(-22\sqrt{2}i)$\\
+$\lambda$ & 
+$\sqrt{10}$\\
+$L$& 15\\
+$H$ & 10 \\
+\end{tabular}
+\caption{The parameters for the problem with the resonance}
+\label{tab:parameters}
+\end{table}
+
+ We fix $\nu$ and compute the error of the solution compared to the solution computed on the finest mesh  (with $h=2e-6$). 
+ The results are depicted in Figures \ref{} and \ref{fig:l2_err_e2}.
+ \begin{figure}
+
+ \end{figure}
+
+\begin{figure}
+\begin{tabular}{cc}
+\begin{tikzpicture}
+    \begin{loglogaxis}[
+    	width=0.49\textwidth,
+    	height=0.5\textwidth,
+        xlabel=$h$,
+        ylabel=$Error$,
+        legend style={
+at={(0.2,1.5)},
+legend pos= south east,
+anchor=south east, 
+draw=none, 
+font=\tiny
+}
+]
+\addplot[mark=*,blue] table {pics/result_l2e1.1.dat}; 
+\addlegendentry{$\nu=1$};
+\addplot[mark=*,green] table {pics/result_l2e1.0.25.dat}; 
+\addlegendentry{$\nu=2^{-2}$};
+\addplot[mark=*,red] table {pics/result_l2e1.0.0625.dat}; 
+\addlegendentry{$\nu=2^{-4}$};
+\addplot[mark=square,blue] table {pics/result_l2e1.0.015625.dat}; 
+\addlegendentry{$\nu=2^{-6}$};
+\addplot[mark=square,green] table {pics/result_l2e1.0.0039062.dat}; 
+\addlegendentry{$\nu=2^{-8}$};
+\addplot[mark=triangle,red] table {pics/result_l2e1.0.00097656.dat}; 
+\addlegendentry{$\nu=2^{-10}$};
+\addplot[mark=triangle,blue] table {pics/result_l2e1.0.00024414.dat}; 
+\addlegendentry{$\nu=2^{-12}$};
+\addplot[mark=triangle, green] table {pics/result_l2e1.6.1035e-05.dat};
+\addlegendentry{$\nu=2^{-14}$};
+\addplot[mark=triangle, red] table{pics/result_l2e1.1.5259e-05.dat};
+\addlegendentry{$\nu=2^{-16}$};
+\end{loglogaxis}
+\end{tikzpicture} &
+\begin{tikzpicture}
+    \begin{loglogaxis}[
+    	width=0.49\textwidth,
+    	height=0.5\textwidth,
+        xlabel=$h$,
+        ylabel=$Error$,
+        legend style={
+at={(0.2,1.5)},
+legend pos= south east,
+anchor=south east, 
+draw=none,
+font=\tiny
+}
+]
+\addplot[mark=*,blue] table {pics/result_l2e2.1.dat}; 
+\addlegendentry{$\nu=1$};
+\addplot[mark=*,green] table {pics/result_l2e2.0.25.dat}; 
+\addlegendentry{$\nu=2^{-2}$};
+\addplot[mark=*,red] table {pics/result_l2e2.0.0625.dat}; 
+\addlegendentry{$\nu=2^{-4}$};
+\addplot[mark=square,blue] table {pics/result_l2e2.0.015625.dat}; 
+\addlegendentry{$\nu=2^{-6}$};
+\addplot[mark=square,green] table {pics/result_l2e2.0.0039062.dat}; 
+\addlegendentry{$\nu=2^{-8}$};
+\addplot[mark=square, red] table {pics/result_l2e2.0.00097656.dat}; 
+\addlegendentry{$\nu=2^{-10}$};
+\addplot[mark=triangle,blue] table {pics/result_l2e2.0.00024414.dat}; 
+\addlegendentry{$\nu=2^{-12}$};
+\addplot[mark=triangle, green] table{pics/result_l2e2.6.1035e-05.dat};
+\addlegendentry{$\nu=2^{-14}$};
+\addplot[mark=triangle, red] table{pics/result_l2e2.1.5259e-05.dat};
+\addlegendentry{$\nu=2^{-16}$};
+\end{loglogaxis}
+\end{tikzpicture} 
+\end{tabular}
+\caption{In the left figure we show the $L_{2}$-error of $E_{x}(x)$, and in the right figure the $L_2$-error of $E_y(x)$ is shown.}
+\label{fig:l2_err_e2}
+\end{figure}
+
+Let us denote by $E_{1}^{h}$ the solution $E_{1}(x)$ computed on the mesh with a width $h$, and by $E_{1}^{c}$ the solution computed on the finest mesh. We introduce 
+\begin{align}
+\label{eq:def_epsilon}
+h_{\epsilon}=\sup\{h: \|E_{1}^{h'}-E_{1}^{c}\|<\epsilon \text{ for all } h'<h\}.
+\end{align}
+The computed dependence of $h_{\epsilon}$ on $\nu$ is shown in Figure \ref{fig:dependence}.
+\begin{figure}
+\begin{tikzpicture}
+    \begin{loglogaxis}[
+    	width=0.7\textwidth,
+        xlabel=$\nu$,
+        ylabel=$h_{\epsilon}$,
+        legend style={
+at={(0.2,1.5)},
+legend pos= south east,
+anchor=south east, 
+draw=none
+}
+]
+\addplot[mark=*,blue] table {pics/h1e-1.dat}; 
+\addlegendentry{$\epsilon=1e-1$};
+%\addplot[mark=o,red] table {pics/h1e-2.dat}; 
+%\addlegendentry{$\epsilon=1e-2$};
+\addplot[mark=triangle,green] table {pics/h1e-3.dat}; 
+\addlegendentry{$\epsilon=1e-3$};
+%\addplot[mark=square,cyan] table {pics/h1e-4.dat}; 
+%\addlegendentry{$\epsilon=1e-4$};
+\addplot[dashed, red] table {pics/nu1.dat}; 
+\addlegendentry{$O(\nu)$};
+\addplot[dashed, blue] table {pics/nu32.dat}; 
+\addlegendentry{$O(\nu^{\frac{3}{2}})$};
+\end{loglogaxis}
+\end{tikzpicture} 
+\caption{The depenence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$.}
+\label{fig:dependence}
+\end{figure}
+
+We can see that the estimate (\ref{eq:estimate_h}) is pessimistic compared to the one suggested by (\ref{eq:def_epsilon}), 
+at least for a given value of $\epsilon$.
+
+\begin{remark}
+ We can show that 
 \begin{align*}
- \|E_1-I^{h}E_1\|_{L_{2}(\Omega)}\leq Ch^2|E_1''|_{L_{2}(\Omega)},\\
- \|E_2-I^{h}E_2\|_{H_{1}(\Omega)}\leq Ch|E_2''|_{H_{1}(\Omega)}.
+ \|E^{\nu}_{x}\|_{L_{2}(\Omega)}\leq \frac{C}{\sqrt{\nu}},\; C>0, 
 \end{align*}
-To obtain these bounds, we require an explicit bound on $E_1, \; E_2$. In \cite{Despers et al Hybrid} 
-it was shown that 
-%\begin{align*}
+and thus the relative error control
+\begin{align*}
+ \frac{\|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}}{\|E^{\nu}_{x}\|_{L_{2}(\Omega)}}\leq \epsilon
+\end{align*}
+can be ensured by choosing $h$ as $\beta_{\epsilon}\nu^{\frac{3}{4}}$.
+\end{remark}
 
-%\end{align*}
+\paragraph{Condition Number}
 
-\end{proof}
+We consider the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
+on $\nu$, for several values of $h$ (see Table \ref{tab:cond_number}).
+\begin{table}[ht!]
+\begin{tabular}{c|ccccccccc}
+\diagbox[width=10em]{$h$}{$\nu$}& 100 & 10 & 1 & 0.1 & 1e-2 & 1e-3 & 1e-4 & 1e-8 & 0\\
+ \hline
+1 & 3.9634&4.3787 &4.987&36.949&42.394& 42.757 &42.79&42.793&42.793\\
+\hline
+0.5&      3.9931& 6.87&48.473 & 168.41  &207.34  & 209.63 & 209.83 & 209.85&  209.85\\
+\hline
+ 0.1&      16.09  &     159.56  &     1146.1   &    8304.1   &     19169  &      20270   &     20344   &     20352   &     20352\\
+ \hline
+0.05&      64.046  &     637.18  &     4686.2   &     38876 &  1.4e5 &  1.58e5 &   1.58e5 &  1.58e5 &  1.58e5\\
+\hline
+ 0.01&       1600    &   15921 & 1.2e5  & 1.1e6 & 8.3e6  & 1.8e7   & 1.93e7  & 1.93e7  & 1.93e7\\
+\end{tabular}
+\caption{The condition number of the matrix of the system (\ref{eq:simple_system}) for different values of $\nu$ and $h$. }
+\label{tab:cond_number}
+\end{table}
+Remarkably, for $\nu=0$ the computed matrices are not singular; perhaps the bilinear form $a(u,v)$ is coercive on the chosen discrete subspace of $(L_{2}(\Omega); H^{1}(\Omega)$ .
+\subsection{Limiting Amplitude and Limited Absorption Principles}
+In this section we perform several numerical experiments,
+with the normalization chosen as $\epsilon_0=\mu_0=1$, $\omega=c=1$. 
+Also, we set $m_e=1$ and $e=-1$. From this it follows that $\omega_c=-B_0$ and $\omega_p^2=N_e$. 
+We consider the following two cases:
+\begin{itemize}
+ \item case $N_e\neq \operatorname{const}$, no resonance
+ \item case $N_e\neq \operatorname{const}$, resonance
+\end{itemize}
+For every fixed absorption rate $\nu$, in the time domain we choose the boundary conditions of the form
+\begin{align}
+\label{eq:bcs}
+\left.\partial_t H\right|_{x=-L}&=-\left.\partial_x E_y\right|_{x=-L}=G\sin(t),\; G\in \mathbb{R}, \\
+ \nonumber
+ \left.\partial_t H\right|_{x=H}&=0,
+\end{align}
+and zero initial conditions, and in the frequency domain
+\begin{align*}
+ \left.\partial_x \hat{E}_y\right|_{x=-L}&=G,\\
+ \left.\partial_x \hat{E}_y\right|_{x=H}&=0.
+\end{align*}
+We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain (the solution computed numerically at the time step $n$ is denoted by $\mathbf{E}^{\nu}_{n}$), and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain.
+Our goal is to check whether
+\begin{align*}
+\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t)=\Im\left(\hat{\mathbf{E}}^{\nu}\exp(it)\right).
+\end{align*}
+\subsubsection{No-Resonance Case}
+We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{2}$ satisfies 
+the Airy equation \cite{}.
 
-\subsection{Discretization of the Time Domain Problem}
-\section{Numerical Experiments}
-\subsection{Frequency Domain}
-\subsection{Time Domain}
+We set $\omega_c=0$ (thus $\delta(x)=0$), $\omega=1$ (hence $\alpha(x)=1-N_e(x)$), 
+choose the domain as $[-0.5, 10]$ and set the electron density $N_e(x)=1+x$. Importantly, $N_e(x)>0$ on the whole interval.
+The boundary conditions in (\ref{eq:bcs}) are chosen as $G=Ai'(0.5)$. 
+In all the experiments in this section the CFL number was chosen to be equal to 0.5.
+
+First let us fix $\nu=1e-2$. 
+To demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
+inside the domain $(-L,\; H)$ and plot the dependence of the solution $E_{2}^{\nu}(x_c,t), \; \hat{E}_2^{\nu}(x_c)\mathrm{e}^{it}$ 
+on time $t$ for a range of $t\gg 1$ in Figure \ref{fig:nu1e2_harmon}.

### 2015-01-20 report/intro.tex
\sqrt{alpha}-> lambda + remark about \sqrt{\alpha) and antennas in intro.tex
bug fix
minor changes #3
small fixes
intro draft

@@
 
-We consider the set of Maxwell equations with a linear current in two dimensions \cite{stable_yee_plasma_current}
- with absorption terms
+ In the case of heating devices for fusion experiment, for example, one can find itself dealing with what is called hybrid resonnance.
+Hybrid resonnance may cause Maxwell's equation with strong magnetic fields to develop singular solutions \textcolor{red}{insert refs}.
+The energy deposit is resonant and may exceed by far the energy exchange which occurs in Landau damping \textcolor{red}{ref}.
+Contrary to the Landau Dumping, however, hybrid resonnance appears in a simpler model coupling fluid equations with the non electrostatic part of Maxwell equations.
+ As it can be found in \cite{stable_yee_plasma_current}, we consider the non-stationary Maxwell system  
+ \begin{align}
+ -\varepsilon_0 \partial_t \E + \curl\, \Hbf = \J\\
+ \mu_0 \partial_t \Hbf + \curl\,  \E = 0
+ \end{align}
+ coupled with a linear current in two dimensions $\J = -eN_e \ubf_e$
+
+ \[
+ m_e \partial_t \ubf_e =-e (\E +\ubf_e \nabla B_0).
+ \]
+ Here the unknows are the electromagnetc field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, $\J$ is the electronic current. We denote by $e$ the absolute value of the charge of elevtrons, 
   \begin{align*}
@@
 \end{align*}
+
+\textcolor{red}{!!!!!!maybe move this next part to later!!!!!!!!}
 \subsection{Boundary condition}
@@
 \be
--curl \E -\imath \sqrt{\alpha(-{ L})}\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath \sqrt{\alpha(-{ L})}\E_{inc} \wedge \n,
+-curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath \lambda\E_{inc} \wedge \n,
 \ee
-where  $\E_{inc} = \exp \left(\imath \sqrt{\alpha(-L)}x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$
+where  $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$
 
 $curl \E = 0$ at the right boundary
+\begin{remark}
+When modelling antennas in plasma physics, in such applications as ITER, a good choice of boundary condition could be the use of $\lambda = \sqrt{alpha(-L)}$
+\end{remark}
+\textcolor{red}{!!!!!!!!!!!!}

### 2015-01-20 report/absorption.tex
committing

@@
 The results for $\nu=10^{-2}$ (chosen as a parameter both in frequency and time domain) 
-are shown in Figure \ref{fig:resonance_nu1e2} and for $\nu=10^{-3}$ in Figure \ref{resonance_nu1e3}. 
+are shown in Figures \ref{fig:resonance_nu1e2_ex, fig:resonance_nu1e2_ey}. 
+In the time domain, we chose the discretization size $\Delta x=0.025$. 
+We display the harmonic dependence of the solution on time by fixing $x_c$ inside the domain and plotting 
+$E_x^{\nu}(x_c,t)$ and $E_y^{\nu}(x_c, t)$. We compare these solutions to $\hat{E}_x^{\nu}(x_c)\mathrm{e}^{it}$ and 
+$\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}$. In this case we choose $x_c=0$, where the resonance occurs. 
 \begin{figure}
 
- \caption{In the }
- \label{fig:resonance_nu1e2}
+ \caption{In the left figure we show the dependence of the solutions $E_x^{\nu}(0,t)$ on time $t$. 
+ In the right figure the solutions at time $t_c=...$ and $t_c=..$ are demonstrated and compared to
+ $\Im{\hat{E}_y\mathrm{e}^{it}}$.
+  \label{fig:resonance_nu1e2_ex}
 \end{figure}
 
+\begin{figure}
+
+ \caption{In the left figure we show the dependence of the solutions $E_x^{\nu}(0,t)$ on time $t$. 
+ In the right figure the solutions at time $t_c=...$ and $t_c=..$ are demonstrated and compared to
+ $\Im{\hat{E}_y\mathrm{e}^{it}}$.
+  \label{fig:resonance_nu1e2_ey}
+\end{figure}
+The $L_2$-error (\ref{eq:error}) on the time interval $()$ did not exceed $0.16$ for $E_x(x,t)$ and $0.085$ for $E_y(x,t)$.
+
 For $\nu=10^{-6}$, like in the previous case, we were not able to obtain the limiting amplitude solution in the time domain.

### 2015-01-20 report/intro.tex
committing

@@
 \section{Introduction}
+In the case of heating devices for fusion experiment, for example, 
+ one can find itself dealing with what is called hybrid resonnance. 
+ Hybrid resonance may cause Maxwell's equation with strong magnetic 
+ fields to develop singular solutions \textcolor{red}{insert refs}. 
+ The energy deposit is resonant and may exceed by far the energy 
+ exchange which occurs in Landau damping \textcolor{red}{ref}. 
+ Contrary to the Landau Dumping, however, 
+ hybrid resonnance appears in a simpler model coupling 
+ fluid equations with the non electrostatic part of Maxwell equations.
 
- In the case of heating devices for fusion experiment, for example, one can find itself dealing with what is called hybrid resonnance.
-Hybrid resonnance may cause Maxwell's equation with strong magnetic fields to develop singular solutions \textcolor{red}{insert refs}.
-The energy deposit is resonant and may exceed by far the energy exchange which occurs in Landau damping \textcolor{red}{ref}.
-Contrary to the Landau Dumping, however, hybrid resonnance appears in a simpler model coupling fluid equations with the non electrostatic part of Maxwell equations.
  As it can be found in \cite{stable_yee_plasma_current}, we consider the non-stationary Maxwell system  
@@
 \end{align}
- coupled with a linear current in two dimensions $\J = -eN_e \ubf_e$
-
- \[
- m_e \partial_t \ubf_e =-e (\E +\ubf_e \nabla B_0).
- \]
- Here the unknows are the electromagnetc field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, $\J$ is the electronic current. We denote by $e$ the absolute value of the charge of elevtrons, 
-  \begin{align*}
-\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\\
-\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\\
+coupled with a linear current in two dimensions $\J = eN_e \ubf_e$, taking into account the friction between electron and ions
+\be
+m_e \partial_t \ubf_e =e (\E +\ubf_e \nabla B_0) -m_e \nu \ubf_e. \label{eq:electronmove}
+\ee
+Here the unknows are the electromagnetc field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, $\J$ is the electronic current.
+We denote by $e<0$ the value of the charge of electrons and by $\m_e$ the electron mass0
+\begin{align}
+\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\nonumber\\
+\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\nonumber\\
 \mu_0\partial_t H+\partial_x E_y-\partial_y E_x=0,\\
-m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
-m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
-\end{align*}
+m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
+m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y\nonumber
+\end{align}
 posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. The boundary conditions
@@
 \end{align*}
-
 \textcolor{red}{!!!!!!maybe move this next part to later!!!!!!!!}
@@
 where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$
-
 $curl \E = 0$ at the right boundary

### 2015-01-20 report/intro.tex
modified intro a bit

@@
 \ee
-Here the unknows are the electromagnetc field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, $\J$ is the electronic current.
-We denote by $e<0$ the value of the charge of electrons and by $\m_e$ the electron mass0
+Here the unknows are the electromagnetc field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, $\J$ is the electronic current, 
+$\ubf_e$ is the velocity of electrons and $B_0$ is the background magnetic field.  
+We denote by $e<0$ the value of the charge of electrons and by $\m_e$ the electron mass.
+Assuming that $\mathbf{B}_0=\left(0,\; 0,\; B_0\right)$, we obtain the following system of equations 
 \begin{align}
+\label{eq:main_model}
+\begin{split}
 \epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\nonumber\\
@@
 m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y\nonumber
+\end{split}
 \end{align}
-posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. The boundary conditions
+posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. 
+In this work we look at a simplification of this model obtained after 
+the Fourier transform in $y$. Denoting by $\theta$ a corresponding Fourier variable, the model (\ref{eq:main_model}) can be rewritten as follows
+\begin{align}
+\label{eq:main_model_theta}
+\begin{split}
+\epsilon_0\partial_t E_{x}-\theta H=-eN_e u_x,\nonumber\\
+\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\nonumber\\
+\mu_0\partial_t H+\partial_x E_y-\theta E_x=0,\\
+m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
+m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y.
+\end{split}
+\end{align}
+It is known \cite{} that when the term $\nu=0$, the electron density $N_e(x)$ vanishes and in plasma there occurs a resonance \cite{Stix}, 
+which was recently investigated in \cite{}. It can be shown that the electric field $E_x$ in this case is no longer square 
+integrable \cite{}. 
+Thus, the goal of this article is two-fold. 
+First, following (\ref{}), we investigate the finite element approximation of the 
+problem (\ref{eq:main_model_theta}) written in the frequency domain:
+\begin{align*}
+
+\end{align*}
+We prove the well-posedness of this problem for $\nu>0$ in Section \ref{} and 
+demonstrate that the use of higher-order (P1) finite elements allows to approximate the singularity of the solution fairly well (Section \ref{}). 
+Second, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
+$\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
+the FDTD discretization (\ref{eq:main_model_theta}), suggested in \cite{}. We compare this result with 
+$\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, i.e.
+$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
+
+To our knowledge, such numerical studies have not been performed in the existing literature.
+
+The boundary conditions
 \begin{align*}

### 2015-01-20 report/intro.tex
intro upd #2

@@
 \end{align}
-It is known \cite{} that when the term $\nu=0$, the electron density $N_e(x)$ vanishes and in plasma there occurs a resonance \cite{Stix}, 
-which was recently investigated in \cite{}. It can be shown that the electric field $E_x$ in this case is no longer square 
-integrable \cite{}. 
+The energy of this system can be expressed as \cite{}
+\begin{align*}
+
+\end{align*}
+From this it can be seen that when the term $\nu=0$, the electron density $N_e(x)$ vanishes and in plasma there occurs a resonance \cite{Stix}, 
+which was recently investigated in \cite{}, in particular, it was shown that the electric field $E_x$ in this case is no longer square 
+integrable, and explicit estimates on the behaviour of the solutions of (\ref{eq:main_model_theta}) were given.
+
 Thus, the goal of this article is two-fold. 

### 2015-01-20 report/intro.tex
adding macros.sty

@@
 $\ubf_e$ is the velocity of electrons and $B_0$ is the background magnetic field.  
-We denote by $e<0$ the value of the charge of electrons and by $\m_e$ the electron mass.
+We denote by $e<0$ the value of the charge of electrons and by $m_e$ the electron mass.
 Assuming that $\mathbf{B}_0=\left(0,\; 0,\; B_0\right)$, we obtain the following system of equations 
@@
 \begin{split}
-\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\nonumber\\
-\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\nonumber\\
+\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\\
+\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\\
 \mu_0\partial_t H+\partial_x E_y-\partial_y E_x=0,\\
-m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
-m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y\nonumber
+m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
+m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
 \end{split}

### 2015-01-20 report/intro.tex
fixed!
changed intro

@@
 \begin{align*}
-
 \end{align*}
-From this it can be seen that when the term $\nu=0$, the electron density $N_e(x)$ vanishes and in plasma there occurs a resonance \cite{Stix}, 
-which was recently investigated in \cite{}, in particular, it was shown that the electric field $E_x$ in this case is no longer square 
+From this it can be seen that when the term $\nu=0$ and the electron density $N_e(x)$ vanishes, 
+in plasma there occurs a resonance \cite{Stix}. Mathematically, this effect was recently investigated in \cite{}, 
+in particular, it was shown that the electric field $E_x$ in this case is no longer square 
 integrable, and explicit estimates on the behaviour of the solutions of (\ref{eq:main_model_theta}) were given.
@@
 \begin{align*}
-
 \end{align*}

### 2015-01-20 report/intro.tex
adding first batch of refs

--- 2015-01-20 report/intro.tex
@@
 \end{align}
-The energy of this system can be expressed as \cite{}
+The energy of this system in a domain $\Omega$ can be expressed as \cite{stable_yee_plasma_current}
 \begin{align*}
+{\mathcal E}(t)= \int_\Omega \frac{1}{2\mu_0}|U(t,\x)|^2\mathrm{d}\x =\int_\Omega \left(
+\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|}{2|e|N_e(\x)} \mathrm{d}\x.
+\right)
+\end{align*}
 
-\end{align*}
-From this it can be seen that when the term $\nu=0$, the electron density $N_e(x)$ vanishes and in plasma there occurs a resonance \cite{Stix}, 
-which was recently investigated in \cite{}, in particular, it was shown that the electric field $E_x$ in this case is no longer square 
+From this it can be seen that when the term $\nu=0$ and the electron density $N_e(x)$ vanishes, 
+in plasma there occurs a resonance~\cite{Stix}. Mathematically, this effect was recently investigated in \textcolor{red}{citationtofix}\cite{}, 
+in particular, it was shown that the electric field $E_x$ in this case is no longer square 
 integrable, and explicit estimates on the behaviour of the solutions of (\ref{eq:main_model_theta}) were given.
@@
 Thus, the goal of this article is two-fold. 
-First, following (\ref{}), we investigate the finite element approximation of the 
+First, following (\textcolor{red}{reftofix}\ref{}), we investigate the finite element approximation of the 
 problem (\ref{eq:main_model_theta}) written in the frequency domain:
 \begin{align*}
-
 \end{align*}
-We prove the well-posedness of this problem for $\nu>0$ in Section \ref{} and 
-demonstrate that the use of higher-order (P1) finite elements allows to approximate the singularity of the solution fairly well (Section \ref{}). 
+We prove the well-posedness of this problem for $\nu>0$ in Section \textcolor{red}{reftofix}\ref{} and 
+demonstrate that the use of higher-order (P1) finite elements allows to approximate the singularity of the solution fairly well (Section \textcolor{red}{reftofix}\ref{}). 
 Second, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
 $\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
-the FDTD discretization (\ref{eq:main_model_theta}), suggested in \cite{}. We compare this result with 
+the FDTD discretization (\ref{eq:main_model_theta}), suggested in \textcolor{red}{citationtofix}\cite{}. We compare this result with 
 $\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, i.e.

### 2015-01-20 report/proc.tex
small fixes decided at the phone
changed the formulation of the theorem
experiments adding+ formatting has changed a bit
modified intro a bit
intro upd #2
adding first batch of refs

@@
 \usepackage{hyperref}
+%\usepackage{diagbox}
 \newenvironment{remark}[1][Remark]{\begin{trivlist}
@@
 \author{Bruno Depsr\'es}\address{Laboratoire Jacques-Louis Lions, University PARIS 6}
-\author{Lise-Marie Imbert}\address{Courant Institute of Mathematical Sciences, New York University}
-\author{Maryna Kachanovska}\address{UMA, ENSTA, Paris}
+\author{Lise-Marie Imbert-Gérard}\address{Courant Institute of Mathematical Sciences, New York University}
+\author{Maryna Kachanovska}\address{POEMS, INRIA, ENSTA ParisTech, Paris}
 
@@
 \input{timedomain}
-\input{absorption}
+%\input{absorption}
 \begin{thebibliography}{99}
-\bibitem{stable_yee_plasma_current} F. da Silva, M. Campos Pinto, B. Despres, S. Heuraux, Stable Coupling of the Yee Scheme with a Linear Current Model,
+\bibitem{stable_yee_plasma_current} F. da Silva M. Campos Pinto, B. Despres and S. Heuraux, Stable Coupling of the Yee Scheme with a Linear Current Model,
 2014
+\bibitem{Depres_2014} Després, B., Imbert-Gérard, L. M. and Weder, R. (2014). Hybrid resonance of Maxwell's equations in slab geometry. Journal de Mathématiques Pures et Appliquées, 101(5), 623-659.
+\bibitem{LMIG_thesis} Imbert-Gérard, L.
+M.
+(2013).
+Analyse mathématique et numérique de problèmes d'ondes apparaissant dans les plasmas magnétiques (Doctoral dissertation, Université Pierre et Marie Curie-Paris VI).
+\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
+\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
 \end{thebibliography}

### 2015-01-20 report/intro.tex
added some labels and ref (minor)

@@
 In this work we look at a simplification of this model obtained after 
-the Fourier transform in $y$. Denoting by $\theta$ a corresponding Fourier variable, the model (\ref{eq:main_model}) can be rewritten as follows
+the Fourier transform in $y$. Denoting by $\theta$ a corresponding Fourier variable, the model \eqref{eq:main_model} can be rewritten as follows
 \begin{align}
@@
 in particular, it was shown that the electric field $E_x$ in this case is no longer square 
-integrable, and explicit estimates on the behaviour of the solutions of (\ref{eq:main_model_theta}) were given.
+integrable, and explicit estimates on the behaviour of the solutions of \eqref{eq:main_model_theta} were given.
 
@@
 First, following (\textcolor{red}{reftofix}\ref{}), we investigate the finite element approximation of the 
-problem (\ref{eq:main_model_theta}) written in the frequency domain:
+problem \eqref{eq:main_model_theta} written in the frequency domain:
 \begin{align*}
+
 \end{align*}
-We prove the well-posedness of this problem for $\nu>0$ in Section \textcolor{red}{reftofix}\ref{} and 
+We prove the well-posedness of this problem for $\nu>0$ in Section~\ref{sec:wellposedness} and 
 demonstrate that the use of higher-order (P1) finite elements allows to approximate the singularity of the solution fairly well (Section \textcolor{red}{reftofix}\ref{}). 
@@
 $\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
-the FDTD discretization (\ref{eq:main_model_theta}), suggested in \textcolor{red}{citationtofix}\cite{}. We compare this result with 
+the FDTD discretization \eqref{eq:main_model_theta}, suggested in \textcolor{red}{citationtofix}\cite{}. We compare this result with 
 $\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, i.e.

### 2015-01-21 report/absorption.tex
extra changes
full working version of the documents

--- 2015-01-20 report/absorption.tex
@@
 \begin{itemize}
- \item case $N_e\neq \operatorname{const}$, no resonance
- \item case $N_e\neq \operatorname{const}$, resonance
+ \item case $N_e\neq \operatorname{const}$, no resonance;
+ \item case $N_e\neq \operatorname{const}$, resonance.
 \end{itemize}
@@
 We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain (the solution computed numerically at the time step $n$ is denoted by $\mathbf{E}^{\nu}_{n}$), and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain.
-Our goal is to check whether
+In the numerical experiments we check whether the following two quantities
 \begin{align*}
-\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t)=\Im\left(\hat{\mathbf{E}}^{\nu}\exp(it)\right).
+\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t), \text{ and } \Im\left(\hat{\mathbf{E}}^{\nu}\exp(it)\right)
 \end{align*}
-
+are close as $\nu\rightarrow 0$ (provided that the first of these quantities exists). 
 \subsubsection{No-Resonance Case}
-We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{2}$ satisfies 
-the Airy equation (\ref{}).
+We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{y}$ satisfies 
+the Airy equation.
 
 We set $\omega_c=0$ (thus $\delta(x)=0$), $\omega=1$ (hence $\alpha(x)=1-N_e(x)$), 
-choose the domain as $[-0.5, 10]$ and set the electron density $N_e(x)=1+x$. Importantly, $N_e(x)>0$ on the whole interval.
+choose the domain as $(-0.5, 10)$ and set the electron density $N_e(x)=1+x$. Importantly, $N_e(x)>0$ on the whole interval.
 The boundary conditions in (\ref{eq:bcs}) are chosen as $G=Ai'(0.5)$. 
-In all the experiments in this section the CFL number was chosen to be equal to 0.5.
+In all the experiments in this section the CFL number=0.5.
 
-First let us fix $\nu=1e-2$. 
-To demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
-inside the domain $(-L,\; H)$ and plot the dependence of the solution $E_{2}^{\nu}(x_c,t), \; \hat{E}_2^{\nu}(x_c)\mathrm{e}^{it}$ 
+First we set $\nu=10^{-2}$. To demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
+inside the domain and plot the dependence of the solution $E_{y}^{\nu}(x_c,t), \; \Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right)$ 
 on time $t$ for a range of $t\gg 1$ in Figure \ref{fig:nu1e2_harmon}.
@@
 \begin{figure}[htb]
-\includegraphics[width=0.9\textwidth]{figure_nu1e2-crop.pdf}
+\includegraphics[width=0.9\textwidth]{airy/figure_nu1e2-crop.pdf}
+\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time for $t\rightarrow +\infty$.}
  \label{fig:nu1e2_harmon}
@@
 
-In Figure \ref{fig:nu1e2_harmon2} (left figure) we compare this solution to the computed $\hat{E}_2^{\nu}\mathrm{e}^{it}$, for
+In Figure \ref{fig:nu1e2_harmon2} (left figure) we compare this solution to the computed $\hat{E}_y^{\nu}\mathrm{e}^{it}$, for
 fixed values of $t$. Both solutions appear to be in close agreement. 
 \begin{figure}[htb]
- \begin{tabular}{ll}
-\includegraphics[width=0.5\textwidth]{figure_nu1e2_2-crop.pdf}
+ \begin{tabular}{cc}
+\includegraphics[width=0.5\textwidth]{airy/figure_nu1e2_2-crop.pdf}
 &
-\includegraphics[width=0.5\textwidth]{figure_error_nu1e4-crop.pdf}\\
+\includegraphics[width=0.5\textwidth]{airy/figure_error_nu1e4-crop.pdf}\\
 \end{tabular}
-\caption{In the left figure we show the solution to (\ref{}) for $\nu=10^{-2}$, for two fixed moment of times. In the right figure 
+\caption{In the left figure we show the solution for $\nu=10^{-2}$, for two fixed moment of times. In the right figure 
 the dependence of the error (\ref{eq:error}) on time for $\nu=10^{-4}$ is demonstrated. 
-We can see that the error is decreasing.}
+We can see that the error is decreasing on the given time interval.}
  \label{fig:nu1e2_harmon2}
 \end{figure}
+\FloatBarrier
 The computed $L_2$ error
@@
 \label{eq:error}
-\mathcal{E}(t)=\|\Im\left(\hat{E}_y^{\nu}\exp(it)\right)-E_y^{\nu}(t)\|_{L_{2}(-L;H)}.
+\mathcal{E}_{x,y}(t)=\|\Im\left(\hat{E}_{x,y}^{\nu}\exp(it)\right)-E_{x,y}^{\nu}(t)\|_{L_{y}(-L;H)}.
 \end{align}
-for $\nu=1e-2$ did not exceed $1.1e-3$ for values of $t\in \left(28501,  30000\right)$.
+for $\nu=10^{-2}$ did not exceed 1.1e-3 for values of $t\in \left(28501,  30000\right)$.
 
-Figure show the solutions at fixed time steps for $\nu=1e-4$. As before, 
+Figure \ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=1e-4$. As previously, 
 to demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
-inside the domain $(-L,\; H)$ and plot 
-the dependence of the solution $E_{2}^{\nu}(x_c,t)$ on time $t$ for a range of $t\gg 1$. 
+inside the domain and plot 
+the dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time $t$ for a range of $t\gg 1$. 
 The error (\ref{eq:error}) for $\nu=1e-4$ at the time interval $[228000.05,\; 240000.05]$ does not exceed 2.8e-4. 
@@
 c.f. e.g. Figure \ref{fig:nu1e2_harmon2}. 
-We were not able to obtain the limiting amplitude solution for $t<3\cdot 10^{4}$, unlike in the case of $\nu=10^{-2}$. 
-For example, for $\nu=1e-6$ we were not able to reach the limiting amplitude solution even on the time interval $t\leq 1.92e6$, 
-see Figure \ref{fig:nu1e4_harmon}. 
+For $\nu=10^{-4}$ we were not able to obtain the limiting amplitude solution for $t<3\cdot 10^{4}$, unlike in the case of $\nu=10^{-2}$, 
+see also Figure \ref{fig:nu1e2_harmon2}(right). 
+For example, for $\nu=10^{-6}$ we were not able to reach the limiting amplitude solution even on the time interval $t\leq 1.92e6$, 
+see Figure \ref{fig:nu1e4_harmon} (right). 
 \begin{figure}
-\begin{tabular}{c}
- \includegraphics[width=\textwidth]{figure_nu1e4-crop.pdf}\\
- \includegraphics[width=\textwidth]{figure_nu1e6-crop.pdf}\\
+\begin{tabular}{cc}
+ \includegraphics[width=0.5\textwidth]{airy/figure_nu1e4-crop.pdf}&
+ \includegraphics[width=0.5\textwidth]{airy/figure_nu1e6-crop.pdf}\\
 \end{tabular}
-\caption{In the upper figure we plot the dependence of the solution $E_{2}^{\nu}(x_c,t)$ on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$. 
+\caption{In the upper figure we plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$. 
 In the lower figure we show the solution for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
@@
 \label{sec:resn}
-For the resonance case, we choose the parameters as given in Table \ref{tab:parameters_resonance}.
+For the resonance case, we choose the parameters as in Table \ref{tab:parameters_resonance}.
 \begin{table}[htb!]
@@
 $H$ & 19\\
-$\omega_c$ &  $\sqrt{0.5}$\\
+$\omega_c$ &  $-\sqrt{0.5}$\\
 $N_e(x)$ &  $\left\{
@@
 \end{tabular}
+\caption{Parameters for numerical simulations in Section \ref{sec:resn}}
 \label{tab:parameters_resonance}
-\caption{Parameters for numerical simulations in Section \ref{sec:resn}}
 \end{table}
-Since $\alpha(x)=(1-2N_e(x))$, $\alpha(0)=0$. Clearly, $\delta(0)\neq 0$ (resonance case).
+Since $\alpha(x)=(1-2N_e(x))$, $\alpha(0)=0$, and clearly, $\delta(0)\neq 0$.
 
-The results for $\nu=1e-2$ (chosen as a parameter both in frequency and time domain) 
-are shown in Figure \ref{resonance_nu1e2}.
+We compare the results for $\nu=10^{-2},\; 10^{-3}$ in Figures \ref{fig:resonance_nus_ex_x}, 
+\ref{fig:resonance_nus_ey_x}, \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}. 
+%In the time domain, we chose the discretization size $\Delta x=0.025$. 
+The harmonic dependence of the solution on time is demonstrated by fixing $x_c$ inside the domain and plotting 
+$E_x^{\nu}(x_c,t)$ and $E_y^{\nu}(x_c, t)$ for a range of $t$. We compare these solutions to $\Im\left(\hat{E}_x^{\nu}(x_c)\mathrm{e}^{it}\right)$ and 
+$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right)$. In the former case we choose the point $x_c=0$, where the resonance occurs.
+
+\begin{figure}
+\begin{tabular}{cc}
+\includegraphics[width=0.5\textwidth]{res/ex_fixed_x-crop.pdf}&
+\includegraphics[width=0.5\textwidth]{res/ex_fixed_x_1e3-crop.pdf}
+\end{tabular}
+\caption{The figures demonstrate the dependence of the solutions 
+$E_x^{\nu}(0,t)$ on time $t$ for different values of $\nu$. }
+\label{fig:resonance_nus_ex_x}
+\end{figure}
+\begin{figure}
+\begin{tabular}{cc}
+\includegraphics[width=0.5\textwidth]{res/ey_fixed_x-crop.pdf}&
+\includegraphics[width=0.5\textwidth]{res/ey_fixed_x_1e3-crop.pdf}
+ \end{tabular}
+\caption{The figures demonstrate the dependence of the solutions 
+$E_y^{\nu}(-2.5125,t)$ on time $t$ for different values of $\nu$. }
+\label{fig:resonance_nus_ey_x}
+\end{figure}
+
+\begin{figure}
+\begin{tabular}{cc}
+\includegraphics[width=0.5\textwidth]{res/ex_fixed_t-crop.pdf}&
+\includegraphics[width=0.5\textwidth]{res/ex_fixed_t_1e3-crop.pdf}
+\end{tabular}
+\caption{The figures demonstrate the dependence of the solutions 
+$E_y^{\nu}(x,t)$ on $x$ for fixed values of $t$. }
+\label{fig:resonance_nus_ex_t}
+\end{figure}
+\begin{figure}
+\begin{tabular}{cc}
+\includegraphics[width=0.5\textwidth]{res/ey_fixed_t-crop.pdf}&
+\includegraphics[width=0.5\textwidth]{res/ey_fixed_t_1e3-crop.pdf}
+ \end{tabular}
+\caption{The figures demonstrate the dependence of the solutions 
+$E_y^{\nu}(x,t)$ on $x$ for fixed values of $t$. }
+\label{fig:resonance_nus_ey_t}
+\end{figure}
+
+We can see that in the case of the resonance, the solution seem to achieve the limiting amplitude solution, 
+and both solutions are in relatively close agreement (but the point where the resonance occurs). 
+Similarly to the case with the regular case, 
+longer computations are needed to achieve the limiting amplitude solution  
+for smaller $\nu$.

### 2015-01-21 report/intro.tex
extra changes
full working version of the documents

--- 2015-01-20 report/intro.tex
@@
 \section{Introduction}
-In the case of heating devices for fusion experiment, for example, 
-one can find itself dealing with what is called hybrid resonnance. 
-Hybrid resonance may cause Maxwell's equation with strong magnetic 
-fields to develop singular solutions \textcolor{red}{insert refs}. 
+Modelling various phenomena in plasmas is of practical importance for developing new sources of energy 
+based on plasma fusion, see the ITER project\footnote{www.iter.org}. 
+In particular, this article concentrates on studying a phenomenon of a hybrid resonance \cite{Stix}, 
+which is observed in experiments  \textcolor{red}{insert refs}\cite{} and 
+mathematically is described as non-regularity of
+the solutions of Maxwell equations in plasmas under strong background magnetic field \cite{Despres_2014}. 
 The energy deposit is resonant and may exceed by far the energy 
 exchange which occurs in Landau damping \textcolor{red}{ref}. 
-Contrary to the Landau Dumping, however, 
-hybrid resonnance appears in a simpler model coupling 
+Contrary to the Landau damping, however, 
+hybrid resonance appears in a simpler model coupling 
 fluid equations with the non electrostatic part of Maxwell equations.
 
-As it can be found in \cite{stable_yee_plasma_current}, we consider the non-stationary Maxwell system  
+We consider the model of cold plasma of \cite{Stix} which is described by the non-stationary Maxwell system  
 \begin{align}
@@
 \end{align}
-coupled with a linear current in two dimensions $\J = eN_e \ubf_e$, taking into account the friction between electron and ions
+coupled with a linear current in two dimensions $\J = eN_e \ubf_e$, and takes into account the friction  $\nu$ between particles
 \be
@@
 \ee
-Here the unknows are the electromagnetc field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, $\J$ is the electronic current, 
-$\ubf_e$ is the velocity of electrons and $B_0$ is the background magnetic field.  
-We denote by $e<0$ the value of the charge of electrons and by $m_e$ the electron mass.
-Assuming that $\mathbf{B}_0=\left(0,\; 0,\; B_0\right)$, we obtain the following system of equations 
+The unknows are the electromagnetic field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, 
+the electronic current $\J$, 
+and the velocity of electrons $\ubf_e$. Here $B_0$ is the background magnetic field, typically assumed to be uniform in time and space.  
+We denote by $e<0$ the value of the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density that in general 
+depends on spatial variables and is uniform in time. 
+Without loss of generality, we set $\mathbf{B}_0=\left(0,\; 0,\; B_0\right)$, which allows to obtain the following system of equations 
 \begin{align}
@@
 posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. 
+The energy of this system for $\nu=0$ in a domain $\Omega$ can be expressed as \cite{stable_yee_plasma_current}
+\begin{align*}
+{\mathcal E}(t)= \int_\Omega \left(
+\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|}{2|e|N_e(\x)} \mathrm{d}\x.
+\right)
+\end{align*}
+From this it can be seen that if the electron density $N_e(x)$ vanishes, 
+the energy blows up~\cite{stable_yee_plasma_current}. 
+Mathematically, this effect was recently investigated in \cite{Despres_2014}, 
+in particular, it was shown that the electric field $E_x$ in this case is no longer square 
+integrable, and explicit estimates on the behaviour of the solutions of \eqref{eq:main_model} in 1D were given.
+
 In this work we look at a simplification of this model obtained after 
-the Fourier transform in $y$. Denoting by $\theta$ a corresponding Fourier variable, the model (\ref{eq:main_model}) can be rewritten as follows
+the Fourier transform of (\ref{eq:main_model}) in $y$.
+
+The goal of this article is two-fold. 
+First, we investigate the finite element approximation of the 1D 
+problem \eqref{eq:main_model} written in the frequency domain ($\partial_t\rightarrow i\omega$), with 
+linearized dielectric tensor (see \cite{Despres_2014}):
 \begin{align}
-\label{eq:main_model_theta}
-\begin{split}
-\epsilon_0\partial_t E_{x}-\theta H=-eN_e u_x,\nonumber\\
-\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\nonumber\\
-\mu_0\partial_t H+\partial_x E_y-\theta E_x=0,\\
-m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
-m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y.
-\end{split}
+\label{eq:main_frequency_domain}
+\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}+\frac{\omega^2}{c^2}
+\left(\epsilon_0(\omega)+\nu Id\right)\hat{\mathbf{E}}=0,\\
+\nonumber
+\epsilon_0(\omega)=\left(
+\begin{matrix}
+ \alpha & i\delta \\
+ -i\delta & \alpha 
+\end{matrix}
+\right), \\
+\nonumber
+\alpha(\omega)=1-\frac{\omega\omega_p^2}{\omega(\omega^2-\omega_c^2)},\qquad 
+\nonumber
+\delta(\omega)=\frac{\omega_c\omega_p^2}{\omega(\omega^2-\omega_c^2)},\\
+\nonumber
+\omega_c=-\frac{eB_0}{m_e},\; \omega_p^2=\frac{e^2 N_e}{\epsilon_0 m_e}.
 \end{align}
-The energy of this system can be expressed as \cite{}
-\begin{align*}
-\end{align*}
-From this it can be seen that when the term $\nu=0$ and the electron density $N_e(x)$ vanishes, 
-in plasma there occurs a resonance \cite{Stix}. Mathematically, this effect was recently investigated in \cite{}, 
-in particular, it was shown that the electric field $E_x$ in this case is no longer square 
-integrable, and explicit estimates on the behaviour of the solutions of (\ref{eq:main_model_theta}) were given.
-
-Thus, the goal of this article is two-fold. 
-First, following (\ref{}), we investigate the finite element approximation of the 
-problem (\ref{eq:main_model_theta}) written in the frequency domain:
-\begin{align*}
-\end{align*}
-We prove the well-posedness of this problem for $\nu>0$ in Section \ref{} and 
-demonstrate that the use of higher-order (P1) finite elements allows to approximate the singularity of the solution fairly well (Section \ref{}). 
+\urev{Additionally, we assume $\alpha(\omega)$ and $\delta(\omega)$ be sufficiently smooth, i.e. bounded and continuous in  
+$\left[-L,\; \mathbb{R}\right)$.}
+In particular, we again investigate this problem in one dimension, performing the Fourier transform in $y$.
+We prove the well-posedness of this problem for $\nu>0$ in Section~\ref{sec:wellposedness} and 
+demonstrate that the use of higher-order (P1) finite elements allows to approximate the singularity 
+of the solution fairly well (Section \ref{sec:freq_dep}). 
 Second, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
 $\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
-the FDTD discretization (\ref{eq:main_model_theta}), suggested in \cite{}. We compare this result with 
+the FDTD discretization of \eqref{eq:main_model}, suggested in \cite{stable_yee_plasma_current}. 
+We compare this result with 
 $\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, i.e.
@@
 
-The boundary conditions
-\begin{align*}
-H|_{-L}=g(t).
-\end{align*}
-\textcolor{red}{!!!!!!maybe move this next part to later!!!!!!!!}
-\subsection{Boundary condition}
-Robin Boundary condition at the left boundary of the domain
+To solve the problem (\ref{eq:main_model}) numerically, we equip it with the following boundary conditions.
+At the left boundary of the domain we choose Robin boundary conditions 
 \be
--curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath \lambda\E_{inc} \wedge \n,
+-curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
 \ee
-where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$
-$curl \E = 0$ at the right boundary
+where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$. We truncate the domain 
+$(-L,\; \mathbb{R})$ to $(-L,\; H)$ and set on the right boundary $\operatorname{curl} \E = 0$. 
 \begin{remark}
-	When modelling antennas in plasma physics, in such applications as ITER, a good choice of boundary condition could be the use of $\lambda = \sqrt{alpha(-L)}$
+	When modelling antennas in plasma physics, in such applications as ITER, 
+	a good choice of boundary condition could be $\lambda = \sqrt{\alpha(-L)}$
 \end{remark}
-\textcolor{red}{!!!!!!!!!!!!}

### 2015-01-21 report/numerics.tex
full working version of the documents

@@
-\section{Discretization of the Frequency Domain Problem}
-\label{sec:discr}
-Testing the variational formulation (\ref{eq:varformulation}) with $(\tilde E_x,0)$ and $(0,\; \tilde{E}_y)\in\mathbf{V}(\Omega)$, we can rewrite it as a system of two equations:
-\begin{align*}
-\begin{split}
-i\theta \displaystyle \int_{-L}^H (E_y' -\imath\theta E_x)\overline{\tilde E_x} - \int_{-L}^H \left((\epsilon_0 +\imath\nu \operatorname{Id}) \E\right)_{1} \overline{\tilde E}_{x}
-&=0,\\
-\displaystyle \int_{-L}^H (E_y' -\imath\theta E_x)\tilde {E_y'} - \int_{-L}^H\left( (\epsilon_0 +\imath\nu\operatorname{Id}) \E\right)_{2}\overline{\tilde{E}}_{y}
-  - \imath \sqrt{\alpha(-L)} E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
-  \text{ for all } \tilde E_x\in L_{2}(\Omega), \; \tilde{E}_{y}\in H_{1}(\Omega).
-  \end{split}
-\end{align*}
-Inserting an explicit expression for the dielectric permittivity tensor 
-\be \label{eq:epsilonmu}
- \epsilon_0(x) =
-\left(
-\begin{array}{cc}
-\alpha(\x) & \imath \delta (\x)\\
--\imath \delta (\x) & \alpha(\x)
-\end{array}
-\right)
-\ee
-into the above, we obtain
-\begin{align}
-\label{eq:var_form2}
-\begin{split}
- i\theta \displaystyle \int_{-L}^H (E_y' -\imath\theta E_x)\overline{\tilde E_x} - 
- \int_{-L}^H \left((\alpha+i\nu)E_x+\imath\delta E_y\right)_{1} \overline{\tilde E}_{x}
-&=0,\\
-\int_{-L}^H (E_y' -\imath\theta E_x)\tilde {E_y'} -
-\int_{-L}^H\left( -\imath \delta E_x+(\alpha+i\nu) E_y\right)_{2}\overline{\tilde{E}}_{y}
-  - \imath \sqrt{\alpha(-L)} E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
-  \text{ for all } \tilde E_x\in L_{2}(\Omega), \; \tilde{E}_{y}\in H_{1}(\Omega).
-  \end{split}
-\end{align}
-Let us introduce the basis spaces $V_{E_x}=\{\psi_{j}\}_{j=1}^{N_{1}}$ and $V_{E_{2}}=\{\phi_{i}\}_{i=1}^{N_{2}}$, we look for the solution of the problem (\ref{}) in the form:
-\begin{align*}
-E_x=\sum\limits_{k=1}^{N_{1}}e_{1k}\psi_{k},\; E_{2}=\sum\limits_{k=1}^{N_{2}}e_{2k}\phi_{k}.
-\end{align*}
-
-% Substituting $\tilde{E}_{x}=\psi_{m}, \; m=1,\ldots,N_{1}$ and $\tilde{E}_{y}=0$ into the variational formulation (\ref{}), we obtain:
-% \begin{align*}
-% i\theta\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}\bar{\psi}_{m}dx+\theta^2\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx\\
-% -\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{k}\bar{\psi}_{m}dx-i\sum\limits_{1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\delta(x)\phi_{k}(x)\bar{\psi}_{m}dx=0.
-% \end{align*}
-% Similarly, for $\tilde{E}_{x}=0$ and $\tilde{E}_{y}=\phi_{\ell},\; \ell=1,\ldots, N_{2}$:
-% \begin{align*}
-% \sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx-i\theta\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}(x)\bar{\phi}'_{\ell}(x)dx\\
-% +i
-% \sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\delta(x)\psi_{k}\bar{\phi}_{m}dx-\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\phi_{k}\bar{\phi}_{m}dx\\
-% -
-% i\lambda\sum\limits_{k=1}^{N_{2}}e_{2k}\phi_{k}(-L)\bar{\phi}_{m}(-L)=-g_{inc}(x)\bar{\phi}_{m}(-L).
-% \end{align*}
-After introduction 
-\begin{align*}
-\left(K^{\psi,\phi'}\right)_{mk}=\int\limits_{-L}^{H}\bar{\psi}_{m}\phi'_{k}dx,\qquad \left(M^{\psi}\right)_{mk}=\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx,\\
-\left(M^{\alpha,\psi}\right)_{mk}=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{m}\bar{\psi}_{k}dx, \qquad \left(M^{\delta,\psi,\phi}\right)_{mk}=\int\limits_{-L}^{H}\delta(x)\bar{\psi}_{m}\phi_{k}dx,\\
-K_{\ell k}=\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx,\qquad \left(M^{\alpha,\phi}\right)_{\ell k}=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\bar{\phi}_{\ell}\phi_{k}dx,\\
-I_{km}^{\Gamma}=\bar{\phi}_{m}(-L)\phi_{k}(-L),\\
-\boldsymbol{e}_{x}=\left(e_{11},\ldots,e_{1 N_{1}}\right)^{T},\; \boldsymbol{e}_{y}=\left(e_{21},\ldots,e_{2 N_{1}}\right)^{T},\\
-\boldsymbol{0}_{n} \text{ is an $n$-dimensional zero column vector}.
-\end{align*}
-the system (\ref{eq:var_form2}) can be rewritten in an antisymmetric block form:
-\begin{align*}
-\left(\begin{matrix}
-\theta^2 M_{\psi}-M^{\alpha,\psi} & i\theta K^{\psi,\phi'}-i M^{\delta,\psi,\phi} \\
--i\theta (K^{\psi,\phi'})^{*}+i (M^{\delta,\psi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
-\end{matrix}\right)
-\left(
-\begin{matrix}
-\boldsymbol{e}_x\\
-\boldsymbol{e}_y
-\end{matrix}
-\right)=-g_{inc}(-L)
-\left(
-\begin{matrix}
-\boldsymbol{0}_{N_{1}}\\
-\bar{\phi}_{x}(-L)\\
-\bar{\phi}_{y}(-L)\\
-\vdots\\
-\bar{\phi}_{N_{2}}(-L)
-\end{matrix}
-\right).
-\end{align*}
-This expression greatly simplifies when choosing $V_{E_x}=V_{E_{2}}=\left(\phi_{m}\right)_{m=1}^{N_{2}}$ and in the case $\theta=0$:
-\begin{align}
-\label{eq:simple_system}
-\left(\begin{matrix}
-M^{\alpha,\phi} & i M^{\delta,\phi,\phi} \\
-i (M^{\delta,\phi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
-\end{matrix}\right)
-\left(
-\begin{matrix}
-\boldsymbol{e}_x\\ 
-\boldsymbol{e}_y
-\end{matrix}
-\right)=-g_{inc}(-L)
-\left(
-\begin{matrix}
-\boldsymbol{0}_{N_{1}}\\
-\bar{\phi}_{x}(-L)\\
-\bar{\phi}_{y}(-L)\\
-\vdots\\
-\bar{\phi}_{N_{2}}(-L)
-\end{matrix}
-\right).
-\end{align}
-
 \section{Numerical Experiments}
 This section is organized as follows. The first part is dedicated to the numerical implementation
-of the frequency domain formulation (\ref{}). We study the convergence of this formulation and the behaviour 
+of the frequency domain formulation (\ref{eq:main_frequency_domain}). We study the convergence of this formulation and the behaviour 
 of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
@@
 We implemented the scheme described in Section \ref{sec:discr} for a simple case of $P_{1}$-space used 
-for the approximation of $E_{1}$ and $E_{2}$ and $\theta=0$, thus working with the system (\ref{eq:simple_system}). 
+for the approximation of $E_{x}$ and $E_{y}$ and $\theta=0$, thus working with the system (\ref{eq:simple_system}). 
 We apply permutation to the above system 
@@
 and of the time domain code (computed for large values of time). 
-The time-domain code implements the scheme described in Section \ref{} and 
+The time-domain code implements the scheme described in Section \ref{sec:discr} and 
 is written in Fortran. 
 \subsection{Frequency Domain Problem}
+\label{sec:freq_dep}
 \subsubsection{Validity of Implementation}
@@
 \label{eq:bcs}
-\partial_{1}E_{2}(-L)+2iE_{2}(-L)=2iAi(-L)+Ai'(-L),\\
-\partial_{1}E_{2}(H)=0,
+\partial_{1}E_{y}(-L)+2iE_{y}(-L)=2iAi(-L)+Ai'(-L),\\
+\partial_{1}E_{y}(H)=0,
 \end{align}
-where $Ai(x)$ is the Airy function \cite{}.
+where $Ai(x)$ is the Airy function. 
+For more detail on Airy functions and the Airy equation see \cite[Chapter 10.4]{abramowitz_stegun}.
 
-It can be shown that $E_{y}$ thus satisfies the Airy equation \cite{}, and hence, with the choice of the boundary conditions as above, we obtain  
+It can be shown that $E_{y}$ thus satisfies the Airy equation, and hence, 
+with the choice of the boundary conditions as above, we obtain that 
 \begin{align*}
@@
 \begin{align*}
-\|E_{1}-E_{1}^{c}\|_{L_{2}(\Omega)}=\left(\int\limits_{\Omega}\left|E_{1}(x)-\sum\limits_{k=0}^{N}E_{1i}\phi_{i}\right|^2dx\right),
+\|E_{x}-E_{x}^{c}\|_{L_{2}(\Omega)}=\left(\int\limits_{\Omega}\left|E_{x}(x)-\sum\limits_{k=1}^{N}e_{xk}\phi_{k}\right|^2dx\right),
 \end{align*}
-where $\left(\phi_{i}\right)_{i=1}^{N}$ are $P_{1}$-finite elements and $E_{1}(x)$ is a known analytic solution.
-Similarly $\|E_{2}-E_{2}^{c}\|_{L_{2}(\Omega)}$ and $\|E_{2}-E_{2}^{c}\|_{H_{1}(\Omega)}$ are defined.
+where $\left(\phi_{i}\right)_{i=1}^{N}$ are $P_{1}$-finite elements and $E_{x}(x)$ is a known analytic solution.
+Similarly $\|E_{y}-E_{y}^{c}\|_{L_{2}(\Omega)}$ and $\|E_{y}-E_{y}^{c}\|_{H_{1}(\Omega)}$ are defined.
 
@@
         ylabel=$Error$,
+        width=0.6\textwidth,
         legend style={
@@
 }
-]
-    \addplot[mark=*,blue] table {pics/E1L2.dat}; 
-    \addlegendentry{$\|E_{1}-E_{1}^{c}\|_{L_{2}}$};
+]\addplot[mark=*,blue] table {pics/E1L2.dat}; 
+    \addlegendentry{$\|E_{x}-E_{x}^{c}\|_{L_{2}}$};
     \addplot[mark=*,red] table {pics/E2H1.dat};
-        \addlegendentry{$\|E_{2}-E_{2}^{c}\|_{H_{1}}$};
+        \addlegendentry{$\|E_{y}-E_{y}^{c}\|_{H_{1}}$};
 
           \addplot[mark=*,cyan] table {pics/E2L2.dat};
-        \addlegendentry{$\|E_{2}-E_{2}^{c}\|_{L_{2}}$};  
+        \addlegendentry{$\|E_{y}-E_{y}^{c}\|_{L_{2}}$};  
         \addplot[dotted] table{pics/E_h2.dat};
@@
 
-Importantly, the obtained convergence rates are in agreement with standard estimates of \cite{brenner}.
+Importantly, the obtained convergence rates are in agreement with known estimates of \cite{brenner}.
 
@@
 $\alpha,\delta$, s.t. $\alpha(0)=0$ and $\delta(0)\neq 0$, and the solvability conditions 
-of Theorem \ref{}  are satisfied. 
+of Lemma \ref{lemma:well_posedness}  are satisfied. 
 For simplicity, let us consider 
@@
 \end{align}
-
-Given the space $\mathbf{V}_{h}=S_{h}^{1}\times S_{h}^{1}$, with $S_{h}^{1}$ consisting of piecewise-linear (hat) functions, we look for a ratio $h(\nu)$ that would ensure that the absolute error 
+Given $\mathbf{V}_{h}=P_{h}^{1}\times P_{h}^{1}$, with $P_{h}^{1}$ consisting of piecewise-linear (hat) functions, 
+we look for a ratio $h(\nu)$ that would ensure that the absolute error 
 \begin{align}
@@
 \begin{itemize}
- \item The C\'ea's lemma applied to the problem (\ref{}); here $C_c$ is the continuity and $C_i$ is the coercivity constants:
+ \item The C\'ea's lemma applied to the problem (\ref{vf1dcase}); here $C_c$ is the continuity and $C_i$ is the coercivity constants:
 \begin{align}
@@
 \end{align}
-The last inequality follows from Theorem \ref{}.  
-\item The form of the exact solution to the problem (\ref{}):
+The last inequality follows from Lemma \ref{lemma:well_posedness}.  
+\item The form of the exact solution to the problem (\ref{vf1dcase}):
 \begin{align}
 \label{eq:exact}
- E_x^{\nu}=E_{2}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f(x)}{\alpha(x)+i\nu},
+ E_x^{\nu}=E_{y}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f(x)}{\alpha(x)+i\nu},
 \end{align}
 for some $f(x)\in L_{2}(\Omega)$. 
-\item The estimate from \cite[Chapter 0]{Brenner_Scott} on the rate of convergence of the interpolation 
+\item The estimate from \cite[Chapter 0]{brenner} on the rate of convergence of the interpolation 
 \begin{align}
 \label{eq:bsc}
- \|v-I^{h}v\|_{L_{2}(\Omega)}\leq Ch^2|v''|_{L_{2}(\Omega)},\; C>0,\\
- %\|v-I^{h}v\|_{H_{1}(\Omega)}\leq Ch|v''|_{L_{2}(\Omega)},\; C>0, 
+ \|v-I^{h}v\|_{L_{2}(\Omega)}\leq Ch^2|v''|_{L_{2}(\Omega)},\; C>0,
+ %\\ \|v-I^{h}v\|_{H_{1}(\Omega)}\leq Ch|v''|_{L_{2}(\Omega)},\; C>0, 
 \end{align}
-where $I^{h}v$ is an interpolation operator onto $S_{h}^{1}$.
+where $I^{h}v$ is an interpolation operator onto $P_{h}^{1}$.
 \end{itemize}
@@
  We fix $\nu$ and compute the error of the solution compared to the solution computed on the finest mesh  (with $h=2e-6$). 
- The results are depicted in Figures \ref{} and \ref{fig:l2_err_e2}.
- \begin{figure}
-
- \end{figure}
-
+ The results are depicted in Figures \ref{fig:dependence} and \ref{fig:l2_err_e2}.
 \begin{figure}
@@
     \begin{loglogaxis}[
-    	width=0.49\textwidth,
+    	width=0.5\textwidth,
     	height=0.5\textwidth,
@@
         ylabel=$Error$,
+        ymin=1e-8,
         legend style={
@@
 
-Let us denote by $E_{1}^{h}$ the solution $E_{1}(x)$ computed on the mesh with a width $h$, and by $E_{1}^{c}$ the solution computed on the finest mesh. We introduce 
+Let us denote by $E_{x}^{h}$ the solution $E_{x}(x)$ computed on the mesh with a width $h$, and by $E_{x}^{c}$ the solution computed on the finest mesh. We introduce 
 \begin{align}
 \label{eq:def_epsilon}
-h_{\epsilon}=\sup\{h: \|E_{1}^{h'}-E_{1}^{c}\|<\epsilon \text{ for all } h'<h\}.
+h_{\epsilon}=\sup\{h: \|E_{x}^{h'}-E_{x}^{c}\|<\epsilon \text{ for all } h'<h\}.
 \end{align}
@@
 \begin{figure}
+\begin{tabular}{cc}
 \begin{tikzpicture}
     \begin{loglogaxis}[
-    	width=0.7\textwidth,
+    	width=0.5\textwidth,
+    	height=0.5\textwidth,
         xlabel=$\nu$,
@@
 \end{tikzpicture} 
-\caption{The depenence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$.}
+&
+\includegraphics[width=0.5\textwidth]{figure1-crop.pdf}
+\end{tabular}
+\caption{In the left figure the depenence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated. 
+In the right figure we show the solutions for the problem for different values of $\nu$. }
 \label{fig:dependence}
@@
 
+\FloatBarrier
 \paragraph{Condition Number}
@@
 \end{table}
-Remarkably, for $\nu=0$ the computed matrices are not singular; perhaps the bilinear form $a(u,v)$ is coercive on the chosen discrete subspace of $(L_{2}(\Omega); H^{1}(\Omega)$ .
-\subsection{Limiting Amplitude and Limited Absorption Principles}
-In this section we perform several numerical experiments,
-with the normalization chosen as $\epsilon_0=\mu_0=1$, $\omega=c=1$. 
-Also, we set $m_e=1$ and $e=-1$. From this it follows that $\omega_c=-B_0$ and $\omega_p^2=N_e$. 
-We consider the following two cases:
-\begin{itemize}
- \item case $N_e\neq \operatorname{const}$, no resonance
- \item case $N_e\neq \operatorname{const}$, resonance
-\end{itemize}
-For every fixed absorption rate $\nu$, in the time domain we choose the boundary conditions of the form
-\begin{align}
-\label{eq:bcs}
-\left.\partial_t H\right|_{x=-L}&=-\left.\partial_x E_y\right|_{x=-L}=G\sin(t),\; G\in \mathbb{R}, \\
- \nonumber
- \left.\partial_t H\right|_{x=H}&=0,
-\end{align}
-and zero initial conditions, and in the frequency domain
-\begin{align*}
- \left.\partial_x \hat{E}_y\right|_{x=-L}&=G,\\
- \left.\partial_x \hat{E}_y\right|_{x=H}&=0.
-\end{align*}
-We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain (the solution computed numerically at the time step $n$ is denoted by $\mathbf{E}^{\nu}_{n}$), and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain.
-Our goal is to check whether
-\begin{align*}
-\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t)=\Im\left(\hat{\mathbf{E}}^{\nu}\exp(it)\right).
-\end{align*}
-\subsubsection{No-Resonance Case}
-We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{2}$ satisfies 
-the Airy equation \cite{}.
+Remarkably, for $\nu=0$ the computed matrices are not singular. \urev{We do not know the exact reason for such a behavior.}
+As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Figure \ref{fig:small_nu}. 
+\begin{figure}
+ \includegraphics[width=0.4\textwidth]{figure2-crop.pdf}
+ \caption{The plot shows $E_{y}^{\nu}$ computed on different meshes for small $\nu$. It can be seen that for meshes that are coarse 
+ with respect to $\nu$ (e.g. $\nu=10^{-4}, \; h=10^{-2}$, or $\nu=0,\; h=10^{-2}$), the computed solution seems to be only piecewise-continuous in $\nu$, 
+ while for finer meshes and $\nu>0$ the solution seems to be smooth. It can be also seen that for $h=10^{-2}$ and $h=10^{-3}$ the solutions 
+ computed for $\nu=0$ are indistinguishable on this scale.}
+ \label{fig:small_nu}
+\end{figure}
 
-We set $\omega_c=0$ (thus $\delta(x)=0$), $\omega=1$ (hence $\alpha(x)=1-N_e(x)$), 
-choose the domain as $[-0.5, 10]$ and set the electron density $N_e(x)=1+x$. Importantly, $N_e(x)>0$ on the whole interval.
-The boundary conditions in (\ref{eq:bcs}) are chosen as $G=Ai'(0.5)$. 
-In all the experiments in this section the CFL number was chosen to be equal to 0.5.
+%\subsubsection{No-Resonance Case}
+%We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{2}$ satisfies 
+%the Airy equation \cite{}.
 
-First let us fix $\nu=1e-2$. 
-To demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
-inside the domain $(-L,\; H)$ and plot the dependence of the solution $E_{2}^{\nu}(x_c,t), \; \hat{E}_2^{\nu}(x_c)\mathrm{e}^{it}$ 
-on time $t$ for a range of $t\gg 1$ in Figure \ref{fig:nu1e2_harmon}.
+%We set $\omega_c=0$ (thus $\delta(x)=0$), $\omega=1$ (hence $\alpha(x)=1-N_e(x)$), 
+%choose the domain as $[-0.5, 10]$ and set the electron density $N_e(x)=1+x$. Importantly, $N_e(x)>0$ on the whole interval.
+%The boundary conditions in (\ref{eq:bcs}) are chosen as $G=Ai'(0.5)$. 
+%In all the experiments in this section the CFL number was chosen to be equal to 0.5.
+
+%First let us fix $\nu=1e-2$. 
+%To demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
+%inside the domain $(-L,\; H)$ and plot the dependence of the solution $E_{y}^{\nu}(x_c,t), \; \hat{E}_2^{\nu}(x_c)\mathrm{e}^{it}$ 
+%on time $t$ for a range of $t\gg 1$ in Figure \ref{fig:nu1e2_harmon}.

### 2015-01-23 report/intro.tex
corrected multiple mistakes+extended the explanation slightly

@@
 First, we investigate the finite element approximation of the 1D 
-problem \eqref{eq:main_model} written in the frequency domain ($\partial_t\rightarrow i\omega$), with 
-linearized dielectric tensor (see \cite{Despres_2014}):
+problem \eqref{eq:main_model} written in the frequency domain ($\partial_t\rightarrow -i\omega$).
+\mrev{More precisely, 
+\begin{align*}
+%\label{eq:main_frequency_domain_1}
+\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-
+\epsilon(\omega)\hat{\mathbf{E}}=0,\\
+\epsilon(\omega)=\left(
+\begin{matrix}
+ \tilde{\alpha} & i\tilde{\delta} \\
+ -i\tilde{\delta}  & \tilde{\alpha}
+\end{matrix}
+\right),\\
+\tilde{\alpha}(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\tilde{\omega}\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)}\right),\qquad 
+\tilde{\delta}(\omega)=\frac{\omega_c\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)},\\
+\tilde{\omega}=\omega+i\nu,\qquad \omega_c=\mrev{\frac{eB_0}{m_e}},\qquad \omega_p^2=\frac{e^2 N_e}{\epsilon_0 m_e}.
+\end{align*}
+After expansion in $\nu\rightarrow 0$ and keeping lower-order terms only
+\begin{align*}
+ \tilde{\alpha}(\omega)=\alpha(\omega)+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}\frac{\omega^2}{c^2},\qquad \alpha(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\omega_p^2}{\omega^2-\omega_c^2}\right),\\
+ \tilde{\delta}(\omega)=\delta(\omega)-\frac{2i\omega^3\nu}{c^2(\omega^2-\omega_c^2)^2},\qquad \delta(\omega)=\frac{\omega\omega_c\omega_p^2}{c^2(\omega^2-\omega_c^2)}.
+\end{align*}
+Then the limiting absorption principle can be obtained leaving only the diagonal terms in the above expansion (see \cite{Despres_2014}):
 \begin{align}
 \label{eq:main_frequency_domain}
-\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}+\frac{\omega^2}{c^2}
+\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}
 \left(\epsilon_0(\omega)+\nu Id\right)\hat{\mathbf{E}}=0,\\
@@
 \end{matrix}
-\right), \\
-\nonumber
-\alpha(\omega)=1-\frac{\omega\omega_p^2}{\omega(\omega^2-\omega_c^2)},\qquad 
-\nonumber
-\delta(\omega)=\frac{\omega_c\omega_p^2}{\omega(\omega^2-\omega_c^2)},\\
-\nonumber
-\omega_c=-\frac{eB_0}{m_e},\; \omega_p^2=\frac{e^2 N_e}{\epsilon_0 m_e}.
+\right)
 \end{align}
+}
 \urev{Additionally, we assume $\alpha(\omega)$ and $\delta(\omega)$ be sufficiently smooth, i.e. bounded and continuous in  

### 2015-01-25 report/proc.tex
morawetz
full working version of the documents
corrected multiple mistakes+extended the explanation slightly
bruno's last name typo

@@
 \usepackage{hyperref}
-%\usepackage{diagbox}
+\usepackage{diagbox}
+\usepackage{color}
+\usepackage{placeins}
 \newenvironment{remark}[1][Remark]{\begin{trivlist}
@@
 \begin{document}
+\newcommand{\urev}[1]{{\color{red}#1}}
+\newcommand{\mrev}[1]{{\color{blue}#1}}
 
@@
 \author{C\'eline Caldini-Queiros}\address{Max Planck Institute für PlasmaPhysik, Garching bei Muenchen}
-\author{Bruno Depsr\'es}\address{Laboratoire Jacques-Louis Lions, University PARIS 6}
+\author{Bruno Despr\'es}\address{Laboratoire Jacques-Louis Lions, University PARIS 6}
 \author{Lise-Marie Imbert-Gérard}\address{Courant Institute of Mathematical Sciences, New York University}
@@
 \input{equations}
+
+\input{timedomain}
+\input{freqdomain}
 \input{numerics}
-\input{timedomain}
-%\input{absorption}
+\input{absorption}
+
 \begin{thebibliography}{99}
@@
 2014
-\bibitem{Depres_2014} Després, B., Imbert-Gérard, L. M. and Weder, R. (2014). Hybrid resonance of Maxwell's equations in slab geometry. Journal de Mathématiques Pures et Appliquées, 101(5), 623-659.
+\bibitem{Despres_2014} Després, B., Imbert-Gérard, L. M. and Weder, R. (2014). Hybrid resonance of Maxwell's equations in slab geometry. Journal de Mathématiques Pures et Appliquées, 101(5), 623-659.
 \bibitem{LMIG_thesis} Imbert-Gérard, L.
@@
 \bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
+\bibitem{Morawetz} Morawetz, C. S. (1962). The limiting amplitude principle. Communications on Pure and Applied Mathematics, 15(3), 349-361.
+\bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
+Handbook of mathematical functions
 \end{thebibliography}

### 2015-01-26 report/intro.tex
working on refs, add reflectometers exp, Dumont paper

@@
 based on plasma fusion, see the ITER project\footnote{www.iter.org}. 
-In particular, this article concentrates on studying a phenomenon of a hybrid resonance \cite{Stix}, 
-which is observed in experiments  \textcolor{red}{insert refs}\cite{} and 
-mathematically is described as non-regularity of
+In particular, this article concentrates on studying a phenomenon of hybrid resonance \cite{Stix}, 
+which is observed in experiments \cite{reflectometers_2006, reflectometers_2010, Dumont_2005} and 
+mathematically is described as the non-regularity of
 the solutions of Maxwell equations in plasmas under strong background magnetic field \cite{Despres_2014}. 
 The energy deposit is resonant and may exceed by far the energy 
-exchange which occurs in Landau damping \textcolor{red}{ref}. 
+exchange which occurs in Landau damping \cite{}. 
 Contrary to the Landau damping, however, 

### 2015-01-26 report/proc.tex
add some files
working on refs, add reflectometers exp, Dumont paper

@@
 %
-\begin{abstract} ... \end{abstract}
+\begin{abstract}
+\input{abstract}
+\end{abstract}
 %
-\begin{resume} ... \end{resume}
+\begin{resume} 
+\input{resume}
+\end{resume}
 %
@@
 \begin{thebibliography}{99}
-\bibitem{stable_yee_plasma_current} F. da Silva M. Campos Pinto, B. Despres and S. Heuraux, Stable Coupling of the Yee Scheme with a Linear Current Model,
-2014
+\bibitem{stable_yee_plasma_current} Da Silva F., Campos Pinto M., Despres B. and Heuraux S., (2014) Stable Coupling of the Yee Scheme with a Linear Current Model,
+\bibitem{reflectometers_2006} Da Silva, F., Heuraux, S and  Manso, M.
+(2006).
+Developments on reflectometry simulations for fusion plasmas: application to ITER position reflectometers.
+Journal of plasma physics, 72(06), 1205-1208.
+\bibitem{reflectometers_2010}Da Silva, F., Heuraux, S., Gusakov, E.
+Z., and Popov, A.
+(2010).
+A Numerical Study of Forward-and Backscattering Signatures on Doppler-Reflectometry Signals.
+Plasma Science, IEEE Transactions on, 38(9), 2144-2149.
 \bibitem{Despres_2014} Després, B., Imbert-Gérard, L. M. and Weder, R. (2014). Hybrid resonance of Maxwell's equations in slab geometry. Journal de Mathématiques Pures et Appliquées, 101(5), 623-659.
+\bibitem{Dumont_2005} Dumont, R.
+J., Phillips, C.
+K., and Smithe, D.
+N.
+(2005).
+Effects of non-Maxwellian species on ion cyclotron waves propagation and absorption in magnetically confined plasmas.
+Physics of Plasmas (1994-present), 12(4), 042508.
 \bibitem{LMIG_thesis} Imbert-Gérard, L.

### 2015-01-26 report/proc.tex
working on refs, add landau dumping refs
fix in first ref

@@
 \begin{thebibliography}{99}
-\bibitem{stable_yee_plasma_current} Da Silva F., Campos Pinto M., Despres B. and Heuraux S., (2014) Stable Coupling of the Yee Scheme with a Linear Current Model,
+\bibitem{stable_yee_plasma_current} Da Silva, F., Campos-Pinto, M., Després, B., and Heuraux, S. (2014). Stable coupling of the Yee scheme with a linear current model.
 \bibitem{reflectometers_2006} Da Silva, F., Heuraux, S and  Manso, M.
@@
 Physics of Plasmas (1994-present), 12(4), 042508.
+\bibitem{Freidberg_2007} Freidberg, J. P. (2007). Plasma physics and fusion energy. Cambridge university press.
 \bibitem{LMIG_thesis} Imbert-Gérard, L.
@@
 \bibitem{Morawetz} Morawetz, C. S. (1962). The limiting amplitude principle. Communications on Pure and Applied Mathematics, 15(3), 349-361.
+\bibitem{Mouhot_2011} Mouhot, C., and Villani, C. (2011). On landau damping. Acta mathematica, 207(1), 29-201.
 \bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.

### 2015-01-26 report/intro.tex
working on refs, add landau dumping refs
add 'see'

--- 2015-01-23 report/intro.tex
@@
 based on plasma fusion, see the ITER project\footnote{www.iter.org}. 
-In particular, this article concentrates on studying a phenomenon of a hybrid resonance \cite{Stix}, 
-which is observed in experiments  \textcolor{red}{insert refs}\cite{} and 
-mathematically is described as non-regularity of
+In particular, this article concentrates on studying a phenomenon of hybrid resonance \cite{Stix}, 
+which is observed in experiments (see \cite{reflectometers_2006, reflectometers_2010, Dumont_2005}) and 
+mathematically is described as the non-regularity of
 the solutions of Maxwell equations in plasmas under strong background magnetic field \cite{Despres_2014}. 
 The energy deposit is resonant and may exceed by far the energy 
-exchange which occurs in Landau damping \textcolor{red}{ref}. 
+exchange which occurs in Landau damping, see \cite{Freidberg_2007,Mouhot_2011}. 
 Contrary to the Landau damping, however, 

### 2015-01-26 report/abstract.tex
english abstract : first rough draft

Hybrid resonnance is a physical phenomenon that appears for example in the heating of plasma, and as such is of interest in the developping of new energy source, like for instance in the ITER project. In this paper we focus on the  non-regularity of
the solutions of Maxwell equations in plasmas under strong background magnetic field. Our purpose here is two-fold. On one hand we investigate the finite element approximation of the one dimensionnal problem written in the frequency domain, and on the other hand we investigate the finite difference approximation of the one dimensionnal time dependant problem. We will also compare the results of theses to differents methods.

### 2015-01-26 report/resume.tex
resume first draft : litteral translation of english abstract

La résonnance hybride est un phénomène physique qui apparait par exemple lorsque l'on chauffe un plasma, et est ainsi d'intérêt dans le développement d'une nouvelle source d'énergie, comme dans le cadre du projet ITER. Dans ce papier, nous nous concentrons sur la non régularité des solutions des équations de Maxwell pour les plasmas sous l'influence de champ magnétiques fort. Notre but est ici double. D'un côté nous regardons l'approximation à l'aide d'éléments finis du problème en une dimension écrit dans le domaine en fréquence, et de l'autre nous regardons l'approximation à l'aide de différences finies du problème en une dimension mais dépendant en temps. Nous comparons également les résultats de ces deux différentes méthodes.

### 2015-01-26 report/resume.tex
french accents fix

@@
-La résonnance hybride est un phénomène physique qui apparait par exemple lorsque l'on chauffe un plasma, et est ainsi d'intérêt dans le développement d'une nouvelle source d'énergie, comme dans le cadre du projet ITER.
-Dans ce papier, nous nous concentrons sur la non régularité des solutions des équations de Maxwell pour les plasmas sous l'influence de champ magnétiques fort.
+La r\'esonnance hybride est un ph\'enom\`ene physique qui apparait par exemple lorsque l'on chauffe un plasma, et est ainsi d'int\`er\^et dans le d\`eveloppement d'une nouvelle source d'\`energie, comme dans le cadre du projet ITER.
+Dans ce papier, nous nous concentrons sur la non r\`egularit\`e des solutions des \`equations de Maxwell pour les plasmas sous l'influence de champ magn\`etiques fort.
 Notre but est ici double.
-D'un côté nous regardons l'approximation à l'aide d'éléments finis du problème en une dimension écrit dans le domaine en fréquence, et de l'autre nous regardons l'approximation à l'aide de différences finies du problème en une dimension mais dépendant en temps.
-Nous comparons également les résultats de ces deux différentes méthodes.
+D'un c\^ot\`e nous regardons l'approximation \`a l'aide d'\`el\`ements finis du probl\`eme en une dimension \`ecrit dans le domaine en fr\`equence, et de l'autre nous regardons l'approximation \`a l'aide de diff\`erences finies du probl\`eme en une dimension mais d\`ependant en temps.
+Nous comparons \`egalement les r\`esultats de ces deux diff\`erentes m\`eth\^odes.

### 2015-01-26 report/resume.tex
small fixes in resume.tex

--- 2015-01-26 report/resume.tex
@@
-La résonnance hybride est un phénomène physique qui apparait par exemple lorsque l'on chauffe un plasma, et est ainsi d'intérêt dans le développement d'une nouvelle source d'énergie, comme dans le cadre du projet ITER.
-Dans ce papier, nous nous concentrons sur la non régularité des solutions des équations de Maxwell pour les plasmas sous l'influence de champ magnétiques fort.
+La r\'esonnance hybride est un ph\'enom\`ene physique qui apparait par exemple lorsque l'on chauffe un plasma, et est ainsi d'int\'er\^et dans le d\'eveloppement d'une nouvelle source d'\'energie, comme dans le cadre du projet ITER.
+Dans ce papier, nous nous concentrons sur la non r\'egularit\'e des solutions des \'equations de Maxwell pour les plasmas sous l'influence de champ magn\'etiques forts.
 Notre but est ici double.
-D'un côté nous regardons l'approximation à l'aide d'éléments finis du problème en une dimension écrit dans le domaine en fréquence, et de l'autre nous regardons l'approximation à l'aide de différences finies du problème en une dimension mais dépendant en temps.
-Nous comparons également les résultats de ces deux différentes méthodes.
+D'un c\^ot\'e nous regardons l'approximation \`a l'aide d'\'el\'ements finis du probl\`eme en une dimension \'ecrit dans le domaine en fr\'equence, et de l'autre nous regardons l'approximation \`a l'aide de diff\'erences finies du probl\`eme en une dimension mais d\'ependant en temps.
+Nous comparons \'egalement les r\'esultats de ces deux diff\'erentes m\'ethodes.

### 2015-01-27 report/intro.tex
added really bad sentence to emphasize more than the "additionnaly"
revised LM

@@
 
-We consider the model of cold plasma of \cite{Stix} which is described by the non-stationary Maxwell system  
+We consider the model of cold plasma of \cite{Stix} which is described by the 2D time-dependent Maxwell system  
 \begin{align}
@@
 \end{align}
-coupled with a linear current in two dimensions $\J = eN_e \ubf_e$, and takes into account the friction  $\nu$ between particles
+coupled with a linear electronic current  $\J = eN_e \ubf_e$, 
 \be
-m_e \partial_t \ubf_e =e (\E +\ubf_e \nabla B_0) -m_e \nu \ubf_e. \label{eq:electronmove}
+m_e \partial_t \ubf_e =e (\E +\ubf_e \wedge B_0) -m_e \nu \ubf_e, \label{eq:electronmove}
 \ee
-The unknows are the electromagnetic field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, 
-the electronic current $\J$, 
+where $\nu$ is  the friction  between particles.
+The unknowns are the electromagnetic fields $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, 
+ %the electronic current $\J$, 
 and the velocity of electrons $\ubf_e$. Here $B_0$ is the background magnetic field, typically assumed to be uniform in time and space.  
@@
 \label{eq:main_model}
-\begin{split}
-\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\\
-\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\\
-\mu_0\partial_t H+\partial_x E_y-\partial_y E_x=0,\\
+\left\{\begin{array}{l}
+\epsilon_0\partial_t E_{x}-\partial_y H_z=-eN_e u_x,\\
+\epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\\
+\mu_0\partial_t H_z+\partial_x E_y-\partial_y E_x=0,\\
 m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
 m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
-\end{split}
-\end{align}
-posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. 
-The energy of this system for $\nu=0$ in a domain $\Omega$ can be expressed as \cite{stable_yee_plasma_current}
+\end{array}
+\right.\end{align}
+posed in $[-L,\; \infty)\times \mathbb{R}$, for some $L>0$. This domain represents the physical case of a wave sent from a wall facing a plasma. 
+The energy of this system for $\nu=0$ in a domain $\Omega\in\mathbb R^2$ can be expressed as \cite{stable_yee_plasma_current}
 \begin{align*}
 {\mathcal E}(t)= \int_\Omega \left(
-\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|}{2|e|N_e(\x)} \mathrm{d}\x.
-\right)
+\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|}{2|e|N_e(\x)} 
+\right)\mathrm{d}\x.
 \end{align*}
-From this it can be seen that if the electron density $N_e(x)$ vanishes, 
+So if the electron density $N_e(x)$ vanishes, 
 the energy blows up~\cite{stable_yee_plasma_current}. 
 Mathematically, this effect was recently investigated in \cite{Despres_2014}, 
-in particular, it was shown that the electric field $E_x$ in this case is no longer square 
-integrable, and explicit estimates on the behaviour of the solutions of \eqref{eq:main_model} in 1D were given.
+in particular, it was shown that the electric field component $E_x$ in this case is no longer square 
+integrable, and explicit estimates on the behaviour of the solutions of \eqref{eq:main_model} in 1D were provided.
 
-In this work we look at a simplification of this model obtained after 
-the Fourier transform of (\ref{eq:main_model}) in $y$.
+We complement Problem (\ref{eq:main_model}) with the following boundary conditions.
+At the left boundary of the domain, which represents the wall, we choose Robin boundary conditions 
+\be
+-curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
+\ee
+where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$. We truncate the domain 
+$(-L,\; \infty)$ to $(-L,\; H)$ and set on the right boundary $\operatorname{curl} \E = 0$. 
+\begin{remark}
+	When modeling antennas in plasma physics, in such applications as ITER, 
+	a good choice of boundary condition could be $\lambda = \sqrt{\alpha(-L)}$
+\end{remark}
 
@@
 First, we investigate the finite element approximation of the 1D 
-problem \eqref{eq:main_model} written in the frequency domain ($\partial_t\rightarrow -i\omega$).
-\mrev{More precisely, 
-\begin{align*}
-%\label{eq:main_frequency_domain_1}
-\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-
-\epsilon(\omega)\hat{\mathbf{E}}=0,\\
-\epsilon(\omega)=\left(
-\begin{matrix}
- \tilde{\alpha} & i\tilde{\delta} \\
- -i\tilde{\delta}  & \tilde{\alpha}
-\end{matrix}
-\right),\\
-\tilde{\alpha}(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\tilde{\omega}\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)}\right),\qquad 
-\tilde{\delta}(\omega)=\frac{\omega_c\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)},\\
-\tilde{\omega}=\omega+i\nu,\qquad \omega_c=\mrev{\frac{eB_0}{m_e}},\qquad \omega_p^2=\frac{e^2 N_e}{\epsilon_0 m_e}.
-\end{align*}
-After expansion in $\nu\rightarrow 0$ and keeping lower-order terms only
-\begin{align*}
- \tilde{\alpha}(\omega)=\alpha(\omega)+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}\frac{\omega^2}{c^2},\qquad \alpha(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\omega_p^2}{\omega^2-\omega_c^2}\right),\\
- \tilde{\delta}(\omega)=\delta(\omega)-\frac{2i\omega^3\nu}{c^2(\omega^2-\omega_c^2)^2},\qquad \delta(\omega)=\frac{\omega\omega_c\omega_p^2}{c^2(\omega^2-\omega_c^2)}.
-\end{align*}
-Then the limiting absorption principle can be obtained leaving only the diagonal terms in the above expansion (see \cite{Despres_2014}):
-\begin{align}
-\label{eq:main_frequency_domain}
-\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}
-\left(\epsilon_0(\omega)+\nu Id\right)\hat{\mathbf{E}}=0,\\
-\nonumber
-\epsilon_0(\omega)=\left(
-\begin{matrix}
- \alpha & i\delta \\
- -i\delta & \alpha 
-\end{matrix}
-\right)
-\end{align}
-}
-\urev{Additionally, we assume $\alpha(\omega)$ and $\delta(\omega)$ be sufficiently smooth, i.e. bounded and continuous in  
-$\left[-L,\; \mathbb{R}\right)$.}
+problem \eqref{eq:main_model} written in the frequency domain ($\partial_t\rightarrow -i\omega$), with a linearized dielectric tensor with respect to $\nu$.
 In particular, we again investigate this problem in one dimension, performing the Fourier transform in $y$.
@@
 We compare this result with 
-$\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, i.e.
-$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
-
+$\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
+$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$. DRAWING A COMMUTATIVE DIAGRAM ?
 To our knowledge, such numerical studies have not been performed in the existing literature.
-
-To solve the problem (\ref{eq:main_model}) numerically, we equip it with the following boundary conditions.
-At the left boundary of the domain we choose Robin boundary conditions 
-\be
--curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
-\ee
-where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$. We truncate the domain 
-$(-L,\; \mathbb{R})$ to $(-L,\; H)$ and set on the right boundary $\operatorname{curl} \E = 0$. 
-\begin{remark}
-	When modelling antennas in plasma physics, in such applications as ITER, 
-	a good choice of boundary condition could be $\lambda = \sqrt{\alpha(-L)}$
-\end{remark}

### 2015-01-27 report/timedomain.tex
experiments adding+ formatting has changed a bit
full working version of the documents
add refs to yee plasma current paper on timedomain.tex
revised LM

@@
-The equations of consideration for the one dimensionnal model write as
+\section{Time Dependent Problem Discretization}
+EXPLAIN HOW IS THIS SYSTEM OBTAINED FROM THE SYSTEM PROVIDED IN THE INTRO
+
  \begin{align}
@@
  \end{align}
-We compute a numerical approximation of~\eqref{eq:tdpb} on a Cartesian grid using the Yee scheme.
-Let $n$ denote the time step, as usual $t_n = n \Delta t$.
-$H_z$ will then be taken on a half time step, and our equation, discretized in them write :
+We compute a numerical approximation of~\eqref{eq:tdpb} on a Cartesian grid using the Yee scheme, as  suggested in \cite{stable_yee_plasma_current}.
+Let $n$ denote the time step index, as usual $t_n = n \Delta t$.
+The unknown $H_z$ will then be discretized on half time steps, $t_{n+1/2}$.
+The time discretization of the system reads:
  \begin{align}
+ \left\{\begin{array}{l}
  \epsilon_0\frac{ E_{x}^{n+1}-E_x^{n}}{\Delta t}=-eN_e u_x, \nonumber\\
@@
  m_e\frac{u_{y}^{n+1}-u_y^{n}}{\Delta t}=eE_y-eu_xB_0-\nu m_e u_y.\nonumber
+\end{array}\right.
  \end{align}
- We discretize our equation on staggered grid, meaning $E_x$, $u_x$, $E_y$, $u_y$ and $H_z$ are not and the same grid.
-Evidently we already stated it for $H_z$ in the time discretization.
+The space discretization is performed on staggered grid, meaning $E_x$, $u_x$, $E_y$, $u_y$ and $H_z$ are not and the same grid points.
+RAPID JUSTIFICATION ?
 Fig.~\ref{schemepos} shows the positions of $Ex$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) on the discretized grid in space and time.
-We obtain the following discretized equations,
+The fully discretized system then reads
 
@@
 m_e \frac{u_y\ihnp-u_y\ihn}{\Delta t} = eN_e \frac{E_y\ihnp + E_y\ihn}{2}- \nu m_e \frac{u_y\ihnp +u_y\ihn}{2}-eB_0 \frac{u_x\midin+u_x\inp}{2},
+\label{eq:ns401}
 \ee
@@
 
-We first compute $H_z$ at time $n+1/2$ with \eqref{eq:ns3}. Then, \eqref{eq:ns2} gives the expression $E_y\ihnp$ as a function of known variables, and $u_y^{n+1}$, as follow
+It is now possible to describe explicitly how to solve the proviso discrete system.
+We first compute $H_z$ at time $n+1/2$ with \eqref{eq:ns3}.
+Then, \eqref{eq:ns2} gives the expression $E_y\ihnp$ as a function of known variables, and $u_y^{n+1}$, as follow
 \be
@@
 
-By incorporating this expression into \eqref{eq:ns5} we then obtain $u_y$ at time $n+1$ as a function of known variables and $u_x^{n+1}$, 
+By incorporating this expression into \eqref{eq:ns401} we then obtain $u_y$ at time $n+1$ as a function of known variables and $u_x^{n+1}$, 
 \be 
@@
 \ee
-which gives the following expression for $u_y\ihnp$
-
+or equivalently the explicit expression
 \begin{align}
 u_y\ihnp \left(m_e(1+\frac{\Delta t \nu}{2}) +\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right) =&\left(m_e(1-\frac{\Delta t \nu}{2}) -\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right)u_y\ihn +\Delta t eN_e E_y\ihn \nonumber\\
-&- \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x} - \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right),
+&- \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x} - \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right).
 \label{eq:ns7} 
 \end{align}
-which we write 
+To simplify this expression, consider
 \begin{align}
@@
 
-Now we just need an expression of $E_x\inp$ as a function of time $n$ variables and $u_x^{n+1}$ and putting \eqref{eq:ns7} in \eqref{eq:ns4}, the scheme will be explicit. 
-We can find such and expression in \eqref{eq:ns1}
+At this point only $E_x^{n+1}$ and $u_x^{n+1}$ still need to be computed. 
+Since \eqref{eq:ns1} reads
 \be 
-E_x\inp = E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2}.
+E_x\inp = E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2},
 \label{eq:ns8}
 \ee
-
-We then have the scheme
-
+we then have the scheme 
 \begin{align}
 m_e u_x\inp= & m_e u_x\midin  + \Delta t e N_e \frac{1}{2}\left( E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2}\right) + \Delta t  e N_e \frac{1}{2}E_x\midin -\Delta t\nu m_e\frac{u_x\inp+u_x \midin}{2}\nonumber\\
-&+  \frac{e B_O \Delta t}{2K_1}\Big(K_2 u_y\ihn +\Delta t eN_e E_y\ihn -  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}\nonumber\\
-&- \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right)\Big)+  \frac{1}{2}\Delta teB_0u_y\ihn,
+&+  \frac{e B_0 \Delta t}{2K_1}\Big(K_2 u_y\ihn +\Delta t eN_e E_y\ihn -  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}\nonumber\\
+&- \frac{e B_0 \Delta t}{2}\left(u_x\midin+u_x\inp\right)\Big)+  \frac{1}{2}\Delta teB_0u_y\ihn,
 \label{eq:ns9}
 \end{align}
-
-which one can simplify into
+which can be simplified as
 \begin{align}
-u_x & \left(me(1+\frac{\Delta t \nu}{2})+ \frac{(eB_0\Delta t)^2}{4K_1} + \frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\inp 
+ \left(me(1+\frac{\Delta t \nu}{2})+ \frac{(eB_0\Delta t)^2}{4K_1} + \frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\inp 
 = \left(me(1-\frac{\Delta t \nu}{2})- \frac{(eB_0\Delta t)^2}{4K_1} -\frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\midin \nonumber\\
-& + e \Delta t N_e E_x \midin  + \left( \frac{eB_0 \Delta t K_2}{2 K_1}+ \frac{e B_0 \Delta t}{2}\right) u_y\ihn - \frac{(e\Delta t)^2 N_e B_0}{2K_1}E_y\ihn  - \frac{e^2(\Delta t)^3 B_0}{4K_1}\frac{H_z \ipnh- H_z \inh}{\Delta x},
-&\label{eq:ns10} 
+ + e \Delta t N_e E_x \midin  + \left( \frac{eB_0 \Delta t K_2}{2 K_1}+ \frac{e B_0 \Delta t}{2}\right) u_y\ihn - \frac{(e\Delta t)^2 N_e B_0}{2K_1}E_y\ihn  - \frac{e^2(\Delta t)^3 B_0}{4K_1}\frac{H_z \ipnh- H_z \inh}{\Delta x},
+\label{eq:ns10} 
 \end{align}
 and the scheme is then fully explicit.
+
+To summarize, the algorithm to solve the discrete system \eqref{} is
+\begin{itemize}
+\item compute $H_z^{n+1/2}$ thanks to \eqref{eq:ns3},
+\item compute $E_y^{n+1/2}$ thanks to \eqref{eq:ns6},
+\item compute $u_y^{n+1}$ thanks to \eqref{eq:ns7bis},
+\item compute $u_x^{n+1}$ thanks to \eqref{eq:ns10},
+\item compute $E_x^{n+1}$ thanks to \eqref{eq:ns8}.
+\end{itemize}

### 2015-01-27 report/timedomain.tex
comments colored

@@
 \section{Time Dependent Problem Discretization}
-EXPLAIN HOW IS THIS SYSTEM OBTAINED FROM THE SYSTEM PROVIDED IN THE INTRO
+\textcolor{green}{EXPLAIN HOW IS THIS SYSTEM OBTAINED FROM THE SYSTEM PROVIDED IN THE INTRO}
 
@@
 The space discretization is performed on staggered grid, meaning $E_x$, $u_x$, $E_y$, $u_y$ and $H_z$ are not and the same grid points.
-RAPID JUSTIFICATION ?
-Fig.~\ref{schemepos} shows the positions of $Ex$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) on the discretized grid in space and time.
+\textcolor{green}{RAPID JUSTIFICATION ?}  Fig.~\ref{schemepos} shows the positions of $Ex$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) on the discretized grid in space and time.
 The fully discretized system then reads

### 2015-01-27 report/intro.tex
comments colored
anged intro.tex

@@
 The energy of this system for $\nu=0$ in a domain $\Omega\in\mathbb R^2$ can be expressed as \cite{stable_yee_plasma_current}
-\begin{align*}
+\nrev{\begin{align*}
 {\mathcal E}(t)= \int_\Omega \left(
-\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|}{2|e|N_e(\x)} 
+\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e N_e|\u (t,\x)|^2}{2} 
 \right)\mathrm{d}\x.
-\end{align*}
-So if the electron density $N_e(x)$ vanishes, 
-the energy blows up~\cite{stable_yee_plasma_current}. 
-Mathematically, this effect was recently investigated in \cite{Despres_2014}, 
-in particular, it was shown that the electric field component $E_x$ in this case is no longer square 
-integrable, and explicit estimates on the behaviour of the solutions of \eqref{eq:main_model} in 1D were provided.
+\end{align*}}
+\nrev{An energy-preserving scheme for discretizing (\ref{eq:main_model}) was recently developed in \cite{Despres_2014}. 
+It can be shown that for non-zero collision frequency $\nu$ the loss of energy is proportional to $\nu$, however, as $\nu\rightarrow0+$, it 
+does not vanish. This paradox had been investigated in \cite{Despres_2014}}.
 

### 2015-01-27 report/abstract.tex
corrected abstract

@@
-Hybrid resonnance is a physical phenomenon that appears for example in the heating of plasma, and as such is of interest in the developping of new energy source, like for instance in the ITER project.
-In this paper we focus on the  non-regularity of
-the solutions of Maxwell equations in plasmas under strong background magnetic field.
+Hybrid resonance is a physical phenomenon 
+that appears for example in the heating of plasma, 
+and as such is of interest in the developing of new sources of energy, 
+e.g. in the ITER project. In this paper we focus on the non-regularity of
+the solutions of Maxwell equations in plasmas 
+under strong background magnetic field. 
 Our purpose here is two-fold. 
-On one hand we investigate the finite element approximation of the one dimensionnal problem written in the frequency domain, and on the other hand we investigate the finite difference approximation of the one dimensionnal time dependant problem.
-We will also compare the results of theses to differents methods.
+On one hand we investigate the finite element approximation of the one-dimensional problem 
+written in the frequency domain, 
+and on the other hand we study the finite difference approximation 
+of the one-dimensional time dependant problem. 
+We compare the results of these two differents methods in the context of limiting absorption and limiting amplitude principles.

### 2015-01-27 report/intro.tex
corrected abstract

@@
 It can be shown that for non-zero collision frequency $\nu$ the loss of energy is proportional to $\nu$, however, as $\nu\rightarrow0+$, it 
-does not vanish. This paradox had been investigated in \cite{Despres_2014}}.
+does not vanish. This paradox had been recently investigated in \cite{Despres_2014}}.
 
@@
 $\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
-$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$. DRAWING A COMMUTATIVE DIAGRAM ?
+$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$. \textcolor{green}{DRAWING A COMMUTATIVE DIAGRAM ?}
 To our knowledge, such numerical studies have not been performed in the existing literature.

### 2015-01-27 report/timedomain.tex
first : comment all easy computations

@@
 \input{grid}
-
-It is now possible to describe explicitly how to solve the proviso discrete system.
+Some rapid computations left to the reader make it possible to show this discrete system is fully explicit.
+%It is now possible to describe explicitly how to solve the proviso discrete system.
 We first compute $H_z$ at time $n+1/2$ with \eqref{eq:ns3}.
 Then, \eqref{eq:ns2} gives the expression $E_y\ihnp$ as a function of known variables, and $u_y^{n+1}$, as follow
-\be
-E_y\ihnp = E_y\ihn - \frac{\Delta t }{\eps_0}\frac{H_z\ipnh-H_z\inh}{\Delta x} - \frac{\Delta t e N_e}{\eps_0}\frac{u_y\ihnp + u_y\ihn}{2}.
-\label{eq:ns5}
-\ee
-
-By incorporating this expression into \eqref{eq:ns401} we then obtain $u_y$ at time $n+1$ as a function of known variables and $u_x^{n+1}$, 
-\be 
-\begin{array}{l}
-u_y\ihnp m_e = m_e u_y\ihn + \Delta t eN_e \frac{E_y\ihn}{2}\\
-+ \Delta teN_e\left(E_y\ihn - \frac{\Delta t }{\eps_0}\frac{H_z\ipnh-H_z\inh}{\Delta x} - \frac{\Delta t e N_e}{\eps_0}\frac{u_y\ihnp + u_y\ihn}{2}\right) \\
--\nu \Delta t m_e \frac{u_y\ihnp +u_y\ihn}{2}-\Delta teB_0 \frac{u_x\midin-u_x\inp}{2},
-\end{array}
-\label{eq:ns6}
-\ee
-or equivalently the explicit expression
-\begin{align}
-u_y\ihnp \left(m_e(1+\frac{\Delta t \nu}{2}) +\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right) =&\left(m_e(1-\frac{\Delta t \nu}{2}) -\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right)u_y\ihn +\Delta t eN_e E_y\ihn \nonumber\\
-&- \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x} - \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right).
-\label{eq:ns7} 
-\end{align}
-To simplify this expression, consider
-\begin{align}
-u_y\ihnp K_1&= K_2 u_y\ihn +\Delta t eN_e E_y\ihn-  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}- \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right).
-\label{eq:ns7bis} 
-\end{align}
-with $K_1 =  m_e(1+\frac{\Delta t \nu}{2}) +\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}$ and $K_2 =m_e(1- \frac{\Delta t \nu}{2}) -\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}$.
-
-At this point only $E_x^{n+1}$ and $u_x^{n+1}$ still need to be computed. 
-Since \eqref{eq:ns1} reads
-\be 
-E_x\inp = E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2},
-\label{eq:ns8}
-\ee
-we then have the scheme 
-\begin{align}
-m_e u_x\inp= & m_e u_x\midin  + \Delta t e N_e \frac{1}{2}\left( E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2}\right) + \Delta t  e N_e \frac{1}{2}E_x\midin -\Delta t\nu m_e\frac{u_x\inp+u_x \midin}{2}\nonumber\\
-&+  \frac{e B_0 \Delta t}{2K_1}\Big(K_2 u_y\ihn +\Delta t eN_e E_y\ihn -  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}\nonumber\\
-&- \frac{e B_0 \Delta t}{2}\left(u_x\midin+u_x\inp\right)\Big)+  \frac{1}{2}\Delta teB_0u_y\ihn,
-\label{eq:ns9}
-\end{align}
-which can be simplified as
-\begin{align}
- \left(me(1+\frac{\Delta t \nu}{2})+ \frac{(eB_0\Delta t)^2}{4K_1} + \frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\inp 
-= \left(me(1-\frac{\Delta t \nu}{2})- \frac{(eB_0\Delta t)^2}{4K_1} -\frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\midin \nonumber\\
- + e \Delta t N_e E_x \midin  + \left( \frac{eB_0 \Delta t K_2}{2 K_1}+ \frac{e B_0 \Delta t}{2}\right) u_y\ihn - \frac{(e\Delta t)^2 N_e B_0}{2K_1}E_y\ihn  - \frac{e^2(\Delta t)^3 B_0}{4K_1}\frac{H_z \ipnh- H_z \inh}{\Delta x},
-\label{eq:ns10} 
-\end{align}
-and the scheme is then fully explicit.
-
-To summarize, the algorithm to solve the discrete system \eqref{} is
-\begin{itemize}
-\item compute $H_z^{n+1/2}$ thanks to \eqref{eq:ns3},
-\item compute $E_y^{n+1/2}$ thanks to \eqref{eq:ns6},
-\item compute $u_y^{n+1}$ thanks to \eqref{eq:ns7bis},
-\item compute $u_x^{n+1}$ thanks to \eqref{eq:ns10},
-\item compute $E_x^{n+1}$ thanks to \eqref{eq:ns8}.
-\end{itemize}
+%\be
+%E_y\ihnp = E_y\ihn - \frac{\Delta t }{\eps_0}\frac{H_z\ipnh-H_z\inh}{\Delta x} - \frac{\Delta t e N_e}{\eps_0}\frac{u_y\ihnp + u_y\ihn}{2}.
+%\label{eq:ns5}
+%\ee
+%
+%By incorporating this expression into \eqref{eq:ns401} we then obtain $u_y$ at time $n+1$ as a function of known variables and $u_x^{n+1}$, 
+%\be 
+%\begin{array}{l}
+%u_y\ihnp m_e = m_e u_y\ihn + \Delta t eN_e \frac{E_y\ihn}{2}\\
+%+ \Delta teN_e\left(E_y\ihn - \frac{\Delta t }{\eps_0}\frac{H_z\ipnh-H_z\inh}{\Delta x} - \frac{\Delta t e N_e}{\eps_0}\frac{u_y\ihnp + u_y\ihn}{2}\right) \\
+%-\nu \Delta t m_e \frac{u_y\ihnp +u_y\ihn}{2}-\Delta teB_0 \frac{u_x\midin-u_x\inp}{2},
+%\end{array}
+%\label{eq:ns6}
+%\ee
+%or equivalently the explicit expression
+%\begin{align}
+%u_y\ihnp \left(m_e(1+\frac{\Delta t \nu}{2}) +\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right) =&\left(m_e(1-\frac{\Delta t \nu}{2}) -\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right)u_y\ihn +\Delta t eN_e E_y\ihn \nonumber\\
+%&- \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x} - \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right).
+%\label{eq:ns7} 
+%\end{align}
+%To simplify this expression, consider
+%\begin{align}
+%u_y\ihnp K_1&= K_2 u_y\ihn +\Delta t eN_e E_y\ihn-  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}- \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right).
+%\label{eq:ns7bis} 
+%\end{align}
+%with $K_1 =  m_e(1+\frac{\Delta t \nu}{2}) +\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}$ and $K_2 =m_e(1- \frac{\Delta t \nu}{2}) -\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}$.
+%
+%
+%At this point only $E_x^{n+1}$ and $u_x^{n+1}$ still need to be computed. 
+%Since \eqref{eq:ns1} reads
+%\be 
+%E_x\inp = E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2},
+%\label{eq:ns8}
+%\ee
+%we then have the scheme 
+%\begin{align}
+%m_e u_x\inp= & m_e u_x\midin  + \Delta t e N_e \frac{1}{2}\left( E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2}\right) + \Delta t  e N_e \frac{1}{2}E_x\midin -\Delta t\nu m_e\frac{u_x\inp+u_x \midin}{2}\nonumber\\
+%&+  \frac{e B_0 \Delta t}{2K_1}\Big(K_2 u_y\ihn +\Delta t eN_e E_y\ihn -  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}\nonumber\\
+%&- \frac{e B_0 \Delta t}{2}\left(u_x\midin+u_x\inp\right)\Big)+  \frac{1}{2}\Delta teB_0u_y\ihn,
+%\label{eq:ns9}
+%\end{align}
+%which can be simplified as
+%\begin{align}
+% \left(me(1+\frac{\Delta t \nu}{2})+ \frac{(eB_0\Delta t)^2}{4K_1} + \frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\inp 
+%= \left(me(1-\frac{\Delta t \nu}{2})- \frac{(eB_0\Delta t)^2}{4K_1} -\frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\midin \nonumber\\
+% + e \Delta t N_e E_x \midin  + \left( \frac{eB_0 \Delta t K_2}{2 K_1}+ \frac{e B_0 \Delta t}{2}\right) u_y\ihn - \frac{(e\Delta t)^2 N_e B_0}{2K_1}E_y\ihn  - \frac{e^2(\Delta t)^3 B_0}{4K_1}\frac{H_z \ipnh- H_z \inh}{\Delta x},
+%\label{eq:ns10} 
+%\end{align}
+%and the scheme is then fully explicit.
+%
+%To summarize, the algorithm to solve the discrete system \eqref{} is
+%\begin{itemize}
+%\item compute $H_z^{n+1/2}$ thanks to \eqref{eq:ns3},
+%\item compute $E_y^{n+1/2}$ thanks to \eqref{eq:ns6},
+%\item compute $u_y^{n+1}$ thanks to \eqref{eq:ns7bis},
+%\item compute $u_x^{n+1}$ thanks to \eqref{eq:ns10},
+%\item compute $E_x^{n+1}$ thanks to \eqref{eq:ns8}.
+%\end{itemize}

### 2015-01-27 report/timedomain.tex
adding some precision/reformulation of some sentences on timedomain.tex

@@
 \section{Time Dependent Problem Discretization}
-\textcolor{green}{EXPLAIN HOW IS THIS SYSTEM OBTAINED FROM THE SYSTEM PROVIDED IN THE INTRO}
+In this section, we develop a discretization of the time dependant problem~\eqref{eq:main_model} in one dimension.
+In 1D, the derivatives with respect to $y$ vanish, and we are left with the following problem,
 
@@
 Let $n$ denote the time step index, as usual $t_n = n \Delta t$.
-The unknown $H_z$ will then be discretized on half time steps, $t_{n+1/2}$.
+It is standard (see \cite{Xu_2006,stable_yee_plasma_current }) to discretize the electrical field on the integer time step, whereas the other fields, as $H_z$, are discretized on half time steps, $t_{n+1/2}$.
 The time discretization of the system reads:
@@
  \end{align}
-The space discretization is performed on staggered grid, meaning $E_x$, $u_x$, $E_y$, $u_y$ and $H_z$ are not and the same grid points.
-\textcolor{green}{RAPID JUSTIFICATION ?}  Fig.~\ref{schemepos} shows the positions of $Ex$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) on the discretized grid in space and time.
+In Yee scheme, the differents components of the vector fields are defined on staggered points.
+We summarize this discretization on Fig.~\ref{schemepos} where the positions of $Ex$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) on the discretized grid in space and time are shown.
 The fully discretized system then reads

### 2015-01-27 report/timedomain.tex
C->c in timedomain.tex

@@
  \end{align}
-We compute a numerical approximation of~\eqref{eq:tdpb} on a Cartesian grid using the Yee scheme, as  suggested in \cite{stable_yee_plasma_current}.
+We compute a numerical approximation of~\eqref{eq:tdpb} on a cartesian grid using the Yee scheme, as  suggested in \cite{stable_yee_plasma_current}.
 Let $n$ denote the time step index, as usual $t_n = n \Delta t$.

### 2015-01-27 report/intro.tex
made a modification in intro.tex

--- 2015-01-27 report/intro.tex
@@
 The energy of this system for $\nu=0$ in a domain $\Omega\in\mathbb R^2$ can be expressed as \cite{stable_yee_plasma_current}
-\nrev{\begin{align*}
+\mrev{\begin{align*}
 {\mathcal E}(t)= \int_\Omega \left(
-\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e N_e|\u (t,\x)|^2}{2} 
+\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e N_e|\mathbf{u} (t,\x)|^2}{2} 
 \right)\mathrm{d}\x.
 \end{align*}}
-\nrev{An energy-preserving scheme for discretizing (\ref{eq:main_model}) was recently developed in \cite{Despres_2014}. 
+\mrev{An energy-preserving scheme for discretizing (\ref{eq:main_model}) was recently developed in \cite{Despres_2014}. 
 It can be shown that for non-zero collision frequency $\nu$ the loss of energy is proportional to $\nu$, however, as $\nu\rightarrow0+$, it 
-does not vanish. This paradox had been investigated in \cite{Despres_2014}}.
+does not vanish. This paradox had been recently investigated in \cite{Despres_2014}}.
 
@@
 \begin{remark}
-	When modeling antennas in plasma physics, in such applications as ITER, 
+	When modeling antennas in plasma physics \mrev{(e.g. in such applications as ITER)}, 
 	a good choice of boundary condition could be $\lambda = \sqrt{\alpha(-L)}$
@@
 $\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
-$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$. DRAWING A COMMUTATIVE DIAGRAM ?
+$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$, i.e. we check the validity of the scheme in Figure \ref{fig:limits}. 
+\begin{figure}
+\begin{tikzpicture}
+   \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em] {
+     \mathbf{E}^{\nu}(t) & \mathbf{E}^{0+}(t)\\
+     \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t} & 
+     \lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow \infty}\mathbf{E}^{\nu}(t)=\lim\limits_{t\rightarrow \infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}^{\nu}(t)\\
+     };
+  \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow\infty$} (m-2-1);
+  \path[-stealth, font=\scriptsize]   (m-1-1) edge node [above] {$\nu\rightarrow 0+$} (m-1-2);
+  \path[-stealth, font=\scriptsize]   (m-2-1) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
+  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow \infty$} (m-2-2);
+
+  % \path[-stealth] (m-2-1.east) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
+    %(m-1-2) edge node [right] {$\nu\rightarrow 0$} (m-2-2);
+\end{tikzpicture}
+ \caption{Schematic representation of the equivalence of the limited absorption and limiting amplitude principles.}
+ \label{fig:limits}
+\end{figure}
+
 To our knowledge, such numerical studies have not been performed in the existing literature.

### 2015-01-27 report/resume.tex
found the names of the 2 principles in french =)
typo in french accent

@@
-La r\'esonnance hybride est un ph\'enom\`ene physique qui apparait par exemple lorsque l'on chauffe un plasma, et est ainsi d'int\'er\^et dans le d\'eveloppement d'une nouvelle source d'\'energie, comme dans le cadre du projet ITER.
+La r\'esonnance hybride est un ph\'enom\`ene physique qui appara\^it par exemple lorsque l'on chauffe un plasma, et est ainsi d'int\'er\^et dans le d\'eveloppement d'une nouvelle source d'\'energie, comme dans le cadre du projet ITER.
 Dans ce papier, nous nous concentrons sur la non r\'egularit\'e des solutions des \'equations de Maxwell pour les plasmas sous l'influence de champ magn\'etiques forts.
@@
 D'un c\^ot\'e nous regardons l'approximation \`a l'aide d'\'el\'ements finis du probl\`eme en une dimension \'ecrit dans le domaine en fr\'equence, et de l'autre nous regardons l'approximation \`a l'aide de diff\'erences finies du probl\`eme en une dimension mais d\'ependant en temps.
-Nous comparons \'egalement les r\'esultats de ces deux diff\'erentes m\'ethodes.
+Nous comparons \'egalement les r\'esultats de ces deux diff\'erentes m\'ethodes dans le contexte des principes d'absorption limite et d'amplitude limite.

### 2015-01-27 report/intro.tex
fix ref
corrected one unclear part in FD.tex

@@
 based on plasma fusion, see the ITER project\footnote{www.iter.org}. 
-In particular, this article concentrates on studying a phenomenon of hybrid resonance \cite{Stix}, 
+This article concentrates on studying a phenomenon of hybrid resonance \cite{Stix}, 
 which is observed in experiments (see \cite{reflectometers_2006, reflectometers_2010, Dumont_2005}) and 
@@
 \begin{remark}
-	When modeling antennas in plasma physics \mrev{(e.g. in such applications as ITER)}, 
+	When modelling antennas in plasma physics \mrev{(e.g. in such applications as ITER)}, 
 	a good choice of boundary condition could be $\lambda = \sqrt{\alpha(-L)}$

### 2015-01-27 report/timedomain.tex
fixed a reference in proc.tex, changed minor things in timedomain.tex

@@
 \section{Time Dependent Problem Discretization}
-In this section, we develop a discretization of the time dependant problem~\eqref{eq:main_model} in one dimension.
-In 1D, the derivatives with respect to $y$ vanish, and we are left with the following problem,
-
+In this section, we develop a discretization of the time dependant problem~\eqref{eq:main_model} 
+in one dimension. In 1D, the derivatives with respect to $y$ vanish, and we are left with the following problem, 
  \begin{align}
@@
  \end{align}
-We compute a numerical approximation of~\eqref{eq:tdpb} on a cartesian grid using the Yee scheme, as  suggested in \cite{stable_yee_plasma_current}.
-Let $n$ denote the time step index, as usual $t_n = n \Delta t$.
-It is standard (see \cite{Xu_2006,stable_yee_plasma_current }) to discretize the electrical field on the integer time step, whereas the other fields, as $H_z$, are discretized on half time steps, $t_{n+1/2}$.
-The time discretization of the system reads:
+We compute a numerical approximation of~\eqref{eq:tdpb} on a cartesian grid using the Yee scheme, 
+as suggested in \cite{stable_yee_plasma_current}. Let $n$ denote the time step index, as usual $t_n = n \Delta t$. 
+It is standard (see \cite{Xu_2006,stable_yee_plasma_current }) to discretize the electrical field on the integer time step, 
+\mrev{whereas the field $H_z$ is on half time steps, $t_{n+1/2}$}. The time discretization of the system reads:
  \begin{align}
@@
  \end{align}
-In Yee scheme, the differents components of the vector fields are defined on staggered points.
-We summarize this discretization on Fig.~\ref{schemepos} where the positions of $Ex$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) on the discretized grid in space and time are shown.
-The fully discretized system then reads
+In Yee scheme, the differents components of the vector fields 
+are defined on staggered points. 
+We summarize this discretization on Fig.~\ref{schemepos} where the positions 
+of $Ex$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) 
+on the discretized grid in space and time are shown. The fully discretized system then reads
 
@@
 \input{grid}
-Some rapid computations left to the reader make it possible to show this discrete system is fully explicit.
+It is possible to rewrite this system in an explicit form (we omit here these simple but slightly tedious computations).
 %It is now possible to describe explicitly how to solve the proviso discrete system.

### 2015-01-27 report/intro.tex
'is' deleted in intro.tex line 3

@@
 which is observed in experiments (see \cite{reflectometers_2006, reflectometers_2010, Dumont_2005}) and 
-mathematically is described as the non-regularity of
+mathematically described as the non-regularity of
 the solutions of Maxwell equations in plasmas under strong background magnetic field \cite{Despres_2014}. 
@@
 \end{tikzpicture}
- \caption{Schematic representation of the equivalence of the limited absorption and limiting amplitude principles.}
- \label{fig:limits}
+ \caption{\label{fig:limits}Schematic representation of the equivalence of the limited absorption and limiting amplitude principles.}
+
 \end{figure}

### 2015-01-27 report/intro.tex
and is described mathematically

@@
 This article concentrates on studying a phenomenon of hybrid resonance \cite{Stix}, 
-which is observed in experiments (see \cite{reflectometers_2006, reflectometers_2010, Dumont_2005}) and 
-mathematically described as the non-regularity of
+which is observed in experiments (see \cite{reflectometers_2006, reflectometers_2010, Dumont_2005}) and is described
+mathematically as the non-regularity of
 the solutions of Maxwell equations in plasmas under strong background magnetic field \cite{Despres_2014}. 

### 2015-01-27 absorption.tex

--- 2015-01-20 report/absorption.tex
@@
+\documentclass[a4paper,10pt]{article}
+\usepackage[utf8]{inputenc}
+\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
+\usepackage{tikz}
+\usepackage{caption}
+\usepackage{pgfplots}
+\usepackage{ulem}
+\usepackage{pifont}% http://ctan.org/pkg/pifont
+\usepackage{hyperref}
+\begin{document}
 \subsection{Limiting Amplitude and Limiting Absorption Principle}
@@
 
-\subsubsection{No-Resonance Case}
-We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{2}$ satisfies 
+\subsubsection{No-resonance Case}
+We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{y}$ satisfies 
 the Airy equation (\ref{}).
@@
 choose the domain as $[-0.5, 10]$ and set the electron density $N_e(x)=1+x$. Importantly, $N_e(x)>0$ on the whole interval.
-The boundary conditions in (\ref{eq:bcs}) are chosen as $G=Ai'(0.5)$. 
-In all the experiments in this section the CFL number was chosen to be equal to 0.5.
+The boundary conditions in (\ref{eq:bcs}) are chosen as $G=-Ai'(0.5)$.
 
-First let us fix $\nu=1e-2$. 
-To demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
-inside the domain $(-L,\; H)$ and plot the dependence of the solution $E_{2}^{\nu}(x_c,t), \; \hat{E}_2^{\nu}(x_c)\mathrm{e}^{it}$ 
-on time $t$ for a range of $t\gg 1$ in Figure \ref{fig:nu1e2_harmon}.
+In Figure \ref{} we show the dependence of the error 
+\begin{align*}
+\mathcal{E}(t)=\|\Im\left(\hat{E}_y^{\nu}\exp(it)\right)-E_y^{\nu}(t)\|_{L_{2}(-L;H)}.
+\end{align*}
+on time, for $\nu=1e-1$, for $\Delta t=0.05$ and $\Delta t=0.025$: it can be seen that the error between the solutions is caused by the numerical discretization.
 
-\begin{figure}[htb]
-\includegraphics[width=0.9\textwidth]{figure_nu1e2-crop.pdf}
- \label{fig:nu1e2_harmon}
+\begin{figure}
+
 \end{figure}
 
-In Figure \ref{fig:nu1e2_harmon2} (left figure) we compare this solution to the computed $\hat{E}_2^{\nu}\mathrm{e}^{it}$, for
-fixed values of $t$. Both solutions appear to be in close agreement. 
-\begin{figure}[htb]
- \begin{tabular}{ll}
-\includegraphics[width=0.5\textwidth]{figure_nu1e2_2-crop.pdf}
-&
-\includegraphics[width=0.5\textwidth]{figure_error_nu1e4-crop.pdf}\\
-\end{tabular}
-\caption{In the left figure we show the solution to (\ref{}) for $\nu=10^{-2}$, for two fixed moment of times. In the right figure 
-the dependence of the error (\ref{eq:error}) on time for $\nu=10^{-4}$ is demonstrated. 
-We can see that the error is decreasing.}
- \label{fig:nu1e2_harmon2}
-\end{figure}
-The computed $L_2$ error
-\begin{align}
-\label{eq:error}
-\mathcal{E}(t)=\|\Im\left(\hat{E}_y^{\nu}\exp(it)\right)-E_y^{\nu}(t)\|_{L_{2}(-L;H)}.
-\end{align}
-for $\nu=1e-2$ did not exceed $1.1e-3$ for values of $t\in \left(28501,  30000\right)$.
-
-Figure show the solutions at fixed time steps for $\nu=1e-4$. As before, 
-to demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
-inside the domain $(-L,\; H)$ and plot 
-the dependence of the solution $E_{2}^{\nu}(x_c,t)$ on time $t$ for a range of $t\gg 1$. 
-The error (\ref{eq:error}) for $\nu=1e-4$ at the time interval $[228000.05,\; 240000.05]$ does not exceed 2.8e-4. 
-One of our observations was that for smaller $\nu$ one requires more time steps to achieve the limiting amplitude solution, 
-c.f. e.g. Figure \ref{fig:nu1e2_harmon2}. 
-We were not able to obtain the limiting amplitude solution for $t<3\cdot 10^{4}$, unlike in the case of $\nu=10^{-2}$. 
-For example, for $\nu=1e-6$ we were not able to reach the limiting amplitude solution even on the time interval $t\leq 1.92e6$, 
-see Figure \ref{fig:nu1e4_harmon}. 
-\begin{figure}
-\begin{tabular}{c}
- \includegraphics[width=\textwidth]{figure_nu1e4-crop.pdf}\\
- \includegraphics[width=\textwidth]{figure_nu1e6-crop.pdf}\\
-\end{tabular}
-\caption{In the upper figure we plot the dependence of the solution $E_{2}^{\nu}(x_c,t)$ on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$. 
-In the lower figure we show the solution for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
-$\nu=10^{-4}$ the limiting amplitude solution was reached for large $t$. For $\nu=10^{-6}$ we were not able 
-to obtain the limiting amplitude solution even for $t\approx 1.9e6$. }
-  \label{fig:nu1e4_harmon}
-\end{figure}
-
-\subsubsection{Resonance Case}
-\label{sec:resn}
-For the resonance case, we choose the parameters as given in Table \ref{tab:parameters_resonance}.
-\begin{table}[htb!]
-\begin{tabular}{c|c}
-Parameter & Value \\
-\hline
-$L$ & 5\\
-$H$ & 19\\
-$\omega_c$ &  $\sqrt{0.5}$\\
-$N_e(x)$ &  $\left\{
- \begin{array}{cc}
-  0.25, & x<-0.5,\\
-  \frac{1+x}{2}, & x\geq -0.5, x\leq 9\\
-  5, & x>9.
- \end{array}\right.$\\
- $G$ as in (\ref{eq:bcs}) & 0.11 \\
-\end{tabular}
-\label{tab:parameters_resonance}
-\caption{Parameters for numerical simulations in Section \ref{sec:resn}}
-\end{table}
-Since $\alpha(x)=(1-2N_e(x))$, $\alpha(0)=0$. Clearly, $\delta(0)\neq 0$ (resonance case).
-
-The results for $\nu=10^{-2}$ (chosen as a parameter both in frequency and time domain) 
-are shown in Figure \ref{fig:resonance_nu1e2} and for $\nu=10^{-3}$ in Figure \ref{resonance_nu1e3}. 
-\begin{figure}
-
- \caption{In the }
- \label{fig:resonance_nu1e2}
-\end{figure}
-
-For $\nu=10^{-6}$, like in the previous case, we were not able to obtain the limiting amplitude solution in the time domain.
+\end{document}

### 2015-01-27 code_validity.tex
removed a bug

@@
 \usepackage{pgfplots}
-\usepackage{slashbox}
+%\usepackage{slashbox}
 \newtheorem{theor}{Theorem}
@@
 \end{align*}
-defines an isomorphism from $L_{2}(\Omega)$ to $L_{2}(\Omega)$, it can be shown that 
-$ \frac{i\delta}{(\alpha+i\nu)}\left((\alpha+i\nu)E_{1}+i\delta E_{2}\right)$ also belongs to $L_{2}(\Omega)$ and equals zero.
+defines an isomorphism from $L_{2}(\Omega)$ to $L_{2}(\Omega)$. Then, for bounded continous $\alpha, \delta$, the 
+$\frac{i\delta}{(\alpha+i\nu)}\left((\alpha+i\nu)E_{1}+i\delta E_{2}\right)$ also belongs to $L_{2}(\Omega)$ and equals zero.
 

### 2015-01-27 report/attic/numerics.tex

@@
 \end{align*}
-Inserting an explisit expression for the dielectric permittivity tensor 
+Inserting an explicit expression for the dielectric permittivity tensor 
 \be \label{eq:epsilonmu}
@@
 \begin{align*}
-E_{1}=\sum\limits_{k=1}^{N_{1}}e_{1k}\psi_{k},\; E_{2}=\sum\limits_{k=1}^{N_{2}}e_{2k}\phi_{k}.
+E_{1}=\sum\limits_{k=1}^{N_{1}}e_{1k}\psi_{k},\qquad E_{2}=\sum\limits_{k=1}^{N_{2}}e_{2k}\phi_{k}.
 \end{align*}
@@
 \begin{align*}
-i\theta\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}\bar{\psi}_{m}dx+\theta^2\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx\\
+i\theta\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}\bar{\psi}_{m}dx+\theta^2\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx
 -\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{k}\bar{\psi}_{m}dx-i\sum\limits_{1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\delta(x)\phi_{k}(x)\bar{\psi}_{m}dx=0.
@@
 \begin{align*}
-\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx-i\theta\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}(x)\bar{\phi}'_{\ell}(x)dx\\
+\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx-i\theta\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}(x)\bar{\phi}'_{\ell}(x)dx
 +i
-\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\delta(x)\psi_{k}\bar{\phi}_{m}dx-\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\phi_{k}\bar{\phi}_{m}dx\\
+\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\delta(x)\psi_{k}\bar{\phi}_{m}dx-\\
+\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\phi_{k}\bar{\phi}_{m}dx
 -
@@
 \begin{align*}
-\left(K^{\psi,\phi'}\right)_{mk}=\int\limits_{-L}^{H}\bar{\psi}_{m}\phi'_{k}dx,\qquad \left(M^{\psi}\right)_{mk}=\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx,\\
-\left(M^{\alpha,\psi}\right)_{mk}=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{m}\bar{\psi}_{k}dx, \qquad \left(M^{\delta,\psi,\phi}\right)_{mk}=\int\limits_{-L}^{H}\delta(x)\bar{\psi}_{m}\phi_{k}dx,\\
-K_{\ell k}=\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx,\qquad \left(M^{\alpha,\phi}\right)_{\ell k}=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\bar{\phi}_{\ell}\phi_{k}dx,\\
-I_{km}^{\Gamma}=\bar{\phi}_{m}(-L)\phi_{k}(-L),\\
-\boldsymbol{e}_{1}=\left(e_{11},\ldots,e_{1 N_{1}}\right)^{T},\; \boldsymbol{e}_{2}=\left(e_{21},\ldots,e_{2 N_{1}}\right)^{T},\\
+\left(K^{\psi,\phi'}\right)_{mk}&=\int\limits_{-L}^{H}\bar{\psi}_{m}\phi'_{k}dx,\qquad \left(M^{\psi}\right)_{mk}&=\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx,\\
+\left(M^{\alpha,\psi}\right)_{mk}&=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{m}\bar{\psi}_{k}dx, \qquad \left(M^{\delta,\psi,\phi}\right)_{mk}&=\int\limits_{-L}^{H}\delta(x)\bar{\psi}_{m}\phi_{k}dx,\\
+K_{\ell k}&=\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx,\qquad \left(M^{\alpha,\phi}\right)_{\ell k}&=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\bar{\phi}_{\ell}\phi_{k}dx,\\
+I_{km}^{\Gamma}&=\bar{\phi}_{m}(-L)\phi_{k}(-L),\\
+\boldsymbol{e}_{1}&=\left(e_{11},\ldots,e_{1 N_{1}}\right)^{T},\; \boldsymbol{e}_{2}&=\left(e_{21},\ldots,e_{2 N_{1}}\right)^{T},\\
 \boldsymbol{0}_{n} \text{ is an $n$-dimensional zero column vector}.
@@
 \subsubsection{Validity of Implementation}
-\subsubsection{Solution of $X$-Mode Prolbem}
+
+\subsubsection{Solution of the $X$-Mode Problem and Convergence}
 
@@
 \label{eq:bsc}
- \|v-I^{h}v\|_{L_{2}(\Omega)}\leq Ch^2|v''|_{L_{2}(\Omega)},\; C>0,\\
- %\|v-I^{h}v\|_{H_{1}(\Omega)}\leq Ch|v''|_{L_{2}(\Omega)},\; C>0, 
+ \|v-I^{h}v\|_{L_{2}(\Omega)}\leq Ch^2|v''|_{L_{2}(\Omega)},\; C>0, %\\ \|v-I^{h}v\|_{H_{1}(\Omega)}\leq Ch|v''|_{L_{2}(\Omega)},\; C>0, 
 \end{align}
@@
 
-\subsection{Discretization of the Time Domain Problem}
-\section{Numerical Experiments}
-\subsection{Frequency Domain}
 \subsection{Time Domain}
+In this section we study the equivalence of the limiting amplitude and limiting absorption principles. 
+\subsubsection{Regular Solution}
+First we consider the problem with $\alpha,\beta$ chosen as in (\ref{}) and its time-dependent counterpart. We conduct several numerical experiments, with values of the absorption chosen as $\nu=...$,
+
+\subsubsection{Hybrid Resonance Solution}
 \end{document}

### 2015-01-27 report/proc.tex
slight change
revised LM
adding some precision/reformulation of some sentences on timedomain.tex
made a modification in intro.tex
alphabetical ordering of refs
corrected one unclear part in FD.tex
fixed a reference in proc.tex, changed minor things in timedomain.tex
synch versions, remove draft from options

--- 2015-01-25 report/proc.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This is a template file for Proccedings 
-%
-% Copy it to a new file with a new name and use it as the basis
-% for your article
-%
-%%%%%%%%%%%%%%%%%%%%%%%%   EDP Sciences  %%%%%%%%%%%%%%%%%%%%%%%%%%
-%
 \documentclass[proc]{edpsmath}
-%
-%\usepackage{amsfonts,graphicx,amssymb}%amsfonts pour les \mathbb
-%\usepackage{amsmath,amsthm,amssymb}
-%%%%%%%%%%%%%--PREAMBLE--%%%%%%%%%%%%%%%%%%
-%%-----------------------------
-%%         ...........
-%%         your macros
-\usepackage[frenchb,english]{babel}
+
 \usepackage{macros}
-\usepackage{tikz}
-\usepackage{xcolor}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
-\usepackage{tikz}
-\usepackage{caption}
-\usepackage{pgfplots}
-\usepackage{ulem}
-\usepackage{pifont}% http://ctan.org/pkg/pifont
-\usepackage{hyperref}
-\usepackage{diagbox}
-\usepackage{color}
-\usepackage{placeins}
-\newenvironment{remark}[1][Remark]{\begin{trivlist}
-\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\definecolor{blue}{rgb}{0.30,0.8,1}
-\definecolor{red}{rgb}{1,0.3,0.3}
-\usetikzlibrary{positioning,shapes,shadows,arrows}
 
-%%         ...........
-%%-------------------------%%----
-%%%%%%%%%%%%%%%--BODY--%%%%%%%%%%%%%%%%%%
+% intro 
+% theoretical part 
+% numerical part : frequential domain
+% numerical part : time dependant scheme
+% numerical part : comparison
+% concl.
 
 \begin{document}
-\newcommand{\urev}[1]{{\color{red}#1}}
-\newcommand{\mrev}[1]{{\color{blue}#1}}
-
-%%-----------------------------
-%%      the top matter
-%%-----------------------------
-\title{Study of the
-	numerical solution of X-Modes equations around the hybrid resonnance} %\thanks{...}\thanks{...}% At most 5 thanks
-%
-\author{C\'eline Caldini-Queiros}\address{Max Planck Institute für PlasmaPhysik, Garching bei Muenchen}
-\author{Bruno Despr\'es}\address{Laboratoire Jacques-Louis Lions, University PARIS 6}
-\author{Lise-Marie Imbert-Gérard}\address{Courant Institute of Mathematical Sciences, New York University}
-\author{Maryna Kachanovska}\address{POEMS, INRIA, ENSTA ParisTech, Paris}
-
-%
-%\dedicated{\it Dedicated to Maurice Dupont} %if necessary
-%
-\begin{abstract} ... \end{abstract}
-%
-\begin{resume} ... \end{resume}
-%
-%
-\maketitle
-\textcolor{red}{should we add Olivier Lafitte and Remi Sart anywhere in the proceeding ?}\\
-%!!!!!!!!!!!todo !!!!!!!!!!!
-
-%\item !!!!to do : correct proof of coercivity (celine)
-%\item !!!!to do : write Yee scheme 			(celine)
-%
-%%with explicit in \nu coercivity and continuity constants
+\begin{itemize}
+\item !!!!to do : correct proof of coercivity (celine)
+\item !!!!to do : write Yee scheme 			(celine)
+\item !!!!to do : well posedness = lemma		(celine)
+%with explicit in \nu coercivity and continuity constants 
+\end{itemize}
 
@@
 \input{equations}
-
-\input{timedomain}
-\input{freqdomain}
 \input{numerics}
-\input{absorption}
-
 \begin{thebibliography}{99}
-\bibitem{stable_yee_plasma_current} F. da Silva M. Campos Pinto, B. Despres and S. Heuraux, Stable Coupling of the Yee Scheme with a Linear Current Model,
+\bibitem{stable_yee_plasma_current} F. da Silva, M. Campos Pinto, B. Despres, S. Heuraux, Stable Coupling of the Yee Scheme with a Linear Current Model,
 2014
-\bibitem{Despres_2014} Després, B., Imbert-Gérard, L. M. and Weder, R. (2014). Hybrid resonance of Maxwell's equations in slab geometry. Journal de Mathématiques Pures et Appliquées, 101(5), 623-659.
-\bibitem{LMIG_thesis} Imbert-Gérard, L.
-M.
-(2013).
-Analyse mathématique et numérique de problèmes d'ondes apparaissant dans les plasmas magnétiques (Doctoral dissertation, Université Pierre et Marie Curie-Paris VI).
-\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
-\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
-\bibitem{Morawetz} Morawetz, C. S. (1962). The limiting amplitude principle. Communications on Pure and Applied Mathematics, 15(3), 349-361.
-\bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
-Handbook of mathematical functions
 \end{thebibliography}

### 2015-01-27 report/absorption.tex
corrected multiple mistakes+extended the explanation slightly

@@
 \begin{figure}[htb]
-\includegraphics[width=0.9\textwidth]{airy/figure_nu1e2-crop.pdf}
+\includegraphics[width=0.85\textwidth]{airy/figure_nu1e2-crop.pdf}
 \caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time for $t\rightarrow +\infty$.}
@@
  \begin{tabular}{cc}
-\includegraphics[width=0.5\textwidth]{airy/figure_nu1e2_2-crop.pdf}
+\includegraphics[width=0.45\textwidth]{airy/figure_nu1e2_2-crop.pdf}
 &
-\includegraphics[width=0.5\textwidth]{airy/figure_error_nu1e4-crop.pdf}\\
+\includegraphics[width=0.45\textwidth]{airy/figure_error_nu1e4-crop.pdf}\\
 \end{tabular}
@@
 $H$ & 19\\
-$\omega_c$ &  $-\sqrt{0.5}$\\
+$\omega_c$ &  \mrev{$\sqrt{0.5}$}\\
 $N_e(x)$ &  $\left\{

### 2015-01-27 report/intro.2.tex

\section{Introduction}

 In the case of heating devices for fusion experiment, for example, one can find itself dealing with what is called hybrid resonnance. Hybrid resonnance may cause Maxwell's equation with strong magnetic fields to develop singular solutions \textcolor{red}{insert refs}. The energy deposit is resonant and may exceed by far the energy exchange which occurs in Landau damping \textcolor{red}{ref}. Contrary to the Landau Dumping, however, hybrid resonnance appears in a simpler model coupling fluid equations with the non electrostatic part of Maxwell equations.
 As it can be found in \cite{stable_yee_plasma_current}, we consider the non-stationary Maxwell system 
 \begin{align}
 -\varepsilon_0 \partial_t \E + \curl\, \Hbf = \J\\
 \mu_0 \partial_t \Hbf + \curl\,  \E = 0
 \end{align}
 coupled with a linear current in two dimensions $\J = eN_e \ubf_e$, taking into account the friction between electron and ions

 \be
 m_e \partial_t \ubf_e =e (\E +\ubf_e \nabla B_0) -m_e \nu \ubf_e. \label{eq:electronmove}
 \ee
 Here the unknows are the electromagnetc field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, $\J$ is the electronic current. We denote by $e<0$ the value of the charge of electrons and by $\m_e$ the electron mass0
  \begin{align}
\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\nonumber\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\nonumber\\
\mu_0\partial_t H+\partial_x E_y-\partial_y E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y\nonumber
\end{align}
posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. The boundary conditions 
\begin{align*}
 H|_{-L}=g(t).
\end{align*}

\textcolor{red}{!!!!!!maybe move this next part to later!!!!!!!!}
\subsection{Boundary condition}
Robin Boundary condition at the left boundary of the domain
\be
-curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath \lambda\E_{inc} \wedge \n,
\ee
where  $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$

$curl \E = 0$ at the right boundary
\begin{remark}
When modelling antennas in plasma physics, in such applications as ITER, a good choice of boundary condition could be the use of $\lambda = \sqrt{alpha(-L)}$
\end{remark}
\textcolor{red}{!!!!!!!!!!!!}

### 2015-01-27 report/numerics.tex

@@
         ylabel=$Error$,
-        width=0.6\textwidth,
+        width=0.4\textwidth,
         legend style={
-at={(0.2,1.5)},
-legend pos= south east,
-anchor=south east, 
-draw=none
+at={(1.7,0.5)},
+%legend pos=outer north east, 
+anchor=east,
+%legend pos=south east,
+%anchor=east, 
+draw=none,
+font=\small
 }

### 2015-01-27 report/intro.tex
macros + intro with macros

@@
 We consider the model of cold plasma of \cite{Stix} which is described by the 2D time-dependent Maxwell system  
-\begin{align}
+\bealn
 -\varepsilon_0 \partial_t \E + \curl\, \Hbf = \J\\
 \mu_0 \partial_t \Hbf + \curl\, \E = 0
-\end{align}
+\eealn
 coupled with a linear electronic current  $\J = eN_e \ubf_e$, 
-\be
+\ben
 m_e \partial_t \ubf_e =e (\E +\ubf_e \wedge B_0) -m_e \nu \ubf_e, \label{eq:electronmove}
-\ee
+\een
 where $\nu$ is  the friction  between particles.
@@
 The energy of this system for $\nu=0$ in a domain $\Omega\in\mathbb R^2$ can be expressed as \cite{stable_yee_plasma_current}
-\mrev{\begin{align*}
+\mrev{\ben
 {\mathcal E}(t)= \int_\Omega \left(
@@
 \right)\mathrm{d}\x.
-\end{align*}}
+\een}
 \mrev{An energy-preserving scheme for discretizing (\ref{eq:main_model}) was recently developed in \cite{Despres_2014}. 
 It can be shown that for non-zero collision frequency $\nu$ the loss of energy is proportional to $\nu$, however, as $\nu\rightarrow0+$, it 
-does not vanish. This paradox had been recently investigated in \cite{Despres_2014}}.
+does not vanish. This behaviour had been recently investigated in \cite{Despres_2014}}.
 
@@
 At the left boundary of the domain, which represents the wall, we choose Robin boundary conditions 
-\be
+\ben
 -curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
-\ee
+\een
 where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$. We truncate the domain 

### 2015-01-27 report/numerics.tex
numbering in numerics.tex

@@
 Additionally, the boundary conditions read as 
-\begin{align}
+\bealn
 \label{eq:bcs}
@@
 \partial_{1}E_{y}(H)=0,
-\end{align}
+\eealn
 where $Ai(x)$ is the Airy function. 
@@
 with the choice of the boundary conditions as above, we obtain that 
-\begin{align*}
+\bealn
 E_{y}=Ai(x),\qquad 
 E_{x}=-i\frac{\delta(x)}{\alpha(x)}Ai(x)
-\end{align*}
+\ealn
 is the solution to the problem with parameters (\ref{eq:parameters}) with the boundary condition (\ref{eq:bcs}).
@@
 In Figure \ref{fig:conv_rate} we demonstrate the convergence rates for this problem, with 
-\begin{align*}
+\ben
 \|E_{x}-E_{x}^{c}\|_{L_{2}(\Omega)}=\left(\int\limits_{\Omega}\left|E_{x}(x)-\sum\limits_{k=1}^{N}e_{xk}\phi_{k}\right|^2dx\right),
-\end{align*}
+\een
 where $\left(\phi_{i}\right)_{i=1}^{N}$ are $P_{1}$-finite elements and $E_{x}(x)$ is a known analytic solution.
@@
 For $E_x^{\nu},\;f(x)$ in (\ref{eq:exact}) being sufficiently smooth, 
-\begin{align*}
+\ben
  \frac{d^2}{dx^2}E_x^{\nu}=\frac{f''}{\alpha+i\nu}-2\frac{f'\alpha'}{(\alpha+i\nu)^2}+\frac{f\alpha''}{(\alpha+i\nu)^3},
-\end{align*}
+\een
 from which, together with (\ref{eq:cond}), it follows that there exists $c>0$ s.t. for all sufficiently small $\nu$ 
-\begin{align*}
+\ben
  \left|  \frac{d^2}{dx^2}E_x^{\nu}\right|_{L_2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
@@
  \leq C\nu^{-5},\; 
-\end{align*}
+\een
 where $C>0$ does not depend on $\nu$. This, together with the estimates (\ref{eq:cea}) and (\ref{eq:bsc}), results in 
-\begin{align*}
+\ben
  \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}\leq C\nu^{-\frac{7}{2}}h^2,
-\end{align*}
+\een
 from which it follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
@@
  We can show that 
-\begin{align*}
+\bealn
  \|E^{\nu}_{x}\|_{L_{2}(\Omega)}\leq \frac{C}{\sqrt{\nu}},\; C>0, 
-\end{align*}
+\eealn
 and thus the relative error control
-\begin{align*}
+\bealn
  \frac{\|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}}{\|E^{\nu}_{x}\|_{L_{2}(\Omega)}}\leq \epsilon
-\end{align*}
+\eealn
 can be ensured by choosing $h$ as $\beta_{\epsilon}\nu^{\frac{3}{4}}$.

### 2015-01-27 report/absorption.tex
numbering in absortption.tex

@@
 and zero initial conditions, and in the frequency domain
-\begin{align*}
+\bealn
  \left.\partial_x \hat{E}_y\right|_{x=-L}&=G,\\
  \left.\partial_x \hat{E}_y\right|_{x=H}&=0.
-\end{align*}
+\eealn
 We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain (the solution computed numerically at the time step $n$ is denoted by $\mathbf{E}^{\nu}_{n}$), and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain.
 In the numerical experiments we check whether the following two quantities
-\begin{align*}
+\ben
 \lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t), \text{ and } \Im\left(\hat{\mathbf{E}}^{\nu}\exp(it)\right)
-\end{align*}
+\een
 are close as $\nu\rightarrow 0$ (provided that the first of these quantities exists). 

### 2015-01-27 report/numerics.tex
Fig. in numerics.tex

@@
 
-In Figure \ref{fig:conv_rate} we demonstrate the convergence rates for this problem, with 
+In Fig.~\ref{fig:conv_rate} we demonstrate the convergence rates for this problem, with 
 \ben
@@
  We fix $\nu$ and compute the error of the solution compared to the solution computed on the finest mesh  (with $h=2e-6$). 
- The results are depicted in Figures \ref{fig:dependence} and \ref{fig:l2_err_e2}.
+ The results are depicted in Fig. \ref{fig:dependence} and \ref{fig:l2_err_e2}.
 \begin{figure}
@@
 \end{align}
-The computed dependence of $h_{\epsilon}$ on $\nu$ is shown in Figure \ref{fig:dependence}.
+The computed dependence of $h_{\epsilon}$ on $\nu$ is shown in Fig.~\ref{fig:dependence}.
 \begin{figure}
@@
 Remarkably, for $\nu=0$ the computed matrices are not singular. \urev{We do not know the exact reason for such a behavior.}
-As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Figure \ref{fig:small_nu}. 
+As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Fig.~\ref{fig:small_nu}. 
 \begin{figure}

### 2015-01-27 report/absorption.tex
Fig. in absorption.tex

@@
 inside the domain and plot the dependence of the solution $E_{y}^{\nu}(x_c,t), \; \Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right)$ 
-on time $t$ for a range of $t\gg 1$ in Figure \ref{fig:nu1e2_harmon}.
+on time $t$ for a range of $t\gg 1$ in Fig.~\ref{fig:nu1e2_harmon}.
 
@@
 
-In Figure \ref{fig:nu1e2_harmon2} (left figure) we compare this solution to the computed $\hat{E}_y^{\nu}\mathrm{e}^{it}$, for
+In Fig.~\ref{fig:nu1e2_harmon2} (left figure) we compare this solution to the computed $\hat{E}_y^{\nu}\mathrm{e}^{it}$, for
 fixed values of $t$. Both solutions appear to be in close agreement. 
@@
 
-Figure \ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=1e-4$. As previously, 
+Fig.~\ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=1e-4$. As previously, 
 to demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
@@
 One of our observations was that for smaller $\nu$ one requires more time steps to achieve the limiting amplitude solution, 
-c.f. e.g. Figure \ref{fig:nu1e2_harmon2}. 
+c.f. e.g. Fig.~\ref{fig:nu1e2_harmon2}. 
 For $\nu=10^{-4}$ we were not able to obtain the limiting amplitude solution for $t<3\cdot 10^{4}$, unlike in the case of $\nu=10^{-2}$, 
-see also Figure \ref{fig:nu1e2_harmon2}(right). 
+see also Fig.~\ref{fig:nu1e2_harmon2}(right). 
 For example, for $\nu=10^{-6}$ we were not able to reach the limiting amplitude solution even on the time interval $t\leq 1.92e6$, 
-see Figure \ref{fig:nu1e4_harmon} (right). 
+see Fig.~\ref{fig:nu1e4_harmon} (right). 
 \begin{figure}
@@
 
-We compare the results for $\nu=10^{-2},\; 10^{-3}$ in Figures \ref{fig:resonance_nus_ex_x}, 
+We compare the results for $\nu=10^{-2},\; 10^{-3}$ in Fig. \ref{fig:resonance_nus_ex_x}, 
 \ref{fig:resonance_nus_ey_x}, \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}. 

### 2015-01-28 report/numerics.tex
fixed mistakes
fixed some mistakes
some errors corrected

@@
 \label{sec:freq_dep}
-\subsubsection{Validity of Implementation}
+\subsubsection{Validity of the Implementation}
 To check the validity of the code, we perform a numerical experiment with (formally chosen) parameters:
@@
 \bealn
-\label{eq:bcs}
+\label{eq:bcs_airy}
 \partial_{1}E_{y}(-L)+2iE_{y}(-L)=2iAi(-L)+Ai'(-L),\\
@@
 For more detail on Airy functions and the Airy equation see \cite[Chapter 10.4]{abramowitz_stegun}. 
-
-It can be shown that $E_{y}$ thus satisfies the Airy equation, and hence, 
+It can be shown that $E_{y}$ that solves (\ref{eq:main_frequency_domain}) in 1D, with the Fourier variable $\theta=0$ (see (\ref{vf1dcase}), and $\nu=0$, 
+satisfies the Airy equation, and hence, 
 with the choice of the boundary conditions as above, we obtain that 
@@
 E_{x}=-i\frac{\delta(x)}{\alpha(x)}Ai(x)
-\ealn
-is the solution to the problem with parameters (\ref{eq:parameters}) with the boundary condition (\ref{eq:bcs}).
+\eealn
+is the solution to the problem with parameters (\ref{eq:parameters}) with the boundary condition (\ref{eq:bcs_airy}). 
+The well-posedness of the respective variational formulation is due to Remark \ref{remark:other}.
 
@@
 \ben
-\|E_{x}-E_{x}^{c}\|_{L_{2}(\Omega)}=\left(\int\limits_{\Omega}\left|E_{x}(x)-\sum\limits_{k=1}^{N}e_{xk}\phi_{k}\right|^2dx\right),
+\|E_{x}-E_{x}^{c}\|_{L_{2}(\Omega)}=\left(\int\limits_{\Omega}\left|E_{x}(x)-\sum\limits_{k=1}^{N}e_{xk}\phi_{k}\right|^2dx\right)^{\frac{1}{2}},
 \een
@@
 of Lemma \ref{lemma:well_posedness}  are satisfied. 
-For simplicity, let us consider 
+For simplicity, let 
 \begin{align}
@@
 \label{eq:exact}
- E_x^{\nu}=E_{y}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f(x)}{\alpha(x)+i\nu},
+ E_x^{\nu}=-iE_{y}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f(x)}{\alpha(x)+i\nu},
 \end{align}
@@
 \label{eq:bsc}
- \|v-I^{h}v\|_{L_{2}(\Omega)}\leq Ch^2|v''|_{L_{2}(\Omega)},\; C>0,
+ \|v-I^{h}v\|_{L_{2}(\Omega)}\leq Ch^2\left|v''\right|_{L_{2}(\Omega)},\; C>0,
  %\\ \|v-I^{h}v\|_{H_{1}(\Omega)}\leq Ch|v''|_{L_{2}(\Omega)},\; C>0, 
@@
 \ben
- \left|  \frac{d^2}{dx^2}E_x^{\nu}\right|_{L_2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
- %\\
- %&=c\left.
- %\left(\frac{x}{4(x^2+\nu^2)^2}\nu^{-2}+\frac{3x}{8(x^2+\nu^2)}\nu^{-4}+\frac{3}{8}\nu^{-5}\operatorname{atan}\frac{x}{\nu}\right)\right|_{-L}^{H}
+ \left|\frac{d^2}{dx^2}E_x^{\nu}\right|_{L_2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
+  &=c\left.
+ \left(\frac{x}{4(x^2+\nu^2)^2}\nu^{-2}+\frac{3x}{8(x^2+\nu^2)}\nu^{-4}+\frac{3}{8}\nu^{-5}\operatorname{atan}\frac{x}{\nu}\right)\right|_{-L}^{H}
  \leq C\nu^{-5},\; 
@@
 \end{align}
-where $\alpha_{\epsilon}>0$ depends on $\epsilon$ but does not depend on $\nu$.
-
-Let us check whether this holds true. 
+where $\alpha_{\epsilon}>0$ depends on $\epsilon$ but does not depend on $\nu$. Let us check optimality of this estimate.  
 To do so, we conduct the  numerical experiment with parameters for the problem as given in Table \ref{tab:parameters}.
@@
 \end{table}
-
 We fix $\nu$ and compute the error of the solution compared to the solution computed on the finest mesh  (with $h=2e-6$). 
@@
 
-Let us denote by $E_{x}^{h}$ the solution $E_{x}(x)$ computed on the mesh with a width $h$, and by $E_{x}^{c}$ the solution computed on the finest mesh. We introduce 
+Denoting by $E_{x}^{h}$ the solution $E_{x}(x)$ computed on the mesh with a width $h$, and by $E_{x}^{c}$ the solution computed on the finest mesh, let 
 \begin{align}
@@
 \end{figure}
-
 We can see that the estimate (\ref{eq:estimate_h}) is pessimistic compared to the one suggested by (\ref{eq:def_epsilon}), 

### 2015-01-28 report/absorption.tex
1) bug fix 2) new pics 3) conclusions

@@
 \bealn
- \left.\partial_x \hat{E}_y\right|_{x=-L}&=G,\\
- \left.\partial_x \hat{E}_y\right|_{x=H}&=0.
+ \left.\partial_x \hat{E}_y\right|_{x=-L}=G,\; \left.\partial_x \hat{E}_y\right|_{x=H}=0.
 \eealn
@@
 \subsubsection{No-Resonance Case}
-We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{y}$ satisfies 
-the Airy equation.
+We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{y}^{\nu},\; \nu=0,$ satisfies 
+the Airy equation, c.f. also Remark \ref{remark:other}.
 
@@
 The boundary conditions in (\ref{eq:bcs}) are chosen as $G=Ai'(0.5)$.
-In all the experiments in this section the CFL number=0.5.
 
@@
 \includegraphics[width=0.85\textwidth]{airy/figure_nu1e2-crop.pdf}
-\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time for $t\rightarrow +\infty$.}
+\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time for large times.}
  \label{fig:nu1e2_harmon}
@@
 
-In Fig.~\ref{fig:nu1e2_harmon2} (left figure) we compare this solution to the computed $\hat{E}_y^{\nu}\mathrm{e}^{it}$, for
+In Fig.~\ref{fig:nu1e2_harmon2} (left figure) we compare this solution to the computed $\Im\left(\hat{E}_y^{\nu}\mathrm{e}^{it}\right)$, for
 fixed values of $t$. Both solutions appear to be in close agreement. 
@@
 \label{eq:error}
-\mathcal{E}_{x,y}(t)=\|\Im\left(\hat{E}_{x,y}^{\nu}\exp(it)\right)-E_{x,y}^{\nu}(t)\|_{L_{y}(-L;H)}.
+\mathcal{E}_{x,y}(t)=\|\Im\left(\hat{E}_{x,y}^{\nu}\exp(it)\right)-E_{x,y}^{\nu}(t)\|_{L_{2}(-L;H)}.
 \end{align}
@@
 The error (\ref{eq:error}) for $\nu=1e-4$ at the time interval $[228000.05,\; 240000.05]$ does not exceed 2.8e-4. 
-One of our observations was that for smaller $\nu$ one requires more time steps to achieve the limiting amplitude solution, 
-c.f. e.g. Fig.~\ref{fig:nu1e2_harmon2}. 
+One of our observations was that for smaller $\nu$ one requires more time steps to achieve the limiting amplitude solution. 
 For $\nu=10^{-4}$ we were not able to obtain the limiting amplitude solution for $t<3\cdot 10^{4}$, unlike in the case of $\nu=10^{-2}$, 
@@
 \begin{tabular}{cc}
- \includegraphics[width=0.5\textwidth]{airy/figure_nu1e4-crop.pdf}&
- \includegraphics[width=0.5\textwidth]{airy/figure_nu1e6-crop.pdf}\\
+ \includegraphics[width=0.45\textwidth]{airy/figure_nu1e4-crop.pdf}&
+ \includegraphics[width=0.45\textwidth]{airy/figure_nu1e6-crop.pdf}\\
 \end{tabular}
-\caption{In the upper figure we plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$. 
-In the lower figure we show the solution for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
+\caption{In the left figure we plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$. 
+In the right figure we show the solution for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
 $\nu=10^{-4}$ the limiting amplitude solution was reached for large $t$. For $\nu=10^{-6}$ we were not able 
@@
 
-We compare the results for $\nu=10^{-2},\; 10^{-3}$ in Fig. \ref{fig:resonance_nus_ex_x}, 
-\ref{fig:resonance_nus_ey_x}, \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}. 
+We compare the results for $\nu=10^{-2},\; 10^{-3},\; 10^{-4}$ in Fig. \ref{fig:resonance_nus_ex_x}, 
+\ref{fig:resonance_nus_ey_x}, \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}, \ref{fig:resonance_nus_eyx_t}. 
 %In the time domain, we chose the discretization size $\Delta x=0.025$. 
@@
 
-\begin{figure}
-\begin{tabular}{cc}
-\includegraphics[width=0.5\textwidth]{res/ex_fixed_x-crop.pdf}&
-\includegraphics[width=0.5\textwidth]{res/ex_fixed_x_1e3-crop.pdf}
-\end{tabular}
-\caption{The figures demonstrate the dependence of the solutions 
-$E_x^{\nu}(0,t)$ on time $t$ for different values of $\nu$. }
-\label{fig:resonance_nus_ex_x}
-\end{figure}
 \begin{figure}
@@
 \end{figure}
-
+\begin{figure}
+ \includegraphics[width=0.8\textwidth]{res/ex_fixed_x_nu1e4-crop.pdf}
+ \caption{The plot shows the dependence of the solution $E_x^{\nu}(x_c,t),\;\nu=10^{-4}$ on time $t$ for fixed 
+ $x_c=0.0125$ and for $x_c=-2.5$. We can see that the solutions computed in the time domain are in close agreement 
+ with the solution computed in the frequency domain at the point $x_c=-2.5$, however, differ at the point $0.0125$ which is 
+ close to the $x=0$ where the resonance occurs.}
+ \label{fig:resonance_nus_ex_x}
+\end{figure}
 \begin{figure}
@@
 \caption{The figures demonstrate the dependence of the solutions 
-$E_y^{\nu}(x,t)$ on $x$ for fixed values of $t$. }
+$E_x^{\nu}(x,t)$ on $x$ for fixed values of $t$. }
 \label{fig:resonance_nus_ex_t}
@@
 \begin{figure}
-\begin{tabular}{cc}
-\includegraphics[width=0.5\textwidth]{res/ey_fixed_t-crop.pdf}&
-\includegraphics[width=0.5\textwidth]{res/ey_fixed_t_1e3-crop.pdf}
- \end{tabular}
+\includegraphics[width=0.45\textwidth]{res/ey_fixed_t_1e3-crop.pdf}
+\includegraphics[width=0.55\textwidth]{res/ey_fixed_x_nu1e4-crop.pdf}
+\caption{The left figure demonstrates the dependence of the solution  
+$E_y^{\nu}(x,y)$ on $x$ for fixed values of $t$. For a chosen value of $\nu$ the solutions computed in the time domain are in close agreement 
+to the solutions computed in the frequency domain (this seem to be only partially 
+true for the computed values $E_x^{\nu}(x,y)$ in this case (which also may be caused by the discretization). 
+The right figure shows the dependence of the solution $E_y^{\nu}(x,t)$ for $\nu=10^{-4}$ on time for fixed $x=x_c$. 
+We can see that the while the limiting amplitude principle holds true, the difference between the solutions computed in 
+the time and frequency domain is noticeable on this scale. 
+}
+\label{fig:resonance_nus_ey_t}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.95\textwidth]{res/ex_fixed_t_1e4_2-crop.pdf}
 \caption{The figures demonstrate the dependence of the solutions 
-$E_y^{\nu}(x,t)$ on $x$ for fixed values of $t$. }
-\label{fig:resonance_nus_ey_t}
+$E_x^{\nu}(x,t)$ and $E_y^{\nu}(x,y)$ on $x$ for fixed values of $t$. While the solution in the time-domain 
+in the resonance point $x=0$ has a smaller absolute value than that computed in the frequency domain (in the plot both solutions are truncated to 
+axis limits), in other points the values are rather close. }
+\label{fig:resonance_nus_eyx_t}
 \end{figure}

### 2015-01-28 report/conclusions.tex
1) bug fix 2) new pics 3) conclusions

\section{Conclusions}
In this work we considered the frequency- and the time-domain formulations of the $X$-mode Maxwell equations. 
In particular, we proved the well-posedness of the respective regularized (with the help of 
the absorption parameter $\nu$) variational formulation, as 
well as studied the convergence of the finite element method for the problem with the resonance. 
The piecewise-constant FEM approximates the resonant solution rather well, at least for moderate values of $\nu$, 
however, the discretization size should be chosen roughly proportional to $\nu^{\frac{3}{2}}$, in order to obtain an accurate discretization.
Indeed, it would be interesting to look at the convergence of the adaptive finite elements for this kind of problems. 
Another unanswered question is the well-posedness of the discrete problem when the continuous problem is ill-posed. We have 
demonstrated that while the condition number of the FEM matrix grows, the matrix remains always invertible, even for $\nu=0$.

The other part of the experiments concerned the equivalence of the limiting absorption and limiting amplitude solutions. We have shown 
that for small $\nu$ and large times the solution computed in the time domain is close to the solution predicted by the limiting amplitude principle; as 
$\nu\rightarrow 0$, the solution oscillates harmonically as $t\rightarrow +\infty$, however, we were not able to compute the limiting amplitude solution for very 
small values of $\nu$.

### 2015-01-28 report/numerics.tex
1) bug fix 2) new pics 3) conclusions

@@
 Additionally, the boundary conditions read as 
-\bealn
+\begin{align}
 \label{eq:bcs_airy}
@@
 \partial_{1}E_{y}(H)=0,
-\eealn
+\end{align}
 where $Ai(x)$ is the Airy function. 
@@
 from which, together with (\ref{eq:cond}), it follows that there exists $c>0$ s.t. for all sufficiently small $\nu$ 
-\ben
+\begin{align*}
  \left|\frac{d^2}{dx^2}E_x^{\nu}\right|_{L_2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
@@
  \leq C\nu^{-5},\; 
-\een
+\end{align*}
 where $C>0$ does not depend on $\nu$. This, together with the estimates (\ref{eq:cea}) and (\ref{eq:bsc}), results in 
@@
     \begin{loglogaxis}[
-    	width=0.5\textwidth,
+    	width=0.45\textwidth,
     	height=0.5\textwidth,
@@
         ylabel=$Error$,
+        ymin=1e-10,
         legend style={
@@
     \begin{loglogaxis}[
-    	width=0.5\textwidth,
-    	height=0.5\textwidth,
+    	width=0.4\textwidth,
+    	height=0.4\textwidth,
         xlabel=$\nu$,
@@
 at={(0.2,1.5)},
-legend pos= south east,
-anchor=south east, 
+legend pos=north west,
+%anchor=south east, 
 draw=none
@@
 &
-\includegraphics[width=0.5\textwidth]{figure1-crop.pdf}
+\includegraphics[width=0.4\textwidth]{figure1-crop.pdf}
 \end{tabular}
 \caption{In the left figure the depenence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated. 
-In the right figure we show the solutions for the problem for different values of $\nu$. }
+In the right figure we show the computed solutions for the problem with parameters in Table \ref{tab:parameters} for different values of $\nu$. }
 \label{fig:dependence}
@@
 \paragraph{Condition Number}
-
-We consider the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
-on $\nu$, for several values of $h$ (see Table \ref{tab:cond_number}).
+In Table \ref{tab:cond_number} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
+on $\nu$, for several values of $h$.
 \begin{table}[ht!]
@@
 \end{table}
-Remarkably, for $\nu=0$ the computed matrices are not singular. \urev{We do not know the exact reason for such a behavior.}
+Remarkably, for $\nu=0$ the computed matrices are not singular. \urev{We do not know the exact reason for this.}
 As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Fig.~\ref{fig:small_nu}. 

### 2015-01-28 report/proc.tex
some errors corrected
1) bug fix 2) new pics 3) conclusions

--- 2015-01-26 report/proc.tex
@@
 \usepackage{tikz}
+\usetikzlibrary{matrix,arrows,decorations.pathmorphing}
 \usepackage{caption}
@@
 \newtheorem{theorem}{Theorem}[section]
+\newtheorem{df}{Definition}[section]
 \newtheorem{lemma}[theorem]{Lemma}
@@
 \definecolor{red}{rgb}{1,0.3,0.3}
-\usetikzlibrary{positioning,shapes,shadows,arrows}
+%\usetikzlibrary{positioning,shapes,shadows,arrows}
 
@@
 \title{Study of the
-	numerical solution of X-Modes equations around the hybrid resonnance} %\thanks{...}\thanks{...}% At most 5 thanks
+	numerical solution of X-Modes equations around the hybrid resonance} %\thanks{...}\thanks{...}% At most 5 thanks
 %
@@
 \textcolor{red}{should we add Olivier Lafitte and Remi Sart anywhere in the proceeding ?}\\
-%!!!!!!!!!!!todo !!!!!!!!!!!
-
-%\item !!!!to do : correct proof of coercivity (celine)
-%\item !!!!to do : write Yee scheme 			(celine)
-%
-%%with explicit in \nu coercivity and continuity constants
 
 \input{intro}
-\input{equations}
+\input{FD}%\input{equations}
 
 \input{timedomain}
-\input{freqdomain}
+%\input{freqdomain}
 \input{numerics}
 \input{absorption}
+\input{conclusions}
 
 \begin{thebibliography}{99}
+\bibitem{abramowitz_stegun} Abramowitz M.
+and Stegun I.
+A., eds.
+(1972).
+Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables.
+New York: Dover Publications.	Handbook of mathematical functions
+\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
 \bibitem{stable_yee_plasma_current} Da Silva, F., Campos-Pinto, M., Després, B., and Heuraux, S. (2014). Stable coupling of the Yee scheme with a linear current model.
-\bibitem{reflectometers_2006} Da Silva, F., Heuraux, S and  Manso, M.
-(2006).
-Developments on reflectometry simulations for fusion plasmas: application to ITER position reflectometers.
-Journal of plasma physics, 72(06), 1205-1208.
 \bibitem{reflectometers_2010}Da Silva, F., Heuraux, S., Gusakov, E.
@@
 Plasma Science, IEEE Transactions on, 38(9), 2144-2149.
+\bibitem{reflectometers_2006} Da Silva, F., Heuraux, S and  Manso, M.
+(2006).
+Developments on reflectometry simulations for fusion plasmas: application to ITER position reflectometers.
+Journal of plasma physics, 72(06), 1205-1208.
 \bibitem{Despres_2014} Després, B., Imbert-Gérard, L. M. and Weder, R. (2014). Hybrid resonance of Maxwell's equations in slab geometry. Journal de Mathématiques Pures et Appliquées, 101(5), 623-659.
@@
 Analyse mathématique et numérique de problèmes d'ondes apparaissant dans les plasmas magnétiques (Doctoral dissertation, Université Pierre et Marie Curie-Paris VI).
-\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
-\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
 \bibitem{Morawetz} Morawetz, C. S. (1962). The limiting amplitude principle. Communications on Pure and Applied Mathematics, 15(3), 349-361.
 \bibitem{Mouhot_2011} Mouhot, C., and Villani, C. (2011). On landau damping. Acta mathematica, 207(1), 29-201.
-\bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
-Handbook of mathematical functions
+\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
+ \bibitem{Xu_2006}Xu, L., ans Yuan, N. (2006). FDTD formulations for scattering from 3-D anisotropic magnetized plasma objects. Antennas and Wireless Propagation Letters, IEEE, 5(1), 335-338.
 \end{thebibliography}

### 2015-01-29 report/numerics.tex
detail : changed align* command once
changed the pic to a cooler one, removed incorrect data (due to a bug in the code)

@@
 from which, together with (\ref{eq:cond}), it follows that there exists $c>0$ s.t. for all sufficiently small $\nu$ 
-\begin{align*}
+\bealn
  \left|\frac{d^2}{dx^2}E_x^{\nu}\right|_{L_2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
@@
  \leq C\nu^{-5},\; 
-\end{align*}
+\eealn
 where $C>0$ does not depend on $\nu$. This, together with the estimates (\ref{eq:cea}) and (\ref{eq:bsc}), results in 
@@
 \end{table}
-We fix $\nu$ and compute the error of the solution compared to the solution computed on the finest mesh  (with $h=2e-6$). 
- The results are depicted in Fig. \ref{fig:dependence} and \ref{fig:l2_err_e2}.
-\begin{figure}
-\begin{tabular}{cc}
-\begin{tikzpicture}
-    \begin{loglogaxis}[
-    	width=0.45\textwidth,
-    	height=0.5\textwidth,
-        xlabel=$h$,
-        ylabel=$Error$,
-        ymin=1e-10,
-        legend style={
-at={(0.2,1.5)},
-legend pos= south east,
-anchor=south east, 
-draw=none, 
-font=\tiny
-}
-]
-\addplot[mark=*,blue] table {pics/result_l2e1.1.dat}; 
-\addlegendentry{$\nu=1$};
-\addplot[mark=*,green] table {pics/result_l2e1.0.25.dat}; 
-\addlegendentry{$\nu=2^{-2}$};
-\addplot[mark=*,red] table {pics/result_l2e1.0.0625.dat}; 
-\addlegendentry{$\nu=2^{-4}$};
-\addplot[mark=square,blue] table {pics/result_l2e1.0.015625.dat}; 
-\addlegendentry{$\nu=2^{-6}$};
-\addplot[mark=square,green] table {pics/result_l2e1.0.0039062.dat}; 
-\addlegendentry{$\nu=2^{-8}$};
-\addplot[mark=triangle,red] table {pics/result_l2e1.0.00097656.dat}; 
-\addlegendentry{$\nu=2^{-10}$};
-\addplot[mark=triangle,blue] table {pics/result_l2e1.0.00024414.dat}; 
-\addlegendentry{$\nu=2^{-12}$};
-\addplot[mark=triangle, green] table {pics/result_l2e1.6.1035e-05.dat};
-\addlegendentry{$\nu=2^{-14}$};
-\addplot[mark=triangle, red] table{pics/result_l2e1.1.5259e-05.dat};
-\addlegendentry{$\nu=2^{-16}$};
-\end{loglogaxis}
-\end{tikzpicture} &
-\begin{tikzpicture}
-    \begin{loglogaxis}[
-    	width=0.45\textwidth,
-    	height=0.5\textwidth,
-        xlabel=$h$,
-        ylabel=$Error$,
-        ymin=1e-8,
-        legend style={
-at={(0.2,1.5)},
-legend pos= south east,
-anchor=south east, 
-draw=none,
-font=\tiny
-}
-]
-\addplot[mark=*,blue] table {pics/result_l2e2.1.dat}; 
-\addlegendentry{$\nu=1$};
-\addplot[mark=*,green] table {pics/result_l2e2.0.25.dat}; 
-\addlegendentry{$\nu=2^{-2}$};
-\addplot[mark=*,red] table {pics/result_l2e2.0.0625.dat}; 
-\addlegendentry{$\nu=2^{-4}$};
-\addplot[mark=square,blue] table {pics/result_l2e2.0.015625.dat}; 
-\addlegendentry{$\nu=2^{-6}$};
-\addplot[mark=square,green] table {pics/result_l2e2.0.0039062.dat}; 
-\addlegendentry{$\nu=2^{-8}$};
-\addplot[mark=square, red] table {pics/result_l2e2.0.00097656.dat}; 
-\addlegendentry{$\nu=2^{-10}$};
-\addplot[mark=triangle,blue] table {pics/result_l2e2.0.00024414.dat}; 
-\addlegendentry{$\nu=2^{-12}$};
-\addplot[mark=triangle, green] table{pics/result_l2e2.6.1035e-05.dat};
-\addlegendentry{$\nu=2^{-14}$};
-\addplot[mark=triangle, red] table{pics/result_l2e2.1.5259e-05.dat};
-\addlegendentry{$\nu=2^{-16}$};
-\end{loglogaxis}
-\end{tikzpicture} 
-\end{tabular}
-\caption{In the left figure we show the $L_{2}$-error of $E_{x}(x)$, and in the right figure the $L_2$-error of $E_y(x)$ is shown.}
-\label{fig:l2_err_e2}
-\end{figure}
+The results of the experiments for different $\nu$ are shown in Figure \ref{fig:dependence}.
 
-Denoting by $E_{x}^{h}$ the solution $E_{x}(x)$ computed on the mesh with a width $h$, and by $E_{x}^{c}$ the solution computed on the finest mesh, let 
+Denoting by $E_{x}^{h}$ the solution $E_{x}(x)$ computed on the mesh with a width $h$, and by $E_{x}^{c}$ the solution computed on a \urev{mesh multiple times finer}, let 
 \begin{align}
@@
 %anchor=south east, 
-draw=none
+draw=none, 
+xmin=0.5e-5
 }

### 2015-01-29 report/proc.tex
Bruno's proc.tex

@@
 \usepackage{placeins}
-\newenvironment{remark}[1][Remark]{\begin{trivlist}
-\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
+%\newenvironment{remark}[1][Remark]{\begin{trivlist}
+%\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
 \newtheorem{theorem}{Theorem}[section]
@@
 \newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{remark}[theorem]{Remark}
 \definecolor{blue}{rgb}{0.30,0.8,1}
@@
 %%-----------------------------
-\title{Study of the
-	numerical solution of X-Modes equations around the hybrid resonance} %\thanks{...}\thanks{...}% At most 5 thanks
+\title{A numerical study of the
+	solution of X-Mode equations around the hybrid resonance}
+\thanks{\rm The authors acknowledge 
+	the support
+	of ANR under contract ANR-12-BS01-0006-01. Moreover 
+	this work was carried out within the framework of the European Fusion Development Agreement and 
+	the French Research Federation for Fusion Studies. 
+	It is supported by the European Communities under the contract of Association between Euratom and CEA. 
+	The views and opinions expressed herein do not necessarily reflect those of the European Commission.} %\thanks{...}\thanks{...}% At most 5 thanks
 %
@@
 \maketitle
-\textcolor{red}{should we add Olivier Lafitte and Remi Sart anywhere in the proceeding ?}\\
+%\textcolor{red}{should we add Olivier Lafitte and Remi Sart anywhere in the proceeding ?}\\
 
@@
 \begin{thebibliography}{99}
-\bibitem{abramowitz_stegun} Abramowitz M.
-and Stegun I.
-A., eds.
-(1972).
-Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables.
-New York: Dover Publications.	Handbook of mathematical functions
-\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
+\bibitem{cedar}
+Charles, F., Despr\'es, B., Merhenberg, M, 
+Enhanced convergence estimates for semi-lagrangian schemes Application to the Vlasov-Poisson equation, SIAM J. Numer. Anal. 2013, 51(2), 840-863.
+
 \bibitem{stable_yee_plasma_current} Da Silva, F., Campos-Pinto, M., Després, B., and Heuraux, S. (2014). Stable coupling of the Yee scheme with a linear current model.
+
+\bibitem{compfluids}
+S. Del Pino, B. Despr\'es, P. Hav\'e, H. Jourdren, and P. F. Piserchia. 3D finite
+volume simulation of acoustic waves in the earth atmosphere.
+Comput. \&
+Fluids, 38(4):765-777, 2009.
+
+\bibitem{reflectometers_2006} Da Silva, F., Heuraux, S and  Manso, M.
+(2006).
+Developments on reflectometry simulations for fusion plasmas: application to ITER position reflectometers.
+Journal of plasma physics, 72(06), 1205-1208.
+
 \bibitem{reflectometers_2010}Da Silva, F., Heuraux, S., Gusakov, E.
@@
 Plasma Science, IEEE Transactions on, 38(9), 2144-2149.
-\bibitem{reflectometers_2006} Da Silva, F., Heuraux, S and  Manso, M.
-(2006).
-Developments on reflectometry simulations for fusion plasmas: application to ITER position reflectometers.
-Journal of plasma physics, 72(06), 1205-1208.
+
 \bibitem{Despres_2014} Després, B., Imbert-Gérard, L. M. and Weder, R. (2014). Hybrid resonance of Maxwell's equations in slab geometry. Journal de Mathématiques Pures et Appliquées, 101(5), 623-659.
+
 \bibitem{Dumont_2005} Dumont, R.
@@
 Physics of Plasmas (1994-present), 12(4), 042508.
+
 \bibitem{Freidberg_2007} Freidberg, J. P. (2007). Plasma physics and fusion energy. Cambridge university press.
+
+\bibitem{phdhattori}
+T. Hattori, T. (2014).
+D\'ecomposition de domaine pour la simulation Full-Wave dans un plasma froid.
+Ph.D. Thesis, Universit\'e de
+Lorraine.
+
 \bibitem{LMIG_thesis} Imbert-Gérard, L.
@@
 Analyse mathématique et numérique de problèmes d'ondes apparaissant dans les plasmas magnétiques (Doctoral dissertation, Université Pierre et Marie Curie-Paris VI).
+
+\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
+
+\bibitem{simon}
+Simon Labrunie, Pierre Bertrand, Jean-Rodolphe Roche, Aurore Back,
+Takashi Hattori, 
+Electromagnetic wave propagation and absorption in
+magnetised plasmas: variational formulations and
+domain decomposition, Hal preprint 2014, https://hal.archives-ouvertes.fr/hal-01075137.
+
+\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
+
 \bibitem{Morawetz} Morawetz, C. S. (1962). The limiting amplitude principle. Communications on Pure and Applied Mathematics, 15(3), 349-361.
-\bibitem{Mouhot_2011} Mouhot, C., and Villani, C. (2011). On landau damping. Acta mathematica, 207(1), 29-201.
-\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
- \bibitem{Xu_2006}Xu, L., ans Yuan, N. (2006). FDTD formulations for scattering from 3-D anisotropic magnetized plasma objects. Antennas and Wireless Propagation Letters, IEEE, 5(1), 335-338.
+
+\bibitem{Mouhot_2011} Mouhot, C., and Villani, C. (2011). On Landau damping. Acta mathematica, 207(1), 29-201.
+
+\bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
+Handbook of mathematical functions
 \end{thebibliography}

### 2015-01-29 report/abstract.tex
Bruno's abstract/resume/intro/FD/timedomain

--- 2015-01-26 report/abstract.tex
@@
-Hybrid resonnance is a physical phenomenon that appears for example in the heating of plasma, and as such is of interest in the developping of new energy source, like for instance in the ITER project.
-In this paper we focus on the  non-regularity of
-the solutions of Maxwell equations in plasmas under strong background magnetic field.
-Our purpose here is two-fold.
-On one hand we investigate the finite element approximation of the one dimensionnal problem written in the frequency domain, and on the other hand we investigate the finite difference approximation of the one dimensionnal time dependant problem.
-We will also compare the results of theses to differents methods.
+Hybrid resonance is a physical phenomenon
+that appears for example in the heating of plasma,
+and as such is of scientific interest in the development  of  the ITER project.
+In this paper we focus some solutions with low regularity of Maxwell equations in
+plasmas under strong background magnetic field.
+Our purpose is two-fold.
+On one hand we investigate the finite element approximation of the one dimensional problem 
+written in the frequency domain, and on the other hand we investigate two different 
+finite difference approximations of the one dimensional time dependent problem.
+We will also compare the results of these different methods.

### 2015-01-29 report/intro.tex
Bruno's abstract/resume/intro/FD/timedomain

@@
 depends on spatial variables and is uniform in time. 
-Without loss of generality, we set $\mathbf{B}_0=\left(0,\; 0,\; B_0\right)$, which allows to obtain the following system of equations 
+Without loss of generality, we set $\mathbf{B}_0=\left(0,\; 0,\; B_0\right)$, which allows to obtain the following system of 1D equations 
 \begin{align}
@@
 \left\{\begin{array}{l}
-\epsilon_0\partial_t E_{x}-\partial_y H_z=-eN_e u_x,\\
-\epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\\
-\mu_0\partial_t H_z+\partial_x E_y-\partial_y E_x=0,\\
-m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
-m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
+\epsilon_0\partial_t E_{x}&=-eN_e u_x,\\
+\epsilon_0\partial_t E_{y}+\partial_x H_z&=-eN_e u_y,\\
+\mu_0\partial_t H_z+\partial_x E_y &=0,\\
+m_e\partial_t u_x&=eE_x+eu_yB_0-\nu m_e u_x,\\
+m_e\partial_t u_y&=eE_y-eu_xB_0-\nu m_e u_y
 \end{array}
@@
 {\mathcal E}(t)= \int_\Omega \left(
-\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e N_e|\mathbf{u} (t,\x)|^2}{2} 
+\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|^2}{2|e|N_e(\x)} 
 \right)\mathrm{d}\x.
 \een}
-\mrev{An energy-preserving scheme for discretizing (\ref{eq:main_model}) was recently developed in \cite{Despres_2014}. 
-It can be shown that for non-zero collision frequency $\nu$ the loss of energy is proportional to $\nu$, however, as $\nu\rightarrow0+$, it 
-does not vanish. This behaviour had been recently investigated in \cite{Despres_2014}}.
+It can be shown    \cite{Despres_2014} 
+that the time harmonic electric field component $E_x$ in this case is no longer square 
+integrable, with 
+explicit estimates on the behavior of the solutions of \eqref{eq:main_model} in 1D were provided. 
+This apparent paradox  is of course the source of important numerical difficulties which are the subject of the present study.
 
-We complement Problem (\ref{eq:main_model}) with the following boundary conditions.
-At the left boundary of the domain, which represents the wall, we choose Robin boundary conditions 
+We complement Problem (\ref{eq:main_model}) with the boundary conditions.
+At the left boundary of the domain, which represents the wall of the Tokamak, we choose Robin boundary conditions 
+\be
+-curl \E -\imath \omega\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath\omega\E_{inc} \wedge \n,
+\ee
+where $\E_{inc} = \exp \left(\imath \omega x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and $\omega$ is 
+the frequency of the antenna.
+%some given 
+%frequency. 
+We truncate the domain 
 \ben
@@
 $(-L,\; \infty)$ to $(-L,\; H)$ and set on the right boundary $\operatorname{curl} \E = 0$. 
-\begin{remark}
-	When modelling antennas in plasma physics \mrev{(e.g. in such applications as ITER)}, 
-	a good choice of boundary condition could be $\lambda = \sqrt{\alpha(-L)}$
-\end{remark}
+%\begin{remark}
+%	When modelling antennas in plasma physics \mrev{(e.g. in such applications as ITER)}, 
+%	a good choice of boundary condition could be $\lambda = \sqrt{\alpha(-L)}$
+%\end{remark}
 
-The goal of this article is two-fold. 
+The goal of this article is three-fold. 
 First, we investigate the finite element approximation of the 1D 
@@
 We prove the well-posedness of this problem for $\nu>0$ in Section~\ref{sec:wellposedness} and 
-demonstrate that the use of higher-order (P1) finite elements allows to approximate the singularity 
+demonstrate that the use of  (P1) finite elements allows to approximate the singularity 
 of the solution fairly well (Section \ref{sec:freq_dep}). 
-Second, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
+Second, we briefly develop an original scheme based on widely appreciated semi-lagrangian schemes
+for the discretization of time domain Maxwell's equations with a linear current.
+Thirdly we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
 $\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
@@
 $\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
-$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$, i.e. we check the validity of the scheme in Figure \ref{fig:limits}. 
-\begin{figure}
-\begin{tikzpicture}
-   \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em] {
-     \mathbf{E}^{\nu}(t) & \mathbf{E}^{0+}(t)\\
-     \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t} & 
-     \lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow \infty}\mathbf{E}^{\nu}(t)=\lim\limits_{t\rightarrow \infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}^{\nu}(t)\\
-     };
-  \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow\infty$} (m-2-1);
-  \path[-stealth, font=\scriptsize]   (m-1-1) edge node [above] {$\nu\rightarrow 0+$} (m-1-2);
-  \path[-stealth, font=\scriptsize]   (m-2-1) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
-  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow \infty$} (m-2-2);
-
-  % \path[-stealth] (m-2-1.east) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
-    %(m-1-2) edge node [right] {$\nu\rightarrow 0$} (m-2-2);
-\end{tikzpicture}
- \caption{\label{fig:limits}Schematic representation of the equivalence of the limited absorption and limiting amplitude principles.}
-
-\end{figure}
+$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
+Such a comparison is a way to study the formal commutation relation
+$$
+\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}= \lim\limits_{t\rightarrow+\infty}\lim\limits_{\nu\rightarrow 0}.
+$$
+Even it is true for standard linear wave problems, it is not clear that it still hold in our case due the singularity
+of the hybrid resonance.
+%\begin{figure}
+%\begin{tikzpicture}
+%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em] {
+%     \mathbf{E}^{\nu}(t) & \mathbf{E}^{0+}(t)\\
+%     \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t} & 
+%     \lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow \infty}\mathbf{E}^{\nu}(t)=\lim\limits_{t\rightarrow \infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}^{\nu}(t)\\
+%     };
+%  \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow\infty$} (m-2-1);
+%  \path[-stealth, font=\scriptsize]   (m-1-1) edge node [above] {$\nu\rightarrow 0+$} (m-1-2);
+%  \path[-stealth, font=\scriptsize]   (m-2-1) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
+%  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow \infty$} (m-2-2);
+%
+%
+%  % \path[-stealth] (m-2-1.east) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
+%    %(m-1-2) edge node [right] {$\nu\rightarrow 0$} (m-2-2);
+%\end{tikzpicture}
+% \caption{\label{fig:limits}Schematic representation of the equivalence of the limited absorption and limiting amplitude principles.}
+%
+%\end{figure}
 

### 2015-01-29 report/resume.tex
Bruno's abstract/resume/intro/FD/timedomain

--- 2015-01-26 report/resume.tex
@@
-La r\'esonnance hybride est un ph\'enom\`ene physique qui apparait par exemple lorsque l'on chauffe un plasma, et est ainsi d'int\'er\^et dans le d\'eveloppement d'une nouvelle source d'\'energie, comme dans le cadre du projet ITER.
-Dans ce papier, nous nous concentrons sur la non r\'egularit\'e des solutions des \'equations de Maxwell pour les plasmas sous l'influence de champ magn\'etiques forts.
+La r\'esonnance hybride est un ph\'enom\`ene physique qui apparait par exemple lorsque l'on chauffe un plasma, et 
+ainsi est d'int\'er\^et scientifique dans le cadre du d\'eveloppement  du projet ITER.
+Dans ce papier, nous nous concentrons sur certaines  solutions faiblement r\'eguli\`eres des \'equations de Maxwell pour les plasmas sous l'influence de champ magn\'etiques forts.
 Notre but est ici double.
-D'un c\^ot\'e nous regardons l'approximation \`a l'aide d'\'el\'ements finis du probl\`eme en une dimension \'ecrit dans le domaine en fr\'equence, et de l'autre nous regardons l'approximation \`a l'aide de diff\'erences finies du probl\`eme en une dimension mais d\'ependant en temps.
-Nous comparons \'egalement les r\'esultats de ces deux diff\'erentes m\'ethodes.
+D'un c\^ot\'e nous \'evaluons l'approximation
+num\'erique \`a l'aide d'\'el\'ements finis en une dimension en formulation 
+fr\'equentielle, et de l'autre nous \'etudions l'approximation num\'erique \`a l'aide de deux m\'ethodes de  diff\'erences finies pour la formulation
+temporelle monodimensionelle. Nous comparons les r\'esultats de ces  diff\'erentes m\'ethodes.

### 2015-01-29 report/timedomain.tex
Bruno's abstract/resume/intro/FD/timedomain

@@
 \section{Time Dependent Problem Discretization}
+Let us consider the system (\ref{eq:main_model}) in dimension one in the X-mode configuration which is transverse electric.
+\subsection{A staggered scheme}
 In this section, we develop a discretization of the time dependant problem~\eqref{eq:main_model} 
 in one dimension. In 1D, the derivatives with respect to $y$ vanish, and we are left with the following problem, 
- \begin{align}
- \epsilon_0\partial_t E_{x}=-eN_e u_x, \nonumber\\
- \epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\nonumber\\
- \mu_0\partial_t H_z+\partial_x E_y-\partial_y E_x=0, \label{eq:tdpb}\\
- m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
- m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y.\nonumber
- \end{align}
+% \begin{align}
+% \epsilon_0\partial_t E_{x}=-eN_e u_x, \nonumber\\
+% \epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\nonumber\\
+% \mu_0\partial_t H_z+\partial_x E_y-\partial_y E_x=0, \label{eq:tdpb}\\
+% m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
+% m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y.\nonumber
+% \end{align}
 We compute a numerical approximation of~\eqref{eq:tdpb} on a cartesian grid using the Yee scheme, 
@@
 \mrev{whereas the field $H_z$ is on half time steps, $t_{n+1/2}$}. The time discretization of the system reads:
- \begin{align}
+ \bealn
  \left\{\begin{array}{l}
@@
 \end{array}\right.
- \end{align}
+ \eealn
 In Yee scheme, the differents components of the vector fields 
@@
 
-\be 
+\ben 
 \eps_0 \frac{E_x\inp- E_x\midin}{\Delta t} = -e N_e \frac{u_x\inp + u_x \midin}{2},
 \label{eq:ns1}
-\ee 
-\be
+\een 
+\ben
 \eps_0 \frac{E_y\ihnp-E_y\ihn}{\Delta t}+ \frac{H_z\ipnh-H_z\inh}{\Delta x} = -eN_x \frac{u_y\ihnp + u_y\ihn}{2} ,
 \label{eq:ns2}
-\ee
-\be
+\een
+\ben
  \frac{H_z\inh-H_z\inmh}{\Delta t}+ \frac{E_y\ihn-E_y\imhn}{\Delta x}=0,
  \label{eq:ns3}
-\ee
-\be 
+\een
+\ben 
 m_e \frac{u_x\inp-u_x\midin }{\Delta x} = e N_e \frac{E_x\inp+E_x\midin}{2}-\nu m_e\frac{u_x\inp+u_x \midin}{2}+ eB_0\frac{u_y\ihn+u_y\ihnp}{2},
 \label{eq:ns4}
-\ee
-\be
+\een
+\ben
 m_e \frac{u_y\ihnp-u_y\ihn}{\Delta t} = eN_e \frac{E_y\ihnp + E_y\ihn}{2}- \nu m_e \frac{u_y\ihnp +u_y\ihn}{2}-eB_0 \frac{u_x\midin+u_x\inp}{2},
 \label{eq:ns401}
-\ee
-\input{grid}
+\een
+%\input{grid}
+\begin{figure}[h!]
+	\begin{center}
+		\begin{tikzpicture}
+
+		\draw[thin] (0, 0) grid (2, 2);
+		\foreach \x in {0,1,2}
+		\foreach \y in {0,1,2}
+		\draw[fill](\x,\y) circle (2pt) ;
+		\foreach \x in {0.5,1.5}
+		\foreach \y in {0,1,2}
+		\draw[fill,blue](\x,\y) circle (2pt) ;
+		\foreach \x in {0,1,2}
+		\foreach \y in {0.5,1.5}
+		\draw[fill,red](\x,\y) circle (2pt) ;		
+		\draw[->] (0,0) -- (0,2.5);
+		\draw[->] (0,0) -- (2.5,0);
+		\coordinate (Origin)   at (0,0);
+		\node (xlab) at (2.5,-0.5){\tiny $x$};
+		\node (tlab) at (-0.5,2.5){\tiny $t$};
+		%      \node[black] (exux) at (2.6,1){\tiny $E_x$, $u_x$};
+		%      \node[blue](eyuy) at (1.5,2.5){\tiny $E_y$, $u_y$};
+		%      \node[red] (hz) at (2.5,1.5) {\tiny $H_z$};
+		\node[black] (xilab) at (-0.5,0){\tiny $(x_i, t^n)$};
+		\node[blue](xid) at (0.5,-0.3){\tiny $(x_{i+1/2},t^n)$};
+		\node[red] (tid) at (-0.8,0.5) {\tiny $(x_i,t^{n+1/2})$};
+
+		\end{tikzpicture} 
+		%	\label{schemepos}
+	\end{center}
+	\caption{Positions of $E_x$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) on the discretized grid in space and time}
+
+	\label{schemepos}
+\end{figure}
+
 It is possible to rewrite this system in an explicit form (we omit here these simple but slightly tedious computations).
@@
 % + e \Delta t N_e E_x \midin  + \left( \frac{eB_0 \Delta t K_2}{2 K_1}+ \frac{e B_0 \Delta t}{2}\right) u_y\ihn - \frac{(e\Delta t)^2 N_e B_0}{2K_1}E_y\ihn  - \frac{e^2(\Delta t)^3 B_0}{4K_1}\frac{H_z \ipnh- H_z \inh}{\Delta x},
-%\label{eq:ns10} 
+%\labelnd{align}{eq:ns10} 
 %\end{align}
@@
 %\end{itemize}
+\subsection{A co-localized scheme based on semi-lagrangian discretisation}
+
+The scheme that is described hereafter is mentioned since it is based on some well-known 
+numerical methods in plasma physics, the so-called semi-lagrangian schemes 
+which are widely used for the numerical approximation of transport equations.
+It seems to be an original use of semi-lagrangian schemes 
+and is mentioned since it can be an option. 
+We restrict the presentation to the minimum and leave the details  of the construction to the alert reader.
+
+The idea is to split 
+the system (\ref{eq:main_model})
+into a series of  transport equations (here just 2) and a local in-the-cell system.
+
+- At time step $t_n=n\Delta t$, all quantities are given $(E_x,E_y, H_z, u_x,u_y)_{i}^n$ in the cells, that is for all $i$ in the 
+computational domain.
+
+- The first step is to solve 
+$$
+\left\{
+\begin{array}{lll}
+\epsilon_0\partial_t E_{x}=0,\\
+\epsilon_0\partial_t E_{y}+\partial_x H_z=0,\\
+\mu_0\partial_t H_z+\partial_x E_y=0,\\
+m_e\partial_t u_x=0,\\
+m_e\partial_t u_y=0,
+\end{array}
+\right.
+$$
+Since  $\epsilon_0 \mu_0c^2=1$, this can be  performed solving
+two transport equations 
+$$
+\left\{
+\begin{array}{lll}
+\partial_t w +c \partial_x w=0, & w=E_{y}+ c H_z,  \\
+\partial_t z -c \partial_x z=0& z=E_{y}-  c H_z.
+\end{array}
+\right.
+$$
+In our case we used 
+a semi-lagrangian scheme for a time step $\Delta t$.
+In the tests, we used Strang's stencils described in \cite{cedar} with CFL $\nu=0.5$, at order 7. 
+It  yields the chain 
+$(E_y,H_z)_i^n\mapsto ( w,z)_i^n\mapsto ( w,z)_i^{n*}\mapsto E_y,H_z)_i^{n*} $.
+Here $n*$ denotes the intermediate stage of the algorithm.
+
+- The second (and final) step is to solve
+$$
+\left\{\begin{array}{l}
+\epsilon_0\partial_t E_{x}=-eN_e u_x,\\
+\epsilon_0\partial_t E_{y}=-eN_e u_y,\\
+\mu_0\partial_t H_z=0,\\
+m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
+m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y.
+\end{array}
+\right.$$
+This is performed locally in every cells starting from the data at the preceding 
+step. In our case we just adapt the algorithm developed for the staggered scheme.
+We make sure that the method is conservative in total energy if $\nu=0$, using a half step discretization
+of the right hand sides.
+
+- Therefore  all quantities are now given $(E_x,E_y, H_z, u_x,u_y)_{i}^{n+1}$ in the cells 
+at time step $t_{n+1}=(n+1)\Delta t$, and it is enough to loop in time.
+
+\begin{remark}
+	The structure of this algorithm is very similar to the one developed in \cite{compfluids} and can be adapted and studied numerically
+	in any dimension on a Cartesian grid and for more complex right hand sides.
+\end{remark}

### 2015-01-29 report/intro.tex
align mistake in intro.tex
decolouring

@@
 Without loss of generality, we set $\mathbf{B}_0=\left(0,\; 0,\; B_0\right)$, which allows to obtain the following system of 1D equations 
-\begin{align}
+\begin{equation}
 \label{eq:main_model}
-\left\{\begin{array}{l}
-\epsilon_0\partial_t E_{x}&=-eN_e u_x,\\
-\epsilon_0\partial_t E_{y}+\partial_x H_z&=-eN_e u_y,\\
-\mu_0\partial_t H_z+\partial_x E_y &=0,\\
-m_e\partial_t u_x&=eE_x+eu_yB_0-\nu m_e u_x,\\
-m_e\partial_t u_y&=eE_y-eu_xB_0-\nu m_e u_y
-\end{array}
-\right.\end{align}
+\begin{cases}
+\epsilon_0\partial_t E_{x}=-eN_e u_x,\\
+\epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\\
+\mu_0\partial_t H_z+\partial_x E_y =0,\\
+m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
+m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
+\end{cases}
+\end{equation}
 posed in $[-L,\; \infty)\times \mathbb{R}$, for some $L>0$. This domain represents the physical case of a wave sent from a wall facing a plasma. 
 The energy of this system for $\nu=0$ in a domain $\Omega\in\mathbb R^2$ can be expressed as \cite{stable_yee_plasma_current}
-\mrev{\ben
+\ben
 {\mathcal E}(t)= \int_\Omega \left(
@@
 \right)\mathrm{d}\x.
-\een}
+\een
 It can be shown    \cite{Despres_2014} 

### 2015-01-29 report/numerics.tex
numerics.tex, this one was tricky

@@
 This section is organized as follows. The first part is dedicated to the numerical implementation
-of the frequency domain formulation (\ref{eq:main_frequency_domain}). We study the convergence of this formulation and the behaviour 
+of the frequency domain formulation \eqref{eq:main_frequency_domain}. We study the convergence of this formulation and the behaviour 
 of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
@@
 
-The second part of the section deals with the question of the equivalence of the limiting absorption and limited amplitude 
+The intermediate part briefly validates the semi-lagrangian discretization of the time domain formulation.
+
+The last part of the section deals with the question of the equivalence of the limiting absorption and limited amplitude 
 principle. We compare the solutions obtained as $\nu\rightarrow 0$ with the help of our frequency domain code 
@@
 is written in Fortran.
+
 \subsection{Frequency Domain Problem}
@@
 \subsubsection{Validity of the Implementation}
-To check the validity of the code, we perform a numerical experiment with (formally chosen) parameters:
+To check the validity of the code, we first perform a numerical experiment with (formally chosen) parameters:
 \begin{align}
@@
 with the choice of the boundary conditions as above, we obtain that 
-\bealn
-E_{y}=Ai(x),\qquad 
-E_{x}=-i\frac{\delta(x)}{\alpha(x)}Ai(x)
-\eealn
+$
+E_{y}=Ai(x)  $  and   %,\qquad 
+$E_{x}=-i\frac{\delta(x)}{\alpha(x)}Ai(x)$
 is the solution to the problem with parameters (\ref{eq:parameters}) with the boundary condition (\ref{eq:bcs_airy}). 
-The well-posedness of the respective variational formulation is due to Remark \ref{remark:other}.
+%The well-posedness of the respective variational formulation is due to Remark \ref{remark:other}.
 
@@
 
-Note that in the last 3 experiments the error of the solution of the system of equations, namely $\|Ae-r\|$ (where $e$ is the solution vector, $r$ is the right hand side and $A$ is the block matrix (\ref{eq:simple_system}) ) exceeded 1.6e-9
+Note that in the last 3 numerical experiments the error of the solution of the system of equations, namely $\|Ae-r\|$ (where $e$ is the solution vector, $r$ is the right hand side and $A$ is the block matrix (\ref{eq:simple_system}) ) exceeded 1.6e-9
 (namely, it was 1.6e-9 ($h=3.2e-5$), 1.3e-08 ($h=8e-6$), 1.04e-07 ($h=2e-6$)).
 
-Importantly, the obtained convergence rates are in agreement with known estimates of \cite{brenner}.
+Importantly, the obtained convergence rates are in agreement with known estimates of the standard theory of convergence~\cite{brenner}.
 
-\subsubsection{Solution of $X$-Mode Prolbem}
-\paragraph{Convergence}
+\subsubsection{Solution of $X$-Mode Problem}
+%\paragraph{Convergence}
 Let us consider the case of the resonance, more precisely, we consider sufficiently smooth
@@
 of Lemma \ref{lemma:well_posedness}  are satisfied. 
-For simplicity, let 
+For simplicity, let us consider 
 \begin{align}
@@
 Given $\mathbf{V}_{h}=P_{h}^{1}\times P_{h}^{1}$, with $P_{h}^{1}$ consisting of piecewise-linear (hat) functions, 
-we look for a ratio $h(\nu)$ that would ensure that the absolute error 
+we look for a ratio $h(\nu)$ that would ensure the bound on the absolute error 
 \begin{align}
@@
  \left|\frac{d^2}{dx^2}E_x^{\nu}\right|_{L_2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
-  &=c\left.
- \left(\frac{x}{4(x^2+\nu^2)^2}\nu^{-2}+\frac{3x}{8(x^2+\nu^2)}\nu^{-4}+\frac{3}{8}\nu^{-5}\operatorname{atan}\frac{x}{\nu}\right)\right|_{-L}^{H}
+ % &=c\left.
+ %\left(\frac{x}{4(x^2+\nu^2)^2}\nu^{-2}+\frac{3x}{8(x^2+\nu^2)}\nu^{-4}+\frac{3}{8}\nu^{-5}\operatorname{atan}\frac{x}{\nu}\right)\right|_{-L}^{H}
  \leq C\nu^{-5},\; 
@@
 \een
-from which it follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
+Let us assume that $d=2$ is possible by some Aubin-Nitsche lemma for our problem.
+It follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
 \begin{align}
@@
 \end{align}
-where $\alpha_{\epsilon}>0$ depends on $\epsilon$ but does not depend on $\nu$. Let us check optimality of this estimate.  
+where $\alpha_{\epsilon}>0$ depends on $\epsilon$ but does not depend on $\nu$. his prediction is very severe and is due to the singular nature of the problem under consideration.
+
+Let us check numerically whether this holds true. 
 To do so, we conduct the  numerical experiment with parameters for the problem as given in Table \ref{tab:parameters}.
@@
 \end{table}
-Remarkably, for $\nu=0$ the computed matrices are not singular. \urev{We do not know the exact reason for this.}
+Remarkably, for $\nu=0$ the computed matrices are not singular. We do not know the exact reason for this.
 As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Fig.~\ref{fig:small_nu}. 
@@
  \label{fig:small_nu}
+\end{figure}
+
+\FloatBarrier
+
+\subsection{A validation of the semi-lagrangian scheme}
+
+We show the results of very basic simulations that the numerical strategy 
+based on co-localised semi-lagrangian discretization is valid even for the resonant 
+case.
+The numerical tests have been kept to a minimum since much more are needed to fully validate
+the concept.
+
+The setting of the numerical results of figure \ref{fig:vasl}
+is the following. We use a 7th order semi-lagrangian scheme, and the CFL is $\nu=0.5$.
+The Pike is the hybrid resonance, visible on $E_x$ and $u_x$.
+The total energy $\mathcal E(t)$ is the physical energy. 
+The comparison with figures \ref{fig:dependence} and \ref{fig:resonance_nus_ey_x} show that the 
+singular nature of the resonant is captured by this new scheme without any duobt.
+
+\begin{figure}{h}
+	\begin{center}
+		\begin{tabular}{ccc}
+			\includegraphics[angle=-90,width=5.cm]{Ey_moit.eps}
+			&
+			\includegraphics[angle=-90,width=5.cm]{Hz_moit.eps} &
+			\includegraphics[angle=-90,width=5.cm]{Ex_moit.eps}
+			\\
+			$E_y$ & $H_z$  & $E_x^\nu$ \\
+			%\hline
+			\hline
+			\includegraphics[angle=-90,width=5.cm]{uy_moit.eps}
+			&
+			\includegraphics[angle=-90,width=5.cm]{normes_moit.eps}
+			&
+			\includegraphics[angle=-90,width=5.cm]{ux_moit.eps}
+			\\      
+			$u_y$ & $t\mapsto \mathcal E(t)$ & $u_x^\nu$  \\
+
+			%\includegraphics[width=4.cm]{cap14.png} 
+			\\
+
+		\end{tabular}   \end{center}
+		\caption{An antenna sends a time harmonic wave on the left. The medium is propagative
+			on the left and non propagative
+			on the right. The resonance is visible on $E_x$ and $u_x$. The time of the simulation is $T=2000$. The number of cells
+			is typically 10000 to reach convergence.}
+		\label{fig:vasl}
 	\end{figure}

### 2015-01-29 report/absorption.tex
absorption.tex

@@
 \subsection{Limiting Amplitude and Limiting Absorption Principle}
-In this section we perform several numerical experiments,
-with the normalization chosen as $\epsilon_0=\mu_0=1$, $\omega=c=1$. 
+In this section we perform several numerical experiments to check wether the limit amplitude
+principle and the limit
+absorption principle are equivalent for our problem.
+That is we compare the solution of the time harmonic code with the solution of the time domain staggered code.
+
+We normalize  $\epsilon_0=\mu_0=1$ and $\omega=c=1$. 
 Also, we set $m_e=1$ and $e=-1$. From this it follows that $w_c=-B_0$ and $w_p^2=N_e$. 

### 2015-01-29 report/proc.tex
booboo in bruno's adress
smalls changes to check

@@
 \author{C\'eline Caldini-Queiros}\address{Max Planck Institute für PlasmaPhysik, Garching bei Muenchen}
-\author{Bruno Despr\'es}\address{Laboratoire Jacques-Louis Lions, University PARIS 6}
+\author{Bruno Despr\'es}\address{Sorbonne Universit\'es, UPMC Univ Paris 06, UMR 7598, Laboratoire Jacques-Louis Lions, F-75005, Paris, France}
 \author{Lise-Marie Imbert-Gérard}\address{Courant Institute of Mathematical Sciences, New York University}
@@
 \begin{thebibliography}{99}
+	\bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
+	Handbook of mathematical functions
+	\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
 \bibitem{cedar}
@@
 
-\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
-
 \bibitem{simon}
@@
 
-\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
-
 \bibitem{Morawetz} Morawetz, C. S. (1962). The limiting amplitude principle. Communications on Pure and Applied Mathematics, 15(3), 349-361.
@@
 \bibitem{Mouhot_2011} Mouhot, C., and Villani, C. (2011). On Landau damping. Acta mathematica, 207(1), 29-201.
-
-\bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
-Handbook of mathematical functions
+\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
+\bibitem{Xu_2006}Xu, L., ans Yuan, N. (2006). FDTD formulations for scattering from 3-D anisotropic magnetized plasma objects. Antennas and Wireless Propagation Letters, IEEE, 5(1), 335-338.
 \end{thebibliography}

### 2015-01-29 report/timedomain.tex
smalls changes to check

@@
 % \end{align}
-We compute a numerical approximation of~\eqref{eq:tdpb} on a cartesian grid using the Yee scheme, 
+We compute a numerical approximation of~\eqref{eq:main_model} on a cartesian grid using the Yee scheme, 
 as suggested in \cite{stable_yee_plasma_current}. Let $n$ denote the time step index, as usual $t_n = n \Delta t$. 
 It is standard (see \cite{Xu_2006,stable_yee_plasma_current }) to discretize the electrical field on the integer time step, 
-\mrev{whereas the field $H_z$ is on half time steps, $t_{n+1/2}$}. The time discretization of the system reads:
+whereas the field $H_z$ is on half time steps, $t_{n+1/2}$. The time discretization of the system reads:
  \bealn

### 2015-02-02 report/intro.tex
ctrlv error fixed
comma missing

@@
 %frequency. 
+%We truncate the domain 
+%\ben
+%-curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
+%\een
+%where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$.
 We truncate the domain 
-\ben
--curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
-\een
-where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$. We truncate the domain 
 $(-L,\; \infty)$ to $(-L,\; H)$ and set on the right boundary $\operatorname{curl} \E = 0$. 
@@
 for the discretization of time domain Maxwell's equations with a linear current.
-Thirdly we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
+Thirdly, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
 $\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 

### 2015-02-02 report/numerics.tex
removed red line 184

@@
 
-Denoting by $E_{x}^{h}$ the solution $E_{x}(x)$ computed on the mesh with a width $h$, and by $E_{x}^{c}$ the solution computed on a \urev{mesh multiple times finer}, let 
+Denoting by $E_{x}^{h}$ the solution $E_{x}(x)$ computed on the mesh with a width $h$, and by $E_{x}^{c}$ the solution computed on a mesh multiple times finer, let 
 \begin{align}

### 2015-02-02 report/numerics.tex
typo removed (l.290)

@@
 The comparison with figures \ref{fig:dependence} and \ref{fig:resonance_nus_ey_x} show that the 
-singular nature of the resonant is captured by this new scheme without any duobt.
+singular nature of the resonant is captured by this new scheme without any doubt.
 

### 2015-02-02 report/intro.tex
intro modified

@@
 \een
-It can be shown    \cite{Despres_2014} 
+In  \cite{Despres_2014} it was shown
 that the time harmonic electric field component $E_x$ in this case is no longer square 
-integrable, with 
+integrable, and  
 explicit estimates on the behavior of the solutions of \eqref{eq:main_model} in 1D were provided. 
@@
 \be
--curl \E -\imath \omega\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath\omega\E_{inc} \wedge \n,
+-curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
 \ee
-where $\E_{inc} = \exp \left(\imath \omega x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and $\omega$ is 
+where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and $\lambda$ is 
 the frequency of the antenna.
@@
 $$
-\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}= \lim\limits_{t\rightarrow+\infty}\lim\limits_{\nu\rightarrow 0}.
+\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}= \lim\limits_{t\rightarrow+\infty}\lim\limits_{\nu\rightarrow 0},
 $$
+see Figure \ref{fig:limits}. 
 Even it is true for standard linear wave problems, it is not clear that it still hold in our case due the singularity
 of the hybrid resonance.
-%\begin{figure}
-%\begin{tikzpicture}
-%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em] {
-%     \mathbf{E}^{\nu}(t) & \mathbf{E}^{0+}(t)\\
-%     \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t} & 
-%     \lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow \infty}\mathbf{E}^{\nu}(t)=\lim\limits_{t\rightarrow \infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}^{\nu}(t)\\
-%     };
-%  \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow\infty$} (m-2-1);
-%  \path[-stealth, font=\scriptsize]   (m-1-1) edge node [above] {$\nu\rightarrow 0+$} (m-1-2);
-%  \path[-stealth, font=\scriptsize]   (m-2-1) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
-%  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow \infty$} (m-2-2);
-%
-%
-%  % \path[-stealth] (m-2-1.east) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
-%    %(m-1-2) edge node [right] {$\nu\rightarrow 0$} (m-2-2);
-%\end{tikzpicture}
-% \caption{\label{fig:limits}Schematic representation of the equivalence of the limited absorption and limiting amplitude principles.}
-%
-%\end{figure}
+\begin{figure}
+\begin{tikzpicture}
+   \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em] {
+     \mathbf{E}^{\nu}(t) & \mathbf{E}^{0+}(t)\\
+     \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t} & 
+    \lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow \infty}\mathbf{E}^{\nu}(t)=\lim\limits_{t\rightarrow \infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}^{\nu}(t)\\
+     };
+ \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow\infty$} (m-2-1);
+  \path[-stealth, font=\scriptsize]   (m-1-1) edge node [above] {$\nu\rightarrow 0+$} (m-1-2);
+ \path[-stealth, font=\scriptsize]   (m-2-1) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
+  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow \infty$} (m-2-2);
+
+   \path[-stealth] (m-2-1.east) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
+   (m-1-2) edge node [right] {$\nu\rightarrow 0$} (m-2-2);
+\end{tikzpicture}
+ \caption{Schematic representation of the equivalence of the limited absorption and limiting amplitude principles.}
+\label{fig:limits}
+\end{figure}
 

### 2015-02-03 report/numerics.tex
removed some pics+cleaning up

@@
 of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
-performed on a laptop with 2.6GHz Intel Core i5 CPU, with the help of the code written in Octave (compatible with Matlab). 
+performed with the help of the code written in Octave.  
 We implemented the scheme described in Section \ref{sec:discr} for a simple case of $P_{1}$-space used 
@@
 \label{eq:bcs_airy}
-\partial_{1}E_{y}(-L)+2iE_{y}(-L)=2iAi(-L)+Ai'(-L),\\
+\partial_{1}E_{y}(-L)+2iE_{y}(-L)=2iAi(-L)+Ai'(-L),\qquad 
 \partial_{1}E_{y}(H)=0,
@@
 is the solution to the problem with parameters (\ref{eq:parameters}) with the boundary condition (\ref{eq:bcs_airy}). 
-%The well-posedness of the respective variational formulation is due to Remark \ref{remark:other}.
+The well-posedness of the respective variational formulation for $\nu=0$ is due to Remark \ref{remark:other}.
 
-In Fig.~\ref{fig:conv_rate} we demonstrate the convergence rates for this problem, with 
-\ben
-\|E_{x}-E_{x}^{c}\|_{L_{2}(\Omega)}=\left(\int\limits_{\Omega}\left|E_{x}(x)-\sum\limits_{k=1}^{N}e_{xk}\phi_{k}\right|^2dx\right)^{\frac{1}{2}},
-\een
-where $\left(\phi_{i}\right)_{i=1}^{N}$ are $P_{1}$-finite elements and $E_{x}(x)$ is a known analytic solution.
+In Fig.~\ref{fig:conv_rate} we demonstrate the convergence rates for this problem, comparing the solution to the 
+known analytic solution. 
+%with 
+%\ben
+%\|E_{x}-E_{x}^{c}\|_{L_{2}(\Omega)}=\left(\int\limits_{\Omega}\left|E_{x}(x)-\sum\limits_{k=1}^{N}e_{xk}\phi_{k}\right|^2dx\right)^{\frac{1}{2}},
+%\een
+%where $\left(\phi_{i}\right)_{i=1}^{N}$ are $P_{1}$-finite elements and $E_{x}(x)$ is a known analytic solution.
 Similarly $\|E_{y}-E_{y}^{c}\|_{L_{2}(\Omega)}$ and $\|E_{y}-E_{y}^{c}\|_{H_{1}(\Omega)}$ are defined.
@@
 
-Note that in the last 3 numerical experiments the error of the solution of the system of equations, namely $\|Ae-r\|$ (where $e$ is the solution vector, $r$ is the right hand side and $A$ is the block matrix (\ref{eq:simple_system}) ) exceeded 1.6e-9
-(namely, it was 1.6e-9 ($h=3.2e-5$), 1.3e-08 ($h=8e-6$), 1.04e-07 ($h=2e-6$)).
+%Note that in the last 3 numerical experiments the error of the solution of the system of equations, namely $\|Ae-r\|$ (where $e$ is the solution vector, $r$ is the right hand side and $A$ is the block matrix (\ref{eq:simple_system}) ) exceeded 1.6e-9
+%(namely, it was 1.6e-9 ($h=3.2e-5$), 1.3e-08 ($h=8e-6$), 1.04e-07 ($h=2e-6$)).
 
@@
 
-We use the following well-known facts:
+We use the following ingredients (for $\nu\rightarrow 0$):
 \begin{itemize}
@@
  \|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|_{V}\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}
- \leq \nu^{-1}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}.
+ \leq C\nu^{-1}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V},\; C>0.
  \end{split}
@@
 \een
-Let us assume that $d=2$ is possible by some Aubin-Nitsche lemma for our problem.
-It follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
+Let us assume that $d=2$ is possible by some Aubin-Nitsche lemma for our problem. It follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
 \begin{align}
@@
 \end{align}
-where $\alpha_{\epsilon}>0$ depends on $\epsilon$ but does not depend on $\nu$. his prediction is very severe and is due to the singular nature of the problem under consideration.
+where $\alpha_{\epsilon}>0$ depends on $\epsilon$ but does not depend on $\nu$. 
+This prediction is very severe and is due to the singular nature of the problem under consideration.
 
@@
 \begin{table}
-\begin{tabular}{l|r}
+\begin{tabular}{l|l}
 Parameter & Value \\
 \hline
-$\alpha(x)$ & $\left\{\begin{array}{cc}
+$\alpha(x)$ & $\left\{\begin{array}{lr}
 10, & x\leq -10,\\
@@
 $\delta(x)$ & 
-$\left\{\begin{array}{cc}
+$\left\{\begin{array}{lr}
 0, & x\leq -10,\\
@@
         ylabel=$h_{\epsilon}$,
+        ymax=5e3,
+        xmin=0.5e-4,
+        xmax=0.3,
         legend style={
@@
 legend pos=north west,
-%anchor=south east, 
-draw=none, 
-xmin=0.5e-5
+font=\tiny, 
+draw=none
 }
@@
 %\addlegendentry{$\epsilon=1e-4$};
-\addplot[dashed, red] table {pics/nu1.dat}; 
-\addlegendentry{$O(\nu)$};
-\addplot[dashed, blue] table {pics/nu32.dat}; 
-\addlegendentry{$O(\nu^{\frac{3}{2}})$};
+\addplot[dashed, red] table {pics/nu32.dat}; 
+\addlegendentry{$O\left(\nu^{\frac{3}{2}}\right)$};
+\addplot[dashed, blue] table {pics/nu54.dat}; 
+\addlegendentry{$O\left(\nu^{\frac{5}{4}}\right)$};
+\addplot[dashed, green] table {pics/nu1.dat}; 
+\addlegendentry{$O\left(\nu\right)$};
 \end{loglogaxis}
@@
 &
-\includegraphics[width=0.4\textwidth]{figure1-crop.pdf}
+\includegraphics[height=0.3\textwidth]{figure1-crop.pdf}
 \end{tabular}
@@
 We can see that the estimate (\ref{eq:estimate_h}) is pessimistic compared to the one suggested by (\ref{eq:def_epsilon}), 
-at least for a given value of $\epsilon$.
+at least for given values of $\epsilon$ and for a chosen range of $\nu>0$.
 
@@
 \paragraph{Condition Number}
-In Table \ref{tab:cond_number} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
+In Figure \ref{tab:cond_number} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
 on $\nu$, for several values of $h$.
+\begin{figure}
+
+\end{figure}
+
 \begin{table}[ht!]

### 2015-02-03 report/absorption.tex
similarly to...

@@
 inside the domain and plot the dependence of the solution $E_{y}^{\nu}(x_c,t), \; \Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right)$ 
-on time $t$ for a range of $t\gg 1$ in Fig.~\ref{fig:nu1e2_harmon}.
+on time $t$ for a range of $t\gg 1$ in Fig.~\ref{fig:nu1e2_harmon}. We compare this solution to the computed $\Im\left(\hat{E}_y^{\nu}\mathrm{e}^{it}\right)$, for
+fixed values of $t$. Both solutions appear to be in close agreement.
 
 \begin{figure}[htb]
-\includegraphics[width=0.85\textwidth]{airy/figure_nu1e2-crop.pdf}
-\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time for large times.}
+\begin{tabular}{cc}
+\includegraphics[height=0.2\textwidth]{airy/figure_nu1e2-crop.pdf} & \includegraphics[height=0.2\textwidth]{airy/figure_nu1e2_2-crop.pdf}
+\end{tabular}
+\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time for large times is demonstrated in the left figure.  
+In the right figure we show the solution for $\nu=10^{-2}$, for two fixed moment of times.}
  \label{fig:nu1e2_harmon}
@@
 
-In Fig.~\ref{fig:nu1e2_harmon2} (left figure) we compare this solution to the computed $\Im\left(\hat{E}_y^{\nu}\mathrm{e}^{it}\right)$, for
-fixed values of $t$. Both solutions appear to be in close agreement. 
-\begin{figure}[htb]
- \begin{tabular}{cc}
-\includegraphics[width=0.45\textwidth]{airy/figure_nu1e2_2-crop.pdf}
-&
-\includegraphics[width=0.45\textwidth]{airy/figure_error_nu1e4-crop.pdf}\\
-\end{tabular}
-\caption{In the left figure we show the solution for $\nu=10^{-2}$, for two fixed moment of times. In the right figure 
-the dependence of the error (\ref{eq:error}) on time for $\nu=10^{-4}$ is demonstrated. 
-We can see that the error is decreasing on the given time interval.}
- \label{fig:nu1e2_harmon2}
-\end{figure}
 \FloatBarrier
@@
 for $\nu=10^{-2}$ did not exceed 1.1e-3 for values of $t\in \left(28501,  30000\right)$.
-
-Fig.~\ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=1e-4$. As previously, 
+Fig.~\ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=1e-4$.
+As previously,
 to demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
@@
 One of our observations was that for smaller $\nu$ one requires more time steps to achieve the limiting amplitude solution. 
-For $\nu=10^{-4}$ we were not able to obtain the limiting amplitude solution for $t<3\cdot 10^{4}$, unlike in the case of $\nu=10^{-2}$, 
-see also Fig.~\ref{fig:nu1e2_harmon2}(right). 
+For $\nu=10^{-4}$ we were not able to obtain the limiting amplitude solution for $t<3\cdot 10^{4}$, unlike in the case of $\nu=10^{-2}$. 
 For example, for $\nu=10^{-6}$ we were not able to reach the limiting amplitude solution even on the time interval $t\leq 1.92e6$, 
@@
 
-We compare the results for $\nu=10^{-2},\; 10^{-3},\; 10^{-4}$ in Fig. \ref{fig:resonance_nus_ex_x}, 
-\ref{fig:resonance_nus_ey_x}, \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}, \ref{fig:resonance_nus_eyx_t}. 
+We compare the results for $\nu=10^{-2},\; 10^{-3},\; 10^{-4}$ in Fig. \ref{fig:resonance_nus_ey_x}, 
+\ref{fig:resonance_nus_ex_x}, \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}, \ref{fig:resonance_nus_eyx_t}. 
 %In the time domain, we chose the discretization size $\Delta x=0.025$. 
@@
 $E_x^{\nu}(x_c,t)$ and $E_y^{\nu}(x_c, t)$ for a range of $t$. We compare these solutions to $\Im\left(\hat{E}_x^{\nu}(x_c)\mathrm{e}^{it}\right)$ and 
-$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right)$. In the former case we choose the point $x_c=0$, where the resonance occurs.
+$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right)$.
 
@@
 The right figure shows the dependence of the solution $E_y^{\nu}(x,t)$ for $\nu=10^{-4}$ on time for fixed $x=x_c$. 
-We can see that the while the limiting amplitude principle holds true, the difference between the solutions computed in 
+We can see that the while the limiting amplitude principle holds true, however, the difference between the solutions computed in 
 the time and frequency domain is noticeable on this scale. 
@@
 
-We can see that in the case of the resonance, the solution seem to achieve the limiting amplitude solution, 
-and both solutions are in relatively close agreement (but the point where the resonance occurs). 
-Similarly to the case with the regular case, 
+Figures \ref{fig:resonance_nus_ex_t, fig:resonance_nus_ey_t, fig:resonance_nus_eyx_t} show that in the case of the resonance
+the solution achieves the limiting amplitude solution, and both solutions are in close agreement (but in the points close to a point where the resonance occurs).
+These numerical results show that the staggered scheme resolves the resonance, similarly to the semi-lagrangian scheme described before.  
+Like in the regular case, 
 longer computations are needed to achieve the limiting amplitude solution  

### 2015-02-03 report/numerics.tex
almost final version

@@
         width=0.4\textwidth,
+        xmin=2e-6,
+        ymin=1e-8,
+        xmax=2,
         legend style={
@@
 }
-]\addplot[mark=*,blue] table {pics/E1L2.dat}; 
+]\addplot[mark=*,black] table {pics/E1L2.dat}; 
     \addlegendentry{$\|E_{x}-E_{x}^{c}\|_{L_{2}}$};
-    \addplot[mark=*,red] table {pics/E2H1.dat};
+    \addplot[mark=*,red, mark size=1pt] table {pics/E2H1.dat};
         \addlegendentry{$\|E_{y}-E_{y}^{c}\|_{H_{1}}$};
 
-          \addplot[mark=*,cyan] table {pics/E2L2.dat};
+          \addplot[mark=*,cyan, mark size=1pt] table {pics/E2L2.dat};
         \addlegendentry{$\|E_{y}-E_{y}^{c}\|_{L_{2}}$};  
@@
 \begin{tabular}{cc}
-\begin{tikzpicture}
-    \begin{loglogaxis}[
-    	width=0.4\textwidth,
-    	height=0.4\textwidth,
-        xlabel=$\nu$,
-        ylabel=$h_{\epsilon}$,
-        ymax=5e3,
-        xmin=0.5e-4,
-        xmax=0.3,
-        legend style={
-at={(0.2,1.5)},
-legend pos=north west,
-font=\tiny, 
-draw=none
-}
-]
-\addplot[mark=*,blue] table {pics/h1e-1.dat}; 
-\addlegendentry{$\epsilon=1e-1$};
-%\addplot[mark=o,red] table {pics/h1e-2.dat}; 
-%\addlegendentry{$\epsilon=1e-2$};
-\addplot[mark=triangle,green] table {pics/h1e-3.dat}; 
-\addlegendentry{$\epsilon=1e-3$};
-%\addplot[mark=square,cyan] table {pics/h1e-4.dat}; 
-%\addlegendentry{$\epsilon=1e-4$};
-\addplot[dashed, red] table {pics/nu32.dat}; 
-\addlegendentry{$O\left(\nu^{\frac{3}{2}}\right)$};
-\addplot[dashed, blue] table {pics/nu54.dat}; 
-\addlegendentry{$O\left(\nu^{\frac{5}{4}}\right)$};
-\addplot[dashed, green] table {pics/nu1.dat}; 
-\addlegendentry{$O\left(\nu\right)$};
-\end{loglogaxis}
-\end{tikzpicture} 
+\includegraphics[height=0.35\textwidth]{h_nu.pdf}
 &
-\includegraphics[height=0.3\textwidth]{figure1-crop.pdf}
+\includegraphics[height=0.35\textwidth]{figure1-crop.pdf}
 \end{tabular}
@@
 \begin{remark}
- We can show that 
-\bealn
- \|E^{\nu}_{x}\|_{L_{2}(\Omega)}\leq \frac{C}{\sqrt{\nu}},\; C>0, 
-\eealn
+ We can show that $\|E^{\nu}_{x}\|_{L_{2}(\Omega)}\leq \frac{C}{\sqrt{\nu}},\; C>0$, 
 and thus the relative error control
@@
 \paragraph{Condition Number}
-In Figure \ref{tab:cond_number} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
+In Figure \ref{fig:small_nu} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
 on $\nu$, for several values of $h$.
 \begin{figure}
-
-\end{figure}
-
-\begin{table}[ht!]
-\begin{tabular}{c|ccccccccc}
-\diagbox[width=10em]{$h$}{$\nu$}& 100 & 10 & 1 & 0.1 & 1e-2 & 1e-3 & 1e-4 & 1e-8 & 0\\
- \hline
-1 & 3.9634&4.3787 &4.987&36.949&42.394& 42.757 &42.79&42.793&42.793\\
-\hline
-0.5&      3.9931& 6.87&48.473 & 168.41  &207.34  & 209.63 & 209.83 & 209.85&  209.85\\
-\hline
- 0.1&      16.09  &     159.56  &     1146.1   &    8304.1   &     19169  &      20270   &     20344   &     20352   &     20352\\
- \hline
-0.05&      64.046  &     637.18  &     4686.2   &     38876 &  1.4e5 &  1.58e5 &   1.58e5 &  1.58e5 &  1.58e5\\
-\hline
- 0.01&       1600    &   15921 & 1.2e5  & 1.1e6 & 8.3e6  & 1.8e7   & 1.93e7  & 1.93e7  & 1.93e7\\
+\begin{tabular}{cc}
+\includegraphics[height=0.3\textwidth]{fig_cond_num.pdf}&
+ \includegraphics[height=0.3\textwidth]{figure2-crop.pdf}
  \end{tabular}
-\caption{The condition number of the matrix of the system (\ref{eq:simple_system}) for different values of $\nu$ and $h$. }
-\label{tab:cond_number}
-\end{table}
-Remarkably, for $\nu=0$ the computed matrices are not singular. We do not know the exact reason for this.
-As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Fig.~\ref{fig:small_nu}. 
-\begin{figure}
- \includegraphics[width=0.4\textwidth]{figure2-crop.pdf}
- \caption{The plot shows $E_{y}^{\nu}$ computed on different meshes for small $\nu$. It can be seen that for meshes that are coarse 
+ \caption{
+ The left plot demonstrates the dependence of the condition number of the system (\ref{eq:simple_system}) on $\nu$, for different values of $h$ (the condition 
+ number for $\nu=0$ is not shown, however, for values of $h$ as shown in the plot, the matrix appears to be non-singular). 
+ The right plot shows $E_{y}^{\nu}$ computed on different meshes for small $\nu$. It can be seen that for meshes that are coarse 
  with respect to $\nu$ (e.g. $\nu=10^{-4}, \; h=10^{-2}$, or $\nu=0,\; h=10^{-2}$), the computed solution seems to be only piecewise-continuous in $\nu$, 
@@
 \end{figure}
+%\begin{table}[ht!]
+%\begin{tabular}{c|ccccccccc}
+%\diagbox[width=10em]{$h$}{$\nu$}& 100 & 10 & 1 & 0.1 & 1e-2 & 1e-3 & 1e-4 & 1e-8 & 0\\
+% \hline
+%1 & 3.9634&4.3787 &4.987&36.949&42.394& 42.757 &42.79&42.793&42.793\\
+%\hline
+%0.5&      3.9931& 6.87&48.473 & 168.41  &207.34  & 209.63 & 209.83 & 209.85&  209.85\\
+%\hline
+% 0.1&      16.09  &     159.56  &     1146.1   &    8304.1   &     19169  &      20270   &     20344   &     20352   &     20352\\
+% \hline
+%0.05&      64.046  &     637.18  &     4686.2   &     38876 &  1.4e5 &  1.58e5 &   1.58e5 &  1.58e5 &  1.58e5\\
+%\hline
+% 0.01&       1600    &   15921 & 1.2e5  & 1.1e6 & 8.3e6  & 1.8e7   & 1.93e7  & 1.93e7  & 1.93e7\\
+%\end{tabular}
+%\caption{The condition number of the matrix of the system (\ref{eq:simple_system}) for different values of $\nu$ and $h$. }
+%\label{tab:cond_number}
+%\end{table}
+Remarkably, for $\nu=0$ the computed matrices are not singular. We do not know the exact reason for this.
+As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Fig.~\ref{fig:small_nu}.
 

### 2015-02-03 report/absorption.tex
almost final version
modified an error

@@
 $H$ & 19\\
-$\omega_c$ &  \mrev{$\sqrt{0.5}$}\\
+$\omega_c$ &  $\sqrt{0.5}$\\
 $N_e(x)$ &  $\left\{
@@
 
-Figures \ref{fig:resonance_nus_ex_t, fig:resonance_nus_ey_t, fig:resonance_nus_eyx_t} show that in the case of the resonance
+Figures \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}, \ref{fig:resonance_nus_eyx_t} show that in the case of the resonance
 the solution achieves the limiting amplitude solution, and both solutions are in close agreement (but in the points close to a point where the resonance occurs).

### 2015-02-04 report_clean/FD.tex
added cleaned report file

\section{Frequency domain study}
In the frequency domain, the velocity can be eliminated and it yields a simpler system under the form
of  Maxwell equations with the cold plasma dielectric tensor \cite{Stix,Despres_2014}. One obtains the equations
\bealn
%\label{eq:main_frequency_domain_1}
\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-
\epsilon(\omega)\hat{\mathbf{E}}=0,\\
\epsilon(\omega)=\left(
\begin{matrix}
 \tilde{\alpha} & i\tilde{\delta} \\
 -i\tilde{\delta}  & \tilde{\alpha}
\end{matrix}
\right),\\
\tilde{\alpha}(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\tilde{\omega}\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)}\right),\qquad 
\tilde{\delta}(\omega)=\frac{\omega_c\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)},
\eealn
where the frequency 
$\tilde{\omega}=\omega+i\nu$ is shifted in the complex plane,
the cyclotron frequency is 
$ \omega_c={\frac{eB_0}{m_e}}$ and the plasma frequency is $ \omega_p^2=\frac{e^2 N_e}{\epsilon_0 m_e}$.
The series expansion as $\nu\rightarrow 0$ gives at leading orders
\bealn
 \tilde{\alpha}(\omega)=\alpha(\omega)+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}\frac{\omega^2}{c^2},\qquad \alpha(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\omega_p^2}{\omega^2-\omega_c^2}\right),\\
 \tilde{\delta}(\omega)=\delta(\omega)-\frac{2i\omega^3\nu}{c^2(\omega^2-\omega_c^2)^2},\qquad \delta(\omega)=\frac{\omega\omega_c\omega_p^2}{c^2(\omega^2-\omega_c^2)}.
\eealn
We finally obtain a simpler equation \cite{Despres_2014} 
%\ben
% \epsilon_{\nu}(\omega)\approx \epsilon_0+i\nu Id,\; \nu\rightarrow 0.
%\een
%Thus, in this work we concentrate on a model
\begin{align}
\label{eq:main_frequency_domain}
\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}
\left(\epsilon_0(\omega)+\nu Id\right)\hat{\mathbf{E}}=0,\\
\label{eq:epsilon_0}
\epsilon_0(\omega)=\left(
\begin{matrix}
 \alpha & i\delta \\
 -i\delta & \alpha 
\end{matrix}
\right).
\end{align}
 In this model problem, the coefficients  $\alpha(\omega)$ and $\delta(\omega)$ are sufficiently smooth, i.e. bounded and continuous in  
$\left[-L,\; \mathbb{R}\right)$.

%%%%%%%%%%%%%%%%%%%%%% 
\subsection{1D case}
%%%%%%%%%%%%%%%%%%%%%% 
\label{sec:wellposedness}

In order to reduce problem \eqref{eq:main_frequency_domain} to one dimension, perform a Fourier transform in the $y$ variable, 
denoting by $\theta$ the corresponding Fourier variable. 
After introducing $\Omega=(-L,\; H)\subset \mathbb R$ and defining the function space of the problem  $\mathbf{V}=L_{2}(\Omega)\times H_{1}(\Omega)$, 
equipped with the norm
\ben
 \|\mathbf{v}\|_{\mathbf{V}}^2= \|v_1\|_{L_{2}(\Omega)}^2+\|v_2\|_{H^{1}(\Omega)}^2,
\een
the resulting one-dimensional system can be rewritten in the following variational form:
\begin{align}
\label{vf1dcase}
\begin{array}{l}
\displaystyle \int_{-L}^H (E_y' -\imath\theta E_x)\overline{(\tilde E_y' -\imath \theta \tilde E_x)} - \int_{-L}^H (\eps_0 +\imath\nu Id) \E \cdot \overline{\tilde \E}
%\\ \displaystyle 
 - \imath \lambda E_y (-L)\overline{ \tilde E_y (-L)} = -g_{inc} (-L) \overline{( \tilde E_y(-L) )},
\end{array}\\
\nonumber
\text{ for all } \tilde{\mathbf{E}}=(\tilde E_x,\tilde E_y)\in \mathbf{V}.
\end{align}
Recall that here $\lambda\geq 0$. 
%=\omega\geq 0$. 
Let us remark that in this and further sections, where it is not ambiguous, we will use the notation $E_{x,y}$ instead of $\hat{E}_{x,y}$ for convenience.

The above can be reformulated as 
\be
a\left(\mathbf{u},\mathbf{v}\right)=l(\mathbf{v}), \; \text{ for all }\mathbf{v}\in \mathbf{V},
\ee
with a bilinear form $a$ and a linear form $l$:
\be
a(\ubf,\vbf) = a_1 (\ubf,\vbf) +\imath a_2(\ubf,\vbf)\  \text{ and } \  l(\vbf) = -g_{inc} (-L) \overline{(v_2(-L) )} 
\ee
where $a_1= a_1^*$ and $a_2=a_2^*$ are hermitian
\be
\left\{\begin{array}{l}
	a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -\imath\theta u_1)\overline{(v_2' -\imath \theta v_1)} - \int_{-L}^H \eps_0 \ubf\cdot \overline{\vbf}, 
	\\ a_2(\ubf,\vbf) = -\nu \int_{-L}^H  \ubf\cdot \overline{\vbf} - \lambda u_2 (-L) \overline{v_2 (-L)} , 
\end{array}\right.
\ee
The unknown is $\ubf=(E_x,E_y)=(u_1,u_2)$ and $\vbf$ is a test function.

Let us denote the spectral radius of $\eps_0$ by $\heps =  \|\rho(\eps_0)\|_{L^\infty}$.
%\end{df}

We now prove the following result.
\mrev{
\begin{lemma}
\label{lemma:well_posedness}
If $\heps<+\infty$, the bilinear form 
\ben
 a(\ubf,\vbf):  \mathbf{V}\times \mathbf{V}\rightarrow \mathbb{C}
\een
is continuous and coercive for all $\nu\neq 0$: for all $\ubf,\vbf\in \mathbf{V}$ it holds that
\bealn
\label{eq:bilinear_cont}
\left\{\begin{array}{l}
\Re\left(\mathrm{e}^{i\alpha_{\nu}}a(\ubf,\ubf)\right)\geq \frac{|\nu|}{\sqrt{(\heps+\theta^2+1)^2+\nu^2}}\left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right),\; 
\text{ for some $\alpha_{\nu}\in\left(-\frac{\pi}{2}, 0\right)\cup \left(0,\frac{\pi}{2}\right)$},\\
|a(\ubf,\vbf)|\leq C \|\ubf\|_{\mathbf{V}}\|\vbf\|_{\mathbf{V}},
\end{array}\right.
\eealn
where $C>0$ does not depend on $\nu$. The problem~\eqref{vf1dcase} is well-posed in $\mathbf{V}$.

\end{lemma}
%\textcolor{red}{!!!! redo coercivity computations !!!}
\begin{proof}
	The boundedness of $a$ is obvious using the continuous embedding in dimension
	one  $H_1(\Omega)\subset C^0(\overline \Omega)$. Let us focus on the proof of coercivity. 
	W.l.o.g. let $\nu>0$. We denote $\heps =  \|\rho(\eps_0)\|_{L^\infty}$, the spectral radius of $\eps_0$ so that
	$\heps Id- \eps_0 $ is a non negative hermitian matrix.
	Therefore
	\be 
	a_1(\ubf,\ubf) + \heps\|\ubf\|^2_{L^2}= \|u_2' - \imath \theta u_1 \|^2_{L^2} + \left( (\heps Id - \eps_0 ) \ubf, \overline{\ubf} \right)  \geq \|u_2 ' - \imath \theta u_1 \|_{L^ 2}^ 2
	\geq \frac12 \|u_2 '  \|_{L^ 2}^ 2 -
	\theta ^2 \| u_1 \|_{L^ 2}^ 2.
	\ee
	Thus one can write
	$
	a_1(\ubf,\ubf)  \geq \frac{1}{2}\|u_2'\|^2_{L^2}-  (\heps  +  \theta^2) \| \ubf \|_{L^2}^2$.
	One also has that
	$
	a_2 (\ubf ,\ubf) \leq -\nu \| \ubf \|_{L^2}^2$. 
	Therefore
	\ben
	a_1(\ubf,\ubf)-\frac{\heps  +  \theta^2 + 1 }\nu a_2(\ubf,\ubf)\geq \frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2,
	\een
	or, introducing $\alpha_{\nu}=\arccos\frac{1}{\sqrt{1+\left(\heps+\theta^2+1\right)^2\nu^{-2}}}$, this is equivalent to 
	\ben
	\Re\left(\mathrm{e}^{i\alpha_{\nu}}a(\ubf,\ubf)\right)\geq 
	\frac{1}{\sqrt{1+\left(\heps+\theta^2+1\right)^2\nu^{-2}}} \left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right)\\
	\geq \frac{\nu}{\sqrt{(\heps+\theta^2+1)^2+\nu^2}}\left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right).
	\een
	The problem \eqref{vf1dcase} is uniquely solvable thanks to Lax-Milgram theorem.
\end{proof}

\begin{remark} 
\label{remark:other}
The above proof is not optimal in the case when $\left|\alpha(x)\right|>c>0$ for $c>0$ on the whole interval $[-L,\; H]$, at least 
for the case $\theta=0$. In this case the problem (\ref{eq:var_form2}) is well-posed for $\nu=0$. More precisely, it can be written 
as a system of two equations, where the first equation (for $E_y$) is the variational formulation for the Helmholtz equation 
with the variable coefficient $k^2=(\alpha-\frac{\delta^2}{\alpha})$, and second equation 
\begin{align*}
  \left(E_x,u\right)=-\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L_{2}(\Omega), 
\end{align*}
uniquely defines $E_x\in L_{2}(\Omega)$. The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
was demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H_{1}(\Omega)$, we can obtain $E_x$ from the second equation.

%%Let us consider the problem (\ref{eq:var_form2}) for $\nu=0,\; \theta=0$, which, after testing it 
%%with $(\tilde{E}_x,\; 0)$ and $(0,\; \tilde{E}_y)$ from $\mathbf{V}$, can be rewritten as, see also (\ref{eq:epsilon_0})
%%\begin{align}
%%\label{eq:full_var}
%%\begin{split}
%%\int_{-L}^H \left(\alpha E_x+i\delta E_y \right)_{1} \overline{\tilde E}_{x}&=0,\; \text{ for all }\tilde{E}_x\in L_{2}(\Omega), \;\\
%%\displaystyle \int_{-L}^H E_y'\tilde {E_y'} - \int_{-L}^H\left( -i\delta E_x+\alpha E_y \right)_{2}\overline{\tilde{E}}_{y}
%%  - \imath \lambda E_y (-L) \overline{\tilde E_y} (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
%%  \text{ for all }  \tilde{E}_{y}\in H_{1}(\Omega).
%%  \end{split}
%%\end{align}
%%The first equation of the above can be rewritten as 
%%\ben
%% \left(E_x,\alpha \tilde{E}_x\right)=-\left(i\delta E_y,  \tilde{E}_x\right).
%%\een
%%If the multiplication operator $M_{\alpha}$ defined as $M_{\alpha}\psi=\frac{1}{\alpha}\psi$ is an isomorphism from $L_{2}([-L,\;H])$ to $L_{2}([-L,\;H])$ (this is true if e.g.
%%$\alpha \in C_{0}([-L,\;H])$ and $|\alpha(x)|>c>0$, for some $c>0$, on the whole interval), this equation is equivalent to 
%%\begin{align}
%%\label{eq:mult_eq}
%%  \left(E_x,u\right)=-\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L_{2}(\Omega). 
%%\end{align}

%%Choosing in the above $u=-i\delta \tilde{E}_y \in L_{2}(\Omega)$ and adding it to the second equation of (\ref{eq:full_var}), we obtain
%%\bealn
%% \displaystyle \int_{-L}^H E_y'\tilde {E_y'} - \int_{-L}^H (\alpha-\frac{\delta^2}{\alpha})E_y \overline{\tilde{E}}_{y}
%%  - \imath \lambda E_y (-L) \overline{\tilde E_y} (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
%%  \text{ for all } \tilde{E}_{y}\in H_{1}(\Omega). \nonumber
%%\eealn
%%Thus we obtain the variational formulation for $E_y$, or the variational formulation for the Helmholtz equation. The well-posedness 
%%of this problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
%%had been demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H_{1}(\Omega)$, we can obtain $E_x$ from the equation (\ref{eq:mult_eq}).
\end{remark}
}

%\subsection{2D case}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%% 
%\textcolor{red}{!!!!!!!!!!!!!!!! TODO : deal with this part !!!!!!!!!!!}
%$curl$ ibp formula
%\be
%\int_\Omega \curl u \cdot \f = \int_\Omega u\ curl \f + \int_\Gamma u (\f \wedge \n)
%\ee
%\be
%\int_\Omega curl \E \cdot \overline{curl \tilde \E} - \int_\Omega \eps \E \cdot \overline{\tilde \E} + \int _\Gamma curl \E \overline{\left( \tilde \E\wedge \n \right)} d\sigma = 0
%\ee
%\be
%\begin{array}{l}
%\displaystyle \int_\Omega curl \E \cdot \overline{curl \tilde \E} - \int_\Omega (\eps_0+i\nu Id) \E \cdot \overline{\tilde \E} - \int _{\{x=-L\}} \imath \sqrt{\alpha(-L)}(\E\wedge \n) \overline{\left( \tilde \E\wedge \n \right)} d\sigma 
%\\ \displaystyle \phantom{ fffffffff}= \int_{\{x=-L\}} g_{inc}  \overline{\left( \tilde \E\wedge \n \right)} d\sigma
%\end{array}\ee
%\textcolor{red}{!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}

%%%%%%%%%%%%%%%%%%%%
\subsection{Discretization of the Frequency Domain Problem}
\label{sec:discr}
Testing the variational formulation (\ref{vf1dcase}) with $(\tilde E_x,0)$ and $(0,\; \tilde{E}_y)\in\mathbf{V}(\Omega)$ and using 
an explicit expression for the tensor of the dielectric permittivity (\ref{eq:epsilon_0}), we can rewrite it as a system of two equations
%\begin{align*}
%\begin{split}
%i\theta \displaystyle \int_{-L}^H (E_y' -\imath\theta E_x)\overline{\tilde E_x} - \int_{-L}^H \left((\epsilon_0 +\imath\nu \operatorname{Id}) \E\right)_{1} \overline{\tilde E}_{x}
%&=0,\\
%\displaystyle \int_{-L}^H (E_y' -\imath\theta E_x)\tilde {E_y'} - \int_{-L}^H\left( (\epsilon_0 +\imath\nu\operatorname{Id}) \E\right)_{2}\overline{\tilde{E}}_{y}
%  - \imath \lambda E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
%  \text{ for all } \tilde E_x\in L_{2}(\Omega), \; \tilde{E}_{y}\in H_{1}(\Omega).
%  \end{split}
%\end{align*}
%Using the explicit expression for the dielectric permittivity tensor in the above, it yields:

\begin{align}
\label{eq:var_form2}
\begin{split}
 i\theta \displaystyle \int_{-L}^H (E_y' -\imath\theta E_x)\overline{\tilde E_x} - 
 \int_{-L}^H \left((\alpha+i\nu)E_x+\imath\delta E_y\right)_{1} \overline{\tilde E}_{x}
&=0,\\
\int_{-L}^H (E_y' -\imath\theta E_x)\tilde {E_y'} -
\int_{-L}^H\left( -\imath \delta E_x+(\alpha+i\nu) E_y\right)_{2}\overline{\tilde{E}}_{y}
  - \imath \lambda E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
 \text{ for all } \tilde E_x\in L_{2}(\Omega), \; \tilde{E}_{y}\in H_{1}(\Omega).
  \end{split}
\end{align}
Let us introduce two basis function spaces $V_{E_x}=\{\psi_{j}\}_{j=1}^{N_{1}}$ and $V_{E_{y}}=\{\phi_{i}\}_{i=1}^{N_{2}}$. 
%We look for the solution of the problem (\ref{eq:var_form2}) in the form:
We discretize problem (\ref{eq:var_form2}) as:
\ben
E_x=\sum\limits_{k=1}^{N_{1}}e_{xk}\psi_{k},\qquad E_{y}=\sum\limits_{k=1}^{N_{2}}e_{yk}\phi_{k}.
\een

% Substituting $\tilde{E}_{x}=\psi_{m}, \; m=1,\ldots,N_{1}$ and $\tilde{E}_{y}=0$ into the variational formulation (\ref{}), we obtain:
% \begin{align*}
% i\theta\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}\bar{\psi}_{m}dx+\theta^2\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx\\
% -\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{k}\bar{\psi}_{m}dx-i\sum\limits_{1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\delta(x)\phi_{k}(x)\bar{\psi}_{m}dx=0.
% \end{align*}
% Similarly, for $\tilde{E}_{x}=0$ and $\tilde{E}_{y}=\phi_{\ell},\; \ell=1,\ldots, N_{2}$:
% \begin{align*}
% \sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx-i\theta\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}(x)\bar{\phi}'_{\ell}(x)dx\\
% +i
% \sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\delta(x)\psi_{k}\bar{\phi}_{m}dx-\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\phi_{k}\bar{\phi}_{m}dx\\
% -
% i\lambda\sum\limits_{k=1}^{N_{2}}e_{2k}\phi_{k}(-L)\bar{\phi}_{m}(-L)=-g_{inc}(x)\bar{\phi}_{m}(-L).
% \end{align*}
Introducing the notation
\bealn
\left(K^{\psi,\phi'}\right)_{mk}=\int\limits_{-L}^{H}\bar{\psi}_{m}\phi'_{k}dx,\qquad \left(M^{\psi}\right)_{mk}=\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx, \qquad 
\left(M^{\alpha,\psi}\right)_{mk}=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{m}\bar{\psi}_{k}dx,\\
\left(M^{\delta,\psi,\phi}\right)_{mk}=\int\limits_{-L}^{H}\delta(x)\bar{\psi}_{m}\phi_{k}dx, \qquad 
K_{\ell k}=\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx,\qquad
\left(M^{\alpha,\phi}\right)_{\ell k}=\int\limits_{-L}^{H}(\alpha(x)+i\nu)\bar{\phi}_{\ell}\phi_{k}dx,\\
I_{km}^{\Gamma}=\bar{\phi}_{m}(-L)\phi_{k}(-L), \\
\boldsymbol{e}_{x}=\left(e_{11},\ldots,e_{1 N_{1}}\right)^{T},\; \boldsymbol{e}_{y}=\left(e_{21},\ldots,e_{2 N_{1}}\right)^{T},\\
\boldsymbol{0}_{n} \text{ is an $n$-dimensional zero column vector},
\eealn
we rewrite the system (\ref{eq:var_form2}) in an antisymmetric block form:
\ben
\left(\begin{matrix}
\theta^2 M^{\psi}-M^{\alpha,\psi} & i\theta K^{\psi,\phi'}-i M^{\delta,\psi,\phi} \\
-i\theta (K^{\psi,\phi'})^{*}+i (M^{\delta,\psi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
\end{matrix}\right)
\left(
\begin{matrix}
\boldsymbol{e}_x\\
\boldsymbol{e}_y
\end{matrix}
\right)=-g_{inc}(-L)
\left(
\begin{matrix}
\boldsymbol{0}_{N_{1}}\\
\bar{\phi}_{1}(-L)\\
\bar{\phi}_{2}(-L)\\
\vdots\\
\bar{\phi}_{N_{2}}(-L)
\end{matrix}
\right).
\een
This expression greatly simplifies when choosing $V_{E_x}=V_{E_{y}}=\left(\phi_{m}\right)_{m=1}^{N_{2}}$ and
in the case $\theta=0$. One obtains the matricial structure
\begin{align}
\label{eq:simple_system}
\left(\begin{matrix}
M^{\alpha,\phi} & i M^{\delta,\phi,\phi} \\
i (M^{\delta,\phi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
\end{matrix}\right)
\left(
\begin{matrix}
\boldsymbol{e}_x\\ 
\boldsymbol{e}_y
\end{matrix}
\right)=-g_{inc}(-L)
\left(
\begin{matrix}
\boldsymbol{0}_{N_{1}}\\
\bar{\phi}_{x}(-L)\\
\bar{\phi}_{y}(-L)\\
\vdots\\
\bar{\phi}_{N_{2}}(-L)
\end{matrix}
\right).
\end{align}
In this work we use the above formulation with the Lagrange $P_{1}$ basis elements.

### 2015-02-04 report_clean/absorption.tex
added cleaned report file

--- 2015-02-03 report/absorption.tex
@@
 We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{y}^{\nu},\; \nu=0,$ satisfies 
-the Airy equation, c.f. also Remark \ref{remark:other}.
-
-We set $\omega_c=0$ (thus $\delta(x)=0$), $\omega=1$ (hence $\alpha(x)=1-N_e(x)$), 
+the Airy equation, c.f. also Remark \ref{remark:other}. We set $\omega_c=0$ (thus $\delta(x)=0$), $\omega=1$ (hence $\alpha(x)=1-N_e(x)$), 
 choose the domain as $(-0.5, 10)$ and set the electron density $N_e(x)=1+x$. Importantly, $N_e(x)>0$ on the whole interval.
@@
 \begin{tabular}{cc}
-\includegraphics[height=0.2\textwidth]{airy/figure_nu1e2-crop.pdf} & \includegraphics[height=0.2\textwidth]{airy/figure_nu1e2_2-crop.pdf}
+\includegraphics[height=0.2\textwidth]{pics_time_domain/airy/figure_nu1e2-crop.pdf} & \includegraphics[height=0.2\textwidth]{pics_time_domain/airy/figure_nu1e2_2-crop.pdf}
 \end{tabular}
@@
 \label{eq:error}
-\mathcal{E}_{x,y}(t)=\|\Im\left(\hat{E}_{x,y}^{\nu}\exp(it)\right)-E_{x,y}^{\nu}(t)\|_{L_{2}(-L;H)}.
+\mathcal{E}_{x,y}(t)=\|\Im\left(\hat{E}_{x,y}^{\nu}\mathrm{e}^{it}\right)-E_{x,y}^{\nu}(t)\|_{L_{2}(-L;H)}.
 \end{align}
-for $\nu=10^{-2}$ did not exceed 1.1e-3 for values of $t\in \left(28501,  30000\right)$.
+for $\nu=10^{-2}$ did not exceed $1.1e-3$ for values of $t\in \left(28501,  30000\right)$.
 Fig.~\ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=1e-4$.
 As previously,
-to demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
-inside the domain and plot 
+ we fix a point $x=x_c$ inside the domain and plot 
 the dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time $t$ for a range of $t\gg 1$. 
-The error (\ref{eq:error}) for $\nu=1e-4$ at the time interval $[228000.05,\; 240000.05]$ does not exceed 2.8e-4. 
+The error (\ref{eq:error}) for $\nu=10^{-4}$ at the time interval $[228000.05,\; 240000.05]$ does not exceed 2.8e-4. 
 One of our observations was that for smaller $\nu$ one requires more time steps to achieve the limiting amplitude solution. 
@@
 \begin{tabular}{cc}
- \includegraphics[width=0.45\textwidth]{airy/figure_nu1e4-crop.pdf}&
- \includegraphics[width=0.45\textwidth]{airy/figure_nu1e6-crop.pdf}\\
+ \includegraphics[width=0.45\textwidth]{pics_time_domain/airy/figure_nu1e4-crop.pdf}&
+ \includegraphics[width=0.45\textwidth]{pics_time_domain/airy/figure_nu1e6-crop.pdf}\\
 \end{tabular}
@@
 \end{table}
-Since $\alpha(x)=(1-2N_e(x))$, $\alpha(0)=0$, and clearly, $\delta(0)\neq 0$.
-
-We compare the results for $\nu=10^{-2},\; 10^{-3},\; 10^{-4}$ in Fig. \ref{fig:resonance_nus_ey_x}, 
+Since $\alpha(x)=(1-2N_e(x))$, $\alpha(0)=0$, and clearly, $\delta(0)\neq 0$. We compare the results for $\nu=10^{-2},\; 10^{-3},\; 10^{-4}$ in Fig. \ref{fig:resonance_nus_ey_x}, 
 \ref{fig:resonance_nus_ex_x}, \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}, \ref{fig:resonance_nus_eyx_t}. 
@@
 The harmonic dependence of the solution on time is demonstrated by fixing $x_c$ inside the domain and plotting 
-$E_x^{\nu}(x_c,t)$ and $E_y^{\nu}(x_c, t)$ for a range of $t$. We compare these solutions to $\Im\left(\hat{E}_x^{\nu}(x_c)\mathrm{e}^{it}\right)$ and 
-$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right)$.
-
+$E_x^{\nu}(x_c,t)$ and $E_y^{\nu}(x_c, t)$ for a range of $t$. 
 \begin{figure}
 \begin{tabular}{cc}
-\includegraphics[width=0.5\textwidth]{res/ey_fixed_x-crop.pdf}&
-\includegraphics[width=0.5\textwidth]{res/ey_fixed_x_1e3-crop.pdf}
+\includegraphics[width=0.45\textwidth]{pics_time_domain/res/ey_fixed_x-crop.pdf}&
+\includegraphics[width=0.45\textwidth]{pics_time_domain/res/ey_fixed_x_1e3-crop.pdf}
  \end{tabular}
@@
 \begin{figure}
- \includegraphics[width=0.8\textwidth]{res/ex_fixed_x_nu1e4-crop.pdf}
+ \includegraphics[width=0.8\textwidth]{pics_time_domain/res/ex_fixed_x_nu1e4-crop.pdf}
  \caption{The plot shows the dependence of the solution $E_x^{\nu}(x_c,t),\;\nu=10^{-4}$ on time $t$ for fixed 
@@
 \begin{tabular}{cc}
-\includegraphics[width=0.5\textwidth]{res/ex_fixed_t-crop.pdf}&
-\includegraphics[width=0.5\textwidth]{res/ex_fixed_t_1e3-crop.pdf}
+\includegraphics[width=0.45\textwidth]{pics_time_domain/res/ex_fixed_t-crop.pdf}&
+\includegraphics[width=0.45\textwidth]{pics_time_domain/res/ex_fixed_t_1e3-crop.pdf}
 \end{tabular}
@@
 \begin{figure}
-\includegraphics[width=0.45\textwidth]{res/ey_fixed_t_1e3-crop.pdf}
-\includegraphics[width=0.55\textwidth]{res/ey_fixed_x_nu1e4-crop.pdf}
+\begin{tabular}{cc}
+\includegraphics[width=0.4\textwidth]{pics_time_domain/res/ey_fixed_t_1e3-crop.pdf}&
+\includegraphics[width=0.5\textwidth]{pics_time_domain/res/ey_fixed_x_nu1e4-crop.pdf}
+\end{tabular}
 \caption{The left figure demonstrates the dependence of the solution  
 $E_y^{\nu}(x,y)$ on $x$ for fixed values of $t$. For a chosen value of $\nu$ the solutions computed in the time domain are in close agreement 
-to the solutions computed in the frequency domain (this seem to be only partially 
-true for the computed values $E_x^{\nu}(x,y)$ in this case (which also may be caused by the discretization). 
+to the solutions computed in the frequency domain. This seem to be only partially 
+true for the computed values $E_x^{\nu}(x,t)$ in this case (which may be caused by the discretization). 
 The right figure shows the dependence of the solution $E_y^{\nu}(x,t)$ for $\nu=10^{-4}$ on time for fixed $x=x_c$. 
-We can see that the while the limiting amplitude principle holds true, however, the difference between the solutions computed in 
-the time and frequency domain is noticeable on this scale. 
+We can see that the while the limiting amplitude principle holds true, the difference between the solutions computed in 
+the time and frequency domain is not visible on this scale (c.f. Figure \ref{fig:resonance_nus_eyx_t}). 
 }
@@
 \begin{figure}
-\includegraphics[width=0.95\textwidth]{res/ex_fixed_t_1e4_2-crop.pdf}
+\includegraphics[width=0.9\textwidth]{pics_time_domain/res/ex_fixed_t_1e4_2-crop.pdf}
 \caption{The figures demonstrate the dependence of the solutions 

### 2015-02-04 report_clean/conclusions.tex
added cleaned report file

--- 2015-01-28 report/conclusions.tex
@@
 The piecewise-constant FEM approximates the resonant solution rather well, at least for moderate values of $\nu$, 
-however, the discretization size should be chosen roughly proportional to $\nu^{\frac{3}{2}}$, in order to obtain an accurate discretization.
+however, the discretization size should be chosen roughly proportional to $\nu^{\frac{7}{4}}$, in order to obtain an accurate discretization.
 Indeed, it would be interesting to look at the convergence of the adaptive finite elements for this kind of problems. 
@@
 demonstrated that while the condition number of the FEM matrix grows, the matrix remains always invertible, even for $\nu=0$.
+
+We proposed two different schemes for solving the time-dependent problem. Our numerical experiments demonstrate that both of them capture the singular behaviour of the solutions in the resonant case.
 

### 2015-02-04 report_clean/figure_generator/pics_frequency_domain/res_sol.tex
added cleaned report file

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[frenchb,english]{babel}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
\usepackage{tikz}
\usepackage{caption}
\usepackage{pgfplots}
\usepackage{ulem}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{hyperref}

\usepackage{color}
\newenvironment{remark}[1][Remark]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\definecolor{blue}{rgb}{0.30,0.8,1}
\definecolor{red}{rgb}{1,0.3,0.3}
\usetikzlibrary{positioning,shapes,shadows,arrows}
\begin{document}

\begin{figure}
\pagenumbering{gobble}
\begin{tikzpicture}
    \begin{axis}[
    	width=\textwidth,
    	height=\textwidth,
    	xmin=-15,
    	xmax=10,
        xlabel=$x$,
        ylabel=$E_{x,y}$,
        legend style={
at={(0.2,1.5)},
legend pos= south east,
anchor=south east, 
draw=none, 
font=\small
}
]
\addplot[blue] table {pics_resonance/ime1.0.1.dat}; 
\addlegendentry{$\Im{E_x^{\nu}},\nu=10^{-1}$};
\addplot[red] table {pics_resonance/ime1.0.01.dat}; 
\addlegendentry{$\Im{E_x^{\nu}},\nu=10^{-2}$};
\addplot[black] table {pics_resonance/ime1.0.001.dat}; 
\addlegendentry{$\Im{E_x^{\nu}},\nu=10^{-3}$};
\addplot[blue,dashed] table {pics_resonance/ree2.0.1.dat}; 
\addlegendentry{$\Re{E_y^{\nu}},\nu=10^{-1}$};
\addplot[red,dashed] table {pics_resonance/ree2.0.01.dat}; 
\addlegendentry{$\Im{E_y^{\nu}},\nu=10^{-2}$};
\addplot[black,dashed] table {pics_resonance/ree2.0.001.dat}; 
\addlegendentry{$\Im{E_y^{\nu}},\nu=10^{-3}$};
 \end{axis}
\end{tikzpicture}
\end{figure}

\end{document}

### 2015-02-04 report_clean/figure_generator/pics_time_domain/airy/figure_nu1e2.tex
added cleaned report file

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
\usepackage{tikz}
\usepackage{caption}
\usepackage{pgfplots}
\usepackage{ulem}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\pgfplotsset{compat=1.10}
\usepackage{hyperref}

\begin{document}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)
\clearpage
\thispagestyle{empty}
\begin{figure}
\begin{tikzpicture}
 \begin{axis}[
  width=1.2\textwidth, 
  height=0.5\textwidth,
   xlabel={$t$},
  enlarge x limits=false,
  ymax=0.5,
  xmin=2.97e4,
  xtick={2.97e4,2.98e4,2.99e4,3e4},
  x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
  ylabel={$E_y^{\nu}(x_c,t)$},
  legend style={draw=none, fill=white, font=\tiny}
   ]
 \addplot[color=blue] file{airy/sol_1e2_dt0.05_timedomain.dat};
  \addlegendentry{$E_y^{\nu}(x_c,t),\; x_c=0.45, \; \nu=10^{-2}$};
  \addplot[color=red, mark=*, dashed, mark size=0.6] file{airy/sol_1e2_dt0.05_freqdomain.dat};
  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right),\; x_c=0.45, \; \nu=10^{-2}$};
  \end{axis}
\end{tikzpicture}
\end{figure}
\end{document}

### 2015-02-04 report_clean/figure_generator/pics_time_domain/airy/figure_nu1e2_2.tex
added cleaned report file

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
\usepackage{tikz}
\usepackage{caption}
\usepackage{pgfplots}
\usepackage{ulem}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\pgfplotsset{compat=1.10}
\usepackage{hyperref}

\begin{document}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)
\clearpage
\thispagestyle{empty}
\begin{figure}
\begin{tikzpicture}
 \begin{axis}[
  width=\textwidth, 
  height=0.5\textwidth,
  xlabel={$x$},
  enlarge x limits=false,
  x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
  ylabel={$E_y^{\nu}(x,t_c)$},
  legend style={draw=none, fill=white, font=\small}
   ]
 \addplot[color=blue, line width=1] file{airy/td_nu_0.01_dt0.05_t28525.dat};
  \addlegendentry{$E_y^{\nu}(x,t_c),\; t_c=28525, \; \nu=10^{-2}$};
  \addplot[color=red, mark=*, dashed, mark size=0.6] file{airy/fd_nu_0.01_dt0.05_t28525.dat};
  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x)\mathrm{e}^{it_c}\right),\; t_c=28525, \; \nu=10^{-2}$};
  \addplot[color=blue, dashed] file{airy/sol_1e2_dt0.05_td_t_28509.9.dat};
  \addlegendentry{$E_y^{\nu}(x,t_c),\; t_c=28509.9, \; \nu=10^{-2}$};
  \addplot[color=red] file{airy/sol_1e2_dt0.05_fd_t_28509.9.dat};
  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x)\mathrm{e}^{it_c}\right),\; t_c=28509.9, \; \nu=10^{-2}$};
  \end{axis}
\end{tikzpicture}
\end{figure}
\end{document}

### 2015-02-04 report_clean/figure_generator/pics_time_domain/airy/figure_nu1e4.tex
added cleaned report file

--- 2015-02-04 report_clean/figure_generator/pics_time_domain/airy/figure_nu1e2_2.tex
@@
  \begin{axis}[
-  width=\textwidth, 
+  width=1.2\textwidth, 
   height=0.5\textwidth,
-  xlabel={$x$},
+   xlabel={$t$},
   enlarge x limits=false,
+  ymax=0.4,
+  xtick={2.3976e5,2.3982e5,2.3988e5,2.3994e5, 2.39999e5},
   x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
-  ylabel={$E_y^{\nu}(x,t_c)$},
-  legend style={draw=none, fill=white, font=\small}
+  ylabel={$E_y^{\nu}(x_c,t)$},
+  legend style={draw=none, fill=white, font=\tiny}
    ]
- \addplot[color=blue, line width=1] file{airy/td_nu_0.01_dt0.05_t28525.dat};
-  \addlegendentry{$E_y^{\nu}(x,t_c),\; t_c=28525, \; \nu=10^{-2}$};
-  \addplot[color=red, mark=*, dashed, mark size=0.6] file{airy/fd_nu_0.01_dt0.05_t28525.dat};
-  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x)\mathrm{e}^{it_c}\right),\; t_c=28525, \; \nu=10^{-2}$};
-  \addplot[color=blue, dashed] file{airy/sol_1e2_dt0.05_td_t_28509.9.dat};
-  \addlegendentry{$E_y^{\nu}(x,t_c),\; t_c=28509.9, \; \nu=10^{-2}$};
-  \addplot[color=red] file{airy/sol_1e2_dt0.05_fd_t_28509.9.dat};
-  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x)\mathrm{e}^{it_c}\right),\; t_c=28509.9, \; \nu=10^{-2}$};
+ \addplot[color=blue] file{airy/td_x_0.45_nu0.0001.dat};
+  \addlegendentry{$E_y^{\nu}(x_c,t),\; x_c=0.45, \; \nu=10^{-4}$};
+  \addplot[color=red, mark=*, dashed, mark size=0.6] file{airy/fd_x_0.45_nu0.0001.dat};
+  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right),\; x_c=0.45, \; \nu=10^{-4}$};
   \end{axis}

### 2015-02-04 report_clean/figure_generator/pics_time_domain/airy/figure_nu1e6.tex
added cleaned report file

--- 2015-02-04 report_clean/figure_generator/pics_time_domain/airy/figure_nu1e4.tex
@@
   enlarge x limits=false,
-  ymax=0.4,
-  xtick={2.3976e5,2.3982e5,2.3988e5,2.3994e5, 2.39999e5},
+  ymax=0.6,
+  xtick={1.9198e6, 1.91999e6},
   x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
   ylabel={$E_y^{\nu}(x_c,t)$},
-  legend style={draw=none, fill=white, font=\tiny}
+  legend style={draw=none, fill=white, font=\small}
    ]
- \addplot[color=blue] file{airy/td_x_0.45_nu0.0001.dat};
-  \addlegendentry{$E_y^{\nu}(x_c,t),\; x_c=0.45, \; \nu=10^{-4}$};
-  \addplot[color=red, mark=*, dashed, mark size=0.6] file{airy/fd_x_0.45_nu0.0001.dat};
-  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right),\; x_c=0.45, \; \nu=10^{-4}$};
+ \addplot[color=blue] file{airy/td_nu_1e6_unachived.dat};
+  \addlegendentry{$E_y^{\nu}(x_c,t),\; x_c=0.45, \; \nu=10^{-6}$};
   \end{axis}

### 2015-02-04 report_clean/figure_generator/pics_time_domain/res/ex_fixed_t.tex
added cleaned report file

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
\usepackage{tikz}
\usepackage{caption}
\usepackage{pgfplots}
\usepackage{ulem}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\pgfplotsset{compat=1.10}
\usepackage{hyperref}

\begin{document}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)
\clearpage
\thispagestyle{empty}
\begin{figure}
\begin{tabular}{c}
\begin{tikzpicture}
 \begin{axis}[
  width=\textwidth, 
  height=0.5\textwidth,
  xlabel={$x$},
  enlarge x limits=false,
  x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
  ylabel={$E_x^{\nu}(x,t_c)$},
  legend style={draw=none, fill=white, font=\small}
   ]
     \addplot[color=red, dashed] file{nu_1e2/E1_fd_t_29765.dat};
  \addlegendentry{$\Im\left(\hat{E}_x^{\nu}(x)\mathrm{e}^{it_c}\right),\; t_c=29765, \; \nu=10^{-2}$};
 \addplot[color=blue] file{nu_1e2/E1_td_t_29765.dat};
  \addlegendentry{$E_x^{\nu}(x,t_c),\; t_c=29765, \; \nu=10^{-2}$};
  \end{axis}
\end{tikzpicture}\\
\begin{tikzpicture}
 \begin{axis}[
  width=\textwidth, 
  height=0.5\textwidth,
  xlabel={$x$},
  enlarge x limits=false,
  x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
  ylabel={$E_x^{\nu}(x,t_c)$},
  legend style={draw=none, fill=white, font=\small}, 
  legend pos=south east
   ]
 \addplot[color=red, dashed] file{nu_1e2/E1_fd_t_29800.dat};
 \addlegendentry{$\Im\left(\hat{E}_x^{\nu}(x)\mathrm{e}^{it_c}\right),\; t_c=29800, \; \nu=10^{-2}$};

 \addplot[color=blue] file{nu_1e2/E1_td_t_29800.dat};
 \addlegendentry{$E_x^{\nu}(x,t_c),\; t_c=29800, \; \nu=10^{-2}$};
  \end{axis}
\end{tikzpicture}
\end{tabular}
\end{figure}
\end{document}

### 2015-02-04 report_clean/figure_generator/pics_time_domain/res/ex_fixed_t_1e3.tex
added cleaned report file

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
\usepackage{tikz}
\usepackage{caption}
\usepackage{pgfplots}
\usepackage{ulem}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\pgfplotsset{compat=1.10}
\usepackage{hyperref}

\begin{document}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)
\clearpage
\thispagestyle{empty}
\begin{figure}
\begin{tabular}{c}
\begin{tikzpicture}
 \begin{axis}[
  width=\textwidth, 
  height=0.5\textwidth,
  xlabel={$x$},
  ymax=0.6,
  enlarge x limits=false,
  x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
  ylabel={$E_x^{\nu}(x,t_c)$},
  legend style={draw=none, fill=white, font=\small}
   ]
     \addplot[color=red, dashed] file{nu1e3/Ex_nu1e3_t_29765_FD.dat};
  \addlegendentry{$\Im\left(\hat{E}_x^{\nu}(x)\mathrm{e}^{it_c}\right),\; t_c=29765, \; \nu=10^{-3}$};
 \addplot[color=blue] file{nu1e3/Ex_nu1e3_t_29765_TD.dat};
  \addlegendentry{$E_x^{\nu}(x,t_c),\; t_c=29765, \; \nu=10^{-3}$};
\end{axis}
\end{tikzpicture}
\\
\begin{tikzpicture}
 \begin{axis}[
  width=\textwidth, 
  height=0.5\textwidth,
  xlabel={$x$},
  ymax=0.6,
  ymin=-2,
  enlarge x limits=false,
  x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
  ylabel={$E_x^{\nu}(x,t_c)$},
  legend style={draw=none, fill=white, font=\small}, 
  legend pos=south east
   ]
  \addplot[color=red, dashed] file{nu1e3/Ex_nu1e3_t_29800_FD.dat};
  \addlegendentry{$\Im\left(\hat{E}_x^{\nu}(x)\mathrm{e}^{it_c}\right),\; t_c=29800, \; \nu=10^{-3}$};

  \addplot[color=blue] file{nu1e3/Ex_nu1e3_t_29800_TD.dat};
  \addlegendentry{$E_x^{\nu}(x,t_c),\; t_c=29800, \; \nu=10^{-3}$};
  \end{axis}
\end{tikzpicture}
\end{tabular}
\end{figure}
\end{document}

### 2015-02-04 report_clean/figure_generator/pics_time_domain/res/ex_fixed_t_1e4.tex
added cleaned report file

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
\usepackage{tikz}
\usepackage{caption}
\usepackage{pgfplots}
\usepackage{ulem}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\pgfplotsset{compat=1.10}
\usepackage{hyperref}
\usepackage{lscape}
\begin{document}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)
\clearpage
\thispagestyle{empty}
\begin{landscape}
\begin{figure}
\begin{tabular}{ll}
\begin{tikzpicture}
 \begin{axis}[
  width=0.9\textwidth, 
  %height=0.5\textwidth,
  xlabel={$x$},
  enlarge x limits=false,
  x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
  ylabel={$E_y^{\nu}(x,t_c)$},
 % ymin=-0.1,
  %ymax=2,
  legend style={draw=none, fill=white, font=\small}, 
    legend pos=north east
   ]
    \addplot[color=blue] file{nu_1e4/e2_td_t_119000.dat};
  \addlegendentry{$E_y^{\nu}(x,t_c),\; t_c=119000, \; \nu=10^{-4}$};
     \addplot[color=green, dashed, each nth point=10] file{nu_1e4/e2_fd_t_119000.dat};
  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x)\mathrm{e}^{it_c}\right)\; t_c=119000, \; \nu=10^{-4}$};
    \addplot[color=red,each nth point=10] file{nu_1e4/e2_fd_t_120000.dat};
 \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x)\mathrm{e}^{it_c}\right),\; t_c=120000, \; \nu=10^{-4}$};
   \addplot[color=black,dashed] file{nu_1e4/e2_td_t_120000.dat};
 \addlegendentry{$E_y^{\nu}(x,t_c),\; t_c=120000, \; \nu=10^{-4}$};
  \end{axis}
\end{tikzpicture}&
\begin{tikzpicture}
 \begin{axis}[
  width=0.9\textwidth, 
  %height=0.5\textwidth,
  xlabel={$x$},
  enlarge x limits=false,
  x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
  ylabel={$E_x^{\nu}(x,t_c)$},
  ymax=1,
  ymin=-1,
  legend style={draw=none, fill=white, font=\small}
   ]
  \addplot[color=blue] file{nu_1e4/e1_td_t_120000.dat};
 \addlegendentry{$E_x^{\nu}(x,t_c),\; t_c=120000, \; \nu=10^{-4}$};
  \addplot[color=red, dashed] file{nu_1e4/e1_fd_t_120000.dat};
 \addlegendentry{$\Im\left(\hat{E}_x^{\nu}(x)\mathrm{e}^{it_c}\right),\; t_c=120000, \; \nu=10^{-4}$};
  \end{axis}
\end{tikzpicture}
\end{tabular}
\end{figure}
\end{landscape}
\end{document}

### 2015-02-04 report_clean/figure_generator/pics_time_domain/res/ex_fixed_x_nu1e4.tex
added cleaned report file

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
\usepackage{tikz}
\usepackage{caption}
\usepackage{pgfplots}
\usepackage{ulem}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\pgfplotsset{compat=1.10}
\usepackage{hyperref}

\begin{document}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)
\clearpage
\thispagestyle{empty}
\begin{figure}
\begin{tikzpicture}
 \begin{axis}[
  width=1.2\textwidth, 
  height=0.5\textwidth,
   xlabel={$t$},
  enlarge x limits=false,
  ymax=2,
  xmin=1.1988e5,
  xtick={1.1988e5,1.1994e5,1.1999e5},
  x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
  ylabel={$E_x^{\nu}(x_c,t)$},
  legend style={draw=none, fill=white, font=\tiny}, 
  legend columns=2
   ]

   \addplot[color=blue,each nth point=10] file{nu_1e4/e1_td_point0.125.dat};
  \addlegendentry{$E_x^{\nu}(x_c,t),\; x_c=0.0125, \; \nu=10^{-4}$};
    \addplot[color=red, dashed, each nth point=10] file{nu_1e4/e1_fd_point0.125.dat};
  \addlegendentry{$\Im\left(\hat{E}_x^{\nu}(x_c)\mathrm{e}^{it}\right),\; x_c=0.0125, \; \nu=10^{-4}$};

   \addplot[color=green,each nth point=10] file{nu_1e4/e1_td_point2.5.dat};
  \addlegendentry{$E_x^{\nu}(x_c,t),\; x_c=-2.5, \; \nu=10^{-4}$};
      \addplot[color=black, dashed, each nth point=10] file{nu_1e4/e1_fd_point2.5.dat};
  \addlegendentry{$\Im\left(\hat{E}_x^{\nu}(x_c)\mathrm{e}^{it}\right),\; x_c=-2.5, \; \nu=10^{-4}$};
  \end{axis}
\end{tikzpicture}
\end{figure}
\end{document}

### 2015-02-04 report_clean/figure_generator/pics_time_domain/res/ey_fixed_t_1e3.tex
added cleaned report file

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
\usepackage{tikz}
\usepackage{caption}
\usepackage{pgfplots}
\usepackage{ulem}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\pgfplotsset{compat=1.10}
\usepackage{hyperref}

\begin{document}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)
\clearpage
\thispagestyle{empty}
\begin{figure}
\begin{tikzpicture}
 \begin{axis}[
  width=\textwidth, 
  height=0.5\textwidth,
  xlabel={$x$},
  ymax=0.6,
  enlarge x limits=false,
  x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
  ylabel={$E_y^{\nu}(x,t_c)$},
  legend style={draw=none, fill=white, font=\small}
   ]

 \addplot[color=blue] file{nu1e3/Ey_nu1e3_t_29765_TD.dat};
  \addlegendentry{$E_y^{\nu}(x,t_c),\; t_c=29765, \; \nu=10^{-3}$};
     \addplot[color=green, dashed, each nth point=2] file{nu1e3/Ey_nu1e3_t_29765_FD.dat};
  \addlegendentry{$\Im\left({\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}}\right),\; t_c=29765, \; \nu=10^{-3}$};
  \addplot[color=red, each nth point=2] file{nu1e3/Ey_nu1e3_t_29800_FD.dat};
  \addlegendentry{$\Im\left({\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}}\right),\; t_c=29800, \; \nu=10^{-3}$};

  \addplot[color=black, dashed] file{nu1e3/Ey_nu1e3_t_29800_TD.dat};
  \addlegendentry{$E_y^{\nu}(x,t_c),\; t_c=29800, \; \nu=10^{-3}$};
  \end{axis}
\end{tikzpicture}
\end{figure}
\end{document}

### 2015-02-04 report_clean/figure_generator/pics_time_domain/res/ey_fixed_x.tex
added cleaned report file

--- 2015-02-04 report_clean/figure_generator/pics_time_domain/res/ey_fixed_t_1e3.tex
@@
  \begin{axis}[
-  width=\textwidth, 
+  width=1.2\textwidth, 
   height=0.5\textwidth,
-  xlabel={$x$},
+   xlabel={$t$},
+  enlarge x limits=false,
   ymax=0.6,
-  enlarge x limits=false,
+  xmin=2.9955e4,
+  %xtick={2.97e4,2.98e4,2.99e4,3e4},
   x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
-  ylabel={$E_y^{\nu}(x,t_c)$},
-  legend style={draw=none, fill=white, font=\small}
+  ylabel={$E_y^{\nu}(x_c,t)$},
+  legend style={draw=none, fill=white, font=\tiny}
    ]
-
- \addplot[color=blue] file{nu1e3/Ey_nu1e3_t_29765_TD.dat};
-  \addlegendentry{$E_y^{\nu}(x,t_c),\; t_c=29765, \; \nu=10^{-3}$};
-     \addplot[color=green, dashed, each nth point=2] file{nu1e3/Ey_nu1e3_t_29765_FD.dat};
-  \addlegendentry{$\Im\left({\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}}\right),\; t_c=29765, \; \nu=10^{-3}$};
-  \addplot[color=red, each nth point=2] file{nu1e3/Ey_nu1e3_t_29800_FD.dat};
-  \addlegendentry{$\Im\left({\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}}\right),\; t_c=29800, \; \nu=10^{-3}$};
-
-  \addplot[color=black, dashed] file{nu1e3/Ey_nu1e3_t_29800_TD.dat};
-  \addlegendentry{$E_y^{\nu}(x,t_c),\; t_c=29800, \; \nu=10^{-3}$};
+ \addplot[color=blue] file{nu_1e2/E2_td_nu0.01_x_2.5125.dat};
+  \addlegendentry{$E_y^{\nu}(x_c,t),\; x_c=-2.5125, \; \nu=10^{-2}$};
+  \addplot[color=red, dashed] file{nu_1e2/E2_fd_nu0.01_x_2.5125.dat};
+  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right),\; x_c=-2.5125, \; \nu=10^{-2}$};
   \end{axis}

### 2015-02-04 report_clean/figure_generator/pics_time_domain/res/ey_fixed_x_1e3.tex
added cleaned report file

--- 2015-02-04 report_clean/figure_generator/pics_time_domain/res/ey_fixed_x.tex
@@
   enlarge x limits=false,
-  ymax=0.6,
+  ymax=0.5,
   xmin=2.9955e4,
@@
    ]
- \addplot[color=blue] file{nu_1e2/E2_td_nu0.01_x_2.5125.dat};
-  \addlegendentry{$E_y^{\nu}(x_c,t),\; x_c=-2.5125, \; \nu=10^{-2}$};
-  \addplot[color=red, dashed] file{nu_1e2/E2_fd_nu0.01_x_2.5125.dat};
-  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right),\; x_c=-2.5125, \; \nu=10^{-2}$};
+      \addplot[color=blue] file{nu1e3/Ey_nu1e3_x2.5125TD.dat};
+  \addlegendentry{$E_y^{\nu}(x_c,t),\; x_c=-2.5125, \; \nu=10^{-3}$};
+  \addplot[color=red, dashed] file{nu1e3/Ey_nu1e3_x2.5125FD.dat};
+  \addlegendentry{$\Im\left({\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}}\right),\; x_c=-2.5125, \; \nu=10^{-3}$};
+
   \end{axis}

### 2015-02-04 report_clean/figure_generator/pics_time_domain/res/ey_fixed_x_nu1e4.tex
added cleaned report file

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
\usepackage{tikz}
\usepackage{caption}
\usepackage{pgfplots}
\usepackage{ulem}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\pgfplotsset{compat=1.10}
\usepackage{hyperref}

\begin{document}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)
\clearpage
\thispagestyle{empty}
\begin{figure}
\begin{tikzpicture}
 \begin{axis}[
  width=1.2\textwidth, 
  height=0.5\textwidth,
   xlabel={$t$},
  enlarge x limits=false,
  ymax=0.5,
  xmin=1.1988e5,
  xtick={1.1988e5,1.1994e5,1.1999e5},
  x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
  ylabel={$E_y^{\nu}(x_c,t)$},
  legend style={draw=none, fill=white, font=\tiny}, 
  legend columns=2
   ]
   \addplot[color=blue,each nth point=10] file{nu_1e4/e2_point1.25625.dat};
  \addlegendentry{$E_y^{\nu}(x_c,t),\; x_c=1.25625, \; \nu=10^{-4}$};
    \addplot[color=red, dashed, each nth point=10] file{nu_1e4/e2_fd_point1.25625.dat};
  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right),\; x_c=1.25625, \; \nu=10^{-4}$};

   \addplot[color=green,each nth point=10] file{nu_1e4/e2_point2.5125.dat};
  \addlegendentry{$E_y^{\nu}(x_c,t),\; x_c=-2.50625, \; \nu=10^{-4}$};
      \addplot[color=black, dashed, each nth point=10] file{nu_1e4/e2_fd_point2.5125.dat};
  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right),\; x_c=-2.50625, \; \nu=10^{-4}$};
  \end{axis}
\end{tikzpicture}
\end{figure}
\end{document}

### 2015-02-04 report_clean/intro.tex
added cleaned report file

--- 2015-02-02 report/intro.tex
@@
 \end{equation}
-posed in $[-L,\; \infty)\times \mathbb{R}$, for some $L>0$. This domain represents the physical case of a wave sent from a wall facing a plasma. 
+posed in $(-L,\; \infty)\times \mathbb{R}$, for some $L>0$. This domain represents the physical case of a wave sent from a wall facing a plasma. 
 The energy of this system for $\nu=0$ in a domain $\Omega\in\mathbb R^2$ can be expressed as \cite{stable_yee_plasma_current}
@@
 In  \cite{Despres_2014} it was shown
-that the time harmonic electric field component $E_x$ in this case is no longer square 
+that the time harmonic electric field component $E_x$ in this case is not necessarily square 
 integrable, and  
@@
 see Figure \ref{fig:limits}. 
-Even it is true for standard linear wave problems, it is not clear that it still hold in our case due the singularity
+Even though it is true for standard linear wave problems, it is not clear that it still hold in our case due the singularity
 of the hybrid resonance.
@@
      };
- \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow\infty$} (m-2-1);
+ \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow+\infty$} (m-2-1);
   \path[-stealth, font=\scriptsize]   (m-1-1) edge node [above] {$\nu\rightarrow 0+$} (m-1-2);
  \path[-stealth, font=\scriptsize]   (m-2-1) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
-  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow \infty$} (m-2-2);
+  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow +\infty$} (m-2-2);
 
-   \path[-stealth] (m-2-1.east) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
-   (m-1-2) edge node [right] {$\nu\rightarrow 0$} (m-2-2);
+  % \path[-stealth] (m-2-1.east) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
+   %(m-1-2) edge node [right] {$\nu\rightarrow 0$} (m-2-2);
 \end{tikzpicture}

### 2015-02-04 report_clean/numerics.tex
added cleaned report file

--- 2015-02-03 report/numerics.tex
@@
 performed with the help of the code written in Octave.  
-We implemented the scheme described in Section \ref{sec:discr} for a simple case of $P_{1}$-space used 
+We implemented the scheme described in Section \ref{sec:discr} for a case of $P_{1}$-space used 
 for the approximation of $E_{x}$ and $E_{y}$ and $\theta=0$, thus working with the system (\ref{eq:simple_system}). 
@@
 $E_{x}=-i\frac{\delta(x)}{\alpha(x)}Ai(x)$
-is the solution to the problem with parameters (\ref{eq:parameters}) with the boundary condition (\ref{eq:bcs_airy}). 
+is the solution to the problem with parameters (\ref{eq:parameters}) and the boundary condition (\ref{eq:bcs_airy}). 
 The well-posedness of the respective variational formulation for $\nu=0$ is due to Remark \ref{remark:other}.
 
-In Fig.~\ref{fig:conv_rate} we demonstrate the convergence rates for this problem, comparing the solution to the 
-known analytic solution. 
-%with 
-%\ben
-%\|E_{x}-E_{x}^{c}\|_{L_{2}(\Omega)}=\left(\int\limits_{\Omega}\left|E_{x}(x)-\sum\limits_{k=1}^{N}e_{xk}\phi_{k}\right|^2dx\right)^{\frac{1}{2}},
-%\een
-%where $\left(\phi_{i}\right)_{i=1}^{N}$ are $P_{1}$-finite elements and $E_{x}(x)$ is a known analytic solution.
-Similarly $\|E_{y}-E_{y}^{c}\|_{L_{2}(\Omega)}$ and $\|E_{y}-E_{y}^{c}\|_{H_{1}(\Omega)}$ are defined.
-
+In Fig.~\ref{fig:conv_rate} we demonstrate the convergence rates for this problem, comparing the solution with the 
+known analytic solution. Importantly, the obtained convergence rates are in agreement with known estimates of the standard theory of convergence~\cite{brenner}.
 \begin{figure}
@@
         xmax=2,
+	legend cell align=left,
         legend style={
@@
 }
-]\addplot[mark=*,black] table {pics/E1L2.dat}; 
+]\addplot[mark=*,black] table {pics_frequency_domain/data_airy/E1L2.dat}; 
     \addlegendentry{$\|E_{x}-E_{x}^{c}\|_{L_{2}}$};
-    \addplot[mark=*,red, mark size=1pt] table {pics/E2H1.dat};
+    \addplot[mark=*,red, mark size=1pt] table {pics_frequency_domain/data_airy/E2H1.dat};
         \addlegendentry{$\|E_{y}-E_{y}^{c}\|_{H_{1}}$};
 
-          \addplot[mark=*,cyan, mark size=1pt] table {pics/E2L2.dat};
+          \addplot[mark=*,cyan, mark size=1pt] table {pics_frequency_domain/data_airy/E2L2.dat};
         \addlegendentry{$\|E_{y}-E_{y}^{c}\|_{L_{2}}$};  
-        \addplot[dotted] table{pics/E_h2.dat};
+        \addplot[dotted] table{pics_frequency_domain/data_airy/E_h2.dat};
          \addlegendentry{$O(h^2)$};
-         \addplot[dashed] table{pics/H.dat};
+         \addplot[dashed] table{pics_frequency_domain/data_airy/H.dat};
          \addlegendentry{$O(h)$};
@@
 \end{figure}
-
-%Note that in the last 3 numerical experiments the error of the solution of the system of equations, namely $\|Ae-r\|$ (where $e$ is the solution vector, $r$ is the right hand side and $A$ is the block matrix (\ref{eq:simple_system}) ) exceeded 1.6e-9
-%(namely, it was 1.6e-9 ($h=3.2e-5$), 1.3e-08 ($h=8e-6$), 1.04e-07 ($h=2e-6$)).
-
-Importantly, the obtained convergence rates are in agreement with known estimates of the standard theory of convergence~\cite{brenner}.
-
 \subsubsection{Solution of $X$-Mode Problem}
 %\paragraph{Convergence}
-Let us consider the case of the resonance, more precisely, we consider sufficiently smooth
+Let us consider the case of the resonance, more precisely, we choose sufficiently smooth
 $\alpha,\delta$, s.t. $\alpha(0)=0$ and $\delta(0)\neq 0$, and the solvability conditions 
@@
 \end{align}
-given a fixed value of $\epsilon>0$.
+given a fixed value of $\epsilon>0$ and $\nu\rightarrow 0$. W.l.o.g. here we assume that $\nu>0$.
 
-We use the following ingredients (for $\nu\rightarrow 0$):
+We use the following ingredients:
 \begin{itemize}
@@
 \end{align}
-The last inequality follows from Lemma \ref{lemma:well_posedness}.  
+The last inequality follows from Lemma \ref{lemma:well_posedness} and is valid for $\nu\rightarrow 0$.   
 \item The form of the exact solution to the problem (\ref{vf1dcase}):
@@
 \label{eq:exact}
- E_x^{\nu}=-iE_{y}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f(x)}{\alpha(x)+i\nu},
+ E_x^{\nu}=-iE_{y}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f(x)}{\alpha(x)+i\nu}, \; \text{for some }f(x)\in L_{2}(\Omega).
 \end{align}
-for some $f(x)\in L_{2}(\Omega)$. 
 \item The estimate from \cite[Chapter 0]{brenner} on the rate of convergence of the interpolation 
@@
 \eealn
-where $C>0$ does not depend on $\nu$. This, together with the estimates (\ref{eq:cea}) and (\ref{eq:bsc}), results in 
+where $C>0$ does not depend on $\nu$. This, combined with the estimates (\ref{eq:cea}) and (\ref{eq:bsc}), results in 
 \ben
@@
 \een
-Let us assume that $d=2$ is possible by some Aubin-Nitsche lemma for our problem. It follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
+\mrev{Let us assume that $d=2$ is possible by some Aubin-Nitsche lemma for our problem}. It follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
 \begin{align}
@@
 \end{table}
-The results of the experiments for different $\nu$ are shown in Figure \ref{fig:dependence}.
-
 Denoting by $E_{x}^{h}$ the solution $E_{x}(x)$ computed on the mesh with a width $h$, and by $E_{x}^{c}$ the solution computed on a mesh multiple times finer, let 
@@
 \begin{tabular}{cc}
-\includegraphics[height=0.35\textwidth]{h_nu.pdf}
+\includegraphics[height=0.35\textwidth]{pics_frequency_domain/h_nu.pdf}
 &
-\includegraphics[height=0.35\textwidth]{figure1-crop.pdf}
+\includegraphics[height=0.35\textwidth]{pics_frequency_domain/res_sol.pdf}
 \end{tabular}
@@
 \end{figure}
-We can see that the estimate (\ref{eq:estimate_h}) is pessimistic compared to the one suggested by (\ref{eq:def_epsilon}), 
-at least for given values of $\epsilon$ and for a chosen range of $\nu>0$.
+\mrev{We can see that the estimate (\ref{eq:estimate_h}) is pessimistic compared to the one suggested by (\ref{eq:def_epsilon}), 
+at least for given values of $\epsilon$ and for a chosen range of $\nu>0$.}
 
 \begin{remark}
- We can show that $\|E^{\nu}_{x}\|_{L_{2}(\Omega)}\leq \frac{C}{\sqrt{\nu}},\; C>0$, 
+It can be shown that $\|E^{\nu}_{x}\|_{L_{2}(\Omega)}\leq \frac{C}{\sqrt{\nu}},\; C>0$, 
 and thus the relative error control
@@
 \eealn
- can be ensured by choosing $h$ as $\beta_{\epsilon}\nu^{\frac{3}{4}}$.
+ is ensured by choosing $h$ as $\beta_{\epsilon}\nu^{\frac{3}{4}}$.
 \end{remark}
@@
 \begin{tabular}{cc}
-\includegraphics[height=0.3\textwidth]{fig_cond_num.pdf}&
- \includegraphics[height=0.3\textwidth]{figure2-crop.pdf}
+\includegraphics[height=0.3\textwidth]{pics_frequency_domain/fig_cond_num.pdf}&
+ \includegraphics[height=0.3\textwidth]{pics_frequency_domain/ey_resonance.pdf}
  \end{tabular}
@@
  The left plot demonstrates the dependence of the condition number of the system (\ref{eq:simple_system}) on $\nu$, for different values of $h$ (the condition 
- number for $\nu=0$ is not shown, however, for values of $h$ as shown in the plot, the matrix appears to be non-singular). 
+ number for $\nu=0$ is not shown, however, for all values of $h$ as shown in the plot, the matrix was non-singular even for $\nu=0$). 
  The right plot shows $E_{y}^{\nu}$ computed on different meshes for small $\nu$. It can be seen that for meshes that are coarse 
@@
  while for finer meshes and $\nu>0$ the solution seems to be smooth. It can be also seen that for $h=10^{-2}$ and $h=10^{-3}$ the solutions 
- computed for $\nu=0$ are indistinguishable on this scale.}
+ computed for $\nu=0$ are almost indistinguishable.}
  \label{fig:small_nu}
@@
 		\begin{tabular}{ccc}
-			\includegraphics[angle=-90,width=5.cm]{Ey_moit.eps}
+			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/Ey_moit.eps}
 			&
-			\includegraphics[angle=-90,width=5.cm]{Hz_moit.eps} &
-			\includegraphics[angle=-90,width=5.cm]{Ex_moit.eps}
+			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/Hz_moit.eps} &
+			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/Ex_moit.eps}
 			\\
@@
 			\hline
-			\includegraphics[angle=-90,width=5.cm]{uy_moit.eps}
+			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/uy_moit.eps}
 			&
-			\includegraphics[angle=-90,width=5.cm]{normes_moit.eps}
+			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/normes_moit.eps}
 			&
-			\includegraphics[angle=-90,width=5.cm]{ux_moit.eps}
+			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/ux_moit.eps}
 			\\      

### 2015-02-04 report_clean/proc.tex
added cleaned report file

--- 2015-01-29 report/proc.tex
@@
 	the support
-	of ANR under contract ANR-12-BS01-0006-01. Moreover 
+	of ANR under contract ANR-12-BS01-0006-01. Moreover,  
 	this work was carried out within the framework of the European Fusion Development Agreement and 
@@
 %
-\author{C\'eline Caldini-Queiros}\address{Max Planck Institute für PlasmaPhysik, Garching bei Muenchen}
+\author{C\'eline Caldini-Queiros}\address{Max Planck Institute für PlasmaPhysik, Garching bei München, Germany}
 \author{Bruno Despr\'es}\address{Sorbonne Universit\'es, UPMC Univ Paris 06, UMR 7598, Laboratoire Jacques-Louis Lions, F-75005, Paris, France}
 \author{Lise-Marie Imbert-Gérard}\address{Courant Institute of Mathematical Sciences, New York University}
-\author{Maryna Kachanovska}\address{POEMS, INRIA, ENSTA ParisTech, Paris}
+\author{Maryna Kachanovska}\address{POEMS, INRIA, ENSTA ParisTech, Palaiseau, France}
 
@@
 \input{timedomain}
-%\input{freqdomain}
 \input{numerics}

### 2015-02-04 report_clean/timedomain.tex
added cleaned report file

--- 2015-01-29 report/timedomain.tex
@@
 In this section, we develop a discretization of the time dependant problem~\eqref{eq:main_model} 
-in one dimension. In 1D, the derivatives with respect to $y$ vanish, and we are left with the following problem, 
+in one dimension. %In 1D, the derivatives with respect to $y$ vanish, and we are left with the following problem, 
 % \begin{align}
@@
 as suggested in \cite{stable_yee_plasma_current}. Let $n$ denote the time step index, as usual $t_n = n \Delta t$. 
-It is standard (see \cite{Xu_2006,stable_yee_plasma_current }) to discretize the electrical field on the integer time step, 
-whereas the field $H_z$ is on half time steps, $t_{n+1/2}$. The time discretization of the system reads:
+It is standard (see \cite{Xu_2006,stable_yee_plasma_current }) to discretize the electrical field on the integer time steps, 
+whereas the field $H_z$ on half time steps, $t_{n+1/2}$. The time discretization of the system reads:
  \bealn
@@
 We summarize this discretization on Fig.~\ref{schemepos} where the positions 
-of $Ex$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) 
+of $Ex$, $u_x$ (black dots), $E_y$, $u_y$ (blue dots) and $H_z$ (red dots) 
 on the discretized grid in space and time are shown. The fully discretized system then reads
@@
 It  yields the chain 
-$(E_y,H_z)_i^n\mapsto ( w,z)_i^n\mapsto ( w,z)_i^{n*}\mapsto E_y,H_z)_i^{n*} $.
+$(E_y,H_z)_i^n\mapsto ( w,z)_i^n\mapsto ( w,z)_i^{n*}\mapsto (E_y,H_z)_i^{n*} $.
 Here $n*$ denotes the intermediate stage of the algorithm.
@@
 \right.$$
-This is performed locally in every cells starting from the data at the preceding 
+This is performed locally in every cell starting from the data at the preceding 
 step. In our case we just adapt the algorithm developed for the staggered scheme.
-We make sure that the method is conservative in total energy if $\nu=0$, using a half step discretization
+We make sure that the method is conservative in total energy if $\nu=0$, using a half-step discretization
 of the right hand sides.

### 2015-02-04 report_clean/numerics.tex
cosmetic changes

@@
 \begin{tabular}{cc}
-\includegraphics[height=0.3\textwidth]{pics_frequency_domain/fig_cond_num.pdf}&
- \includegraphics[height=0.3\textwidth]{pics_frequency_domain/ey_resonance.pdf}
+\includegraphics[height=0.35\textwidth]{pics_frequency_domain/fig_cond_num.pdf}&
+ \includegraphics[height=0.35\textwidth]{pics_frequency_domain/ey_resonance.pdf}
  \end{tabular}

### 2015-02-04 report_clean/FD.tex
article missing

@@
 as a system of two equations, where the first equation (for $E_y$) is the variational formulation for the Helmholtz equation 
-with the variable coefficient $k^2=(\alpha-\frac{\delta^2}{\alpha})$, and second equation 
+with the variable coefficient $k^2=(\alpha-\frac{\delta^2}{\alpha})$, and the second equation 
 \begin{align*}

### 2015-02-09 report_clean/numerics.tex
bruno's changes

--- 2015-02-04 report_clean/numerics.tex
@@
 of Lemma \ref{lemma:well_posedness}  are satisfied. 
-For simplicity, let us consider 
+For simplicity, let us assume 
 \begin{align}
@@
 The last inequality follows from Lemma \ref{lemma:well_posedness} and is valid for $\nu\rightarrow 0$.   
-\item The form of the exact solution to the problem (\ref{vf1dcase}):
+\item The form of the exact solution to the problem (\ref{vf1dcase}), see \cite{Despres_2014},
 \begin{align}
 \label{eq:exact}
- E_x^{\nu}=-iE_{y}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f(x)}{\alpha(x)+i\nu}, \; \text{for some }f(x)\in L_{2}(\Omega).
+ E_x^{\nu}=-iE_{y}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f^{\nu}(x)}{\alpha(x)+i\nu}, \; \text{for some }f^{\nu}(x)\in L_{2}(\Omega).
 \end{align}
+\mrev{We additionally assume that $E_y^{\nu}(x)$ is sufficiently smooth and $\|(E_y^{\nu})''\|_{H_{2}(\Omega)}$
+can be bounded independently of $\nu$}.
 \item The estimate from \cite[Chapter 0]{brenner} on the rate of convergence of the interpolation 
 \begin{align}
-\label{eq:bsc}
- \|v-I^{h}v\|_{L_{2}(\Omega)}\leq Ch^2\left|v''\right|_{L_{2}(\Omega)},\; C>0,
- %\\ \|v-I^{h}v\|_{H_{1}(\Omega)}\leq Ch|v''|_{L_{2}(\Omega)},\; C>0, 
+\label{eq:interp}
+\begin{split}
+ \|v-I^{h}v\|_{L_{2}(\Omega)}\leq Ch^2\left|v''\right|_{L_{2}(\Omega)},\; C>0,\\
+ \|v-I^{h}v\|_{H_{1}(\Omega)}\leq Ch|v''|_{L_{2}(\Omega)},\; C>0, 
+ \end{split}
 \end{align}
@@
 \end{itemize}
-For $E_x^{\nu},\;f(x)$ in (\ref{eq:exact}) being sufficiently smooth, 
+\mrev{The estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C_1,\;C_2, \; C>0$:
+\begin{align}
+  \label{eq:final_est}
+  \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}%\leq C_1\nu^{-1}h\|\left(E_y^{\nu}\right)''\|_{L_{2}}+C_2\nu^{-1}h^2\|\left(E_x^{\nu}\right)''\|_{L_{2}}
+  \leq C\nu^{-1}h+C\nu^{-1}h^2\|\left(E_x^{\nu}\right)''\|_{L_{2}},
+\end{align}
+where we used an assumption that the $L_2$-norm of $\left(E_y^{\nu}(x)\right)''$ can be bounded independently of $\nu$.} For $E_x^{\nu},\; f^{\nu}(x)$ in (\ref{eq:exact}) being sufficiently smooth, 
 \ben
- \frac{d^2}{dx^2}E_x^{\nu}=\frac{f''}{\alpha+i\nu}-2\frac{f'\alpha'}{(\alpha+i\nu)^2}+\frac{f\alpha''}{(\alpha+i\nu)^3},
+ \frac{d^2}{dx^2}E_x^{\nu}=\frac{(f^{\nu})''}{\alpha+i\nu}-2\frac{(f^{\nu})'\alpha'}{(\alpha+i\nu)^2}+\frac{f^{\nu}\alpha''}{(\alpha+i\nu)^3},
 \een
@@
 \eealn
-where $C>0$ does not depend on $\nu$. This, combined with the estimates (\ref{eq:cea}) and (\ref{eq:bsc}), results in 
+where $C>0$ does not depend on $\nu$. After inserting this into (\ref{eq:final_est}) we obtain
 \ben
- \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}\leq C\nu^{-\frac{7}{2}}h^2,
+ \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}\leq C\nu^{-\frac{7}{2}}h^2+C\nu^{-1}h.
 \een
-\mrev{Let us assume that $d=2$ is possible by some Aubin-Nitsche lemma for our problem}. It follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
+From (\ref{eq:final_est}) it thus follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
 \begin{align}
@@
 To do so, we conduct the  numerical experiment with parameters for the problem as given in Table \ref{tab:parameters}.
-\begin{table}
+\begin{table}[htb!]
 \begin{tabular}{l|l}
@@
 \end{tabular}
-\caption{The parameters for the problem with the resonance}
+\caption{The parameters for the problem with the resonance.}
 \label{tab:parameters}
@@
 \begin{tabular}{cc}
-\includegraphics[height=0.35\textwidth]{pics_frequency_domain/h_nu.pdf}
+\includegraphics[height=0.32\textwidth]{pics_frequency_domain/h_nu.pdf}
 &
-\includegraphics[height=0.35\textwidth]{pics_frequency_domain/res_sol.pdf}
+\includegraphics[height=0.32\textwidth]{pics_frequency_domain/res_sol.pdf}
 \end{tabular}
@@
 \end{figure}
-\mrev{We can see that the estimate (\ref{eq:estimate_h}) is pessimistic compared to the one suggested by (\ref{eq:def_epsilon}), 
-at least for given values of $\epsilon$ and for a chosen range of $\nu>0$.}
-
+We can see that the estimate (\ref{eq:estimate_h}) is pessimistic compared to the one suggested by (\ref{eq:def_epsilon}), 
+at least for given values of $\epsilon$ and for a chosen range of $\nu>0$.
 \begin{remark}
@@
 
-\FloatBarrier
-\paragraph{Condition Number}
-In Figure \ref{fig:small_nu} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
-on $\nu$, for several values of $h$.
-\begin{figure}
+\begin{figure}[htb!]
 \begin{tabular}{cc}
-\includegraphics[height=0.3\textwidth]{pics_frequency_domain/fig_cond_num.pdf}&
- \includegraphics[height=0.3\textwidth]{pics_frequency_domain/ey_resonance.pdf}
+\includegraphics[height=0.32\textwidth]{pics_frequency_domain/fig_cond_num.pdf}&
+ \includegraphics[height=0.32\textwidth]{pics_frequency_domain/ey_resonance.pdf}
  \end{tabular}
@@
 %\end{table}
+\paragraph{Condition Number}
+In Figure \ref{fig:small_nu} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
+on $\nu$, for several values of $h$.
 Remarkably, for $\nu=0$ the computed matrices are not singular. We do not know the exact reason for this.

### 2015-02-09 report_clean/numerics.tex
fixed mistakes

@@
 \end{itemize}
-\mrev{The estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C_1,\;C_2, \; C>0$:
+\mrev{The estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C>0$:
 \begin{align}
@@
 \een
-From (\ref{eq:final_est}) it thus follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
+From this it thus follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
 \begin{align}

### 2015-02-09 report_clean/numerics.tex
mistake
bug

@@
 \end{itemize}
-\mrev{The estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C>0$:
+\mrev{The estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C>0$,
 \begin{align}
@@
 \end{remark}
-
+\paragraph{Condition Number}
+In Figure \ref{fig:small_nu} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
+on $\nu$, for several values of $h$.
+Remarkably, for $\nu=0$ the computed matrices are not singular. We do not know the exact reason for this.
+As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Fig.~\ref{fig:small_nu}. 
 \begin{figure}[htb!]
@@
  number for $\nu=0$ is not shown, however, for all values of $h$ as shown in the plot, the matrix was non-singular even for $\nu=0$). 
- The right plot shows $E_{y}^{\nu}$ computed on different meshes for small $\nu$. It can be seen that for meshes that are coarse 
- with respect to $\nu$ (e.g. $\nu=10^{-4}, \; h=10^{-2}$, or $\nu=0,\; h=10^{-2}$), the computed solution seems to be only piecewise-continuous in $\nu$, 
- while for finer meshes and $\nu>0$ the solution seems to be smooth. It can be also seen that for $h=10^{-2}$ and $h=10^{-3}$ the solutions 
+ The right plot shows $E_{y}^{\nu}$ computed on different meshes for small $\nu$. It can be seen that for $h=10^{-2}$ and $h=10^{-3}$ the solutions 
  computed for $\nu=0$ are almost indistinguishable.}
+ %It can be seen that for meshes that are coarse 
+ %with respect to $\nu$ (e.g. $\nu=10^{-4}, \; h=10^{-2}$, or $\nu=0,\; h=10^{-2}$), the computed solution seems to be only piecewise-continuous in $\nu$, 
+ %while for finer meshes and $\nu>0$ the solution seems to be smooth. }
  \label{fig:small_nu}
@@
 %\end{table}
-\paragraph{Condition Number}
-In Figure \ref{fig:small_nu} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
-on $\nu$, for several values of $h$.
-Remarkably, for $\nu=0$ the computed matrices are not singular. We do not know the exact reason for this.
-As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Fig.~\ref{fig:small_nu}.
 

### 2015-02-10 report_clean/numerics.tex
minor changes

@@
 \end{align}
-\mrev{We additionally assume that $E_y^{\nu}(x)$ is sufficiently smooth and $\|(E_y^{\nu})''\|_{H_{2}(\Omega)}$
-can be bounded independently of $\nu$}.
+We additionally assume that $E_y^{\nu}(x)$ is sufficiently smooth and $\|(E_y^{\nu})''\|_{H_{2}(\Omega)}$
+can be bounded independently of $\nu$. 
 \item The estimate from \cite[Chapter 0]{brenner} on the rate of convergence of the interpolation 
@@
 \end{itemize}
-\mrev{The estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C>0$,
+The estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C>0$,
 \begin{align}
@@
 \end{align}
-where we used an assumption that the $L_2$-norm of $\left(E_y^{\nu}(x)\right)''$ can be bounded independently of $\nu$.} For $E_x^{\nu},\; f^{\nu}(x)$ in (\ref{eq:exact}) being sufficiently smooth, 
+where we used an assumption that the $L_2$-norm of $\left(E_y^{\nu}(x)\right)''$ can be bounded independently of $\nu$.
+
+For $E_x^{\nu},\; f^{\nu}(x)$ in (\ref{eq:exact}) being sufficiently smooth, 
 \ben

### 2015-02-10 report_clean/numerics.tex
numerics.tex: removed Condition number paragraph

--- 2015-02-09 report_clean/numerics.tex
@@
 \end{itemize}
-\mrev{The estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C>0$:
+The estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C>0$,
 \begin{align}
@@
 
+In Figure \ref{fig:small_nu} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
+on $\nu$, for several values of $h$.
+Remarkably, for $\nu=0$ the computed matrices are not singular. We do not know the exact reason for this.
+As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Fig.~\ref{fig:small_nu}. 
 \begin{figure}[htb!]

### 2015-02-10 solve_mH1_interesting.m
added an extra file with interesting rhs....

@@ -1,0 +1,340 @@
+function [e1, e2,M,x, A,B,D]=solve_mH1_interesting(dx,lambda, nu, uniform)
+
+%mesh generation
+L=7; %20!!!
+H=10;%10!!!
+if uniform
+x=-L:dx:H;
+else
+phi=-pi/2:dx:pi/2;
+ x=(H+L)*sin(phi)/2.0+(H-L)./2.0;
+
+
+end
+tic
+[A,B,D]=construct_block_matrix(x,nu,lambda);
+time_passed=toc();
+display (strcat(num2str(time_passed),' for the construction of the matrix'));
+r=construct_rhs(x);
+
+tic
+[M,rhs]=permute(A,B,D,r);
+%save('M.mat', 'M');
+sol=M\rhs;
+
+norm(M*sol-rhs)
+
+[e1, e2]=permute_solution_back(sol);
+
+time_passed=toc();
+display(strcat(num2str(time_passed),' for the solution of the system of eqs'));
+
+
+end
+
+
+function [M,rhs]=permute(A,B,D,rhs_old)
+n1=size(A);
+n2=size(B);
+band=zeros(n1(1)+n2(1), 4);%7-diagonal symmetric system; the 'band' contains the diagonals and subdiagonals
+%column permutation
+%e_new_{j}=e_{1,(j+1)/2} if j is odd
+%e_new_{j}=e_{2,j/2} if j is even
+rhs=zeros(length(rhs_old),1);
+rhs(2)=rhs_old(n1(1)+1);
+%forming the new symmetric matrix, with the row permutation being the same as the column permutation
+%main diagonal
+band(1:2:(end-1),1)=A(:,1);
+band(2:2:end, 1)=D(:,1);
+%subdiagonal
+band(1:2:(end-1),2)=B(:,1);
+band(2:2:(end),2)=B(:,2);
+%subsubiagonal
+band(1:2:(end-1),3)=A(:,2);
+band(2:2:end, 3)=D(:,2);
+%subsubsubdiagonal
+band(1:2:(end-1),4)=B(:,2);
+
+M=spdiags([band(:,4) band(:,3) band(:,2) band(:,1) ...
+  circshift(band(:,2),1) circshift(band(:,3),2) circshift(band(:,4),3)], -3:3, n1(1)+n2(1), n1(1)+n2(1));
+
+
+end
+function [e1, e2]=permute_solution_back(sol)
[…]

### 2015-04-13 report_clean/responce_reviewers.tex
petites changements dans l'intro (General Issues: physics of the problem)+le fichier pour responce_reviewers

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}

%opening
\title{}
\author{}

\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\section{Responce to the reviewer #1}

All the corrections are marked in blue.

\end{document}

### 2015-04-13 report_clean/intro.tex
mistaek
petites changements dans l'intro (General Issues: physics of the problem)+le fichier pour responce_reviewers

@@
 The energy deposit is resonant and may exceed by far the energy 
-exchange which occurs in Landau damping, see \cite{Freidberg_2007,Mouhot_2011}. 
+exchange which occurs in Landau damping, see \cite{Freidberg_2007}. 
 Contrary to the Landau damping, however, 
@@
 
-We consider the model of cold plasma of \cite{Stix} which is described by the 2D time-dependent Maxwell system  
+\urev{
+We consider the wave propagation in the collisionless cold plasma that consists of particles of single species 
+under a uniform in time background magnetic field $\mathbf{B}_0=(0,\;0,\; B_0)$. This process can be described by the 2D time-dependent Maxwell system  \cite{Stix}
 \bealn
--\varepsilon_0 \partial_t \E + \curl\, \Hbf = \J\\
-\mu_0 \partial_t \Hbf + \curl\, \E = 0
+-\varepsilon_0 \partial_t E_x +\partial_y H_z = J_x,\\
+-\varepsilon_0 \partial_t E_y -\partial_x H_z = J_y,\\
+\mu_0 \partial_t H_z + \partial_x E_y-\partial_y E_x= 0
 \eealn
-coupled with a linear electronic current  $\J = eN_e \ubf_e$, 
+coupled with \mrev{an equation for the } linear electronic current  $\J = eN_e(\mathbf{r}) \ubf$, 
 \ben
-m_e \partial_t \ubf_e =e (\E +\ubf_e \wedge B_0) -m_e \nu \ubf_e, \label{eq:electronmove}
+m_e \partial_t u_x =\epsilon_0 e E_x+e B_0(\mathbf{r}) u_y -m_e \nu u_x, \label{eq:electronmove}\\
+m_e \partial_t u_y =\epsilon_0 e E_y-e B_0(\mathbf{r}) u_x -m_e \nu u_y,
 \een
-where $\nu$ is  the friction  between particles.
-The unknowns are the electromagnetic fields $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, 
- %the electronic current $\J$, 
-and the velocity of electrons $\ubf_e$. Here $B_0$ is the background magnetic field, typically assumed to be uniform in time and space.  
-We denote by $e<0$ the value of the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density that in general 
+where \mrev{$\nu>0$} is the friction  between particles, $e<0$ is the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density that in general 
 depends on spatial variables and is uniform in time.
-Without loss of generality, we set $\mathbf{B}_0=\left(0,\; 0,\; B_0\right)$, which allows to obtain the following system of 1D equations 
+The unknowns are the electron velocity $\ubf$ and the electromagnetic field.
+
+The energy of this system in a domain $\Omega\in\mathbb R^2$ in the case $\nu=0$ can be expressed as \cite{stable_yee_plasma_current}
+\ben
+{\mathcal E}(t)= \int_\Omega \left(
+\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|^2}{2|e|N_e(\x)} 
+\right)\mathrm{d}\x.
+\een
+
+To demonstrate the resonance that can occur in the system, we introduce the plasma frequency $w_p(\mathbf{r})=\sqrt{\frac{|e|^2N_e(\mathbf{r})}{m\epsilon_0}}$, 
+the cyclotron frequency $w_c(\mathbf{r})=\frac{e B_0(\mathbf{r})}{m_e}$ and rewrite the system in the frequency domain ($\partial_t\rightarrow iw$) 
+\begin{align*}
+\label{eq:model_freq_domain}
+ \mathbf{curl}{\operatorname{curl}}\mathbf{E}-\frac{w^2}{c^2}\underline{\epsilon}(w,\mathbf{r})\mathbf{E}=0,
+\end{align*}
+where the cold-plasma dielectric tensor \cite[Chapter 1-2]{Stix}
+\begin{align*}
+ \underline{\epsilon}(w,\mathbf{r})=\left(
+ \begin{matrix}
+  \alpha(\mathbf{r}) & i\delta(\mathbf{r})\\
+  -i\delta(\mathbf{r}) & \alpha(\mathbf{r})
+ \end{matrix}
+\right),\; \alpha=1-\frac{w_p^2}{w^2-w_c^2},\; \delta=\frac{w_cw_p^2}{w(w^2-w_c^2)}.
+\end{align*}
+The case $w=w_c$, when $\underline{\epsilon}(w,\mathbf{r})$ is singular, is a so-called cyclotron resonance (c.f. \cite[Chapter 1-5]{Stix}). It can be 
+demonstrated that for this geometry there is no resonant heating associated to these points, see \cite{singular_solutions}, and the solutions are well-defined 
+in the limite $w\rightarrow w_c(\mathbf{r})$. Hence this case is not 
+studied in the present work.
+
+Another interesting case is $w^2=w_p^2+w_c^2$, when the diagonal part of the tensor $\underline{\epsilon}(w,\mathbf{r})$ vanishes. 
+This is a hybrid resonance case. As demonstrated in  \cite{Despres_2014} the time-harmonic electric field component $E_x$ is not necessarily square 
+integrable. This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.
+}
+
+\urev{In some physical applications (e.g. when modelling antennas in plasmas), it is required to study the above system in an 
+infinite domain $(a,\; \infty)\times\mathbb{R}$, $a\in \mathbb{R}$, with appropriately chosen boundary conditions which will be discussed later}.
+\mrev{ADD REFERENCE}
+To simplify the above system, we perform the Fourier transform in $y$ ($\partial_y\rightarrow i\theta$) and consider the one-dimensional setting
+
 \begin{equation}
@@
 posed in $(-L,\; \infty)\times \mathbb{R}$, for some $L>0$. This domain represents the physical case of a wave sent from a wall facing a plasma.
-The energy of this system for $\nu=0$ in a domain $\Omega\in\mathbb R^2$ can be expressed as \cite{stable_yee_plasma_current}
-\ben
-{\mathcal E}(t)= \int_\Omega \left(
-\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|^2}{2|e|N_e(\x)} 
-\right)\mathrm{d}\x.
-\een
-In  \cite{Despres_2014} it was shown
-that the time harmonic electric field component $E_x$ in this case is not necessarily square 
-integrable, and  
-explicit estimates on the behavior of the solutions of \eqref{eq:main_model} in 1D were provided. 
-This apparent paradox  is of course the source of important numerical difficulties which are the subject of the present study.
+
+%In  \cite{Despres_2014} it was shown
+%that the time harmonic electric field component $E_x$ in this case is not necessarily square 
+%integrable, and  
+%explicit estimates on the behavior of the solutions of \eqref{eq:main_model} in 1D were provided.
 

### 2015-04-14 report_clean/intro.tex
extra small changes

@@
 \bealn
+\label{eq:main_system}
+\begin{split}
 -\varepsilon_0 \partial_t E_x +\partial_y H_z = J_x,\\
@@
 \mu_0 \partial_t H_z + \partial_x E_y-\partial_y E_x= 0
+\end{split}
 \eealn
@@
 \een
-where \mrev{$\nu>0$} is the friction  between particles, $e<0$ is the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density that in general 
-depends on spatial variables and is uniform in time.
+where \mrev{$\nu\geq 0$} is the friction  between particles, $e<0$ is the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density that in general 
+depends on spatial variables and is uniform in time. \mrev{A non-zero value of $\nu$ constitutes a basis for the limiting absorption principle.} 
 The unknowns are the electron velocity $\ubf$ and the electromagnetic field.
@@
 To demonstrate the resonance that can occur in the system, we introduce the plasma frequency $w_p(\mathbf{r})=\sqrt{\frac{|e|^2N_e(\mathbf{r})}{m\epsilon_0}}$, 
-the cyclotron frequency $w_c(\mathbf{r})=\frac{e B_0(\mathbf{r})}{m_e}$ and rewrite the system in the frequency domain ($\partial_t\rightarrow iw$) 
+the cyclotron frequency $w_c(\mathbf{r})=\frac{e B_0(\mathbf{r})}{m_e}$ and rewrite \ref{eq:main_system} in the frequency domain ($\partial_t\rightarrow iw$), for a 
+particular case $\nu=0$:
 \begin{align*}
@@
 Another interesting case is $w^2=w_p^2+w_c^2$, when the diagonal part of the tensor $\underline{\epsilon}(w,\mathbf{r})$ vanishes. 
-This is a hybrid resonance case. As demonstrated in  \cite{Despres_2014} the time-harmonic electric field component $E_x$ is not necessarily square 
+This is a hybrid resonance case. As demonstrated in  \cite{Despres_2014}, in this case the time-harmonic electric field component $E_x$ is not necessarily square 
 integrable. This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.

### 2015-04-15 report_clean/proc.tex
bruno's changes
petites changements dans l'intro (General Issues: physics of the problem)+le fichier pour responce_reviewers
references

@@
 \begin{document}
-\newcommand{\urev}[1]{{\color{red}#1}}
-\newcommand{\mrev}[1]{{\color{blue}#1}}
+\newcommand{\urev}[1]{{\color{blue}#1}}
+\newcommand{\arev}[1]{{\color{red}#1}}
+\newcommand{\mrev}[1]{{\color{green}#1}}
 
@@
 \bibitem{cedar}
-Charles, F., Despr\'es, B., Merhenberg, M, 
+Charles, F., Despr\'es, B., Mehrenberg, M, 
 Enhanced convergence estimates for semi-lagrangian schemes Application to the Vlasov-Poisson equation, SIAM J. Numer. Anal. 2013, 51(2), 840-863.
@@
 \bibitem{phdhattori}
-T. Hattori, T. (2014).
+Hattori, T. (2014).
 D\'ecomposition de domaine pour la simulation Full-Wave dans un plasma froid.
@@
 \bibitem{simon}
-Simon Labrunie, Pierre Bertrand, Jean-Rodolphe Roche, Aurore Back,
-Takashi Hattori, 
+Labrunie, S., Bertrand, P., Roche, J.-R., Back, A., and
+Hattori, T. 
 Electromagnetic wave propagation and absorption in
@@
 
-\bibitem{Mouhot_2011} Mouhot, C., and Villani, C. (2011). On Landau damping. Acta mathematica, 207(1), 29-201.
 \bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
-\bibitem{Xu_2006}Xu, L., ans Yuan, N. (2006). FDTD formulations for scattering from 3-D anisotropic magnetized plasma objects. Antennas and Wireless Propagation Letters, IEEE, 5(1), 335-338.
+\bibitem{Xu_2006}Xu, L., and Yuan, N. (2006). FDTD formulations for scattering from 3-D anisotropic magnetized plasma objects. Antennas and Wireless Propagation Letters, IEEE, 5(1), 335-338.
+
+\bibitem{singular_solutions}
+Despr\'es, B., Imbert-G\'erard, L.-M. and Lafitte, O.. Singular solutions for the plasma at the resonance. 2014. <hal-01097364>
+
 \end{thebibliography}

### 2015-04-15 report_clean/FD.tex
bruno's changes
fixed mistakes
p6, before 11 matricial structure -> matrix structure

@@
 denoting by $\theta$ the corresponding Fourier variable. 
-After introducing $\Omega=(-L,\; H)\subset \mathbb R$ and defining the function space of the problem  $\mathbf{V}=L_{2}(\Omega)\times H_{1}(\Omega)$, 
+After introducing $\Omega=(-L,\; H)\subset \mathbb R$ and defining the function space of the problem  $\mathbf{V}=L_{2}(\Omega)\times H^{1}(\Omega)$, 
 equipped with the norm
@@
 We now prove the following result.
-\mrev{
+
 \begin{lemma}
@@
 	one  $H_1(\Omega)\subset C^0(\overline \Omega)$. Let us focus on the proof of coercivity. 
-	W.l.o.g. let $\nu>0$. We denote $\heps =  \|\rho(\eps_0)\|_{L^\infty}$, the spectral radius of $\eps_0$ so that
+	Without loss of generality let us assume that $\nu>0$. We denote $\heps =  \|\rho(\eps_0)\|_{L^\infty}$, the spectral radius of $\eps_0$ so that
 	$\heps Id- \eps_0 $ is a non negative hermitian matrix.
@@
 \end{remark}
-}
 
@@
 This expression greatly simplifies when choosing $V_{E_x}=V_{E_{y}}=\left(\phi_{m}\right)_{m=1}^{N_{2}}$ and
-in the case $\theta=0$. One obtains the matricial structure
+in the case $\theta=0$. One obtains the matrix structure
 \begin{align}

### 2015-04-15 report_clean/FD.tex
FD : all L_{2}->L^{2} and all H_{1}->H^{1}

@@
 denoting by $\theta$ the corresponding Fourier variable. 
-After introducing $\Omega=(-L,\; H)\subset \mathbb R$ and defining the function space of the problem  $\mathbf{V}=L_{2}(\Omega)\times H^{1}(\Omega)$, 
+After introducing $\Omega=(-L,\; H)\subset \mathbb R$ and defining the function space of the problem  $\mathbf{V}=L^{2}(\Omega)\times H^{1}(\Omega)$, 
 equipped with the norm
 \ben
- \|\mathbf{v}\|_{\mathbf{V}}^2= \|v_1\|_{L_{2}(\Omega)}^2+\|v_2\|_{H^{1}(\Omega)}^2,
+ \|\mathbf{v}\|_{\mathbf{V}}^2= \|v_1\|_{L^{2}(\Omega)}^2+\|v_2\|_{H^{1}(\Omega)}^2,
 \een
@@
 \begin{align*}
-  \left(E_x,u\right)=-\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L_{2}(\Omega), 
+  \left(E_x,u\right)=-\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega), 
 \end{align*}
-uniquely defines $E_x\in L_{2}(\Omega)$. The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
-was demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H_{1}(\Omega)$, we can obtain $E_x$ from the second equation.
+uniquely defines $E_x\in L^{2}(\Omega)$. The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
+was demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H^{1}(\Omega)$, we can obtain $E_x$ from the second equation.
 
@@
 %%\begin{split}
-%%\int_{-L}^H \left(\alpha E_x+i\delta E_y \right)_{1} \overline{\tilde E}_{x}&=0,\; \text{ for all }\tilde{E}_x\in L_{2}(\Omega), \;\\
+%%\int_{-L}^H \left(\alpha E_x+i\delta E_y \right)_{1} \overline{\tilde E}_{x}&=0,\; \text{ for all }\tilde{E}_x\in L^{2}(\Omega), \;\\
 %%\displaystyle \int_{-L}^H E_y'\tilde {E_y'} - \int_{-L}^H\left( -i\delta E_x+\alpha E_y \right)_{2}\overline{\tilde{E}}_{y}
 %%  - \imath \lambda E_y (-L) \overline{\tilde E_y} (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
-%%  \text{ for all }  \tilde{E}_{y}\in H_{1}(\Omega).
+%%  \text{ for all }  \tilde{E}_{y}\in H^{1}(\Omega).
 %%  \end{split}
@@
 %%\een
-%%If the multiplication operator $M_{\alpha}$ defined as $M_{\alpha}\psi=\frac{1}{\alpha}\psi$ is an isomorphism from $L_{2}([-L,\;H])$ to $L_{2}([-L,\;H])$ (this is true if e.g.
+%%If the multiplication operator $M_{\alpha}$ defined as $M_{\alpha}\psi=\frac{1}{\alpha}\psi$ is an isomorphism from $L^{2}([-L,\;H])$ to $L^{2}([-L,\;H])$ (this is true if e.g.
 %%$\alpha \in C_{0}([-L,\;H])$ and $|\alpha(x)|>c>0$, for some $c>0$, on the whole interval), this equation is equivalent to 
@@
 %%\label{eq:mult_eq}
-%%  \left(E_x,u\right)=-\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L_{2}(\Omega). 
+%%  \left(E_x,u\right)=-\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega). 
 %%\end{align}
 
-%%Choosing in the above $u=-i\delta \tilde{E}_y \in L_{2}(\Omega)$ and adding it to the second equation of (\ref{eq:full_var}), we obtain
+%%Choosing in the above $u=-i\delta \tilde{E}_y \in L^{2}(\Omega)$ and adding it to the second equation of (\ref{eq:full_var}), we obtain
 %%\bealn
@@
 %%  - \imath \lambda E_y (-L) \overline{\tilde E_y} (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
-%%  \text{ for all } \tilde{E}_{y}\in H_{1}(\Omega). \nonumber
+%%  \text{ for all } \tilde{E}_{y}\in H^{1}(\Omega). \nonumber
 %%\eealn
@@
 %%of this problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
-%%had been demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H_{1}(\Omega)$, we can obtain $E_x$ from the equation (\ref{eq:mult_eq}).
+%%had been demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H^{1}(\Omega)$, we can obtain $E_x$ from the equation (\ref{eq:mult_eq}).
 \end{remark}
@@
 %  - \imath \lambda E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
-%  \text{ for all } \tilde E_x\in L_{2}(\Omega), \; \tilde{E}_{y}\in H_{1}(\Omega).
+%  \text{ for all } \tilde E_x\in L^{2}(\Omega), \; \tilde{E}_{y}\in H^{1}(\Omega).
 %  \end{split}
@@
   - \imath \lambda E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
- \text{ for all } \tilde E_x\in L_{2}(\Omega), \; \tilde{E}_{y}\in H_{1}(\Omega).
+ \text{ for all } \tilde E_x\in L^{2}(\Omega), \; \tilde{E}_{y}\in H^{1}(\Omega).
   \end{split}

### 2015-04-22 report_clean/numerics.tex
- p11 Figure 4
  dependence
much more → many more. Pike → peak. resonant → resonance.

@@
 \end{tabular}
-\caption{In the left figure the depenence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated. 
+\caption{In the left figure the dependence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated. 
 In the right figure we show the computed solutions for the problem with parameters in Table \ref{tab:parameters} for different values of $\nu$. }
@@
 case.
-The numerical tests have been kept to a minimum since much more are needed to fully validate
+The numerical tests have been kept to a minimum since many more are needed to fully validate
 the concept.
@@
 is the following. We use a 7th order semi-lagrangian scheme, and the CFL is $\nu=0.5$.
-The Pike is the hybrid resonance, visible on $E_x$ and $u_x$.
+The peak is the hybrid resonance, visible on $E_x$ and $u_x$.
 The total energy $\mathcal E(t)$ is the physical energy. 
 The comparison with figures \ref{fig:dependence} and \ref{fig:resonance_nus_ey_x} show that the 
-singular nature of the resonant is captured by this new scheme without any doubt.
+singular nature of the resonance is captured by this new scheme without any doubt.
 

### 2015-04-22 report_clean/intro.tex
recall the limiting amplitude and absorption principles in a few words to go along Figure 1.

@@
 $\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
-Such a comparison is a way to study the formal commutation relation
+\textcolor{red}{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principle.
+The limited absorption principle states that the form of the limit as $\nu \to 0$ whereas the limited amplitude principle states that as $t$ tends to infinity, the solutions tends to a steady state of the form $ \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t}$.
+The commutation between the two principles then write as}
 $$

### 2015-04-22 report_clean/FD.tex
\alpha => \alpha(\mathbf{r}) TO DOUBLE CHECK

@@
 \right),\\
-\tilde{\alpha}(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\tilde{\omega}\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)}\right),\qquad 
+\tilde{\alpha}(\omega,x)=\frac{\omega^2}{c^2}\left(1-\frac{\tilde{\omega}\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)}\right),\qquad 
 \tilde{\delta}(\omega)=\frac{\omega_c\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)},
@@
 \bealn
- \tilde{\alpha}(\omega)=\alpha(\omega)+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}\frac{\omega^2}{c^2},\qquad \alpha(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\omega_p^2}{\omega^2-\omega_c^2}\right),\\
+ \tilde{\alpha}(\omega,x)=\alpha(\omega,x)+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}\frac{\omega^2}{c^2},\qquad \alpha(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\omega_p^2}{\omega^2-\omega_c^2}\right),\\
  \tilde{\delta}(\omega)=\delta(\omega)-\frac{2i\omega^3\nu}{c^2(\omega^2-\omega_c^2)^2},\qquad \delta(\omega)=\frac{\omega\omega_c\omega_p^2}{c^2(\omega^2-\omega_c^2)}.
@@
 \end{align}
- In this model problem, the coefficients  $\alpha(\omega)$ and $\delta(\omega)$ are sufficiently smooth, i.e. bounded and continuous in  
+ In this model problem, the coefficients  $\alpha(\omega,x)$ and $\delta(\omega)$ are sufficiently smooth, i.e. bounded and continuous in  
 $\left[-L,\; \mathbb{R}\right)$.
@@
 as a system of two equations, where the first equation (for $E_y$) is the variational formulation for the Helmholtz equation 
-with the variable coefficient $k^2=(\alpha-\frac{\delta^2}{\alpha})$, and the second equation 
+with the variable coefficient $k^2=(\alpha(x)-\frac{\delta^2}{\alpha})$, and the second equation 
 \begin{align*}
-  \left(E_x,u\right)=-\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega), 
+  \left(E_x,u\right)=-\left(\frac{i\delta}{\alpha(x)}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega), 
 \end{align*}

### 2015-04-22 report_clean/FD.tex
one more alpha

@@
 as a system of two equations, where the first equation (for $E_y$) is the variational formulation for the Helmholtz equation 
-with the variable coefficient $k^2=(\alpha(x)-\frac{\delta^2}{\alpha})$, and the second equation 
+with the variable coefficient $k^2=(\alpha(x)-\frac{\delta^2}{\alpha(x)})$, and the second equation 
 \begin{align*}

### 2015-04-22 report_clean/FD.tex
epsilon defined

@@
 the cyclotron frequency is 
-$ \omega_c={\frac{eB_0}{m_e}}$ and the plasma frequency is $ \omega_p^2=\frac{e^2 N_e}{\epsilon_0 m_e}$.
+$ \omega_c={\frac{eB_0}{m_e}}$ and the plasma frequency is $ \omega_p^2=\frac{e^2 N_e}{\epsilon_0 m_e}$,\textcolor{red}{and $\epsilon(\omega)$ is the dielectric tensor of the cold plasma approximation.}
 The series expansion as $\nu\rightarrow 0$ gives at leading orders

### 2015-04-23 report_clean/responce_reviewers.tex
added/corrected item 1

@@
 
+A. General issues.
+
+1. We agree with the remarks of the reviewer. We included a short introduction into the physics of the problem, 
+which hopefully will facilitate in reading the article. The Section 4.3.1 contains of course a mistake in the description of the 
+parameters of the problem.
+
+- on page 3, the cold plasma dielectric tensor seems to be primarily a function of \omega the antenna frequency. But afterwards
+one realizes that it is also a function of x, and that this dependence is critical in the problems under consideration. That should
+be stressed at the beginning of Section 2. And maybe alpha should be introduced as a function of x (as is done in Remark 2.2),
+with omega a parameter.
+
+- using "epsilon_0" to denote a non-uniform dielectric tensor does not help readability... Do the authors really expect the readers 
+to understand that the letter "epsilon_0" in  Problem (5) represents a non-uniform tensor which variations are the cause of singular
+solutions ?
+
+- as mentionned above, in Lemma 2.1 it would be clearer to write "\omega \neq \omega_c" than "\hat \epsilon < + \infty"
+(especially given that \hat \epsilon is not defined in Lemma 2.1).
+
 \end{document}

### 2015-04-23 report_clean/intro.tex
\alpha => \alpha(\mathbf{r})
added/corrected item 1

@@
 \urev{
-We consider the wave propagation in the collisionless cold plasma that consists of particles of single species 
-under a uniform in time background magnetic field $\mathbf{B}_0=(0,\;0,\; B_0)$. This process can be described by the 2D time-dependent Maxwell system  \cite{Stix}
-\bealn
+We consider the wave propagation in the cold plasma that consists of particles of single species 
+under a uniform in time background magnetic field $\mathbf{B}_0=(0,\;0,\; B_0)$. This process in 2D can be described by the time-dependent Maxwell system  \cite{Stix}
+\begin{align}
 \label{eq:main_system}
@@
 \end{split}
-\eealn
+\end{align}
 coupled with \mrev{an equation for the } linear electronic current  $\J = eN_e(\mathbf{r}) \ubf$, 
-\ben
-m_e \partial_t u_x =\epsilon_0 e E_x+e B_0(\mathbf{r}) u_y -m_e \nu u_x, \label{eq:electronmove}\\
+\begin{align}
+\begin{split}
+\label{eq:electronmove}
+m_e \partial_t u_x =\epsilon_0 e E_x+e B_0(\mathbf{r}) u_y -m_e \nu u_x,\\
 m_e \partial_t u_y =\epsilon_0 e E_y-e B_0(\mathbf{r}) u_x -m_e \nu u_y,
-\een
+\end{split}
+\end{align}
 where \mrev{$\nu\geq 0$} is the friction  between particles, $e<0$ is the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density that in general 
@@
 {\mathcal E}(t)= \int_\Omega \left(
-\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|^2}{2|e|N_e(\x)} 
-\right)\mathrm{d}\x.
+\frac{\epsilon_0 |\E(t,\mathbf{r})|^2}{2}+\frac{ |\B(t,\mathbf{r})|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|^2}{2|e|N_e(\mathbf{r})} 
+\right)\mathrm{d}\mathbf{r}.
 \een
 
-To demonstrate the resonance that can occur in the system, we introduce the plasma frequency $w_p(\mathbf{r})=\sqrt{\frac{|e|^2N_e(\mathbf{r})}{m\epsilon_0}}$, 
-the cyclotron frequency $w_c(\mathbf{r})=\frac{e B_0(\mathbf{r})}{m_e}$ and rewrite \ref{eq:main_system} in the frequency domain ($\partial_t\rightarrow iw$), for a 
+To illustrate unexpected difficulties that can occur in this system, let us rewrite it in the frequency domain. To do so, 
+we introduce the plasma frequency $\omega_p(\mathbf{r})=\sqrt{\frac{|e|^2N_e(\mathbf{r})}{m\epsilon_0}}$, 
+the cyclotron frequency $\omega_c(\mathbf{r})=\frac{e B_0(\mathbf{r})}{m_e}$ and perform the Fourier transform 
+in time of \ref{eq:main_system} ($\partial_t\rightarrow -i\omega$), for a 
 particular case $\nu=0$:
-\begin{align*}
+\begin{align}
 \label{eq:model_freq_domain}
- \mathbf{curl}{\operatorname{curl}}\mathbf{E}-\frac{w^2}{c^2}\underline{\epsilon}(w,\mathbf{r})\mathbf{E}=0,
-\end{align*}
+ \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\underline{\epsilon}^{0}(\omega,\mathbf{r})\hat{\mathbf{E}}=0,
+\end{align}
 where the cold-plasma dielectric tensor \cite[Chapter 1-2]{Stix}
 \begin{align*}
- \underline{\epsilon}(w,\mathbf{r})=\left(
+\underline{\epsilon}^{0}(\omega,\mathbf{r})=\left(
  \begin{matrix}
@@
  \end{matrix}
-\right),\; \alpha=1-\frac{w_p^2}{w^2-w_c^2},\; \delta=\frac{w_cw_p^2}{w(w^2-w_c^2)}.
+\right),\; \alpha(\mathbf{r})=1-\frac{\omega_p^2(\mathbf{r})}{\omega^2-\omega_c^2(\mathbf{r})},\; \delta=\frac{\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})}{\omega(\omega^2-\omega_c^2(\mathbf{r}))}.
 \end{align*}
-The case $w=w_c$, when $\underline{\epsilon}(w,\mathbf{r})$ is singular, is a so-called cyclotron resonance (c.f. \cite[Chapter 1-5]{Stix}). It can be 
-demonstrated that for this geometry there is no resonant heating associated to these points, see \cite{singular_solutions}, and the solutions are well-defined 
-in the limite $w\rightarrow w_c(\mathbf{r})$. Hence this case is not 
-studied in the present work.
 
-Another interesting case is $w^2=w_p^2+w_c^2$, when the diagonal part of the tensor $\underline{\epsilon}(w,\mathbf{r})$ vanishes. 
-This is a hybrid resonance case. As demonstrated in  \cite{Despres_2014}, in this case the time-harmonic electric field component $E_x$ is not necessarily square 
+The point $\mathbf{r}_c=(x_c,y_c)$ s.t.
+$\omega_c(\mathbf{r}_c)=\omega$, i.e.
+when $\underline{\epsilon}(\omega,\mathbf{r})$ is singular, is called a cyclotron resonance (c.f.
+\cite[Chapter 1-5]{Stix}).
+In \cite{singular_solutions} it was demonstrated for a 1D-counterpart of the above system that such points behave like removable singularities, 
+and the solutions are well-defined in the limit $x\rightarrow x_c$. Hence this case is not of interest for the present work.
+
+Another interesting case is $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$, when the diagonal part of the tensor $\underline{\epsilon}(w,\mathbf{r})$ vanishes, 
+under the condition that the non-diagonal part remains non-zero. This is a hybrid resonance case. 
+As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component $E_x$ is not necessarily square 
 integrable. This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.  
+Jumping ahead, instead of (\ref{eq:model_freq_domain}) 
+one considers a sequence of regularized problems
+\begin{align}
+\label{eq:seq_regularized}
+  \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{w^2}{c^2}\underline{\epsilon}^{\nu}(w,\mathbf{r})\hat{\mathbf{E}}=0,\;
+  \underline{\epsilon}^{\nu}(\omega,\mathbf{r})= \underline{\epsilon}^{0}(\omega,\mathbf{r})+i\nu \mathbb{E},\; 
+\end{align}
+with $\nu\rightarrow 0$. 
 }
@@
 \urev{In some physical applications (e.g. when modelling antennas in plasmas), it is required to study the above system in an 
-infinite domain $(a,\; \infty)\times\mathbb{R}$, $a\in \mathbb{R}$, with appropriately chosen boundary conditions which will be discussed later}.
-\mrev{ADD REFERENCE}
-To simplify the above system, we perform the Fourier transform in $y$ ($\partial_y\rightarrow i\theta$) and consider the one-dimensional setting
+infinite domain $(-L,\; \infty)\times\mathbb{R}$, $L\in \mathbb{R}$,
+c.f. e.g. \cite{Despres_2014}. We complement Problem (\ref{eq:model_freq_domain}) with the boundary conditions.
+At the left boundary of the domain, which represents the wall of the Tokamak, we choose Robin boundary conditions 
+\be
+-curl \hat{\mathbf{E}} -\imath \lambda\hat{\mathbf{E}} \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
+\ee
+where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and $\lambda$ is 
+the frequency of the antenna.
+
+Therefore, we will concentrate on a 1D-version of the system (\ref{eq:main_model}), similarly to works \cite{Despres_2014, singular_solutions}. 
+It already contains difficulties intrinsic to the hybrid resonance case. We truncate the domain 
+$(-L,\; \infty)$ to $(-L,\; H)$ and set on the right boundary $\operatorname{curl} \E = 0$. }
+
+Hence, we perform the Fourier transform in $y$ ($\partial_y\rightarrow i\theta$) and consider the one-dimensional setting
 
@@
 \end{equation}
-posed in $(-L,\; \infty)\times \mathbb{R}$, for some $L>0$. This domain represents the physical case of a wave sent from a wall facing a plasma.
+ posed in $(-L,\; H)$, for some $L,H>0$, with the boundary conditions 
+ \begin{align*}
+  \left.\left(-\partial_x E_y+i\theta E_x -\imath \lambda E_y\right)\right|_{x=-L} =g_{inc},\\
+  \left.\partial_xE_y\right|_{x=H}=0.
+ \end{align*}
+
+ %This domain represents the physical case of a wave sent from a wall facing a plasma.
 
@@
 
-We complement Problem (\ref{eq:main_model}) with the boundary conditions.
-At the left boundary of the domain, which represents the wall of the Tokamak, we choose Robin boundary conditions 
-\be
--curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
-\ee
-where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and $\lambda$ is 
-the frequency of the antenna.
 %some given 
@@
 %where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$.
-We truncate the domain 
-$(-L,\; \infty)$ to $(-L,\; H)$ and set on the right boundary $\operatorname{curl} \E = 0$. 
+
 %\begin{remark}
@@
 First, we investigate the finite element approximation of the 1D 
-problem \eqref{eq:main_model} written in the frequency domain ($\partial_t\rightarrow -i\omega$), with a linearized dielectric tensor with respect to $\nu$.
-In particular, we again investigate this problem in one dimension, performing the Fourier transform in $y$.
+problem \eqref{eq:main_model} written in the frequency domain ($\partial_t\rightarrow -i\omega$), with a dielectric tensor \mrev{regularized
+with the help of a small parameter $\nu$}. More details on regularization will be given in further sections. 
+%linearized with respect to $\nu$.
 We prove the well-posedness of this problem for $\nu>0$ in Section~\ref{sec:wellposedness} and 
@@
 of the solution fairly well (Section \ref{sec:freq_dep}).
+
 Second, we briefly develop an original scheme based on widely appreciated semi-lagrangian schemes
@@
 \textcolor{red}{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principle. 
-The limited absorption principle states that the form of the limit as $\nu \to 0$ whereas the limited amplitude principle states that as $t$ tends to infinity, the solutions tends to a steady state of the form $ \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t}$.
-The commutation between the two principles then write as}
+In application to e.g. non-resonant case of (\ref{eq:model_freq_domain}), the limited absorption principle states that with 
+appropriately chosen boundary conditions the solution of (\ref{eq:seq_regularized}) 
+as $\nu\rightarrow 0\pm$ 
+would coincide with the solution of (\ref{eq:model_freq_domain}). Similarly, the limiting amplitude principle applied to the problem (\ref{eq:main_system}) 
+states that if the boundary conditions are chosen harmonic in time, e.g. $\partial_x E_y=\mathrm{e}^{-i\omega_{*} t}$ on 
+the boundary, then the solution of this problem $(\mathbf{E}(t),\;H(t))$ asymptotically ($t\rightarrow +\infty$)
+tends to a steady state of the form $ \left(\mathbf{E}(\omega_{*}),\; \hat{H}(\omega_{*})\right)\mathrm{e}^{-i\omega_{*} t}$, where 
+$\left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)$ is the solution of (\ref{eq:main_model})
+in the frequency domain, with $\omega=\omega_{*}$. The commutation between the two principles then write as}
 $$
@@
 see Figure \ref{fig:limits}. 
-Even though it is true for standard linear wave problems, it is not clear that it still hold in our case due the singularity
+Even though it is true for standard linear wave problems, it is not clear \mrev{if it still holds} in our case due the singularity
 of the hybrid resonance.

### 2015-04-23 report_clean/responce_reviewers.tex
changed notation, corrected some defs

--- 2015-04-13 report_clean/responce_reviewers.tex
@@
 
+\section{Extra Corrections}
+As an extra improvement, not asked by the reviewers, we changed $\tilde{\omega}$ to $\omega_{\nu}$ in Section 2.
+
+Corrected the definitions of $\alpha,\delta$ to comply with the definition of the cold plasma dielectric tensor of Stix (more precisely, removed terms $\frac{\omega^2}{c^2}$ in 
+front of them)
+
 \section{Responce to the reviewer #1}
@@
 
+A. General issues.
+
+1. We agree with the remarks of the reviewer. We included a short introduction into the physics of the problem, 
+which hopefully will facilitate in reading the article. The Section 4.3.1 contains of course a mistake in the description of the 
+parameters of the problem.
+
+Concerning the notation: from now on $\epsilon^{\nu}_{\omega}(\mathbf{r})$ denotes the cold plasma dielectric tensor, similarly we denote its parameters.
+
+ We added explicitely dependence on space in parameters 
+that depend on the spatial variables.
+
+- as mentionned above, in Lemma 2.1 it would be clearer to write "\omega \neq \omega_c" than "\hat \epsilon < + \infty"
+(especially given that \hat \epsilon is not defined in Lemma 2.1).
+
+We added as well a brief description of what limiting absorption and limiting amplitude principles
+
 \end{document}

### 2015-04-23 report_clean/FD.tex
Afterwards say that from now on we define $epsilon_0(x)=epsilon(x)$
bug fix"
changed notation, corrected some defs

--- 2015-04-22 report_clean/FD.tex
@@
 \section{Frequency domain study}
-In the frequency domain, the velocity can be eliminated and it yields a simpler system under the form
-of  Maxwell equations with the cold plasma dielectric tensor \cite{Stix,Despres_2014}. One obtains the equations
+The goal of this section is to review the connection between the system (\ref{eq:main_system}), its frequency domain counterpart and 
+the regularized problem (\ref{eq:seq_regularized}).
+
+In the frequency domain, the velocity can be eliminated to obtain a simpler system under the form
+of  Maxwell equations with the cold plasma dielectric tensor \cite{Stix,Despres_2014}, more precisely
+\urev{
 \bealn
@@
 \operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-
-\epsilon(\omega)\hat{\mathbf{E}}=0,\\
-\epsilon(\omega)=\left(
+\frac{\omega^2}{c^2}\underline{\epsilon}^{\nu}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,\\
+\underline{\epsilon}^{\nu}_{\omega}(\mathbf{r})=\left(
 \begin{matrix}
- \tilde{\alpha} & i\tilde{\delta} \\
- -i\tilde{\delta}  & \tilde{\alpha}
+ \alpha^{\nu}_{\omega}(\mathbf{r}) & i\delta^{\nu}_{\omega}(\mathbf{r}) \\
+ -i\delta^{\nu}_{\omega}(\mathbf{r}) & \alpha^{\nu}_{\omega}(\mathbf{r})
 \end{matrix}
-\right),\\
-\tilde{\alpha}(\omega,x)=\frac{\omega^2}{c^2}\left(1-\frac{\tilde{\omega}\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)}\right),\qquad 
-\tilde{\delta}(\omega)=\frac{\omega_c\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)},
+\right),\qquad 
+ \alpha^{\nu}_{\omega}(\mathbf{r})=\frac{\omega^2}{c^2}\left(1-\frac{\omega_{\nu}\omega_p^2(\mathbf{r})}{\omega(\omega_{\nu}^2-\omega_c^2(\mathbf{r}))}\right),\qquad 
+\delta^{\nu}_{\omega}(\mathbf{r})=\frac{\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})}{\omega(\omega_{\nu}^2-\omega_c^2(\mathbf{r}))},
 \eealn
-where the frequency 
-$\tilde{\omega}=\omega+i\nu$ is shifted in the complex plane,
-the cyclotron frequency is 
-$ \omega_c={\frac{eB_0}{m_e}}$ and the plasma frequency is $ \omega_p^2=\frac{e^2 N_e}{\epsilon_0 m_e}$.
+}
+\mrev{where the frequency 
+$\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane.
+Note that neither cyclotron, nor hybrid resonances occur in the problem with the dielectric tensor $\epsilon^{\nu}_{\omega}(\mathbf{r}), \; \nu>0,$ (since all parameters are real).
+Hence
+the choice of the non-zero plasma friction $\nu>0$ can be viewed as a regularization of the problem. }
+
+\mrev{
 The series expansion as $\nu\rightarrow 0$ gives at leading orders
 \bealn
- \tilde{\alpha}(\omega,x)=\alpha(\omega,x)+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}\frac{\omega^2}{c^2},\qquad \alpha(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\omega_p^2}{\omega^2-\omega_c^2}\right),\\
- \tilde{\delta}(\omega)=\delta(\omega)-\frac{2i\omega^3\nu}{c^2(\omega^2-\omega_c^2)^2},\qquad \delta(\omega)=\frac{\omega\omega_c\omega_p^2}{c^2(\omega^2-\omega_c^2)}.
+ \alpha^{\nu}_{\omega}=\alpha^{0}_{\omega}+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}=\alpha^{0}_{\omega}+i\nu D_{\alpha},\\
+ \delta^{\nu}_{\omega}=\delta^{0}_{\omega}-i\nu\frac{2\omega}{(\omega^2-\omega_c^2)^2}=\alpha^{0}_{\omega}+i\nu D_{\delta},
 \eealn
-We finally obtain a simpler equation \cite{Despres_2014} 
-%\ben
-% \epsilon_{\nu}(\omega)\approx \epsilon_0+i\nu Id,\; \nu\rightarrow 0.
-%\een
-%Thus, in this work we concentrate on a model
+where $\alpha^{0}_{\omega},\;\delta^{0}_{\omega}$ are defined by (\ref{eq:alpha_delta}). In the frequency domain one thus can consider 
+the following regularization of the cold plasma dielectric tensor of (\ref{eq:main_frequency_domain}):
+\begin{align*}
+\underline{\epsilon}^{\nu}_{\omega}\approx \underline{\epsilon}^0_{\omega}+i\nu \left(
+ \begin{matrix}
+  D_{\alpha} & D_{\delta}\\
+  -D_{\delta} & D_{\alpha}
+ \end{matrix}
+\right).
+\end{align*}
+However, as demonstrated in \cite{singular_solutions} for the 1D setting, a significantly simpler regularization (considered in \cite{Despres_2014})
+\ben
+\epsilon^{\nu}_{\omega}(\mathbf{r})\approx \epsilon^{0}_{\omega}(\mathbf{r})+i\nu \mathbb{E}
+\een
+yields the same solution as $\nu\rightarrow 0$. }
+%We finally obtain a simpler equation \cite{Despres_2014}
+
+\textcolor{red}{Thus, applying the above process to (\ref{eq:main_model}), we obtain, see also \cite{Despres_2014},
 \begin{align}
 \label{eq:main_frequency_domain}
-\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}
-\left(\epsilon_0(\omega)+\nu Id\right)\hat{\mathbf{E}}=0,\\
+\left(
+\begin{matrix}
+ i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
+ i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
+\end{matrix}
+\right)-\frac{\omega^2}{c^2}
+\left(\epsilon^{0}_{\omega}(x)+\nu \mathbb{E}\right)\left(
+\begin{matrix}
+ \hat{E}_x\\
+ \hat{E}_y
+\end{matrix}
+\right)
+=0,\\
 \label{eq:epsilon_0}
-\epsilon_0(\omega)=\left(
+\epsilon^0_{\omega}(x)=\left(
 \begin{matrix}
- \alpha & i\delta \\
- -i\delta & \alpha 
+ \alpha_{\omega}^{0}(x) & i\delta_{\omega}^{0}(x) \\
+ -i\delta_{\omega}^{0}(x) & \alpha_{\omega}^{0}(x)
+\end{matrix}
+\right)=
+\left(
+\begin{matrix}
+ \alpha(x) & i\delta(x) \\
+ -i\delta(x) & \alpha(x)
 \end{matrix}
@@
 \end{align}
- In this model problem, the coefficients  $\alpha(\omega,x)$ and $\delta(\omega)$ are sufficiently smooth, i.e. bounded and continuous in  
-$\left[-L,\; \mathbb{R}\right)$.
+ In this model problem, the coefficients  $\alpha(x)$ and $\delta(x)$ are sufficiently smooth, i.e. bounded and continuous in  
+$\left[-L,\; H\right)$.
+}
 

### 2015-04-23 report_clean/intro.tex
changed notation, corrected some defs

@@
 \label{eq:model_freq_domain}
- \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\underline{\epsilon}^{0}(\omega,\mathbf{r})\hat{\mathbf{E}}=0,
+ \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\underline{\epsilon}^{0}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,
 \end{align}
 where the cold-plasma dielectric tensor \cite[Chapter 1-2]{Stix}
-\begin{align*}
-\underline{\epsilon}^{0}(\omega,\mathbf{r})=\left(
+\begin{align}
+\nonumber
+\underline{\epsilon}^{0}_{\omega}(\mathbf{r})=\left(
  \begin{matrix}
-  \alpha(\mathbf{r}) & i\delta(\mathbf{r})\\
-  -i\delta(\mathbf{r}) & \alpha(\mathbf{r})
+  \alpha_{\omega}^{0}(\mathbf{r}) & i\delta_{\omega}^{0}(\mathbf{r})\\
+  -i\delta_{\omega}^{0}(\mathbf{r}) & \alpha_{\omega}^{0}(\mathbf{r})
  \end{matrix}
-\right),\; \alpha(\mathbf{r})=1-\frac{\omega_p^2(\mathbf{r})}{\omega^2-\omega_c^2(\mathbf{r})},\; \delta=\frac{\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})}{\omega(\omega^2-\omega_c^2(\mathbf{r}))}.
-\end{align*}
+\right),\\
+\label{eq:alpha_delta}
+\alpha_{\omega}^{0}(\mathbf{r})=1-\frac{\omega_p^2(\mathbf{r})}{\omega^2-\omega_c^2(\mathbf{r})},\; \delta_{\omega}^{0}(\mathbf{r})=\frac{\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})}{\omega(\omega^2-\omega_c^2(\mathbf{r}))}.
+\end{align}
 
@@
 $\omega_c(\mathbf{r}_c)=\omega$, i.e.
-when $\underline{\epsilon}(\omega,\mathbf{r})$ is singular, is called a cyclotron resonance (c.f.
+when $\underline{\epsilon}_{\omega}^{0}(\mathbf{r})$ is singular, is called a cyclotron resonance (c.f.
 \cite[Chapter 1-5]{Stix}).
@@
 
-Another interesting case is $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$, when the diagonal part of the tensor $\underline{\epsilon}(w,\mathbf{r})$ vanishes, 
+Another interesting case is $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$, when the diagonal part of the tensor $\underline{\epsilon}_{\omega}^{0}(\mathbf{r})$ vanishes, 
 under the condition that the non-diagonal part remains non-zero. This is a hybrid resonance case. 
@@
 \label{eq:seq_regularized}
-  \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{w^2}{c^2}\underline{\epsilon}^{\nu}(w,\mathbf{r})\hat{\mathbf{E}}=0,\;
-  \underline{\epsilon}^{\nu}(\omega,\mathbf{r})= \underline{\epsilon}^{0}(\omega,\mathbf{r})+i\nu \mathbb{E},\; 
+  \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\underline{\epsilon}^{\nu}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,\;
+  \underline{\epsilon}^{\nu}_{\omega}(\mathbf{r})= \underline{\epsilon}^{0}_{\omega}(\mathbf{r})+i\nu \mathbb{E},\; 
 \end{align}
@@
 
-\urev{In some physical applications (e.g. when modelling antennas in plasmas), it is required to study the above system in an 
-infinite domain $(-L,\; \infty)\times\mathbb{R}$, $L\in \mathbb{R}$,
-c.f. e.g. \cite{Despres_2014}. We complement Problem (\ref{eq:model_freq_domain}) with the boundary conditions.
+\urev{We will concentrate on a simplified model (which nevertheless is of physical interest when modelling antennas in plasmas), where it is required to study the above system in an 
+infinite domain $(-L,\; \infty)\times\mathbb{R}$, $L\in \mathbb{R}$, under the assumption that the electron density $N_{e}$ and the magnetic field $B_0$ are \textbf{uniform} in the second coordinate, more precisely
+$N_{e}=N_{e}(x)$ and $B_0=B_0(x)$, see e.g.
+\cite{Despres_2014}.
+Despite such a simplfication, already a 1D-version of the system (\ref{eq:main_model}) contains difficulties intrinsic to the hybrid resonance case
+\cite{Despres_2014, singular_solutions}.
+
+The problem (\ref{eq:model_freq_domain}) should be equipped with the boundary conditions.
 At the left boundary of the domain, which represents the wall of the Tokamak, we choose Robin boundary conditions 
@@
 where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and $\lambda$ is 
-the frequency of the antenna.
+the frequency of the antenna. We truncate the domain 
+$(-L,\; \infty)\times\mathbb{R}$ to $(-L,\; H)\times\mathbb{R}$ and set on the right boundary $\operatorname{curl} \E = 0$.
 
-Therefore, we will concentrate on a 1D-version of the system (\ref{eq:main_model}), similarly to works \cite{Despres_2014, singular_solutions}. 
-It already contains difficulties intrinsic to the hybrid resonance case. We truncate the domain 
-$(-L,\; \infty)$ to $(-L,\; H)$ and set on the right boundary $\operatorname{curl} \E = 0$. }
+}
 
-Hence, we perform the Fourier transform in $y$ ($\partial_y\rightarrow i\theta$) and consider the one-dimensional setting
+Hence, recalling that $N_e=N_e(x), \; B_0=B_0(x)$, we perform the Fourier transform in $y$ ($\partial_y\rightarrow i\theta, \; \theta\in\mathbb{R},$) and consider the one-dimensional setting
 
@@
 \begin{cases}
-\epsilon_0\partial_t E_{x}=-eN_e u_x,\\
+\epsilon_0\partial_t E_{x}-i\theta H_z=-eN_e u_x,\\
 \epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\\
-\mu_0\partial_t H_z+\partial_x E_y =0,\\
+\mu_0\partial_t H_z+\partial_x E_y-i\theta E_x =0,\\
 m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
@@
  \end{align*}
+This is the model that will be considered in the rest of the article, unless stated otherwise.
 
@@
 %	When modelling antennas in plasma physics \mrev{(e.g. in such applications as ITER)}, 
-%	a good choice of boundary condition could be $\lambda = \sqrt{\alpha(-L)}$
+%	a good choice of boundary condition could be $\lambda = \sqrt{\alpha_{\omega}(-L)}$
 %\end{remark}
@@
 $\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
-\textcolor{red}{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principle. 
+\textcolor{red}{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principles. 
 In application to e.g. non-resonant case of (\ref{eq:model_freq_domain}), the limited absorption principle states that with 
@@
 $\left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)$ is the solution of (\ref{eq:main_model})
-in the frequency domain, with $\omega=\omega_{*}$. The commutation between the two principles then write as}
+in the frequency domain, with $\omega=\omega_{*}$. For more details see e.g. \cite{Morawetz, Eidus}. The commutation between the two principles then write as}
 $$

### 2015-04-24 report_clean/responce_reviewers.tex
+2 remarks taken into account

@@
 
- We added explicitely dependence on space in parameters 
-that depend on the spatial variables.
+We added explicitely dependence on space in parameters that depend on the spatial variables.
 
-- as mentionned above, in Lemma 2.1 it would be clearer to write "\omega \neq \omega_c" than "\hat \epsilon < + \infty"
-(especially given that \hat \epsilon is not defined in Lemma 2.1).
+Indeed, $\epsilon_{\infty}<\infty$ if $\omega_c^2\neq \omega^2$, but formally one also needs to require the boundedness of $\omega_p^2$. Therefore we 
+added an assumption in the end of the Section Frequency Domain Study on the coefficients of the dielectric tensor, and made a remark on the absence
+of the cyclotron resonance.
 
-We added as well a brief description of what limiting absorption and limiting amplitude principles
+A brief description of what limiting absorption and limiting amplitude principles had been added in the end of the introduction.
+
+2. The reduction to a 1d problem is not clearly justified - indeed, we changed this in the introduction by adding an assumption on $N_e, B_0$, 
+and changed the wording in the introduction to underline that the 1D case is the one of interest.
+
+Specific remarks:
+
+- abstract: changed
+
+- in the frequency domain, as we have shown in Lemma 2.1, the problem is regularized by a choice $|\nu|>0$, independently of the sign of $\nu$. 
+It is interesting however that for a fixed $\omega$ the limits $\lim_{\nu\rightarrow 0\pm}$ do not result in the same solution. 
+In the time domain the sign of $\nu>0$ is indeed of crucial importance for the stability. We added a remark on this before Section 2.1
+
+- $L$ is just a non-negative number. We found it more convenient to place the point of the isolated hybrid resonance in $x=0$.
+For $\nu\neq 0$ the energy decays, we added this in the introduction
+-
 

### 2015-04-24 report_clean/FD.tex
+2 remarks taken into account

@@
 \operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-
-\frac{\omega^2}{c^2}\underline{\epsilon}^{\nu}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,\\
-\underline{\epsilon}^{\nu}_{\omega}(\mathbf{r})=\left(
+\frac{\omega^2}{c^2}\underline{\varepsilon}^{\nu}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,\\
+\underline{\varepsilon}^{\nu}_{\omega}(\mathbf{r})=\left(
 \begin{matrix}
@@
 \bealn
- \alpha^{\nu}_{\omega}=\alpha^{0}_{\omega}+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}=\alpha^{0}_{\omega}+i\nu D_{\alpha},\\
- \delta^{\nu}_{\omega}=\delta^{0}_{\omega}-i\nu\frac{2\omega}{(\omega^2-\omega_c^2)^2}=\alpha^{0}_{\omega}+i\nu D_{\delta},
+ \alpha^{\nu}_{\omega}=\alpha_{\omega}+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}=\alpha_{\omega}+i\nu D_{\alpha},\\
+ \delta^{\nu}_{\omega}=\delta_{\omega}-i\nu\frac{2\omega}{(\omega^2-\omega_c^2)^2}=\alpha_{\omega}+i\nu D_{\delta},
 \eealn
-where $\alpha^{0}_{\omega},\;\delta^{0}_{\omega}$ are defined by (\ref{eq:alpha_delta}). In the frequency domain one thus can consider 
+where $\alpha_{\omega},\;\delta_{\omega}$ are defined by (\ref{eq:alpha_delta}). In the frequency domain one thus can consider 
 the following regularization of the cold plasma dielectric tensor of (\ref{eq:main_frequency_domain}):
 \begin{align*}
-\underline{\epsilon}^{\nu}_{\omega}\approx \underline{\epsilon}^0_{\omega}+i\nu \left(
+\underline{\varepsilon}^{\nu}_{\omega}\approx \underline{\varepsilon}^0_{\omega}+i\nu \left(
  \begin{matrix}
@@
 
-\textcolor{red}{Thus, applying the above process to (\ref{eq:main_model}), we obtain, see also \cite{Despres_2014},
+Thus, applying the above process to (\ref{eq:main_model}), we obtain, see also \cite{Despres_2014},
 \begin{align}
@@
 \begin{matrix}
- \alpha_{\omega}^{0}(x) & i\delta_{\omega}^{0}(x) \\
- -i\delta_{\omega}^{0}(x) & \alpha_{\omega}^{0}(x)
+ \alpha_{\omega}(x) & i\delta^{0}(x) \\
+ -i\delta_{\omega}(x) & \alpha^{0}(x)
 \end{matrix}
@@
 \end{align}
- In this model problem, the coefficients  $\alpha(x)$ and $\delta(x)$ are sufficiently smooth, i.e. bounded and continuous in  
-$\left[-L,\; H\right)$.
+\urev{
+From now on we will assume the following assumption to hold.
+\begin{assumption}
+\label{assumption:smooth}
+The coefficients  $\alpha(x)$ and $\delta(x)$ are assumed to be sufficiently smooth, i.e. bounded and continuous in  
+$\left[-L,\; H\right]$.
+\end{assumption}
+It can be ensured e.g. by requiring the continuity of $N_e(x), B_0(x) \in [-L,\;H]$ and the absence of the cyclotron resonance, i.e. for all $x$ $|\omega_c^2(x)-\omega^2(x)|>c>0$ on this interval. 
 }
+
+\begin{remark}
+For the time domain problem (\ref{eq:main_model}) the choice of the sign of $\nu>0$ is of crucial importance for the stability of the problem. 
+In the frequency domain, as we can see from above and from \cite{Despres_2014,LMIG_thesis}, the sign 
+of the parameter $\nu$ can be chosen arbitrarily to regularize the problem. However, as demonstrated in the above references, as $\nu\rightarrow 0\pm$, the 
+limiting solutions differ, though both exhibit the singularity in the point of the hybrid resonance.  
+\end{remark}
+%}
 
@@
 
-Let us denote the spectral radius of $\eps_0$ by $\heps =  \|\rho(\eps_0)\|_{L^\infty}$.
+\urev{
+Let us denote the spectral radius of $\eps_0$ by $\heps =  \|\rho(\eps_0)\|_{L^{\infty}[-L,\;H]}$. 
+By Assumption \ref{assumption:smooth}, the spectral radius $\heps=\max\left(\|\alpha+\delta^2\|_{L^{\infty}[-L,\;H]}, \|\alpha-\delta^2\|_{L^{\infty}[-L,\;H]}\right)$ 
+is bounded.}
 %\end{df}
@@
 \label{lemma:well_posedness}
-If $\heps<+\infty$, the bilinear form 
+Provided that Assumption \ref{assumption:smooth} holds, the bilinear form 
 \ben

### 2015-04-24 report_clean/intro.tex
+2 remarks taken into account

@@
 We consider the wave propagation in the cold plasma that consists of particles of single species 
-under a uniform in time background magnetic field $\mathbf{B}_0=(0,\;0,\; B_0)$. This process in 2D can be described by the time-dependent Maxwell system  \cite{Stix}
+under a uniform in time background magnetic field $\mathbf{B}_0=(0,\;0,\; B_0)$. In two dimensions, in the plane 
+perpendicular to the direction of the magnetic field, this process can be described by the time-dependent Maxwell system  \cite{Stix}
 \begin{align}
@@
 
-The energy of this system in a domain $\Omega\in\mathbb R^2$ in the case $\nu=0$ can be expressed as \cite{stable_yee_plasma_current}
+The energy of this system in a domain $\Omega\in\mathbb R^2$ can be expressed as, see \cite{Despres_2014}
 \ben
@@
 \frac{\epsilon_0 |\E(t,\mathbf{r})|^2}{2}+\frac{ |\B(t,\mathbf{r})|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|^2}{2|e|N_e(\mathbf{r})} 
-\right)\mathrm{d}\mathbf{r}.
+\right)\mathrm{d}\mathbf{r},
+\een
+and
+\ben
+\frac{d}{dt}{\mathcal E}=-\nu\left(\|u_{x}\|_{L_{2}(\Omega)}^2+\|u_{y}\|_{L_{2}(\Omega)}^2\right)+\text{boundary terms}.
 \een
@@
 \label{eq:model_freq_domain}
- \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\underline{\epsilon}^{0}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,
+ \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\underline{\varepsilon}^{0}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,
 \end{align}
@@
 \nonumber
-\underline{\epsilon}^{0}_{\omega}(\mathbf{r})=\left(
+\underline{\varepsilon}^{0}_{\omega}(\mathbf{r})=\left(
  \begin{matrix}
-  \alpha_{\omega}^{0}(\mathbf{r}) & i\delta_{\omega}^{0}(\mathbf{r})\\
-  -i\delta_{\omega}^{0}(\mathbf{r}) & \alpha_{\omega}^{0}(\mathbf{r})
+  \alpha_{\omega}(\mathbf{r})& i\delta_{\omega}(\mathbf{r})\\
+  -i\delta_{\omega}(\mathbf{r}) & \alpha_{\omega}(\mathbf{r})
  \end{matrix}
@@
 \label{eq:alpha_delta}
-\alpha_{\omega}^{0}(\mathbf{r})=1-\frac{\omega_p^2(\mathbf{r})}{\omega^2-\omega_c^2(\mathbf{r})},\; \delta_{\omega}^{0}(\mathbf{r})=\frac{\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})}{\omega(\omega^2-\omega_c^2(\mathbf{r}))}.
+\alpha_{\omega}(\mathbf{r})=1-\frac{\omega_p^2(\mathbf{r})}{\omega^2-\omega_c^2(\mathbf{r})},\; \delta_{\omega}(\mathbf{r})=\frac{\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})}{\omega(\omega^2-\omega_c^2(\mathbf{r}))}.
 \end{align}
@@
 $\omega_c(\mathbf{r}_c)=\omega$, i.e.
-when $\underline{\epsilon}_{\omega}^{0}(\mathbf{r})$ is singular, is called a cyclotron resonance (c.f.
+when $\underline{\varepsilon}_{\omega}^{0}(\mathbf{r})$ is singular, is called a cyclotron resonance (c.f.
 \cite[Chapter 1-5]{Stix}).
@@
 
-Another interesting case is $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$, when the diagonal part of the tensor $\underline{\epsilon}_{\omega}^{0}(\mathbf{r})$ vanishes, 
+Another interesting case is $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$, when the diagonal part of the tensor $\underline{\varepsilon}_{\omega}^{0}(\mathbf{r})$ vanishes, 
 under the condition that the non-diagonal part remains non-zero. This is a hybrid resonance case.
+
 As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component $E_x$ is not necessarily square 
@@
 \label{eq:seq_regularized}
-  \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\underline{\epsilon}^{\nu}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,\;
-  \underline{\epsilon}^{\nu}_{\omega}(\mathbf{r})= \underline{\epsilon}^{0}_{\omega}(\mathbf{r})+i\nu \mathbb{E},\; 
+  \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\underline{\varepsilon}^{\nu}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,\;
+  \underline{\varepsilon}^{\nu}_{\omega}(\mathbf{r})= \underline{\varepsilon}^{0}_{\omega}(\mathbf{r})+i\nu \mathbb{E},\; 
 \end{align}
-with $\nu\rightarrow 0$. 
+with $\nu\rightarrow 0$ and $\mathbb{E}$ being an identity matrix. 
 }
@@
 This is the model that will be considered in the rest of the article, unless stated otherwise. 
+\urev{
+Indeed, the dielectric tensor for this problem with $\nu=0$ and its coefficients $\alpha_{\omega},\;\delta_{\omega}$, 
+see \ref{eq:alpha_delta}, depend solely on $x$, $\omega$ and $\theta$.
 
+We concentrate on the physical situation of the hybrid resonance, which we define as in \cite{singular_solutions}.
+\begin{df}
+Let $\omega,\theta\in\mathbb{R}$ be fixed. 
+We will call a point $x_h\in \mathbb{R}$ a hybrid resonance if $\alpha_{\omega}$ has 
+a simple root in $x_h$ and has no other roots in an $\epsilon$-vicinity of $x_h$ $B_{\epsilon}(x_h)$, for some $\epsilon>0$. 
+\end{df}
+}
  %This domain represents the physical case of a wave sent from a wall facing a plasma.

### 2015-04-27 report_clean/responce_reviewers.tex
+multiple items changed

@@
 
-- abstract: changed
+- p1, abstract: changed
 
-- in the frequency domain, as we have shown in Lemma 2.1, the problem is regularized by a choice $|\nu|>0$, independently of the sign of $\nu$. 
+- p2: in the frequency domain, as we have shown in Lemma 2.1, the problem is regularized by a choice $|\nu|>0$, independently of the sign of $\nu$. 
 It is interesting however that for a fixed $\omega$ the limits $\lim_{\nu\rightarrow 0\pm}$ do not result in the same solution. 
@@
 
-- $L$ is just a non-negative number. We found it more convenient to place the point of the isolated hybrid resonance in $x=0$.
-For $\nu\neq 0$ the energy decays, we added this in the introduction
+- p2, after (1): $L$ is just a non-negative real number. We found it more convenient to place the point of the isolated hybrid resonance in $x=0$.
+For $\nu\neq 0$ the energy decays, we added this in the introduction.
+
+- p3: yes, indeed, fixed
+
+- p3 eq (4): the notation had been changed
+
+- p4, top: we changed the notation
+
+- p4, eq. (5) fixed
+
+- p4, eq. (8): changed the notation in eq (8), though a more general result in Lemma 2.1 is formulated with $u,v$.
+
+- p4: we changed $\alpha_{\nu}$ to $\beta_{\nu}$ not to confuse with $\alpha$ in the dielectric tensor. The index $\nu$ 
+just underlines the dependence of this angle $\beta_{\nu}$ on $\nu$.
+
+- p. 5: indeed, we changed this
+
+- p.6:  changed
+
+-p 6: $Ex$ changed
+
+-p 8: our code, changed
+
+ - p.8: fixed section number
+
  -

### 2015-04-27 report_clean/FD.tex
+multiple items changed

@@
 \right),\qquad 
- \alpha^{\nu}_{\omega}(\mathbf{r})=\frac{\omega^2}{c^2}\left(1-\frac{\omega_{\nu}\omega_p^2(\mathbf{r})}{\omega(\omega_{\nu}^2-\omega_c^2(\mathbf{r}))}\right),\qquad 
+ \alpha^{\nu}_{\omega}(\mathbf{r})=1-\frac{\omega_{\nu}\omega_p^2(\mathbf{r})}{\omega(\omega_{\nu}^2-\omega_c^2(\mathbf{r}))},\qquad 
 \delta^{\nu}_{\omega}(\mathbf{r})=\frac{\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})}{\omega(\omega_{\nu}^2-\omega_c^2(\mathbf{r}))},
@@
 $\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane.
-Note that neither cyclotron, nor hybrid resonances occur in the problem with the dielectric tensor $\epsilon^{\nu}_{\omega}(\mathbf{r}), \; \nu>0,$ (since all parameters are real).
+Note that neither cyclotron, nor hybrid resonances occur in the problem with the dielectric tensor $\varepsilon^{\nu}_{\omega}(\mathbf{r}), \; \nu>0,$ (since all parameters are real).
 Hence
@@
 where $\alpha_{\omega},\;\delta_{\omega}$ are defined by (\ref{eq:alpha_delta}). In the frequency domain one thus can consider 
-the following regularization of the cold plasma dielectric tensor of (\ref{eq:main_frequency_domain}):
+the following regularization of the cold plasma dielectric tensor of \mrev{the above problem}:
 \begin{align*}
@@
 \ben
-\epsilon^{\nu}_{\omega}(\mathbf{r})\approx \epsilon^{0}_{\omega}(\mathbf{r})+i\nu \mathbb{E}
+\varepsilon^{\nu}_{\omega}(\mathbf{r})\approx \varepsilon^{0}_{\omega}(\mathbf{r})+i\nu \mathbb{E}
 \een
@@
 
-Thus, applying the above process to (\ref{eq:main_model}), we obtain, see also \cite{Despres_2014},
+Thus, applying the above process to (\ref{eq:main_model}) in the frequency domain, we obtain, see also \cite{Despres_2014},
 \begin{align}
@@
 \right)-\frac{\omega^2}{c^2}
-\left(\epsilon^{0}_{\omega}(x)+\nu \mathbb{E}\right)\left(
+\left(\varepsilon^{0}_{\omega}(x)+i\nu \mathbb{E}\right)\left(
 \begin{matrix}
@@
 \label{eq:epsilon_0}
-\epsilon^0_{\omega}(x)=\left(
+\varepsilon^0_{\omega}(x)=\left(
 \begin{matrix}
@@
 \end{matrix}
-\right).
+\right)=\varepsilon^{0}(x).
 \end{align}
@@
 \end{assumption}
-It can be ensured e.g. by requiring the continuity of $N_e(x), B_0(x) \in [-L,\;H]$ and the absence of the cyclotron resonance, i.e. for all $x$ $|\omega_c^2(x)-\omega^2(x)|>c>0$ on this interval. 
+This assumption can be ensured, for example, by requiring the continuity of $N_e(x), B_0(x) \in [-L,\;H]$ and the absence of the cyclotron resonance, i.e.
+for all $x$ $|\omega_c^2(x)-\omega^2(x)|>c>0$ on this interval.
 }
@@
 %%%%%%%%%%%%%%%%%%%%%% 
-\subsection{1D case}
+\mrev{\subsection{Well-Posedness of the Frequency Domain Problem}}
 %%%%%%%%%%%%%%%%%%%%%% 
@@
 
-In order to reduce problem \eqref{eq:main_frequency_domain} to one dimension, perform a Fourier transform in the $y$ variable, 
-denoting by $\theta$ the corresponding Fourier variable. 
+%In order to reduce problem \eqref{eq:main_frequency_domain} to one dimension, perform a Fourier transform in the $y$ variable, 
+%denoting by $\theta$ the corresponding Fourier variable. 
+\mrev{In this section we study the well-posedness of the problem (\ref{eq:main_frequency_domain}) with the help of Lax-Milgram lemma.} 
 After introducing $\Omega=(-L,\; H)\subset \mathbb R$ and defining the function space of the problem  $\mathbf{V}=L^{2}(\Omega)\times H^{1}(\Omega)$, 
@@
 \begin{array}{l}
-\displaystyle \int_{-L}^H (E_y' -\imath\theta E_x)\overline{(\tilde E_y' -\imath \theta \tilde E_x)} - \int_{-L}^H (\eps_0 +\imath\nu Id) \E \cdot \overline{\tilde \E}
+\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\tilde E_y' -i \theta \tilde E_x)} - \int_{-L}^H (\varepsilon^{0} +i\nu Id) \E \cdot \overline{\tilde \E}
 %\\ \displaystyle 
- - \imath \lambda E_y (-L)\overline{ \tilde E_y (-L)} = -g_{inc} (-L) \overline{( \tilde E_y(-L) )},
+ - i \lambda E_y (-L)\overline{ \tilde E_y (-L)} = -g_{inc} (-L) \overline{( \tilde E_y(-L) )},
 \end{array}\\
@@
 \be
-a\left(\mathbf{u},\mathbf{v}\right)=l(\mathbf{v}), \; \text{ for all }\mathbf{v}\in \mathbf{V},
+a\left(\mathbf{E},\mathbf{v}\right)=l(\mathbf{v}), \; \text{ for all }\mathbf{v}\in \mathbf{V},
 \ee
@@
 \be
-a(\ubf,\vbf) = a_1 (\ubf,\vbf) +\imath a_2(\ubf,\vbf)\  \text{ and } \  l(\vbf) = -g_{inc} (-L) \overline{(v_2(-L) )} 
+a(\ubf,\vbf) = a_1 (\ubf,\vbf) +i a_2(\ubf,\vbf)\  \text{ and } \  l(\vbf) = -g_{inc} (-L) \overline{(v_2(-L) )} 
 \ee
@@
 \left\{\begin{array}{l}
-	a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -\imath\theta u_1)\overline{(v_2' -\imath \theta v_1)} - \int_{-L}^H \eps_0 \ubf\cdot \overline{\vbf}, 
+	a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -i\theta u_1)\overline{(v_2' -i \theta v_1)} - \int_{-L}^H \varepsilon^{0} \ubf\cdot \overline{\vbf}, 
 	\\ a_2(\ubf,\vbf) = -\nu \int_{-L}^H  \ubf\cdot \overline{\vbf} - \lambda u_2 (-L) \overline{v_2 (-L)} , 
@@
 \ee
-The unknown is $\ubf=(E_x,E_y)=(u_1,u_2)$ and $\vbf$ is a test function.
+The unknown is $\mathbf{E}=(E_x,E_y)$ and $\vbf$ is a test function.
 
 \urev{
-Let us denote the spectral radius of $\eps_0$ by $\heps =  \|\rho(\eps_0)\|_{L^{\infty}[-L,\;H]}$. 
+Let us denote the spectral radius of $\varepsilon^{0}$ by $\heps =  \|\rho(\varepsilon^{0})\|_{L^{\infty}[-L,\;H]}$. 
 By Assumption \ref{assumption:smooth}, the spectral radius $\heps=\max\left(\|\alpha+\delta^2\|_{L^{\infty}[-L,\;H]}, \|\alpha-\delta^2\|_{L^{\infty}[-L,\;H]}\right)$ 
@@
 \left\{\begin{array}{l}
-\Re\left(\mathrm{e}^{i\alpha_{\nu}}a(\ubf,\ubf)\right)\geq \frac{|\nu|}{\sqrt{(\heps+\theta^2+1)^2+\nu^2}}\left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right),\; 
-\text{ for some $\alpha_{\nu}\in\left(-\frac{\pi}{2}, 0\right)\cup \left(0,\frac{\pi}{2}\right)$},\\
+\Re\left(\mathrm{e}^{i\beta_{\nu}}a(\ubf,\ubf)\right)\geq \frac{|\nu|}{\sqrt{(\heps+\theta^2+1)^2+\nu^2}}\left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right),\; 
+\text{ for some $\beta_{\nu}\in\left(-\frac{\pi}{2}, 0\right)\cup \left(0,\frac{\pi}{2}\right)$},\\
 |a(\ubf,\vbf)|\leq C \|\ubf\|_{\mathbf{V}}\|\vbf\|_{\mathbf{V}},
@@
 	one  $H_1(\Omega)\subset C^0(\overline \Omega)$. Let us focus on the proof of coercivity. 
-	Without loss of generality let us assume that $\nu>0$. We denote $\heps =  \|\rho(\eps_0)\|_{L^\infty}$, the spectral radius of $\eps_0$ so that
-	$\heps Id- \eps_0 $ is a non negative hermitian matrix.
+	Without loss of generality let us assume that $\nu>0$. We denote $\heps =  \|\rho(\varepsilon^{0})\|_{L^\infty}$, the spectral radius of $\varepsilon^{0}$ so that
+	$\heps Id- \varepsilon^{0} $ is a non negative hermitian matrix.
 	Therefore
 	\be 
-	a_1(\ubf,\ubf) + \heps\|\ubf\|^2_{L^2}= \|u_2' - \imath \theta u_1 \|^2_{L^2} + \left( (\heps Id - \eps_0 ) \ubf, \overline{\ubf} \right)  \geq \|u_2 ' - \imath \theta u_1 \|_{L^ 2}^ 2
+	a_1(\ubf,\ubf) + \heps\|\ubf\|^2_{L^2}= \|u_2' - i \theta u_1 \|^2_{L^2} + \left( (\heps Id - \varepsilon^{0} ) \ubf, \overline{\ubf} \right)  \geq \|u_2 ' - i \theta u_1 \|_{L^ 2}^ 2
 	\geq \frac12 \|u_2 '  \|_{L^ 2}^ 2 -
@@
 	\een
-	or, introducing $\alpha_{\nu}=\arccos\frac{1}{\sqrt{1+\left(\heps+\theta^2+1\right)^2\nu^{-2}}}$, this is equivalent to 
+	or, introducing $\beta_{\nu}=\arccos\frac{1}{\sqrt{1+\left(\heps+\theta^2+1\right)^2\nu^{-2}}}$, this is equivalent to 
 	\ben
-	\Re\left(\mathrm{e}^{i\alpha_{\nu}}a(\ubf,\ubf)\right)\geq 
+	\Re\left(\mathrm{e}^{i\beta_{\nu}}a(\ubf,\ubf)\right)\geq 
 	\frac{1}{\sqrt{1+\left(\heps+\theta^2+1\right)^2\nu^{-2}}} \left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right)\\
@@
 The above proof is not optimal in the case when $\left|\alpha(x)\right|>c>0$ for $c>0$ on the whole interval $[-L,\; H]$, at least 
-for the case $\theta=0$. In this case the problem (\ref{eq:var_form2}) is well-posed for $\nu=0$. More precisely, it can be written 
+for the case $\theta=0$. In this case the problem (\ref{eq:var_form2}) is well-posed for $\nu=0$. \mrev{More precisely, it can be written 
 as a system of two equations, where the first equation (for $E_y$) is the variational formulation for the Helmholtz equation 
-with the variable coefficient $k^2=(\alpha(x)-\frac{\delta^2}{\alpha(x)})$, and the second equation 
+with the variable coefficient $k^2=(\alpha-\frac{\delta^2}{\alpha})$, and the second equation 
 \begin{align*}
-  \left(E_x,u\right)=-\left(\frac{i\delta}{\alpha(x)}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega), 
+  \left(E_x,u\right)=-\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega), 
 \end{align*}
-uniquely defines $E_x\in L^{2}(\Omega)$. The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
+uniquely defines $E_x\in L^{2}(\Omega)$. }The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
 was demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H^{1}(\Omega)$, we can obtain $E_x$ from the second equation.
@@
 %%\displaystyle \int_{-L}^H E_y'\tilde {E_y'} - \int_{-L}^H\left( -i\delta E_x+\alpha E_y \right)_{2}\overline{\tilde{E}}_{y}
-%%  - \imath \lambda E_y (-L) \overline{\tilde E_y} (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
+%%  - i \lambda E_y (-L) \overline{\tilde E_y} (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
 %%  \text{ for all }  \tilde{E}_{y}\in H^{1}(\Omega).
@@
 %% \displaystyle \int_{-L}^H E_y'\tilde {E_y'} - \int_{-L}^H (\alpha-\frac{\delta^2}{\alpha})E_y \overline{\tilde{E}}_{y}
-%%  - \imath \lambda E_y (-L) \overline{\tilde E_y} (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
+%%  - i \lambda E_y (-L) \overline{\tilde E_y} (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
 %%  \text{ for all } \tilde{E}_{y}\in H^{1}(\Omega). \nonumber
@@
 %\begin{array}{l}
-%\displaystyle \int_\Omega curl \E \cdot \overline{curl \tilde \E} - \int_\Omega (\eps_0+i\nu Id) \E \cdot \overline{\tilde \E} - \int _{\{x=-L\}} \imath \sqrt{\alpha(-L)}(\E\wedge \n) \overline{\left( \tilde \E\wedge \n \right)} d\sigma
+%\displaystyle \int_\Omega curl \E \cdot \overline{curl \tilde \E} - \int_\Omega (\varepsilon^{0}+i\nu Id) \E \cdot \overline{\tilde \E} - \int _{\{x=-L\}} i \sqrt{\alpha(-L)}(\E\wedge \n) \overline{\left( \tilde \E\wedge \n \right)} d\sigma
 %\\ \displaystyle \phantom{ fffffffff}= \int_{\{x=-L\}} g_{inc}  \overline{\left( \tilde \E\wedge \n \right)} d\sigma
@@
 %\begin{split}
-%i\theta \displaystyle \int_{-L}^H (E_y' -\imath\theta E_x)\overline{\tilde E_x} - \int_{-L}^H \left((\epsilon_0 +\imath\nu \operatorname{Id}) \E\right)_{1} \overline{\tilde E}_{x}
+%i\theta \displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{\tilde E_x} - \int_{-L}^H \left((\epsilon_0 +i\nu \operatorname{Id}) \E\right)_{1} \overline{\tilde E}_{x}
 %&=0,\\
-%\displaystyle \int_{-L}^H (E_y' -\imath\theta E_x)\tilde {E_y'} - \int_{-L}^H\left( (\epsilon_0 +\imath\nu\operatorname{Id}) \E\right)_{2}\overline{\tilde{E}}_{y}
-%  - \imath \lambda E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
+%\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\tilde {E_y'} - \int_{-L}^H\left( (\epsilon_0 +i\nu\operatorname{Id}) \E\right)_{2}\overline{\tilde{E}}_{y}
+%  - i \lambda E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
 %  \text{ for all } \tilde E_x\in L^{2}(\Omega), \; \tilde{E}_{y}\in H^{1}(\Omega).
@@
 \begin{split}
- i\theta \displaystyle \int_{-L}^H (E_y' -\imath\theta E_x)\overline{\tilde E_x} - 
- \int_{-L}^H \left((\alpha+i\nu)E_x+\imath\delta E_y\right)_{1} \overline{\tilde E}_{x}
+ i\theta \displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{\tilde E_x} - 
+ \int_{-L}^H \left((\alpha+i\nu)E_x+i\delta E_y\right)_{1} \overline{\tilde E}_{x}
 &=0,\\
-\int_{-L}^H (E_y' -\imath\theta E_x)\tilde {E_y'} -
-\int_{-L}^H\left( -\imath \delta E_x+(\alpha+i\nu) E_y\right)_{2}\overline{\tilde{E}}_{y}
-  - \imath \lambda E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
+\int_{-L}^H (E_y' -i\theta E_x)\tilde {E_y'} -
+\int_{-L}^H\left( -i \delta E_x+(\alpha+i\nu) E_y\right)_{2}\overline{\tilde{E}}_{y}
+  - i \lambda E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
  \text{ for all } \tilde E_x\in L^{2}(\Omega), \; \tilde{E}_{y}\in H^{1}(\Omega).
@@
 \end{align}
-Let us introduce two basis function spaces $V_{E_x}=\{\psi_{j}\}_{j=1}^{N_{1}}$ and $V_{E_{y}}=\{\phi_{i}\}_{i=1}^{N_{2}}$. 
+\urev{Let us introduce two function spaces $V_{E_x}\subset L_{2}(\Omega)$ spanned by the basis function set $\{\psi_{j}\}_{j=1}^{N_{1}}$ and $V_{E_{y}}\subset H_{1}(\Omega)$ spanned by 
+the set $\{\phi_{i}\}_{i=1}^{N_{2}}$. }
 %We look for the solution of the problem (\ref{eq:var_form2}) in the form:
@@
 \een
-This expression greatly simplifies when choosing $V_{E_x}=V_{E_{y}}=\left(\phi_{m}\right)_{m=1}^{N_{2}}$ and
-in the case $\theta=0$. One obtains the matrix structure
+This expression greatly simplifies when \mrev{ choosing $V_{E_x}=V_{E_{y}}$, spanned by $\left(\phi_{m}\right)_{m=1}^{N_{2}}$,} and
+in the case $\theta=0$. One obtains the \mrev{matrix} structure
 \begin{align}

### 2015-04-27 report_clean/numerics.tex
+multiple items changed

@@
 of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
-performed with the help of the code written in Octave.  
+performed with the help of \mrev{our} code written in Octave.  
 We implemented the scheme described in Section \ref{sec:discr} for a case of $P_{1}$-space used 
@@
 and of the time domain code (computed for large values of time). 
-The time-domain code implements the scheme described in Section \ref{sec:discr} and 
+The time-domain code implements the scheme described in \mrev{Section \ref{sec:staggered_discretization}} and 
 is written in Fortran.
@@
 \label{eq:parameters}
-\alpha(x)=x^2+1,\qquad \delta(x)=\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}.
+\alpha(x)=x^2+1,\qquad \delta(x)=\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}, \qquad \mrev{\nu=0}.
 \end{align}
+\mrev{As we remark a bit further, such a choice of parameters for the problem (\ref{eq:main_frequency_domain}) with $\theta=0$ will allow 
+us to obtain the solution in the analytic form}.
 Additionally, the boundary conditions read as 
@@
 \label{eq:bcs_airy}
-\partial_{1}E_{y}(-L)+2iE_{y}(-L)=2iAi(-L)+Ai'(-L),\qquad 
+\partial_{1}E_{y}(-L)+2iE_{y}(-L)=2i\Ai(-L)+\Ai'(-L),\qquad 
 \partial_{1}E_{y}(H)=0,
 \end{align}
-where $Ai(x)$ is the Airy function. 
+where $\Ai(x)$ is the Airy function. 
 For more detail on Airy functions and the Airy equation see \cite[Chapter 10.4]{abramowitz_stegun}. 
@@
 $
-E_{y}=Ai(x)  $  and   %,\qquad 
-$E_{x}=-i\frac{\delta(x)}{\alpha(x)}Ai(x)$
+E_{y}=\Ai(x)  $  and   %,\qquad 
+$E_{x}=-i\frac{\delta(x)}{\alpha(x)}\Ai(x)$
 is the solution to the problem with parameters (\ref{eq:parameters}) and the boundary condition (\ref{eq:bcs_airy}). 

### 2015-04-27 report_clean/timedomain.tex
bruno's changes
fixed mistakes
small issues
+multiple items changed

@@
 \subsection{A staggered scheme}
+\label{sec:staggered_discretization}
 In this section, we develop a discretization of the time dependant problem~\eqref{eq:main_model} 
@@
 We summarize this discretization on Fig.~\ref{schemepos} where the positions 
-of $Ex$, $u_x$ (black dots), $E_y$, $u_y$ (blue dots) and $H_z$ (red dots) 
+of \mrev{$E_x$}, $u_x$ (black dots), $E_y$, $u_y$ (blue dots) and $H_z$ (red dots) 
 on the discretized grid in space and time are shown. The fully discretized system then reads
@@
 	\begin{center}
+ \scalebox{1.2}{
 		\begin{tikzpicture}
@@
 		\coordinate (Origin)   at (0,0);
-		\node (xlab) at (2.5,-0.5){\tiny $x$};
-		\node (tlab) at (-0.5,2.5){\tiny $t$};
+		\node (xlab) at (2.5,-0.5){\small $x$};
+		\node (tlab) at (-0.5,2.5){\small $t$};
 		%      \node[black] (exux) at (2.6,1){\tiny $E_x$, $u_x$};
@@
 		\end{tikzpicture} 
-		%	\label{schemepos}
+}
 	\end{center}
-	\caption{Positions of $E_x$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) on the discretized grid in space and time}
+	\caption{Positions of $E_x$, $u_x$ (black dots), $E_y$, $u_y$ (blue dots) and $H_z$ (red dots) on the discretized grid in space and time}
 
@@
 m_e\partial_t u_x=0,\\
-m_e\partial_t u_y=0,
+m_e\partial_t u_y=0.
 \end{array}

### 2015-04-27 report_clean/FD.tex
+multiple extra remarks

@@
 \end{matrix}
-\right)=
+\right). 
+\end{align}
+\mrev{
+We consider the following generalized model of the above system
+\begin{align}
+\label{eq:main_frequency_domain_general}
 \left(
+\begin{matrix}
+ i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
+ i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
+\end{matrix}
+\right)-
+\left(\varepsilon^{0}(x)+i\nu \mathbb{E}\right)\left(
+\begin{matrix}
+ \hat{E}_x\\
+ \hat{E}_y
+\end{matrix}
+\right)
+=0,\\
+\varepsilon^{0}(x)=\left(
 \begin{matrix}
@@
 \end{matrix}
-\right)=\varepsilon^{0}(x).
+\right).
 \end{align}
@@
 %denoting by $\theta$ the corresponding Fourier variable. 
-\mrev{In this section we study the well-posedness of the problem (\ref{eq:main_frequency_domain}) with the help of Lax-Milgram lemma.} 
+\mrev{In this section we study the well-posedness of the problem (\ref{eq:main_frequency_domain_general}) with the help of Lax-Milgram lemma.} 
 After introducing $\Omega=(-L,\; H)\subset \mathbb R$ and defining the function space of the problem  $\mathbf{V}=L^{2}(\Omega)\times H^{1}(\Omega)$, 

### 2015-04-27 report_clean/numerics.tex
+multiple extra remarks

@@
 This section is organized as follows. The first part is dedicated to the numerical implementation
-of the frequency domain formulation \eqref{eq:main_frequency_domain}. We study the convergence of this formulation and the behaviour 
+of the frequency domain formulation \eqref{eq:main_frequency_domain_general}. We study the convergence of this formulation and the behaviour 
 of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
@@
 \end{align}
-\mrev{As we remark a bit further, such a choice of parameters for the problem (\ref{eq:main_frequency_domain}) with $\theta=0$ will allow 
-us to obtain the solution in the analytic form}.
-Additionally, the boundary conditions read as 
+\mrev{It can be shown that $E_{y}$ that solves \mrev{(\ref{eq:main_frequency_domain_general})} in 1D, with the Fourier variable $\theta=0$ (see (\ref{vf1dcase}), 
+and $\nu=0$, satisfies the Airy equation, see also Remark \ref{remark:other},
+\begin{align*}
+ E_y''-xE_y=0,\qquad x\in [-L,\; H].
+\end{align*}
+One of the solutions of this equation, an Airy function $\Ai(x)$, see \cite[Chapter 10.4]{abramowitz_stegun}, decays rapidly as $x\rightarrow \infty$. 
+Hence, choosing $H$ sufficiently large \mrev{TODOOO(the actual value used in the experiments $H=10$)} and the boundary conditions as 
 \begin{align}
@@
 \partial_{1}E_{y}(-L)+2iE_{y}(-L)=2i\Ai(-L)+\Ai'(-L),\qquad 
-\partial_{1}E_{y}(H)=0,
+\partial_{1}E_{y}(H)=0\approx Ai(H),
 \end{align}
-where $\Ai(x)$ is the Airy function. 
-For more detail on Airy functions and the Airy equation see \cite[Chapter 10.4]{abramowitz_stegun}. 
-It can be shown that $E_{y}$ that solves (\ref{eq:main_frequency_domain}) in 1D, with the Fourier variable $\theta=0$ (see (\ref{vf1dcase}), and $\nu=0$, 
-satisfies the Airy equation, and hence, 
-with the choice of the boundary conditions as above, we obtain that 
-$
-E_{y}=\Ai(x)  $  and   %,\qquad 
-$E_{x}=-i\frac{\delta(x)}{\alpha(x)}\Ai(x)$
-is the solution to the problem with parameters (\ref{eq:parameters}) and the boundary condition (\ref{eq:bcs_airy}). 
-The well-posedness of the respective variational formulation for $\nu=0$ is due to Remark \ref{remark:other}.
+where $\Ai(x)$ is an Airy function, we ensure that $E_{y}$ that solves the above problem is well approximated by $\Ai(x)$, and $E_{x}$ by $-i\frac{\delta(x)}{\alpha(x)}\Ai(x)$. 
+The well-posedness of the respective variational formulation for $\nu=0$ is due to Remark \ref{remark:other}. }
 
 In Fig.~\ref{fig:conv_rate} we demonstrate the convergence rates for this problem, comparing the solution with the 
-known analytic solution. Importantly, the obtained convergence rates are in agreement with known estimates of the standard theory of convergence~\cite{brenner}.
+known analytic solution. \mrev{TODO:We can expect the solution to be smooth, due to the smoothness of the coefficients of the problem}.
+Importantly, the obtained convergence rates are in agreement with known estimates of the standard theory of convergence~\cite[Chapter 5.7,
+Chapter 0.4]{brenner}.  
 \begin{figure}

### 2015-04-29 report_clean/responce_reviewers.tex
+multiple extra remarks
final changes. To-Do: more changes

@@
 
- -
+ - p.8 eq (12): added $\nu=0$ + explanation
+
+ - p.8: added the Airy equation. Additionally added a remark on the behaviour of the Airy function to justify the choice of the right boundary 
+ condition $\partial_x E=0$.
+
+ -  p9, Figure 3: fixed the captions. This had been done for other figures as well. The values $E^{c}_{x,y}$ had been defined in the caption.
+
+ -p9 on top
+  The title of Section 4.1.2 had been changed to Solution of a Frequency-Domain Problem with Resonance
+
+ - p9 Equation (15,16): changed
+
+ - p9 after (17): we would like to assume that it is $H^2$-norm that is bounded, for using the inequality (19). 
+  \mrev{TODO: While this assumption is fairly strong, it is not unsubstantial: for sufficiently smooth $\alpha,\delta$,  }
+
+ - p10 before and after Table 1 : fixed
+
+ -- p11 Figure 5:
+Agree, fixed. We added a remark in a caption to Figure 4 as well.
+
+- p12 Section 4.3: this explanation had been moved to the introduction
+
+- p12 Section 4.3.1
+
+  It is true, but in this case there is no resonance, since $\delta(x)\equiv 0$. Hence $E_x=-\frac{i\delta}{\alpha}E_y\equiv 0$, 
+  and $E_y$ solves the Airy equation in the frequency domain. We added a small to Section 4.3.1 to underline this.
+
+- p12 Equation (23)
+We changed it to $e$
+
+- p14 Figures 8 and 9
+Added the captions  
+- p15 in Conclusion
+  Indeed $P1$!
+
+ Reviewer 2:
+
+ • p2: In this case Ex is not square integrable: confirm that it is when ν is not zero and that
+the singularity appears for ν = 0.
+
+We tried to change the wording in the introduction to make it more clear what is a hybrid resonance. 
+The singularity appears for $\nu=0$, when the diagonal part of the dielectric tensor vanishes and non-diagonal part does not.
+
+• p6, 3.1. It is not clear how the Yee scheme, which is a finite difference scheme, is linked to the
+finite element scheme developed in the previous section. This should be made more explicit.
+
+We employed the Yee scheme to discretize the problem in the time domain, and the finite element scheme solely for the frequency domain, 
+and considered them independently. We added a remark on that in the very beginning of Section 3.
+
+• p10: mesh multiple times finer. It should be said exactly how many times.
+
+We added a remark that it was at least two times for very fine meshes, and more for coarser ones.
 

### 2015-04-29 report_clean/numerics.tex
final changes. To-Do: more changes

@@
 \label{eq:parameters}
-\alpha(x)=x^2+1,\qquad \delta(x)=\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}, \qquad \mrev{\nu=0}.
+\alpha(x)=x^2+1,\qquad \delta(x)=\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}, \qquad \mrev{\nu=0, \qquad \theta=0.}
 \end{align}
-\mrev{It can be shown that $E_{y}$ that solves \mrev{(\ref{eq:main_frequency_domain_general})} in 1D, with the Fourier variable $\theta=0$ (see (\ref{vf1dcase}), 
+\mrev{It can be shown that $E_{y}$ that solves (\ref{eq:main_frequency_domain_general}) in 1D, with the Fourier variable $\theta=0$ (see (\ref{vf1dcase}), 
 and $\nu=0$, satisfies the Airy equation, see also Remark \ref{remark:other},
@@
 \end{align*}
-One of the solutions of this equation, an Airy function $\Ai(x)$, see \cite[Chapter 10.4]{abramowitz_stegun}, decays rapidly as $x\rightarrow \infty$. 
-Hence, choosing $H$ sufficiently large \mrev{TODOOO(the actual value used in the experiments $H=10$)} and the boundary conditions as 
+One of the solutions of this equation, an Airy function $\Ai(x)$, see \cite[Chapter 10.4]{abramowitz_stegun}, is analytic and decays rapidly as $x\rightarrow \infty$. 
+Hence, choosing $H$ sufficiently large \mrev{TODOOO(the actual value used in the experiments $H=10$, where $\Ai'(10)\approx -3.5e-10$)} and the boundary conditions as 
 \begin{align}
@@
 \partial_{1}E_{y}(-L)+2iE_{y}(-L)=2i\Ai(-L)+\Ai'(-L),\qquad 
-\partial_{1}E_{y}(H)=0\approx Ai(H),
+\partial_{1}E_{y}(H)=0\approx \Ai'(H),
 \end{align}
@@
     \end{tikzpicture}
-    \caption{Convergence rates for the problem with parameters (\ref{eq:parameters}) with the boundary condition (\ref{eq:bcs}).}
+    \caption{Convergence rates for \mrev{the problem (\ref{eq:main_frequency_domain}) discretized as (\ref{eq:simple_system})} 
+    with the parameters (\ref{eq:parameters}) and the \mrev{boundary condition (\ref{eq:bcs_airy})}. \mrev{Here $E_{y}^{c}(x)=\Ai(x)$ and 
+    $E_{x}^{c}(x)=-i\frac{\delta(x)}{\alpha(x)}\Ai(x)$.} }
     \label{fig:conv_rate}
 \end{figure}
-\subsubsection{Solution of $X$-Mode Problem}
+\subsubsection{Solution of a Frequency-Domain Problem with Resonance}
 %\paragraph{Convergence}
@@
 Given $\mathbf{V}_{h}=P_{h}^{1}\times P_{h}^{1}$, with $P_{h}^{1}$ consisting of piecewise-linear (hat) functions, 
+\mrev{and $E^{\nu}_{x},\;E^{\nu,h}_{x}$ being correspondingly the exact solution and the solution computed with the help $\mathbf{V}_h$, }
 we look for a ratio $h(\nu)$ that would ensure the bound on the absolute error 
@@
 \begin{itemize}
- \item The C\'ea's lemma applied to the problem (\ref{vf1dcase}); here $C_c$ is the continuity and $C_i$ is the coercivity constants:
+ \item The C\'ea's lemma applied to the problem (\ref{vf1dcase}); here \mrev{$\mathbf{E}^{\nu}$ is the exact solution, 
+ $\mathbf{E}^{\nu,h}$ is the computed solution}, and $C_c$ is the continuity and $C_i$ is the coercivity constants:
 \begin{align}
@@
 \begin{split}
- \|\mathbf{E}^{\nu}-\mathbf{E}^{h,\nu}\|_{V}\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V}
- \leq C\nu^{-1}\min_{\mathbf{v}\in V_h}\|\mathbf{E}-\mathbf{v}\|_{V},\; C>0.
+ \|\mathbf{E}^{\nu}-\mathbf{E}^{\nu,h}\|_{V}\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}^{\nu}-\mathbf{v}\|_{V}
+ \leq C\nu^{-1}\min_{\mathbf{v}\in V_h}\|\mathbf{E}^{\nu}-\mathbf{v}\|_{V},\; C>0.
  \end{split}
@@
 
-For $E_x^{\nu},\; f^{\nu}(x)$ in (\ref{eq:exact}) being sufficiently smooth, 
+For $E_x^{c,\nu},\; f^{\nu}(x)$ in (\ref{eq:exact}) being sufficiently smooth, 
 \ben
@@
 Let us check numerically whether this holds true. 
-To do so, we conduct the  numerical experiment with parameters for the problem as given in Table \ref{tab:parameters}.
+To do so, we conduct the  numerical experiment with parameters for the problem (\ref{eq:main_frequency_domain} as given in Table \ref{tab:parameters}.
 \begin{table}[htb!]
@@
 \end{table}
-Denoting by $E_{x}^{h}$ the solution $E_{x}(x)$ computed on the mesh with a width $h$, and by $E_{x}^{c}$ the solution computed on a mesh multiple times finer, let 
+\mrev{Recall that we choose $\theta=0$. }
+Denoting by \mrev{$E_{x}^{\nu,h}$ the solution $E_{x}(x)$} computed on the mesh with a \mrev{ width $h$ with 
+the absorption $\nu$, and by $E_{x}^{\nu}$} the solution computed on a mesh multiple times finer (\mrev{more precisely, the reference mesh
+was typically 10-20 times finer, with the exception when the computation was done for very small values of $h$ where twice finer meshes for comparison were used}), let 
 \begin{align}
 \label{eq:def_epsilon}
-h_{\epsilon}=\sup\{h: \|E_{x}^{h'}-E_{x}^{c}\|<\epsilon \text{ for all } h'<h\}.
+h_{\epsilon}=\sup\{h: \|E_{x}^{\nu,h'}-E_{x}^{\nu}\|<\epsilon \text{ for all } h'<h\}.
 \end{align}
@@
 \end{tabular}
-\caption{In the left figure the dependence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated. 
-In the right figure we show the computed solutions for the problem with parameters in Table \ref{tab:parameters} for different values of $\nu$. }
+\caption{We consider the problem (\ref{eq:main_frequency_domain}) with the parameters 
+defined in Table \ref{tab:parameters}. In the left figure the dependence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated.  
+In the right figure we show the computed solutions for this problem (\mrev{for brevity denoted as $E_{x,y}^{\nu}$}) for different values of $\nu$. }
 \label{fig:dependence}
@@
 \eealn
- is ensured by choosing $h$ as $\beta_{\epsilon}\nu^{\frac{3}{4}}$.
+ is ensured by choosing $h$ as $\beta_{\epsilon}\nu^{\frac{3}{4}}$, \mrev{$\beta_{\epsilon}>0$.}
 \end{remark}
@@
  \caption{
- The left plot demonstrates the dependence of the condition number of the system (\ref{eq:simple_system}) on $\nu$, for different values of $h$ (the condition 
+ We consider the problem (\ref{eq:main_frequency_domain}) with the parameters 
+defined in Table \ref{tab:parameters}. The left plot demonstrates the dependence of the condition number of the system (\ref{eq:simple_system}) on $\nu$, for different values of $h$ (the condition 
  number for $\nu=0$ is not shown, however, for all values of $h$ as shown in the plot, the matrix was non-singular even for $\nu=0$). 
- The right plot shows $E_{y}^{\nu}$ computed on different meshes for small $\nu$. It can be seen that for $h=10^{-2}$ and $h=10^{-3}$ the solutions 
+ The right plot shows \mrev{$E_{y}^{\nu,h}$} computed on different meshes for small $\nu$. It can be seen that for $h=10^{-2}$ and $h=10^{-3}$ the solutions 
  computed for $\nu=0$ are almost indistinguishable.}

### 2015-04-29 report_clean/timedomain.tex
final changes. To-Do: more changes

@@
 \section{Time Dependent Problem Discretization}
-Let us consider the system (\ref{eq:main_model}) in dimension one in the X-mode configuration which is transverse electric.
+\mrev{
+In this section we develop the discretization of the time-dependent one-dimensional model (\ref{eq:main_model}), for a particular case $\theta=0$. 
+In the first part of this section we show how this system can be discretized with the help of 
+a version of the Yee scheme suggested in \cite{stable_yee_plasma_current}, and in the second part a scheme based on semi-lagrangian discretization is employed.}
 \subsection{A staggered scheme}
@@
 % \end{align}
-We compute a numerical approximation of~\eqref{eq:main_model} on a cartesian grid using the Yee scheme, 
+We compute a numerical approximation of~\eqref{eq:main_model} \mrev{with $\theta=0$} on a cartesian grid using the Yee scheme, 
 as suggested in \cite{stable_yee_plasma_current}. Let $n$ denote the time step index, as usual $t_n = n \Delta t$. 

### 2015-04-30 report_clean/abstract.tex
small issues
p.1 -> we focus on
+2 remarks taken into account
abstract: fixed

--- 2015-01-29 report/abstract.tex
@@
 that appears for example in the heating of plasma,
-and as such is of scientific interest in the development  of  the ITER project.
-In this paper we focus some solutions with low regularity of Maxwell equations in
-plasmas under strong background magnetic field.
-Our purpose is two-fold.
-On one hand we investigate the finite element approximation of the one dimensional problem 
-written in the frequency domain, and on the other hand we investigate two different 
-finite difference approximations of the one dimensional time dependent problem.
-We will also compare the results of these different methods.
+and as such is of scientific interest for the development  of  the ITER project.
+In this paper \urev{we focus on} solutions of low regularity to Maxwell equations in
+\mrev{magnetized plasmas}. 
+Our main purpose is two-fold. First, we aim at the investigation of the finite element approximation 
+of the frequency-domain problem. Second, we would like to study the resonant solutions 
+in the time domain, with the help of two different finite difference approximations, 
+and compare the results with the ones obtained in the frequency domain. This is done by  
+numerical examination of the limiting absorption and limited amplitude principles.

### 2015-04-30 report_clean/numerics.tex
fixed a major bug

@@
 This section is organized as follows. The first part is dedicated to the numerical implementation
-of the frequency domain formulation \eqref{eq:main_frequency_domain_general}. We study the convergence of this formulation and the behaviour 
+of the frequency domain formulation \eqref{eq:main_frequency_domain}. We study the convergence of this formulation and the behaviour 
 of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
@@
 The last part of the section deals with the question of the equivalence of the limiting absorption and limited amplitude 
-principle. We compare the solutions obtained as $\nu\rightarrow 0$ with the help of our frequency domain code 
-and of the time domain code (computed for large values of time). 
+principle. We compare the solutions obtained as $\nu\rightarrow 0$ with the help of \mrev{the frequency   
+and time domain codes }(computed for large values of time). 
 The time-domain code implements the scheme described in \mrev{Section \ref{sec:staggered_discretization}} and 
@@
 \end{align}
-\mrev{It can be shown that $E_{y}$ that solves (\ref{eq:main_frequency_domain_general}) in 1D, with the Fourier variable $\theta=0$ (see (\ref{vf1dcase}), 
+\urev{It can be shown that $E_{y}$ that solves (\ref{eq:main_frequency_domain}) with the above parameters,  
 and $\nu=0$, satisfies the Airy equation, see also Remark \ref{remark:other},
@@
 \end{align*}
-One of the solutions of this equation, an Airy function $\Ai(x)$, see \cite[Chapter 10.4]{abramowitz_stegun}, is analytic and decays rapidly as $x\rightarrow \infty$. 
-Hence, choosing $H$ sufficiently large \mrev{TODOOO(the actual value used in the experiments $H=10$, where $\Ai'(10)\approx -3.5e-10$)} and the boundary conditions as 
+One of the solutions of this equation, an Airy function $\Ai(x)$, see \cite[Chapter 10.4]{abramowitz_stegun}, is analytic and 
+decays rapidly as $x\rightarrow \infty$. }
+\mrev{Hence, choosing $H$ sufficiently large (the actual value used in the experiments $H=10$, where $\Ai'(10)\approx -3.5e-10$) and the boundary conditions as 
 \begin{align}
@@
 In Fig.~\ref{fig:conv_rate} we demonstrate the convergence rates for this problem, comparing the solution with the 
-known analytic solution. \mrev{TODO:We can expect the solution to be smooth, due to the smoothness of the coefficients of the problem}.
+known analytic solution. 
 Importantly, the obtained convergence rates are in agreement with known estimates of the standard theory of convergence~\cite[Chapter 5.7,
-Chapter 0.4]{brenner}.  
+Chapter 0.4]{brenner}, \mrev{provided that the Aubin-Nitsche lemma \cite[Theorems 3.2.4,3.2.5]{ciarlet_fem} holds for the variational formulation.}  
+\urev{Since the coefficients of the problem are smooth, we expect the solution to be at least in $C^2(\Omega)$.}  
 \begin{figure}
@@
 \end{align}
-We additionally assume that $E_y^{\nu}(x)$ is sufficiently smooth and $\|(E_y^{\nu})''\|_{H_{2}(\Omega)}$
-can be bounded independently of $\nu$. 
+\item \mrev{An explicit bound on $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ based on the results of \cite{singular_solutions}. First of all, we
+will assume that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the behaviour in the vicinity of the point of the resonance, where 
+the following expansion is valid \cite[Proposition 1]{singular_solutions}
+\begin{align*}
+E_{y}^{\nu}(x)=\tilde{E}_{y}^{\nu}(x)+\text{smooth terms with derivatives bounded independently of $\nu$,} \\
+\tilde{E}_{y}^{\nu}(x)=\log\rho_{\nu}(x-X_{\nu})(\alpha(x)+i\nu)p_{\nu}(x),
+\end{align*}
+where $\rho_{\nu}$ is a smooth function s.t. $\rho_{\nu}(0)=0,\; \rho_{\nu}'(0)\neq 0$, the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R}$, 
+and $p_{\nu}(x)$ is a smooth function with derivatives bounded independently of $\nu$. 
+}
 \item The estimate from \cite[Chapter 0]{brenner} on the rate of convergence of the interpolation 
@@
   \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}%\leq C_1\nu^{-1}h\|\left(E_y^{\nu}\right)''\|_{L_{2}}+C_2\nu^{-1}h^2\|\left(E_x^{\nu}\right)''\|_{L_{2}}
-  \leq C\nu^{-1}h+C\nu^{-1}h^2\|\left(E_x^{\nu}\right)''\|_{L_{2}},
+  \leq C\nu^{-1}h\|\left(E_y^{\nu}\right)''\|_{L_{2}}+C\nu^{-1}h^2\|\left(E_x^{\nu}\right)''\|_{L_{2}}.
 \end{align}
-where we used an assumption that the $L_2$-norm of $\left(E_y^{\nu}(x)\right)''$ can be bounded independently of $\nu$.
+\mrev{
+First of all let us examine the behaviour the derivatives of $E_{y}^{\nu}$ in the vicinity of the resonance:
+\begin{align}
+\label{eq:eynuprime}
+ \left(\tilde{E}_{y}^{\nu}\right)'&=\frac{\alpha(x)+i\nu}{\rho_{\nu}(x-X_{\nu})}p_{\nu}(x)+\alpha'\log\rho_{\nu}(x-X_{\nu})p_{\nu}(x)+p'_{\nu}(x)(\alpha+i\nu)\log\rho_{\nu}(x-X_{\nu}).
+\end{align}
+The first term in the above expression is well-defined in $x=0$ (the L'Hopital's rule), and for sufficiently small $\nu$ can be bounded independently of $\nu$. 
+Similarly, the third term is non-singular.
+To examine the behaviour of $\left(\tilde{E}_{y}^{\nu}\right)''$, we study solely the singular second term of (\ref{eq:eynuprime}) (the derivatives for the rest of the terms can be shown to be bounded
+independently of $\nu$)
+\begin{align*}
+ \left(\alpha'\log\rho_{\nu}(x-X_{\nu})p_{\nu}\right)'=\alpha''\log\rho_{\nu}(x-X_{\nu})p_{\nu}+\frac{\alpha'p_{\nu}}{\rho_{\nu}(x-X_{\nu})}\rho'_{\nu}(x-X_{\nu})+
+ \alpha'\log\rho_{\nu}(x-X_{\nu})p_{\nu}'.
+\end{align*}
+The most singular term in the above expression is $\frac{\alpha'p_{\nu}}{\rho_{\nu}(x-X_{\nu})}\rho'_{\nu}(x-X_{\nu})$ which can be bounded, for sufficiently small $x$, 
+\begin{align*}
+ \left|\frac{\alpha'p_{\nu}}{\rho_{\nu}(x-X_{\nu})}\rho'_{\nu}(x-X_{\nu})\right|\leq \frac{C}{|x+i\nu c|},\; C>0,c\in\mathbb{R},
+\end{align*}
+where we used an explicit form for $X_{\nu}$.
 
+Therefore, assuming that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the vicinity of the resonance, where for $\nu=0$ this function is singular, 
+we obtain the following rough bound
+\begin{align*}
+ \|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}\leq G+G'\left(\int\limits_{-L}^{H}\frac{1}{|x+i\nu c|^2}dx\right)^{\frac{1}{2}}\\
+ \leq G+G'\left(\frac{1}{\nu c}\int\limits_{-\infty}^{\infty}\frac{dv}{v^2+1}\right)^{\frac{1}{2}}\\
+ \leq \frac{C}{\sqrt{\nu}},\qquad G,G',C>0,
+\end{align*}
+for sufficiently small $\nu>0$.
+}
 For $E_x^{c,\nu},\; f^{\nu}(x)$ in (\ref{eq:exact}) being sufficiently smooth, 
@@
 \ben
- \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}\leq C\nu^{-\frac{7}{2}}h^2+C\nu^{-1}h.
+ \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}\leq C\nu^{-\frac{7}{2}}h^2+C\nu^{-\frac{3}{2}}h.
 \een

### 2015-04-30 report_clean/timedomain.tex
fixed a major bug

@@
 \section{Time Dependent Problem Discretization}
-\mrev{
+\arev{
 In this section we develop the discretization of the time-dependent one-dimensional model (\ref{eq:main_model}), for a particular case $\theta=0$. 
@@
 \label{sec:staggered_discretization}
-In this section, we develop a discretization of the time dependant problem~\eqref{eq:main_model} 
+In this section, we develop a discretization of the time-dependent problem~\eqref{eq:main_model} 
 in one dimension. %In 1D, the derivatives with respect to $y$ vanish, and we are left with the following problem, 

### 2015-04-30 report_clean/resume.tex
small issues

--- 2015-01-29 report/resume.tex
@@
 ainsi est d'int\'er\^et scientifique dans le cadre du d\'eveloppement  du projet ITER.
-Dans ce papier, nous nous concentrons sur certaines  solutions faiblement r\'eguli\`eres des \'equations de Maxwell pour les plasmas sous l'influence de champ magn\'etiques forts.
-Notre but est ici double.
+Dans ce papier, nous nous concentrons sur des solutions faiblement r\'eguli\`eres des \'equations de Maxwell pour les plasmas sous l'influence de champ magn\'etiques forts.
+Notre but principal est ici double.
 D'un c\^ot\'e nous \'evaluons l'approximation
-num\'erique \`a l'aide d'\'el\'ements finis en une dimension en formulation 
-fr\'equentielle, et de l'autre nous \'etudions l'approximation num\'erique \`a l'aide de deux m\'ethodes de  diff\'erences finies pour la formulation
-temporelle monodimensionelle. Nous comparons les r\'esultats de ces  diff\'erentes m\'ethodes.
+num\'erique \`a l'aide d'\'el\'ements finis de la formulation 
+fr\'equentielle, et de l'autre nous \'etudions les solutions r\'esonnantes dans le domaine temporelle, \`a l'aide de deux approximation diff\'erences finies diff\'erentes.
+Nous comparons ensuite les r\'esultats ainsi obtenus avec ceux donn\'es dans le domaine fr\'equentiel.
+Ceci est fait en regardant num\'eriquement les principes d'amplitude et d'absorption limite.

### 2015-05-03 report_clean/numerics.tex
local modifications

--- 2015-04-27 report_clean/numerics.tex
@@
 This section is organized as follows. The first part is dedicated to the numerical implementation
-of the frequency domain formulation \eqref{eq:main_frequency_domain_general}. We study the convergence of this formulation and the behaviour 
+of the frequency domain formulation \eqref{eq:main_frequency_domain}. We study the convergence of this formulation and the behaviour 
 of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
-performed with the help of \mrev{our} code written in Octave.  
+performed with the help of the code written in Octave.  
 We implemented the scheme described in Section \ref{sec:discr} for a case of $P_{1}$-space used 
@@
 and of the time domain code (computed for large values of time). 
-The time-domain code implements the scheme described in \mrev{Section \ref{sec:staggered_discretization}} and 
+The time-domain code implements the scheme described in Section \ref{sec:discr} and 
 is written in Fortran.
@@
 \label{eq:parameters}
-\alpha(x)=x^2+1,\qquad \delta(x)=\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}, \qquad \mrev{\nu=0}.
+\alpha(x)=x^2+1,\qquad \delta(x)=\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}.
 \end{align}
-\mrev{It can be shown that $E_{y}$ that solves \mrev{(\ref{eq:main_frequency_domain_general})} in 1D, with the Fourier variable $\theta=0$ (see (\ref{vf1dcase}), 
-and $\nu=0$, satisfies the Airy equation, see also Remark \ref{remark:other},
-\begin{align*}
- E_y''-xE_y=0,\qquad x\in [-L,\; H].
-\end{align*}
-One of the solutions of this equation, an Airy function $\Ai(x)$, see \cite[Chapter 10.4]{abramowitz_stegun}, decays rapidly as $x\rightarrow \infty$. 
-Hence, choosing $H$ sufficiently large \mrev{TODOOO(the actual value used in the experiments $H=10$)} and the boundary conditions as 
+Additionally, the boundary conditions read as 
 \begin{align}
 \label{eq:bcs_airy}
-\partial_{1}E_{y}(-L)+2iE_{y}(-L)=2i\Ai(-L)+\Ai'(-L),\qquad 
-\partial_{1}E_{y}(H)=0\approx Ai(H),
+\partial_{1}E_{y}(-L)+2iE_{y}(-L)=2iAi(-L)+Ai'(-L),\qquad 
+\partial_{1}E_{y}(H)=0,
 \end{align}
-where $\Ai(x)$ is an Airy function, we ensure that $E_{y}$ that solves the above problem is well approximated by $\Ai(x)$, and $E_{x}$ by $-i\frac{\delta(x)}{\alpha(x)}\Ai(x)$. 
-The well-posedness of the respective variational formulation for $\nu=0$ is due to Remark \ref{remark:other}. }
+where $Ai(x)$ is the Airy function. 
+For more detail on Airy functions and the Airy equation see \cite[Chapter 10.4]{abramowitz_stegun}. 
+It can be shown that $E_{y}$ that solves (\ref{eq:main_frequency_domain}) in 1D, with the Fourier variable $\theta=0$ (see (\ref{vf1dcase}), and $\nu=0$, 
+satisfies the Airy equation, and hence, 
+with the choice of the boundary conditions as above, we obtain that 
+$
+E_{y}=Ai(x)  $  and   %,\qquad 
+$E_{x}=-i\frac{\delta(x)}{\alpha(x)}Ai(x)$
+is the solution to the problem with parameters (\ref{eq:parameters}) and the boundary condition (\ref{eq:bcs_airy}). 
+The well-posedness of the respective variational formulation for $\nu=0$ is due to Remark \ref{remark:other}.
 
 In Fig.~\ref{fig:conv_rate} we demonstrate the convergence rates for this problem, comparing the solution with the 
-known analytic solution. \mrev{TODO:We can expect the solution to be smooth, due to the smoothness of the coefficients of the problem}.
-Importantly, the obtained convergence rates are in agreement with known estimates of the standard theory of convergence~\cite[Chapter 5.7,
-Chapter 0.4]{brenner}.  
+known analytic solution. Importantly, the obtained convergence rates are in agreement with known estimates of the standard theory of convergence~\cite{brenner}.
 \begin{figure}
@@
 \end{tabular}
-\caption{In the left figure the dependence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated. 
+\caption{In the left figure the depenence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated. 
 In the right figure we show the computed solutions for the problem with parameters in Table \ref{tab:parameters} for different values of $\nu$. }
@@
 \end{remark}
-
+\paragraph{Condition Number}
 In Figure \ref{fig:small_nu} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
@@
 case.
-The numerical tests have been kept to a minimum since many more are needed to fully validate
+The numerical tests have been kept to a minimum since much more are needed to fully validate
 the concept.
@@
 is the following. We use a 7th order semi-lagrangian scheme, and the CFL is $\nu=0.5$.
-The peak is the hybrid resonance, visible on $E_x$ and $u_x$.
+The Pike is the hybrid resonance, visible on $E_x$ and $u_x$.
 The total energy $\mathcal E(t)$ is the physical energy. 
 The comparison with figures \ref{fig:dependence} and \ref{fig:resonance_nus_ey_x} show that the 
-singular nature of the resonance is captured by this new scheme without any doubt.
+singular nature of the resonant is captured by this new scheme without any doubt.
 

### 2015-05-03 solve_mH1.m

@@ -19,6 +19,7 @@ r=construct_rhs(x);
 
 tic
 [M,rhs]=permute(A,B,D,r);
+%save('D.mat', 'D');
 %save('M.mat', 'M');
 sol=M\rhs;
 
@@ -326,6 +327,8 @@ function [A,B,D]=construct_block_matrix(x,nu,lambda)
                    A=Malpha+1i*nu*M;
                    B=1i*Mdelta;
                    D=S-(Malpha+1i*nu*M);
+		   %save ('D1.mat', 'D');
+
 %adding a boundary condition
                    D(1,1)=D(1,1)-1i*lambda;
 

### 2015-05-03 report_clean/responce_reviewers.tex
abstract: fixed

@@
 
-\section{Extra Corrections}
-As an extra improvement, not asked by the reviewers, we changed $\tilde{\omega}$ to $\omega_{\nu}$ in Section 2.
+\section{General}
 
-Corrected the definitions of $\alpha,\delta$ to comply with the definition of the cold plasma dielectric tensor of Stix (more precisely, removed terms $\frac{\omega^2}{c^2}$ in 
+We marked corrections suggested by the reviewer 1 in blue, by the reviewer 2 in red, 
+and some extra corrections made by us that can be important in green.
+
+More important corrections include
+- changed the wording in the abstract
+- corrected the definitions of $\alpha,\delta$ to comply with the definition of the cold plasma dielectric tensor of Stix 
+(more precisely, removed terms $\frac{\omega^2}{c^2}$ in 
 front of them)
 
-\section{Responce to the reviewer #1}
+\section{Responce to the reviewer 1}
 
@@
 1. We agree with the remarks of the reviewer. We included a short introduction into the physics of the problem, 
-which hopefully will facilitate in reading the article. The Section 4.3.1 contains of course a mistake in the description of the 
-parameters of the problem.
+which hopefully will facilitate in reading the article.
 
-Concerning the notation: from now on $\epsilon^{\nu}_{\omega}(\mathbf{r})$ denotes the cold plasma dielectric tensor, similarly we denote its parameters.
+Concerning Sections 4.1.2, 4.3.1: 
+We define more precisely the hybrid resonance now, which in fact requires that $\alpha$ vanishes, 
+and $\delta$ does not (while in Section 4.3.1 $\delta$ vanishes as well).
 
+The notation: 
+from now on $\varepsilon^{\nu}_{\omega}(\mathbf{r})$ denotes the cold plasma dielectric tensor, similarly we denote its parameters. 
 We added explicitely dependence on space in parameters that depend on the spatial variables.
 
+The case $\omega=\omega_c$:
 Indeed, $\epsilon_{\infty}<\infty$ if $\omega_c^2\neq \omega^2$, but formally one also needs to require the boundedness of $\omega_p^2$. Therefore we 
@@
 
+The limiting amplitude/absorption principle:
+
 A brief description of what limiting absorption and limiting amplitude principles had been added in the end of the introduction.
 
-2. The reduction to a 1d problem is not clearly justified - indeed, we changed this in the introduction by adding an assumption on $N_e, B_0$, 
+2. 'The reduction to a 1d problem is not clearly justified' - indeed, we changed this in the introduction by adding an assumption on $N_e, B_0$, 
 and changed the wording in the introduction to underline that the 1D case is the one of interest.
@@
  - p9 after (17): we would like to assume that it is $H^2$-norm that is bounded, for using the inequality (19). 
-  \mrev{TODO: While this assumption is fairly strong, it is not unsubstantial: for sufficiently smooth $\alpha,\delta$,  }
+  \mrev{TODO: While this assumption is fairly strong, it is often used in the approximation theory.   }
 

### 2015-05-03 report_clean/FD.tex
final changes. To-Do: more changes

--- 2015-04-27 report_clean/FD.tex
@@
 \section{Frequency domain study}
-The goal of this section is to review the connection between the system (\ref{eq:main_system}), its frequency domain counterpart and 
+The goal of this section is to review the connection between the frequency domain counterpart of the problem (\ref{eq:main_model}) and 
 the regularized problem (\ref{eq:seq_regularized}).
 
-In the frequency domain, the velocity can be eliminated to obtain a simpler system under the form
-of  Maxwell equations with the cold plasma dielectric tensor \cite{Stix,Despres_2014}, more precisely
-\urev{
+The model (\ref{eq:main_model}) can be rewritten in the frequency domain as 
 \bealn
-%\label{eq:main_frequency_domain_1}
-\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-
-\frac{\omega^2}{c^2}\underline{\varepsilon}^{\nu}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,\\
-\underline{\varepsilon}^{\nu}_{\omega}(\mathbf{r})=\left(
+\left(
 \begin{matrix}
- \alpha^{\nu}_{\omega}(\mathbf{r}) & i\delta^{\nu}_{\omega}(\mathbf{r}) \\
- -i\delta^{\nu}_{\omega}(\mathbf{r}) & \alpha^{\nu}_{\omega}(\mathbf{r})
+ i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
+ i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
+\end{matrix}
+\right)-\frac{\omega^2}{c^2}
+\underline{\varepsilon}_{\omega}^{\nu}(x)\left(
+\begin{matrix}
+ \hat{E}_x\\
+ \hat{E}_y
+\end{matrix}
+\right)
+=0,\\
+\underline{\varepsilon}^{\nu}_{\omega}(x)=\left(
+\begin{matrix}
+ \alpha^{\nu}_{\omega}(x) & i\delta^{\nu}_{\omega}(x) \\
+ -i\delta^{\nu}_{\omega}(x) & \alpha^{\nu}_{\omega}(x)
 \end{matrix}
 \right),\qquad 
- \alpha^{\nu}_{\omega}(\mathbf{r})=1-\frac{\omega_{\nu}\omega_p^2(\mathbf{r})}{\omega(\omega_{\nu}^2-\omega_c^2(\mathbf{r}))},\qquad 
-\delta^{\nu}_{\omega}(\mathbf{r})=\frac{\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})}{\omega(\omega_{\nu}^2-\omega_c^2(\mathbf{r}))},
+ \alpha^{\nu}_{\omega}(x)=1-\frac{\omega_{\nu}\omega_p^2(x)}{\omega(\omega_{\nu}^2-\omega_c^2(x))},\qquad 
+\delta^{\nu}_{\omega}(x)=\frac{\omega_c(\mathbf{r})\omega_p^2(x)}{\omega(\omega_{\nu}^2-\omega_c^2(x))},
 \eealn
-}
-\mrev{where the frequency 
-$\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane.
-Note that neither cyclotron, nor hybrid resonances occur in the problem with the dielectric tensor $\varepsilon^{\nu}_{\omega}(\mathbf{r}), \; \nu>0,$ (since all parameters are real).
-Hence
+where the frequency 
+$\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane. \arev{Note that neither cyclotron, nor hybrid resonances occur in the problem 
+with the dielectric tensor $\varepsilon^{\nu}_{\omega}(\mathbf{r}), \; \nu>0$ (since all parameters are real). Hence 
 the choice of the non-zero plasma friction $\nu>0$ can be viewed as a regularization of the problem. }
@@
 \bealn
- \alpha^{\nu}_{\omega}=\alpha_{\omega}+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}=\alpha_{\omega}+i\nu D_{\alpha},\\
- \delta^{\nu}_{\omega}=\delta_{\omega}-i\nu\frac{2\omega}{(\omega^2-\omega_c^2)^2}=\alpha_{\omega}+i\nu D_{\delta},
+ \alpha^{\nu}_{\omega}=\alpha_{\omega}+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{\omega(\omega^2-\omega_c^2)^2}=\alpha_{\omega}+i\nu D_{\alpha},\\
+ \delta^{\nu}_{\omega}=\delta_{\omega}-i\nu\frac{2\omega_c\omega_p^2}{(\omega^2-\omega_c^2)^2}=\alpha_{\omega}+i\nu D_{\delta},
 \eealn
 where $\alpha_{\omega},\;\delta_{\omega}$ are defined by (\ref{eq:alpha_delta}). In the frequency domain one thus can consider 
-the following regularization of the cold plasma dielectric tensor of \mrev{the above problem}:
+the following regularization of the cold plasma dielectric tensor of the above problem:
 \begin{align*}
@@
 yields the same solution as $\nu\rightarrow 0$. }
-%We finally obtain a simpler equation \cite{Despres_2014}
-
 Thus, applying the above process to (\ref{eq:main_model}) in the frequency domain, we obtain, see also \cite{Despres_2014},
+\begin{align*}
+\left(
+\begin{matrix}
+ i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
+ i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
+\end{matrix}
+\right)-\frac{\omega^2}{c^2}
+\left(\varepsilon^{0}_{\omega}(x)+i\nu \mathrm{Id}\right)\left(
+\begin{matrix}
+ \hat{E}_x\\
+ \hat{E}_y
+\end{matrix}
+\right)
+=0,\\
+\varepsilon^0_{\omega}(x)=\left(
+\begin{matrix}
+ \alpha_{\omega}(x) & i\delta_{\omega}(x) \\
+ -i\delta_{\omega}(x) & \alpha_{\omega}(x)
+\end{matrix}
+\right). 
+\end{align*}
+\mrev{
+For simplicity, from now on we will denote $\alpha_{\omega},\; \delta_{\omega}$ by $\alpha,\; \delta$ and consider a sequence of regularized problems. 
 \begin{align}
@@
 \end{matrix}
-\right)-\frac{\omega^2}{c^2}
-\left(\varepsilon^{0}_{\omega}(x)+i\nu \mathbb{E}\right)\left(
+\right)-
+\left(\varepsilon^{0}(x)+i\nu \mathrm{Id}\right)\left(
 \begin{matrix}
@@
 \label{eq:epsilon_0}
-\varepsilon^0_{\omega}(x)=\left(
-\begin{matrix}
- \alpha_{\omega}(x) & i\delta^{0}(x) \\
- -i\delta_{\omega}(x) & \alpha^{0}(x)
-\end{matrix}
-\right)=
-\left(
+\varepsilon^{0}(x)=\left(
 \begin{matrix}
@@
 \end{matrix}
-\right)=\varepsilon^{0}(x).
+\right),
 \end{align}
+where $\alpha,\;\delta$ satisfy the following.
+}
 \urev{
-From now on we will assume the following assumption to hold.
 \begin{assumption}
@@
 }
-
+\urev{
 \begin{remark}
@@
 In the frequency domain, as we can see from above and from \cite{Despres_2014,LMIG_thesis}, the sign 
-of the parameter $\nu$ can be chosen arbitrarily to regularize the problem. However, as demonstrated in the above references, as $\nu\rightarrow 0\pm$, the 
-limiting solutions differ, though both exhibit the singularity in the point of the hybrid resonance.  
+of the parameter $\nu$ can be chosen arbitrarily to regularize the problem. However, as demonstrated in the aforementioned works, as $\nu\rightarrow 0\pm$, the 
+corresonding limiting solutions differ, though both exhibit the singularity in the point of the hybrid resonance.  
 \end{remark}
-%}
+}
 
@@
 %denoting by $\theta$ the corresponding Fourier variable. 
-\mrev{In this section we study the well-posedness of the problem (\ref{eq:main_frequency_domain}) with the help of Lax-Milgram lemma.} 
+\mrev{In this section we study the well-posedness of the problem (\ref{eq:main_frequency_domain}) with the 
+ boundary conditions (\ref{eq:boundary_conditions_frequency_domain}) with the help of Lax-Milgram lemma.} 
 After introducing $\Omega=(-L,\; H)\subset \mathbb R$ and defining the function space of the problem  $\mathbf{V}=L^{2}(\Omega)\times H^{1}(\Omega)$, 
@@
 	one  $H_1(\Omega)\subset C^0(\overline \Omega)$. Let us focus on the proof of coercivity. 
-	Without loss of generality let us assume that $\nu>0$. We denote $\heps =  \|\rho(\varepsilon^{0})\|_{L^\infty}$, the spectral radius of $\varepsilon^{0}$ so that
-	$\heps Id- \varepsilon^{0} $ is a non negative hermitian matrix.
+	Without loss of generality let us assume that $\nu>0$. \mrev{Given $\heps$ the spectral radius of $\varepsilon^{0}$, 
+	$\heps Id- \varepsilon^{0} $ is a non negative hermitian matrix.}
 	Therefore
@@
 The above proof is not optimal in the case when $\left|\alpha(x)\right|>c>0$ for $c>0$ on the whole interval $[-L,\; H]$, at least 
-for the case $\theta=0$. In this case the problem (\ref{eq:var_form2}) is well-posed for $\nu=0$. \mrev{More precisely, it can be written 
+for the case $\theta=0$. In this case the problem (\ref{eq:var_form2}) is well-posed for $\nu=0$. More precisely, it can be written 
 as a system of two equations, where the first equation (for $E_y$) is the variational formulation for the Helmholtz equation 
@@
 \end{align*}
-uniquely defines $E_x\in L^{2}(\Omega)$. }The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
+uniquely defines $E_x\in L^{2}(\Omega)$. The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
 was demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H^{1}(\Omega)$, we can obtain $E_x$ from the second equation.

### 2015-05-03 report_clean/absorption.tex
cosmetic changes
small issues

@@
 \eealn
-We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain (the solution computed numerically at the time step $n$ is denoted by $\mathbf{E}^{\nu}_{n}$), and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain.
+We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain 
+(the solution computed numerically at the time step $n$ is denoted by $\mathbf{E}^{\nu}_{n}$), and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain. 
 In the numerical experiments we check whether the following two quantities
@@
 are close as $\nu\rightarrow 0$ (provided that the first of these quantities exists).
+
+In all the experiments in this section the CFL number was chosen as 0.5.
 \subsubsection{No-Resonance Case}
+\label{section:absorption_airy}
 We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{y}^{\nu},\; \nu=0,$ satisfies 
 the Airy equation, c.f. also Remark \ref{remark:other}. We set $\omega_c=0$ (thus $\delta(x)=0$), $\omega=1$ (hence $\alpha(x)=1-N_e(x)$), 
-choose the domain as $(-0.5, 10)$ and set the electron density $N_e(x)=1+x$. Importantly, $N_e(x)>0$ on the whole interval.
+choose the domain as $(-0.5, 10)$ and set the electron density $N_e(x)=1+x>0,\; x\in \Omega$. 
+\mrev{Importantly, since $\delta(x)=0$, in this case no resonance occurs and $E_x(x)=0$. This corresponds to the case when the
+tensor of dielectric permittivity $\underline{\varepsilon}^{\nu}$ is 
+diagonal.}
+
 The boundary conditions in (\ref{eq:bcs}) are chosen as $G=Ai'(0.5)$.
@@
 \end{tabular}
-\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time for large times is demonstrated in the left figure.  
-In the right figure we show the solution for $\nu=10^{-2}$, for two fixed moment of times.}
+\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ \mrev{to the problem described in Section \ref{section:absorption_airy}} on time for large times is demonstrated in the left figure.  
+In the right figure we show the solution \mrev{to the same problem} for $\nu=10^{-2}$, for two fixed moment of times.}
  \label{fig:nu1e2_harmon}
@@
 \label{eq:error}
-\mathcal{E}_{x,y}(t)=\|\Im\left(\hat{E}_{x,y}^{\nu}\mathrm{e}^{it}\right)-E_{x,y}^{\nu}(t)\|_{L_{2}(-L;H)}.
+e_{x,y}(t)=\|\Im\left(\hat{E}_{x,y}^{\nu}\mathrm{e}^{it}\right)-E_{x,y}^{\nu}(t)\|_{L_{2}(-L;H)}
 \end{align}
@@
 \end{tabular}
-\caption{In the left figure we plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$. 
-In the right figure we show the solution for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
+\caption{In the left figure we plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ \mrev{to the problem described in Section \ref{section:absorption_airy}} on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$.
+In the right figure we show the solution \mrev{to the same problem} for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
 $\nu=10^{-4}$ the limiting amplitude solution was reached for large $t$. For $\nu=10^{-6}$ we were not able 
@@
 \begin{table}[htb!]
-\begin{tabular}{c|c}
+\begin{tabular}{l|l}
 Parameter & Value \\
@@
  \end{tabular}
-\caption{The figures demonstrate the dependence of the solutions 
+\caption{The figures demonstrate the dependence of the solutions to the problem \mrev{described in Section \ref{sec:resn}}
 $E_y^{\nu}(-2.5125,t)$ on time $t$ for different values of $\nu$. }
@@
  \includegraphics[width=0.8\textwidth]{pics_time_domain/res/ex_fixed_x_nu1e4-crop.pdf}
- \caption{The plot shows the dependence of the solution $E_x^{\nu}(x_c,t),\;\nu=10^{-4}$ on time $t$ for fixed 
+ \caption{The plot shows the dependence of the solution $E_x^{\nu}(x_c,t),\;\nu=10^{-4},$ to 
+ the problem \mrev{described in Section \ref{sec:resn}} on time $t$ for fixed 
  $x_c=0.0125$ and for $x_c=-2.5$. We can see that the solutions computed in the time domain are in close agreement 
@@
 \caption{The figures demonstrate the dependence of the solutions 
-$E_x^{\nu}(x,t)$ on $x$ for fixed values of $t$. }
+$E_x^{\nu}(x,t)$ to the problem \mrev{described in Section \ref{sec:resn}} on $x$ for fixed values of $t$. }
 \label{fig:resonance_nus_ex_t}
@@
 \caption{The left figure demonstrates the dependence of the solution  
-$E_y^{\nu}(x,y)$ on $x$ for fixed values of $t$. For a chosen value of $\nu$ the solutions computed in the time domain are in close agreement 
+$E_y^{\nu}(x,y)$ to the problem \mrev{described in Section \ref{sec:resn}} on $x$ for fixed values of $t$. 
+For a chosen value of $\nu$ the solutions computed in the time domain are in close agreement 
 to the solutions computed in the frequency domain. This seem to be only partially 
 true for the computed values $E_x^{\nu}(x,t)$ in this case (which may be caused by the discretization). 
-The right figure shows the dependence of the solution $E_y^{\nu}(x,t)$ for $\nu=10^{-4}$ on time for fixed $x=x_c$. 
+The right figure shows the dependence of the solution $E_y^{\nu}(x,t)$ \mrev{to the same problem} for $\nu=10^{-4}$ on time for fixed $x=x_c$. 
 We can see that the while the limiting amplitude principle holds true, the difference between the solutions computed in 
@@
 \caption{The figures demonstrate the dependence of the solutions 
-$E_x^{\nu}(x,t)$ and $E_y^{\nu}(x,y)$ on $x$ for fixed values of $t$. While the solution in the time-domain 
+$E_x^{\nu}(x,t)$ and $E_y^{\nu}(x,y)$ to the problem \mrev{described in Section \ref{sec:resn}} on $x$ for fixed values of $t$. While the solution in the time-domain 
 in the resonance point $x=0$ has a smaller absolute value than that computed in the frequency domain (in the plot both solutions are truncated to 

### 2015-05-03 report_clean/conclusions.tex
bruno's changes

@@
 well as studied the convergence of the finite element method for the problem with the resonance. 
-The piecewise-constant FEM approximates the resonant solution rather well, at least for moderate values of $\nu$, 
+The piecewise-\mrev{linear} FEM approximates the resonant solution rather well, at least for moderate values of $\nu$, 
 however, the discretization size should be chosen roughly proportional to $\nu^{\frac{7}{4}}$, in order to obtain an accurate discretization.
@@
 Another unanswered question is the well-posedness of the discrete problem when the continuous problem is ill-posed. We have 
-demonstrated that while the condition number of the FEM matrix grows, the matrix remains always invertible, even for $\nu=0$.
+demonstrated by numerical means that while the condition number of the FEM matrix grows, the matrix remains always invertible, even for $\nu=0$.
 
-We proposed two different schemes for solving the time-dependent problem. Our numerical experiments demonstrate that both of them capture the singular behaviour of the solutions in the resonant case.
+We proposed two different schemes for solving the time-dependent problem. 
+Our numerical experiments demonstrate that both of them capture the singular behaviour of the solutions in the resonant case.
 

### 2015-05-03 report_clean/intro.tex
final changes. To-Do: more changes

@@
 mathematically as the non-regularity of
-the solutions of Maxwell equations in plasmas under strong background magnetic field \cite{Despres_2014}. 
+the solutions of Maxwell equations in \mrev{magnetized plasmas} \cite{Despres_2014}. 
 The energy deposit is resonant and may exceed by far the energy 
@@
 \end{align}
-coupled with \mrev{an equation for the } linear electronic current  $\J = eN_e(\mathbf{r}) \ubf$, 
+coupled with an equation for the linear electronic current  $\J = eN_e(\mathbf{r}) \ubf$, 
 \begin{align}
@@
 where \mrev{$\nu\geq 0$} is the friction  between particles, $e<0$ is the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density that in general 
-depends on spatial variables and is uniform in time. \mrev{A non-zero value of $\nu$ constitutes a basis for the limiting absorption principle.} 
+depends on spatial variables and is uniform in time. A non-zero value of $\nu$ constitutes a basis for the limiting absorption principle. 
 The unknowns are the electron velocity $\ubf$ and the electromagnetic field.
@@
 the cyclotron frequency $\omega_c(\mathbf{r})=\frac{e B_0(\mathbf{r})}{m_e}$ and perform the Fourier transform 
-in time of \ref{eq:main_system} ($\partial_t\rightarrow -i\omega$), for a 
+in time of (\ref{eq:main_system}) (with the convention $\partial_t\rightarrow -i\omega$), for a 
 particular case $\nu=0$:
@@
 
-The point $\mathbf{r}_c=(x_c,y_c)$ s.t.
-$\omega_c(\mathbf{r}_c)=\omega$, i.e.
-when $\underline{\varepsilon}_{\omega}^{0}(\mathbf{r})$ is singular, is called a cyclotron resonance (c.f.
+The point $\mathbf{r}_0$ s.t.
+$\omega_c(\mathbf{r}_0)=\omega$, i.e.
+when $\underline{\varepsilon}_{\omega}^{0}(\mathbf{r}_0)$ is singular, is called a cyclotron resonance (c.f.
 \cite[Chapter 1-5]{Stix}).
 In \cite{singular_solutions} it was demonstrated for a 1D-counterpart of the above system that such points behave like removable singularities, 
-and the solutions are well-defined in the limit $x\rightarrow x_c$. Hence this case is not of interest for the present work.
+hence this case is not of interest for the present work.
 
-Another interesting case is $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$, when the diagonal part of the tensor $\underline{\varepsilon}_{\omega}^{0}(\mathbf{r})$ vanishes, 
-under the condition that the non-diagonal part remains non-zero. This is a hybrid resonance case.
+Another interesting case is $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$ and $\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})\neq 0$, i.e. when the diagonal part of the tensor 
+$\underline{\varepsilon}_{\omega}^{0}(\mathbf{r})$ vanishes and the non-diagonal part remains non-zero. This is a hybrid resonance case.
 
@@
 integrable. This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.
-Jumping ahead, instead of (\ref{eq:model_freq_domain}) 
-one considers a sequence of regularized problems
-\begin{align}
-\label{eq:seq_regularized}
-  \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\underline{\varepsilon}^{\nu}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,\;
-  \underline{\varepsilon}^{\nu}_{\omega}(\mathbf{r})= \underline{\varepsilon}^{0}_{\omega}(\mathbf{r})+i\nu \mathbb{E},\; 
-\end{align}
-with $\nu\rightarrow 0$ and $\mathbb{E}$ being an identity matrix. 
-}
 
-\urev{We will concentrate on a simplified model (which nevertheless is of physical interest when modelling antennas in plasmas), where it is required to study the above system in an 
-infinite domain $(-L,\; \infty)\times\mathbb{R}$, $L\in \mathbb{R}$, under the assumption that the electron density $N_{e}$ and the magnetic field $B_0$ are \textbf{uniform} in the second coordinate, more precisely
-$N_{e}=N_{e}(x)$ and $B_0=B_0(x)$, see e.g.
-\cite{Despres_2014}.
-Despite such a simplfication, already a 1D-version of the system (\ref{eq:main_model}) contains difficulties intrinsic to the hybrid resonance case
-\cite{Despres_2014, singular_solutions}.
-
-The problem (\ref{eq:model_freq_domain}) should be equipped with the boundary conditions.
-At the left boundary of the domain, which represents the wall of the Tokamak, we choose Robin boundary conditions 
+Before proceeding, let us define the geometrical setting of the problem.
+We consider the frequency domain problem (\ref{eq:model_freq_domain}) posed in the domain $(-L,\;\infty)\times\mathbb{R},\; L>0$, with the
+ boundary conditions chosen as follows. At the left boundary of the domain, which represents the wall of the Tokamak, we pose Robin boundary conditions 
 \be
--curl \hat{\mathbf{E}} -\imath \lambda\hat{\mathbf{E}} \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
+\label{eq:boundary_conditions_intro}
+curl \hat{\mathbf{E}} -\imath \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} =curl \E_{inc} -\imath\lambda\E_{inc}\wedge \n,
 \ee
@@
 the frequency of the antenna. We truncate the domain 
-$(-L,\; \infty)\times\mathbb{R}$ to $(-L,\; H)\times\mathbb{R}$ and set on the right boundary $\operatorname{curl} \E = 0$.
+$(-L,\; \infty)\times\mathbb{R}$ to $(-L,\; H)\times\mathbb{R},\; H>0,$ and set on the right boundary $\operatorname{curl} \hat{\E} = 0$.
 
-}
+In this article we concentrate on a simplified model (which nevertheless is of physical interest when modelling antennas in plasmas), 
+where it is required to study the above system under the assumption that the electron density $N_{e}$ and the magnetic field $B_0$ are \textbf{uniform} in the second coordinate, more precisely 
+$N_{e}=N_{e}(x)$ and $B_0=B_0(x)$, see e.g. \cite{Despres_2014}. Even this simplified case contains difficulties intrinsic to hybrid resonance \cite{Despres_2014, singular_solutions}.
 
-Hence, recalling that $N_e=N_e(x), \; B_0=B_0(x)$, we perform the Fourier transform in $y$ ($\partial_y\rightarrow i\theta, \; \theta\in\mathbb{R},$) and consider the one-dimensional setting
+The one-dimensional model can be derived from (\ref{eq:main_system}) by performing the Fourier transform in $y$ ($\partial_y\rightarrow i\theta, \; \theta\in\mathbb{R}$), 
+under the assumption that $N_e=N_e(x), \; B_0=B_0(x)$
 
@@
 \end{equation}
- posed in $(-L,\; H)$, for some $L,H>0$, with the boundary conditions 
- \begin{align*}
-  \left.\left(-\partial_x E_y+i\theta E_x -\imath \lambda E_y\right)\right|_{x=-L} =g_{inc},\\
+ posed in $(-L,\; H)$, for some $L,H>0$, with \mrev{the (simplified) boundary conditions compatible with (\ref{eq:boundary_conditions_intro})}
+ \begin{align}
+ \label{eq:boundary_conditions_frequency_domain}
+  \left.\left(-\partial_x E_y -\imath \lambda E_y\right)\right|_{x=-L} =g_{inc},\\
   \left.\partial_xE_y\right|_{x=H}=0.
- \end{align*}
-This is the model that will be considered in the rest of the article, unless stated otherwise. 
-\urev{
-Indeed, the dielectric tensor for this problem with $\nu=0$ and its coefficients $\alpha_{\omega},\;\delta_{\omega}$, 
-see \ref{eq:alpha_delta}, depend solely on $x$, $\omega$ and $\theta$.
+ \end{align}
+This is the time-domain model that will be considered in the rest of the article, unless stated otherwise.
 
-We concentrate on the physical situation of the hybrid resonance, which we define as in \cite{singular_solutions}.
+In the frequency domain (\ref{eq:main_model}) for $\nu=0$ is of the form 
+\begin{align}
+\label{eq:main_frequency_domain_intro}
+\left(
+\begin{matrix}
+ i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
+ i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
+\end{matrix}
+\right)-\frac{\omega^2}{c^2}
+\underline{\varepsilon}_{\omega}^{0}(x)\left(
+\begin{matrix}
+ \hat{E}_x\\
+ \hat{E}_y
+\end{matrix}
+\right)
+=0,
+\end{align}
+see (\ref{eq:alpha_delta}). Indeed, the coefficients $\alpha_{\omega},\;\delta_{\omega}$ depend solely on $x$ and $\omega$.  
+\arev{
+We concentrate on a physical situation of the hybrid resonance, which we define as in \cite{singular_solutions}.
 \begin{df}
-Let $\omega,\theta\in\mathbb{R}$ be fixed. 
+Let $\omega\in\mathbb{R}$ be fixed. 
 We will call a point $x_h\in \mathbb{R}$ a hybrid resonance if $\alpha_{\omega}$ has 
-a simple root in $x_h$ and has no other roots in an $\epsilon$-vicinity of $x_h$ $B_{\epsilon}(x_h)$, for some $\epsilon>0$. 
+a simple root in $x_h$ and has no other roots in an $\epsilon$-vicinity of $x_h$ $B_{\epsilon}(x_h)$, for some $\epsilon>0$, and 
+$\delta(x_h)\neq 0$. 
 \end{df}
 }
+
+To investigate the behaviour of the solutions in the vicinity of the hybrid resonance, 
+instead of the above problem we will study a sequence of the regularized problems 
+\begin{align}
+\label{eq:seq_regularized}
+\left(
+\begin{matrix}
+ i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
+ i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
+\end{matrix}
+\right)-\frac{\omega^2}{c^2}
+\left(\underline{\varepsilon}_{\omega}^{0}(x)+i\nu \mathrm{Id}\right)\left(
+\begin{matrix}
+ \hat{E}_x\\
+ \hat{E}_y
+\end{matrix}
+\right)
+=0,
+\end{align}
+where $\mathrm{Id}$ is the identity matrix. More details on the connection of this problem with (\ref{eq:main_model}) will be provided in further sections.
+
  %This domain represents the physical case of a wave sent from a wall facing a plasma.
@@
 First, we investigate the finite element approximation of the 1D 
-problem \eqref{eq:main_model} written in the frequency domain ($\partial_t\rightarrow -i\omega$), with a dielectric tensor \mrev{regularized
-with the help of a small parameter $\nu$}. More details on regularization will be given in further sections. 
+problem (\ref{eq:seq_regularized}), with a dielectric tensor \mrev{regularized
+with the help of a small parameter $\nu$}. 
 %linearized with respect to $\nu$.
-We prove the well-posedness of this problem for $\nu>0$ in Section~\ref{sec:wellposedness} and 
+We prove the well-posedness of this problem for \mrev{$\nu\neq 0$} in Section~\ref{sec:wellposedness} and 
 demonstrate that the use of  (P1) finite elements allows to approximate the singularity 
 of the solution fairly well (Section \ref{sec:freq_dep}). 
+}
 
@@
 $\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
-\textcolor{red}{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principles. 
+\urev{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principles. 
 In application to e.g. non-resonant case of (\ref{eq:model_freq_domain}), the limited absorption principle states that with 
@@
 see Figure \ref{fig:limits}. 
-Even though it is true for standard linear wave problems, it is not clear \mrev{if it still holds} in our case due the singularity
+Even though it is true for standard linear wave problems, it is not clear \mrev{if it still holds} in our case due to the singularity
 of the hybrid resonance.

### 2015-05-03 report_clean/FD.tex
intro looks a bit more reasonable now

@@
  \alpha^{\nu}_{\omega}=\alpha_{\omega}+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{\omega(\omega^2-\omega_c^2)^2}=\alpha_{\omega}+i\nu D_{\alpha},\\
- \delta^{\nu}_{\omega}=\delta_{\omega}-i\nu\frac{2\omega_c\omega_p^2}{(\omega^2-\omega_c^2)^2}=\alpha_{\omega}+i\nu D_{\delta},
+ \delta^{\nu}_{\omega}=\delta_{\omega}-i\nu\frac{2\omega_c\omega_p^2}{(\omega^2-\omega_c^2)^2}=\delta_{\omega}+i\nu D_{\delta},
 \eealn
@@
 \ben
-\varepsilon^{\nu}_{\omega}(\mathbf{r})\approx \varepsilon^{0}_{\omega}(\mathbf{r})+i\nu \mathbb{E}
+\varepsilon^{\nu}_{\omega}(\mathbf{r})\approx \varepsilon^{0}_{\omega}(\mathbf{r})+i\nu \mathrm{Id}
 \een
@@
 \end{assumption}
-This assumption can be ensured, for example, by requiring the continuity of $N_e(x), B_0(x) \in [-L,\;H]$ and the absence of the cyclotron resonance, i.e.
+This assumption can be ensured, for example, by requiring the continuity of $N_e(x), B_0(x)$ in $[-L,\;H]$ and the absence of the cyclotron resonance, i.e.
 for all $x$ $|\omega_c^2(x)-\omega^2(x)|>c>0$ on this interval.
@@
 \begin{array}{l}
-\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\tilde E_y' -i \theta \tilde E_x)} - \int_{-L}^H (\varepsilon^{0} +i\nu Id) \E \cdot \overline{\tilde \E}
+\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\tilde E_y' -i \theta \tilde E_x)} - \int_{-L}^H (\varepsilon^{0} +i\nu \mathrm{Id}) \E \cdot \overline{\tilde \E}
 %\\ \displaystyle 

### 2015-05-03 report_clean/intro.tex
intro looks a bit more reasonable now

@@
 \end{align}
-coupled with an equation for the linear electronic current  $\J = eN_e(\mathbf{r}) \ubf$, 
+coupled with the equations for the linear electronic current  $\J = eN_e(\mathbf{r}) \ubf$
 \begin{align}
@@
 
-The energy of this system in a domain $\Omega\in\mathbb R^2$ can be expressed as, see \cite{Despres_2014}
+The energy of this system in a domain $\Omega\in\mathbb R^2$ can be expressed as, see \cite{Despres_2014},
 \ben
@@
 \label{eq:boundary_conditions_intro}
-curl \hat{\mathbf{E}} -\imath \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} =curl \E_{inc} -\imath\lambda\E_{inc}\wedge \n,
+curl \hat{\mathbf{E}} -i \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} =curl \E_{inc} -\imath\lambda\E_{inc}\wedge \n,
 \ee
@@
 
-The one-dimensional model can be derived from (\ref{eq:main_system}) by performing the Fourier transform in $y$ ($\partial_y\rightarrow i\theta, \; \theta\in\mathbb{R}$), 
-under the assumption that $N_e=N_e(x), \; B_0=B_0(x)$
-
+Under the aforementioned assumptions on $N_e$ and $B_0$, the one-dimensional model can be derived from (\ref{eq:main_system}) by performing the Fourier transform in $y$ ($\partial_y\rightarrow i\theta, \; \theta\in\mathbb{R}$).
+For a parameter $\theta$,
 \begin{equation}
@@
 \end{equation}
- posed in $(-L,\; H)$, for some $L,H>0$, with \mrev{the (simplified) boundary conditions compatible with (\ref{eq:boundary_conditions_intro})}
+ posed in $(-L,\; H)$, for some $L,H>0$, with \mrev{the boundary conditions as in (\ref{eq:boundary_conditions_intro}),
  \begin{align}
  \label{eq:boundary_conditions_frequency_domain}
-  \left.\left(-\partial_x E_y -\imath \lambda E_y\right)\right|_{x=-L} =g_{inc},\\
-  \left.\partial_xE_y\right|_{x=H}=0.
+ \begin{split}
+  \left.\left(\partial_x E_y -i\theta E_x-i\lambda E_y\right)\right|_{x=-L} =g_{inc}(t),\\
+  \left.\partial_xE_y\right|_{x=H}=0, 
+  \end{split}
  \end{align}
+and the initial conditions for values $\left.E_{x}\right|_{t=0},\; \left.u_{x}\right|_{t=0},\; \left.E_{y}\right|_{t=0}, \; \left.u_{y}\right|_{t=0}, \; \left.H_z\right|_{t=0}$. }
+
 This is the time-domain model that will be considered in the rest of the article, unless stated otherwise.
@@
 We will call a point $x_h\in \mathbb{R}$ a hybrid resonance if $\alpha_{\omega}$ has 
-a simple root in $x_h$ and has no other roots in an $\epsilon$-vicinity of $x_h$ $B_{\epsilon}(x_h)$, for some $\epsilon>0$, and 
+a simple root in $x_h$ and has no other roots in an $\epsilon$-vicinity of this point $B_{\epsilon}(x_h)$, for some $\epsilon>0$, and 
 $\delta(x_h)\neq 0$. 
@@
 
-To investigate the behaviour of the solutions in the vicinity of the hybrid resonance, 
-instead of the above problem we will study a sequence of the regularized problems 
+To investigate the behaviour of the solutions in the case when the hybrid resonance occurs in the sustem, 
+instead of the above problem we will study a sequence of the regularized problems, for $\nu\rightarrow 0$, 
 \begin{align}
@@
 We compare this result with 
-$\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
+$\hat{\mathbf{E}}\mathrm{e}^{\mrev{-i\omega} t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
 $\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.

### 2015-05-03 report_clean/numerics.tex
intro looks a bit more reasonable now

--- 2015-04-30 report_clean/numerics.tex
@@
 decays rapidly as $x\rightarrow \infty$. }
-\mrev{Hence, choosing $H$ sufficiently large (the actual value used in the experiments $H=10$, where $\Ai'(10)\approx -3.5e-10$) and the boundary conditions as 
+\mrev{Hence, choosing $H$ sufficiently large (the actual value used in the experiments $H=10$, where $\left|\Ai'(10)\right|<1e-9$) and the boundary conditions as 
 \begin{align}

### 2015-05-03 report_clean/responce_reviewers.tex
timedomain, intro, frequency domain tex should look better now

@@
 - p4: we changed $\alpha_{\nu}$ to $\beta_{\nu}$ not to confuse with $\alpha$ in the dielectric tensor. The index $\nu$ 
-just underlines the dependence of this angle $\beta_{\nu}$ on $\nu$.
+just underlines the dependence of this angle $\beta_{\nu}$ on $\nu$ (indeed, the coercivity result as it is stated, holds for this specific value of $\beta_{\nu}$ stated 
+in the end of the proof of the lemma).
 

### 2015-05-03 report_clean/FD.tex
timedomain, intro, frequency domain tex should look better now

@@
 $\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane. \arev{Note that neither cyclotron, nor hybrid resonances occur in the problem 
-with the dielectric tensor $\varepsilon^{\nu}_{\omega}(\mathbf{r}), \; \nu>0$ (since all parameters are real). Hence 
+with the dielectric tensor $\varepsilon^{\nu}_{\omega}(\mathbf{r}), \; \nu>0$ (since all the parameters are real). Hence 
 the choice of the non-zero plasma friction $\nu>0$ can be viewed as a regularization of the problem. }
@@
 \ben
-\varepsilon^{\nu}_{\omega}(\mathbf{r})\approx \varepsilon^{0}_{\omega}(\mathbf{r})+i\nu \mathrm{Id}
+\underline{\varepsilon}^{\nu}_{\omega}(\mathbf{r})\approx \underline{\varepsilon}^{0}_{\omega}(\mathbf{r})+i\nu \mathrm{Id}
 \een
@@
 \right)-\frac{\omega^2}{c^2}
-\left(\varepsilon^{0}_{\omega}(x)+i\nu \mathrm{Id}\right)\left(
+\left(\underline{\varepsilon}^{0}_{\omega}(x)+i\nu \mathrm{Id}\right)\left(
 \begin{matrix}
@@
 =0,\\
-\varepsilon^0_{\omega}(x)=\left(
+\underline{\varepsilon}^0_{\omega}(x)=\left(
 \begin{matrix}
@@
 \mrev{
-For simplicity, from now on we will denote $\alpha_{\omega},\; \delta_{\omega}$ by $\alpha,\; \delta$ and consider a sequence of regularized problems. 
+For brevity, from now on we will denote $\alpha_{\omega},\; \delta_{\omega}$ by $\alpha,\; \delta$ and consider a sequence of regularized problems. 
 \begin{align}
@@
 \right)-
-\left(\varepsilon^{0}(x)+i\nu \mathrm{Id}\right)\left(
+\left(\underline{\varepsilon}^{0}(x)+i\nu \mathrm{Id}\right)\left(
 \begin{matrix}
@@
 \label{eq:epsilon_0}
-\varepsilon^{0}(x)=\left(
+\underline{\varepsilon}^{0}(x)=\left(
 \begin{matrix}
@@
 \end{align}
-where $\alpha,\;\delta$ satisfy the following.
+where $\alpha,\;\delta$ satisfy the following assumption.
 }
@@
 For the time domain problem (\ref{eq:main_model}) the choice of the sign of $\nu>0$ is of crucial importance for the stability of the problem. 
-In the frequency domain, as we can see from above and from \cite{Despres_2014,LMIG_thesis}, the sign 
+In the frequency domain, as we can see from the above and from \cite{Despres_2014,LMIG_thesis}, the sign 
 of the parameter $\nu$ can be chosen arbitrarily to regularize the problem. However, as demonstrated in the aforementioned works, as $\nu\rightarrow 0\pm$, the 
-corresonding limiting solutions differ, though both exhibit the singularity in the point of the hybrid resonance.  
+corresponding limiting solutions differ, though both exhibit the singularity in the point of the hybrid resonance.  
 \end{remark}
@@
 \begin{array}{l}
-\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\tilde E_y' -i \theta \tilde E_x)} - \int_{-L}^H (\varepsilon^{0} +i\nu \mathrm{Id}) \E \cdot \overline{\tilde \E}
+\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\tilde E_y' -\urev{i} \theta \tilde E_x)} - \int_{-L}^H (\varepsilon^{0} +i\nu \mathrm{Id}) \E \cdot \overline{\tilde \E}
 %\\ \displaystyle 
@@
 %=\omega\geq 0$. 
-Let us remark that in this and further sections, where it is not ambiguous, we will use the notation $E_{x,y}$ instead of $\hat{E}_{x,y}$ for convenience.
+Let us remark that in this and further sections, where it is not ambiguous, we will use the notation $E_{x,y}$ instead of $\hat{E}_{x,y}$ for convenience, \mrev{
+and $\|.\|_{L^2}$ and $\|.\|_{H^1}$ will denote the norms in $L^2(\Omega)$ and $H^1(\Omega)$. }
 
-The above can be reformulated as 
+The above can be reformulated as, \urev{for the unknown $\mathbf{E}$ and $\tilde{\mathbf{E}}$ a test function},
 \be
-a\left(\mathbf{E},\mathbf{v}\right)=l(\mathbf{v}), \; \text{ for all }\mathbf{v}\in \mathbf{V},
+a\left(\mathbf{E},\tilde{\mathbf{E}}\right)=l(\tilde{\mathbf{E}}), \; \text{ for all }\tilde{\mathbf{E}}\in \mathbf{V},
 \ee
-with a bilinear form $a$ and a linear form $l$:
+with a bilinear form $a$ and a linear form $l$, \urev{defined for $\mathbf{u},\; \mathbf{v}\in \mathbf{V}$}:
 \be
@@
 \ee
-The unknown is $\mathbf{E}=(E_x,E_y)$ and $\vbf$ is a test function.
 
 \urev{
-Let us denote the spectral radius of $\varepsilon^{0}$ by $\heps =  \|\rho(\varepsilon^{0})\|_{L^{\infty}[-L,\;H]}$. 
-By Assumption \ref{assumption:smooth}, the spectral radius $\heps=\max\left(\|\alpha+\delta^2\|_{L^{\infty}[-L,\;H]}, \|\alpha-\delta^2\|_{L^{\infty}[-L,\;H]}\right)$ 
+Let us denote the spectral radius of $\underline{\varepsilon}^{0}$ by $\heps =  \|\rho(\underline{\varepsilon}^{0})\|_{L^{\infty}(\Omega)}$. 
+By Assumption \ref{assumption:smooth}, the spectral radius $\heps=\max\left(\|\alpha+\delta^2\|_{L^{\infty}(\Omega)}, \|\alpha-\delta^2\|_{L^{\infty}(\Omega)}\right)$ 
 is bounded.}
@@
 \left\{\begin{array}{l}
-\Re\left(\mathrm{e}^{i\beta_{\nu}}a(\ubf,\ubf)\right)\geq \frac{|\nu|}{\sqrt{(\heps+\theta^2+1)^2+\nu^2}}\left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right),\; 
-\text{ for some $\beta_{\nu}\in\left(-\frac{\pi}{2}, 0\right)\cup \left(0,\frac{\pi}{2}\right)$},\\
+\Re\left(\mathrm{e}^{i\urev{\beta_{\nu}}}a(\ubf,\ubf)\right)\geq \frac{|\nu|}{\sqrt{(\heps+\theta^2+1)^2+\nu^2}}\left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right),\; 
+\text{ for some $\urev{\beta_{\nu}}\in\left(-\frac{\pi}{2}, 0\right)\cup \left(0,\frac{\pi}{2}\right)$},\\
 |a(\ubf,\vbf)|\leq C \|\ubf\|_{\mathbf{V}}\|\vbf\|_{\mathbf{V}},
@@
 \end{lemma}
-%\textcolor{red}{!!!! redo coercivity computations !!!}
 \begin{proof}
 	The boundedness of $a$ is obvious using the continuous embedding in dimension
-	one  $H_1(\Omega)\subset C^0(\overline \Omega)$. Let us focus on the proof of coercivity. 
-	Without loss of generality let us assume that $\nu>0$. \mrev{Given $\heps$ the spectral radius of $\varepsilon^{0}$, 
-	$\heps Id- \varepsilon^{0} $ is a non negative hermitian matrix.}
+	one  $H^1(\Omega)\subset C^0(\overline \Omega)$. Let us focus on the proof of coercivity. 
+	Without loss of generality let us assume that $\nu>0$. \mrev{Given $\heps$ the spectral radius of $\underline{\varepsilon}^{0}$, 
+	$\heps \mathrm{Id}- \underline{\varepsilon}^{0} $ is a non-negative hermitian matrix.}
 	Therefore
 	\be 
-	a_1(\ubf,\ubf) + \heps\|\ubf\|^2_{L^2}= \|u_2' - i \theta u_1 \|^2_{L^2} + \left( (\heps Id - \varepsilon^{0} ) \ubf, \overline{\ubf} \right)  \geq \|u_2 ' - i \theta u_1 \|_{L^ 2}^ 2
+	a_1(\ubf,\ubf) + \heps\|\ubf\|^2_{L^2}= \|u_2' - i \theta u_1 \|^2_{L^2} + \left( (\heps \mathrm{Id} - \underline{\varepsilon}^{0} ) \ubf, \overline{\ubf} \right)  \geq \|u_2 ' - i \theta u_1 \|_{L^ 2}^ 2
 	\geq \frac12 \|u_2 '  \|_{L^ 2}^ 2 -
@@
 \end{proof}
-
 \begin{remark} 
@@
 as a system of two equations, where the first equation (for $E_y$) is the variational formulation for the Helmholtz equation 
-with the variable coefficient $k^2=(\alpha-\frac{\delta^2}{\alpha})$, and the second equation 
+with the variable coefficient $k^2=(\alpha-\frac{\delta^2}{\alpha})$ \mrev{and the boundary conditions (\ref{eq:boundary_conditions_frequency_domain})}, and the second equation 
 \begin{align*}
@@
 was demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H^{1}(\Omega)$, we can obtain $E_x$ from the second equation.
-
-%%Let us consider the problem (\ref{eq:var_form2}) for $\nu=0,\; \theta=0$, which, after testing it 
-%%with $(\tilde{E}_x,\; 0)$ and $(0,\; \tilde{E}_y)$ from $\mathbf{V}$, can be rewritten as, see also (\ref{eq:epsilon_0})
-%%\begin{align}
-%%\label{eq:full_var}
-%%\begin{split}
-%%\int_{-L}^H \left(\alpha E_x+i\delta E_y \right)_{1} \overline{\tilde E}_{x}&=0,\; \text{ for all }\tilde{E}_x\in L^{2}(\Omega), \;\\
-%%\displaystyle \int_{-L}^H E_y'\tilde {E_y'} - \int_{-L}^H\left( -i\delta E_x+\alpha E_y \right)_{2}\overline{\tilde{E}}_{y}
-%%  - i \lambda E_y (-L) \overline{\tilde E_y} (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
-%%  \text{ for all }  \tilde{E}_{y}\in H^{1}(\Omega).
-%%  \end{split}
-%%\end{align}
-%%The first equation of the above can be rewritten as 
-%%\ben
-%% \left(E_x,\alpha \tilde{E}_x\right)=-\left(i\delta E_y,  \tilde{E}_x\right).
-%%\een
-%%If the multiplication operator $M_{\alpha}$ defined as $M_{\alpha}\psi=\frac{1}{\alpha}\psi$ is an isomorphism from $L^{2}([-L,\;H])$ to $L^{2}([-L,\;H])$ (this is true if e.g.
-%%$\alpha \in C_{0}([-L,\;H])$ and $|\alpha(x)|>c>0$, for some $c>0$, on the whole interval), this equation is equivalent to 
-%%\begin{align}
-%%\label{eq:mult_eq}
-%%  \left(E_x,u\right)=-\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega). 
-%%\end{align}
-
-%%Choosing in the above $u=-i\delta \tilde{E}_y \in L^{2}(\Omega)$ and adding it to the second equation of (\ref{eq:full_var}), we obtain
-%%\bealn
-%% \displaystyle \int_{-L}^H E_y'\tilde {E_y'} - \int_{-L}^H (\alpha-\frac{\delta^2}{\alpha})E_y \overline{\tilde{E}}_{y}
-%%  - i \lambda E_y (-L) \overline{\tilde E_y} (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
-%%  \text{ for all } \tilde{E}_{y}\in H^{1}(\Omega). \nonumber
-%%\eealn
-%%Thus we obtain the variational formulation for $E_y$, or the variational formulation for the Helmholtz equation. The well-posedness 
-%%of this problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
-%%had been demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H^{1}(\Omega)$, we can obtain $E_x$ from the equation (\ref{eq:mult_eq}).
 \end{remark}
@@
 \int_{-L}^H\left( -i \delta E_x+(\alpha+i\nu) E_y\right)_{2}\overline{\tilde{E}}_{y}
-  - i \lambda E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
+  - i \lambda E_y (-L) \overline{\tilde E_y (-L)} &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
  \text{ for all } \tilde E_x\in L^{2}(\Omega), \; \tilde{E}_{y}\in H^{1}(\Omega).
@@
 % \end{align*}
-Introducing the notation
+Introducing
 \bealn
@@
 \een
-This expression greatly simplifies when \mrev{ choosing $V_{E_x}=V_{E_{y}}$, spanned by $\left(\phi_{m}\right)_{m=1}^{N_{2}}$,} and
-in the case $\theta=0$. One obtains the \mrev{matrix} structure
+This expression greatly simplifies when \urev{ choosing $V_{E_x}=V_{E_{y}}$, spanned by $\left(\phi_{m}\right)_{m=1}^{N_{2}}$,} and
+in the case $\theta=0$. One obtains the \urev{matrix} structure
 \begin{align}

### 2015-05-03 report_clean/intro.tex
timedomain, intro, frequency domain tex should look better now

@@
 \urev{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principles. 
-In application to e.g. non-resonant case of (\ref{eq:model_freq_domain}), the limited absorption principle states that with 
-appropriately chosen boundary conditions the solution of (\ref{eq:seq_regularized}) 
-as $\nu\rightarrow 0\pm$ 
-would coincide with the solution of (\ref{eq:model_freq_domain}). Similarly, the limiting amplitude principle applied to the problem (\ref{eq:main_system}) 
-states that if the boundary conditions are chosen harmonic in time, e.g. $\partial_x E_y=\mathrm{e}^{-i\omega_{*} t}$ on 
-the boundary, then the solution of this problem $(\mathbf{E}(t),\;H(t))$ asymptotically ($t\rightarrow +\infty$)
+In application to a non-resonant case of (\ref{eq:main_frequency_domain_intro}), equipped with boundary conditions, the limited absorption principle states that the solution of (\ref{eq:seq_regularized}) would coincide with the solution of (\ref{eq:main_frequency_domain_intro})
+as $\nu\rightarrow 0\pm$. Similarly, the limiting amplitude principle applied to the problem (\ref{eq:main_model}) 
+states that if the boundary conditions are chosen harmonic in time, e.g.
+$\left.\partial_x E_y\right|_{x=-L}=\mathrm{e}^{-i\omega_{*} t}$, then the solution of this problem $(\mathbf{E}(t),\;H(t))$ asymptotically ($t\rightarrow +\infty$)
 tends to a steady state of the form $ \left(\mathbf{E}(\omega_{*}),\; \hat{H}(\omega_{*})\right)\mathrm{e}^{-i\omega_{*} t}$, where 
 $\left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)$ is the solution of (\ref{eq:main_model})
-in the frequency domain, with $\omega=\omega_{*}$. For more details see e.g. \cite{Morawetz, Eidus}. The commutation between the two principles then write as}
+in the frequency domain, with $\omega=\omega_{*}$ and the boundary condition $\left.\partial_x \hat{E}_y\right|_{x=-L}=1$.
+For more details see e.g.
+\cite{Morawetz, Eidus}.
+The commutation between the two principles then write as}
 $$

### 2015-05-03 report_clean/timedomain.tex
timedomain, intro, frequency domain tex should look better now

@@
 We summarize this discretization on Fig.~\ref{schemepos} where the positions 
-of \mrev{$E_x$}, $u_x$ (black dots), $E_y$, $u_y$ (blue dots) and $H_z$ (red dots) 
+of \urev{$E_x$}, $u_x$ (black dots), $E_y$, $u_y$ (blue dots) and $H_z$ (red dots) 
 on the discretized grid in space and time are shown. The fully discretized system then reads

### 2015-05-03 report_clean/responce_reviewers.tex
fixed extra stupid bugs

@@
 front of them)
+- corrected the formulation of the lemma on the well-posedness and added a remark after the lemma on the sign of $\nu$.
 
@@
 
- - p.8: added the Airy equation. Additionally added a remark on the behaviour of the Airy function to justify the choice of the right boundary 
+ - p.8: added the Airy equation and pointed out the analyticity of the Airy equation. Additionally added a remark on the behaviour of the Airy function to justify the choice of the right boundary 
  condition $\partial_x E=0$.

### 2015-05-03 report_clean/FD.tex
fixed extra stupid bugs

@@
 In the frequency domain, as we can see from the above and from \cite{Despres_2014,LMIG_thesis}, the sign 
-of the parameter $\nu$ can be chosen arbitrarily to regularize the problem. However, as demonstrated in the aforementioned works, as $\nu\rightarrow 0\pm$, the 
+of the parameter $\nu$ can be chosen arbitrarily to regularize the problem. 
+However, as demonstrated in the aforementioned works, as $\nu\rightarrow 0\pm$, the 
 corresponding limiting solutions differ, though both exhibit the singularity in the point of the hybrid resonance.  
@@
 }
-
 %%%%%%%%%%%%%%%%%%%%%% 
@@
 %=\omega\geq 0$. 
-Let us remark that in this and further sections, where it is not ambiguous, we will use the notation $E_{x,y}$ instead of $\hat{E}_{x,y}$ for convenience, \mrev{
-and $\|.\|_{L^2}$ and $\|.\|_{H^1}$ will denote the norms in $L^2(\Omega)$ and $H^1(\Omega)$. }
+Let us remark that in this and further sections, where it is not ambiguous, we will use the notation $E_{x,y}$ instead of $\hat{E}_{x,y}$ for convenience. \mrev{Also, 
+by $\|u\|_{L^{2}}$ we will denote $\|u\|_{L^{2}(\Omega)}$, for $u\in L^2(\Omega)$, and $\|\ubf\|_{L^2(\Omega)}=\left(\|u_1\|^2_{L_2}+\|u_2\|^2_{L_2}\right)^{\frac{1}{2}}$, 
+for $\ubf=(u_1,\;u_2)\in \left(L^2(\Omega)\right)^2$.}
 
@@
 \label{lemma:well_posedness}
-Provided that Assumption \ref{assumption:smooth} holds, the bilinear form 
+\urev{Let Assumption \ref{assumption:smooth} holds}. Then the bilinear form 
 \ben
@@
 \een
-is continuous and coercive for all $\nu\neq 0$: for all $\ubf,\vbf\in \mathbf{V}$ it holds that
+is continuous and coercive for all \mrev{$\lambda\geq 0$} and $\nu>0$: for all $\ubf,\vbf\in \mathbf{V}$ it holds that
 \bealn
@@
 \Re\left(\mathrm{e}^{i\urev{\beta_{\nu}}}a(\ubf,\ubf)\right)\geq \frac{|\nu|}{\sqrt{(\heps+\theta^2+1)^2+\nu^2}}\left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right),\; 
-\text{ for some $\urev{\beta_{\nu}}\in\left(-\frac{\pi}{2}, 0\right)\cup \left(0,\frac{\pi}{2}\right)$},\\
+\text{ for some $\urev{\beta_{\nu}}\in\left(0,\frac{\pi}{2}\right)$},\\
 |a(\ubf,\vbf)|\leq C \|\ubf\|_{\mathbf{V}}\|\vbf\|_{\mathbf{V}},
@@
 	one  $H^1(\Omega)\subset C^0(\overline \Omega)$. Let us focus on the proof of coercivity. 
-	Without loss of generality let us assume that $\nu>0$. \mrev{Given $\heps$ the spectral radius of $\underline{\varepsilon}^{0}$, 
+	\mrev{Given $\heps$ the spectral radius of $\underline{\varepsilon}^{0}$, 
 	$\heps \mathrm{Id}- \underline{\varepsilon}^{0} $ is a non-negative hermitian matrix.}
@@
 	a_1(\ubf,\ubf) + \heps\|\ubf\|^2_{L^2}= \|u_2' - i \theta u_1 \|^2_{L^2} + \left( (\heps \mathrm{Id} - \underline{\varepsilon}^{0} ) \ubf, \overline{\ubf} \right)  \geq \|u_2 ' - i \theta u_1 \|_{L^ 2}^ 2
-	\geq \frac12 \|u_2 '  \|_{L^ 2}^ 2 -
-	\theta ^2 \| u_1 \|_{L^ 2}^ 2.
+	\geq \frac12 \|u_2 '  \|_{L^2}^ 2 -
+	\theta ^2 \| u_1 \|_{L^2}^ 2.
 	\ee
@@
 	a_1(\ubf,\ubf)  \geq \frac{1}{2}\|u_2'\|^2_{L^2}-  (\heps  +  \theta^2) \| \ubf \|_{L^2}^2$.
-	One also has that
+	One also has that, \mrev{for $\lambda \geq 0$},
 	$
@@
 \end{proof}
+\begin{remark}
+\mrev{Note that in the case $\lambda=0$, one can show that the problem is well-posed for all $\nu\neq 0$, since $a_2(\ubf,\ubf)=-\nu\|\ubf\|_{L^2}^2$ and 
+thus in the above proof
+\begin{align*}
+a_1(\ubf,\ubf)-\frac{\heps  +  \theta^2 + 1 }\nu a_2(\ubf,\ubf)=\left(a_1(\ubf,\ubf)+(\heps  +  \theta^2)\|\ubf\|_{L^2}^2\right)+\|\ubf\|_{L^2}^2.
+\end{align*}
+Similarly, in the case $\lambda<0$, it is possible to demonstrate the well-posedness of the problem for $\nu<0$. 
+}
+\end{remark}
 \begin{remark} 
@@
 \end{align}
-\urev{Let us introduce two function spaces $V_{E_x}\subset L_{2}(\Omega)$ spanned by the basis function set $\{\psi_{j}\}_{j=1}^{N_{1}}$ and $V_{E_{y}}\subset H_{1}(\Omega)$ spanned by 
+\urev{Let us introduce two function spaces $V_{E_x}\subset L^{2}(\Omega)$ spanned by the basis function set $\{\psi_{j}\}_{j=1}^{N_{1}}$ and $V_{E_{y}}\subset H^{1}(\Omega)$ spanned by 
 the set $\{\phi_{i}\}_{i=1}^{N_{2}}$. }

### 2015-05-03 report_clean/intro.tex
fixed extra stupid bugs

@@
 \ee
-where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and $\lambda$ is 
+where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and \mrev{$\lambda\geq 0$} is 
 the frequency of the antenna. We truncate the domain 
@@
 In application to a non-resonant case of (\ref{eq:main_frequency_domain_intro}), equipped with boundary conditions, the limited absorption principle states that the solution of (\ref{eq:seq_regularized}) would coincide with the solution of (\ref{eq:main_frequency_domain_intro})
-as $\nu\rightarrow 0\pm$. Similarly, the limiting amplitude principle applied to the problem (\ref{eq:main_model}) 
+as $\nu\rightarrow 0$. Similarly, the limiting amplitude principle applied to the problem (\ref{eq:main_model}) 
 states that if the boundary conditions are chosen harmonic in time, e.g.

### 2015-05-03 report_clean/numerics.tex
fixed extra stupid bugs

@@
 of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
-performed with the help of \mrev{our} code written in Octave.  
+performed with the help of \urev{our} code written in Octave.  
 We implemented the scheme described in Section \ref{sec:discr} for a case of $P_{1}$-space used 
@@
 and time domain codes }(computed for large values of time). 
-The time-domain code implements the scheme described in \mrev{Section \ref{sec:staggered_discretization}} and 
+The time-domain code implements the scheme described in \urev{Section \ref{sec:staggered_discretization}} and 
 is written in Fortran.
@@
 \subsubsection{Validity of the Implementation}
+\label{sec:airy_fd_validity}
 To check the validity of the code, we first perform a numerical experiment with (formally chosen) parameters:
@@
 \end{align*}
-One of the solutions of this equation, an Airy function $\Ai(x)$, see \cite[Chapter 10.4]{abramowitz_stegun}, is analytic and 
+One of the solutions of this equation, an Airy function \urev{$\Ai(x)$}, see \cite[Chapter 10.4]{abramowitz_stegun}, is analytic and 
 decays rapidly as $x\rightarrow \infty$. }
@@
 Chapter 0.4]{brenner}, \mrev{provided that the Aubin-Nitsche lemma \cite[Theorems 3.2.4,3.2.5]{ciarlet_fem} holds for the variational formulation.}  
-\urev{Since the coefficients of the problem are smooth, we expect the solution to be at least in $C^2(\Omega)$.}  
 \begin{figure}
@@
     \end{tikzpicture}
-    \caption{Convergence rates for \mrev{the problem (\ref{eq:main_frequency_domain}) discretized as (\ref{eq:simple_system})} 
-    with the parameters (\ref{eq:parameters}) and the \mrev{boundary condition (\ref{eq:bcs_airy})}. \mrev{Here $E_{y}^{c}(x)=\Ai(x)$ and 
-    $E_{x}^{c}(x)=-i\frac{\delta(x)}{\alpha(x)}\Ai(x)$.} }
+    \caption{Convergence rates for the \mrev{problem described in Section \ref{sec:airy_fd_validity} (the problem (\ref{eq:main_frequency_domain}) discretized as (\ref{eq:simple_system})} 
+    with the parameters (\ref{eq:parameters}) and the \mrev{boundary condition (\ref{eq:bcs_airy}))}. \mrev{Here $E_{y}^{c}(x)=\Ai(x)$ and 
+    $E_{x}^{c}(x)=-i\frac{\delta(x)}{\alpha(x)}\Ai(x)$.}}
     \label{fig:conv_rate}
@@
 \end{align}
-Given $\mathbf{V}_{h}=P_{h}^{1}\times P_{h}^{1}$, with $P_{h}^{1}$ consisting of piecewise-linear (hat) functions, 
-\mrev{and $E^{\nu}_{x},\;E^{\nu,h}_{x}$ being correspondingly the exact solution and the solution computed with the help $\mathbf{V}_h$, }
+\mrev{Let $h>0$ denote the meshwidth. }Given $\mathbf{V}_{h}=P_{h}^{1}\times P_{h}^{1}$, with $P_{h}^{1}$ consisting of piecewise-linear (hat) functions, 
+\mrev{and $E^{\nu}_{x},\;E^{\nu,h}_{x}$ being correspondingly the exact and the numerical solution, }
 we look for a ratio $h(\nu)$ that would ensure the bound on the absolute error 
@@
 \begin{split}
- \|\mathbf{E}^{\nu}-\mathbf{E}^{\nu,h}\|_{V}\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in V_h}\|\mathbf{E}^{\nu}-\mathbf{v}\|_{V}
- \leq C\nu^{-1}\min_{\mathbf{v}\in V_h}\|\mathbf{E}^{\nu}-\mathbf{v}\|_{V},\; C>0.
+ \|\mathbf{E}^{\nu}-\mathbf{E}^{\nu,h}\|_{\mathbf{V}}\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in \mathbf{V}_h}\|\mathbf{E}^{\nu}-\mathbf{v}\|_{V}
+ \leq C\nu^{-1}\min_{\mathbf{v}\in \mathbf{V}_h}\|\mathbf{E}^{\nu}-\mathbf{v}\|_{\mathbf{V}},\; C>0.
  \end{split}
@@
 \begin{align*}
-E_{y}^{\nu}(x)=\tilde{E}_{y}^{\nu}(x)+\text{smooth terms with derivatives bounded independently of $\nu$,} \\
+E_{y}^{\nu}(x)=\tilde{E}_{y}^{\nu}(x)+\text{smooth terms, which, together with their derivatives, are bounded independently of $\nu$,} \\
 \tilde{E}_{y}^{\nu}(x)=\log\rho_{\nu}(x-X_{\nu})(\alpha(x)+i\nu)p_{\nu}(x),
@@
 where $\rho_{\nu}$ is a smooth function s.t. $\rho_{\nu}(0)=0,\; \rho_{\nu}'(0)\neq 0$, the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R}$, 
-and $p_{\nu}(x)$ is a smooth function with derivatives bounded independently of $\nu$. 
+and $p_{\nu}(x)$ is a smooth function, which, together with its derivatives,  is bounded independently of $\nu$. 
 }
@@
   \label{eq:final_est}
-  \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}%\leq C_1\nu^{-1}h\|\left(E_y^{\nu}\right)''\|_{L_{2}}+C_2\nu^{-1}h^2\|\left(E_x^{\nu}\right)''\|_{L_{2}}
+  \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}%\leq C_1\nu^{-1}h\|\left(E_y^{\nu}\right)''\|_{L_{2}}+C_2\nu^{-1}h^2\|\left(E_x^{\nu}\right)''\|_{L_{2}}
   \leq C\nu^{-1}h\|\left(E_y^{\nu}\right)''\|_{L_{2}}+C\nu^{-1}h^2\|\left(E_x^{\nu}\right)''\|_{L_{2}}.
@@
 \end{align}
-The first term in the above expression is well-defined in $x=0$ (the L'Hopital's rule), and for sufficiently small $\nu$ can be bounded independently of $\nu$. 
-Similarly, the third term is non-singular.
-To examine the behaviour of $\left(\tilde{E}_{y}^{\nu}\right)''$, we study solely the singular second term of (\ref{eq:eynuprime}) (the derivatives for the rest of the terms can be shown to be bounded
-independently of $\nu$)
+The first term in the above expression is well-defined in $x=0$, even for $\nu=0$ (the limit can be obtained with the help of the L'Hopital's rule), and is uniformly bounded in $\nu$, together with its derivatives.
+The same holds for the third term.
+To examine the behaviour of $\left(\tilde{E}_{y}^{\nu}\right)''$, we study solely the singular second term of (\ref{eq:eynuprime})
 \begin{align*}
@@
 \end{align*}
-where we used an explicit form for $X_{\nu}$.
+where we used an explicit form of $\rho_{\nu}$ and $X_{\nu}$.
 
@@
 \begin{align*}
- \|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}\leq G+G'\left(\int\limits_{-L}^{H}\frac{1}{|x+i\nu c|^2}dx\right)^{\frac{1}{2}}\\
- \leq G+G'\left(\frac{1}{\nu c}\int\limits_{-\infty}^{\infty}\frac{dv}{v^2+1}\right)^{\frac{1}{2}}\\
+ \|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}\leq G+G'\left(\int\limits_{-L}^{H}\frac{1}{|x+i\nu c|^2}dx\right)^{\frac{1}{2}}
+ %\leq G+G'\left(\frac{1}{\nu c}\int\limits_{-\infty}^{\infty}\frac{dv}{v^2+1}\right)^{\frac{1}{2}}\\
  \leq \frac{C}{\sqrt{\nu}},\qquad G,G',C>0,
@@
 }
-For $E_x^{c,\nu},\; f^{\nu}(x)$ in (\ref{eq:exact}) being sufficiently smooth, 
+Let us now derive a similar bound on the second derivative of $E_{x}^{\nu}$:
 \ben
@@
 \een
-from which, together with (\ref{eq:cond}), it follows that there exists $c>0$ s.t. for all sufficiently small $\nu$ 
+from which, together with (\ref{eq:cond}, \ref{eq:eynuprime}, \ref{eq:exact}), it follows that there exists $c>0$ s.t. for all sufficiently small $\nu$ 
 \bealn
- \left|\frac{d^2}{dx^2}E_x^{\nu}\right|_{L_2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
+ \left|\frac{d^2}{dx^2}E_x^{\nu}\right|_{L^2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
  % &=c\left.

### 2015-05-03 report_clean/numerics.tex
plus extra modifications

@@
 ]\addplot[mark=*,black] table {pics_frequency_domain/data_airy/E1L2.dat}; 
-    \addlegendentry{$\|E_{x}-E_{x}^{c}\|_{L_{2}}$};
+    \addlegendentry{$\|E_{x}-E_{x}^{c}\|_{L^2}$};
     \addplot[mark=*,red, mark size=1pt] table {pics_frequency_domain/data_airy/E2H1.dat};
-        \addlegendentry{$\|E_{y}-E_{y}^{c}\|_{H_{1}}$};
+        \addlegendentry{$\|E_{y}-E_{y}^{c}\|_{H^{1}}$};
 
           \addplot[mark=*,cyan, mark size=1pt] table {pics_frequency_domain/data_airy/E2L2.dat};
-        \addlegendentry{$\|E_{y}-E_{y}^{c}\|_{L_{2}}$};  
+        \addlegendentry{$\|E_{y}-E_{y}^{c}\|_{L^{2}}$};  
         \addplot[dotted] table{pics_frequency_domain/data_airy/E_h2.dat};
@@
 \label{eq:problem1}
-\|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}<\epsilon,
+\|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}<\epsilon,
 \end{align}
@@
 \label{eq:exact}
- E_x^{\nu}=-iE_{y}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f^{\nu}(x)}{\alpha(x)+i\nu}, \; \text{for some }f^{\nu}(x)\in L_{2}(\Omega).
+ E_x^{\nu}=-iE_{y}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f^{\nu}(x)}{\alpha(x)+i\nu}, \; \text{for some }f^{\nu}(x)\in L^2(\Omega).
 \end{align}
@@
 \begin{align*}
-E_{y}^{\nu}(x)=\tilde{E}_{y}^{\nu}(x)+\text{smooth terms, which, together with their derivatives, are bounded independently of $\nu$,} \\
+E_{y}^{\nu}(x)=\tilde{E}_{y}^{\nu}(x)+S_{\nu}(x), \\
 \tilde{E}_{y}^{\nu}(x)=\log\rho_{\nu}(x-X_{\nu})(\alpha(x)+i\nu)p_{\nu}(x),
@@
 where $\rho_{\nu}$ is a smooth function s.t. $\rho_{\nu}(0)=0,\; \rho_{\nu}'(0)\neq 0$, the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R}$, 
-and $p_{\nu}(x)$ is a smooth function, which, together with its derivatives,  is bounded independently of $\nu$. 
-}
+and $p_{\nu}(x),\; S_{\nu}(x)$ are smooth functions, which, together with their derivatives, are bounded independently of $\nu$.}
 \item The estimate from \cite[Chapter 0]{brenner} on the rate of convergence of the interpolation 
@@
 \begin{split}
- \|v-I^{h}v\|_{L_{2}(\Omega)}\leq Ch^2\left|v''\right|_{L_{2}(\Omega)},\; C>0,\\
- \|v-I^{h}v\|_{H_{1}(\Omega)}\leq Ch|v''|_{L_{2}(\Omega)},\; C>0, 
+ \|v-I^{h}v\|_{L^2}\leq Ch^2\left|v''\right|_{L^2},\; C>0,\\
+ \|v-I^{h}v\|_{H^1}\leq Ch|v''|_{L^2},\; C>0, 
  \end{split}
@@
   \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}%\leq C_1\nu^{-1}h\|\left(E_y^{\nu}\right)''\|_{L_{2}}+C_2\nu^{-1}h^2\|\left(E_x^{\nu}\right)''\|_{L_{2}}
-  \leq C\nu^{-1}h\|\left(E_y^{\nu}\right)''\|_{L_{2}}+C\nu^{-1}h^2\|\left(E_x^{\nu}\right)''\|_{L_{2}}.
+  \leq C\nu^{-1}h\|\left(E_y^{\nu}\right)''\|_{L^2}+C\nu^{-1}h^2\|\left(E_x^{\nu}\right)''\|_{L^2}.
 \end{align}
@@
 \ben
- \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}\leq C\nu^{-\frac{7}{2}}h^2+C\nu^{-\frac{3}{2}}h.
+ \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}\leq C\nu^{-\frac{7}{2}}h^2+C\nu^{-\frac{3}{2}}h.
 \een
@@
 \begin{remark}
-It can be shown that $\|E^{\nu}_{x}\|_{L_{2}(\Omega)}\leq \frac{C}{\sqrt{\nu}},\; C>0$, 
+It can be shown that $\|E^{\nu}_{x}\|_{L^2}\leq \frac{C}{\sqrt{\nu}},\; C>0$, 
 and thus the relative error control
 \bealn
- \frac{\|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L_{2}(\Omega)}}{\|E^{\nu}_{x}\|_{L_{2}(\Omega)}}\leq \epsilon
+ \frac{\|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}}{\|E^{\nu}_{x}\|_{L^2}}\leq \epsilon
 \eealn

### 2015-05-03 report_clean/proc.tex
changed notation, corrected some defs
+2 remarks taken into account
+multiple items changed
final changes. To-Do: more changes
intro looks a bit more reasonable now
plus extra modifications

@@
 \newtheorem{remark}[theorem]{Remark}
+\newtheorem{assumption}[theorem]{Assumption}
 \definecolor{blue}{rgb}{0.30,0.8,1}
+\definecolor{greem}{rgb}{0,0.5,0}
+\definecolor{bluer}{rgb}{0,0,1}
 \definecolor{red}{rgb}{1,0.3,0.3}
+\DeclareMathOperator{\Ai}{Ai}
 %\usetikzlibrary{positioning,shapes,shadows,arrows}
@@
 \begin{document}
-\newcommand{\urev}[1]{{\color{blue}#1}}
+\newcommand{\urev}[1]{{\color{bluer}#1}}
 \newcommand{\arev}[1]{{\color{red}#1}}
-\newcommand{\mrev}[1]{{\color{green}#1}}
+\newcommand{\mrev}[1]{{\color{greem}#1}}
 
@@
 \bibitem{cedar}
-Charles, F., Despr\'es, B., Mehrenberg, M, 
+Charles, F., Despr\'es, B., Mehrenberg, M., 
 Enhanced convergence estimates for semi-lagrangian schemes Application to the Vlasov-Poisson equation, SIAM J. Numer. Anal. 2013, 51(2), 840-863.
@@
 
-\bibitem{Freidberg_2007} Freidberg, J. P. (2007). Plasma physics and fusion energy. Cambridge university press.
+\bibitem{Freidberg_2007} Freidberg, J. P. (2007). Plasma physics and fusion energy. Cambridge University Press.
 
@@
 \bibitem{Morawetz} Morawetz, C. S. (1962). The limiting amplitude principle. Communications on Pure and Applied Mathematics, 15(3), 349-361.
+\bibitem{Eidus} Eidus. D.M. (1969). The principle of limit amplitude. Russian Mathematical Surveys, vol. 24, issue 3, 97-167.
 
@@
 \bibitem{singular_solutions}
-Despr\'es, B., Imbert-G\'erard, L.-M. and Lafitte, O.. Singular solutions for the plasma at the resonance. 2014. <hal-01097364>
+Despr\'es, B., Imbert-G\'erard, L.-M. and Lafitte, O. Singular solutions for the plasma at the resonance. 2014. $\langle$ hal-01097364$\rangle$
 
+\bibitem{ciarlet_fem}
+Ciarlet, P. G. (1978).  The Finite Element Method For Elliptic Problems. North-Holland Publishing Company.
 \end{thebibliography}

### 2015-05-03 report_clean/responce_reviewers.tex
plus extra modifications
fixed major mistakes

@@
 - corrected the formulation of the lemma on the well-posedness and added a remark after the lemma on the sign of $\nu$.
+-corrected assumption on smoothness of $E_y^{\nu}$ in the section 'Numerical Experiments'.
 
@@
 
-- p2: in the frequency domain, as we have shown in Lemma 2.1, the problem is regularized by a choice $|\nu|>0$, independently of the sign of $\nu$. 
+- p2: in the frequency domain  the problem is regularized by a choice $|\nu|>0$, independently of the sign of $\nu$. 
 It is interesting however that for a fixed $\omega$ the limits $\lim_{\nu\rightarrow 0\pm}$ do not result in the same solution. 
-In the time domain the sign of $\nu>0$ is indeed of crucial importance for the stability. We added a remark on this before Section 2.1
+In the time domain the sign of $\nu>0$ is indeed of crucial importance for the stability, as well as in Lemma 2.1, provided that $\lambda$ in the 
+frequency of the antenna is larger than zero. We added a remark on this before Section 2.1
 
@@
 
- - p9 after (17): we would like to assume that it is $H^2$-norm that is bounded, for using the inequality (19). 
-  \mrev{TODO: While this assumption is fairly strong, it is often used in the approximation theory.   }
+ - p9 after (17): it is really necessary to assume that $H^2$-norm that is bounded, for using the inequality (19). 
+ We fixed an assumption of $E_y$.
 
@@
 
- Reviewer 2:
+\section{Response to  Reviewer 2}
 
- • p2: In this case Ex is not square integrable: confirm that it is when ν is not zero and that
-the singularity appears for ν = 0.
+-p2:  We tried to change the wording in the introduction to make it more clear what is a hybrid resonance. 
+The singularity appears for $\nu=0$, provided that the diagonal part of the dielectric tensor vanishes and the non-diagonal part does not.
 
-We tried to change the wording in the introduction to make it more clear what is a hybrid resonance. 
-The singularity appears for $\nu=0$, when the diagonal part of the dielectric tensor vanishes and non-diagonal part does not.
+- 'matricial' had been changed to 'matrix'.
 
-• p6, 3.1. It is not clear how the Yee scheme, which is a finite difference scheme, is linked to the
+- p6, 3.1. It is not clear how the Yee scheme, which is a finite difference scheme, is linked to the
 finite element scheme developed in the previous section. This should be made more explicit.
@@
 
-• p10: mesh multiple times finer. It should be said exactly how many times.
+- p10: mesh multiple times finer. It should be said exactly how many times.
 
@@
 
+-p.12: fixed the typos.
+
 \end{document}

### 2015-05-03 report_clean/FD.tex
fixed major mistakes

@@
 \right)-\frac{\omega^2}{c^2}
-\underline{\varepsilon}_{\omega}^{\nu}(x)\left(
+\uuline{\varepsilon_{\omega}}^{\nu}(x)\left(
 \begin{matrix}
@@
 =0,\\
-\underline{\varepsilon}^{\nu}_{\omega}(x)=\left(
+\uuline{\varepsilon_{\omega}}^{\nu}(x)=\left(
 \begin{matrix}
- \alpha^{\nu}_{\omega}(x) & i\delta^{\nu}_{\omega}(x) \\
- -i\delta^{\nu}_{\omega}(x) & \alpha^{\nu}_{\omega}(x)
+ \alpha^{\nu}_{\omega}(x) & -i\delta^{\nu}_{\omega}(x) \\
+ i\delta^{\nu}_{\omega}(x) & \alpha^{\nu}_{\omega}(x)
 \end{matrix}
@@
 \begin{align*}
-\underline{\varepsilon}^{\nu}_{\omega}\approx \underline{\varepsilon}^0_{\omega}+i\nu \left(
+\uuline{\varepsilon_{\omega}}^{\nu}\approx \uuline{\varepsilon_{\omega}}^{0}+i\nu \left(
  \begin{matrix}
-  D_{\alpha} & D_{\delta}\\
-  -D_{\delta} & D_{\alpha}
+  D_{\alpha} & -D_{\delta}\\
+  D_{\delta} & D_{\alpha}
  \end{matrix}
@@
 \ben
-\underline{\varepsilon}^{\nu}_{\omega}(\mathbf{r})\approx \underline{\varepsilon}^{0}_{\omega}(\mathbf{r})+i\nu \mathrm{Id}
+\uuline{\varepsilon_{\omega}}^{\nu}(\mathbf{r})\approx \uuline{\varepsilon_{\omega}}^{0}(\mathbf{r})+i\nu \mathrm{Id}
 \een
@@
 \right)-\frac{\omega^2}{c^2}
-\left(\underline{\varepsilon}^{0}_{\omega}(x)+i\nu \mathrm{Id}\right)\left(
+\left(\uuline{\varepsilon_{\omega}}^{0}(x)+i\nu \mathrm{Id}\right)\left(
 \begin{matrix}
@@
 =0,\\
-\underline{\varepsilon}^0_{\omega}(x)=\left(
+\uuline{\varepsilon_{\omega}}^{0}(x)=\left(
 \begin{matrix}
- \alpha_{\omega}(x) & i\delta_{\omega}(x) \\
- -i\delta_{\omega}(x) & \alpha_{\omega}(x)
+ \alpha_{\omega}(x) & -i\delta_{\omega}(x) \\
+ i\delta_{\omega}(x) & \alpha_{\omega}(x)
 \end{matrix}
@@
 \right)-
-\left(\underline{\varepsilon}^{0}(x)+i\nu \mathrm{Id}\right)\left(
+\left(\uuline{\varepsilon}^{0}(x)+i\nu \mathrm{Id}\right)\left(
 \begin{matrix}
@@
 \label{eq:epsilon_0}
-\underline{\varepsilon}^{0}(x)=\left(
+\uuline{\varepsilon}^{0}(x)=\left(
 \begin{matrix}
- \alpha(x) & i\delta(x) \\
- -i\delta(x) & \alpha(x)
+ \alpha(x) & -i\delta(x) \\
+ i\delta(x) & \alpha(x)
 \end{matrix}
@@
 \begin{array}{l}
-\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\tilde E_y' -\urev{i} \theta \tilde E_x)} - \int_{-L}^H (\varepsilon^{0} +i\nu \mathrm{Id}) \E \cdot \overline{\tilde \E}
+\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\tilde E_y' -\urev{i} \theta \tilde E_x)} - \int_{-L}^H (\uuline{\varepsilon}^{0} +i\nu \mathrm{Id}) \E \cdot \overline{\tilde \E}
 %\\ \displaystyle 
@@
 \left\{\begin{array}{l}
-	a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -i\theta u_1)\overline{(v_2' -i \theta v_1)} - \int_{-L}^H \varepsilon^{0} \ubf\cdot \overline{\vbf}, 
+	a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -i\theta u_1)\overline{(v_2' -i \theta v_1)} - \int_{-L}^H \uuline{\varepsilon}^{0} \ubf\cdot \overline{\vbf}, 
 	\\ a_2(\ubf,\vbf) = -\nu \int_{-L}^H  \ubf\cdot \overline{\vbf} - \lambda u_2 (-L) \overline{v_2 (-L)} , 
@@
 \urev{
-Let us denote the spectral radius of $\underline{\varepsilon}^{0}$ by $\heps =  \|\rho(\underline{\varepsilon}^{0})\|_{L^{\infty}(\Omega)}$. 
+Let us denote the spectral radius of $\uuline{\varepsilon}^{0}$ by $\heps =  \|\rho(\uuline{\varepsilon}^{0})\|_{L^{\infty}(\Omega)}$. 
 By Assumption \ref{assumption:smooth}, the spectral radius $\heps=\max\left(\|\alpha+\delta^2\|_{L^{\infty}(\Omega)}, \|\alpha-\delta^2\|_{L^{\infty}(\Omega)}\right)$ 
@@
 	one  $H^1(\Omega)\subset C^0(\overline \Omega)$. Let us focus on the proof of coercivity. 
-	\mrev{Given $\heps$ the spectral radius of $\underline{\varepsilon}^{0}$, 
-	$\heps \mathrm{Id}- \underline{\varepsilon}^{0} $ is a non-negative hermitian matrix.}
+	\mrev{Given $\heps$ the spectral radius of $\uuline{\varepsilon}^{0}$, 
+	$\heps \mathrm{Id}- \uuline{\varepsilon}^{0} $ is a non-negative hermitian matrix.}
 	Therefore
 	\be 
-	a_1(\ubf,\ubf) + \heps\|\ubf\|^2_{L^2}= \|u_2' - i \theta u_1 \|^2_{L^2} + \left( (\heps \mathrm{Id} - \underline{\varepsilon}^{0} ) \ubf, \overline{\ubf} \right)  \geq \|u_2 ' - i \theta u_1 \|_{L^ 2}^ 2
+	a_1(\ubf,\ubf) + \heps\|\ubf\|^2_{L^2}= \|u_2' - i \theta u_1 \|^2_{L^2} + \left( (\heps \mathrm{Id} - \uuline{\varepsilon}^{0} ) \ubf, \overline{\ubf} \right)  \geq \|u_2 ' - i \theta u_1 \|_{L^ 2}^ 2
 	\geq \frac12 \|u_2 '  \|_{L^2}^ 2 -
@@
 \begin{align*}
-  \left(E_x,u\right)=-\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega), 
+  \left(E_x,u\right)=\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega), 
 \end{align*}
@@
  i\theta \displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{\tilde E_x} - 
- \int_{-L}^H \left((\alpha+i\nu)E_x+i\delta E_y\right)_{1} \overline{\tilde E}_{x}
+ \int_{-L}^H \left((\alpha+i\nu)E_x-i\delta E_y\right)_{1} \overline{\tilde E}_{x}
 &=0,\\
 \int_{-L}^H (E_y' -i\theta E_x)\tilde {E_y'} -
-\int_{-L}^H\left( -i \delta E_x+(\alpha+i\nu) E_y\right)_{2}\overline{\tilde{E}}_{y}
+\int_{-L}^H\left( i \delta E_x+(\alpha+i\nu) E_y\right)_{2}\overline{\tilde{E}}_{y}
   - i \lambda E_y (-L) \overline{\tilde E_y (-L)} &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
@@
 \left(\begin{matrix}
-\theta^2 M^{\psi}-M^{\alpha,\psi} & i\theta K^{\psi,\phi'}-i M^{\delta,\psi,\phi} \\
--i\theta (K^{\psi,\phi'})^{*}+i (M^{\delta,\psi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
+\theta^2 M^{\psi}-M^{\alpha,\psi} & i\theta K^{\psi,\phi'}+i M^{\delta,\psi,\phi} \\
+-i\theta (K^{\psi,\phi'})^{*}-i (M^{\delta,\psi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
 \end{matrix}\right)
@@
 \left(\begin{matrix}
-M^{\alpha,\phi} & i M^{\delta,\phi,\phi} \\
-i (M^{\delta,\phi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
+M^{\alpha,\phi} & -i M^{\delta,\phi,\phi} \\
+-i (M^{\delta,\phi,\phi})^{*} & K-M^{\alpha,\phi}-i\lambda I^{\Gamma}
 \end{matrix}\right)

### 2015-05-03 report_clean/absorption.tex
fixed major mistakes

@@
 \end{itemize}
-For every fixed absorption rate $\nu$, in the time domain we choose the boundary conditions of the form
+For every fixed absorption rate \urev{$\nu>0$}, in the time domain we choose the boundary conditions of the form
 \begin{align}
@@
 \ben
-\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t), \text{ and } \Im\left(\hat{\mathbf{E}}^{\nu}\exp(it)\right)
+\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t), \text{ and } \Im\left(\hat{\mathbf{E}}^{\nu}\exp(\mrev{-it})\right)
 \een
@@
 choose the domain as $(-0.5, 10)$ and set the electron density $N_e(x)=1+x>0,\; x\in \Omega$. 
-\mrev{Importantly, since $\delta(x)=0$, in this case no resonance occurs and $E_x(x)=0$. This corresponds to the case when the
+\urev{Importantly, since $\delta(x)=0$, in this case no resonance occurs and $\hat{E}_x(x)\equiv 0$. This corresponds to the case when the
 tensor of dielectric permittivity $\underline{\varepsilon}^{\nu}$ is 
@@
 First we set $\nu=10^{-2}$. To demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
-inside the domain and plot the dependence of the solution $E_{y}^{\nu}(x_c,t), \; \Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right)$ 
-on time $t$ for a range of $t\gg 1$ in Fig.~\ref{fig:nu1e2_harmon}. We compare this solution to the computed $\Im\left(\hat{E}_y^{\nu}\mathrm{e}^{it}\right)$, for
+inside the domain and plot the dependence of the solution $E_{y}^{\nu}(x_c,t), \; \Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{\mrev{-it}}\right)$ 
+on time $t$ for a range of $t\gg 1$ in Fig.~\ref{fig:nu1e2_harmon}. We compare this solution to the computed $\Im\left(\hat{E}_y^{\nu}\mathrm{e}^{\mrev{-it}}\right)$, for
 fixed values of $t$. Both solutions appear to be in close agreement.
@@
 \end{tabular}
-\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ \mrev{to the problem described in Section \ref{section:absorption_airy}} on time for large times is demonstrated in the left figure.  
-In the right figure we show the solution \mrev{to the same problem} for $\nu=10^{-2}$, for two fixed moment of times.}
+\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ \urev{to the problem described in Section \ref{section:absorption_airy}} on time for large times is demonstrated in the left figure.  
+In the right figure we show the solution \urev{to the same problem} for $\nu=10^{-2}$, for two fixed moment of times.}
  \label{fig:nu1e2_harmon}
@@
 \end{tabular}
-\caption{In the left figure we plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ \mrev{to the problem described in Section \ref{section:absorption_airy}} on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$.
-In the right figure we show the solution \mrev{to the same problem} for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
+\caption{In the left figure we plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ \urev{to the problem described in Section \ref{section:absorption_airy}} on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$.
+In the right figure we show the solution \urev{to the same problem} for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
 $\nu=10^{-4}$ the limiting amplitude solution was reached for large $t$. For $\nu=10^{-6}$ we were not able 
@@
 $N_e(x)$ &  $\left\{
- \begin{array}{cc}
+ \begin{array}{lr}
   0.25, & x<-0.5,\\
@@
  \end{tabular}
-\caption{The figures demonstrate the dependence of the solutions to the problem \mrev{described in Section \ref{sec:resn}}
+\caption{The figures demonstrate the dependence of the solutions to the problem \urev{described in Section \ref{sec:resn}}
 $E_y^{\nu}(-2.5125,t)$ on time $t$ for different values of $\nu$. }
@@
  \caption{The plot shows the dependence of the solution $E_x^{\nu}(x_c,t),\;\nu=10^{-4},$ to 
- the problem \mrev{described in Section \ref{sec:resn}} on time $t$ for fixed 
+ the problem \urev{described in Section \ref{sec:resn}} on time $t$ for fixed 
  $x_c=0.0125$ and for $x_c=-2.5$. We can see that the solutions computed in the time domain are in close agreement 
@@
 \caption{The figures demonstrate the dependence of the solutions 
-$E_x^{\nu}(x,t)$ to the problem \mrev{described in Section \ref{sec:resn}} on $x$ for fixed values of $t$. }
+$E_x^{\nu}(x,t)$ to the problem \urev{described in Section \ref{sec:resn}} on $x$ for fixed values of $t$. }
 \label{fig:resonance_nus_ex_t}
@@
 \caption{The left figure demonstrates the dependence of the solution  
-$E_y^{\nu}(x,y)$ to the problem \mrev{described in Section \ref{sec:resn}} on $x$ for fixed values of $t$. 
+$E_y^{\nu}(x,y)$ to the problem \urev{described in Section \ref{sec:resn}} on $x$ for fixed values of $t$. 
 For a chosen value of $\nu$ the solutions computed in the time domain are in close agreement 
@@
 \caption{The figures demonstrate the dependence of the solutions 
-$E_x^{\nu}(x,t)$ and $E_y^{\nu}(x,y)$ to the problem \mrev{described in Section \ref{sec:resn}} on $x$ for fixed values of $t$. While the solution in the time-domain 
+$E_x^{\nu}(x,t)$ and $E_y^{\nu}(x,y)$ to the problem \urev{described in Section \ref{sec:resn}} on $x$ for fixed values of $t$. While the solution in the time-domain 
 in the resonance point $x=0$ has a smaller absolute value than that computed in the frequency domain (in the plot both solutions are truncated to 

### 2015-05-03 report_clean/intro.tex
fixed major mistakes

@@
 \label{eq:model_freq_domain}
- \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\underline{\varepsilon}^{0}_{\omega}(\mathbf{r})\hat{\mathbf{E}}=0,
+ \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\uuline{\varepsilon_{\omega}}^{0}(\mathbf{r})\hat{\mathbf{E}}=0,
 \end{align}
@@
 \nonumber
-\underline{\varepsilon}^{0}_{\omega}(\mathbf{r})=\left(
+\uuline{\varepsilon_{\omega}}^{0}(\mathbf{r})=\left(
  \begin{matrix}
-  \alpha_{\omega}(\mathbf{r})& i\delta_{\omega}(\mathbf{r})\\
-  -i\delta_{\omega}(\mathbf{r}) & \alpha_{\omega}(\mathbf{r})
+  \alpha_{\omega}(\mathbf{r})& -i\delta_{\omega}(\mathbf{r})\\
+  i\delta_{\omega}(\mathbf{r}) & \alpha_{\omega}(\mathbf{r})
  \end{matrix}
@@
 $\omega_c(\mathbf{r}_0)=\omega$, i.e.
-when $\underline{\varepsilon}_{\omega}^{0}(\mathbf{r}_0)$ is singular, is called a cyclotron resonance (c.f.
+when $\uuline{\varepsilon_{\omega}}^{0}(\mathbf{r}_0)$ is singular, is called a cyclotron resonance (c.f.
 \cite[Chapter 1-5]{Stix}).
@@
 Another interesting case is $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$ and $\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})\neq 0$, i.e. when the diagonal part of the tensor 
-$\underline{\varepsilon}_{\omega}^{0}(\mathbf{r})$ vanishes and the non-diagonal part remains non-zero. This is a hybrid resonance case.
+$\uuline{\varepsilon_{\omega}}^{0}(\mathbf{r})$ vanishes and the non-diagonal part remains non-zero. This is a hybrid resonance case.
 
@@
 \right)-\frac{\omega^2}{c^2}
-\underline{\varepsilon}_{\omega}^{0}(x)\left(
+\uuline{\varepsilon_{\omega}}^{0}(x)\left(
 \begin{matrix}
@@
 \right)-\frac{\omega^2}{c^2}
-\left(\underline{\varepsilon}_{\omega}^{0}(x)+i\nu \mathrm{Id}\right)\left(
+\left(\uuline{\varepsilon_{\omega}}{0}(x)+i\nu \mathrm{Id}\right)\left(
 \begin{matrix}

### 2015-05-03 report_clean/numerics.tex
fixed major mistakes

@@
 \end{align*}
-The most singular term in the above expression is $\frac{\alpha'p_{\nu}}{\rho_{\nu}(x-X_{\nu})}\rho'_{\nu}(x-X_{\nu})$ which can be bounded, for sufficiently small $x$, 
+The most singular term in the above expression is $\frac{\alpha'p_{\nu}}{\rho_{\nu}(x-X_{\nu})}\rho'_{\nu}(x-X_{\nu})$ which can be bounded, for sufficiently small $x$, by 
 \begin{align*}
@@
 \mrev{Recall that we choose $\theta=0$. }
-Denoting by \mrev{$E_{x}^{\nu,h}$ the solution $E_{x}(x)$} computed on the mesh with a \mrev{ width $h$ with 
-the absorption $\nu$, and by $E_{x}^{\nu}$} the solution computed on a mesh multiple times finer (\mrev{more precisely, the reference mesh
+Denoting by \mrev{$E_{x}^{\nu,h}$ the solution $E_{x}(x)$} computed on the mesh with the \mrev{width $h$ with 
+the absorption $\nu$, and by $E_{x}^{\nu}$} the solution computed on a mesh multiple times finer (\arev{more precisely, the reference mesh
 was typically 10-20 times finer, with the exception when the computation was done for very small values of $h$ where twice finer meshes for comparison were used}), let 
@@
 defined in Table \ref{tab:parameters}. In the left figure the dependence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated.  
-In the right figure we show the computed solutions for this problem (\mrev{for brevity denoted as $E_{x,y}^{\nu}$}) for different values of $\nu$. }
+In the right figure we show the computed solutions for this problem (\urev{for brevity denoted by $E_{x,y}^{\nu}$}) for different values of $\nu$. }
 \label{fig:dependence}
@@
 case.
-The numerical tests have been kept to a minimum since many more are needed to fully validate
+The numerical tests have been kept to a minimum since \arev{many more} are needed to fully validate
 the concept.
@@
 is the following. We use a 7th order semi-lagrangian scheme, and the CFL is $\nu=0.5$.
-The peak is the hybrid resonance, visible on $E_x$ and $u_x$.
+The \arev{peak} is the hybrid resonance, visible on $E_x$ and $u_x$.
 The total energy $\mathcal E(t)$ is the physical energy. 
 The comparison with figures \ref{fig:dependence} and \ref{fig:resonance_nus_ey_x} show that the 
-singular nature of the resonance is captured by this new scheme without any doubt.
+singular nature of the \arev{resonance} is captured by this new scheme without any doubt.
 

### 2015-05-04 report_clean/responce_reviewers.tex
plus a few small bugs fixed

@@
 More important corrections include
+
 - changed the wording in the abstract
+
+- corrected the definition of the cold plasma dielectric tensor, to match the convention $\partial_t\rightarrow -i\omega$ (it had to be hermitian conjugate; 
+this had been done everywhere, the corresponding corrections had been made in Table 1 and some figures)
+
 - corrected the definitions of $\alpha,\delta$ to comply with the definition of the cold plasma dielectric tensor of Stix
+
 (more precisely, removed terms $\frac{\omega^2}{c^2}$ in 
 front of them)
+
 - corrected the formulation of the lemma on the well-posedness and added a remark after the lemma on the sign of $\nu$.
+
 -corrected assumption on smoothness of $E_y^{\nu}$ in the section 'Numerical Experiments'.
 
-\section{Responce to the reviewer 1}
+\section{Response to the reviewer 1}
 
@@
 
-Specific remarks:
+B. Specific remarks:
 
@@
 
--p 8: our code, changed
+-p 8: 'our' code, changed
 
@@
 Added the captions
+
 - p15 in Conclusion
   Indeed $P1$!
+
+ -references: corrected
 

### 2015-05-04 report_clean/absorption.tex
plus a few small bugs fixed

@@
 \urev{Importantly, since $\delta(x)=0$, in this case no resonance occurs and $\hat{E}_x(x)\equiv 0$. This corresponds to the case when the
-tensor of dielectric permittivity $\underline{\varepsilon}^{\nu}$ is 
+tensor of dielectric permittivity $\uuline{\varepsilon^{\nu}_{\omega}}$ is 
 diagonal.}
 
-The boundary conditions in (\ref{eq:bcs}) are chosen as $G=Ai'(0.5)$.
+The boundary conditions in (\ref{eq:bcs}) are chosen as $G=Ai'(-0.5)$.
 

### 2015-05-04 report_clean/intro.tex
plus a few small bugs fixed

@@
 \label{eq:model_freq_domain}
- \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\uuline{\varepsilon_{\omega}}^{0}(\mathbf{r})\hat{\mathbf{E}}=0,
+ \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})\hat{\mathbf{E}}=0,
 \end{align}
@@
 \nonumber
-\uuline{\varepsilon_{\omega}}^{0}(\mathbf{r})=\left(
+\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})=\left(
  \begin{matrix}
@@
 $\omega_c(\mathbf{r}_0)=\omega$, i.e.
-when $\uuline{\varepsilon_{\omega}}^{0}(\mathbf{r}_0)$ is singular, is called a cyclotron resonance (c.f.
+when $\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r}_0)$ is singular, is called a cyclotron resonance (c.f.
 \cite[Chapter 1-5]{Stix}).
@@
 Another interesting case is $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$ and $\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})\neq 0$, i.e. when the diagonal part of the tensor 
-$\uuline{\varepsilon_{\omega}}^{0}(\mathbf{r})$ vanishes and the non-diagonal part remains non-zero. This is a hybrid resonance case.
+$\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})$ vanishes and the non-diagonal part remains non-zero. This is a hybrid resonance case.
 
@@
 \right)-\frac{\omega^2}{c^2}
-\uuline{\varepsilon_{\omega}}^{0}(x)\left(
+\uuline{\varepsilon_{\omega}^{0}}(x)\left(
 \begin{matrix}
@@
 \right)-\frac{\omega^2}{c^2}
-\left(\uuline{\varepsilon_{\omega}}{0}(x)+i\nu \mathrm{Id}\right)\left(
+\left(\uuline{\varepsilon_{\omega}^{0}}(x)+i\nu \mathrm{Id}\right)\left(
 \begin{matrix}

### 2015-05-04 report_clean/numerics.tex
plus a few small bugs fixed

@@
 \label{eq:parameters}
-\alpha(x)=x^2+1,\qquad \delta(x)=\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}, \qquad \mrev{\nu=0, \qquad \theta=0.}
+\alpha(x)=x^2+1,\qquad \delta(x)=-\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}, \qquad \mrev{\nu=0, \qquad \theta=0.}
 \end{align}
@@
     with the parameters (\ref{eq:parameters}) and the \mrev{boundary condition (\ref{eq:bcs_airy}))}. \mrev{Here $E_{y}^{c}(x)=\Ai(x)$ and 
-    $E_{x}^{c}(x)=-i\frac{\delta(x)}{\alpha(x)}\Ai(x)$.}}
+    $E_{x}^{c}(x)=i\frac{\delta(x)}{\alpha(x)}\Ai(x)$.}}
     \label{fig:conv_rate}
@@
 \label{eq:exact}
- E_x^{\nu}=-iE_{y}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f^{\nu}(x)}{\alpha(x)+i\nu}, \; \text{for some }f^{\nu}(x)\in L^2(\Omega).
+ E_x^{\nu}=iE_{y}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f^{\nu}(x)}{\alpha(x)+i\nu}, \; \text{for some }f^{\nu}(x)\in L^2(\Omega).
 \end{align}
@@
 Let us check numerically whether this holds true. 
-To do so, we conduct the  numerical experiment with parameters for the problem (\ref{eq:main_frequency_domain} as given in Table \ref{tab:parameters}.
+To do so, we conduct the  numerical experiment with parameters for the problem (\ref{eq:main_frequency_domain} as given in Table \ref{tab:parameters}. \mrev{Recall as well that we choose $\theta=0$. }
 \begin{table}[htb!]
@@
 0, & x\leq -10,\\
-4/30x+4/3,& -10<x\leq 5,\\
-2, & x>5.
+-4/30x-4/3,& -10<x\leq 5,\\
+-2, & x>5.
 \end{array}\right.$ \\
@@
 \end{table}
-\mrev{Recall that we choose $\theta=0$. }
 Denoting by \mrev{$E_{x}^{\nu,h}$ the solution $E_{x}(x)$} computed on the mesh with the \mrev{width $h$ with 

### 2015-05-04 report_clean/figure_generator/pics_time_domain/airy/figure_nu1e2_2.tex
figure update

@@
 \usepackage{pifont}% http://ctan.org/pkg/pifont
-\pgfplotsset{compat=1.10}
+\pgfplotsset{compat=newest}
 \usepackage{hyperref}
@@
   x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
+  ymax=0.8,
+  xmin=-0.45,
   ylabel={$E_y^{\nu}(x,t_c)$},
@@
    ]
- \addplot[color=blue, line width=1] file{airy/td_nu_0.01_dt0.05_t28525.dat};
-  \addlegendentry{$E_y^{\nu}(x,t_c),\; t_c=28525, \; \nu=10^{-2}$};
-  \addplot[color=red, mark=*, dashed, mark size=0.6] file{airy/fd_nu_0.01_dt0.05_t28525.dat};
-  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x)\mathrm{e}^{it_c}\right),\; t_c=28525, \; \nu=10^{-2}$};
-  \addplot[color=blue, dashed] file{airy/sol_1e2_dt0.05_td_t_28509.9.dat};
-  \addlegendentry{$E_y^{\nu}(x,t_c),\; t_c=28509.9, \; \nu=10^{-2}$};
-  \addplot[color=red] file{airy/sol_1e2_dt0.05_fd_t_28509.9.dat};
-  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x)\mathrm{e}^{it_c}\right),\; t_c=28509.9, \; \nu=10^{-2}$};
+ \addplot[color=blue, line width=1] file{airy/ey_td_nu1e2_t_29730.dat};
+  \addlegendentry{$E_y^{\nu}(x,t_c),\; t_c=29730, \; \nu=10^{-2}$};
+  \addplot[color=red, mark=*, dashed, mark size=0.6] file{airy/ey_fd_nu1e2_t_29730.dat};
+ \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x)\mathrm{e}^{-it_c}\right),\; t_c=29730, \; \nu=10^{-2}$};
+  \addplot[color=blue, mark=*, dashed, mark size=0.6] file{airy/ey_td_nu1e2_t_29960.dat};
+  \addlegendentry{$E_y^{\nu}(x,t_c),\; t_c=29960, \; \nu=10^{-2}$};
+  \addplot[color=red] file{airy/ey_fd_nu1e2_t_29960.dat};
+  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x)\mathrm{e}^{-it_c}\right),\; t_c=29960, \; \nu=10^{-2}$};
   \end{axis}

### 2015-05-04 report_clean/absorption.tex
final?

@@
 \FloatBarrier
-The computed $L_2$ error
-\begin{align}
-\label{eq:error}
-e_{x,y}(t)=\|\Im\left(\hat{E}_{x,y}^{\nu}\mathrm{e}^{it}\right)-E_{x,y}^{\nu}(t)\|_{L_{2}(-L;H)}
-\end{align}
-for $\nu=10^{-2}$ did not exceed $1.1e-3$ for values of $t\in \left(28501,  30000\right)$.
-Fig.~\ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=1e-4$.
-As previously,
+Fig.~\ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=1e-4$. As previously, 
  we fix a point $x=x_c$ inside the domain and plot 
 the dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time $t$ for a range of $t\gg 1$. 
-The error (\ref{eq:error}) for $\nu=10^{-4}$ at the time interval $[228000.05,\; 240000.05]$ does not exceed 2.8e-4. 
 One of our observations was that for smaller $\nu$ one requires more time steps to achieve the limiting amplitude solution. 

### 2015-05-04 report_clean/conclusions.tex
final?

@@
 well as studied the convergence of the finite element method for the problem with the resonance. 
-The piecewise-\mrev{linear} FEM approximates the resonant solution rather well, at least for moderate values of $\nu$, 
+The piecewise-\urev{linear} FEM approximates the resonant solution rather well, at least for moderate values of $\nu$, 
 however, the discretization size should be chosen roughly proportional to $\nu^{\frac{7}{4}}$, in order to obtain an accurate discretization.

### 2015-05-04 report_clean/FD.tex
plus a few small bugs fixed
extra typo
fixed typos

@@
 \right)-\frac{\omega^2}{c^2}
-\uuline{\varepsilon_{\omega}}^{\nu}(x)\left(
+\uuline{\varepsilon_{\omega}^{\nu}}(x)\left(
 \begin{matrix}
@@
 =0,\\
-\uuline{\varepsilon_{\omega}}^{\nu}(x)=\left(
+\uuline{\varepsilon_{\omega}^{\nu}}(x)=\left(
 \begin{matrix}
@@
 \begin{align*}
-\uuline{\varepsilon_{\omega}}^{\nu}\approx \uuline{\varepsilon_{\omega}}^{0}+i\nu \left(
+\uuline{\varepsilon_{\omega}^{\nu}}\approx \uuline{\varepsilon_{\omega}^{0}}+i\nu \left(
  \begin{matrix}
@@
 \ben
-\uuline{\varepsilon_{\omega}}^{\nu}(\mathbf{r})\approx \uuline{\varepsilon_{\omega}}^{0}(\mathbf{r})+i\nu \mathrm{Id}
+\uuline{\varepsilon_{\omega}}^{\nu}(\mathbf{r})\approx \uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})+i\nu \mathrm{Id}
 \een
@@
 \right)-\frac{\omega^2}{c^2}
-\left(\uuline{\varepsilon_{\omega}}^{0}(x)+i\nu \mathrm{Id}\right)\left(
+\left(\uuline{\varepsilon_{\omega}^{0}}(x)+i\nu \mathrm{Id}\right)\left(
 \begin{matrix}
@@
 =0,\\
-\uuline{\varepsilon_{\omega}}^{0}(x)=\left(
+\uuline{\varepsilon_{\omega}^{0}}(x)=\left(
 \begin{matrix}
@@
 \mrev{
-For brevity, from now on we will denote $\alpha_{\omega},\; \delta_{\omega}$ by $\alpha,\; \delta$ and consider a sequence of regularized problems. 
+For brevity, from now on we will denote $\frac{\omega^2}{c^2}\alpha_{\omega},\; \frac{\omega^2}{c^2}\delta_{\omega}$ by $\alpha,\; \delta$ and consider a sequence of regularized problems. 
 \begin{align}
@@
 \right)-
-\left(\uuline{\varepsilon}^{0}(x)+i\nu \mathrm{Id}\right)\left(
+\left(\uuline{\varepsilon^{0}}(x)+i\nu \mathrm{Id}\right)\left(
 \begin{matrix}
@@
 \label{eq:epsilon_0}
-\uuline{\varepsilon}^{0}(x)=\left(
+\uuline{\varepsilon^{0}}(x)=\left(
 \begin{matrix}
@@
 \begin{array}{l}
-\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\tilde E_y' -\urev{i} \theta \tilde E_x)} - \int_{-L}^H (\uuline{\varepsilon}^{0} +i\nu \mathrm{Id}) \E \cdot \overline{\tilde \E}
+\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\tilde E_y' -\urev{i} \theta \tilde E_x)} - \int_{-L}^H (\uuline{\varepsilon^{0}} +i\nu \mathrm{Id}) \E \cdot \overline{\tilde \E}
 %\\ \displaystyle 
@@
 Let us remark that in this and further sections, where it is not ambiguous, we will use the notation $E_{x,y}$ instead of $\hat{E}_{x,y}$ for convenience. \mrev{Also, 
-by $\|u\|_{L^{2}}$ we will denote $\|u\|_{L^{2}(\Omega)}$, for $u\in L^2(\Omega)$, and $\|\ubf\|_{L^2(\Omega)}=\left(\|u_1\|^2_{L_2}+\|u_2\|^2_{L_2}\right)^{\frac{1}{2}}$, 
+by $\|u\|_{L^{2}}$ we will denote $\|u\|_{L^{2}(\Omega)}$, for $u\in L^2(\Omega)$, and $\|\ubf\|_{L^2(\Omega)}=\left(\|u_1\|^2_{L^2}+\|u_2\|^2_{L^2}\right)^{\frac{1}{2}}$, 
 for $\ubf=(u_1,\;u_2)\in \left(L^2(\Omega)\right)^2$.}
@@
 \left\{\begin{array}{l}
-	a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -i\theta u_1)\overline{(v_2' -i \theta v_1)} - \int_{-L}^H \uuline{\varepsilon}^{0} \ubf\cdot \overline{\vbf}, 
+	a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -i\theta u_1)\overline{(v_2' -i \theta v_1)} - \int_{-L}^H \uuline{\varepsilon^{0}} \ubf\cdot \overline{\vbf}, 
 	\\ a_2(\ubf,\vbf) = -\nu \int_{-L}^H  \ubf\cdot \overline{\vbf} - \lambda u_2 (-L) \overline{v_2 (-L)} , 
@@
 \urev{
-Let us denote the spectral radius of $\uuline{\varepsilon}^{0}$ by $\heps =  \|\rho(\uuline{\varepsilon}^{0})\|_{L^{\infty}(\Omega)}$. 
+Let us denote the spectral radius of $\uuline{\varepsilon}^{0}$ by $\heps =  \|\rho(\uuline{\varepsilon^{0}})\|_{L^{\infty}(\Omega)}$. 
 By Assumption \ref{assumption:smooth}, the spectral radius $\heps=\max\left(\|\alpha+\delta^2\|_{L^{\infty}(\Omega)}, \|\alpha-\delta^2\|_{L^{\infty}(\Omega)}\right)$ 
@@
 \label{lemma:well_posedness}
-\urev{Let Assumption \ref{assumption:smooth} holds}. Then the bilinear form 
+\urev{Let Assumption \ref{assumption:smooth} hold}. Then the bilinear form 
 \ben
@@
 	\be 
-	a_1(\ubf,\ubf) + \heps\|\ubf\|^2_{L^2}= \|u_2' - i \theta u_1 \|^2_{L^2} + \left( (\heps \mathrm{Id} - \uuline{\varepsilon}^{0} ) \ubf, \overline{\ubf} \right)  \geq \|u_2 ' - i \theta u_1 \|_{L^ 2}^ 2
+	a_1(\ubf,\ubf) + \heps\|\ubf\|^2_{L^2}= \|u_2' - i \theta u_1 \|^2_{L^2} + \left( (\heps \mathrm{Id} - \uuline{\varepsilon^{0}} ) \ubf, \overline{\ubf} \right)  \geq \|u_2 ' - i \theta u_1 \|_{L^ 2}^ 2
 	\geq \frac12 \|u_2 '  \|_{L^2}^ 2 -
@@
 \label{sec:discr}
-Testing the variational formulation (\ref{vf1dcase}) with $(\tilde E_x,0)$ and $(0,\; \tilde{E}_y)\in\mathbf{V}(\Omega)$ and using 
+Testing the variational formulation (\ref{vf1dcase}) with $(\tilde E_x,0)$ and $(0,\; \tilde{E}_y)\in\mathbf{V}$ and using 
 an explicit expression for the tensor of the dielectric permittivity (\ref{eq:epsilon_0}), we can rewrite it as a system of two equations
@@
  i\theta \displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{\tilde E_x} - 
- \int_{-L}^H \left((\alpha+i\nu)E_x-i\delta E_y\right)_{1} \overline{\tilde E}_{x}
+ \int_{-L}^H \left((\alpha+i\nu)E_x-i\delta E_y\right) \overline{\tilde E}_{x}
 &=0,\\
 \int_{-L}^H (E_y' -i\theta E_x)\tilde {E_y'} -
-\int_{-L}^H\left( i \delta E_x+(\alpha+i\nu) E_y\right)_{2}\overline{\tilde{E}}_{y}
+\int_{-L}^H\left( i \delta E_x+(\alpha+i\nu) E_y\right)\overline{\tilde{E}}_{y}
   - i \lambda E_y (-L) \overline{\tilde E_y (-L)} &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
@@
 \end{align}
-\urev{Let us introduce two function spaces $V_{E_x}\subset L^{2}(\Omega)$ spanned by the basis function set $\{\psi_{j}\}_{j=1}^{N_{1}}$ and $V_{E_{y}}\subset H^{1}(\Omega)$ spanned by 
-the set $\{\phi_{i}\}_{i=1}^{N_{2}}$. }
+\urev{Let us introduce two function spaces $V_{E_x}\subset L^{2}(\Omega)$ spanned by a set of basis functions $\{\psi_{j}\}_{j=1}^{N_{1}}$ and $V_{E_{y}}\subset H^{1}(\Omega)$ spanned by $\{\phi_{i}\}_{i=1}^{N_{2}}$.
+}
 %We look for the solution of the problem (\ref{eq:var_form2}) in the form:

### 2015-05-04 report_clean/numerics.tex
fixed an error
fixed typos

@@
 \end{align}
-where $\Ai(x)$ is an Airy function, we ensure that $E_{y}$ that solves the above problem is well approximated by $\Ai(x)$, and $E_{x}$ by $-i\frac{\delta(x)}{\alpha(x)}\Ai(x)$. 
+we ensure that $E_{y}$ that solves the above problem is well approximated by $\Ai(x)$, and $E_{x}$ by $-i\frac{\delta(x)}{\alpha(x)}\Ai(x)$ (\urev{and hence both functions are smooth}). 
 The well-posedness of the respective variational formulation for $\nu=0$ is due to Remark \ref{remark:other}. }
@@
 \end{figure}
-\subsubsection{Solution of a Frequency-Domain Problem with Resonance}
+\subsubsection{Solution of the Frequency-Domain Problem with Resonance}
 %\paragraph{Convergence}
@@
 \begin{align*}
- \left|\frac{\alpha'p_{\nu}}{\rho_{\nu}(x-X_{\nu})}\rho'_{\nu}(x-X_{\nu})\right|\leq \frac{C}{|x+i\nu c|},\; C>0,c\in\mathbb{R},
+ \left|\frac{\alpha'p_{\nu}}{\rho_{\nu}(x-X_{\nu})}\rho'_{\nu}(x-X_{\nu})\right|\leq \frac{C}{|x-i\nu c|},\; C>0,
 \end{align*}
-where we used an explicit form of $\rho_{\nu}$ and $X_{\nu}$.
+where we used an explicit form of $\rho_{\nu}=G(x-X_{\nu})+O((x-X_{\nu})^2),$ valid for sufficiently small $\nu$ and $|x|$, and $X_{\nu}$.
 
@@
 \caption{We consider the problem (\ref{eq:main_frequency_domain}) with the parameters 
-defined in Table \ref{tab:parameters}. In the left figure the dependence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated.  
+defined in Table \ref{tab:parameters}. In the left figure the \urev{dependence} of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated.  
 In the right figure we show the computed solutions for this problem (\urev{for brevity denoted by $E_{x,y}^{\nu}$}) for different values of $\nu$. }

### 2015-05-04 report_clean/FD.tex
fixed small typos

@@
 $\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane. \arev{Note that neither cyclotron, nor hybrid resonances occur in the problem 
-with the dielectric tensor $\varepsilon^{\nu}_{\omega}(\mathbf{r}), \; \nu>0$ (since all the parameters are real). Hence 
+with the dielectric tensor $\varepsilon^{\nu}_{\omega}(x), \; \nu>0$ (since all the parameters are real). Hence 
 the choice of the non-zero plasma friction $\nu>0$ can be viewed as a regularization of the problem. }
@@
 where $\alpha_{\omega},\;\delta_{\omega}$ are defined by (\ref{eq:alpha_delta}). In the frequency domain one thus can consider 
-the following regularization of the cold plasma dielectric tensor of the above problem:
+the following regularization of the cold plasma dielectric tensor of the above problem, valid as $\nu\rightarrow 0$:
 \begin{align*}
@@
 \ben
-\uuline{\varepsilon_{\omega}}^{\nu}(\mathbf{r})\approx \uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})+i\nu \mathrm{Id}
+\uuline{\varepsilon_{\omega}^{\nu}}(x)\approx \uuline{\varepsilon_{\omega}^{0}}(x)+i\nu \mathrm{Id}
 \een
@@
 \right)-
-\left(\uuline{\varepsilon^{0}}(x)+i\nu \mathrm{Id}\right)\left(
+\left(\uuline{\varepsilon}^{0}(x)+i\nu \mathrm{Id}\right)\left(
 \begin{matrix}
@@
 \label{eq:epsilon_0}
-\uuline{\varepsilon^{0}}(x)=\left(
+\uuline{\varepsilon}^{0}(x)=\left(
 \begin{matrix}
@@
 \mrev{In this section we study the well-posedness of the problem (\ref{eq:main_frequency_domain}) with the 
- boundary conditions (\ref{eq:boundary_conditions_frequency_domain}) with the help of Lax-Milgram lemma.} 
+ boundary conditions (\ref{eq:boundary_conditions_intro}) with the help of Lax-Milgram lemma.} 
 After introducing $\Omega=(-L,\; H)\subset \mathbb R$ and defining the function space of the problem  $\mathbf{V}=L^{2}(\Omega)\times H^{1}(\Omega)$, 
@@
 \begin{array}{l}
-\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\tilde E_y' -\urev{i} \theta \tilde E_x)} - \int_{-L}^H (\uuline{\varepsilon^{0}} +i\nu \mathrm{Id}) \E \cdot \overline{\tilde \E}
+\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\tilde E_y' -\urev{i} \theta \tilde E_x)} - \int_{-L}^H (\uuline{\varepsilon}^{0} +i\nu \mathrm{Id}) \E \cdot \overline{\tilde \E}
 %\\ \displaystyle 
@@
 The above can be reformulated as, \urev{for the unknown $\mathbf{E}$ and $\tilde{\mathbf{E}}$ a test function},
-\be
+\ben
 a\left(\mathbf{E},\tilde{\mathbf{E}}\right)=l(\tilde{\mathbf{E}}), \; \text{ for all }\tilde{\mathbf{E}}\in \mathbf{V},
-\ee
+\een
 with a bilinear form $a$ and a linear form $l$, \urev{defined for $\mathbf{u},\; \mathbf{v}\in \mathbf{V}$}:
-\be
+\ben
 a(\ubf,\vbf) = a_1 (\ubf,\vbf) +i a_2(\ubf,\vbf)\  \text{ and } \  l(\vbf) = -g_{inc} (-L) \overline{(v_2(-L) )} 
-\ee
+\een
 where $a_1= a_1^*$ and $a_2=a_2^*$ are hermitian
-\be
+\ben
 \left\{\begin{array}{l}
-	a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -i\theta u_1)\overline{(v_2' -i \theta v_1)} - \int_{-L}^H \uuline{\varepsilon^{0}} \ubf\cdot \overline{\vbf}, 
+	a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -i\theta u_1)\overline{(v_2' -i \theta v_1)} - \int_{-L}^H \uuline{\varepsilon}^{0} \ubf\cdot \overline{\vbf}, 
 	\\ a_2(\ubf,\vbf) = -\nu \int_{-L}^H  \ubf\cdot \overline{\vbf} - \lambda u_2 (-L) \overline{v_2 (-L)} , 
 \end{array}\right.
-\ee
+\een
 
 \urev{
-Let us denote the spectral radius of $\uuline{\varepsilon}^{0}$ by $\heps =  \|\rho(\uuline{\varepsilon^{0}})\|_{L^{\infty}(\Omega)}$. 
+Let us denote the spectral radius of $\uuline{\varepsilon}^{0}$ by $\heps =  \|\rho(\uuline{\varepsilon}^{0})\|_{L^{\infty}(\Omega)}$. 
 By Assumption \ref{assumption:smooth}, the spectral radius $\heps=\max\left(\|\alpha+\delta^2\|_{L^{\infty}(\Omega)}, \|\alpha-\delta^2\|_{L^{\infty}(\Omega)}\right)$ 
@@
 	Therefore
-	\be 
-	a_1(\ubf,\ubf) + \heps\|\ubf\|^2_{L^2}= \|u_2' - i \theta u_1 \|^2_{L^2} + \left( (\heps \mathrm{Id} - \uuline{\varepsilon^{0}} ) \ubf, \overline{\ubf} \right)  \geq \|u_2 ' - i \theta u_1 \|_{L^ 2}^ 2
+	\ben
+	a_1(\ubf,\ubf) + \heps\|\ubf\|^2_{L^2}= \|u_2' - i \theta u_1 \|^2_{L^2} + \left( (\heps \mathrm{Id} - \uuline{\varepsilon}^{0} ) \ubf, \overline{\ubf} \right)  \geq \|u_2 ' - i \theta u_1 \|_{L^ 2}^ 2
 	\geq \frac12 \|u_2 '  \|_{L^2}^ 2 -
 	\theta ^2 \| u_1 \|_{L^2}^ 2.
-	\ee
+	\een
 	Thus one can write

### 2015-05-04 report_clean/absorption.tex
fixed typos
fixed small typos

@@
 \eealn
-We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain 
-(the solution computed numerically at the time step $n$ is denoted by $\mathbf{E}^{\nu}_{n}$), and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain. 
+We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain, and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain. 
 In the numerical experiments we check whether the following two quantities
@@
 choose the domain as $(-0.5, 10)$ and set the electron density $N_e(x)=1+x>0,\; x\in \Omega$. 
-\urev{Importantly, since $\delta(x)=0$, in this case no resonance occurs and $\hat{E}_x(x)\equiv 0$. This corresponds to the case when the
+\urev{Importantly, since $\delta(x)=0$, in this case no resonance occurs and $E(x,t)\equiv 0$. This corresponds to the case when the
 tensor of dielectric permittivity $\uuline{\varepsilon^{\nu}_{\omega}}$ is 
@@
 First we set $\nu=10^{-2}$. To demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
-inside the domain and plot the dependence of the solution $E_{y}^{\nu}(x_c,t), \; \Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{\mrev{-it}}\right)$ 
+inside the domain and plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ 
 on time $t$ for a range of $t\gg 1$ in Fig.~\ref{fig:nu1e2_harmon}. We compare this solution to the computed $\Im\left(\hat{E}_y^{\nu}\mathrm{e}^{\mrev{-it}}\right)$, for
@@
 \FloatBarrier
-Fig.~\ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=1e-4$. As previously, 
+Fig.~\ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=10^{-4}$. As previously, 
  we fix a point $x=x_c$ inside the domain and plot 

### 2015-05-04 report_clean/intro.tex
intro.tex modified
fixed typos
fixed small typos

@@
 {\mathcal E}(t)= \int_\Omega \left(
-\frac{\epsilon_0 |\E(t,\mathbf{r})|^2}{2}+\frac{ |\B(t,\mathbf{r})|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|^2}{2|e|N_e(\mathbf{r})} 
+\frac{\epsilon_0 |\E(t,\mathbf{r})|^2}{2}+\frac{ |\B(t,\mathbf{r})|^2}{2\mu_0}+\frac{m_e|\J (t,\mathbf{r})|^2}{2|e|N_e(\mathbf{r})} 
 \right)\mathrm{d}\mathbf{r},
@@
 \ben
-\frac{d}{dt}{\mathcal E}=-\nu\left(\|u_{x}\|_{L_{2}(\Omega)}^2+\|u_{y}\|_{L_{2}(\Omega)}^2\right)+\text{boundary terms}.
+\frac{d}{dt}{\mathcal E}=-\nu\left(\|u_{x}\|_{L^{2}(\Omega)}^2+\|u_{y}\|_{L^{2}(\Omega)}^2\right)+\text{boundary terms}.
 \een
@@
 As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component $E_x$ is not necessarily square 
-integrable. This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.
+integrable (for a demonstration of this behaviour with the help of a simpler example, namely the Whittaker problem, see e.g. \cite{Despres_2014}). 
+This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.
 
@@
 where it is required to study the above system under the assumption that the electron density $N_{e}$ and the magnetic field $B_0$ are \textbf{uniform} in the second coordinate, more precisely 
-$N_{e}=N_{e}(x)$ and $B_0=B_0(x)$, see e.g. \cite{Despres_2014}. Even this simplified case contains difficulties intrinsic to hybrid resonance \cite{Despres_2014, singular_solutions}.
+$N_{e}=N_{e}(x)$ and $B_0=B_0(x)$, see e.g. \cite{Despres_2014}. 
+We additionally assume that $N_e>0$ on $[-L,\;H]$. Even this simplified case contains difficulties intrinsic to the hybrid resonance \cite{Despres_2014, singular_solutions}.
 
-Under the aforementioned assumptions on $N_e$ and $B_0$, the one-dimensional model can be derived from (\ref{eq:main_system}) by performing the Fourier transform in $y$ ($\partial_y\rightarrow i\theta, \; \theta\in\mathbb{R}$).
-For a parameter $\theta$,
+Under the aforementioned assumptions on $N_e$ and $B_0$, the one-dimensional model can be derived from (\ref{eq:main_system}) by performing the Fourier transform in $y$ ($\partial_y\rightarrow i\theta, \; \theta\in\mathbb{R}$):
 \begin{equation}
@@
 m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
-m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
+m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y,
 \end{cases}
 \end{equation}
- posed in $(-L,\; H)$, for some $L,H>0$, with \mrev{the boundary conditions as in (\ref{eq:boundary_conditions_intro}),
+ posed in $(-L,\; H)$, for some $L,H>0$, with \mrev{the boundary conditions as in (\ref{eq:boundary_conditions_intro})
  \begin{align}
@@
  \begin{split}
-  \left.\left(\partial_x E_y -i\theta E_x-i\lambda E_y\right)\right|_{x=-L} =g_{inc}(t),\\
+  \left.\left(\partial_x E_y -i\theta E_x+i\lambda E_y\right)\right|_{x=-L} =g_{inc}(t),\\
   \left.\partial_xE_y\right|_{x=H}=0, 
@@
 \end{align}
-see (\ref{eq:alpha_delta}). Indeed, the coefficients $\alpha_{\omega},\;\delta_{\omega}$ depend solely on $x$ and $\omega$.  
+see (\ref{eq:alpha_delta}). Indeed, the coefficients $\alpha_{\omega},\;\delta_{\omega}$, see (\ref{eq:alpha_delta}), in this case depend solely on $x$ and $\omega$.  
 \arev{
@@
 We will call a point $x_h\in \mathbb{R}$ a hybrid resonance if $\alpha_{\omega}$ has 
-a simple root in $x_h$ and has no other roots in an $\epsilon$-vicinity of this point $B_{\epsilon}(x_h)$, for some $\epsilon>0$, and 
-$\delta(x_h)\neq 0$. 
+a simple root in $x_h$ and has no other roots in an $\epsilon$-vicinity of this point $B_{\epsilon}(x_h)$, for some $\epsilon>0$, 
+and $\delta_{\omega}(x_h)\neq 0$.
 \end{df}
@@
 
-To investigate the behaviour of the solutions in the case when the hybrid resonance occurs in the sustem, 
+To investigate the behaviour of the solutions in the case when the hybrid resonance occurs in the system, 
 instead of the above problem we will study a sequence of the regularized problems, for $\nu\rightarrow 0$, 
@@
 We prove the well-posedness of this problem for \mrev{$\nu\neq 0$} in Section~\ref{sec:wellposedness} and 
-demonstrate that the use of  (P1) finite elements allows to approximate the singularity 
+demonstrate that the use of  $P_1$ finite elements allows to approximate the singularity 
 of the solution fairly well (Section \ref{sec:freq_dep}). 
@@
 \urev{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principles. 
-In application to a non-resonant case of (\ref{eq:main_frequency_domain_intro}), equipped with boundary conditions, the limited absorption principle states that the solution of (\ref{eq:seq_regularized}) would coincide with the solution of (\ref{eq:main_frequency_domain_intro})
+In application to a non-resonant case of (\ref{eq:main_frequency_domain_intro}), equipped with boundary conditions, the limited absorption principle states that the solution of (\ref{eq:seq_regularized})
+would approach the solution of (\ref{eq:main_frequency_domain_intro})
 as $\nu\rightarrow 0$. Similarly, the limiting amplitude principle applied to the problem (\ref{eq:main_model}) 
@@
 $\left.\partial_x E_y\right|_{x=-L}=\mathrm{e}^{-i\omega_{*} t}$, then the solution of this problem $(\mathbf{E}(t),\;H(t))$ asymptotically ($t\rightarrow +\infty$)
-tends to a steady state of the form $ \left(\mathbf{E}(\omega_{*}),\; \hat{H}(\omega_{*})\right)\mathrm{e}^{-i\omega_{*} t}$, where 
+tends to a steady state of the form $ \left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)\mathrm{e}^{-i\omega_{*} t}$, where 
 $\left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)$ is the solution of (\ref{eq:main_model})
@@
 \cite{Morawetz, Eidus}.
-The commutation between the two principles then write as}
+The commutation between the two principles then writes as}
 $$

### 2015-05-04 report_clean/numerics.tex
fixed small typos

@@
 This section is organized as follows. The first part is dedicated to the numerical implementation
-of the frequency domain formulation \eqref{eq:main_frequency_domain}. We study the convergence of this formulation and the behaviour 
+of the frequency domain formulation \eqref{vf1dcase}. We study the convergence of this formulation and the behaviour 
 of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
@@
 \label{eq:bcs_airy}
-\partial_{1}E_{y}(-L)+2iE_{y}(-L)=2i\Ai(-L)+\Ai'(-L),\qquad 
-\partial_{1}E_{y}(H)=0\approx \Ai'(H),
+\partial_{x}E_{y}(-L)+2iE_{y}(-L)=2i\Ai(-L)+\Ai'(-L),\qquad 
+\partial_{x}E_{y}(H)=0\approx \Ai'(H),
 \end{align}
 we ensure that $E_{y}$ that solves the above problem is well approximated by $\Ai(x)$, and $E_{x}$ by $-i\frac{\delta(x)}{\alpha(x)}\Ai(x)$ (\urev{and hence both functions are smooth}). 
-The well-posedness of the respective variational formulation for $\nu=0$ is due to Remark \ref{remark:other}. }
+The well-posedness of the respective variational formulation is due to Remark \ref{remark:other}. }
 
@@
 E_{y}^{\nu}(x)=\tilde{E}_{y}^{\nu}(x)+S_{\nu}(x), \\
-\tilde{E}_{y}^{\nu}(x)=\log\rho_{\nu}(x-X_{\nu})(\alpha(x)+i\nu)p_{\nu}(x),
+\tilde{E}_{y}^{\nu}(x)=(\alpha(x)+i\nu)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})=(-x+i\nu)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu}),
 \end{align*}
@@
 \label{eq:eynuprime}
- \left(\tilde{E}_{y}^{\nu}\right)'&=\frac{\alpha(x)+i\nu}{\rho_{\nu}(x-X_{\nu})}p_{\nu}(x)+\alpha'\log\rho_{\nu}(x-X_{\nu})p_{\nu}(x)+p'_{\nu}(x)(\alpha+i\nu)\log\rho_{\nu}(x-X_{\nu}).
+ \left(\tilde{E}_{y}^{\nu}\right)'&=\frac{-x+i\nu}{\rho_{\nu}(x-X_{\nu})}p_{\nu}(x)-\log\rho_{\nu}(x-X_{\nu})p_{\nu}(x)+p'_{\nu}(x)(-x+i\nu)\log\rho_{\nu}(x-X_{\nu}).
 \end{align}
-The first term in the above expression is well-defined in $x=0$, even for $\nu=0$ (the limit can be obtained with the help of the L'Hopital's rule), and is uniformly bounded in $\nu$, together with its derivatives.
-The same holds for the third term.
-To examine the behaviour of $\left(\tilde{E}_{y}^{\nu}\right)''$, we study solely the singular second term of (\ref{eq:eynuprime})
+The first term in the above expression is well-defined in $x=0$, even for $\nu=0$ (the limit can be obtained with the help of the L'Hopital's rule 
+and recalling that $\rho_{\nu}=O(x-X_{\nu})$ in the vicinity of the resonance), and is uniformly bounded in $\nu$, together with its derivatives. 
+The same holds for the third term. To examine the behaviour of $\left(\tilde{E}_{y}^{\nu}\right)''$, 
+we study solely the singular second term of (\ref{eq:eynuprime})
 \begin{align*}
- \left(\alpha'\log\rho_{\nu}(x-X_{\nu})p_{\nu}\right)'=\alpha''\log\rho_{\nu}(x-X_{\nu})p_{\nu}+\frac{\alpha'p_{\nu}}{\rho_{\nu}(x-X_{\nu})}\rho'_{\nu}(x-X_{\nu})+
- \alpha'\log\rho_{\nu}(x-X_{\nu})p_{\nu}'.
+ \left(\log\rho_{\nu}(x-X_{\nu})p_{\nu}\right)'=\frac{p_{\nu}}{\rho_{\nu}(x-X_{\nu})}\rho'_{\nu}(x-X_{\nu})+\log\rho_{\nu}(x-X_{\nu})p_{\nu}'.
 \end{align*}
-The most singular term in the above expression is $\frac{\alpha'p_{\nu}}{\rho_{\nu}(x-X_{\nu})}\rho'_{\nu}(x-X_{\nu})$ which can be bounded, for sufficiently small $x$, by 
+The most singular term in the above expression is $\frac{p_{\nu}}{\rho_{\nu}(x-X_{\nu})}\rho'_{\nu}(x-X_{\nu})$ which can be bounded, for all sufficiently small $x$, by 
 \begin{align*}
- \left|\frac{\alpha'p_{\nu}}{\rho_{\nu}(x-X_{\nu})}\rho'_{\nu}(x-X_{\nu})\right|\leq \frac{C}{|x-i\nu c|},\; C>0,
+ \left|\frac{p_{\nu}\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}\right|\leq \frac{C}{|x-i\nu c|},\; C>0,
 \end{align*}
-where we used an explicit form of $\rho_{\nu}=G(x-X_{\nu})+O((x-X_{\nu})^2),$ valid for sufficiently small $\nu$ and $|x|$, and $X_{\nu}$.
+where we used an explicit form of $\rho_{\nu}=G(x-X_{\nu})+O((x-X_{\nu})^2), G\in\mathbb{R},$ valid for sufficiently small $\nu$ and $|x|$, as well as 
+the expansion $X_{\nu}=ic\nu+O(\nu^2)$.
 
@@
 \bealn
- \left|\frac{d^2}{dx^2}E_x^{\nu}\right|_{L^2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
+ \left|\frac{d^2E_x^{\nu}{dx^2}}\right|_{L^2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
  % &=c\left.
@@
 the absorption $\nu$, and by $E_{x}^{\nu}$} the solution computed on a mesh multiple times finer (\arev{more precisely, the reference mesh
-was typically 10-20 times finer, with the exception when the computation was done for very small values of $h$ where twice finer meshes for comparison were used}), let 
+was typically 10-20 times finer, with the exception when the computation was done for very small values of $h$ where for comparison twice finer meshes were used}), let 
 \begin{align}

### 2015-05-04 report_clean/responce_reviewers.tex
intro.tex

@@
 \usepackage[utf8]{inputenc}
+\usepackage{color}
 
@@
 
+-shortened slightly the section on limiting amplitude for a non-resonant case.
+
 \section{Response to the reviewer 1}
@@
 and $\delta$ does not (while in Section 4.3.1 $\delta$ vanishes as well).
+To give a hint on singularity of equations, we cite an article where a simple model problem is considered.
 
@@
 added an assumption in the end of the Section Frequency Domain Study on the coefficients of the dielectric tensor, and made a remark on the absence
-of the cyclotron resonance.
+of the cyclotron resonance. The formulation of Lemma is correspondingly corrected.
 
@@
 
-- p3: yes, indeed, fixed
+- p3: this should be now fixed in the whole of the article.
 
@@
 - p4: we changed $\alpha_{\nu}$ to $\beta_{\nu}$ not to confuse with $\alpha$ in the dielectric tensor. The index $\nu$ 
-just underlines the dependence of this angle $\beta_{\nu}$ on $\nu$ (indeed, the coercivity result as it is stated, holds for this specific value of $\beta_{\nu}$ stated 
+just underlines the dependence of the angle $\beta_{\nu}$ on $\nu$ (indeed, the coercivity result as it is stated, holds for this specific value of $\beta_{\nu}$ defined 
 in the end of the proof of the lemma).
@@
 
+ -p.8: the citation had been fixed; we expect $E_y$ to be analytic in this case (since we want it to be equal $\mathrm{Ai}(x)$, this is pointed out right now), 
+ and $E_x$ thus is smooth.
+
  -  p9, Figure 3: fixed the captions. This had been done for other figures as well. The values $E^{c}_{x,y}$ had been defined in the caption.
@@
 
- - p9 after (17): it is really necessary to assume that $H^2$-norm that is bounded, for using the inequality (19). 
- We fixed an assumption of $E_y$.
+ - p9 after (17): it is really necessary to assume that $H^2$-norm that is bounded, for using the inequality (25). 
+ We fixed an assumption on $E_y$, which was incorrect before.
 
@@
 
+ --p 11 Figure 4: fixed
+
  -- p11 Figure 5:
 Agree, fixed. We added a remark in a caption to Figure 4 as well.
+
+-{\textcolor{red}{p12}}
 
@@
   It is true, but in this case there is no resonance, since $\delta(x)\equiv 0$. Hence $E_x=-\frac{i\delta}{\alpha}E_y\equiv 0$, 
-  and $E_y$ solves the Airy equation in the frequency domain. We added a small to Section 4.3.1 to underline this.
+  and $E_y$ solves the Airy equation in the frequency domain. We added a small remark to Section 4.3.1 to underline this.
 
-- p12 Equation (23)
-We changed it to $e$
+- p12 Equation (23): it had been removed
 
@@
 
-- p6, 3.1. It is not clear how the Yee scheme, which is a finite difference scheme, is linked to the
-finite element scheme developed in the previous section. This should be made more explicit.
+- p6, 3.1.
 
@@
 
--p.12: fixed the typos.
+- {\textcolor{red}{p.12: fixed the typos.}}
 

### 2015-05-04 report_clean/intro.tex
intro.tex

--- 2015-05-04 report_clean/intro.tex
@@
 As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component $E_x$ is not necessarily square 
-integrable. This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.
+integrable (for an illustrative example of such a system in one dimension see \cite{Despres_2014}).
+This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.
 

### 2015-05-04 report_clean/intro.tex

--- 2015-05-04 report_clean/intro.tex
@@
 As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component $E_x$ is not necessarily square 
-integrable (for a demonstration of this behaviour with the help of a simpler example, namely the Whittaker problem, see e.g. \cite{Despres_2014}). 
+integrable (for a demonstration of this behaviour with the help of a simpler example, namely the Budden problem, see e.g. \cite{Despres_2014}). 
 This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.

### 2015-05-04 report_clean/absorption.tex
errors fixed

@@
 \subsection{Limiting Amplitude and Limiting Absorption Principle}
-In this section we perform several numerical experiments to check wether the limit amplitude
+In this section we perform several numerical experiments to check whether the limit amplitude
 principle and the limit

### 2015-05-04 report_clean/numerics.tex
bug

@@
 \label{eq:exact}
- E_x^{\nu}=iE_{y}^{\nu}\frac{\delta}{\alpha+i\nu}=\frac{f^{\nu}(x)}{\alpha(x)+i\nu}, \; \text{for some }f^{\nu}(x)\in L^2(\Omega).
+ E_x^{\nu}(x)=iE_{y}^{\nu}(x)\frac{\delta(x)}{\alpha(x)+i\nu}=\frac{f^{\nu}(x)}{\alpha(x)+i\nu}, \; \text{for some }f^{\nu}(x)\in L^2(\Omega).
 \end{align}
@@
 \mrev{
-First of all let us examine the behaviour the derivatives of $E_{y}^{\nu}$ in the vicinity of the resonance:
+First of all let us examine the behaviour the derivatives of $E_{y}^{\nu}$ in the vicinity of the resonance, 
+in particular, the term $\tilde{E}_{y}^{\nu}$ which is singular for $\nu=0$ in the resonant point:
 \begin{align}
 \label{eq:eynuprime}
- \left(\tilde{E}_{y}^{\nu}\right)'&=\frac{-x+i\nu}{\rho_{\nu}(x-X_{\nu})}p_{\nu}(x)-\log\rho_{\nu}(x-X_{\nu})p_{\nu}(x)+p'_{\nu}(x)(-x+i\nu)\log\rho_{\nu}(x-X_{\nu}).
+ \left(\tilde{E}_{y}^{\nu}\right)'&=\frac{(-x+i\nu)\rho_{\nu}'(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}p_{\nu}(x)-p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+p'_{\nu}(x)(-x+i\nu)\log\rho_{\nu}(x-X_{\nu}).
 \end{align}
-The first term in the above expression is well-defined in $x=0$, even for $\nu=0$ (the limit can be obtained with the help of the L'Hopital's rule 
+The first term in the above expression is well-defined in $x=0$, even for $\nu=0$ (the limit can be obtained with the help of the L'Hôpital's rule 
 and recalling that $\rho_{\nu}=O(x-X_{\nu})$ in the vicinity of the resonance), and is uniformly bounded in $\nu$, together with its derivatives. 
@@
 \begin{align*}
- \left(\log\rho_{\nu}(x-X_{\nu})p_{\nu}\right)'=\frac{p_{\nu}}{\rho_{\nu}(x-X_{\nu})}\rho'_{\nu}(x-X_{\nu})+\log\rho_{\nu}(x-X_{\nu})p_{\nu}'.
+ \left(p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})\right)'=\frac{p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}+p_{\nu}'(x)\log\rho_{\nu}(x-X_{\nu}).
 \end{align*}
-The most singular term in the above expression is $\frac{p_{\nu}}{\rho_{\nu}(x-X_{\nu})}\rho'_{\nu}(x-X_{\nu})$ which can be bounded, for all sufficiently small $x$, by 
+The term $\frac{p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}$ can be bounded, for all sufficiently small $|x|$, by 
 \begin{align*}
- \left|\frac{p_{\nu}\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}\right|\leq \frac{C}{|x-i\nu c|},\; C>0,
+ \left|\frac{p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}\right|\leq \frac{C}{|x-i\nu c|},\; C>0,
 \end{align*}
-where we used an explicit form of $\rho_{\nu}=G(x-X_{\nu})+O((x-X_{\nu})^2), G\in\mathbb{R},$ valid for sufficiently small $\nu$ and $|x|$, as well as 
-the expansion $X_{\nu}=ic\nu+O(\nu^2)$.
+where we used an explicit form of $\rho_{\nu}=O(x-X_{\nu})$ valid for small $\nu$ and $|x|$, as well as 
+the expansion $X_{\nu}=ic\nu+O(\nu^2)$.  For sufficiently small $\nu$, the term $p_{\nu}'(x)\log\rho_{\nu}(x-X_{\nu})$ can be bounded by the above expression.
 
-Therefore, assuming that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the vicinity of the resonance, where for $\nu=0$ this function is singular, 
+Therefore, assuming that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the vicinity of the resonance, 
+where for $\nu=0$ this function is singular, 
 we obtain the following rough bound
@@
 \bealn
- \left|\frac{d^2E_x^{\nu}{dx^2}}\right|_{L^2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
+ \left|\frac{d^2E_x^{\nu}}{dx^2}\right|_{L^2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
  % &=c\left.

### 2015-05-04 report_clean/FD.tex

@@
 where the frequency 
-$\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane. \arev{Note that neither cyclotron, nor hybrid resonances occur in the problem 
-with the dielectric tensor $\varepsilon^{\nu}_{\omega}(x), \; \nu>0$ (since all the parameters are real). Hence 
+$\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane. \arev{Notice that neither cyclotron, nor hybrid resonances occur in the problem 
+with the dielectric tensor $\uuline{\varepsilon_{\omega}^{\nu}}(x), \; \nu>0$ (since all the problem parameters are real). Hence 
 the choice of the non-zero plasma friction $\nu>0$ can be viewed as a regularization of the problem. }

### 2015-05-04 report_clean/responce_reviewers.tex
cosmetics

@@
 More important corrections include
+\begin{itemize}
+\item changed the wording in the abstract
 
-- changed the wording in the abstract
-
-- corrected the definition of the cold plasma dielectric tensor, to match the convention $\partial_t\rightarrow -i\omega$ (it had to be hermitian conjugate; 
+\item corrected the definition of the cold plasma dielectric tensor, to match the convention $\partial_t\rightarrow -i\omega$ (it had to be hermitian conjugate; 
 this had been done everywhere, the corresponding corrections had been made in Table 1 and some figures)
 
-- corrected the definitions of $\alpha,\delta$ to comply with the definition of the cold plasma dielectric tensor of Stix
+\item corrected the definitions of $\alpha,\delta$ to comply with the definition of the cold plasma dielectric tensor of Stix
 
@@
 
-- corrected the formulation of the lemma on the well-posedness and added a remark after the lemma on the sign of $\nu$.
+\item corrected the formulation of the lemma on the well-posedness and added a remark after the lemma on the sign of $\nu$.
 
--corrected assumption on smoothness of $E_y^{\nu}$ in the section 'Numerical Experiments'.
+\item corrected assumption on smoothness of $E_y^{\nu}$ in the section 'Numerical Experiments'.
 
--shortened slightly the section on limiting amplitude for a non-resonant case.
+\item shortened slightly the section on limiting amplitude for a non-resonant case.
+\end{itemize}
 
@@
 which hopefully will facilitate in reading the article. 
-
-Concerning Sections 4.1.2, 4.3.1: 
+\begin{itemize}
+ \item Concerning Sections 4.1.2, 4.3.1: 
 We define more precisely the hybrid resonance now, which in fact requires that $\alpha$ vanishes, 
@@
 
+\item 
 The notation: 
@@
 
-The case $\omega=\omega_c$:
+\item The case $\omega=\omega_c$:
 Indeed, $\epsilon_{\infty}<\infty$ if $\omega_c^2\neq \omega^2$, but formally one also needs to require the boundedness of $\omega_p^2$. Therefore we 
@@
 
-The limiting amplitude/absorption principle:
+\item The limiting amplitude/absorption principle:
 
 A brief description of what limiting absorption and limiting amplitude principles had been added in the end of the introduction.
+\end{itemize}
 
-2. 'The reduction to a 1d problem is not clearly justified' - indeed, we changed this in the introduction by adding an assumption on $N_e, B_0$, 
+2. 'The reduction to a 1d problem is not clearly justified':  indeed, we changed this in the introduction by adding an assumption on $N_e, B_0$, 
 and changed the wording in the introduction to underline that the 1D case is the one of interest.
@@
 B. Specific remarks: 
+\begin{itemize}
+\item p1, abstract: changed
 
-- p1, abstract: changed
-
-- p2: in the frequency domain  the problem is regularized by a choice $|\nu|>0$, independently of the sign of $\nu$. 
+\item p2: in the frequency domain  the problem is regularized by a choice $|\nu|>0$, independently of the sign of $\nu$. 
 It is interesting however that for a fixed $\omega$ the limits $\lim_{\nu\rightarrow 0\pm}$ do not result in the same solution. 
@@
 
-- p2, after (1): $L$ is just a non-negative real number. We found it more convenient to place the point of the isolated hybrid resonance in $x=0$.
+\item p2, after (1): $L$ is just a non-negative real number. We found it more convenient to place the point of the isolated hybrid resonance in $x=0$.
 For $\nu\neq 0$ the energy decays, we added this in the introduction.
 
-- p3: this should be now fixed in the whole of the article.
+\item p3: this should be now fixed in the whole of the article.
 
-- p3 eq (4): the notation had been changed
+\item p3 eq (4): the notation had been changed
 
-- p4, top: we changed the notation
+\item p4, top: we changed the notation
 
-- p4, eq. (5) fixed
+\item p4, eq. (5) fixed
 
-- p4, eq. (8): changed the notation in eq (8), though a more general result in Lemma 2.1 is formulated with $u,v$.
+\item p4, eq. (8): changed the notation in eq (8), though a more general result in Lemma 2.1 is formulated with $u,v$.
 
-- p4: we changed $\alpha_{\nu}$ to $\beta_{\nu}$ not to confuse with $\alpha$ in the dielectric tensor. The index $\nu$ 
+\item p4: we changed $\alpha_{\nu}$ to $\beta_{\nu}$ not to confuse with $\alpha$ in the dielectric tensor. The index $\nu$ 
 just underlines the dependence of the angle $\beta_{\nu}$ on $\nu$ (indeed, the coercivity result as it is stated, holds for this specific value of $\beta_{\nu}$ defined 
@@
 
-- p. 5: indeed, we changed this
+\item p. 5: indeed, we changed this
 
-- p.6:  changed
+\item p.6:  changed
 
--p 6: $Ex$ changed
+\item p 6: $Ex$ changed
 
--p 8: 'our' code, changed
+\item p 8: 'our' code, changed
 
- - p.8: fixed section number
+ \item p.8: fixed section number
 
- - p.8 eq (12): added $\nu=0$ + explanation
+ \item p.8 eq (12): added $\nu=0$ + explanation
 
- - p.8: added the Airy equation and pointed out the analyticity of the Airy equation. Additionally added a remark on the behaviour of the Airy function to justify the choice of the right boundary 
+ \item p.8: added the Airy equation and pointed out the analyticity of the Airy equation. Additionally added a remark on the behaviour of the Airy function to justify the choice of the right boundary 
  condition $\partial_x E=0$.
 
- -p.8: the citation had been fixed; we expect $E_y$ to be analytic in this case (since we want it to be equal $\mathrm{Ai}(x)$, this is pointed out right now), 
+ \item p.8: the citation had been fixed; we expect $E_y$ to be analytic in this case (since we want it to be equal $\mathrm{Ai}(x)$, this is pointed out right now), 
  and $E_x$ thus is smooth.
 
- -  p9, Figure 3: fixed the captions. This had been done for other figures as well. The values $E^{c}_{x,y}$ had been defined in the caption.
+ \item  p9, Figure 3: fixed the captions. This had been done for other figures as well. The values $E^{c}_{x,y}$ had been defined in the caption.
 
- -p9 on top
+ \item p9 on top
   The title of Section 4.1.2 had been changed to Solution of a Frequency-Domain Problem with Resonance
 
- - p9 Equation (15,16): changed
+ \item p9 Equation (15,16): changed
 
- - p9 after (17): it is really necessary to assume that $H^2$-norm that is bounded, for using the inequality (25). 
+ \item p9 after (17): it is really necessary to assume that $H^2$-norm that is bounded, for using the inequality (25). 
  We fixed an assumption on $E_y$, which was incorrect before.
 
- - p10 before and after Table 1 : fixed
+ \item p10 before and after Table 1 : fixed
 
- --p 11 Figure 4: fixed
+ \item p 11 Figure 4: fixed
 
- -- p11 Figure 5:
+ \item p11 Figure 5:
 Agree, fixed. We added a remark in a caption to Figure 4 as well.
 
--{\textcolor{red}{p12}}
+\item {\textcolor{red}{p12}}
 
-- p12 Section 4.3: this explanation had been moved to the introduction
+\item p12 Section 4.3: this explanation had been moved to the introduction
 
-- p12 Section 4.3.1
+\item p12 Section 4.3.1
 
@@
 
-- p12 Equation (23): it had been removed
+\item p12 Equation (23): it had been removed
 
-- p14 Figures 8 and 9
+\item p14 Figures 8 and 9
 Added the captions
 
-- p15 in Conclusion
+\item p15 in Conclusion
   Indeed $P1$!
 
- -references: corrected
+\item references: corrected
+  \end{itemize}
 
 \section{Response to  Reviewer 2}
-
--p2:  We tried to change the wording in the introduction to make it more clear what is a hybrid resonance. 
+ \begin{itemize}
+\item p2:  We tried to change the wording in the introduction to make it more clear what is a hybrid resonance. 
 The singularity appears for $\nu=0$, provided that the diagonal part of the dielectric tensor vanishes and the non-diagonal part does not.
 
-- 'matricial' had been changed to 'matrix'.
+\item 'matricial' had been changed to 'matrix'.
 
-- p6, 3.1.
+\item p6, 3.1.
 
@@
 
-- p10: mesh multiple times finer. It should be said exactly how many times.
+\item p10: mesh multiple times finer. It should be said exactly how many times.
 
@@
 
-- {\textcolor{red}{p.12: fixed the typos.}}
+\item {\textcolor{red}{p.12: fixed the typos.}}
+\end{itemize}
 

### 2015-05-04 report_clean/numerics.tex
cosmetics

@@
 The first term in the above expression is well-defined in $x=0$, even for $\nu=0$ (the limit can be obtained with the help of the L'Hôpital's rule 
-and recalling that $\rho_{\nu}=O(x-X_{\nu})$ in the vicinity of the resonance), and is uniformly bounded in $\nu$, together with its derivatives. 
+and recalling that $\rho_{\nu}=O(x-X_{\nu})$ in the vicinity of the resonance), and is uniformly bounded for sufficiently small $\nu$, together with its derivatives. 
 The same holds for the third term. To examine the behaviour of $\left(\tilde{E}_{y}^{\nu}\right)''$, 

### 2015-05-04 report_clean/responce_reviewers.tex
report responce

@@
 
-  It is true, but in this case there is no resonance, since $\delta(x)\equiv 0$. Hence $E_x=-\frac{i\delta}{\alpha}E_y\equiv 0$, 
+  True, but in this case there is no resonance, since $\delta(x)\equiv 0$. Hence $E_x=\frac{i\delta}{\alpha}E_y\equiv 0$, 
   and $E_y$ solves the Airy equation in the frequency domain. We added a small remark to Section 4.3.1 to underline this.
@@
 \item p14 Figures 8 and 9
+
 Added the captions
@@
 \item p15 in Conclusion
-  Indeed $P1$!
+
+  Indeed $P1$
 

### 2015-05-04 report_clean/responce_reviewers.tex
mod2

@@
 
-\item corrected the formulation of the lemma on the well-posedness and added a remark after the lemma on the sign of $\nu$.
+\item corrected the formulation of the lemma 2.3 on the well-posedness and added a remark after the lemma on the sign of $\nu$.
 
-\item corrected assumption on smoothness of $E_y^{\nu}$ in the section 'Numerical Experiments'.
+\item Section 4.1.1: corrected assumption on smoothness of $E_y^{\nu}$ in the section 'Numerical Experiments'.
 

### 2015-05-06 report_clean/intro.tex
+1
spotted a sign mistake

@@
 \begin{split}
--\varepsilon_0 \partial_t E_x +\partial_y H_z = J_x,\\
--\varepsilon_0 \partial_t E_y -\partial_x H_z = J_y,\\
+-\epsilon_0 \partial_t E_x +\partial_y H_z = J_x,\\
+-\epsilon_0 \partial_t E_y -\partial_x H_z = J_y,\\
 \mu_0 \partial_t H_z + \partial_x E_y-\partial_y E_x= 0
@@
 \label{eq:boundary_conditions_intro}
-curl \hat{\mathbf{E}} -i \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} =curl \E_{inc} -\imath\lambda\E_{inc}\wedge \n,
+curl \hat{\mathbf{E}} \mrev{+}i \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} =curl \E_{inc} \mrev{+}\imath\lambda\E_{inc}\wedge \n,
 \ee

### 2015-05-06 report_clean/numerics.tex
fixed some mistakes!

--- 2015-05-04 report_clean/numerics.tex
@@
 \label{eq:cond}
- \alpha(x)=-x \text{  in some neighbourhood of $0$ }.
+ \mrev{\alpha(x)=-x+O(x^2) \text{  in some neighbourhood of $0$ }}.
 \end{align}
@@
 E_{y}^{\nu}(x)=\tilde{E}_{y}^{\nu}(x)+S_{\nu}(x), \\
-\tilde{E}_{y}^{\nu}(x)=(\alpha(x)+i\nu)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})=(-x+i\nu)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu}),
+\tilde{E}_{y}^{\nu}(x)=(\alpha(x)+i\nu)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu}).
 \end{align*}
-where $\rho_{\nu}$ is a smooth function s.t. $\rho_{\nu}(0)=0,\; \rho_{\nu}'(0)\neq 0$, the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R}$, 
+Here $\rho_{\nu}$ is a smooth function s.t. $\rho_{\nu}(0)=0,\; \rho_{\nu}'(0)\neq 0$, i.e. $\rho_{\nu}=C_{\rho}(x-X_{\nu})+O\left((x-X_{\nu})^2\right), \; C_{\rho}\neq 0$, 
+the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R},\; c\neq 0,$, 
 and $p_{\nu}(x),\; S_{\nu}(x)$ are smooth functions, which, together with their derivatives, are bounded independently of $\nu$.}
@@
 \begin{split}
- \|v-I^{h}v\|_{L^2}\leq Ch^2\left|v''\right|_{L^2},\; C>0,\\
- \|v-I^{h}v\|_{H^1}\leq Ch|v''|_{L^2},\; C>0, 
+ \|v-I^{h}v\|_{L^2}\leq C_1h^2\left|v''\right|_{L^2},\; C_1>0,\\
+ \|v-I^{h}v\|_{H^1}\leq C_2h|v''|_{L^2},\; C_2>0, 
  \end{split}
@@
   \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}%\leq C_1\nu^{-1}h\|\left(E_y^{\nu}\right)''\|_{L_{2}}+C_2\nu^{-1}h^2\|\left(E_x^{\nu}\right)''\|_{L_{2}}
-  \leq C\nu^{-1}h\|\left(E_y^{\nu}\right)''\|_{L^2}+C\nu^{-1}h^2\|\left(E_x^{\nu}\right)''\|_{L^2}.
+  \leq C\left(\nu^{-1}h\|\left(E_y^{\nu}\right)''\|_{L^2}+\nu^{-1}h^2\|\left(E_x^{\nu}\right)''\|_{L^2}\right).
 \end{align}
@@
 First of all let us examine the behaviour the derivatives of $E_{y}^{\nu}$ in the vicinity of the resonance, 
-in particular, the term $\tilde{E}_{y}^{\nu}$ which is singular for $\nu=0$ in the resonant point:
+in particular, the term $\tilde{E}_{y}^{\nu}$ which is singular for $\nu=0$ in the resonance:
 \begin{align}
 \label{eq:eynuprime}
- \left(\tilde{E}_{y}^{\nu}\right)'&=\frac{(-x+i\nu)\rho_{\nu}'(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}p_{\nu}(x)-p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+p'_{\nu}(x)(-x+i\nu)\log\rho_{\nu}(x-X_{\nu}).
+ \left(\tilde{E}_{y}^{\nu}\right)'&=\frac{(\alpha(x)+i\nu)\rho_{\nu}'(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}p_{\nu}(x)+
+ \alpha'(x)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+p'_{\nu}(x)(\alpha(x)+i\nu)\log\rho_{\nu}(x-X_{\nu}).
 \end{align}
 The first term in the above expression is well-defined in $x=0$, even for $\nu=0$ (the limit can be obtained with the help of the L'Hôpital's rule 
-and recalling that $\rho_{\nu}=O(x-X_{\nu})$ in the vicinity of the resonance), and is uniformly bounded in $\nu$, together with its derivatives. 
+and recalling that $\rho_{\nu}=C_{\rho}(x-X_{\nu})+O((x-X_{\nu})^2)$ in the vicinity of the resonance), and is uniformly bounded for sufficiently small $\nu$, together with its derivatives. 
 The same holds for the third term. To examine the behaviour of $\left(\tilde{E}_{y}^{\nu}\right)''$, 
@@
 \begin{align*}
- \left(p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})\right)'=\frac{p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}+p_{\nu}'(x)\log\rho_{\nu}(x-X_{\nu}).
+ \left(\alpha'(x)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})\right)'=\frac{\alpha'(x)p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}+(\alpha'(x)p_{\nu}(x))'\log\rho_{\nu}(x-X_{\nu}).
 \end{align*}
-The term $\frac{p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}$ can be bounded, for all sufficiently small $|x|$, by 
+The term $\frac{\alpha'(x)p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}$ can be bounded, for all sufficiently small $|x|$, by 
 \begin{align*}
@@
 where we used an explicit form of $\rho_{\nu}=O(x-X_{\nu})$ valid for small $\nu$ and $|x|$, as well as 
-the expansion $X_{\nu}=ic\nu+O(\nu^2)$.  For sufficiently small $\nu$, the term $p_{\nu}'(x)\log\rho_{\nu}(x-X_{\nu})$ can be bounded by the above expression.
+the expansion $X_{\nu}=ic\nu+O(\nu^2)$.  For sufficiently small $\nu$, the term $(\alpha'(x)p_{\nu}(x))'\log\rho_{\nu}(x-X_{\nu})$ 
+can be bounded by the above expression.
 
@@
 \end{align*}
-for sufficiently small $\nu>0$.
+valid for sufficiently small $\nu>0$.
 }
 Let us now derive a similar bound on the second derivative of $E_{x}^{\nu}$:
-\ben
+\begin{align}
+\label{eq:ex_eq1}
  \frac{d^2}{dx^2}E_x^{\nu}=\frac{(f^{\nu})''}{\alpha+i\nu}-2\frac{(f^{\nu})'\alpha'}{(\alpha+i\nu)^2}+\frac{f^{\nu}\alpha''}{(\alpha+i\nu)^3},
-\een
+\end{align}
 from which, together with (\ref{eq:cond}, \ref{eq:eynuprime}, \ref{eq:exact}), it follows that there exists $c>0$ s.t. for all sufficiently small $\nu$ 
@@
 
-Let us check numerically whether this holds true. 
-To do so, we conduct the  numerical experiment with parameters for the problem (\ref{eq:main_frequency_domain} as given in Table \ref{tab:parameters}. \mrev{Recall as well that we choose $\theta=0$. }
+\mrev{
+One can assume $\alpha(x)=-x$ in some interval around zero. In this case the above estimate can be improved. Due to $\alpha''(x)\equiv 0$, 
+the equation (\ref{eq:ex_eq1}) reads
+\begin{align*}
+ \frac{d^2}{dx^2}E_x^{\nu}=\frac{(f^{\nu})''}{\alpha+i\nu}-2\frac{(f^{\nu})'\alpha'}{(\alpha+i\nu)^2},
+\end{align*}
+which, in turn, for sufficiently small $\nu$, can be bounded as follows, see (\ref{eq:eynuprime}), (\ref{eq:exact}) and recall that $\rho_{\nu}=C_{\rho}(x-X_{\nu})+O((x-X_{\nu})^2)$ and $X_{\nu}=ic\nu+O(\nu^2)$,
+\begin{align*}
+ \left| \frac{d^2}{dx^2}E_x^{\nu}\right|_{L^2}^{2}\leq C\int\limits_{\Omega}\frac{\left|\log\rho_{\nu}(x-X_{\nu})\right|^2}{(x^2+\nu^2)^{2}}dx,
+ \leq G\nu^{-3}\log^2\nu,\qquad C,G>0,
+\end{align*}
+and hence the estimate 
+\ben
+ \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}\leq C\nu^{-\frac{5}{2}}h^2\log\frac{1}{\nu}+C\nu^{-\frac{3}{2}}h
+\een
+holds true. From this it follows that $h=O\left(\nu^{\frac{3}{2}}\right)$ in this particular case.
+
+}
+
+To check numerically whether this holds true we conduct the  numerical experiment with parameters for the problem (\ref{eq:main_frequency_domain}) as given in Table \ref{tab:parameters}. 
+Recall as well that we choose $\theta=0$.
+
 \begin{table}[htb!]
@@
 \end{table}
-Denoting by \mrev{$E_{x}^{\nu,h}$ the solution $E_{x}(x)$} computed on the mesh with the \mrev{width $h$ with 
-the absorption $\nu$, and by $E_{x}^{\nu}$} the solution computed on a mesh multiple times finer (\arev{more precisely, the reference mesh
+Denoting by \mrev{$E_{x}^{\nu,h}$ the solution} computed on the mesh with the \mrev{width $h$ with 
+the absorption $\nu$, and by $E_{x}^{\nu}$ the exact solution} (which in practice was approximated by the solution computed on a mesh multiple times finer, \arev{more precisely, the reference mesh
 was typically 10-20 times finer, with the exception when the computation was done for very small values of $h$ where for comparison twice finer meshes were used}), let 

### 2015-06-08 report_clean_merged/FD.tex
added report merged with the files of Lise-Marie and Bruno

--- 2015-05-04 report_clean/FD.tex
@@
 \section{Frequency domain study}
-The goal of this section is to review the connection between the frequency domain counterpart of the problem (\ref{eq:main_model}) and 
+This section reviews the connection between the frequency domain counterpart of the problem (\ref{eq:main_model}) and 
 the regularized problem (\ref{eq:seq_regularized}).
 
-The model (\ref{eq:main_model}) can be rewritten in the frequency domain as 
+Model (\ref{eq:main_model}) can be rewritten in the frequency domain as 
 \bealn
@@
 \begin{matrix}
- i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
- i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
+ i\theta \partial_x \widehat{E}_y+\theta^2 \widehat{E}_x\\
+ i\theta \partial_x \widehat{E}_x -\partial_x^2 \widehat{E}_y
 \end{matrix}
@@
 \begin{matrix}
- \hat{E}_x\\
- \hat{E}_y
+ \widehat{E}_x\\
+ \widehat{E}_y
 \end{matrix}
@@
 where the frequency 
-$\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane. \arev{Note that neither cyclotron, nor hybrid resonances occur in the problem 
-with the dielectric tensor $\varepsilon^{\nu}_{\omega}(x), \; \nu>0$ (since all the parameters are real). Hence 
-the choice of the non-zero plasma friction $\nu>0$ can be viewed as a regularization of the problem. }
+$\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane. \arev{ %Notice that neither cyclotron, nor hybrid resonances occur in the problem 
+%with the dielectric tensor $\uuline{\varepsilon_{\omega}^{\nu}}(x), \; \nu>0$ (since all the problem parameters are real). Hence 
+%t
+The choice of the non-zero plasma friction $\nu>0$ is a regularization of the problem. }
 
 \mrev{
-The series expansion as $\nu\rightarrow 0$ gives at leading orders
+A series expansion as $\nu\rightarrow 0$ gives at leading orders
 \bealn
@@
 \eealn
-where $\alpha_{\omega},\;\delta_{\omega}$ are defined by (\ref{eq:alpha_delta}). In the frequency domain one thus can consider 
+where $\alpha_{\omega},\;\delta_{\omega}$ are defined by (\ref{eq:alpha_delta}). %In the frequency domain 
+One thus can consider 
 the following regularization of the cold plasma dielectric tensor of the above problem, valid as $\nu\rightarrow 0$:
@@
 \een
-yields the same solution as $\nu\rightarrow 0$. }
-Thus, applying the above process to (\ref{eq:main_model}) in the frequency domain, we obtain, see also \cite{Despres_2014},
+yields to the same limit solution as $\nu\rightarrow 0$. }
+As a consequence we will consider in this work the simpler regularized system
+%Thus, applying the above process to (\ref{eq:main_model}) in the frequency domain, we obtain, see also \cite{Despres_2014},
 \begin{align*}
@@
 \label{assumption:smooth}
-The coefficients  $\alpha(x)$ and $\delta(x)$ are assumed to be sufficiently smooth, i.e. bounded and continuous in  
+The coefficients  $\alpha(x)$ and $\delta(x)$ are assumed to be sufficiently smooth, i.e. continuous in  
 $\left[-L,\; H\right]$.
@@
 %denoting by $\theta$ the corresponding Fourier variable. 
-\mrev{In this section we study the well-posedness of the problem (\ref{eq:main_frequency_domain}) with the 
- boundary conditions (\ref{eq:boundary_conditions_intro}) with the help of Lax-Milgram lemma.} 
-After introducing $\Omega=(-L,\; H)\subset \mathbb R$ and defining the function space of the problem  $\mathbf{V}=L^{2}(\Omega)\times H^{1}(\Omega)$, 
+\mrev{In this section we study the well-posedness of Problem (\ref{eq:main_frequency_domain}) with the 
+ boundary conditions (\ref{eq:boundary_conditions_intro}), thanks to the Lax-Milgram lemma.} 
+After introducing $\Omega=(-L,\; H)\subset \mathbb R$ and defining the function space  $\mathbf{V}=L^{2}(\Omega)\times H^{1}(\Omega)$, 
 equipped with the norm
@@
 \een
-the resulting one-dimensional system can be rewritten in the following variational form:
+the resulting one-dimensional system reads in the following variational form:
 \begin{align}
@@
 \begin{array}{l}
-\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\tilde E_y' -\urev{i} \theta \tilde E_x)} - \int_{-L}^H (\uuline{\varepsilon}^{0} +i\nu \mathrm{Id}) \E \cdot \overline{\tilde \E}
+\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\widetilde E_y' -\urev{i} \theta \widetilde E_x)} 
+- \int_{-L}^H (\uuline{\varepsilon}^{0} +i\nu \mathrm{Id}) \E \cdot \overline{\widetilde \E}
 %\\ \displaystyle 
- - i \lambda E_y (-L)\overline{ \tilde E_y (-L)} = -g_{inc} (-L) \overline{( \tilde E_y(-L) )},
+ - i \lambda E_y (-L)\overline{ \widetilde E_y (-L)} = -g_{inc} (-L) \overline{( \widetilde E_y(-L) )},
 \end{array}\\
 \nonumber
-\text{ for all } \tilde{\mathbf{E}}=(\tilde E_x,\tilde E_y)\in \mathbf{V}.
+\text{ for all } \widetilde{\mathbf{E}}=(\widetilde E_x,\widetilde E_y)\in \mathbf{V}.
 \end{align}
@@
 %=\omega\geq 0$. 
-Let us remark that in this and further sections, where it is not ambiguous, we will use the notation $E_{x,y}$ instead of $\hat{E}_{x,y}$ for convenience. \mrev{Also, 
+Let us remark that in this and further sections, where it is not ambiguous, we will use the notation $E_{x,y}$ instead of $\widehat{E}_{x,y}$ for convenience. \mrev{Also, 
 by $\|u\|_{L^{2}}$ we will denote $\|u\|_{L^{2}(\Omega)}$, for $u\in L^2(\Omega)$, and $\|\ubf\|_{L^2(\Omega)}=\left(\|u_1\|^2_{L^2}+\|u_2\|^2_{L^2}\right)^{\frac{1}{2}}$, 
@@
 
-The above can be reformulated as, \urev{for the unknown $\mathbf{E}$ and $\tilde{\mathbf{E}}$ a test function},
-\ben
-a\left(\mathbf{E},\tilde{\mathbf{E}}\right)=l(\tilde{\mathbf{E}}), \; \text{ for all }\tilde{\mathbf{E}}\in \mathbf{V},
-\een
-with a bilinear form $a$ and a linear form $l$, \urev{defined for $\mathbf{u},\; \mathbf{v}\in \mathbf{V}$}:
+For the sake of conciseness, consider the following definitions. Let $a$ and $l$ be the bilinear and linear forms, \urev{defined for $\mathbf{u},\; \mathbf{v}\in \mathbf{V}$}:
 \ben
@@
 	a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -i\theta u_1)\overline{(v_2' -i \theta v_1)} - \int_{-L}^H \uuline{\varepsilon}^{0} \ubf\cdot \overline{\vbf}, 
-	\\ a_2(\ubf,\vbf) = -\nu \int_{-L}^H  \ubf\cdot \overline{\vbf} - \lambda u_2 (-L) \overline{v_2 (-L)} , 
+	\\ a_2(\ubf,\vbf) = -\nu \int_{-L}^H  \ubf\cdot \overline{\vbf} - \lambda u_2 (-L) \overline{v_2 (-L)}.
 \end{array}\right.
+\een
+Then \eqref{vf1dcase} reads: \urev{find $\mathbf{E}$ such that},
+\ben
+a\left(\mathbf{E},\tilde{\mathbf{E}}\right)=l(\tilde{\mathbf{E}}), \; \text{ for all }\tilde{\mathbf{E}}\in \mathbf{V}.
 \een
@@
 Let us denote the spectral radius of $\uuline{\varepsilon}^{0}$ by $\heps =  \|\rho(\uuline{\varepsilon}^{0})\|_{L^{\infty}(\Omega)}$. 
-By Assumption \ref{assumption:smooth}, the spectral radius $\heps=\max\left(\|\alpha+\delta^2\|_{L^{\infty}(\Omega)}, \|\alpha-\delta^2\|_{L^{\infty}(\Omega)}\right)$ 
+By Assumption \ref{assumption:smooth}, the spectral radius $\heps=\max\left(\|\alpha+\delta\|_{L^{\infty}(\Omega)}, \|\alpha-\delta\|_{L^{\infty}(\Omega)}\right)$ 
 is bounded.}
@@
 \eealn
-where $C>0$ does not depend on $\nu$. The problem~\eqref{vf1dcase} is well-posed in $\mathbf{V}$.
+where $C>0$ does not depend on $\nu$. Problem~\eqref{vf1dcase} is well-posed in $\mathbf{V}$.
 
@@
 	\een
-	Thus one can write
+	Thus
 	$
 	a_1(\ubf,\ubf)  \geq \frac{1}{2}\|u_2'\|^2_{L^2}-  (\heps  +  \theta^2) \| \ubf \|_{L^2}^2$.
-	One also has that, \mrev{for $\lambda \geq 0$},
+	On the other hand, \mrev{for $\lambda \geq 0$},
 	$
@@
 	\een	
-	The problem \eqref{vf1dcase} is uniquely solvable thanks to Lax-Milgram theorem.
+	Problem \eqref{vf1dcase} is then uniquely solvable thanks to Lax-Milgram theorem.
 \end{proof}
-\begin{remark}
-\mrev{Note that in the case $\lambda=0$, one can show that the problem is well-posed for all $\nu\neq 0$, since $a_2(\ubf,\ubf)=-\nu\|\ubf\|_{L^2}^2$ and 
-thus in the above proof
-\begin{align*}
-a_1(\ubf,\ubf)-\frac{\heps  +  \theta^2 + 1 }\nu a_2(\ubf,\ubf)=\left(a_1(\ubf,\ubf)+(\heps  +  \theta^2)\|\ubf\|_{L^2}^2\right)+\|\ubf\|_{L^2}^2.
-\end{align*}
-Similarly, in the case $\lambda<0$, it is possible to demonstrate the well-posedness of the problem for $\nu<0$. 
-}
-\end{remark}
+%
+%
+%\begin{remark}
+%\mrev{Not the variational problem can be proved well-posed
+%with the same method for  slightly different coefficients.
+%%For example for $\lambda<0$ and  Note that in the case $\lambda=0$, one can show that the problem is well-posed for all $\nu< 0$, since $a_2(\ubf,\ubf)=-\nu\|\ubf\|_{L^2}^2$ and 
+%%thus in the above proof
+%%\begin{align*}
+%%a_1(\ubf,\ubf)-\frac{\heps  +  \theta^2 + 1 }\nu a_2(\ubf,\ubf)=\left(a_1(\ubf,\ubf)+(\heps  +  \theta^2)\|\ubf\|_{L^2}^2\right)+\|\ubf\|_{L^2}^2.
+%%\end{align*}
+%%Similarly, in the case $\lambda<0$, it is possible to demonstrate the well-posedness of the problem for $\nu<0$. 
+%}
+%\end{remark}
+
 \begin{remark} 
 \label{remark:other}
-The above proof is not optimal in the case when $\left|\alpha(x)\right|>c>0$ for $c>0$ on the whole interval $[-L,\; H]$, at least 
-for the case $\theta=0$. In this case the problem (\ref{eq:var_form2}) is well-posed for $\nu=0$. More precisely, it can be written 
-as a system of two equations, where the first equation (for $E_y$) is the variational formulation for the Helmholtz equation 
-with the variable coefficient $k^2=(\alpha-\frac{\delta^2}{\alpha})$ \mrev{and the boundary conditions (\ref{eq:boundary_conditions_frequency_domain})}, and the second equation 
+The above proof is not optimal when the diagonal coefficient is uniformly positive, namely 
+$\alpha(x)>c$ for some $c>0$ on the whole interval $[-L,\; H]$, at least 
+for the case $\theta=0$. In this particular case Problem (\ref{eq:var_form2}) is well-posed for $\nu=0$. More precisely, it can be written 
+as a system of two equations, the first equation (for $E_y$) being the variational formulation for the Helmholtz equation 
+with the variable coefficient $k^2=(\alpha-\frac{\delta^2}{\alpha})$ \mrev{coupled to boundary conditions (\ref{eq:boundary_conditions_frequency_domain})}, and the second equation being  
 \begin{align*}
-  \left(E_x,u\right)=\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega), 
+  \left(E_x,u\right)=\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega).
 \end{align*}
-uniquely defines $E_x\in L^{2}(\Omega)$. The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
-was demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H^{1}(\Omega)$, we can obtain $E_x$ from the second equation.
+The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
+was demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H^{1}(\Omega)$, $E_x\in L^{2}(\Omega)$ is uniquely defined from the latter equation.
 \end{remark}
@@
 Testing the variational formulation (\ref{vf1dcase}) with $(\tilde E_x,0)$ and $(0,\; \tilde{E}_y)\in\mathbf{V}$ and using 
-an explicit expression for the tensor of the dielectric permittivity (\ref{eq:epsilon_0}), we can rewrite it as a system of two equations
+an explicit expression for the tensor of the dielectric permittivity (\ref{eq:epsilon_0}), we get the following system of two equations
 %\begin{align*}
@@
 \eealn
-we rewrite the system (\ref{eq:var_form2}) in an antisymmetric block form:
+we rewrite System (\ref{eq:var_form2}) in an antisymmetric block form:
 \ben
@@
 \een
-This expression greatly simplifies when \urev{ choosing $V_{E_x}=V_{E_{y}}$, spanned by $\left(\phi_{m}\right)_{m=1}^{N_{2}}$,} and
+This expression greatly simplifies when \urev{ choosing $V_{E_x}=V_{E_{y}}$, spanned by a unique set of basis funtions $\left(\phi_{m}\right)_{m=1}^{N_{2}}$,} and
 in the case $\theta=0$. One obtains the \urev{matrix} structure

### 2015-06-08 report_clean_merged/absorption.tex
added report merged with the files of Lise-Marie and Bruno

--- 2015-05-04 report_clean/absorption.tex
@@
 \end{itemize}
-For every fixed absorption rate \urev{$\nu>0$}, in the time domain we choose the boundary conditions of the form
+For every fixed absorption rate \urev{$\nu>0$}, in the time domain we choose the boundary conditions
 \begin{align}
@@
 \ben
-\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t), \text{ and } \Im\left(\hat{\mathbf{E}}^{\nu}\exp(\mrev{-it})\right)
+\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t), \text{ and } \Im\left(\hat{\mathbf{E}}^{\nu}\mathrm{e}^{\mrev{-it}}\right)
 \een
@@
 
-In all the experiments in this section the CFL number was chosen as 0.5.
+In all the experiments in this section the CFL number was set to 0.5.
 \subsubsection{No-Resonance Case}
@@
 the Airy equation, c.f. also Remark \ref{remark:other}. We set $\omega_c=0$ (thus $\delta(x)=0$), $\omega=1$ (hence $\alpha(x)=1-N_e(x)$), 
-choose the domain as $(-0.5, 10)$ and set the electron density $N_e(x)=1+x>0,\; x\in \Omega$. 
+on the domain as $(-0.5, 10)$ and set the electron density $N_e(x)=1+x>0,\; x\in \Omega$. 
 \urev{Importantly, since $\delta(x)=0$, in this case no resonance occurs and $E(x,t)\equiv 0$. This corresponds to the case when the
@@
 the dependence of the solution $E_{y}^{\nu}(x_c,t)$ on time $t$ for a range of $t\gg 1$. 
-One of our observations was that for smaller $\nu$ one requires more time steps to achieve the limiting amplitude solution. 
+One of our observations was that for smaller $\nu$ more time steps are required to achieve the limiting amplitude solution. 
 For $\nu=10^{-4}$ we were not able to obtain the limiting amplitude solution for $t<3\cdot 10^{4}$, unlike in the case of $\nu=10^{-2}$. 
@@
 for smaller $\nu$.
+
+\FloatBarrier

### 2015-06-08 report_clean_merged/abstract.tex
added report merged with the files of Lise-Marie and Bruno

The hybrid resonance is a physical phenomenon
that appears for example in the heating of plasma,
and as such is of scientific interest for the development  of  the ITER project.
In this paper \urev{we focus on} solutions of low regularity to Maxwell equations in
\mrev{magnetized plasmas}. 
Our main purpose is two-fold. First, we aim at investigating the finite element approximation 
of the frequency-domain problem. Second, we would like to study the resonant solutions 
in the time domain, with the help of two different finite difference approximations. 
We then compare the results with the ones obtained in the frequency domain, by  
numerical examination of the limiting absorption and limited amplitude principles.

### 2015-06-08 report_clean_merged/conclusions.tex
added report merged with the files of Lise-Marie and Bruno

--- 2015-05-04 report_clean/conclusions.tex
@@
 In this work we considered the frequency- and the time-domain formulations of the $X$-mode Maxwell equations. 
-In particular, we proved the well-posedness of the respective regularized (with the help of 
-the absorption parameter $\nu$) variational formulation, as 
+In particular, we proved the well-posedness of the regularized variational formulation with
+the absorption parameter $\nu$, as 
 well as studied the convergence of the finite element method for the problem with the resonance. 

### 2015-06-08 report_clean_merged/intro.tex
added report merged with the files of Lise-Marie and Bruno

--- 2015-05-06 report_clean/intro.tex
@@
 \urev{
-We consider the wave propagation in the cold plasma that consists of particles of single species 
-under a uniform in time background magnetic field $\mathbf{B}_0=(0,\;0,\; B_0)$. In two dimensions, in the plane 
-perpendicular to the direction of the magnetic field, this process can be described by the time-dependent Maxwell system  \cite{Stix}
+We consider the time-dependent wave propagation problem leading to the cold plasma model for a single species 
+under a uniform in time background magnetic field $\mathbf{B}_0=(0,\;0,\; B_0)$. 
+We restrict our attention to the poloidal plane, which is the plane 
+perpendicular to the direction of the magnetic field. The model can be described by the time-dependent Maxwell system  \cite{Stix}
 \begin{align}
@@
 \end{align}
-coupled with the equations for the linear electronic current  $\J = eN_e(\mathbf{r}) \ubf$
+coupled through the linear electronic current  $\J = eN_e(\mathbf{r}) \ubf$
+ with the equations 
  \begin{align}
@@
 \end{align}
-where \mrev{$\nu\geq 0$} is the friction  between particles, $e<0$ is the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density that in general 
-depends on spatial variables and is uniform in time. A non-zero value of $\nu$ constitutes a basis for the limiting absorption principle. 
-The unknowns are the electron velocity $\ubf$ and the electromagnetic field.
+where \mrev{$\nu\geq 0$} is the friction  between particles, $e<0$ is the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density.
+In the cold plasma model, because of the frequencies considered, the electron density
+depends on space and is uniform in time. A non-zero value of $\nu$ constitutes a basis for the limiting absorption principle. 
+The unknowns are the electron velocity $\ubf$ and the electromagnetic fields.
 
@@
 \een
-and
+and (\ref{eq:main_system}-\ref{eq:electronmove}) yield to
 \ben
@@
 
-To illustrate unexpected difficulties that can occur in this system, let us rewrite it in the frequency domain. To do so, 
+To illustrate unexpected difficulties that can occur in this system, consider the frequency domain counterpart of (\ref{eq:main_system}-\ref{eq:electronmove}), which corresponds to the cold plasma model.
+To do so,
 we introduce the plasma frequency $\omega_p(\mathbf{r})=\sqrt{\frac{|e|^2N_e(\mathbf{r})}{m\epsilon_0}}$, 
 the cyclotron frequency $\omega_c(\mathbf{r})=\frac{e B_0(\mathbf{r})}{m_e}$ and perform the Fourier transform 
-in time of (\ref{eq:main_system}) (with the convention $\partial_t\rightarrow -i\omega$), for a 
+in time of (\ref{eq:main_system}-\ref{eq:electronmove}) (with the convention $\partial_t\rightarrow -i\omega$), for a 
 particular case $\nu=0$:
@@
 \label{eq:model_freq_domain}
- \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})\hat{\mathbf{E}}=0,
+ \mathbf{curl}\  {\operatorname{curl}}\  \hat{\mathbf{E}}-\frac{\omega^2}{c^2}\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})\hat{\mathbf{E}}=0,
 \end{align}
@@
 $\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})$ vanishes and the non-diagonal part remains non-zero. This is a hybrid resonance case. 
-
 As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component $E_x$ is not necessarily square 
@@
 Before proceeding, let us define the geometrical setting of the problem. 
-We consider the frequency domain problem (\ref{eq:model_freq_domain}) posed in the domain $(-L,\;\infty)\times\mathbb{R},\; L>0$, with the
- boundary conditions chosen as follows. At the left boundary of the domain, which represents the wall of the Tokamak, we pose Robin boundary conditions 
+We consider the frequency domain problem (\ref{eq:model_freq_domain}) posed in a truncated infinite half-plane, $(-L,\;H)\times\mathbb{R}$, for some $L>0$ and $H>0$, with the following
+ boundary conditions. At the left boundary of the domain, which represents the wall of the Tokamak, we impose a Robin boundary condition
 \be
@@
 where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and \mrev{$\lambda\geq 0$} is 
-the frequency of the antenna. We truncate the domain 
-$(-L,\; \infty)\times\mathbb{R}$ to $(-L,\; H)\times\mathbb{R},\; H>0,$ and set on the right boundary $\operatorname{curl} \hat{\E} = 0$.
+the frequency of the antenna. At the right boundary we impose $\operatorname{curl} \hat{\E} = 0$.
 
-In this article we concentrate on a simplified model (which nevertheless is of physical interest when modelling antennas in plasmas), 
-where it is required to study the above system under the assumption that the electron density $N_{e}$ and the magnetic field $B_0$ are \textbf{uniform} in the second coordinate, more precisely 
+In this work we focus on stratified medium case: we suppose that
+%a simplified model (which nevertheless is of physical interest when modelling antennas in plasmas),  where it is required to study the above system under the assumption that 
+the electron density $N_{e}$ and the magnetic field $B_0$ are \textbf{uniform} in the second coordinate $y$,
 $N_{e}=N_{e}(x)$ and $B_0=B_0(x)$, see e.g. \cite{Despres_2014}. 
-We additionally assume that $N_e>0$ on $[-L,\;H]$. Even this simplified case contains difficulties intrinsic to the hybrid resonance \cite{Despres_2014, singular_solutions}.
+We additionally assume that $N_e>0$ on $[-L,\;H]$. We choose this simplified case to focus on the fundamental mathematical difficulties of the hybrid resonance \cite{Despres_2014, singular_solutions}.
 
@@
 \end{equation}
- posed in $(-L,\; H)$, for some $L,H>0$, with \mrev{the boundary conditions as in (\ref{eq:boundary_conditions_intro})
+ posed in the one dimension domain $(-L,\; H)$, with \mrev{the corresponding boundary conditions:
  \begin{align}
@@
 and the initial conditions for values $\left.E_{x}\right|_{t=0},\; \left.u_{x}\right|_{t=0},\; \left.E_{y}\right|_{t=0}, \; \left.u_{y}\right|_{t=0}, \; \left.H_z\right|_{t=0}$. }
-
 This is the time-domain model that will be considered in the rest of the article, unless stated otherwise.
 
-In the frequency domain (\ref{eq:main_model}) for $\nu=0$ is of the form 
+The frequency domain formulation of (\ref{eq:main_model}) for $\nu=0$ is
 \begin{align}
@@
 \end{align}
-see (\ref{eq:alpha_delta}). Indeed, the coefficients $\alpha_{\omega},\;\delta_{\omega}$, see (\ref{eq:alpha_delta}), in this case depend solely on $x$ and $\omega$.  
+see (\ref{eq:alpha_delta}). Indeed, in a stratified medium, the coefficients $\alpha_{\omega},\;\delta_{\omega}$ depend solely on $x$ and $\omega$.  
 \arev{
@@
 
-To investigate the behaviour of the solutions in the case when the hybrid resonance occurs in the system, 
-instead of the above problem we will study a sequence of the regularized problems, for $\nu\rightarrow 0$, 
+To investigate the behaviour of the solutions at the hybrid resonance, 
+we will study a sequence of the regularized problems, for $\nu\rightarrow 0$.
+These problems are not the frequency domain expression of \eqref{eq:main_model}, but a simple regularization of \eqref{eq:main_frequency_domain_intro}.
+This choice will be justified in further sections.
+The equations read:
 \begin{align}
@@
 \end{align}
-where $\mathrm{Id}$ is the identity matrix. More details on the connection of this problem with (\ref{eq:main_model}) will be provided in further sections.
+where $\mathrm{Id}$ is the identity matrix. %More details on the connection of this problem with (\ref{eq:main_model}) will be provided in further sections.
 
@@
 First, we investigate the finite element approximation of the 1D 
-problem (\ref{eq:seq_regularized}), with a dielectric tensor \mrev{regularized
-with the help of a small parameter $\nu$}. 
+frequency domain problem (\ref{eq:seq_regularized}), with a regularized dielectric tensor \mrev{for a small parameter $\nu$}. 
 %linearized with respect to $\nu$.
@@
 demonstrate that the use of  $P_1$ finite elements allows to approximate the singularity 
-of the solution fairly well (Section \ref{sec:freq_dep}). 
+of the solution efficiently (Section \ref{sec:freq_dep}). 
 }
-
-Second, we briefly develop an original scheme based on widely appreciated semi-lagrangian schemes
+Second, we develop an original scheme based on widely appreciated semi-lagrangian schemes
 for the discretization of time domain Maxwell's equations with a linear current.
-Thirdly, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
+Third, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
 $\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
@@
 We compare this result with 
-$\hat{\mathbf{E}}\mathrm{e}^{\mrev{-i\omega} t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
+$\hat{\mathbf{E}}\mathrm{e}^{\mrev{-i\omega} t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which corresponds to
 $\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
@@
 see Figure \ref{fig:limits}. 
-Even though it is true for standard linear wave problems, it is not clear \mrev{if it still holds} in our case due to the singularity
+Even though it is true for standard linear wave problems, it is not clear \mrev{if it still holds} in the singular case 
 of the hybrid resonance.

### 2015-06-08 report_clean_merged/numerics.tex
added report merged with the files of Lise-Marie and Bruno

--- 2015-05-04 report_clean/numerics.tex
@@
 \section{Numerical Experiments}
-This section is organized as follows. The first part is dedicated to the numerical implementation
+This section is organized as follows. The first part is dedicated to the numerical implementation and simulation 
 of the frequency domain formulation \eqref{vf1dcase}. We study the convergence of this formulation and the behaviour 
 of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
-performed with the help of \urev{our} code written in Octave.  
+performed with \urev{our} code written in Octave.  
 We implemented the scheme described in Section \ref{sec:discr} for a case of $P_{1}$-space used 
-for the approximation of $E_{x}$ and $E_{y}$ and $\theta=0$, thus working with the system (\ref{eq:simple_system}). 
+for the approximation of $E_{x}$ and $E_{y}$ and $\theta=0$, thus working with System (\ref{eq:simple_system}). 
 We apply permutation to the above system 
@@
 \label{sec:airy_fd_validity}
-To check the validity of the code, we first perform a numerical experiment with (formally chosen) parameters:
+To check the validity of the code, we first perform a numerical experiment in the following case:
 \begin{align}
@@
 \end{align}
-\urev{It can be shown that $E_{y}$ that solves (\ref{eq:main_frequency_domain}) with the above parameters,  
-and $\nu=0$, satisfies the Airy equation, see also Remark \ref{remark:other},
+\urev{In this case $E_{y}$ that solves (\ref{eq:main_frequency_domain})  satisfies the Airy equation, see also Remark \ref{remark:other},
 \begin{align*}
@@
 \end{align*}
-One of the solutions of this equation, an Airy function \urev{$\Ai(x)$}, see \cite[Chapter 10.4]{abramowitz_stegun}, is analytic and 
+The physical solution of this equation, the Airy function \urev{$\Ai(x)$}, see \cite[Chapter 10.4]{abramowitz_stegun}, is analytic and 
 decays rapidly as $x\rightarrow \infty$. }
-\mrev{Hence, choosing $H$ sufficiently large (the actual value used in the experiments $H=10$, where $\left|\Ai'(10)\right|<1e-9$) and the boundary conditions as 
+\mrev{Hence, choosing $H$ sufficiently large (the actual value used in the experiments $H=10$, where $\left|\Ai'(10)\right|<1e-9$) and the boundary conditions
 \begin{align}
@@
 \end{align}
-we ensure that $E_{y}$ that solves the above problem is well approximated by $\Ai(x)$, and $E_{x}$ by $-i\frac{\delta(x)}{\alpha(x)}\Ai(x)$ (\urev{and hence both functions are smooth}). 
+the exact solutions are: $\Ai(x)$ for the unknown $E_{y}$, and $i\frac{\delta(x)}{\alpha(x)}\Ai(x)$ for $E_{x}$. \urev{Hence both functions are smooth}. 
 The well-posedness of the respective variational formulation is due to Remark \ref{remark:other}. }
 
-In Fig.~\ref{fig:conv_rate} we demonstrate the convergence rates for this problem, comparing the solution with the 
-known analytic solution. 
+In Fig.~\ref{fig:conv_rate} we verify the convergence rates for this problem, comparing the solution with the analytic solutions. 
 Importantly, the obtained convergence rates are in agreement with known estimates of the standard theory of convergence~\cite[Chapter 5.7,
@@
 of Lemma \ref{lemma:well_posedness}  are satisfied. 
-For simplicity, let us assume 
+For simplicity, let us assume \mrev{that $\alpha(x)$ is smooth and }
 \begin{align}
 \label{eq:cond}
- \alpha(x)=-x \text{  in some neighbourhood of $0$ }.
+ \mrev{\alpha(x)=-x \text{  in some neighbourhood of $0$ }}.
 \end{align}
 \mrev{Let $h>0$ denote the meshwidth. }Given $\mathbf{V}_{h}=P_{h}^{1}\times P_{h}^{1}$, with $P_{h}^{1}$ consisting of piecewise-linear (hat) functions, 
-\mrev{and $E^{\nu}_{x},\;E^{\nu,h}_{x}$ being correspondingly the exact and the numerical solution, }
-we look for a ratio $h(\nu)$ that would ensure the bound on the absolute error 
+\mrev{and $E^{\nu}_{x},\;E^{\nu,h}_{x}$ being respectively the exact and the numerical solution, }
+we look for the ratio $h(\nu)$ that would ensure the bound on the absolute error 
 \begin{align}
@@
  \item The C\'ea's lemma applied to the problem (\ref{vf1dcase}); here \mrev{$\mathbf{E}^{\nu}$ is the exact solution, 
- $\mathbf{E}^{\nu,h}$ is the computed solution}, and $C_c$ is the continuity and $C_i$ is the coercivity constants:
+ $\mathbf{E}^{\nu,h}$ is the computed solution}, and $C_c$ and $C_i$ are respectively the continuity and the coercivity constants:
 \begin{align}
@@
 \begin{split}
- \|\mathbf{E}^{\nu}-\mathbf{E}^{\nu,h}\|_{\mathbf{V}}\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in \mathbf{V}_h}\|\mathbf{E}^{\nu}-\mathbf{v}\|_{V}
+ \|\mathbf{E}^{\nu}-\mathbf{E}^{\nu,h}\|_{\mathbf{V}}\leq \frac{C_c}{C_i}\min_{\mathbf{v}\in \mathbf{V}_h}\|\mathbf{E}^{\nu}-\mathbf{v}\|_{\mathbf{V}}
  \leq C\nu^{-1}\min_{\mathbf{v}\in \mathbf{V}_h}\|\mathbf{E}^{\nu}-\mathbf{v}\|_{\mathbf{V}},\; C>0.
@@
 \end{align}
-The last inequality follows from Lemma \ref{lemma:well_posedness} and is valid for $\nu\rightarrow 0$.   
-\item The form of the exact solution to the problem (\ref{vf1dcase}), see \cite{Despres_2014},
+The last inequality follows from Lemma \ref{lemma:well_posedness} and is still valid for $\nu\rightarrow 0$.   
+\item The form of the exact solution to the problem (\ref{vf1dcase}), see \cite{Despres_2014} and \cite[Proposition 1]{singular_solutions}
 \begin{align}
 \label{eq:exact}
- E_x^{\nu}(x)=iE_{y}^{\nu}(x)\frac{\delta(x)}{\alpha(x)+i\nu}=\frac{f^{\nu}(x)}{\alpha(x)+i\nu}, \; \text{for some }f^{\nu}(x)\in L^2(\Omega).
+ E_x^{\nu}(x)=f_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+\frac{g_{\nu}(x)}{\rho(x-X_{\nu})}+S_{1}^{\nu}(x),
 \end{align}
-\item \mrev{An explicit bound on $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ based on the results of \cite{singular_solutions}. First of all, we
-will assume that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the behaviour in the vicinity of the point of the resonance, where 
+where $\rho_{\nu}$ is a smooth function s.t. $\rho_{\nu}(0)=0,$ with the derivative $\rho_{\nu}'(0)=1$, 
+the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R}_{*}$; $f_{\nu},\; g_{\nu}, \; S_{1}^{\nu}(x)$ are smooth functions, 
+which, together with their derivatives, are bounded independently of $\nu$. 
+\item \mrev{An explicit bound on $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ is available,  
+based on the results of \cite{singular_solutions}. First of all, we
+will assume that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the behaviour in the vicinity of the resonance, where 
 the following expansion is valid \cite[Proposition 1]{singular_solutions}
 \begin{align*}
-E_{y}^{\nu}(x)=\tilde{E}_{y}^{\nu}(x)+S_{\nu}(x), \\
-\tilde{E}_{y}^{\nu}(x)=(\alpha(x)+i\nu)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})=(-x+i\nu)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu}),
+E_{y}^{\nu}(x)=\tilde{E}_{y}^{\nu}(x)+S^{\nu}_2(x), \\
+\tilde{E}_{y}^{\nu}(x)=(\alpha(x)+i\nu)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu}),%=(-x+i\nu)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu}),
 \end{align*}
-where $\rho_{\nu}$ is a smooth function s.t. $\rho_{\nu}(0)=0,\; \rho_{\nu}'(0)\neq 0$, the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R}$, 
-and $p_{\nu}(x),\; S_{\nu}(x)$ are smooth functions, which, together with their derivatives, are bounded independently of $\nu$.}
+where $\rho_{\nu},X_{\nu}$ are is in (\ref{eq:exact}), 
+and $p_{\nu}(x),\; S_{2}^{\nu}(x)$ are smooth functions, which, together with their derivatives, are bounded independently of $\nu$.}
 \item The estimate from \cite[Chapter 0]{brenner} on the rate of convergence of the interpolation 
@@
 \end{align}
-where $I^{h}v$ is an interpolation operator onto $P_{h}^{1}$. 
+where $I^{h}$ is an interpolation operator onto $P_{h}^{1}$. 
 \end{itemize}
-The estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C>0$,
+Estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C>0$,
 \begin{align}
@@
 First of all let us examine the behaviour the derivatives of $E_{y}^{\nu}$ in the vicinity of the resonance, 
-in particular, the term $\tilde{E}_{y}^{\nu}$ which is singular for $\nu=0$ in the resonant point:
+in particular, the term $\tilde{E}_{y}^{\nu}$ which is singular for $\nu=0$ in the resonance:
 \begin{align}
 \label{eq:eynuprime}
- \left(\tilde{E}_{y}^{\nu}\right)'&=\frac{(-x+i\nu)\rho_{\nu}'(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}p_{\nu}(x)-p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+p'_{\nu}(x)(-x+i\nu)\log\rho_{\nu}(x-X_{\nu}).
+ \left(\tilde{E}_{y}^{\nu}\right)'&= \alpha'(x)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+(\alpha(x)+i\nu)p'_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})
+ +\frac{(\alpha(x)+i\nu)p_{\nu}(x)\rho_{\nu}'(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}.
 \end{align}
-The first term in the above expression is well-defined in $x=0$, even for $\nu=0$ (the limit can be obtained with the help of the L'Hôpital's rule 
-and recalling that $\rho_{\nu}=O(x-X_{\nu})$ in the vicinity of the resonance), and is uniformly bounded in $\nu$, together with its derivatives. 
-The same holds for the third term. To examine the behaviour of $\left(\tilde{E}_{y}^{\nu}\right)''$, 
-we study solely the singular second term of (\ref{eq:eynuprime})
+The last term in this expression is well-defined in $x=0$, even for $\nu=0$ (the limit can be obtained with the help of the L'Hôpital's rule 
+and recalling that $\rho_{\nu}(x-X_{\nu})=x-X_{\nu}+O((x-X_{\nu})^2)$ in the vicinity of the resonance), and is uniformly bounded for sufficiently small $\nu$, together with its derivatives. 
+The same holds for the second term. To examine the behaviour of $\left(\tilde{E}_{y}^{\nu}\right)''$, 
+we study solely the singular first term of (\ref{eq:eynuprime})
 \begin{align*}
- \left(p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})\right)'=\frac{p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}+p_{\nu}'(x)\log\rho_{\nu}(x-X_{\nu}).
+ \left(\alpha'(x)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})\right)'=\frac{\alpha'(x)p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}+(\alpha'(x)p_{\nu}(x))'\log\rho_{\nu}(x-X_{\nu}).
 \end{align*}
-The term $\frac{p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}$ can be bounded, for all sufficiently small $|x|$, by 
+The term $\frac{\alpha'(x)p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}$ can be bounded, for all sufficiently small $|x|$, by 
 \begin{align*}
@@
 \end{align*}
-where we used an explicit form of $\rho_{\nu}=O(x-X_{\nu})$ valid for small $\nu$ and $|x|$, as well as 
-the expansion $X_{\nu}=ic\nu+O(\nu^2)$.  For sufficiently small $\nu$, the term $p_{\nu}'(x)\log\rho_{\nu}(x-X_{\nu})$ can be bounded by the above expression.
+where we used an explicit form of $\rho_{\nu}(x-X_{\nu})=x-X_{\nu}+O((x-X_{\nu})^2)$ valid for small $\nu$ and $|x|$, as well as 
+the expansion $X_{\nu}=ic\nu+O(\nu^2)$.  For sufficiently small $\nu$, the term $(\alpha'(x)p_{\nu}(x))'\log\rho_{\nu}(x-X_{\nu})$ 
+can be bounded by the above expression as well.
 
@@
 \begin{align*}
- \|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}\leq G+G'\left(\int\limits_{-L}^{H}\frac{1}{|x+i\nu c|^2}dx\right)^{\frac{1}{2}}
+ \|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}\leq G+G'\left(\int\limits_{-L}^{H}\frac{1}{|x-i\nu c|^2}dx\right)^{\frac{1}{2}}
  %\leq G+G'\left(\frac{1}{\nu c}\int\limits_{-\infty}^{\infty}\frac{dv}{v^2+1}\right)^{\frac{1}{2}}\\
@@
 }
-Let us now derive a similar bound on the second derivative of $E_{x}^{\nu}$:
-\ben
- \frac{d^2}{dx^2}E_x^{\nu}=\frac{(f^{\nu})''}{\alpha+i\nu}-2\frac{(f^{\nu})'\alpha'}{(\alpha+i\nu)^2}+\frac{f^{\nu}\alpha''}{(\alpha+i\nu)^3},
-\een
-from which, together with (\ref{eq:cond}, \ref{eq:eynuprime}, \ref{eq:exact}), it follows that there exists $c>0$ s.t. for all sufficiently small $\nu$ 
+To derive a similar bound on the second derivative of $E_{x}^{\nu}$, we notice that it can be represented in the following form, 
+for some functions $F_{\nu,k}(x),\; k=0,..,3,$ uniformly bounded in $x,\; \nu$ in the vicinity of $(0,0)$:
+\begin{align}
+\label{eq:ex_eq1}
+ \frac{d^2E_x^{\nu}}{dx^2}=\sum\limits_{k=1}^{3}\frac{F_{\nu,k}(x)}{\rho_{\nu}^{k}(x-X_{\nu})}+F_{\nu,0}(x)\log\rho_{\nu}(x-X_{\nu}).
+\end{align}
+Assuming again that the main contribution to $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the vicinity of the resonance, 
+we deduce that there exists $c>0$, s.t. for all sufficiently small $\nu$ 
 \bealn
- \left|\frac{d^2E_x^{\nu}}{dx^2}\right|_{L^2}^{2}&\leq c\int\limits_{\Omega}\frac{1}{(x^2+\nu^2)^{3}}dx
+ \left|\frac{d^2E_x^{\nu}}{dx^2}\right|_{L^2}^{2}&\leq c\int\limits_{-L}^{H}\frac{1}{(x^2+\nu^2)^{3}}dx
  % &=c\left.
@@
 \eealn
-where $C>0$ does not depend on $\nu$. After inserting this into (\ref{eq:final_est}) we obtain
+where $C>0$ does not depend on $\nu$. Plugging this into (\ref{eq:final_est}) we obtain
 \ben
@@
 Let us check numerically whether this holds true. 
-To do so, we conduct the  numerical experiment with parameters for the problem (\ref{eq:main_frequency_domain} as given in Table \ref{tab:parameters}. \mrev{Recall as well that we choose $\theta=0$. }
+To do so, we conduct the  numerical experiment with parameters for Problem 
+(\ref{eq:main_frequency_domain}) as given in Table \ref{tab:parameters}. \mrev{Recall as well that $\theta=0$. }
 \begin{table}[htb!]
@@
 \end{table}
-Denoting by \mrev{$E_{x}^{\nu,h}$ the solution $E_{x}(x)$} computed on the mesh with the \mrev{width $h$ with 
-the absorption $\nu$, and by $E_{x}^{\nu}$} the solution computed on a mesh multiple times finer (\arev{more precisely, the reference mesh
-was typically 10-20 times finer, with the exception when the computation was done for very small values of $h$ where for comparison twice finer meshes were used}), let 
+Denoting by \mrev{$E_{x}^{\nu,h}$ the solution $E_{x}(x)$} computed on the mesh with \mrev{width $h$ and 
+ absorption $\nu$, and by $E_{x}^{\nu}$} the solution computed on a mesh multiple times finer (\arev{more precisely, the reference mesh
+was typically 10-200 times finer, except when the computation was performed for very small values of $h$ when results were compared with results computed on twice finer meshes}), let 
 \begin{align}
@@
 \end{figure}
-We can see that the estimate (\ref{eq:estimate_h}) is pessimistic compared to the one suggested by (\ref{eq:def_epsilon}), 
+We can see that Estimate (\ref{eq:estimate_h}) is pessimistic compared to the one suggested by (\ref{eq:def_epsilon}), 
 at least for given values of $\epsilon$ and for a chosen range of $\nu>0$.
@@
 
-In Figure \ref{fig:small_nu} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
+In Figure \ref{fig:small_nu} we demonstrate the dependence of the condition number of the matrix of System (\ref{eq:simple_system}) 
 on $\nu$, for several values of $h$.
@@
 
-We show the results of very basic simulations that the numerical strategy 
+With very basic simulation, we show that the numerical strategy 
 based on co-localised semi-lagrangian discretization is valid even for the resonant 
 case.
-The numerical tests have been kept to a minimum since \arev{many more} are needed to fully validate
+The numerical tests have been kept to a minimum since \arev{much more} is needed to fully validate
 the concept.
@@
 The total energy $\mathcal E(t)$ is the physical energy. 
-The comparison with figures \ref{fig:dependence} and \ref{fig:resonance_nus_ey_x} show that the 
+The comparison with figures \ref{fig:dependence} and \ref{fig:resonance_nus_ey_x} shows that the 
 singular nature of the \arev{resonance} is captured by this new scheme without any doubt.
@@
 		\end{tabular}   \end{center}
-		\caption{An antenna sends a time harmonic wave on the left. The medium is propagative
+		\caption{An antenna sends a time-harmonic wave on the left. The medium is propagative
 			on the left and non propagative

### 2015-06-08 report_clean_merged/resume.tex
added report merged with the files of Lise-Marie and Bruno

La r\'esonnance hybride est un ph\'enom\`ene physique qui apparait par exemple lorsque l'on chauffe un plasma.
Il est en particulier d'int\'er\^et scientifique dans le cadre du d\'eveloppement  du projet ITER. Dans ce papier, nous nous concentrons sur des solutions faiblement r\'eguli\`eres des \'equations de Maxwell pour les plasmas magn\'etiques. Notre but est ici double. D'un c\^ot\'e nous 
approchons num\'eriquement la formulation fr\'equentielle \`a l'aide d'\'el\'ements finis,
 et de l'autre nous \'etudions les solutions r\'esonnantes dans le domaine temporel, \`a l'aide de deux m\'ethodes distinctes de diff\'erences finies. Nous comparons enfin num\'eriquement les solutions fr\'equentielles avec le comportement en temps long des solutions temporelles, dans le cadre
des principes d'amplitude et d'absorption limite.

### 2015-06-08 report_clean_merged/timedomain.tex
added report merged with the files of Lise-Marie and Bruno

--- 2015-05-03 report_clean/timedomain.tex
@@
-\section{Time Dependent Problem Discretization}
+\section{Time-Dependent Problem Discretization}
 \arev{
-In this section we develop the discretization of the time-dependent one-dimensional model (\ref{eq:main_model}), for a particular case $\theta=0$. 
-In the first part of this section we show how this system can be discretized with the help of 
-a version of the Yee scheme suggested in \cite{stable_yee_plasma_current}, and in the second part a scheme based on semi-lagrangian discretization is employed.}
+We develop hereafter the discretization of the time-dependent one-dimensional model (\ref{eq:main_model}), for the particular case $\theta=0$. 
+We first show how this system can be discretized thanks to a Yee scheme suggested in \cite{stable_yee_plasma_current}, then a scheme based on semi-lagrangian discretization is employed.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{A staggered scheme}
 \label{sec:staggered_discretization}
-In this section, we develop a discretization of the time-dependent problem~\eqref{eq:main_model} 
-in one dimension. %In 1D, the derivatives with respect to $y$ vanish, and we are left with the following problem, 
+%In this section, we develop a discretization of the time-dependent problem~\eqref{eq:main_model} in one dimension.
+%In 1D, the derivatives with respect to $y$ vanish, and we are left with the following problem,
 % \begin{align}
@@
 We compute a numerical approximation of~\eqref{eq:main_model} \mrev{with $\theta=0$} on a cartesian grid using the Yee scheme, 
-as suggested in \cite{stable_yee_plasma_current}. Let $n$ denote the time step index, as usual $t_n = n \Delta t$. 
+as suggested in \cite{stable_yee_plasma_current}. Let $n$ and $\Delta t$ denote the time step index and the time step, as usual the discrete time is $t_n = n \Delta t$. 
 It is standard (see \cite{Xu_2006,stable_yee_plasma_current }) to discretize the electrical field on the integer time steps, 
@@
  \left\{\begin{array}{l}
- \epsilon_0\frac{ E_{x}^{n+1}-E_x^{n}}{\Delta t}=-eN_e u_x, \nonumber\\
- \epsilon_0\frac{ E_{y}^{n+1}-E_y^{n}}{\Delta t}+\partial_x H_z=-eN_e u_y,\nonumber\\
- \mu_0\frac{ H_z^{n+1/2}-H_z^{n-1/2}}{\Delta t}+\partial_x E_y-\partial_y E_x=0, \label{eq:tdiscretizedpb}\\
- m_e\frac{ u_{x}^{n+1}-u_x^{n}}{\Delta t}=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
- m_e\frac{u_{y}^{n+1}-u_y^{n}}{\Delta t}=eE_y-eu_xB_0-\nu m_e u_y.\nonumber
+ \epsilon_0\frac{ E_{x}^{n+1}-E_x^{n}}{\Delta t}=-eN_e \frac{u_x^{n}+u_x^{n+1}}{2}, \nonumber\\
+ \epsilon_0\frac{ E_{y}^{n+1}-E_y^{n}}{\Delta t}+\partial_x H_z^{n+1/2}=-eN_e \frac{u_y^{n}+u_{y}^{n+1}}{2},\nonumber\\
+ \mu_0\frac{ H_z^{n+1/2}-H_z^{n-1/2}}{\Delta t}+\partial_x E_y^{n}-\partial_y E_x^{n}=0, \label{eq:tdiscretizedpb}\\
+ m_e\frac{ u_{x}^{n+1}-u_x^{n}}{\Delta t}=e\frac{E_x^{n+1}+E_x^{n}}{2}+e\frac{u_y^{n+1}+u_{y}^{n}}{2}B_0-\nu m_e \frac{u_x^{n+1}+u_x^{n}}{2},\nonumber\\
+ m_e\frac{u_{y}^{n+1}-u_y^{n}}{\Delta t}=e\frac{E_y^{n+1}+E_y^{n}}{2}-e\frac{u_x^{n+1}+u_x^{n}}{2}B_0-\nu m_e \frac{u_y^{n+1}+u_y^{n}}{2}.\nonumber
 \end{array}\right.
  \eealn
-In Yee scheme, the differents components of the vector fields 
+In Yee scheme, the different components of the vector fields 
 are defined on staggered points. 
@@
 of \urev{$E_x$}, $u_x$ (black dots), $E_y$, $u_y$ (blue dots) and $H_z$ (red dots) 
-on the discretized grid in space and time are shown. The fully discretized system then reads
+on the discretized grid in space and time are displayed. The fully discretized system then reads
 
@@
 
-It is possible to rewrite this system in an explicit form (we omit here these simple but slightly tedious computations).
+It is straightforward to rewrite this system in an explicit form (we omit here these simple but slightly tedious computations).
 %It is now possible to describe explicitly how to solve the proviso discrete system.
@@
 
-The scheme that is described hereafter is mentioned since it is based on some well-known 
-numerical methods in plasma physics, the so-called semi-lagrangian schemes 
-which are widely used for the numerical approximation of transport equations.
+The scheme described hereafter is mentioned since it is based on some well-known 
+numerical methods in plasma physics, the so-called semi-lagrangian schemes widely used for the numerical approximation of transport equations.
 It seems to be an original use of semi-lagrangian schemes 
-and is mentioned since it can be an option. 
+and is mentioned as possible other option. 
 We restrict the presentation to the minimum and leave the details  of the construction to the alert reader.
@@
 The idea is to split 
-the system (\ref{eq:main_model})
+System (\ref{eq:main_model})
 into a series of  transport equations (here just 2) and a local in-the-cell system.
@@
 In the tests, we used Strang's stencils described in \cite{cedar} with CFL $\nu=0.5$, at order 7. 
-It  yields the chain 
+It  yields to the chain 
 $(E_y,H_z)_i^n\mapsto ( w,z)_i^n\mapsto ( w,z)_i^{n*}\mapsto (E_y,H_z)_i^{n*} $.
-Here $n*$ denotes the intermediate stage of the algorithm.
+Here $n*$ denotes the intermediate time step of the algorithm.
 
@@
 We make sure that the method is conservative in total energy if $\nu=0$, using a half-step discretization
-of the right hand sides.
+of the right-hand sides.
 
 - Therefore  all quantities are now given $(E_x,E_y, H_z, u_x,u_y)_{i}^{n+1}$ in the cells 
-at time step $t_{n+1}=(n+1)\Delta t$, and it is enough to loop in time.
+at time step $t_{n+1}=(n+1)\Delta t$, and that defines totally a time step of the algorithm.
 
@@
 	The structure of this algorithm is very similar to the one developed in \cite{compfluids} and can be adapted and studied numerically
-	in any dimension on a Cartesian grid and for more complex right hand sides.
+	in any dimension on a Cartesian grid and for more complex right-hand sides.
 \end{remark}

### 2015-06-10 report_clean_final/TEX/responce_reviewers.tex
addede bruno's modifications

--- 2015-05-04 report_clean/responce_reviewers.tex
@@
 
-We marked corrections suggested by the reviewer 1 in blue, by the reviewer 2 in red, 
-and some extra corrections made by us that can be important in green.
-
+We deeply thank the referees for their remarks. We tried at best to answer and to modify the text accordingly.
+Additional corrections have been made.
+%We marked corrections suggested by the reviewer 1 in blue, by the reviewer 2 in red, 
+%and some extra corrections made by us that can be important in green.
  More important corrections include
@@
 
+Please find below the detail of the modifications/answers.
+
 \section{Response to the reviewer 1}
 
-All the corrections are marked in blue.
+%All the corrections are marked in blue.
 
@@
 and changed the wording in the introduction to underline that the 1D case is the one of interest. 
+We also explain that the mathematics of hybrid resonance is understood essentially
+in 1D, so the reason to concentrate to 1D model. In multiD we know almost nothing concerning the functional spaces
+that would allow for the   study of the hybrid resonance with a limit process $\nu\rightarrow 0^+$.
 
@@
 
-\item {\textcolor{red}{p12}}
+\item p.12: 
+The $h$ was an error.
+The $^\nu$ is now for all variables.
+Note all fields are real functions, this is a time domain simulation.
+$T$ is a time sufficiently large to that a periodic solution seems 
+to be captured by the scheme.
 
@@
 The singularity appears for $\nu=0$, provided that the diagonal part of the dielectric tensor vanishes and the non-diagonal part does not. 
+See definition 1.1.
 
@@
 
-\item p10: mesh multiple times finer. It should be said exactly how many times.
+\item p10:
 
@@
 
-\item {\textcolor{red}{p.12: fixed the typos.}}
+\item p. 12: 
+Typos fixed.
+Additional references on semi-lagrangian schemes have been included.
+
 \end{itemize}

### 2015-06-10 report_clean_final/TEX/FD.tex
addede bruno's modifications

--- 2015-06-08 report_clean_merged/FD.tex
@@
 the regularized problem (\ref{eq:seq_regularized}). 
-
 Model (\ref{eq:main_model}) can be rewritten in the frequency domain as 
@@
 The choice of the non-zero plasma friction $\nu>0$ is a regularization of the problem. }
-
 \mrev{
@@
 with the variable coefficient $k^2=(\alpha-\frac{\delta^2}{\alpha})$ \mrev{coupled to boundary conditions (\ref{eq:boundary_conditions_frequency_domain})}, and the second equation being  
-\begin{align*}
-  \left(E_x,u\right)=\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega).
-\end{align*}
+$
+  \left(E_x,u\right)=\left(\frac{i\delta}{\alpha}E_y,u\right)$  for all  $u\in L^{2}(\Omega)$.
 The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 

### 2015-06-10 report_clean_final/TEX/absorption.tex
addede bruno's modifications

--- 2015-06-08 report_clean_merged/absorption.tex
@@
 on the domain as $(-0.5, 10)$ and set the electron density $N_e(x)=1+x>0,\; x\in \Omega$. 
-\urev{Importantly, since $\delta(x)=0$, in this case no resonance occurs and $E(x,t)\equiv 0$. This corresponds to the case when the
-tensor of dielectric permittivity $\uuline{\varepsilon^{\nu}_{\omega}}$ is 
+\urev{Importantly, since $\delta(x)=0$, in this case no resonance occurs and $E_{x}(x,t)\equiv 0$. This corresponds to the case when the
+tensor of dielectric permittivity $\uuline{\varepsilon^{0}_{\omega}}$ is 
 diagonal.}
@@
 For a chosen value of $\nu$ the solutions computed in the time domain are in close agreement 
-to the solutions computed in the frequency domain. This seem to be only partially 
+to the solutions computed in the frequency domain. This seems to be only partially 
 true for the computed values $E_x^{\nu}(x,t)$ in this case (which may be caused by the discretization). 
@@
 
-\FloatBarrier
+%\FloatBarrier

### 2015-06-10 report_clean_final/TEX/abstract.tex
addede bruno's modifications

--- 2015-06-08 report_clean_merged/abstract.tex
@@
 \mrev{magnetized plasmas}. 
-Our main purpose is two-fold. First, we aim at investigating the finite element approximation 
+Our main purpose is three-fold. First, we aim at investigating the finite element approximation 
 of the frequency-domain problem. Second, we would like to study the resonant solutions 
 in the time domain, with the help of two different finite difference approximations. 
-We then compare the results with the ones obtained in the frequency domain, by  
+We finally  compare the results with the ones obtained in the frequency domain, by  
 numerical examination of the limiting absorption and limited amplitude principles.

### 2015-06-10 report_clean_final/TEX/figure_generator/pics_frequency_domain/figure_cond_number.tex
addede bruno's modifications

--- 2015-02-04 report_clean/figure_generator/pics_frequency_domain/res_sol.tex
@@
 \begin{document}
-
+\pagenumbering{gobble}
 \begin{figure}
-\pagenumbering{gobble}
 \begin{tikzpicture}
-    \begin{axis}[
+    \begin{loglogaxis}[
     	width=\textwidth,
     	height=\textwidth,
-    	xmin=-15,
-    	xmax=10,
-        xlabel=$x$,
-        ylabel=$E_{x,y}$,
+        xlabel=$\nu$,
+        ylabel={Condition number},
+        ymin=1,
         legend style={
 at={(0.2,1.5)},
-legend pos= south east,
-anchor=south east, 
+legend pos=north  east,
+%anchor=north east, 
 draw=none, 
-font=\small
+%font=\tiny
 }
 ]
-\addplot[blue] table {pics_resonance/ime1.0.1.dat}; 
-\addlegendentry{$\Im{E_x^{\nu}},\nu=10^{-1}$};
-\addplot[red] table {pics_resonance/ime1.0.01.dat}; 
-\addlegendentry{$\Im{E_x^{\nu}},\nu=10^{-2}$};
-\addplot[black] table {pics_resonance/ime1.0.001.dat}; 
-\addlegendentry{$\Im{E_x^{\nu}},\nu=10^{-3}$};
-\addplot[blue,dashed] table {pics_resonance/ree2.0.1.dat}; 
-\addlegendentry{$\Re{E_y^{\nu}},\nu=10^{-1}$};
-\addplot[red,dashed] table {pics_resonance/ree2.0.01.dat}; 
-\addlegendentry{$\Im{E_y^{\nu}},\nu=10^{-2}$};
-\addplot[black,dashed] table {pics_resonance/ree2.0.001.dat}; 
-\addlegendentry{$\Im{E_y^{\nu}},\nu=10^{-3}$};
- \end{axis}
+\addplot[blue, mark=*] table {cond_number_pic/g_h1.dat}; 
+\addlegendentry{$h=1$};
+\addplot[black, mark=triangle] table {cond_number_pic/g_h0.5.dat}; 
+\addlegendentry{$h=0.5$};
+\addplot[red, mark=square] table {cond_number_pic/g_h0.1.dat}; 
+\addlegendentry{$h=0.1$};
+\addplot[black, mark=*] table {cond_number_pic/g_h0.01.dat}; 
+\addlegendentry{$h=0.01$};
+\addplot[blue,dashed] table {cond_number_pic/1nu.dat};
+\addlegendentry{$O(\nu^{-1})$};
+ \end{loglogaxis}
 \end{tikzpicture}

### 2015-06-10 report_clean_final/TEX/figure_generator/pics_time_domain/airy/figure_nu1e2.tex
addede bruno's modifications

--- 2015-02-04 report_clean/figure_generator/pics_time_domain/airy/figure_nu1e2.tex
@@
   ymax=0.5,
-  xmin=2.97e4,
-  xtick={2.97e4,2.98e4,2.99e4,3e4},
+ % xmin=2.97e4,
+ % xtick={2.97e4,2.98e4,2.99e4,3e4},
   x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
@@
   \addplot[color=red, mark=*, dashed, mark size=0.6] file{airy/sol_1e2_dt0.05_freqdomain.dat};
-  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}\right),\; x_c=0.45, \; \nu=10^{-2}$};
+  \addlegendentry{$\Im\left(\hat{E}_y^{\nu}(x_c)\mathrm{e}^{-it}\right),\; x_c=0.45, \; \nu=10^{-2}$};
   \end{axis}

### 2015-06-10 report_clean_final/TEX/figure_generator/pics_time_domain/airy/figure_nu1e6.tex
addede bruno's modifications

--- 2015-02-04 report_clean/figure_generator/pics_time_domain/airy/figure_nu1e6.tex
@@
   ymax=0.6,
-  xtick={1.9198e6, 1.91999e6},
-  x tick label style={/pgf/number format/fixed, /pgf/number format/precision=4},
+  xmin=1.91981e6,
+  xtick={1.91981e6, 1.91999e6},
+  %extra x ticks={1.91981e6},
+  x tick label style={/pgf/number format/fixed, /pgf/number format/fixed zerofill, /pgf/number format/precision=6},
   ylabel={$E_y^{\nu}(x_c,t)$},

### 2015-06-10 report_clean_final/TEX/intro.tex
addede bruno's modifications

--- 2015-06-08 report_clean_merged/intro.tex
@@
 \section{Introduction}
-Modelling various phenomena in plasmas is of practical importance for developing new sources of energy 
+Modeling various phenomena in plasmas is of practical importance for developing new sources of energy 
 based on plasma fusion, see the ITER project\footnote{www.iter.org}. 
@@
 the solutions of Maxwell equations in \mrev{magnetized plasmas} \cite{Despres_2014}. 
+Physically the hybrid resonance corresponds to situations where the electric field becomes
+infinite due to some resonance coupling between the background magnetic field and
+the polarization of the wave.
 The energy deposit is resonant and may exceed by far the energy 
@@
 Contrary to the Landau damping, however, 
-hybrid resonance appears in a simpler model coupling 
-fluid equations with the non electrostatic part of Maxwell equations.
+hybrid resonance appears in a simpler one-dimensional  model coupling 
+fluid equations with the non-electrostatic part of Maxwell equations.
+Since  the mathematics of hybrid resonance is far to be understood
+in dimension greater or equal to two, we restrict this work to dimension one.
+% any open problems exist which prevent for having
+%a mathematically sound multidimensional theory  of hybrid resonance.
+% is an open problem.
 
 \urev{
-We consider the time-dependent wave propagation problem leading to the cold plasma model for a single species 
+To illustrate the hybrid resonance, we consider in this work a %one dimensional 
+ time-dependent wave propagation problem leading to the cold plasma model for a single species 
 under a uniform in time background magnetic field $\mathbf{B}_0=(0,\;0,\; B_0)$. 
@@
 The unknowns are the electron velocity $\ubf$ and the electromagnetic fields. 
-
 The energy of this system in a domain $\Omega\in\mathbb R^2$ can be expressed as, see \cite{Despres_2014},
@@
 \een
-
 To illustrate unexpected difficulties that can occur in this system, consider the frequency domain counterpart of (\ref{eq:main_system}-\ref{eq:electronmove}), which corresponds to the cold plasma model.
-To do so,
-we introduce the plasma frequency $\omega_p(\mathbf{r})=\sqrt{\frac{|e|^2N_e(\mathbf{r})}{m\epsilon_0}}$, 
+We introduce the plasma frequency $\omega_p(\mathbf{r})=\sqrt{\frac{|e|^2N_e(\mathbf{r})}{m\epsilon_0}}$, 
 the cyclotron frequency $\omega_c(\mathbf{r})=\frac{e B_0(\mathbf{r})}{m_e}$ and perform the Fourier transform 
@@
 \end{align}
-
 The point $\mathbf{r}_0$ s.t.
@@
 
-Another interesting case is $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$ and $\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})\neq 0$, i.e. when the diagonal part of the tensor 
-$\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})$ vanishes and the non-diagonal part remains non-zero. This is a hybrid resonance case. 
+ The hybrid resonance is precisely defined 
+ where  $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$ and $\omega_c(\mathbf{r})\omega_p(\mathbf{r})\neq 0$, i.e. when the diagonal part of the tensor 
+$\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})$ vanishes and the non-diagonal part remains non-zero.
 As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component $E_x$ is not necessarily square 
@@
 \label{eq:boundary_conditions_intro}
-curl \hat{\mathbf{E}} \mrev{+}i \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} =curl \E_{inc} \mrev{+}\imath\lambda\E_{inc}\wedge \n,
+%curl
+ {\operatorname{curl}} \
+  \hat{\mathbf{E}} \mrev{+}i \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} \equiv
+   {\operatorname{curl}} \ \E_{inc} \mrev{+} i  \lambda\E_{inc}\wedge \n,
 \ee
-where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and \mrev{$\lambda\geq 0$} is 
+where $\E_{inc} = \exp \left(i  \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and \mrev{$\lambda\geq 0$} is 
 the frequency of the antenna. At the right boundary we impose $\operatorname{curl} \hat{\E} = 0$.
@@
 \end{equation}
- posed in the one dimension domain $(-L,\; H)$, with \mrev{the corresponding boundary conditions:
+ posed in the one-dimensional domain $(-L,\; H)$, with \mrev{the corresponding boundary conditions:
  \begin{align}
@@
 We concentrate on a physical situation of the hybrid resonance, which we define as in \cite{singular_solutions}.
-\begin{df}
+
+\begin{df}[of a hybrid resonance]
 Let $\omega\in\mathbb{R}$ be fixed. 
@@
 and $\delta_{\omega}(x_h)\neq 0$.
+The parameter $\nu$ is at the same the physical friction and a regularization parameter.  The hybrid resonance singular solution 
+shows up at $x_h$ at the limit $\nu\rightarrow 0^+$.
 \end{df}
@@
 The commutation between the two principles then writes as}
-$$
-\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}= \lim\limits_{t\rightarrow+\infty}\lim\limits_{\nu\rightarrow 0},
-$$
+$
+\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}= \lim\limits_{t\rightarrow+\infty}\lim\limits_{\nu\rightarrow 0}$,
 see Figure \ref{fig:limits}. 

### 2015-06-10 report_clean_final/TEX/numerics.tex
addede bruno's modifications

--- 2015-06-08 report_clean_merged/numerics.tex
@@
 to obtain a 7-diagonal Hermitian matrix and solve the system with the Gauss back substitution algorithm. 
-
 The intermediate part briefly validates the semi-lagrangian discretization of the time domain formulation.
-
 The last part of the section deals with the question of the equivalence of the limiting absorption and limited amplitude 
@@
 \end{figure}
+
 \subsubsection{Solution of the Frequency-Domain Problem with Resonance}
@@
 \end{align}
-given a fixed value of $\epsilon>0$ and $\nu\rightarrow 0$. W.l.o.g. here we assume that $\nu>0$.
+given a fixed value of $\epsilon>0$ and $\nu\rightarrow 0$. Without loss of generality here we assume that $\nu>0$.
 
@@
 The last inequality follows from Lemma \ref{lemma:well_posedness} and is still valid for $\nu\rightarrow 0$.   
-\item The form of the exact solution to the problem (\ref{vf1dcase}), see \cite{Despres_2014} and \cite[Proposition 1]{singular_solutions}
+\item The estimate from \cite[Chapter 0]{brenner} on the rate of convergence of the interpolation 
 \begin{align}
+\label{eq:interp}
+\begin{split}
+ \|v-I^{h}v\|_{L^2}\leq C_1h^2\left\|v''\right\|_{L^2},\; C_1>0,\\
+ \|v-I^{h}v\|_{H^1}\leq C_2h\|v''\|_{L^2},\; C_2>0, 
+ \end{split}
+\end{align}
+where $I^{h}$ is an interpolation operator onto $P_{h}^{1}$. 
+\item \mrev{An explicit bound on $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$ based on \cite{Despres_2014} and \cite[Proposition 1]{singular_solutions}. 
+First of all, we 
+will assume that the main contribution to $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the behaviour in the vicinity of the resonance, where, 
+for sufficiently small $\nu$, the following expansion is valid \cite[Proposition 1]{singular_solutions}
+\begin{align}
+\begin{split}
 \label{eq:exact}
- E_x^{\nu}(x)=f_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+\frac{g_{\nu}(x)}{\rho(x-X_{\nu})}+S_{1}^{\nu}(x),
+ E_x^{\nu}(x)=\tilde{E}_x^{\nu}+S_{1}^{\nu}(x),\\
+ \tilde{E}_x^{\nu}=f_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+\frac{g_{\nu}(x)}{\rho(x-X_{\nu})},
+ \end{split}
 \end{align}
-where $\rho_{\nu}$ is a smooth function s.t. $\rho_{\nu}(0)=0,$ with the derivative $\rho_{\nu}'(0)=1$, 
-the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R}_{*}$; $f_{\nu},\; g_{\nu}, \; S_{1}^{\nu}(x)$ are smooth functions, 
-which, together with their derivatives, are bounded independently of $\nu$. 
-\item \mrev{An explicit bound on $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ is available,  
-based on the results of \cite{singular_solutions}. First of all, we
-will assume that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the behaviour in the vicinity of the resonance, where 
-the following expansion is valid \cite[Proposition 1]{singular_solutions}
+where $f_{\nu},\; g_{\nu}, \; S_{1}^{\nu}(x)$ are smooth functions, 
+which, together with their derivatives, are bounded independently of $\nu$ for all sufficiently small values of $\nu$; 
+$\rho_{\nu}$ is a smooth function s.t. $\rho_{\nu}(0)=0,$ with the derivative $\rho_{\nu}'(0)=1$, 
+the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R}_{*}$. 
+}
+\item \mrev{An explicit bound on $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ based on \cite{singular_solutions}. As before, we 
+will assume that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the behaviour in the vicinity of the resonance, where,
+for sufficiently small $\nu$, it holds \cite[Proposition 1]{singular_solutions}
 \begin{align*}
@@
 where $\rho_{\nu},X_{\nu}$ are is in (\ref{eq:exact}), 
-and $p_{\nu}(x),\; S_{2}^{\nu}(x)$ are smooth functions, which, together with their derivatives, are bounded independently of $\nu$.}
-\item The estimate from \cite[Chapter 0]{brenner} on the rate of convergence of the interpolation 
-\begin{align}
-\label{eq:interp}
-\begin{split}
- \|v-I^{h}v\|_{L^2}\leq Ch^2\left|v''\right|_{L^2},\; C>0,\\
- \|v-I^{h}v\|_{H^1}\leq Ch|v''|_{L^2},\; C>0, 
- \end{split}
-\end{align}
-where $I^{h}$ is an interpolation operator onto $P_{h}^{1}$. 
+and $p_{\nu}(x),\; S_{2}^{\nu}(x)$ are smooth functions, which, together with their derivatives, are bounded independently of $\nu$ 
+for all sufficiently small values of $\nu$.}
 \end{itemize}
@@
 First of all let us examine the behaviour the derivatives of $E_{y}^{\nu}$ in the vicinity of the resonance, 
-in particular, the term $\tilde{E}_{y}^{\nu}$ which is singular for $\nu=0$ in the resonance:
+in particular, the term $\tilde{E}_{y}^{\nu}$:
 \begin{align}
@@
 \begin{align*}
- \left|\frac{p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}\right|\leq \frac{C}{|x-i\nu c|},\; C>0,
+ \left|\frac{\alpha'(x)p_{\nu}(x)\rho'_{\nu}(x-X_{\nu})}{\rho_{\nu}(x-X_{\nu})}\right|\leq \frac{C}{|x-i\nu c|},\; C>0,
 \end{align*}
@@
 Therefore, assuming that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the vicinity of the resonance, 
-where for $\nu=0$ this function is singular, 
+where for $\nu=0$ $\left(E_{y}^{\nu}\right)''$ is singular,  
 we obtain the following rough bound
@@
 for sufficiently small $\nu>0$.
-}
-To derive a similar bound on the second derivative of $E_{x}^{\nu}$, we notice that it can be represented in the following form, 
-for some functions $F_{\nu,k}(x),\; k=0,..,3,$ uniformly bounded in $x,\; \nu$ in the vicinity of $(0,0)$:
+
+To derive a similar bound on the second derivative of $E_{x}^{\nu}$, we assume that the main contribution to $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$
+comes from the singular part of $\tilde{E}_{x}^{\nu}$, whose second derivative can be represented in the following form, 
+for some functions $F_{\nu,k}(x),\; k=0,..,3,$ uniformly bounded in $x,\; \nu$ in the vicinity of $(x,\nu)=(0,0)$:
 \begin{align}
 \label{eq:ex_eq1}
- \frac{d^2E_x^{\nu}}{dx^2}=\sum\limits_{k=1}^{3}\frac{F_{\nu,k}(x)}{\rho_{\nu}^{k}(x-X_{\nu})}+F_{\nu,0}(x)\log\rho_{\nu}(x-X_{\nu}).
+ \frac{d^2\tilde{E}_x^{\nu}}{dx^2}=\sum\limits_{k=1}^{3}\frac{F_{\nu,k}(x)}{\left(\rho_{\nu}(x-X_{\nu})\right)^{k}}+F_{\nu,0}(x)\log\rho_{\nu}(x-X_{\nu}).
 \end{align}
-Assuming again that the main contribution to $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the vicinity of the resonance, 
-we deduce that there exists $c>0$, s.t. for all sufficiently small $\nu$ 
+}
+Then there exists $c>0$, s.t. for all sufficiently small $\nu$ 
 \bealn
@@
 \eealn
- is ensured by choosing $h$ as $\beta_{\epsilon}\nu^{\frac{3}{4}}$, \mrev{$\beta_{\epsilon}>0$.}
+ is ensured by choosing $h$ as \mrev{$\beta_{\epsilon}\nu^{\frac{3}{2}}$}, \mrev{$\beta_{\epsilon}>0$.}
 \end{remark}
@@
 With very basic simulation, we show that the numerical strategy 
-based on co-localised semi-lagrangian discretization is valid even for the resonant 
-case.
-The numerical tests have been kept to a minimum since \arev{much more} is needed to fully validate
+based on co-localised semi-lagrangian discretization is valid even for the resonance.
+The numerical tests have been kept to a minimum, and \arev{many more} are needed to fully validate
 the concept.
-
-The setting of the numerical results of figure \ref{fig:vasl}
+The setting of the numerical results of Figure \ref{fig:vasl}
 is the following. We use a 7th order semi-lagrangian scheme, and the CFL is $\nu=0.5$.
@@
 The total energy $\mathcal E(t)$ is the physical energy. 
-The comparison with figures \ref{fig:dependence} and \ref{fig:resonance_nus_ey_x} shows that the 
+The comparison with Figures \ref{fig:dependence} and \ref{fig:resonance_nus_ey_x} shows that the 
 singular nature of the \arev{resonance} is captured by this new scheme without any doubt.
 
-\begin{figure}{h}
+\urev{Notice that in this case we shifted the computational domain is shifted
+for visualization purposes,
+so that $L=0$ and the point where the resonance occurs is $x_h=20$.}
+
+\begin{figure}[h]
 	\begin{center}
@@
 			\\
-			$E_y$ & $H_z$  & $E_x^\nu$ \\
+			$x\mapsto E_y^\nu(T,x)$ & $  x\mapsto H_z^\nu(T,x)$  & $x\mapsto E_x^\nu(T,x)$ \\
 			%\hline
-			\hline
+			%\hline
 			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/uy_moit.eps}
@@
 			\\      
-			$u_y$ & $t\mapsto \mathcal E(t)$ & $u_x^\nu$  \\
+			$x\mapsto u_y^\nu(T,x)$ & $t\mapsto \mathcal{E}^{\nu}(t)$ & $x\mapsto u_x^\nu(T,x)$  \\
 
@@
 		\caption{An antenna sends a time-harmonic wave on the left. The medium is propagative
-			on the left and non propagative
-			on the right. The resonance is visible on $E_x$ and $u_x$. The time of the simulation is $T=2000$. The number of cells
-			is typically 10000 to reach convergence.}
+			on the left and non-propagative
+			on the right. The resonance is visible on the real functions
+			$E_x^\nu$ and $u_x^\nu$. The time of the simulation $T=2000$ is chosen large enough so that the
+			periodic solution is captured, at least numerically. The number of cells
+			is typically 10000 to reach space  convergence. The shift for visualization purposes if $+20$, which explains
+			why the resonance is now at $x=20$.}
 		\label{fig:vasl}

### 2015-06-10 report_clean_final/TEX/proc.tex
addede bruno's modifications

--- 2015-05-03 report_clean/proc.tex
@@
 \usepackage[utf8]{inputenc}
-\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
+\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array, ulem}
 \usepackage{tikz}
@@
 \begin{document}
-\newcommand{\urev}[1]{{\color{bluer}#1}}
-\newcommand{\arev}[1]{{\color{red}#1}}
-\newcommand{\mrev}[1]{{\color{greem}#1}}
+%\newcommand{\urev}[1]{%{\color{bluer}#1}   
+\newcommand{\urev}[1]{#1}
+%\newcommand{\arev}[1]{{\color{red}#1}}
+\newcommand{\arev}[1]{#1}
+%\newcommand{\mrev}[1]{{\color{greem}#1}}
+\newcommand{\mrev}[1]{#1}
+%%color printing
+%\newcommand{\urev}[1]{{\color{black}#1}}
+%\newcommand{\arev}[1]{{\color{black}#1}}
+%\newcommand{\mrev}[1]{{\color{black}#1}}
 
@@
 \maketitle
-%\textcolor{red}{should we add Olivier Lafitte and Remi Sart anywhere in the proceeding ?}\\
 
@@
 \input{timedomain}
+
 \input{numerics}
+
 \input{absorption}
+
 \input{conclusions}
@@
 \begin{thebibliography}{99}
-	\bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
+
+\bibitem{abramowitz_stegun} Abramowitz, M. and Stegun, I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
 	Handbook of mathematical functions
 \bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
+
 \bibitem{cedar}
-Charles, F., Despr\'es, B., Mehrenberg, M., 
-Enhanced convergence estimates for semi-lagrangian schemes Application to the Vlasov-Poisson equation, SIAM J. Numer. Anal. 2013, 51(2), 840-863.
+Charles, F., Despr\'es, B., Mehrenberg, M.  (2013).  
+Enhanced convergence estimates for semi-lagrangian schemes Application to the Vlasov-Poisson equation, SIAM J. Numer. Anal., 51(2), 840-863.
 
@@
 \bibitem{compfluids}
-S. Del Pino, B. Despr\'es, P. Hav\'e, H. Jourdren, and P. F. Piserchia. 3D finite
+Del Pino, S., Despr\'es, B., Hav\'e, P., Jourdren, H., and Piserchia, P. F. (2009). 3D finite
 volume simulation of acoustic waves in the earth atmosphere.
 Comput. \&
-Fluids, 38(4):765-777, 2009.
+Fluids, 38(4):765-777.
 
@@
 
+\bibitem{feix} Feix, M. R., Bertrand, P., and Ghizzo, A.  (1994). Eulerian codes for the Vlasov equation.  Series on Advances
+in Mathematics for Applied Sciences 22, Kinetic Theory and Computing, pp. 45.
+
+\bibitem{fifi} 
+ Filbet, F., Sonnendrucker, E.  (2003). 
+ Comparison of Eulerian Vlasov solvers,
+Computer Physics Communications,
+150, pp. 247-266
+
 \bibitem{Freidberg_2007} Freidberg, J. P. (2007). Plasma physics and fusion energy. Cambridge University Press.
+
+\bibitem{guo}
+Guo, W. and Qiu, J. - M. (2013). 
+Hybrid semi-Lagrangian finite element-finite difference methods for the Vlasov
+equation,
+Journal of Computational Physics,
+234, pp. 108-132.
 
@@
 \bibitem{Morawetz} Morawetz, C. S. (1962). The limiting amplitude principle. Communications on Pure and Applied Mathematics, 15(3), 349-361.
-\bibitem{Eidus} Eidus. D.M. (1969). The principle of limit amplitude. Russian Mathematical Surveys, vol. 24, issue 3, 97-167.
+
+\bibitem{Eidus} Eidus, D.M. (1969). The principle of limit amplitude. Russian Mathematical Surveys, vol. 24, issue 3, 97-167.
+
+\bibitem{soso}
+Sonnendrucker, E., Roche, J., Bertrand, P., and A. Ghizzo (1998). 
+The Semi-Lagrangian Method for the
+Numerical Resolution of Vlasov Equations.
+J. Comput. Phys.,
+149, pp. 201-220.
 
@@
 
+\bibitem{umeda}
+Umeda, T., Nariyuki, Y. and Kariya, D. (2012).
+A non-oscillatory and conservative semi-Lagrangian scheme with
+fourth-degree polynomial interpolation for solving the Vlasov equation,
+Computer Physics Communications,183, pp. 1094-1100.
+
 \bibitem{singular_solutions}
-Despr\'es, B., Imbert-G\'erard, L.-M. and Lafitte, O. Singular solutions for the plasma at the resonance. 2014. $\langle$ hal-01097364$\rangle$
+Despr\'es, B., Imbert-G\'erard, L.-M. and Lafitte, O., 2014. Singular solutions for the plasma at the resonance. $\langle$ hal-01097364$\rangle$
 

### 2015-06-10 report_clean_final/TEX/resume.tex
addede bruno's modifications

--- 2015-06-08 report_clean_merged/resume.tex
@@
 Dans ce papier, nous nous concentrons sur des solutions faiblement r\'eguli\`eres des \'equations de Maxwell pour les plasmas magn\'etiques.
-Notre but est ici double.
+Notre but est ici triple.
 D'un c\^ot\'e nous
@@
  et de l'autre nous \'etudions les solutions r\'esonnantes dans le domaine temporel, \`a l'aide de deux m\'ethodes distinctes de diff\'erences finies.
-Nous comparons enfin num\'eriquement les solutions fr\'equentielles avec le comportement en temps long des solutions temporelles, dans le cadre
+Finalement nous comparons  num\'eriquement les solutions fr\'equentielles avec le comportement en temps long des solutions temporelles, dans le cadre
 des principes d'amplitude et d'absorption limite.

### 2015-06-10 report_clean_final/TEX/timedomain.tex
addede bruno's modifications

--- 2015-06-08 report_clean_merged/timedomain.tex
@@
  \left\{\begin{array}{l}
- \epsilon_0\frac{ E_{x}^{n+1}-E_x^{n}}{\Delta t}=-eN_e \frac{u_x^{n}+u_x^{n+1}}{2}, \nonumber\\
- \epsilon_0\frac{ E_{y}^{n+1}-E_y^{n}}{\Delta t}+\partial_x H_z^{n+1/2}=-eN_e \frac{u_y^{n}+u_{y}^{n+1}}{2},\nonumber\\
+ \epsilon_0\frac{ E_{x}^{n+1}-E_x^{n}}{\Delta t}=-eN_e \frac{u_x^{n+1}+u_x^{n}}{2}, \nonumber\\
+ \epsilon_0\frac{ E_{y}^{n+1}-E_y^{n}}{\Delta t}+\partial_x H_z^{n+1/2}=-eN_e \frac{u_y^{n+1}+u_{y}^{n}}{2},\nonumber\\
  \mu_0\frac{ H_z^{n+1/2}-H_z^{n-1/2}}{\Delta t}+\partial_x E_y^{n}-\partial_y E_x^{n}=0, \label{eq:tdiscretizedpb}\\
@@
 We restrict the presentation to the minimum and leave the details  of the construction to the alert reader.
+Concerning the   vast literature on the use of semi-lagrangian schemes
+in numerical plasma physics, we refer the reader to \cite{feix,guo,umeda,fifi,soso} and references therein.
+	The structure of the following  algorithm is very similar to the one developed in \cite{compfluids} and can be adapted and studied numerically
+	in any dimension on a Cartesian grid and for more complex right-hand sides.
+	So mathematical properties of the  first step of the following semi-lagrangian scheme have been described in  \cite{cedar}.
 
@@
 at time step $t_{n+1}=(n+1)\Delta t$, and that defines totally a time step of the algorithm.
-
-\begin{remark}
-	The structure of this algorithm is very similar to the one developed in \cite{compfluids} and can be adapted and studied numerically
-	in any dimension on a Cartesian grid and for more complex right-hand sides.
-\end{remark}

### 2015-06-10 report_clean_merged/numerics.tex
addede bruno's modifications

@@
 The last inequality follows from Lemma \ref{lemma:well_posedness} and is still valid for $\nu\rightarrow 0$.   
-\item The form of the exact solution to the problem (\ref{vf1dcase}), see \cite{Despres_2014} and \cite[Proposition 1]{singular_solutions}
-\begin{align}
-\label{eq:exact}
- E_x^{\nu}(x)=f_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+\frac{g_{\nu}(x)}{\rho(x-X_{\nu})}+S_{1}^{\nu}(x),
-\end{align}
-where $\rho_{\nu}$ is a smooth function s.t. $\rho_{\nu}(0)=0,$ with the derivative $\rho_{\nu}'(0)=1$, 
-the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R}_{*}$; $f_{\nu},\; g_{\nu}, \; S_{1}^{\nu}(x)$ are smooth functions, 
-which, together with their derivatives, are bounded independently of $\nu$. 
-\item \mrev{An explicit bound on $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ is available,  
-based on the results of \cite{singular_solutions}. First of all, we
-will assume that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the behaviour in the vicinity of the resonance, where 
-the following expansion is valid \cite[Proposition 1]{singular_solutions}
-\begin{align*}
-E_{y}^{\nu}(x)=\tilde{E}_{y}^{\nu}(x)+S^{\nu}_2(x), \\
-\tilde{E}_{y}^{\nu}(x)=(\alpha(x)+i\nu)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu}),%=(-x+i\nu)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu}),
-\end{align*}
-where $\rho_{\nu},X_{\nu}$ are is in (\ref{eq:exact}), 
-and $p_{\nu}(x),\; S_{2}^{\nu}(x)$ are smooth functions, which, together with their derivatives, are bounded independently of $\nu$.}
 \item The estimate from \cite[Chapter 0]{brenner} on the rate of convergence of the interpolation 
@@
 where $I^{h}$ is an interpolation operator onto $P_{h}^{1}$. 
+\item \mrev{An explicit bound on $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$ from \cite{Despres_2014} and \cite[Proposition 1]{singular_solutions}. 
+First of all, we 
+will assume that the main contribution to $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the behaviour in the vicinity of the resonance, where, 
+for sufficiently small $\nu$, the following expansion is valid \cite[Proposition 1]{singular_solutions}
+\begin{align}
+\begin{split}
+\label{eq:exact}
+ E_x^{\nu}(x)=\tilde{E}_x^{\nu}+S_{1}^{\nu}(x),\\
+ \tilde{E}_x^{\nu}=f_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+\frac{g_{\nu}(x)}{\rho(x-X_{\nu})},
+ \end{split}
+\end{align}
+where $f_{\nu},\; g_{\nu}, \; S_{1}^{\nu}(x)$ are smooth functions, 
+which, together with their derivatives, are bounded independently of $\nu$ for all sufficiently small values of $\nu$; 
+$\rho_{\nu}$ is a smooth function s.t. $\rho_{\nu}(0)=0,$ with the derivative $\rho_{\nu}'(0)=1$, 
+the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R}_{*}$. 
+}
+\item \mrev{An explicit bound on $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ from \cite{singular_solutions}. As before, we 
+will assume that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the behaviour in the vicinity of the resonance, where,
+for sufficiently small $\nu$, it holds \cite[Proposition 1]{singular_solutions}
+\begin{align*}
+E_{y}^{\nu}(x)=\tilde{E}_{y}^{\nu}(x)+S^{\nu}_2(x), \\
+\tilde{E}_{y}^{\nu}(x)=(\alpha(x)+i\nu)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu}),%=(-x+i\nu)p_{\nu}(x)\log\rho_{\nu}(x-X_{\nu}),
+\end{align*}
+where $\rho_{\nu},X_{\nu}$ are is in (\ref{eq:exact}), 
+and $p_{\nu}(x),\; S_{2}^{\nu}(x)$ are smooth functions, which, together with their derivatives, are bounded independently of $\nu$ 
+for all sufficiently small values of $\nu$.}
 \end{itemize}
@@
 
-The setting of the numerical results of figure \ref{fig:vasl}
+The setting of the numerical results of Figure \ref{fig:vasl}
 is the following. We use a 7th order semi-lagrangian scheme, and the CFL is $\nu=0.5$.
@@
 The total energy $\mathcal E(t)$ is the physical energy. 
-The comparison with figures \ref{fig:dependence} and \ref{fig:resonance_nus_ey_x} shows that the 
+The comparison with Figures \ref{fig:dependence} and \ref{fig:resonance_nus_ey_x} shows that the 
 singular nature of the \arev{resonance} is captured by this new scheme without any doubt.
 
-\begin{figure}{h}
+\urev{Notice that in this case we shifted the computational domain so that $L=0$ and the point where the resonance occurs is $x_h=20$.}
+
+\begin{figure}[h]
 	\begin{center}
@@
 			%\hline
-			\hline
+			%\hline
 			\includegraphics[angle=-90,width=5.cm]{pics_semilagrange/uy_moit.eps}

### 2015-09-14 report_clean_final/TEX/numerics.tex
Correcting typoes as asked by the referee

@@
 \begin{itemize}
- \item The C\'ea's lemma applied to the problem (\ref{vf1dcase}); here \mrev{$\mathbf{E}^{\nu}$ is the exact solution, 
+ \item \lastrev{The C\'ea lemma} applied to the problem (\ref{vf1dcase}); here \mrev{$\mathbf{E}^{\nu}$ is the exact solution, 
  $\mathbf{E}^{\nu,h}$ is the computed solution}, and $C_c$ and $C_i$ are respectively the continuity and the coercivity constants:
@@
 \end{align}
-The last inequality follows from Lemma \ref{lemma:well_posedness} and is still valid for $\nu\rightarrow 0$.   
+The last inequality follows from Lemma \ref{lemma:well_posedness} and \lastrev{is valid} for $\nu\rightarrow 0$.   
 \item The estimate from \cite[Chapter 0]{brenner} on the rate of convergence of the interpolation 
@@
  E_x^{\nu}(x)=\tilde{E}_x^{\nu}+S_{1}^{\nu}(x),\\
- \tilde{E}_x^{\nu}=f_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+\frac{g_{\nu}(x)}{\rho(x-X_{\nu})},
+ \tilde{E}_x^{\nu}=f_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+\frac{g_{\nu}(x)}{\rho\lastrev{_{\nu}}(x-X_{\nu})},
  \end{split}
 \end{align}
-where $f_{\nu},\; g_{\nu}, \; S_{1}^{\nu}(x)$ are smooth functions, 
+where \lastrev{$f_{\nu},\; g_{\nu}, \; S_{1}^{\nu}$} are smooth functions, 
 which, together with their derivatives, are bounded independently of $\nu$ for all sufficiently small values of $\nu$; 
@@
 \end{itemize}
-Estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C>0$,
+\lastrev{Let us recall that we defined the function space  $\mathbf{V}=L^{2}(\Omega)\times H^{1}(\Omega)$. }Estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C>0$. 
 \begin{align}
@@
 \bealn
- \left|\frac{d^2E_x^{\nu}}{dx^2}\right|_{L^2}^{2}&\leq c\int\limits_{-L}^{H}\frac{1}{(x^2+\nu^2)^{3}}dx
+ \left\|\frac{d^2E_x^{\nu}}{dx^2}\right\|_{L^2}^{2}&\leq c\int\limits_{-L}^{H}\frac{1}{(x^2+\nu^2)^{3}}dx
  % &=c\left.

### 2015-09-15 report_clean_final/TEX/FD.tex
Correcting typoes as asked by the referee
fixed multiple typos extra

--- 2015-06-08 report_clean_merged/FD.tex
@@
 where the frequency 
-$\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane. \arev{ %Notice that neither cyclotron, nor hybrid resonances occur in the problem 
-%with the dielectric tensor $\uuline{\varepsilon_{\omega}^{\nu}}(x), \; \nu>0$ (since all the problem parameters are real). Hence 
-%t
-The choice of the non-zero plasma friction $\nu>0$ is a regularization of the problem. }
+$\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane. The choice of the non-zero plasma friction $\nu>0$ is a regularization of the problem.
 
-\mrev{
 A series expansion as $\nu\rightarrow 0$ gives at leading orders
@@
 \een
-yields to the same limit solution as $\nu\rightarrow 0$. }
+yields the same limit solution as $\nu\rightarrow 0$.
 As a consequence we will consider in this work the simpler regularized system
-%Thus, applying the above process to (\ref{eq:main_model}) in the frequency domain, we obtain, see also \cite{Despres_2014},
 \begin{align*}
@@
 \end{align*}
-\mrev{
+
 For brevity, from now on we will denote $\frac{\omega^2}{c^2}\alpha_{\omega},\; \frac{\omega^2}{c^2}\delta_{\omega}$ by $\alpha,\; \delta$ and consider a sequence of regularized problems. 
@@
 where $\alpha,\;\delta$ satisfy the following assumption.
-}
-\urev{
+
 \begin{assumption}
@@
 for all $x$ $|\omega_c^2(x)-\omega^2(x)|>c>0$ on this interval.
-}
-\urev{
+
 \begin{remark}
@@
 \end{remark}
-}
+
 %%%%%%%%%%%%%%%%%%%%%% 
-\mrev{\subsection{Well-Posedness of the Frequency Domain Problem}}
+\subsection{Well-Posedness of the Frequency Domain Problem}
 %%%%%%%%%%%%%%%%%%%%%% 
@@
 %denoting by $\theta$ the corresponding Fourier variable. 
-\mrev{In this section we study the well-posedness of Problem (\ref{eq:main_frequency_domain}) with the 
- boundary conditions (\ref{eq:boundary_conditions_intro}), thanks to the Lax-Milgram lemma.} 
+In this section we study the well-posedness of Problem (\ref{eq:main_frequency_domain}) with the 
+ boundary conditions (\ref{eq:boundary_conditions_intro}), thanks to the Lax-Milgram lemma. 
 After introducing $\Omega=(-L,\; H)\subset \mathbb R$ and defining the function space  $\mathbf{V}=L^{2}(\Omega)\times H^{1}(\Omega)$, 
@@
 \ben
- \|\mathbf{v}\|_{\mathbf{V}}^2= \|v_1\|_{L^{2}(\Omega)}^2+\|v_2\|_{H^{1}(\Omega)}^2,
+ \|\mathbf{v}\|_{\mathbf{V}}^2= \|v_1\|_{L^{2}(\Omega)}^2+\|v_2\|_{H^{1}(\Omega)}^2 \qquad   \text{for }\nrev{\mathbf{v}=(v_1,\; v_2)},
 \een
@@
 \begin{array}{l}
-\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\widetilde E_y' -\urev{i} \theta \widetilde E_x)} 
+\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\widetilde E_y' -i \theta \widetilde E_x)} 
 - \int_{-L}^H (\uuline{\varepsilon}^{0} +i\nu \mathrm{Id}) \E \cdot \overline{\widetilde \E}
@@
 Recall that here $\lambda\geq 0$.
-%=\omega\geq 0$. 
-Let us remark that in this and further sections, where it is not ambiguous, we will use the notation $E_{x,y}$ instead of $\widehat{E}_{x,y}$ for convenience. \mrev{Also, 
+
+Let us remark that in this and further sections, where it is not ambiguous, we will use the notation $E_{x,y}$ instead of $\widehat{E}_{x,y}$ for convenience. Also, 
 by $\|u\|_{L^{2}}$ we will denote $\|u\|_{L^{2}(\Omega)}$, for $u\in L^2(\Omega)$, and $\|\ubf\|_{L^2(\Omega)}=\left(\|u_1\|^2_{L^2}+\|u_2\|^2_{L^2}\right)^{\frac{1}{2}}$, 
-for $\ubf=(u_1,\;u_2)\in \left(L^2(\Omega)\right)^2$.}
+for $\ubf=(u_1,\;u_2)\in \left(L^2(\Omega)\right)^2$.
 
-For the sake of conciseness, consider the following definitions. Let $a$ and $l$ be the bilinear and linear forms, \urev{defined for $\mathbf{u},\; \mathbf{v}\in \mathbf{V}$}:
+\nrev{For the sake of conciseness, we introduce the following notation}. Let $a$ and $l$ be the bilinear and linear forms, defined for $\mathbf{u},\; \mathbf{v}\in \mathbf{V}$:
 \ben
@@
 \een
-Then \eqref{vf1dcase} reads: \urev{find $\mathbf{E}$ such that},
+Then \eqref{vf1dcase} reads: find $\mathbf{E}$ such that
 \ben
@@
 
-\urev{
 Let us denote the spectral radius of $\uuline{\varepsilon}^{0}$ by $\heps =  \|\rho(\uuline{\varepsilon}^{0})\|_{L^{\infty}(\Omega)}$. 
 By Assumption \ref{assumption:smooth}, the spectral radius $\heps=\max\left(\|\alpha+\delta\|_{L^{\infty}(\Omega)}, \|\alpha-\delta\|_{L^{\infty}(\Omega)}\right)$ 
-is bounded.}
+is bounded.
 %\end{df}
@@
 \label{lemma:well_posedness}
-\urev{Let Assumption \ref{assumption:smooth} hold}. Then the bilinear form 
+Let Assumption \ref{assumption:smooth} hold. Then the bilinear form 
 \ben
@@
 \een
-is continuous and coercive for all \mrev{$\lambda\geq 0$} and $\nu>0$: for all $\ubf,\vbf\in \mathbf{V}$ it holds that
+is continuous and coercive for all $\lambda\geq 0$ and $\nu>0$: for all $\ubf,\vbf\in \mathbf{V}$ it holds that
 \bealn
@@
 \left\{\begin{array}{l}
-\Re\left(\mathrm{e}^{i\urev{\beta_{\nu}}}a(\ubf,\ubf)\right)\geq \frac{|\nu|}{\sqrt{(\heps+\theta^2+1)^2+\nu^2}}\left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right),\; 
-\text{ for some $\urev{\beta_{\nu}}\in\left(0,\frac{\pi}{2}\right)$},\\
+\Re\left(\mathrm{e}^{i\beta_{\nu}}a(\ubf,\ubf)\right)\geq \frac{|\nu|}{\sqrt{(\heps+\theta^2+1)^2+\nu^2}}\left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right),\; 
+\text{ for some $\beta_{\nu}\in\left(0,\frac{\pi}{2}\right)$},\\
 |a(\ubf,\vbf)|\leq C \|\ubf\|_{\mathbf{V}}\|\vbf\|_{\mathbf{V}},
@@
 	one  $H^1(\Omega)\subset C^0(\overline \Omega)$. Let us focus on the proof of coercivity. 
-	\mrev{Given $\heps$ the spectral radius of $\uuline{\varepsilon}^{0}$, 
-	$\heps \mathrm{Id}- \uuline{\varepsilon}^{0} $ is a non-negative hermitian matrix.}
+	Given $\heps$ the spectral radius of $\uuline{\varepsilon}^{0}$, 
+	$\heps \mathrm{Id}- \uuline{\varepsilon}^{0} $ is a non-negative hermitian matrix.
 	Therefore
@@
 	a_1(\ubf,\ubf)  \geq \frac{1}{2}\|u_2'\|^2_{L^2}-  (\heps  +  \theta^2) \| \ubf \|_{L^2}^2$.
-	On the other hand, \mrev{for $\lambda \geq 0$},
+	On the other hand, for $\lambda \geq 0$,
 	$
@@
 	\een	
-	Problem \eqref{vf1dcase} is then uniquely solvable thanks to Lax-Milgram theorem.
+	Problem \eqref{vf1dcase} is then uniquely solvable thanks to \nrev{the Lax-Milgram theorem}.
 \end{proof}
-%
-%
-%\begin{remark}
-%\mrev{Not the variational problem can be proved well-posed
-%with the same method for  slightly different coefficients.
-%%For example for $\lambda<0$ and  Note that in the case $\lambda=0$, one can show that the problem is well-posed for all $\nu< 0$, since $a_2(\ubf,\ubf)=-\nu\|\ubf\|_{L^2}^2$ and 
-%%thus in the above proof
-%%\begin{align*}
-%%a_1(\ubf,\ubf)-\frac{\heps  +  \theta^2 + 1 }\nu a_2(\ubf,\ubf)=\left(a_1(\ubf,\ubf)+(\heps  +  \theta^2)\|\ubf\|_{L^2}^2\right)+\|\ubf\|_{L^2}^2.
-%%\end{align*}
-%%Similarly, in the case $\lambda<0$, it is possible to demonstrate the well-posedness of the problem for $\nu<0$. 
-%}
-%\end{remark}
-
 \begin{remark} 
@@
 $\alpha(x)>c$ for some $c>0$ on the whole interval $[-L,\; H]$, at least 
-for the case $\theta=0$. In this particular case Problem (\ref{eq:var_form2}) is well-posed for $\nu=0$. More precisely, it can be written 
+for the case $\theta=0$. In this particular case Problem \lastrev{\eqref{vf1dcase}} is well-posed for $\nu=0$. More precisely, it can be written 
 as a system of two equations, the first equation (for $E_y$) being the variational formulation for the Helmholtz equation 
-with the variable coefficient $k^2=(\alpha-\frac{\delta^2}{\alpha})$ \mrev{coupled to boundary conditions (\ref{eq:boundary_conditions_frequency_domain})}, and the second equation being  
-\begin{align*}
-  \left(E_x,u\right)=\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega).
-\end{align*}
-The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
-was demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H^{1}(\Omega)$, $E_x\in L^{2}(\Omega)$ is uniquely defined from the latter equation.
+with the variable coefficient $k^2=(\alpha-\frac{\delta^2}{\alpha})$ coupled to boundary conditions (\ref{eq:boundary_conditions_frequency_domain}), and the second equation being  
+$
+  \left(E_x,u\right)=\left(\frac{i\delta}{\alpha}E_y,u\right)$  for all  $u\in L^{2}(\Omega)$.
+\nrev{The demonstration of the well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
+can be found in \cite[Theorem 5.2.3]{LMIG_thesis}}. Provided the solution $E_y\in H^{1}(\Omega)$, $E_x\in L^{2}(\Omega)$ is uniquely defined from the latter equation.
 \end{remark}
-
-%\subsection{2D case}
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%% 
-%\textcolor{red}{!!!!!!!!!!!!!!!! TODO : deal with this part !!!!!!!!!!!}
-%$curl$ ibp formula
-%\be
-%\int_\Omega \curl u \cdot \f = \int_\Omega u\ curl \f + \int_\Gamma u (\f \wedge \n)
-%\ee
-%\be
-%\int_\Omega curl \E \cdot \overline{curl \tilde \E} - \int_\Omega \eps \E \cdot \overline{\tilde \E} + \int _\Gamma curl \E \overline{\left( \tilde \E\wedge \n \right)} d\sigma = 0
-%\ee
-%\be
-%\begin{array}{l}
-%\displaystyle \int_\Omega curl \E \cdot \overline{curl \tilde \E} - \int_\Omega (\varepsilon^{0}+i\nu Id) \E \cdot \overline{\tilde \E} - \int _{\{x=-L\}} i \sqrt{\alpha(-L)}(\E\wedge \n) \overline{\left( \tilde \E\wedge \n \right)} d\sigma
-%\\ \displaystyle \phantom{ fffffffff}= \int_{\{x=-L\}} g_{inc}  \overline{\left( \tilde \E\wedge \n \right)} d\sigma
-%\end{array}\ee
-%\textcolor{red}{!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}
 
@@
 an explicit expression for the tensor of the dielectric permittivity (\ref{eq:epsilon_0}), we get the following system of two equations
-%\begin{align*}
-%\begin{split}
-%i\theta \displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{\tilde E_x} - \int_{-L}^H \left((\epsilon_0 +i\nu \operatorname{Id}) \E\right)_{1} \overline{\tilde E}_{x}
-%&=0,\\
-%\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\tilde {E_y'} - \int_{-L}^H\left( (\epsilon_0 +i\nu\operatorname{Id}) \E\right)_{2}\overline{\tilde{E}}_{y}
-%  - i \lambda E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
-%  \text{ for all } \tilde E_x\in L^{2}(\Omega), \; \tilde{E}_{y}\in H^{1}(\Omega).
-%  \end{split}
-%\end{align*}
-%Using the explicit expression for the dielectric permittivity tensor in the above, it yields:
 
@@
 \end{align}
-\urev{Let us introduce two function spaces $V_{E_x}\subset L^{2}(\Omega)$ spanned by a set of basis functions $\{\psi_{j}\}_{j=1}^{N_{1}}$ and $V_{E_{y}}\subset H^{1}(\Omega)$ spanned by $\{\phi_{i}\}_{i=1}^{N_{2}}$.
-}
+Let us introduce two function spaces $V_{E_x}\subset L^{2}(\Omega)$ spanned by a set of basis functions $\{\psi_{j}\}_{j=1}^{N_{1}}$ and $V_{E_{y}}\subset H^{1}(\Omega)$ spanned by $\{\phi_{i}\}_{i=1}^{N_{2}}$.
 %We look for the solution of the problem (\ref{eq:var_form2}) in the form:
@@
 \ben
-E_x=\sum\limits_{k=1}^{N_{1}}e_{xk}\psi_{k},\qquad E_{y}=\sum\limits_{k=1}^{N_{2}}e_{yk}\phi_{k}.
+E_x\lastrev{\approx} \sum\limits_{k=1}^{N_{1}}e_{xk}\psi_{k},\qquad E_{y}\lastrev{\approx} \sum\limits_{k=1}^{N_{2}}e_{yk}\phi_{k}.
 \een
 
-% Substituting $\tilde{E}_{x}=\psi_{m}, \; m=1,\ldots,N_{1}$ and $\tilde{E}_{y}=0$ into the variational formulation (\ref{}), we obtain:
-% \begin{align*}
-% i\theta\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}\bar{\psi}_{m}dx+\theta^2\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}\bar{\psi}_{m}dx\\
-% -\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\psi_{k}\bar{\psi}_{m}dx-i\sum\limits_{1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\delta(x)\phi_{k}(x)\bar{\psi}_{m}dx=0.
-% \end{align*}
-% Similarly, for $\tilde{E}_{x}=0$ and $\tilde{E}_{y}=\phi_{\ell},\; \ell=1,\ldots, N_{2}$:
-% \begin{align*}
-% \sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}\phi'_{k}(x)\bar{\phi}'_{\ell}(x)dx-i\theta\sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\psi_{k}(x)\bar{\phi}'_{\ell}(x)dx\\
-% +i
-% \sum\limits_{k=1}^{N_{1}}e_{1k}\int\limits_{-L}^{H}\delta(x)\psi_{k}\bar{\phi}_{m}dx-\sum\limits_{k=1}^{N_{2}}e_{2k}\int\limits_{-L}^{H}(\alpha(x)+i\nu)\phi_{k}\bar{\phi}_{m}dx\\
-% -
-% i\lambda\sum\limits_{k=1}^{N_{2}}e_{2k}\phi_{k}(-L)\bar{\phi}_{m}(-L)=-g_{inc}(x)\bar{\phi}_{m}(-L).
-% \end{align*}
 Introducing
@@
 I_{km}^{\Gamma}=\bar{\phi}_{m}(-L)\phi_{k}(-L), \\
-\boldsymbol{e}_{x}=\left(e_{11},\ldots,e_{1 N_{1}}\right)^{T},\; \boldsymbol{e}_{y}=\left(e_{21},\ldots,e_{2 N_{1}}\right)^{T},\\
+\boldsymbol{e}_{x}=\left(\lastrev{e_{x1}},\ldots,\lastrev{e_{x N_{1}}}\right)^{T},\; \boldsymbol{e}_{y}=\left(\lastrev{e_{y1}},\ldots,\lastrev{e_{y N_{2}}}\right)^{T},\\
 \boldsymbol{0}_{n} \text{ is an $n$-dimensional zero column vector},
@@
 \een
-This expression greatly simplifies when \urev{ choosing $V_{E_x}=V_{E_{y}}$, spanned by a unique set of basis funtions $\left(\phi_{m}\right)_{m=1}^{N_{2}}$,} and
-in the case $\theta=0$. One obtains the \urev{matrix} structure
+This expression greatly simplifies when  choosing $V_{E_x}=V_{E_{y}}$, spanned by a unique set of basis functions $\left(\phi_{m}\right)_{m=1}^{N_{2}}$, and
+in the case $\theta=0$. One obtains the matrix structure
 \begin{align}
@@
 \boldsymbol{0}_{N_{1}}\\
-\bar{\phi}_{x}(-L)\\
-\bar{\phi}_{y}(-L)\\
+\bar{\phi}_{\lastrev{1}}(-L)\\
+\bar{\phi}_{\lastrev{2}}(-L)\\
 \vdots\\

### 2015-09-15 report_clean_final/TEX/absorption.tex
fixed multiple typos extra

@@
 \end{itemize}
-For every fixed absorption rate \urev{$\nu>0$}, in the time domain we choose the boundary conditions
+For every fixed absorption rate $\nu>0$, in the time domain we choose the boundary conditions
 \begin{align}
@@
 \ben
-\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t), \text{ and } \Im\left(\hat{\mathbf{E}}^{\nu}\mathrm{e}^{\mrev{-it}}\right)
+\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t), \text{ and } \Im\left(\hat{\mathbf{E}}^{\nu}\mathrm{e}^{-it}\right)
 \een
@@
 on the domain as $(-0.5, 10)$ and set the electron density $N_e(x)=1+x>0,\; x\in \Omega$. 
-\urev{Importantly, since $\delta(x)=0$, in this case no resonance occurs and $E_{x}(x,t)\equiv 0$. This corresponds to the case when the
+Importantly, since $\delta(x)=0$, in this case no resonance occurs and $E_{x}(x,t)\equiv 0$. This corresponds to the case when the
 tensor of dielectric permittivity $\uuline{\varepsilon^{0}_{\omega}}$ is 
-diagonal.}
+diagonal.
 
@@
 inside the domain and plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ 
-on time $t$ for a range of $t\gg 1$ in Fig.~\ref{fig:nu1e2_harmon}. We compare this solution to the computed $\Im\left(\hat{E}_y^{\nu}\mathrm{e}^{\mrev{-it}}\right)$, for
+on time $t$ for a range of $t\gg 1$ in Fig.~\ref{fig:nu1e2_harmon}. We compare this solution to the computed $\Im\left(\hat{E}_y^{\nu}\mathrm{e}^{-it}\right)$, for
 fixed values of $t$. Both solutions appear to be in close agreement.
@@
 \end{tabular}
-\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ \urev{to the problem described in Section \ref{section:absorption_airy}} on time for large times is demonstrated in the left figure.  
-In the right figure we show the solution \urev{to the same problem} for $\nu=10^{-2}$, for two fixed moment of times.}
+\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ to the problem described in Section \ref{section:absorption_airy} on time for large times is demonstrated in the left figure.  
+In the right figure we show the solution to the same problem for $\nu=10^{-2}$, for two fixed moment of times.}
  \label{fig:nu1e2_harmon}
@@
 \end{tabular}
-\caption{In the left figure we plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ \urev{to the problem described in Section \ref{section:absorption_airy}} on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$.
-In the right figure we show the solution \urev{to the same problem} for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
+\caption{In the left figure we plot the dependence of the solution $E_{y}^{\nu}(x_c,t)$ to the problem described in Section \ref{section:absorption_airy} on time $t$, with $\nu=10^{-4}$ and $x_c=0.45$.
+In the right figure we show the solution to the same problem for $\nu=10^{-6}$ at the same point $x_c$, for larger times. As we can see, for 
 $\nu=10^{-4}$ the limiting amplitude solution was reached for large $t$. For $\nu=10^{-6}$ we were not able 
@@
  \end{tabular}
-\caption{The figures demonstrate the dependence of the solutions to the problem \urev{described in Section \ref{sec:resn}}
+\caption{The figures demonstrate the dependence of the solutions to the problem described in Section \ref{sec:resn} 
 $E_y^{\nu}(-2.5125,t)$ on time $t$ for different values of $\nu$. }
@@
  \caption{The plot shows the dependence of the solution $E_x^{\nu}(x_c,t),\;\nu=10^{-4},$ to 
- the problem \urev{described in Section \ref{sec:resn}} on time $t$ for fixed 
+ the problem described in Section \ref{sec:resn} on time $t$ for fixed 
  $x_c=0.0125$ and for $x_c=-2.5$. We can see that the solutions computed in the time domain are in close agreement 
  with the solution computed in the frequency domain at the point $x_c=-2.5$, however, differ at the point $0.0125$ which is 
- close to the $x=0$ where the resonance occurs.}
+ close to $x=0$ where the resonance occurs.}
  \label{fig:resonance_nus_ex_x}
@@
 \caption{The figures demonstrate the dependence of the solutions 
-$E_x^{\nu}(x,t)$ to the problem \urev{described in Section \ref{sec:resn}} on $x$ for fixed values of $t$. }
+$E_x^{\nu}(x,t)$ to the problem described in Section \ref{sec:resn} on $x$ for fixed values of $t$. }
 \label{fig:resonance_nus_ex_t}
@@
 \caption{The left figure demonstrates the dependence of the solution  
-$E_y^{\nu}(x,y)$ to the problem \urev{described in Section \ref{sec:resn}} on $x$ for fixed values of $t$. 
+$E_y^{\nu}(x,y)$ to the problem described in Section \ref{sec:resn} on $x$ for fixed values of $t$. 
 For a chosen value of $\nu$ the solutions computed in the time domain are in close agreement 
@@
 true for the computed values $E_x^{\nu}(x,t)$ in this case (which may be caused by the discretization). 
-The right figure shows the dependence of the solution $E_y^{\nu}(x,t)$ \mrev{to the same problem} for $\nu=10^{-4}$ on time for fixed $x=x_c$. 
-We can see that the while the limiting amplitude principle holds true, the difference between the solutions computed in 
-the time and frequency domain is not visible on this scale (c.f. Figure \ref{fig:resonance_nus_eyx_t}). 
+The right figure shows the dependence of the solution $E_y^{\nu}(x,t)$ to the same problem for $\nu=10^{-4}$ on time for fixed $x=x_c$. 
+\nrev{We can see that the limiting amplitude solution had been achieved, and the difference between the solutions computed in 
+the time and frequency domain is not visible on this scale} (c.f. Figure \ref{fig:resonance_nus_eyx_t}). 
 }
@@
 \caption{The figures demonstrate the dependence of the solutions 
-$E_x^{\nu}(x,t)$ and $E_y^{\nu}(x,y)$ to the problem \urev{described in Section \ref{sec:resn}} on $x$ for fixed values of $t$. While the solution in the time-domain 
+$E_x^{\nu}(x,t)$ and $E_y^{\nu}(x,y)$ to the problem described in Section \ref{sec:resn} on $x$ for fixed values of $t$. While the solution in the time-domain 
 in the resonance point $x=0$ has a smaller absolute value than that computed in the frequency domain (in the plot both solutions are truncated to 
@@
 Figures \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}, \ref{fig:resonance_nus_eyx_t} show that in the case of the resonance
-the solution achieves the limiting amplitude solution, and both solutions are in close agreement (but in the points close to a point where the resonance occurs).
+\nrev{the limiting amplitude solution is achieved}, and both \nrev{limiting amplitude and limited absorption solutions} are in close agreement (but in the points close to a point where the resonance occurs).
 These numerical results show that the staggered scheme resolves the resonance, similarly to the semi-lagrangian scheme described before.  

### 2015-09-15 report_clean_final/TEX/conclusions.tex
addede bruno's modifications
fixed multiple typos extra

--- 2015-06-08 report_clean_merged/conclusions.tex
@@
 \section{Conclusions}
-In this work we considered the frequency- and the time-domain formulations of the $X$-mode Maxwell equations. 
+In this work we considered the frequency  and the time-domain formulations of the $X$-mode Maxwell equations. 
 In particular, we proved the well-posedness of the regularized variational formulation with
@@
 well as studied the convergence of the finite element method for the problem with the resonance. 
-The piecewise-\urev{linear} FEM approximates the resonant solution rather well, at least for moderate values of $\nu$, 
+The piecewise-linear FEM approximates the resonant solution rather well, at least for moderate values of $\nu$, 
 however, the discretization size should be chosen roughly proportional to $\nu^{\frac{7}{4}}$, in order to obtain an accurate discretization.
@@
 Another unanswered question is the well-posedness of the discrete problem when the continuous problem is ill-posed. We have 
-demonstrated by numerical means that while the condition number of the FEM matrix grows, the matrix remains always invertible, even for $\nu=0$.
+demonstrated by numerical means that while the condition number of the FEM matrix grows, the matrix remains \nrev{invertible even for $\nu=0$}.
 

### 2015-09-15 report_clean_final/TEX/intro.tex
fixed multiple typos extra

@@
 mathematically as the non-regularity of
-the solutions of Maxwell equations in \mrev{magnetized plasmas} \cite{Despres_2014}. 
+the solutions of Maxwell equations in magnetized plasmas \cite{Despres_2014}. 
 Physically the hybrid resonance corresponds to situations where the electric field becomes
@@
 in dimension greater or equal to two, we restrict this work to dimension one.
-% any open problems exist which prevent for having
-%a mathematically sound multidimensional theory  of hybrid resonance.
-% is an open problem.
 
-\urev{
 To illustrate the hybrid resonance, we consider in this work a %one dimensional 
- time-dependent wave propagation problem leading to the cold plasma model for a single species 
+ time-dependent wave propagation problem leading to the cold plasma model for a single species (\nrev{electrons}) 
 under a uniform in time background magnetic field $\mathbf{B}_0=(0,\;0,\; B_0)$. 
@@
 -\epsilon_0 \partial_t E_y -\partial_x H_z = J_y,\\
-\mu_0 \partial_t H_z + \partial_x E_y-\partial_y E_x= 0
+\mu_0 \partial_t H_z + \partial_x E_y-\partial_y E_x= 0,
 \end{split}
@@
 \end{align}
-where \mrev{$\nu\geq 0$} is the friction  between particles, $e<0$ is the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density.
+where $\nu\geq 0$ is the friction  between particles, $e<0$ is the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density.
 In the cold plasma model, because of the frequencies considered, the electron density
@@
 \een
-and (\ref{eq:main_system}-\ref{eq:electronmove}) yield to
+and (\ref{eq:main_system}-\ref{eq:electronmove}) yield
 \ben
@@
 $\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})$ vanishes and the non-diagonal part remains non-zero.
-As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component $E_x$ is not necessarily square 
+As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component \nrev{$\hat{E}_x$} is not necessarily square
 integrable (for a demonstration of this behaviour with the help of a simpler example, namely the Budden problem, see e.g. \cite{Despres_2014}). 
@@
  {\operatorname{curl}} \
-  \hat{\mathbf{E}} \mrev{+}i \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} \equiv
-   {\operatorname{curl}} \ \E_{inc} \mrev{+} i  \lambda\E_{inc}\wedge \n,
+  \hat{\mathbf{E}} +i \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} \equiv
+   {\operatorname{curl}} \ \E_{inc} + i  \lambda\E_{inc}\wedge \n,
 \ee
-where $\E_{inc} = \exp \left(i  \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and \mrev{$\lambda\geq 0$} is 
+where $\E_{inc} = \exp \left(i  \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and $\lambda\geq 0$ is 
 the frequency of the antenna. At the right boundary we impose $\operatorname{curl} \hat{\E} = 0$.
@@
 \end{equation}
- posed in the one-dimensional domain $(-L,\; H)$, with \mrev{the corresponding boundary conditions:
+ posed in the one-dimensional domain $(-L,\; H)$, with the corresponding boundary conditions:
  \begin{align}
@@
  \end{align}
-and the initial conditions for values $\left.E_{x}\right|_{t=0},\; \left.u_{x}\right|_{t=0},\; \left.E_{y}\right|_{t=0}, \; \left.u_{y}\right|_{t=0}, \; \left.H_z\right|_{t=0}$. }
+and the initial conditions for values $\left.E_{x}\right|_{t=0},\; \left.u_{x}\right|_{t=0},\; \left.E_{y}\right|_{t=0}, \; \left.u_{y}\right|_{t=0}, \; \left.H_z\right|_{t=0}$. 
 This is the time-domain model that will be considered in the rest of the article, unless stated otherwise.
@@
 \end{align}
-see (\ref{eq:alpha_delta}). Indeed, in a stratified medium, the coefficients $\alpha_{\omega},\;\delta_{\omega}$ depend solely on $x$ and $\omega$.  
-\arev{
+see (\ref{eq:alpha_delta}).
+Indeed, in a stratified medium, the coefficients $\alpha_{\omega},\;\delta_{\omega}$ depend solely on $x$ and $\omega$.
 We concentrate on a physical situation of the hybrid resonance, which we define as in \cite{singular_solutions}.
-
 \begin{df}[of a hybrid resonance]
@@
 \end{df}
-}
-
 To investigate the behaviour of the solutions at the hybrid resonance, 
@@
 \end{align}
-where $\mathrm{Id}$ is the identity matrix. %More details on the connection of this problem with (\ref{eq:main_model}) will be provided in further sections.
-
- %This domain represents the physical case of a wave sent from a wall facing a plasma.
-
-%In  \cite{Despres_2014} it was shown
-%that the time harmonic electric field component $E_x$ in this case is not necessarily square 
-%integrable, and  
-%explicit estimates on the behavior of the solutions of \eqref{eq:main_model} in 1D were provided.
-
-%some given 
-%frequency. 
-%We truncate the domain 
-%\ben
-%-curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
-%\een
-%where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$.
-
-%\begin{remark}
-%	When modelling antennas in plasma physics \mrev{(e.g. in such applications as ITER)}, 
-%	a good choice of boundary condition could be $\lambda = \sqrt{\alpha_{\omega}(-L)}$
-%\end{remark}
+where $\mathrm{Id}$ is the identity matrix.
 
@@
 First, we investigate the finite element approximation of the 1D 
-frequency domain problem (\ref{eq:seq_regularized}), with a regularized dielectric tensor \mrev{for a small parameter $\nu$}. 
-%linearized with respect to $\nu$.
-We prove the well-posedness of this problem for \mrev{$\nu\neq 0$} in Section~\ref{sec:wellposedness} and 
+frequency domain problem (\ref{eq:seq_regularized}), with a regularized dielectric tensor for a small parameter $\nu$.
+We prove the well-posedness of this problem for $\nu\neq 0$ in Section~\ref{sec:wellposedness} and
 demonstrate that the use of  $P_1$ finite elements allows to approximate the singularity 
-of the solution efficiently (Section \ref{sec:freq_dep}). 
-}
-Second, we develop an original scheme based on widely appreciated semi-lagrangian schemes
+of the solution efficiently (Section \ref{sec:freq_dep}). Second, we develop an original scheme based on widely appreciated semi-lagrangian schemes
 for the discretization of time domain Maxwell's equations with a linear current.
@@
 We compare this result with 
-$\hat{\mathbf{E}}\mathrm{e}^{\mrev{-i\omega} t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which corresponds to
+$\hat{\mathbf{E}}\mathrm{e}^{-i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which corresponds to
 $\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
-\urev{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principles. 
+Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principles. 
 In application to a non-resonant case of (\ref{eq:main_frequency_domain_intro}), equipped with boundary conditions, the limited absorption principle states that the solution of (\ref{eq:seq_regularized})
@@
 \cite{Morawetz, Eidus}.
-The commutation between the two principles then writes as}
+The commutation between the two principles then writes as
 $
@@
 see Figure \ref{fig:limits}. 
-Even though it is true for standard linear wave problems, it is not clear \mrev{if it still holds} in the singular case 
-of the hybrid resonance.
 \begin{figure}
@@
 \path[-stealth, font=\scriptsize] (m-1-2) edge node [right] {$t\rightarrow +\infty$} (m-2-2);
-
 % \path[-stealth] (m-2-1.east) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
@@
 \end{figure}
+Even though it is true for standard linear wave problems, it is not clear if it still holds in the singular case 
+of the hybrid resonance.
 

### 2015-09-15 report_clean_final/TEX/numerics.tex
fixed multiple typos extra

@@
 of the numerical solution as the absorption parameter $\nu$ tends to zero. The experiments in this section were 
-performed with \urev{our} code written in Octave.  
+performed with our code written in Octave.  
 We implemented the scheme described in Section \ref{sec:discr} for a case of $P_{1}$-space used 
@@
 The last part of the section deals with the question of the equivalence of the limiting absorption and limited amplitude 
-principle. We compare the solutions obtained as $\nu\rightarrow 0$ with the help of \mrev{the frequency   
-and time domain codes }(computed for large values of time). 
-The time-domain code implements the scheme described in \urev{Section \ref{sec:staggered_discretization}} and 
+principle. We compare the solutions obtained as $\nu\rightarrow 0$ with the help of the frequency   
+and time domain codes (computed for large values of time). 
+The time-domain code implements the scheme described in Section \ref{sec:staggered_discretization} and 
 is written in Fortran.
@@
 \label{eq:parameters}
-\alpha(x)=x^2+1,\qquad \delta(x)=-\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}, \qquad \mrev{\nu=0, \qquad \theta=0.}
+\alpha(x)=x^2+1,\qquad \delta(x)=-\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}, \qquad \nu=0, \qquad \theta=0.
 \end{align}
-\urev{In this case $E_{y}$ that solves (\ref{eq:main_frequency_domain})  satisfies the Airy equation, see also Remark \ref{remark:other},
+In this case $E_{y}$ that solves (\ref{eq:main_frequency_domain})  satisfies the Airy equation, see also Remark \ref{remark:other},
 \begin{align*}
@@
 \end{align*}
-The physical solution of this equation, the Airy function \urev{$\Ai(x)$}, see \cite[Chapter 10.4]{abramowitz_stegun}, is analytic and 
-decays rapidly as $x\rightarrow \infty$. }
-\mrev{Hence, choosing $H$ sufficiently large (the actual value used in the experiments $H=10$, where $\left|\Ai'(10)\right|<1e-9$) and the boundary conditions
+The physical solution of this equation, the Airy function $\Ai(x)$, see \cite[Chapter 10.4]{abramowitz_stegun}, is analytic and 
+decays rapidly as $x\rightarrow \infty$. 
+Hence, choosing $H$ sufficiently large (the actual value used in the experiments $H=10$, where $\left|\Ai'(10)\right|<1e-9$) and the boundary conditions
 \begin{align}
 \label{eq:bcs_airy}
-\partial_{x}E_{y}(-L)+2iE_{y}(-L)=2i\Ai(-L)+\Ai'(-L),\qquad 
+\partial_{x}E_{y}(-L)+2iE_{y}(-L)=\Ai'(-L)+2i\Ai(-L),\qquad 
 \partial_{x}E_{y}(H)=0\approx \Ai'(H),
 \end{align}
-the exact solutions are: $\Ai(x)$ for the unknown $E_{y}$, and $i\frac{\delta(x)}{\alpha(x)}\Ai(x)$ for $E_{x}$. \urev{Hence both functions are smooth}. 
-The well-posedness of the respective variational formulation is due to Remark \ref{remark:other}. }
+the exact solutions are: $\Ai(x)$ for the unknown $E_{y}$, and $i\frac{\delta(x)}{\alpha(x)}\Ai(x)$ for $E_{x}$. Hence both functions are smooth. 
+The well-posedness of the respective variational formulation is due to Remark \ref{remark:other}.
 
@@
 Importantly, the obtained convergence rates are in agreement with known estimates of the standard theory of convergence~\cite[Chapter 5.7,
-Chapter 0.4]{brenner}, \mrev{provided that the Aubin-Nitsche lemma \cite[Theorems 3.2.4,3.2.5]{ciarlet_fem} holds for the variational formulation.}  
+Chapter 0.4]{brenner}, provided that the Aubin-Nitsche lemma~\cite[Theorems 3.2.4, 3.2.5]{ciarlet_fem} holds for the variational formulation.  
 \begin{figure}
@@
     \end{tikzpicture}
-    \caption{Convergence rates for the \mrev{problem described in Section \ref{sec:airy_fd_validity} (the problem (\ref{eq:main_frequency_domain}) discretized as (\ref{eq:simple_system})} 
-    with the parameters (\ref{eq:parameters}) and the \mrev{boundary condition (\ref{eq:bcs_airy}))}. \mrev{Here $E_{y}^{c}(x)=\Ai(x)$ and 
-    $E_{x}^{c}(x)=i\frac{\delta(x)}{\alpha(x)}\Ai(x)$.}}
+    \caption{Convergence rates for the problem described in Section \ref{sec:airy_fd_validity} (the problem (\ref{eq:main_frequency_domain}) discretized as (\ref{eq:simple_system})
+    with the parameters (\ref{eq:parameters}) and the boundary condition (\ref{eq:bcs_airy})). Here $E_{y}^{c}(x)=\Ai(x)$ and 
+    $E_{x}^{c}(x)=i\frac{\delta(x)}{\alpha(x)}\Ai(x)$.}
     \label{fig:conv_rate}
@@
 Let us consider the case of the resonance, more precisely, we choose sufficiently smooth
-$\alpha,\delta$, s.t. $\alpha(0)=0$ and $\delta(0)\neq 0$, and the solvability conditions 
+$\alpha,\delta$, so that $\alpha(0)=0$ and $\delta(0)\neq 0$, and the solvability conditions 
 of Lemma \ref{lemma:well_posedness}  are satisfied. 
-For simplicity, let us assume \mrev{that $\alpha(x)$ is smooth and }
+For simplicity, let us assume that $\alpha(x)$ is smooth and 
 \begin{align}
 \label{eq:cond}
- \mrev{\alpha(x)=-x \text{  in some neighbourhood of $0$ }}.
+\alpha(x)=-x \text{  in some neighbourhood of $0$ }.
 \end{align}
-\mrev{Let $h>0$ denote the meshwidth. }Given $\mathbf{V}_{h}=P_{h}^{1}\times P_{h}^{1}$, with $P_{h}^{1}$ consisting of piecewise-linear (hat) functions, 
-\mrev{and $E^{\nu}_{x},\;E^{\nu,h}_{x}$ being respectively the exact and the numerical solution, }
+Let $h>0$ denote the meshwidth. Given $\mathbf{V}_{h}=P_{h}^{1}\times P_{h}^{1}$, with $P_{h}^{1}$ consisting of piecewise-linear (hat) functions, 
+and $E^{\nu}_{x},\;E^{\nu,h}_{x}$ being respectively the exact and the numerical solution, 
 we look for the ratio $h(\nu)$ that would ensure the bound on the absolute error 
@@
 \begin{itemize}
- \item \lastrev{The C\'ea lemma} applied to the problem (\ref{vf1dcase}); here \mrev{$\mathbf{E}^{\nu}$ is the exact solution, 
- $\mathbf{E}^{\nu,h}$ is the computed solution}, and $C_c$ and $C_i$ are respectively the continuity and the coercivity constants:
+ \item \lastrev{The C\'ea lemma} applied to the problem (\ref{vf1dcase}); here $\mathbf{E}^{\nu}$ is the exact solution, 
+ $\mathbf{E}^{\nu,h}$ is the computed solution, and $C_c$ and $C_i$ are respectively the continuity and the coercivity constants:
 \begin{align}
@@
 where $I^{h}$ is an interpolation operator onto $P_{h}^{1}$. 
-\item \mrev{An explicit bound on $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$ based on \cite{Despres_2014} and \cite[Proposition 1]{singular_solutions}. 
+\item An explicit bound on $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$ based on \cite{Despres_2014} and \cite[Proposition 1]{singular_solutions}. 
 First of all, we 
@@
 $\rho_{\nu}$ is a smooth function s.t. $\rho_{\nu}(0)=0,$ with the derivative $\rho_{\nu}'(0)=1$, 
-the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R}_{*}$. 
-}
-\item \mrev{An explicit bound on $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ based on \cite{singular_solutions}. As before, we 
+the point $X_{\nu}\approx i\nu c+O(\nu^2)$, for some $c\in\mathbb{R}\setminus\{0\}$.
+
+\item An explicit bound on $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ based on \cite{singular_solutions}. As before, we 
 will assume that the main contribution to $\|\left(E_{y}^{\nu}\right)''\|_{L^{2}(\Omega)}$ comes from the behaviour in the vicinity of the resonance, where,
@@
 where $\rho_{\nu},X_{\nu}$ are is in (\ref{eq:exact}), 
-and $p_{\nu}(x),\; S_{2}^{\nu}(x)$ are smooth functions, which, together with their derivatives, are bounded independently of $\nu$ 
-for all sufficiently small values of $\nu$.}
+and \lastrev{$p_{\nu},\; S_{2}^{\nu}$} are smooth functions, which, together with their derivatives, are bounded independently of $\nu$ 
+for all sufficiently small values of $\nu$.
 \end{itemize}
@@
 \end{align}
-\mrev{
 First of all let us examine the behaviour the derivatives of $E_{y}^{\nu}$ in the vicinity of the resonance, 
@@
 and recalling that $\rho_{\nu}(x-X_{\nu})=x-X_{\nu}+O((x-X_{\nu})^2)$ in the vicinity of the resonance), and is uniformly bounded for sufficiently small $\nu$, together with its derivatives. 
-The same holds for the second term. To examine the behaviour of $\left(\tilde{E}_{y}^{\nu}\right)''$, 
-we study solely the singular first term of (\ref{eq:eynuprime})
+\nrev{The second term is also well-defined in $x=0$}. To examine the behaviour of $\left(\tilde{E}_{y}^{\nu}\right)''$, \nrev {it is sufficient to 
+we study solely the singular first term of (\ref{eq:eynuprime})}
 \begin{align*}
@@
 \end{align}
-}
+
 Then there exists $c>0$, s.t. for all sufficiently small $\nu$ 
 \bealn
- \left\|\frac{d^2E_x^{\nu}}{dx^2}\right\|_{L^2}^{2}&\leq c\int\limits_{-L}^{H}\frac{1}{(x^2+\nu^2)^{3}}dx
+ \lastrev{\left\|\frac{d^2E_x^{\nu}}{dx^2}\right\|_{L^2}^{2}}&\leq c\int\limits_{-L}^{H}\frac{1}{(x^2+\nu^2)^{3}}dx
  % &=c\left.
@@
 To do so, we conduct the  numerical experiment with parameters for Problem 
-(\ref{eq:main_frequency_domain}) as given in Table \ref{tab:parameters}. \mrev{Recall as well that $\theta=0$. }
+(\ref{eq:main_frequency_domain}) as given in Table \ref{tab:parameters}. Recall as well that $\theta=0$. 
 \begin{table}[htb!]
@@
 \end{table}
-Denoting by \mrev{$E_{x}^{\nu,h}$ the solution $E_{x}(x)$} computed on the mesh with \mrev{width $h$ and 
- absorption $\nu$, and by $E_{x}^{\nu}$} the solution computed on a mesh multiple times finer (\arev{more precisely, the reference mesh
-was typically 10-200 times finer, except when the computation was performed for very small values of $h$ when results were compared with results computed on twice finer meshes}), let 
+Denoting by $E_{x}^{\nu,h}$ the solution $E_{x}(x)$ computed on the mesh with width $h$ and 
+ absorption $\nu$, and by $E_{x}^{\nu}$ the solution computed on a mesh multiple times finer (more precisely, the reference mesh
+was typically 10-200 times finer, except when the computation was performed for very small values of $h$ when results were compared with results computed on twice finer meshes), let 
 \begin{align}
@@
 \caption{We consider the problem (\ref{eq:main_frequency_domain}) with the parameters 
-defined in Table \ref{tab:parameters}. In the left figure the \urev{dependence} of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated.  
-In the right figure we show the computed solutions for this problem (\urev{for brevity denoted by $E_{x,y}^{\nu}$}) for different values of $\nu$. }
+defined in Table \ref{tab:parameters}. In the left figure the dependence of $h_{\epsilon}$ as defined by (\ref{eq:def_epsilon}) on $\nu$ is demonstrated.  
+In the right figure we show the computed solutions for this problem (for brevity denoted by $E_{x,y}^{\nu}$) for different values of $\nu$. }
 \label{fig:dependence}
@@
 \eealn
- is ensured by choosing $h$ as \mrev{$\beta_{\epsilon}\nu^{\frac{3}{2}}$}, \mrev{$\beta_{\epsilon}>0$.}
+ is ensured by choosing $h$ as $\beta_{\epsilon}\nu^{\frac{3}{2}}$, $\beta_{\epsilon}>0$.
 \end{remark}
@@
  number for $\nu=0$ is not shown, however, for all values of $h$ as shown in the plot, the matrix was non-singular even for $\nu=0$). 
- The right plot shows \mrev{$E_{y}^{\nu,h}$} computed on different meshes for small $\nu$. It can be seen that for $h=10^{-2}$ and $h=10^{-3}$ the solutions 
+ The right plot shows $E_{y}^{\nu,h}$ computed on different meshes for small $\nu$. It can be seen that for $h=10^{-2}$ and $h=10^{-3}$ the solutions 
  computed for $\nu=0$ are almost indistinguishable.}
@@
 based on co-localised semi-lagrangian discretization is valid even for the resonance.
-The numerical tests have been kept to a minimum, and \arev{many more} are needed to fully validate
+The numerical tests have been kept to a minimum, and many more are needed to fully validate
 the concept.
@@
 is the following. We use a 7th order semi-lagrangian scheme, and the CFL is $\nu=0.5$.
-The \arev{peak} is the hybrid resonance, visible on $E_x$ and $u_x$.
+The peak is the hybrid resonance, visible on $E_x$ and $u_x$.
 The total energy $\mathcal E(t)$ is the physical energy. 
-The comparison with Figures \ref{fig:dependence} and \ref{fig:resonance_nus_ey_x} shows that the 
-singular nature of the \arev{resonance} is captured by this new scheme without any doubt.
+The comparison with Figures \ref{fig:dependence} and \nrev{\ref{fig:resonance_nus_ex_t}} shows that the 
+singular nature of the resonance is captured by this new scheme without any doubt.
 
-\urev{Notice that in this case we shifted the computational domain is shifted
-for visualization purposes,
-so that $L=0$ and the point where the resonance occurs is $x_h=20$.}
+Notice that in this case \nrev{ we shifted the computational domain 
+for visualization purposes},
+so that $L=0$ and the point where the resonance occurs is $x_h=20$.
 

### 2015-09-15 report_clean_final/TEX/timedomain.tex
Correcting typoes as asked by the referee
fixed multiple typos extra

@@
 \section{Time-Dependent Problem Discretization}
-\arev{
 We develop hereafter the discretization of the time-dependent one-dimensional model (\ref{eq:main_model}), for the particular case $\theta=0$. 
-We first show how this system can be discretized thanks to a Yee scheme suggested in \cite{stable_yee_plasma_current}, then a scheme based on semi-lagrangian discretization is employed.}
+We first show how this system can be discretized thanks to a Yee scheme suggested in \cite{stable_yee_plasma_current}, then a scheme based on semi-lagrangian discretization is employed.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % \end{align}
-We compute a numerical approximation of~\eqref{eq:main_model} \mrev{with $\theta=0$} on a cartesian grid using the Yee scheme, 
+We compute a numerical approximation of~\eqref{eq:main_model} with $\theta=0$ on a cartesian grid using the Yee scheme, 
 as suggested in \cite{stable_yee_plasma_current}. Let $n$ and $\Delta t$ denote the time step index and the time step, as usual the discrete time is $t_n = n \Delta t$. 
@@
  \epsilon_0\frac{ E_{y}^{n+1}-E_y^{n}}{\Delta t}+\partial_x H_z^{n+1/2}=-eN_e \frac{u_y^{n+1}+u_{y}^{n}}{2},\nonumber\\
- \mu_0\frac{ H_z^{n+1/2}-H_z^{n-1/2}}{\Delta t}+\partial_x E_y^{n}-\partial_y E_x^{n}=0, \label{eq:tdiscretizedpb}\\
+ \lastrev{\mu_0\frac{ H_z^{n+1/2}-H_z^{n-1/2}}{\Delta t}+\partial_x E_y^{n}=0,} \label{eq:tdiscretizedpb}\\
  m_e\frac{ u_{x}^{n+1}-u_x^{n}}{\Delta t}=e\frac{E_x^{n+1}+E_x^{n}}{2}+e\frac{u_y^{n+1}+u_{y}^{n}}{2}B_0-\nu m_e \frac{u_x^{n+1}+u_x^{n}}{2},\nonumber\\
@@
  \eealn
-In Yee scheme, the different components of the vector fields 
+In \lastrev{the} Yee scheme, the different components of the vector fields 
 are defined on staggered points. 
 We summarize this discretization on Fig.~\ref{schemepos} where the positions 
-of \urev{$E_x$}, $u_x$ (black dots), $E_y$, $u_y$ (blue dots) and $H_z$ (red dots) 
+of $E_x$, $u_x$ (black dots), $E_y$, $u_y$ (blue dots) and $H_z$ (red dots) 
 on the discretized grid in space and time are displayed. The fully discretized system then reads
@@
 \ben
-\eps_0 \frac{E_y\ihnp-E_y\ihn}{\Delta t}+ \frac{H_z\ipnh-H_z\inh}{\Delta x} = -eN_x \frac{u_y\ihnp + u_y\ihn}{2} ,
+\eps_0 \frac{E_y\ihnp-E_y\ihn}{\Delta t}+ \frac{H_z\ipnh-H_z\inh}{\Delta x} = -e\lastrev{N_e} \frac{u_y\ihnp + u_y\ihn}{2} ,
 \label{eq:ns2}
@@
 \ben
- \frac{H_z\inh-H_z\inmh}{\Delta t}+ \frac{E_y\ihn-E_y\imhn}{\Delta x}=0,
+\lastrev{\mu_0} \frac{H_z\inh-H_z\inmh}{\Delta t}+ \frac{E_y\ihn-E_y\imhn}{\Delta x}=0,
  \label{eq:ns3}
@@
 \ben 
-m_e \frac{u_x\inp-u_x\midin }{\Delta x} = e N_e \frac{E_x\inp+E_x\midin}{2}-\nu m_e\frac{u_x\inp+u_x \midin}{2}+ eB_0\frac{u_y\ihn+u_y\ihnp}{2},
+m_e \frac{u_x\inp-u_x\midin }{\lastrev{\Delta t}} = \lastrev{e} \frac{E_x\inp+E_x\midin}{2}-\nu m_e\frac{u_x\inp+u_x \midin}{2}+ eB_0\frac{u_y\ihn+u_y\ihnp}{2},
 \label{eq:ns4}
@@
 \ben
-m_e \frac{u_y\ihnp-u_y\ihn}{\Delta t} = eN_e \frac{E_y\ihnp + E_y\ihn}{2}- \nu m_e \frac{u_y\ihnp +u_y\ihn}{2}-eB_0 \frac{u_x\midin+u_x\inp}{2},
+m_e \frac{u_y\ihnp-u_y\ihn}{\Delta t} = \lastrev{e}\frac{E_y\ihnp + E_y\ihn}{2}- \nu m_e \frac{u_y\ihnp +u_y\ihn}{2}-eB_0 \frac{u_x\midin+u_x\inp}{2},
 \label{eq:ns401}
@@
 In the tests, we used Strang's stencils described in \cite{cedar} with CFL $\nu=0.5$, at order 7. 
-It  yields to the chain 
+It  yields  the chain 
 $(E_y,H_z)_i^n\mapsto ( w,z)_i^n\mapsto ( w,z)_i^{n*}\mapsto (E_y,H_z)_i^{n*} $.

### 2015-09-15 report_clean_final/TEX/FD.tex
+ one typo

@@
 where the frequency 
-$\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane. The choice of the non-zero plasma friction $\nu>0$ is a regularization of the problem.
-
+$\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane.
+The choice of the non-zero plasma friction $\nu>0$ is a regularization of the problem.
 A series expansion as $\nu\rightarrow 0$ gives at leading orders
@@
 
-For brevity, from now on we will denote $\frac{\omega^2}{c^2}\alpha_{\omega},\; \frac{\omega^2}{c^2}\delta_{\omega}$ by $\alpha,\; \delta$ and consider a sequence of regularized problems. 
+For brevity, from now on we will denote $\frac{\omega^2}{c^2}\alpha_{\omega},\; \frac{\omega^2}{c^2}\delta_{\omega}$ by $\alpha,\; \delta$ and consider a sequence of regularized problems 
 \begin{align}
@@
 \ben
- \|\mathbf{v}\|_{\mathbf{V}}^2= \|v_1\|_{L^{2}(\Omega)}^2+\|v_2\|_{H^{1}(\Omega)}^2 \qquad   \text{for }\nrev{\mathbf{v}=(v_1,\; v_2)},
+ \|\mathbf{v}\|_{\mathbf{V}}^2= \|v_1\|_{L^{2}(\Omega)}^2+\|v_2\|_{H^{1}(\Omega)}^2 \qquad  \nrev{\text{for }\mathbf{v}=(v_1,\; v_2)},
 \een

### 2015-09-15 report_clean_final/TEX/absorption.tex
formatting

@@
 For the resonance case, we choose the parameters as in Table \ref{tab:parameters_resonance}.
+Since $\alpha(x)=(1-2N_e(x))$, $\alpha(0)=0$, and clearly, $\delta(0)\neq 0$.
+We compare the results for $\nu=10^{-2},\; 10^{-3},\; 10^{-4}$ in Fig.
+\ref{fig:resonance_nus_ey_x},
+\ref{fig:resonance_nus_ex_x}, \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}, \ref{fig:resonance_nus_eyx_t}. 
 \begin{table}[htb!]
@@
 \end{table}
-Since $\alpha(x)=(1-2N_e(x))$, $\alpha(0)=0$, and clearly, $\delta(0)\neq 0$. We compare the results for $\nu=10^{-2},\; 10^{-3},\; 10^{-4}$ in Fig. \ref{fig:resonance_nus_ey_x}, 
-\ref{fig:resonance_nus_ex_x}, \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}, \ref{fig:resonance_nus_eyx_t}. 
-%In the time domain, we chose the discretization size $\Delta x=0.025$. 
 The harmonic dependence of the solution on time is demonstrated by fixing $x_c$ inside the domain and plotting 

### 2015-09-15 report_clean_final/TEX/absorption.tex
changed the order of figs... to make a placement for them

@@
 
-\begin{figure}[htb]
-\begin{tabular}{cc}
-\includegraphics[height=0.2\textwidth]{pics_time_domain/airy/figure_nu1e2-crop.pdf} & \includegraphics[height=0.2\textwidth]{pics_time_domain/airy/figure_nu1e2_2-crop.pdf}
-\end{tabular}
-\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ to the problem described in Section \ref{section:absorption_airy} on time for large times is demonstrated in the left figure.  
-In the right figure we show the solution to the same problem for $\nu=10^{-2}$, for two fixed moment of times.}
- \label{fig:nu1e2_harmon}
-\end{figure}
-
-\FloatBarrier
 Fig.~\ref{fig:nu1e4_harmon} (left) shows the solutions at a fixed point in space for $\nu=10^{-4}$. As previously, 
@@
 see Fig.~\ref{fig:nu1e4_harmon} (right). 
+\begin{figure}[htb]
+\begin{tabular}{cc}
+\includegraphics[width=0.45\textwidth]{pics_time_domain/airy/figure_nu1e2-crop.pdf} & \includegraphics[height=0.168\textwidth]{pics_time_domain/airy/figure_nu1e2_2-crop.pdf}
+\end{tabular}
+\caption{Dependence of the solution $E_{y}^{\nu}(x_c,t)$ to the problem described in Section \ref{section:absorption_airy} on time for large times is demonstrated in the left figure.  
+In the right figure we show the solution to the same problem for $\nu=10^{-2}$, for two fixed moment of times.}
+ \label{fig:nu1e2_harmon}
+\end{figure}
 \begin{figure}
@@
 \ref{fig:resonance_nus_ey_x},
-\ref{fig:resonance_nus_ex_x}, \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}, \ref{fig:resonance_nus_eyx_t}. 
+\ref{fig:resonance_nus_ex_x},  \ref{fig:resonance_nus_ey_t}, \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_eyx_t}. 
 \begin{table}[htb!]
@@
 \begin{tabular}{cc}
-\includegraphics[width=0.45\textwidth]{pics_time_domain/res/ex_fixed_t-crop.pdf}&
-\includegraphics[width=0.45\textwidth]{pics_time_domain/res/ex_fixed_t_1e3-crop.pdf}
-\end{tabular}
-\caption{The figures demonstrate the dependence of the solutions 
-$E_x^{\nu}(x,t)$ to the problem described in Section \ref{sec:resn} on $x$ for fixed values of $t$. }
-\label{fig:resonance_nus_ex_t}
-\end{figure}
-\begin{figure}
-\begin{tabular}{cc}
 \includegraphics[width=0.4\textwidth]{pics_time_domain/res/ey_fixed_t_1e3-crop.pdf}&
@@
 \end{figure}
-
+\begin{figure}
+\begin{tabular}{cc}
+\includegraphics[width=0.45\textwidth]{pics_time_domain/res/ex_fixed_t-crop.pdf}&
+\includegraphics[width=0.45\textwidth]{pics_time_domain/res/ex_fixed_t_1e3-crop.pdf}
+\end{tabular}
+\caption{The figures demonstrate the dependence of the solutions 
+$E_x^{\nu}(x,t)$ to the problem described in Section \ref{sec:resn} on $x$ for fixed values of $t$. }
+\label{fig:resonance_nus_ex_t}
+\end{figure}
 \begin{figure}
@@
 
-Figures \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_ey_t}, \ref{fig:resonance_nus_eyx_t} show that in the case of the resonance
+Figures \ref{fig:resonance_nus_ey_t}, \ref{fig:resonance_nus_ex_t}, \ref{fig:resonance_nus_eyx_t} show that in the case of the resonance
 \nrev{the limiting amplitude solution is achieved}, and both \nrev{limiting amplitude and limited absorption solutions} are in close agreement (but in the points close to a point where the resonance occurs).
@@
 for smaller $\nu$.
-
-%\FloatBarrier

### 2015-09-15 report_clean_final/TEX/numerics.tex
changed the order of figs... to make a placement for them

@@
 \end{table}
+
 Denoting by $E_{x}^{\nu,h}$ the solution $E_{x}(x)$ computed on the mesh with width $h$ and 
@@
 \end{figure}
+\begin{figure}%[h!]
+\begin{tabular}{cc}
+\includegraphics[height=0.32\textwidth]{pics_frequency_domain/fig_cond_num.pdf}&
+ \includegraphics[height=0.32\textwidth]{pics_frequency_domain/ey_resonance.pdf}
+ \end{tabular}
+ \caption{
+ We consider the problem (\ref{eq:main_frequency_domain}) with the parameters 
+defined in Table \ref{tab:parameters}. The left plot demonstrates the dependence of the condition number of the system (\ref{eq:simple_system}) on $\nu$, for different values of $h$ (the condition 
+ number for $\nu=0$ is not shown, however, for all values of $h$ as shown in the plot, the matrix was non-singular even for $\nu=0$). 
+ The right plot shows $E_{y}^{\nu,h}$ computed on different meshes for small $\nu$. It can be seen that for $h=10^{-2}$ and $h=10^{-3}$ the solutions 
+ computed for $\nu=0$ are almost indistinguishable.}
+ \label{fig:small_nu}
+\end{figure}
 We can see that Estimate (\ref{eq:estimate_h}) is pessimistic compared to the one suggested by (\ref{eq:def_epsilon}), 
@@
 As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Fig.~\ref{fig:small_nu}.
-\begin{figure}[htb!]
-\begin{tabular}{cc}
-\includegraphics[height=0.32\textwidth]{pics_frequency_domain/fig_cond_num.pdf}&
- \includegraphics[height=0.32\textwidth]{pics_frequency_domain/ey_resonance.pdf}
- \end{tabular}
- \caption{
- We consider the problem (\ref{eq:main_frequency_domain}) with the parameters 
-defined in Table \ref{tab:parameters}. The left plot demonstrates the dependence of the condition number of the system (\ref{eq:simple_system}) on $\nu$, for different values of $h$ (the condition 
- number for $\nu=0$ is not shown, however, for all values of $h$ as shown in the plot, the matrix was non-singular even for $\nu=0$). 
- The right plot shows $E_{y}^{\nu,h}$ computed on different meshes for small $\nu$. It can be seen that for $h=10^{-2}$ and $h=10^{-3}$ the solutions 
- computed for $\nu=0$ are almost indistinguishable.}
- %It can be seen that for meshes that are coarse 
- %with respect to $\nu$ (e.g. $\nu=10^{-4}, \; h=10^{-2}$, or $\nu=0,\; h=10^{-2}$), the computed solution seems to be only piecewise-continuous in $\nu$, 
- %while for finer meshes and $\nu>0$ the solution seems to be smooth. }
- \label{fig:small_nu}
-\end{figure}
-%\begin{table}[ht!]
-%\begin{tabular}{c|ccccccccc}
-%\diagbox[width=10em]{$h$}{$\nu$}& 100 & 10 & 1 & 0.1 & 1e-2 & 1e-3 & 1e-4 & 1e-8 & 0\\
-% \hline
-%1 & 3.9634&4.3787 &4.987&36.949&42.394& 42.757 &42.79&42.793&42.793\\
-%\hline
-%0.5&      3.9931& 6.87&48.473 & 168.41  &207.34  & 209.63 & 209.83 & 209.85&  209.85\\
-%\hline
-% 0.1&      16.09  &     159.56  &     1146.1   &    8304.1   &     19169  &      20270   &     20344   &     20352   &     20352\\
-% \hline
-%0.05&      64.046  &     637.18  &     4686.2   &     38876 &  1.4e5 &  1.58e5 &   1.58e5 &  1.58e5 &  1.58e5\\
-%\hline
-% 0.01&       1600    &   15921 & 1.2e5  & 1.1e6 & 8.3e6  & 1.8e7   & 1.93e7  & 1.93e7  & 1.93e7\\
-%\end{tabular}
-%\caption{The condition number of the matrix of the system (\ref{eq:simple_system}) for different values of $\nu$ and $h$. }
-%\label{tab:cond_number}
-%\end{table}
 
@@
 \subsection{A validation of the semi-lagrangian scheme}
-
 With very basic simulation, we show that the numerical strategy 
@@
 singular nature of the resonance is captured by this new scheme without any doubt.
-
-Notice that in this case \nrev{ we shifted the computational domain 
-for visualization purposes},
-so that $L=0$ and the point where the resonance occurs is $x_h=20$.
-
 \begin{figure}[h]
@@
 
-%\subsubsection{No-Resonance Case}
-%We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{2}$ satisfies 
-%the Airy equation \cite{}.
-
-%We set $\omega_c=0$ (thus $\delta(x)=0$), $\omega=1$ (hence $\alpha(x)=1-N_e(x)$), 
-%choose the domain as $[-0.5, 10]$ and set the electron density $N_e(x)=1+x$. Importantly, $N_e(x)>0$ on the whole interval.
-%The boundary conditions in (\ref{eq:bcs}) are chosen as $G=Ai'(0.5)$. 
-%In all the experiments in this section the CFL number was chosen to be equal to 0.5.
-
-%First let us fix $\nu=1e-2$. 
-%To demonstrate that the limiting amplitude principle indeed holds, we fix a point $x=x_c$ 
-%inside the domain $(-L,\; H)$ and plot the dependence of the solution $E_{y}^{\nu}(x_c,t), \; \hat{E}_2^{\nu}(x_c)\mathrm{e}^{it}$ 
-%on time $t$ for a range of $t\gg 1$ in Figure \ref{fig:nu1e2_harmon}.
+Notice that in this case \nrev{ we shifted the computational domain 
+for visualization purposes},
+so that $L=0$ and the point where the resonance occurs is $x_h=20$.
+\FloatBarrier

### 2015-09-15 report_clean_final/TEX/resume.tex

@@
 Notre but est ici triple.
-D'un c\^ot\'e nous
-approchons num\'eriquement la formulation fr\'equentielle \`a l'aide d'\'el\'ements finis,
- et de l'autre nous \'etudions les solutions r\'esonnantes dans le domaine temporel, \`a l'aide de deux m\'ethodes distinctes de diff\'erences finies.
-Finalement nous comparons  num\'eriquement les solutions fr\'equentielles avec le comportement en temps long des solutions temporelles, dans le cadre
+Dans un premier temps, nous
+approchons num\'eriquement la formulation fr\'equentielle \`a l'aide d'\'el\'ements finis.
+Dans un deuxi\`eme temps, nous \'etudions les solutions r\'esonnantes dans le domaine temporel, \`a l'aide de deux m\'ethodes distinctes de diff\'erences finies.
+Finalement, nous comparons  num\'eriquement les solutions fr\'equentielles avec le comportement en temps long des solutions temporelles, dans le cadre
 des principes d'amplitude et d'absorption limite.
